### 2018-03-09 paper.Rmd
commit 9.3.18_2

---
title: 'The effects of symbols and information in government communication on citizens  trust in policy: Evidence from a survey experiment'
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  word_document: default
  pdf_document:
    toc: yes
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

Preliminary draft. Last edited at `r Sys.Date()`

```{r , include=FALSE, echo=FALSE}
load(".RData")
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(knitr)
library(tidyverse)
```

<br>

---

# Abstract

*Effective public communications have been proposed as a remedy for citizens' distrust in government. The studies that explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies. Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g. logos, images and celebrities). Still, we lack theoretical understanding of the different mechanisms underlying citizens' responses to information and symbolic elements, and accordingly - the interaction between them. Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements have a greater effect on citizens' trust the less citizens perceive the issue as personally relevant. Second, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in ill-conceived policies. I put these hypotheses to test through a survey experiment, where I examine 859 Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste. The policies are presented to subjects under different conditions of substantive information (logically persuasive vs. unpersuasive policies) and symbolic elements (logo, green color, and celebrities endorsers). I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others. The results do not support the hypothesis that personal relevance attenuates the effect of symbols. Rather, they suggest that symbolic elements increase citizens' trust in ill-perceived policies, by distracting them from scrutinizing their content.*

---

<br>

# Introduction

Public administration scholars are often concerned about the implications of citizens’ low trust in government, and their undervaluation of public-service performance. One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens. Congruently, over the past generation, many economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014]. In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].

The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g. @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017]. Congruently, public communications are expected to increase citizens' trust insofar as they provide citizens favorable information on organizations' performance and logically persuasive explanations for their policies. At the same time, experiment-based studies that explored the responses of citizens to variation in substantive information have revealed potential cognitive biases that may distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].

Recently, a few studies also pointed to the potential effect of the *symbolic* elements entangled in government communications, such as brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016]. These symbolic elements are strategically designed to evoke citizens’ positive associations and emotions. Their processing requires relatively little cognitive effort, and is often unconscious and automatically activated without much thinking, as opposed to the processing of substantive information which requires elaboration. Whereas the responsiveness of citizens to substantive information is perceived as a positive phenomenon from a normative view of democratic theory, the potential effect of symbolic elements can be problematic. Shaping citizens' view of governments through symbols stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking. Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape from justified public criticism [@alonbarkat_2017].

Hence, in order to assess the positive and negative possible implications of government communications with citizens, we need to understand the nature of the psychological effect of symbolic elements on citizens' attitudes' formation, and its limitations. To date, public administration research still lacks theory and robust empirical evidence of the mechanisms through which symbolic elements in public communications can increase citizens trust, and their interaction with the substantive content of information in government communications, which is perceived as the basis for rational attitudes formation. Therefore, this study focuses on the following questions: *Under what conditions can symbolic elements in governemnt communication increase citizens' trust in governemnt policy?* Specifically, *does the effect of symbolic elements depend on the substantive information presented in the communication?* *Can these symbols offset the rational, negative effect of logically unpersuasive arguments?*

Given the theoretical gap in existing public administration literature, I address these research questions by introducing a theoretical framework from social psychology - the Elaboration Likelihood Model (ELM). ELM theorizes the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences on attitude change [@petty_1986; @petty_2011]. Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that can be transferred to the government entity or policy, and thereby increasing their trust in it. This effect is likely to be attenuated the more citizens perceive the communication as personally relevant, and therefore motivated to elaborate on it. *Second*, symbolic elements may decrease citizens' inclination to elaborate on the communication and scrutinize it, thus causing them to disregard substantive information that would have affected their trust. Congruently, symbols are likely to have greater effect when entangled in communications that describe logically unpersuasive policies or report poor performance.

To empirically test these theoretical expectations about the effect of symbolic elements on citizens' trust, and their interaction with the substantive information in the communication and the personal relevance of the issue, I conducted a large randomized survey experiment in a fairly realistic setting among `r SVIVA2_01%>%nrow()` Israeli citizens. The experiment focuses on the empirical case of the Israeli Environment Protection Ministry (hereafter EPM), and examines citizens' trust in two policy plans: reducing the air pollution in a specific area in the country - the Bay of Haifa, and reducing domestic waste and increasing recycling. In the experiment, the two policies are presented to subjects under different experimental conditions of substantive information (logically persuasive vs. unpersuasive policy plans) and symbolic elements (ministry’s logo, green color, and celebrities from public campaigns, compared with two control groups). To account for variation in perceived personal relevance, I compared citizens who reside in the polluted Haifa-Bay area with other citizens from selected cities with a similar profile. In addition, I tested the effect of personal relevance experimentally, by priming subjects to think about environmental issues in their area of residence.

I find that the symbolic elements increased citizens' trust in both policies. In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about the negative information. I did not find any support for the hypothesis that the effect of the symbolic elements is attenuated by the  perceived personal relevance of the policy issue. I discuss the theoretical and normative implications of these findings.

<br>

# Symbolic elements in government communications and their shaping of citizens' attitudes: what do we know?

Symbols are fundamental for almost any form of human interaction, as acknowledged by early scholars of social science [@blumer_1986]. A symbol can be broadly defined as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp. 28-29]. My focus is on those symbols that are strategically used by government organizations in their public communications, and are designed to distinguish organizations and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations. Prominent examples are unique logos, colors associated with specific meanings, icons, images, and the use of celebrities as endorsers. These elements are widely used by businesses and political candidates to attract targeted consumers and voters. Yet, they can be also found in the communications  of government bureaucracies with citizens, including in their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.

By comparison with the abundant research on citizens’ responses to informative elements in public communications [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements. Recently, however, a few experimental studies tackled the issue. @marvel_2015 analyzed US citizens' responses to a television advertisement of the public Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and upbeat background music. His study shows that participants who watched the advertisement evaluated the organization's performance more positively. Still, this study did not disentangle the effects of the symbolic and informational elements of the ad on participants’ attitudes. An additional study by @karens_2016 did examine the distinct effect of symbols on citizens' trust. The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of the organization's logo in the communication of the policy plans. They found that including the organization’s logo significantly increased citizens' trust in these policies. Their results show an impressive effect size equivalent to 0.7 standard deviations [^1].

[^1]: The effect size they found was smaller with regard to the "air quality" policy compared with the "digital skills" policy which were presented (Cohen's d = 0.7 vs. 0.6). Also, the effect was smaller among subjects from the Netherlands, compared with those from Belgium and Poland (Cohen's d = 0.5 vs. 0.7).

@alonbarkat_2017 explored whether symbolic element can increase citizens' trust in poorly performing organizations. To do so, they examined Israeli citizens' trust in the Israel Electricity Corporation, a state owned company, and it's shaping by their exposure to comic cartoon figures which were routinely presented in the organization's public campaigns. They compared between citizens who were personally exposed to prolonged power outages, and others who were not. They found that the symbolic element had a positive effect on citizens' trust in the organization (a modest effect size equivalent to 0.25 standard deviations), including among those who personally experienced poor performance. Building on social psychology theory and marketing research, the scholars suggested that the effect occurs by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them (evaluative conditioning). They proposed that effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.

The aforementioned studies tend to suggest that public communications can increase citizens' trust in government organizations and their policies, not only by delivering substantive information, but also symbolically, by incorporating elements that evoke positive associations and emotions. Moreover, the findings of @alonbarkat_2017 suggest that incorporating symbolic elements in public communications can unduly compensate for poor government performance, thus pointing to their potential negative implications.

Although these studies linked between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this effect. Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective. Additionally, non of these studies has theorized and empirically tested the interaction between symbolic elements and citizens’ internalization of substantive information in communications. We do not know whether well-designed symbols reinforce, or offsets, citizens' rational responses to information. Specifically, as I explained above, it is essential to assess the possibility that symbols can compensate for negative or logically unpersuasive information, that would have yielded negative responses. To address this theoretical gap in public administration research, I propose a nuanced theoretical framework for the effects of symbols in communications and their interaction with information, building on social psychology theory on persuasive communication.

<br>

# The Elaboration Likelihood Model (ELM) of communication and persuasion

The Elaboration Likelihood Model (ELM), which has been developed in the social psychology literature to explain attitudinal responses to persuasive communication [@petty_1986; @petty_2011] provides a comprehensive theoretical framework for investigating peoples' varying responses to persuasive communications. In addition to it's general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002]. Yet, thus far, the relevance of ELM has not been directly examined in public administration research, in relation to citizens' responses to government communication.

According to ELM, people respond differently to persuasive communications, depending on the amount of thinking that they dedicate to the message content. Persuasion can occur when thinking is high or low, but the processes and consequences are likely to differ in each situation. This range between high and low degrees of thought is referred to as the "elaboration continuum". Along this continuum, there are numerous specific processes of persuasion or attitude change. At the high end of the elaboration continuum, people are likely to respond cognitively by scrutinizing the arguments central to the merits of the issue. At the low end, people may respond to simple cues automatically and unconsciously  through primitive psychological processes that require very little amount of cognitive effort. For instance, an attractive source would evoke positive emotions, that would be transferred to the evaluated object through evaluative conditioning, and lead to more favorable attitudes. These two different processes are referred to as the "central and peripheral routes for persuasion", a conceptualization that largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].

People's placement along the elaboration continuum is determined by their motivation and ability to think about the communication. For instance, a person that perceives the issue as personally relevant is motivated to invest in thinking about it, and accordingly is likely to process the communication through the central route [@petty_1979; @petty_1981; @petty_1983]. On the other hand, a person that lacks profound knowledge about the subject in the communication, will not be able to scrutinize the content, and thus is more likely to rely on peripheral cues [For a review of motivational and ability factors affecting likelihood to elaborate see @petty_1986; @petty_1998]. These different persuasion mechanisms are also likely to yield different types of attitude change. Persuasion through the central route is expected to be relatively more enduring, resistant and predictive of behavior, compared with peripheral route persuasion. Of course, much of the time, persuasion is determined by a mixture of these processes.

Overall, ELM identifies several mechanisms by which variables can affect attitudes. Variables can function as one or more of the following: (1) Providing potential arguments regarding the evaluated issue that can be scrutinized based on their logical persuasive quality (central route processing); (2) Affecting the direction of thinking (bias) by making positive or negative thoughts more likely to come to mind (in central route processing); (3) Serving as potential peripheral cues that affect attitudes in a direction consistent with their valence, such as in the abovementioned example of the attractive source; (4) Affecting the ammount of thinking people devote to the communication by affecting motivation or ability to think, thus locating them along the elaboration continuum; (5) Affecting people's confidence in their thoughts. The same variable can have different functions for people at different locations along the elaboration continuum. For instance, test... number of lines.. Also, in principle, a variable can affect attitudes in multiple ways. For instance, @petty_1983 demonstrated in a lab experiment that a famous athlet endourser in an advertisment of a new disposable razor reduces the ammount of thinking about the content of the ad, and at the same time serves as a potential peripheral cue that increases positive attitudes towards the product by transferring the positive affect from the endourser to the product.

# The multiple roles of symbols in government public communicatoins.

# Methodology

## *Empirical case background*

## *Experimental design*

# Results

---

#Discussion

---

#References

### 2018-03-09 SVIVA_exp2_01.Rmd
commit 9.3.18_3

---
title: "SVIVA_experiment 2"
author: "Saar Alon-Barkat"
date: "January 2018"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
---

Last update: `r Sys.time()`

```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      message=FALSE,
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                      dependson = NULL,
                      engine = "R", # Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  # Set the figure options
                      fig.align = "center")
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(knitr)
library(sjPlot)
library(tidyverse)
library(stringr)
library(rpivotTable)
library(DT)
library(car)
```

```{r , include=FALSE, echo=FALSE}
load(".RData")
```

```{r}
N_raw = nrow(SVIVA2_raw_00)
N=SVIVA2_00%>%nrow()
```

#Theoretical background
points for revised theoretical discussion:

* Substantive information (e.g. strong vs. weak policy plans) can influence trust through central route (serving as arguments). 
* Symbol can increase trust through 3 supplementary mechanisms: 
1. As a peripheral cue (peripheral route). Specifically, through evaluative conditioning (transfer of positive affect from the symbol).
2. As a factor that decreases citizens' **ability** to elaborate (by creating a distraction).
3. As a factor that decreases citizens' **motivation** to elaborate.

<br>
points 2&3 suggest that symbols can increase trust mainly when substantive information represents weak arguments (e.g. weak policy plan, poor performance information). 
<br>
Also, based on ELM, we expect people to be more susceptible to substantive information when they perceive the issue as more personally relevant. We expect people to be more susceptible to symbols when they perceive the issue as less personally relevant.

.             | .                   
------------------| ----------------------------------------------------------------------------------
**Hypothesis 1**   | *Variation in substantive information in communication (strong vs. weak arguemnts) can shape citizens' trust.*
**Hypothesis 2(a)**| *Familar symbols in communication can increase citizens' trust.*
**Hypothesis 2(b)**| *Symbols in communication are likely to have greater effect on trust when substantive information in communication represents weak arguments (e.g. weak policy plan).*
**Hypothesis 3(a)**| *Symbols in communication reduce elaboration of communication.*
**Hypothesis 3(b)**| *The positive effect of symbols on trust is mediated by lower levels of elaboration of communciation.*
**Hypothesis 4(a)**| *The more (less) citizens perceive a policy issue as having personal relevance for themselves, the more (less) they will be susceptible to substantive information in a communication regarding this issue.* 
**Hypothesis 4(b)**| *The more (less) citizens perceive the policy issue as having personal relevance for themselves, the less (more) they will be susceptible to symbolic elements in a communication regarding this issue.*
---

#Experimental procedure

##Description
The survey is presented to the participants as a study about citizens' attitudes about environmental policies in general. Subjects are first asked pre-manipulation questions about trust in Israel's government ministries and their policies, and participants' political ideology. Then, they are assigned to **Relevance** treatment/control conditions. Subjects in the relevance treatment group are asked about their interest in environmental issues in general, and thereafter they are asked to describe the most salient environmental issue in their area of residence (through an open question). Those in the relevance control group are asked equivalent questions about their interest in their area of profession.

Thereafter, subjects are presented with two policies of Israel's Environmental Protection Ministry: reducing air pollution in Haifa-Bay (hereafter: air) and reducing waste and increasing recycling (hereafter: waste). Policies are presented in random order. The first policy can be presented in one of 6 conditions: one of three **symbol** conditions (no symbols, fake symbols, real symbols) and one of two **informtaion** conditions (strong/weak policy). In the second policy, the symbol condition will be similar, and the information condition will be switched. After each policy they are asked about their trust in that policy. Thereafter, I ask them about their perceived elaboration regarding the second policy which was presented to them, and test their memory of it. After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the real symbols (images of celebrities from real campaigns), and whether they associate it with positive or negative thoughts. Those who were assigned to the fake logo group are also asked about the fake symbols. Finally, the participants are debriefed, and explained about the manipulations, and the possible deception.

##Conditions/manipulations: 
###Relevance

![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/relevance_man.png)

###Information

![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/information_air.png)

![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/information_waste.png)

###Symbol 
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/air_policy.png) 
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/waste_policy.png)

##Outcome variables

###Trust in policy

List of items:

**Competence**             | .                   
-------------| ----------------------------------------------------------------------------------
**Item 1**   | I believe that the measures in the policy plan will assist in fulfilling the policy goal (reducing air pollution in the Haifa Bay/reducing waste and increasing recycling).
**Item 2**| I believe that the measures in the policy plan were designed in a professional manner.

**Benevolance**             | .                   
-------------| ----------------------------------------------------------------------------------
**Item 3**| I believe that the policy plan is in the interest of citizens.
**Item 4**| I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens.

**Integrity**             | .                   
-------------| ----------------------------------------------------------------------------------
**Item 5**| I believe that the Ministry of Environmental Protection made an honest attempt to design a good policy plan.
**Item 6**| I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.

Finally, I decided to remove item 6. Believing that the Ministry intends to fulfill a bad policy plan does not entail higher trust in it, so it's problematic (but does not significantly alter the results so not critical). (Remember to thank Noam Brenner for this point)

###Elaboration

I used three measures of Elaboration: composite index of reported elaboration (5 items), total time of viewing the policy plan (reaction time - RT), a memory test in which respondents were asked to identify measures that appeared in the policy plan.

#####Perceived elaboration
List of items:

.             | .                   
-------------| ----------------------------------------------------------------------------------
**Item 1**   | I paid much attention to reading the content of the measures in the policy plan.
**Item 2**| I skimmed the measures in the policy plan. (reversed)
**Item 3**| I tried to thoroughly understand the measures in the policy plan.
**Item 4**| I tried to think to what extent do the measures assist in promoting the policy goal (reducing air pollution in the Haifa Bay/reducing waste and increasing recycling).
**Item 5**| While going through the policy plan I was thinking about other things which are not related to it. (reversed).

####memory test

![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/memory_air.png) 
![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/memory_waste.png)

---

#Data

---

##Collection

The survey was distributed via Ipanel between 28.1-1.2.2018.
The survey was distributed to 5077 citizens (2549 from Haifa-bay and 2528 from Shfela). Of these, ~330 subjects were denied of access due to threshold of gender (~60 in Haifa and ~270 in Shfela). [according to Ipanel's reports in email]. 
`r N_raw` subjects started the survey, of which `r N` completed it (`r round(N/N_raw*100,1)`%). Response rate of `r round(N/(5077)*100,1)`% (`r round(filter(SVIVA2_00,AREA==1) %>% nrow()/(2549)*100,1)`% among Haifa and `r round(filter(SVIVA2_00,AREA==0) %>% nrow()/(2528-270)*100,1)`% among Shfela). But when counting those who tried to fill the survey (including those who were denied), response rate it higher (`r round((N+330)/(5077)*100,1)`%) without significant differences between areas.
`r round(filter(SVIVA2_00,GENDER==0)%>%nrow()/N*100,1)`% are men, and the median age is `r SVIVA2_00$AGE%>%median(na.rm=T)` (mean is `r round(SVIVA2_00$AGE%>%mean(na.rm=T),1)`). `r round(filter(SVIVA2_00,MOBILE==1)%>%nrow()/N*100,1)`% completed the survey via mobile.

##Area of residence

Below are distribution of subjects across cities, and the two areas.
```{r}
sjt.frq(SVIVA2_00$AREA_reside_haifa,title="Area of residence",value.labels = c("Shfela/other","Haifa-bay"))
sjt.frq(SVIVA2_00$CITY_reside_en,title="Cities of residence")
```

<br>
Eventually, Area was coded as either residing or working/studying in the Haifa bay area (Haifa bay = 1). `r filter(SVIVA2_00,AREA==1) %>% nrow()` were coded 1 (Haifa bay) (`r round(filter(SVIVA2_00,AREA==1)%>%nrow()/N*100,1)`%), and `r filter(SVIVA2_00,AREA==0) %>% nrow()` were coded 0 (Shfela/other) (`r round(filter(SVIVA2_00,AREA==1)%>%nrow()/N*100,1)`%).

#Experiment groups

```{r , warning = FALSE, message = FALSE}
sjt.xtab(SVIVA2_00$RELEVANCE_exp,SVIVA2_00$AREA_names)
sjp.grpfrq(SVIVA2_00$RELEVANCE_exp,SVIVA2_00$AREA_names,ylim=c(0,450))
```
There were slightly more subjects in the Relevance treatment group (`r filter(SVIVA2_00,RELEVANCE_exp==1)%>%nrow()` vs. `r filter(SVIVA2_00,RELEVANCE_exp==0)%>%nrow()`) with differences within the two areas. This might indicate higher attrition rate for those in Haifa assigned to control group, compared with those assigned to the treatment group (see analyses of attrition below).

```{r , warning = FALSE, message = FALSE}
sjp.grpfrq(SVIVA2_00$SYMBOL,SVIVA2_00$AREA_names,ylim=c(0,450))
sjp.grpfrq(SVIVA2_00$INFORMATION_air,SVIVA2_00$AREA_names,ylim=c(0,450))
sjp.grpfrq(SVIVA2_00$INFORMATION_waste,SVIVA2_00$AREA_names,ylim=c(0,450))
sjp.grpfrq(SVIVA2_00$AIR_order,SVIVA2_00$AREA_names,ylim=c(0,450))
```

Also, there are relatively more Haifa subjects in the "weak policy" group (`r filter(SVIVA2_00,AREA==1,INFORMATION_air==0)%>%nrow()` vs. `r filter(SVIVA2_00,AREA==1,INFORMATION_air==1)%>%nrow()`), and in the group who first saw the air policy (`r filter(SVIVA2_00,AREA==1,AIR_order==1)%>%nrow()` vs. `r filter(SVIVA2_00,AREA==1,AIR_order==2)%>%nrow()`). (see analyses of attrition below).

# Attrition
```{r}
N_raw = nrow(SVIVA2_raw_00)
```

`r N_raw` subjects started the survey, of which `r N` completed it (`r round(N/N_raw*100,1)`%).

```{r}
SVIVA2_raw_00 = SVIVA2_raw_00 %>% 
  mutate(DROP = if_else(V10==0,1,0),
         CITY_reside_en = paste0(CITY_00$CITY_reside_en,
                                 CITY_00$CITY_reside_ipanel_en))

t22=ifelse(SVIVA2_raw_00$CITY_reside_en %in% c("HAIFA",
                                           "NESHER",
                                           "OTHER (HAIFA BAY)",
                                           "QIRYAT ATA",
                                           "QIRYAT BIALIK",
                                           "QIRYAT HAIM",
                                           "QIRYAT MOZKIN",
                                           "QIRYAT YAM"),"HAIFA",
            ifelse(SVIVA2_raw_00$CITY_reside_en %in% c("PETACH TIKVA",
                                                        "NATANIA",
                                                        "RISHON LEZION",
                                                        "OTHER"),"SHFELA",NA))

SVIVA2_raw_00 = SVIVA2_raw_00 %>% 
  mutate(AREA_reside_haifa = t22) %>% 
  mutate(RELEVANCE_exp = ifelse(DO.BR.FL_346=="Relevance_control",0,
                                if_else(DO.BR.FL_346=="Relevance_treatment",1,9))) %>% 
  mutate(RELEVANCE_exp=Recode(RELEVANCE_exp,"9=NA"),
  t23 = paste0(SVIVA2_raw_00$DO.BR.FL_269,
                    SVIVA2_raw_00$DO.BR.FL_273,
                    SVIVA2_raw_00$DO.BR.FL_291,
                    SVIVA2_raw_00$DO.BR.FL_365,
                    SVIVA2_raw_00$DO.BR.FL_375,
                    SVIVA2_raw_00$DO.BR.FL_385))

SVIVA2_raw_00 = SVIVA2_raw_00 %>% 
  mutate(AIR_order = if_else(str_detect(SVIVA2_raw_00$t23, "air")==TRUE,1,2))%>%
  mutate(WASTE_order = if_else(str_detect(SVIVA2_raw_00$t23, "waste")==TRUE,1,2))%>%
  ###information
  mutate(INFORMATION_air = if_else(str_detect(SVIVA2_raw_00$t23, "air a")==TRUE|
                                     str_detect(SVIVA2_raw_00$t23, "air b")==TRUE|
                                     str_detect(SVIVA2_raw_00$t23, "air c")==TRUE|
                                     str_detect(SVIVA2_raw_00$t23, "waste d")==TRUE|
                                     str_detect(SVIVA2_raw_00$t23, "waste e")==TRUE|
                                     str_detect(SVIVA2_raw_00$t23, "waste f")==TRUE,1,0))%>%
  mutate(INFORMATION_waste = Recode(INFORMATION_air,"0=1;1=0")) %>% 
    mutate(SYMBOL = Recode(SVIVA2_raw_00$DO.BR.FL_214,
                         "'POLICY PROGRAMS intro_control'=0;
                         'POLICY PROGRAMS intro_placebo'=1;
                         'POLICY PROGRAMS intro_symbol'=2;
                         ''=NA"))

```

**Area:**
```{r}
sjt.xtab(SVIVA2_raw_00$AREA_reside_haifa,SVIVA2_raw_00$DROP,show.row.prc = T)
```
Slightly lower dropout rate among Haifa residents (`r round(filter(SVIVA2_raw_00,AREA_reside_haifa=="SHFELA",DROP==1)%>%nrow()/filter(SVIVA2_raw_00,AREA_reside_haifa=="SHFELA")%>%nrow()*100,1)`% vs. `r round(filter(SVIVA2_raw_00,AREA_reside_haifa=="HAIFA",DROP==1)%>%nrow()/filter(SVIVA2_raw_00,AREA_reside_haifa=="HAIFA")%>%nrow()*100,1)`%)

**Relevance manipulation:**
```{r}
sjt.xtab(SVIVA2_raw_00$RELEVANCE_exp,SVIVA2_raw_00$DROP,show.row.prc = T)
```
Lower dropout rates among those who were assigend to relevance treatment group (`r round(filter(SVIVA2_raw_00,RELEVANCE_exp==0,DROP==1)%>%nrow()/filter(SVIVA2_raw_00,RELEVANCE_exp==0)%>%nrow()*100,1)`% vs. `r round(filter(SVIVA2_raw_00,RELEVANCE_exp==1,DROP==1)%>%nrow()/filter(SVIVA2_raw_00,RELEVANCE_exp==1)%>%nrow()*100,1)`%).

**Relevance manipulation and areas:**
```{r}
SVIVA2_raw_00 %>% 
  group_by(AREA_reside_haifa,RELEVANCE_exp) %>% 
  summarise(N = n(),
            DROP_percent = paste0(round(mean(DROP)*100,1),"%"))

```

**Information:**
```{r}
sjt.xtab(SVIVA2_raw_00$INFORMATION_air,SVIVA2_raw_00$DROP,show.row.prc = T)

SVIVA2_raw_00 %>% 
  group_by(AREA_reside_haifa,INFORMATION_air) %>% 
  summarise(N = n(),
            DROP_percent = paste0(round(mean(DROP)*100,1),"%"))
```

Symbol:
```{r}
sjt.xtab(SVIVA2_raw_00$SYMBOL,SVIVA2_raw_00$DROP,show.row.prc = T)

SVIVA2_raw_00 %>% 
  group_by(AREA_reside_haifa,SYMBOL) %>% 
  summarise(N = n(),
            DROP_percent = paste0(round(mean(DROP)*100,1),"%"))
```

As an additional check, I examined whether dropping out can be predicted by area, manipulations and order of policies via logistic regression model (drop==1).

```{r}
tmod_drop_1 = glm(DROP~AREA_reside_haifa,SVIVA2_raw_00,family = "binomial",na.action=na.omit)
tmod_drop_2 = glm(DROP~AREA_reside_haifa+RELEVANCE_exp+AIR_order+INFORMATION_air+SYMBOL,SVIVA2_raw_00,family = "binomial",na.action=na.omit)
tmod_drop_3 = glm(DROP~AREA_reside_haifa*(RELEVANCE_exp+AIR_order+INFORMATION_air+SYMBOL),SVIVA2_raw_00,family = "binomial",na.action=na.omit)

sjt.glm(tmod_drop_1,tmod_drop_2,tmod_drop_3,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05)
```

In sum - these analyses show that there was lower attrition rate among Haifa-bay, Relevance treatment and the symbols groups. But no interaction between the areas and those manipulations. Overall, drop out rates are very low - in any of those groups not more than 10%. It is reasonable to assume that Shfela residents who dropped out are less interested in environmental issues, and therefore were less motivated to complete the survey.

#Filtering

---

##Filtering

Of these `r N` observations, I filtered observations due to:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
t = SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE)
```
*	Multiple entries from the same IP: `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r,warning=FALSE,message=FALSE}
t = SVIVA2_00 %>%
  filter(!(AGE%in% 1:17))
```
* Respondent's age less than 18: `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r,warning=FALSE,message=FALSE}
t = SVIVA2_00 %>%
  filter(IMC==1)
```
*	Failure in IMC: `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r,warning=FALSE,message=FALSE}
t = SVIVA2_00 %>%
  filter(TIMER_total>=3,TIMER_total<=30)
```
*	Filling the survey in less than 3 minutes or more than 30 minutes:
`r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r}
t = SVIVA2_00 %>%
  filter(TRUST_air_timer>=10|
           TRUST_waste_timer>=10)
```
*	Answering the two sets of DV questions (trust in air pollution and waste policies) in less than 10 seconds each: `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r}
t = SVIVA2_00 %>%
  filter(REPETITION_elaboration==0)
```

*	Repetition of the same value (except 4) in the elaboration questions (which include 2 reversed items, on a scale of 1 to 7): `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r,warning=FALSE,message=FALSE}
SVIVA2_01 = SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE) %>% #exclude double IP
  filter(!(AGE %in% 1:17),
         IMC==1,
         TIMER_total>=3,TIMER_total<=30,  
         TRUST_air_timer>=10|
           TRUST_waste_timer>=10, 
         REPETITION_elaboration==0)
```

**In total**, of the `r N` observations, I filtered out `r N-nrow(SVIVA2_01)` (`r round((N-nrow(SVIVA2_01))/N*100,1)`%).

```{r}
N_01 = nrow(SVIVA2_01)
```

Next, I examined whether filtering out can be predicted by area, manipulations and order of policies via logistic regression model (filtered==1).

```{r,warning=FALSE,message=FALSE}
SVIVA2_00 = SVIVA2_00 %>%
  mutate(FILTER_TOTAL = if_else(!(AGE %in% 1:17)&
                                 IMC==1&
                                 TIMER_total>=3 & TIMER_total<=30 &  
                                 (TRUST_air_timer>=10|
                                   TRUST_waste_timer>=10)& 
                                 REPETITION_elaboration==0,0,1))

tmod_filter_1 = glm(FILTER_TOTAL~AREA_reside_haifa+RELEVANCE_exp+AIR_order+INFORMATION_air+SYMBOL,SVIVA2_00,family = "binomial",na.action=na.omit)

sjt.glm(tmod_filter_1,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05)
```

Haifa-bay subjects less likely to be filtered out (`r round(filter(SVIVA2_00,AREA==1) %>% summarise(mean(FILTER_TOTAL)) %>% max()*100,1)`% vs. `r round(filter(SVIVA2_00,AREA==0) %>% summarise(mean(FILTER_TOTAL)) %>% max()*100,1)`%), which might be explained by their higher motivation/ interest in the issue. Again, it is reasonable to assume that Shfela residents who were filterred out were less interested in environmental issues, and therefore were less motivated to pay attention to the survey. Overrepresentation of those who are interested in the topic probably works against me, with regard to the tests for the effects of the symbols.
Also, relatively more subjects assigned to "no logo" group were screened out (`r round(filter(SVIVA2_00,SYMBOL==0) %>% summarise(mean(FILTER_TOTAL)) %>% max()*100,1)`% vs. `r round(filter(SVIVA2_00,SYMBOL==1) %>% summarise(mean(FILTER_TOTAL)) %>% max()*100,1)`% and `r round(filter(SVIVA2_00,SYMBOL==2) %>% summarise(mean(FILTER_TOTAL)) %>% max()*100,1)`%).

After these filters, we are left with `r N_01` observations: `r filter(SVIVA2_01,AREA==1)%>%nrow()` from Haifa bay (`r round(filter(SVIVA2_01,AREA==1)%>%nrow()/N_01*100,1)`%) and `r filter(SVIVA2_01,AREA==0)%>%nrow()` from Shfela (`r round(filter(SVIVA2_01,AREA==0)%>%nrow()/N_01*100,1)`%)

#Randomization checks

Next, I confirmed that the random assignments are balanced with regard to important covariates: gender, age, home ownership, education, trust in gov.

```{r}
sjt.grpmean(SVIVA2_01[,c("GENDER")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("GENDER")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("AGE")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("AGE")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("HOME")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("HOME")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("EDUCATION")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("EDUCATION")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("IDEOLOGY")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("IDEOLOGY")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("GOV_EVALUATION")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("GOV_EVALUATION")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("GOV_TRUST")],factor(SVIVA2_01$RELEVANCE_exp))
sjt.grpmean(SVIVA2_01[,c("GOV_TRUST")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("ENVIRONMENT_INTEREST")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("ENVIRONMENT_FOLLOW")],factor(SVIVA2_01$CONDITION_air))

sjt.grpmean(SVIVA2_01[,c("ENVIRONMENT_PREFERENCE")],factor(SVIVA2_01$CONDITION_air))
```

#Comparison between areas

```{r}
sjt.grpmean(SVIVA2_01[,c("GENDER")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("AGE")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("HOME")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("EDUCATION")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("IDEOLOGY")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("ENVIRONMENT_PREFERENCE")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("ENVIRONMENT_FOLLOW")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("ENVIRONMENT_INTEREST")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("GOV_EVALUATION")],factor(SVIVA2_01$AREA))

sjt.grpmean(SVIVA2_01[,c("GOV_TRUST")],factor(SVIVA2_01$AREA))

```

Haifa-bay subjects are slightly older, more educated, and more leftists. There are no significant differences with regard to their attitudes and preferences about environmental issues in general.

#Personal relevance
Next, I compared the perceived personal of the two policies across the two areas.

##Air pollution
```{r}
ggplot(SVIVA2_01, aes(factor(AREA_names), RELEVANCE_air_obs,fill=factor(AREA_names)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Area",values=c("gray100","gray90"))+
  scale_x_discrete(name="Area")+
  scale_y_continuous(name = "relevance of Air policy", breaks = c(1:7))
```
Air pollution policy is perceived as highly personally relevant for Haifa subjects, and not very relevant for Shfela subjects, as expected.

##Waste
```{r}
ggplot(SVIVA2_01, aes(factor(AREA_names), RELEVANCE_waste_obs,fill=factor(AREA_names)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Area",values=c("gray100","gray90"))+
  scale_x_discrete(name="Area")+
  scale_y_continuous(name = "relevance of waste policy", breaks = c(1:7))
```
Both areas perceive the waste policy as relatively relevant. Shfela residents perceive it as slightly more (`r filter(SVIVA2_01,AREA==0) %>% summarise(mean(RELEVANCE_waste_obs)) %>% max() %>% round(2)` vs. `r filter(SVIVA2_01,AREA==1) %>% summarise(mean(RELEVANCE_waste_obs)) %>% max() %>% round(2)`, (t= `r t.test(RELEVANCE_waste_obs~AREA,data=SVIVA2_01)[["statistic"]] %>% round(3)`, sig. = `r t.test(RELEVANCE_waste_obs~AREA,data=SVIVA2_01)[["p.value"]] %>% round(3)`)).

#Descriptive statistics

Summary statistics and bivaraite correlation matrix are attached at the end of the file. Next, I explore the main outcome variables.

##TRUST_INDEX
First, I examined the reliability of the trust index for the two policies

```{r}
sjt.itemanalysis(SVIVA2_01[, c("TRUST_air_q1",
                               "TRUST_air_q2",
                               "TRUST_air_q3",
                               "TRUST_air_q4",
                               "TRUST_air_q5")])
```

```{r}
sjt.itemanalysis(SVIVA2_01[, c("TRUST_waste_q1",
                               "TRUST_waste_q2",
                               "TRUST_waste_q3",
                               "TRUST_waste_q4",
                               "TRUST_waste_q5")])
```

Trust index for both policies has high reliability.

Next, I explore the distribution of the trust scales, across the two areas.

**Air policy**
```{r}
sjp.frq(SVIVA2_01$TRUST_air_INDEX, 
        type = "hist", 
        title = "Air policy",
        geom.size = 7/10,
        normal.curve = TRUE,
        show.mean = TRUE,
        axis.title = "Trust in Air policy (7=high)")

sjp.grpfrq(SVIVA2_01$TRUST_air_INDEX,
        SVIVA2_01$AREA_names,facet.grid = T,
        title = "Air policy",
        show.values=F,
        show.axis.values=T,
        axis.titles = "Trust in Air policy (7=high)")

```

```{r}
ggplot(SVIVA2_01, aes(factor(AREA_names), TRUST_air_INDEX,fill=factor(AREA_names)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Area",values=c("gray100","gray90"))+
  scale_x_discrete(name="Area")+
  scale_y_continuous(name = "Trust in air policy", breaks = c(1:7))
```

Haifa bay subjects have significantly lower trust in Haifa bay policy. Also, relatively more Haifa subjects reported extremely low levels of trust.

<br>
**Waste policy**
```{r}
sjp.frq(SVIVA2_01$TRUST_waste_INDEX, 
        type = "hist", 
        title = "waste policy",
        geom.size = 7/10,
        normal.curve = TRUE,
        show.mean = TRUE,
        axis.title = "Trust in waste policy (7=high)")

sjp.grpfrq(SVIVA2_01$TRUST_waste_INDEX,
        SVIVA2_01$AREA_names,facet.grid = T,
        title = "waste policy",
        show.values=F,
        show.axis.values=F,
        axis.titles = "Trust in waste policy (7=high)")

```

```{r}
ggplot(SVIVA2_01, aes(factor(AREA_names), TRUST_waste_INDEX,fill=factor(AREA_names)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Area",values=c("gray100","gray90"))+
  scale_x_discrete(name="Area")+
  scale_y_continuous(name = "Trust in waste policy", breaks = c(1:7))
```

Trust in waste policy is relatively higher, and there are significantly less extremely low values. Haifa bay subjects have slightly lower trust in Haifa bay policy (`r filter(SVIVA2_01,AREA==0) %>% summarise(mean(TRUST_waste_INDEX)) %>% max() %>% round(2)` vs. `r filter(SVIVA2_01,AREA==1) %>% summarise(mean(TRUST_waste_INDEX)) %>% max() %>% round(2)`). These differences are marginally significant (t= `r t.test(TRUST_waste_INDEX~AREA,data=SVIVA2_01)[["statistic"]] %>% round(3)`, sig. = `r t.test(TRUST_waste_INDEX~AREA,data=SVIVA2_01)[["p.value"]] %>% round(3)`).

##Elaboration measures

I used three measures of Elaboration: perceived elaboration index (5 items), total time of viewing the policy plan (reaction time - RT), a memory test in which respondents were asked to identify measures that appeared in the policy plan. Next, I explore these variables for the two policies. 
Perceived elaboration index and memory test scores were measured for each subject only for the second policy which was presented to her (recall that the order was random). RT was measured for both policies.

---

###Air policy

**Percieved Elaboration index**

```{r}
sjt.itemanalysis(SVIVA2_01[,c("ELABORATION_air_q1",
                              "ELABORATION_air_q2.r",
                              "ELABORATION_air_q3",
                              "ELABORATION_air_q4",
                              "ELABORATION_air_q5.r")])
```

Notice that ELABORATION_air_q4 less correlated with all other items, higher then others.

"Item 4: I tried to think to what extent do the measures assist in promoting the policy goal (reducing air pollution in the Haifa Bay/reducing waste and increasing recycling)".

<br>

```{r}
sjp.frq(SVIVA2_01$ELABORATION_air_INDEX, 
        type = "hist", 
        geom.size = 1,
        show.mean = TRUE,
        axis.title = "perceived elaboration index (air)")
```

**Elaboration time:**

The first plot shows the distribution of the reaction time (RT) measured in seconds. To reduce skewness, I log transformed this measure, according to the following formula: 
$ELABORATION timelog = log(ELABORATIONtime+1)$

```{r}
sjp.frq(SVIVA2_01$ELABORATION_air_time, 
        type = "hist", 
        geom.size = 1,
        show.mean = TRUE,
        axis.title = "Reaction time (in seconds) (air)")
```

<br>

```{r}
sjp.frq(SVIVA2_01$ELABORATION_air_time_log, 
        type = "hist", 
        geom.size = 1,
        show.mean = TRUE,
        axis.title = "Reaction time (in seconds) (log) (air)")
```

**Memory test**

In the memory test, the subjects were asked to select issues that were included in the second policy which was presented to them. 4 issues were presented, of which 2 are correct. 
The memory test score is calculated as follows: 
Number of correct issues minus Number of incorrect issues. A subject that selected more incorrect than correct items received the score of 0. Hence, possible scores are: 0,1,2.

```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_air_score,SVIVA2_01$INFORMATION_air_n,
           facet.grid = TRUE,
           axis.titles = "Memory test score (air)",
           show.prc = F)
```

###Waste policy

**Percieved Elaboration index**

```{r}
sjt.itemanalysis(SVIVA2_01[,c("ELABORATION_waste_q1",
                              "ELABORATION_waste_q2.r",
                              "ELABORATION_waste_q3",
                              "ELABORATION_waste_q4",
                              "ELABORATION_waste_q5.r")])
```

Again, ELABORATION_waste_q4 less correlated with all other items, higher then others.

<br>

```{r}
sjp.frq(SVIVA2_01$ELABORATION_waste_INDEX, 
        type = "hist", 
        geom.size = 1,
        show.mean = TRUE,
        axis.title = "perceived elaboration index (waste)")
```

**Elaboration time:**

```{r}
sjp.frq(SVIVA2_01$ELABORATION_waste_time, 
        type = "hist", 
        geom.size = 1,
        show.mean = TRUE,
        axis.title = "Reaction time (in seconds) (waste)")
```

<br>

```{r}
sjp.frq(SVIVA2_01$ELABORATION_waste_time_log, 
        type = "hist", 
        geom.size = 1,
        show.mean = TRUE,
        axis.title = "Reaction time (in seconds) (log) (waste)")
```

**Memory test**

```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$INFORMATION_waste_n,
           facet.grid = TRUE,
           axis.titles = "Memory test score (waste)",
           show.prc = F)
```

Lower scores in memory test of waste policy compared with air policy. Can be explained by the lower media salience of the issue.

Next, I tested the correlations between the three measures for each policy. 
```{r}
sjt.corr(SVIVA2_01[,c("ELABORATION_air_INDEX",
                      "ELABORATION_air_time_log",
                      "MEMORY_air_score")],
         remove.spaces = T,
         triangle="lower")

sjt.corr(SVIVA2_01[,c("ELABORATION_waste_INDEX",
                      "ELABORATION_waste_time_log",
                      "MEMORY_waste_score")],
                  remove.spaces = T,
                  triangle="lower")
```
Reaction time and memory score are strongly correlated in both policies. Perceived elaboration is not correlated with the two other measures, in both policies. This might be explained by social desirability which might shape subjects' answers to the perceived elaboration items (they might not admit that they did not elaborate).

#Manipulation checks
Next, I conducted a series of manipulation checks.

---
##Relevance priming manipulation

###Open answers

First, I look at the open answers for priming question of treatment and control groups, in the two areas:

Treatment: In your opinion, what is the most disturbing environmental issue in your area of residence:

```{r}
x1=filter(SVIVA2_01,str_length(RELEVANCE_exp_treat_text)>0) %>% select(AREA_names,RELEVANCE_exp_treat_text)

filter(x1,AREA_names=="Shfela") %>% datatable()

filter(x1,AREA_names=="Haifa") %>% datatable()
```

Most Haifa bay subjects regarded the air pollution in their answers, whereas very few of those from Shfela, as expected. Shfela respondents regarded veriaty of issues. (TBA - coding those answers...)

Control: what will attract people to choose your area of profession:

```{r}
x2=filter(SVIVA2_01,str_length(RELEVANCE_exp_control_text)>0) %>% select(AREA_names,RELEVANCE_exp_control_text)

filter(x2) %>% datatable()
```
The answers are not related to environmental issues, as expected.

###Air pollution
Next, I test whether the relevance treatment affected subjects' perceived personal relevance and elaboration.

**Perceived Relevance**
```{r}
sjt.grpmean(SVIVA2_00$RELEVANCE_air_obs,SVIVA2_00$RELEVANCE_exp)

ggplot(SVIVA2_00, aes(factor(RELEVANCE_exp), RELEVANCE_air_obs,fill=factor(RELEVANCE_exp)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~factor(AREA_names))+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"),labels=c("Control","Treatment"))+
  scale_x_discrete(name="",breaks=c(0,1),labels=c("",""))+
  scale_y_continuous(name = "Perceived personal relevance (air)", breaks = c(1:7))
```

**Perceived elaboration**
```{r,warning=F}
ggplot(SVIVA2_01, aes(RELEVANCE_exp_n, ELABORATION_air_INDEX,fill=factor(RELEVANCE_exp_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Perceived elaboration (air)", breaks = c(1:7))

```

**Elaboration time**
```{r}
ggplot(SVIVA2_01, aes(RELEVANCE_exp_n, ELABORATION_air_time_log,fill=factor(RELEVANCE_exp_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration air time (log)", breaks = c(1:7))

```

**Memory**
```{r}
ggplot(SVIVA2_01, aes(RELEVANCE_exp_n, MEMORY_air_score,fill=factor(RELEVANCE_exp_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration air time (log)", breaks = c(1:7))
```

```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_air_score[SVIVA2_01$AREA==1],SVIVA2_01$RELEVANCE_exp_n[SVIVA2_01$AREA==1],facet.grid = TRUE)

sjp.grpfrq(SVIVA2_01$MEMORY_air_score[SVIVA2_01$AREA==0],SVIVA2_01$RELEVANCE_exp_n[SVIVA2_01$AREA==0],facet.grid = TRUE)
```

**Models**
```{r}
tmod_relevance_air_full_1=lm(RELEVANCE_air_obs~RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_relevance_air_haifa_1=lm(RELEVANCE_air_obs~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_relevance_air_shfela_1=lm(RELEVANCE_air_obs~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

tmod_elaboration_air_full_1=lm(ELABORATION_air_INDEX~RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_elaboration_air_haifa_1=lm(ELABORATION_air_INDEX~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_elaboration_air_shfela_1=lm(ELABORATION_air_INDEX~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

sjt.lm(tmod_relevance_air_full_1,
       tmod_relevance_air_haifa_1,
       tmod_relevance_air_shfela_1,
       separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE,
       string.dv = "Perceived personal relevance (air)",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))

sjt.lm(tmod_elaboration_air_full_1,
       tmod_elaboration_air_haifa_1,
       tmod_elaboration_air_shfela_1,
       separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE,
       string.dv = "Perceived elaboration (air)",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))

```

Relevance treatment slightly increased perceived relevance of Shfela subjects and not of Haifa subjects. Relevance treatment increased Haifa bay subjects' perceived elaboration (but not reaction time and memory score).

###Waste
Next, I test whether the relevance treatment effected subjects' perceived personal relevance and elaboration of waste policy.

**Perceived Relevance**
```{r}
sjt.grpmean(SVIVA2_00$RELEVANCE_waste_obs,SVIVA2_00$RELEVANCE_exp)

ggplot(SVIVA2_00, aes(factor(RELEVANCE_exp), RELEVANCE_waste_obs,fill=factor(RELEVANCE_exp)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~factor(AREA_names))+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"),labels=c("Control","Treatment"))+
  scale_x_discrete(name="",breaks=c(0,1),labels=c("",""))+
  scale_y_continuous(name = "Perceived personal relevance (waste)", breaks = c(1:7))
```

**Perceived elaboration**
```{r,warning=F}
ggplot(SVIVA2_01, aes(RELEVANCE_exp_n, ELABORATION_waste_INDEX,fill=factor(RELEVANCE_exp_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Perceived elaboration (waste)", breaks = c(1:7))

```

**Elaboration time**
```{r}
ggplot(SVIVA2_01, aes(RELEVANCE_exp_n, ELABORATION_waste_time_log,fill=factor(RELEVANCE_exp_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration waste time (log)", breaks = c(1:7))

```

**Memory**
```{r}
ggplot(SVIVA2_01, aes(RELEVANCE_exp_n, MEMORY_waste_score,fill=factor(RELEVANCE_exp_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Relevance exp.",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration waste time (log)", breaks = c(1:7))
```

**Models**
```{r}
tmod_relevance_waste_full_1=lm(RELEVANCE_waste_obs~RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_relevance_waste_haifa_1=lm(RELEVANCE_waste_obs~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_relevance_waste_shfela_1=lm(RELEVANCE_waste_obs~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

tmod_elaboration_waste_full_1=lm(ELABORATION_waste_INDEX~RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_elaboration_waste_haifa_1=lm(ELABORATION_waste_INDEX~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_elaboration_waste_shfela_1=lm(ELABORATION_waste_INDEX~RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

sjt.lm(tmod_relevance_waste_full_1,
       tmod_relevance_waste_haifa_1,
       tmod_relevance_waste_shfela_1,
       separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE,
       string.dv = "Perceived personal relevance (waste)",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))

sjt.lm(tmod_elaboration_waste_full_1,
       tmod_elaboration_waste_haifa_1,
       tmod_elaboration_waste_shfela_1,
       separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE,
       string.dv = "Perceived elaboration (waste)",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))

```

No significant effect of relevance manipulation on perceived relevance or elaboration of waste policy.

In sum, it seems that the relevance treatment had a very low effect of relevance, if at all, only on air policy.

##Symbols
Next, I explore the recognizability and positive/negative affect of the symbols (images of celebs from Ministry's campaigns).

**Recognizability**

SVIVA LOGO
```{r}

sjp.frq(SVIVA2_01$RECOGNIZE_SVIVA_logo, 
        type = "bar")

sjt.grpmean(SVIVA2_01$RECOGNIZE_SVIVA_logo,factor(SVIVA2_01$AREA_names))
```

Air real celeb
```{r}
sjp.frq(SVIVA2_01$RECOGNIZE_air_real, 
        type = "bar")
sjt.grpmean(SVIVA2_01$RECOGNIZE_air_real,factor(SVIVA2_01$AREA_names))
```

Waste real celeb
```{r}
sjp.frq(SVIVA2_01$RECOGNIZE_waste_real, 
        type = "bar")
sjt.grpmean(SVIVA2_01$RECOGNIZE_waste_real,factor(SVIVA2_01$AREA_names))
```

**Affect**

Air real celeb
```{r}
sjp.frq(SVIVA2_01$AFFECT_air_real, 
        type = "bar")
sjt.grpmean(SVIVA2_01$AFFECT_air_real,factor(SVIVA2_01$AREA_names))
```

Air fake celeb
```{r}
sjp.frq(SVIVA2_01$AFFECT_air_fake, 
        type = "bar")
sjt.grpmean(SVIVA2_01$AFFECT_air_fake,factor(SVIVA2_01$AREA_names))
```

Waste real celeb
```{r}
sjp.frq(SVIVA2_01$AFFECT_waste_real, 
        type = "bar")
sjt.grpmean(SVIVA2_01$AFFECT_waste_real,factor(SVIVA2_01$AREA_names))
```

Waste fake celeb
```{r}
sjp.frq(SVIVA2_01$AFFECT_waste_fake, 
        type = "bar")
sjt.grpmean(SVIVA2_01$AFFECT_waste_fake,factor(SVIVA2_01$AREA_names))
```

There are no differences between areas with regard to recognizability or affect of the logos and images. `r round(filter(SVIVA2_01,RECOGNIZE_air_real==1) %>% nrow()/N_01*100,1)`% did not recognize air real celeb (Tal friedman). `r round(filter(SVIVA2_01,RECOGNIZE_waste_real==1) %>% nrow()/N_01*100,1)`% did not recognize waste real celeb (Ido Rozenblum). `r round(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo==1) %>% nrow()/N_01*100,1)`% did not recognize the SVIVA logo. Images of real celebs have positive affect, and fake images are fairly neutral. In robust analyses I exclude those who did not recognize the symbols.

##Information manipulation

Next, I confirmed that subjects indeed perceived the weak policy as representing weaker arguments, compared with the strong policy.

To do so, I compared the first Item in the trust scale:

*I believe that the measures in the policy plan will assist in fulfilling the policy goal (reducing air pollution in the Haifa Bay/reducing waste and increasing recycling).*

**Air**
```{r}
ggplot(SVIVA2_01, aes(factor(INFORMATION_air_n), TRUST_air_q1,fill=factor(INFORMATION_air_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Information",values=c("gray100","gray90"),labels=c("Poor","Good"))+facet_grid(~AREA_names)+
  scale_x_discrete(name="",breaks=c(0,1),labels=c("",""))+
  scale_y_continuous(name = "Air Trust q1", breaks = c(1:7))

sjt.grpmean(SVIVA2_01$TRUST_air_q1,SVIVA2_01$INFORMATION_air)
```

**Waste**
```{r}
ggplot(SVIVA2_00, aes(factor(INFORMATION_waste), TRUST_waste_q1,fill=factor(INFORMATION_waste)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Information",values=c("gray100","gray90"),labels=c("Poor","Good"))+
  facet_grid(~AREA_names)+
  scale_x_discrete(name="",breaks=c(0,1),labels=c("",""))+
  scale_y_continuous(name = "Waste Trust q1", breaks = c(1:7))

sjt.grpmean(SVIVA2_00$TRUST_waste_q1,SVIVA2_00$INFORMATION_waste)
```

Next, to further substantiate the validity of the information manipulation, I examine the interaction between elaboration and information and their effect on trust. I expect that when subjects are presented with weak policy, higher levels of elaboration will decrease their trust. On the other hand, when subjects are presented with strong policy, higher levels of elaboration will increase their trust.

**Air**

```{r}
sjp.scatter(SVIVA2_01$ELABORATION_air_time_log,
            SVIVA2_01$TRUST_air_INDEX,
            SVIVA2_01$INFORMATION_air,
            fit.line.grps = TRUE,
            show.ci = TRUE,
            geom.size=1,
             axis.titles=c("Air Elaboration time (log)","Trust in air policy"),
            legend.title="Information",
            legend.labels=c("Weak","Strong"))
```

```{r}
sjp.scatter(SVIVA2_01$MEMORY_air_score,
            SVIVA2_01$TRUST_air_INDEX,
            SVIVA2_01$INFORMATION_air,
            fit.line.grps = TRUE,
            show.ci = TRUE,
            geom.size=1,
            axis.titles=c("Air Memory score","Trust in air policy"),
            legend.title="Information",
            legend.labels=c("Weak","Strong"),
            auto.jitter = T,
            emph.dots = TRUE)
```

**Waste**

```{r}
sjp.scatter(SVIVA2_01$ELABORATION_waste_time_log,
            SVIVA2_01$TRUST_waste_INDEX,
            SVIVA2_01$INFORMATION_waste,
            fit.line.grps = TRUE,
            show.ci = TRUE,
            geom.size=1,
             axis.titles=c("waste Elaboration time (log)","Trust in waste policy"),
            legend.title="Information",
            legend.labels=c("Weak","Strong"),
            title = "Haifa")
```

```{r}
sjp.scatter(SVIVA2_01$MEMORY_waste_score,
            SVIVA2_01$TRUST_waste_INDEX,
            SVIVA2_01$INFORMATION_waste,
            fit.line.grps = TRUE,
            show.ci = TRUE,
            geom.size=1,
            axis.titles=c("waste Memory score","Trust in waste policy"),
            legend.title="Information",
            legend.labels=c("Weak","Strong"),
            title = "Haifa",
            auto.jitter = T,
            emph.dots = TRUE)
```

#Trust in Haifa air-pollution policy

I now turn to analyze the hypotheses with regard to trust in air policy.

*First*, I analyze the effects of symbols and information, their interaction and their moderation by areas and by relevance manipulation.

*Second*, I analyze the effect of symbols manipulation on elaboration.

*Third*, I analyze the mediating role of elaboration.

##Descriptive results:

**All sample:** 
```{r}

SVIVA2_01 %>%
    group_by(SYMBOL_n,INFORMATION_air_n) %>%
    summarise(n=n(),
              mean = round(mean(TRUST_air_INDEX),3),
              se = round(sd(TRUST_air_INDEX)/sqrt(n()),3))%>%
    mutate(ci_95 = round(1.96*se,3),
           ci_90 = round(1.65*se,3))

ggplot(SVIVA2_01, aes(factor(INFORMATION_air_n), TRUST_air_INDEX,fill=factor(INFORMATION_air_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_air_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Symbols",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="")+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```

There is a strong and significant main effect for information manipulation (`r filter(SVIVA2_01,INFORMATION_air==1) %>% summarise(mean(TRUST_air_INDEX)) %>% max() %>% round(2)` vs. `r filter(SVIVA2_01,INFORMATION_air==0) %>% summarise(mean(TRUST_air_INDEX)) %>% max() %>% round(2)`). t= `r t.test(TRUST_air_INDEX~INFORMATION_air,data=SVIVA2_01)[["statistic"]] %>% round(3)`). 
Significant main effect of symbol (`r filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_air_INDEX))%>%round(3) %>% max()` [`r filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%round(3) %>% max()`,`r filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%round(3) %>% max()`] vs. `r filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(TRUST_air_INDEX))%>%round(3) %>% max()` and `r filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(TRUST_air_INDEX))%>%round(3) %>% max()` in control groups fake symbol and no symbol).

**By areas:**
```{r}
SVIVA2_01 %>%
    group_by(AREA_names,SYMBOL_n,INFORMATION_air_n) %>%
    summarise(n=n(),
              mean = round(mean(TRUST_air_INDEX),3),
              se = round(sd(TRUST_air_INDEX)/sqrt(n()),3))%>%
    mutate(ci_95 = round(1.96*se,3),
           ci_90 = round(1.65*se,3))
```

```{r}
ggplot(SVIVA2_01, aes(factor(INFORMATION_air_n), TRUST_air_INDEX,fill=factor(INFORMATION_air_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_air_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_air_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names~INFORMATION_air_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray90","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```

No interaction between areas and information manipulation. The effect of the symbol manipulation is strong and significant among Haifa subjects, yet the increase is not significant among Shfela subjects. Among Shfela subjects, the symbols had greater effect among those who received the weak policy.

**By Relevance manipulation**
```{r}
SVIVA2_01 %>%
    group_by(RELEVANCE_exp_n,SYMBOL_n,INFORMATION_air_n) %>%
    summarise(n=n(),
              mean = round(mean(TRUST_air_INDEX),3),
              se = round(sd(TRUST_air_INDEX)/sqrt(n()),3))%>%
    mutate(ci = round(1.96*se,3))
```

```{r}
ggplot(SVIVA2_01, aes(factor(INFORMATION_air_n), TRUST_air_INDEX,fill=factor(INFORMATION_air_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~RELEVANCE_exp_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_air_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~RELEVANCE_exp_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Air Trust index", breaks = c(1:7))
```
No interaction between relevance manipulation and information/symbol manipulations.

##Main Models

```{r}
tmod_air_full_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=SVIVA2_01)
tmod_air_full_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=SVIVA2_01)

tmod_air_haifa_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1))
tmod_air_haifa_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_01,AREA==1))

tmod_air_shfela_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==0))
tmod_air_shfela_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_air_full_1,tmod_air_full_2,
        tmod_air_haifa_1,tmod_air_haifa_2,
        tmod_air_shfela_1,tmod_air_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in Air policy",
       depvar.labels = paste0("(",1:6,")"," ",c(rep(c("Full","Haifa","Shfela"),each=2))))

```

```{r}
tmod_air_full_11 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL+RELEVANCE_exp,data=SVIVA2_01)
tmod_air_full_12 = lm(TRUST_air_INDEX~RELEVANCE_exp*(INFORMATION_air+SYMBOL),data=SVIVA2_01)

tmod_air_haifa_11 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1))
tmod_air_haifa_12 = lm(TRUST_air_INDEX~RELEVANCE_exp*(INFORMATION_air+SYMBOL),data=filter(SVIVA2_01,AREA==1))

tmod_air_shfela_11 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0))
tmod_air_shfela_12 = lm(TRUST_air_INDEX~RELEVANCE_exp*(INFORMATION_air+SYMBOL),data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_air_full_11,tmod_air_full_12,
        tmod_air_haifa_11,tmod_air_haifa_12,
        tmod_air_shfela_11,tmod_air_shfela_12,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE, 
              pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "Relevance treatment",
                       "Relevance treatment*Information",
                       "Relevance treatment*SYMBOL (fake)",
                       "Relevance treatment*SYMBOL (real)"),
       string.dv = "Trust in Air policy",
       depvar.labels = paste0("(",1:6,")"," ",c(rep(c("Full","Haifa","Shfela"),each=2))))

```

In sum, these analyses show that subjects in both areas were responsive to the differences in information. The real symbol increased the trust of Haifa bay subjects compared with the two control groups. The fake logo slightly increased the trust of Haifa bay subjects, but to a lesser extent. Among Shfela subjects, the real symbol did not had a significant effect. The effect was slightly stronger among those who saw the weak policy, but the effect is still only marginally significant. t= `r t.test(TRUST_air_INDEX~SYMBOL,data=filter(SVIVA2_01,AREA==0,INFORMATION_air==0,SYMBOL!=1))[["statistic"]] %>% round(3)`,sig = `r round(t.test(TRUST_air_INDEX~SYMBOL,data=filter(SVIVA2_01,AREA==0,INFORMATION_air==0,SYMBOL!=1))[["p.value"]]/2,3)` in one tailled test. There is no interaction bewteen the relevance treatment and the information or the symbol manipulations.

##Extreme values:
Next, I analyzed the effect of the symbols manipulation on extremely low levels of trust (<=2, on a 1-7 scale). This analysis enables to estimate the extent to which the symbols can reduce distrust.

```{r}
SVIVA2_01=SVIVA2_01%>% 
  mutate(TRUST_air_INDEX_low = ifelse(TRUST_air_INDEX<=2,1,0),
         TRUST_air_INDEX_high = ifelse(TRUST_air_INDEX>=6,1,0)) 
```

```{r}
SVIVA2_01 %>%
    group_by(AREA_names,SYMBOL_n) %>%
    summarise(n=n(),
              mean = mean(TRUST_air_INDEX_low),
              se = sd(TRUST_air_INDEX_low)/sqrt(n()))%>%
    mutate(ci_95 = 1.96*se,
           ci_90 = 1.65*se) %>% 
    mutate(mean = paste0(round(mean*100,1),"%"),
           se = paste0(round(se*100,1),"%"),
           ci_95 = paste0(round(ci_95*100,1),"%"),
           ci_90 = paste0(round(ci_90*100,1),"%"))

```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_air_INDEX_low))+ 
  theme_bw()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names~INFORMATION_air_n)+
  scale_y_continuous(name = "Low trust air",breaks = seq(0,0.4,by=0.05))

sjt.grpmean(filter(SVIVA2_01,AREA==1)$TRUST_air_INDEX_low,
            filter(SVIVA2_01,AREA==1)$SYMBOL_n)
sjt.grpmean(filter(SVIVA2_01,AREA==0)$TRUST_air_INDEX_low,
            filter(SVIVA2_01,AREA==0)$SYMBOL_n)

```

```{r}
tmod_trust_air_low_full_1 = glm(TRUST_air_INDEX_low~INFORMATION_air+SYMBOL,data=SVIVA2_01,family="binomial")

tmod_trust_air_low_haifa_1 = glm(TRUST_air_INDEX_low~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1),family="binomial")

tmod_trust_air_low_shfela_1 = glm(TRUST_air_INDEX_low~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==0),family="binomial")

sjt.glm(tmod_trust_air_low_full_1,
       tmod_trust_air_low_haifa_1,
       tmod_trust_air_low_shfela_1,          
         separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Low trust in Air policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))
```
In both areas, real symbol decreased the likelihood of low trust in the policy. The fake symbol also decreased distrust but only in haifa, but to a lesser extent.

```{r}
SVIVA2_01 %>%
    group_by(AREA_names,SYMBOL_n) %>%
    summarise(n=n(),
              mean = mean(TRUST_air_INDEX_high),
              se = sd(TRUST_air_INDEX_high)/sqrt(n()))%>%
    mutate(ci_95 = 1.96*se,
           ci_90 = 1.65*se) %>% 
    mutate(mean = paste0(round(mean*100,1),"%"),
           se = paste0(round(se*100,1),"%"),
           ci_95 = paste0(round(ci_95*100,1),"%"),
           ci_90 = paste0(round(ci_90*100,1),"%"))

```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_air_INDEX_high))+ 
  theme_bw()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names~INFORMATION_air_n)+
  scale_y_continuous(name = "high trust air",breaks = seq(0,0.4,by=0.05))

sjt.grpmean(filter(SVIVA2_01,AREA==1)$TRUST_air_INDEX_high,
            filter(SVIVA2_01,AREA==1)$SYMBOL_n)
sjt.grpmean(filter(SVIVA2_01,AREA==0)$TRUST_air_INDEX_high,
            filter(SVIVA2_01,AREA==0)$SYMBOL_n)

```

```{r}
tmod_trust_air_high_full_1 = glm(TRUST_air_INDEX_high~INFORMATION_air+SYMBOL,data=SVIVA2_01,family="binomial")

tmod_trust_air_high_haifa_1 = glm(TRUST_air_INDEX_high~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1),family="binomial")

tmod_trust_air_high_shfela_1 = glm(TRUST_air_INDEX_high~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==0),family="binomial")

sjt.glm(tmod_trust_air_high_full_1,
       tmod_trust_air_high_haifa_1,
       tmod_trust_air_high_shfela_1,          
         separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "high trust in Air policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))
```

##Trust aspects
Next, I analyzed the effect of information and symbol manipulations on the three aspects of trust, in separate.
```{r}
tmod_air_competence_full = lm(TRUST_air_competence~INFORMATION_air+SYMBOL,data=SVIVA2_01)
tmod_air_benevolence_full = lm(TRUST_air_benevolence~INFORMATION_air+SYMBOL,data=SVIVA2_01)
tmod_air_integrity_full = lm(TRUST_air_q5~INFORMATION_air+SYMBOL,data=SVIVA2_01)

tmod_air_competence_haifa = lm(TRUST_air_competence~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1))
tmod_air_benevolence_haifa = lm(TRUST_air_benevolence~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1))
tmod_air_integrity_haifa = lm(TRUST_air_q5~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1))

tmod_air_competence_shfela = lm(TRUST_air_competence~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==0))
tmod_air_benevolence_shfela = lm(TRUST_air_benevolence~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==0))
tmod_air_integrity_shfela = lm(TRUST_air_q5~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_air_competence_full,tmod_air_benevolence_full,tmod_air_integrity_full,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real"),
       depvar.labels = c(rep(c("Competence","Benevolence","Integrity"),each=1)))

```

Symbols had greater effect on benevolence and integrity (in line with Alon-Barkat & Gilad 2017). Information had slightly weaker effect on integrity, as expected.

##Elaboration

I now turn to examine the hypothesis that the symbol manipulation decreased subjects' elaboration.

**perceived elaboration**
```{r}
ggplot(SVIVA2_01, aes(SYMBOL_n, ELABORATION_air_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration air index", breaks = c(1:7))

```

**Elaboration time**
```{r}
ggplot(SVIVA2_01, aes(SYMBOL_n, ELABORATION_air_time_log,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration time (log)", breaks = c(1:6),limits = c(0.5,6))

```

**Memory score**

Haifa
```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_air_score[SVIVA2_01$AREA==1],
           SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==1],
           facet=T,
           ylim=c(0,60),
           show.prc =  F,
           title = "Haifa")

sjt.xtab(SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==1],
         SVIVA2_01$MEMORY_air_score[SVIVA2_01$AREA==1],
         show.row.prc = T)
```

Shfela
```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_air_score[SVIVA2_01$AREA==0],
           SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==0],
           facet=T,
           ylim=c(0,60),
           show.prc =  F,
           title = "Shfela")

sjt.xtab(SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==0],
         SVIVA2_01$MEMORY_air_score[SVIVA2_01$AREA==0],
         show.row.prc = T)
```

**models**
I now regress the three elaboration measures on the manipulations. In the analysis of memory score, which is an ordinal scale (1,2,3), I used logistic multinomial regression (predicting likelihood to score 1 and 2, compared with 0).

```{r}
tmod_elaboration_air_index_full_1 = lm(ELABORATION_air_INDEX~SYMBOL+INFORMATION_air+RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_elaboration_air_index_haifa_1 = lm(ELABORATION_air_INDEX~SYMBOL+INFORMATION_air+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_elaboration_air_index_shfela_1 = lm(ELABORATION_air_INDEX~SYMBOL+INFORMATION_air+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

sjt.lm(tmod_elaboration_air_index_full_1,
       tmod_elaboration_air_index_haifa_1,
       tmod_elaboration_air_index_shfela_1,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Fake",
                       "Real",
                       "INFORMATION (1=strong policy)",
                       "Relevance treatment"),
       show.header = TRUE,
       string.dv = "Elaboration in Air policy (perceived)",
       depvar.labels = c("Full","Haifa","Shfela"))
```
No effect on perceived elaboration. However, as explained above, this measure is problematic due to its possible shaping by social desirability.

```{r}
tmod_elaboration_air_time_full_1 = lm(ELABORATION_air_time_log~SYMBOL+INFORMATION_air+RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_elaboration_air_time_haifa_1 = lm(ELABORATION_air_time_log~SYMBOL+INFORMATION_air+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_elaboration_air_time_shfela_1 = lm(ELABORATION_air_time_log~SYMBOL+INFORMATION_air+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

sjt.lm(tmod_elaboration_air_time_full_1,
       tmod_elaboration_air_time_haifa_1,
       tmod_elaboration_air_time_shfela_1,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Fake",
                       "Real",
                       "INFORMATION (1=strong policy)",
                       "Relevance treatment"),
       show.header = TRUE,
       string.dv = "Elaboration in Air policy (Reaction time)",
       depvar.labels = c("Full","Haifa","Shfela"))

```
The real Symbols spent less time in watching the air policy (by `r tmod_elaboration_air_time_full_1[["coefficients"]][["SYMBOL2"]] %>% abs() %>% exp() %>% round(2)` seconds on average). A possible issue which should be addressed is measures the time they spent whatching the policy plan, and not the time they dedicated to read it and think about it. They could have watched the images and graphics instead. So this means that for the fake symbol and real symbol groups, the "real" elaboration time is presumably even lower.

```{r,warning=F}
library(nnet)
library(stargazer)

tmod_elaboration_air_memory_full_1 <- multinom(MEMORY_air_score ~ SYMBOL+INFORMATION_air+RELEVANCE_exp, data = SVIVA2_01)
tmod_elaboration_air_memory_haifa_1=multinom(MEMORY_air_score ~ SYMBOL+INFORMATION_air+RELEVANCE_exp, data = filter(SVIVA2_01,AREA==1))
tmod_elaboration_air_memory_shfela_1=multinom(MEMORY_air_score ~ SYMBOL+INFORMATION_air+RELEVANCE_exp, data = filter(SVIVA2_01,AREA==0))

stargazer(tmod_elaboration_air_memory_full_1,
          tmod_elaboration_air_memory_haifa_1,
          tmod_elaboration_air_memory_shfela_1,
          type="text",
          report="vcsp",
          dep.var.caption  = "Air Memory score (multinomial logit)",
          dep.var.labels   = rep(c("1 vs. 0","2 vs. 0"),3),
          column.labels = rep(c("Full","Haifa", "Shfela"),each=2))

```
The symbols decreased memory test score, but the effect is significant only among Haifa subjects.

In sum, the symbols reduced elaboration (measured by RT and memory score) mainly among Haifa subjects. The relevance manipulation had a significant effect only on perceived elaboration index, only among Haifa subjects.

##Moderated mediation

I showed above that symbols had a positive effect on trust, and that symbols had a negative effect on elaboration. Next, I examine whether the effect of symbols on trust is mediated by lower levels of elaboration. I showed that the effect of elaboration is moderated by information (in weak policy, low levels of elaboration increase trust). Therefore, I examine whether adding the interactions between information and elaboration (measures by RT and memory score) decreases the coefficient of real symbols.

```{r}
xy_full = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air,data=SVIVA2_01)
xmy_full_3 = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air+INFORMATION_air*(ELABORATION_air_time_log+MEMORY_air_score),data=SVIVA2_01)

xy_haifa = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air,data=filter(SVIVA2_01,AREA==1))
xmy_haifa_3 = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air+INFORMATION_air*(ELABORATION_air_time_log+MEMORY_air_score),data=filter(SVIVA2_01,AREA==1))

xy_shfela = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air,data=filter(SVIVA2_01,AREA==0))
xmy_shfela_3 = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air+INFORMATION_air*(ELABORATION_air_time_log+MEMORY_air_score),data=filter(SVIVA2_01,AREA==0))

sjt.lm(xy_full,xmy_full_3,
       xy_haifa,xmy_haifa_3,
       xy_shfela,xmy_shfela_3,
       separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
              pred.labels = c("Fake",
                              "Real",
                              "INFORMATION (1=strong policy)",
                               "INFORMATION*SYMBOL (fake)",
                              "INFORMATION*SYMBOL (real)",
                              "Elaboration time (log)",
                              "Memory score",
                              "INFORMATION*Elaboration time",
                              "INFORMATION*Memory score"),
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))

```
The effect of symbols is partly mediated by elaboration, in both areas. The coefficient of the real symbols decreases from `r xy_full[["coefficients"]][["SYMBOL2"]] %>% round(2)` to `r xmy_full_3[["coefficients"]][["SYMBOL2"]] %>% round(2)`, and is less significant. The coefficients of the fake symbols did not decrease.

<br>
Next, I conducted causal mediaion analysis, using `mediation` package.

Compared with control no logo.

```{r}
library(mediation)

med.fit_RT = lm(ELABORATION_total_time_log~SYMBOL*INFORMATION_air,data=filter(SVIVA2_01,SYMBOL!=1))
med.out_RT = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air+ELABORATION_total_time_log*INFORMATION_air,data=filter(SVIVA2_01,SYMBOL!=1))

med_RT_INFORMTION_0 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_air = 0), sims = 100)

summary(med_RT_INFORMTION_0)
plot(med_RT_INFORMTION_0)

med_RT_INFORMTION_1 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_air = 1), sims = 100)

summary(med_RT_INFORMTION_1)
plot(med_RT_INFORMTION_1)
```

Compared with control fake logo.

```{r}
library(mediation)

med.fit_RT = lm(ELABORATION_total_time_log~SYMBOL*INFORMATION_air,data=filter(SVIVA2_01,SYMBOL!=0))
med.out_RT = lm(TRUST_air_INDEX~SYMBOL*INFORMATION_air+ELABORATION_total_time_log*INFORMATION_air,data=filter(SVIVA2_01,SYMBOL!=0))

med_RT_INFORMTION_0 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_air = 0), sims = 100)

summary(med_RT_INFORMTION_0)
plot(med_RT_INFORMTION_0)

med_RT_INFORMTION_1 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_air = 1), sims = 100)

summary(med_RT_INFORMTION_1)
plot(med_RT_INFORMTION_1)
```

##Conclusions for air policy
The results indicate that:

+ Subjects reported higher trust in strong policy compared with weak policy. 
+ Subjects reported higher trust (and/or lower distrust) when the communication included symbols (compared with both control groups). The effect is greater among Haifa subjects, and marginally significant among shfela subjects, possibly due to ceiling effect. The fake symbols also had a positive, but weaker effect. 
+ The effect of symbols was higher among those who were presented with weak policy, but the interaction is not sufficiently significant.
+ No evidence that greater personal relevance (either operationalized via manipulation or via comparison between areas) moderates the effects of information and symbols, as expected. 
+ Symbols in communication decreased elaboration of the policy.
+ The effect of the symbols of trust is partly mediated by its negative effect on elaboration.

#Trust in waste policy

##Descriptive results:

**All sample:** 
```{r}

SVIVA2_01 %>%
    group_by(SYMBOL_n,INFORMATION_waste_n) %>%
    summarise(n=n(),
              mean = round(mean(TRUST_waste_INDEX),3),
              se = round(sd(TRUST_waste_INDEX)/sqrt(n()),3))%>%
    mutate(ci_95 = round(1.96*se,3),
           ci_90 = round(1.65*se,3))

ggplot(SVIVA2_01, aes(factor(INFORMATION_waste_n), TRUST_waste_INDEX,fill=factor(INFORMATION_waste_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_waste_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Symbols",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="")+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

There is a strong and significant main effect for information manipulation (`r filter(SVIVA2_01,INFORMATION_waste==1) %>% summarise(mean(TRUST_waste_INDEX)) %>% max() %>% round(2)` vs. `r filter(SVIVA2_01,INFORMATION_waste==0) %>% summarise(mean(TRUST_waste_INDEX)) %>% max() %>% round(2)`). t= `r t.test(TRUST_waste_INDEX~INFORMATION_waste,data=SVIVA2_01)[["statistic"]] %>% round(3)`). 
Significant main effect of symbol (`r filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_waste_INDEX))%>%round(3) %>% max()` [`r filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_waste_INDEX)+1.96*sd(TRUST_waste_INDEX)/sqrt(n()))%>%round(3) %>% max()`,`r filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_waste_INDEX)-1.96*sd(TRUST_waste_INDEX)/sqrt(n()))%>%round(3) %>% max()`] vs. `r filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(TRUST_waste_INDEX))%>%round(3) %>% max()` and `r filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(TRUST_waste_INDEX))%>%round(3) %>% max()` in control groups fake symbol and no symbol). Difference from fake symbol is marginally significant. But the effect is weaker compared with the effect in air policy (perhaps weaker symbol).

**By areas:**
```{r}
SVIVA2_01 %>%
    group_by(AREA_names,SYMBOL_n,INFORMATION_waste_n) %>%
    summarise(n=n(),
              mean = round(mean(TRUST_waste_INDEX),3),
              se = round(sd(TRUST_waste_INDEX)/sqrt(n()),3))%>%
    mutate(ci_95 = round(1.96*se,3),
           ci_90 = round(1.65*se,3))
```

```{r}
ggplot(SVIVA2_01, aes(factor(INFORMATION_waste_n), TRUST_waste_INDEX,fill=factor(INFORMATION_waste_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_waste_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_waste_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names~INFORMATION_waste_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray90","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

No interaction between areas and information manipulation. The effect of the symbol manipulation is strong and significant among Haifa subjects, yet the increase is not significant among Shfela subjects. The symbols had greater effect among those who received the weak policy.

**By Relevance manipulation**
```{r}
SVIVA2_01 %>%
    group_by(RELEVANCE_exp_n,SYMBOL_n,INFORMATION_waste_n) %>%
    summarise(n=n(),
              mean = round(mean(TRUST_waste_INDEX),3),
              se = round(sd(TRUST_waste_INDEX)/sqrt(n()),3))%>%
    mutate(ci = round(1.96*se,3))
```

```{r}
ggplot(SVIVA2_01, aes(factor(INFORMATION_waste_n), TRUST_waste_INDEX,fill=factor(INFORMATION_waste_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~RELEVANCE_exp_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_waste_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~RELEVANCE_exp_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```
No interaction between relevance manipulation and information/symbol manipulations.

##Main Models

```{r}
tmod_waste_full_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=SVIVA2_01)
tmod_waste_full_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=SVIVA2_01)

tmod_waste_haifa_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==1))
tmod_waste_haifa_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_01,AREA==1))

tmod_waste_shfela_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==0))
tmod_waste_shfela_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_waste_full_1,tmod_waste_full_2,
        tmod_waste_haifa_1,tmod_waste_haifa_2,
        tmod_waste_shfela_1,tmod_waste_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = paste0("(",1:6,")"," ",c(rep(c("Full","Haifa","Shfela"),each=2))))

```

```{r}
tmod_waste_full_11 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL+RELEVANCE_exp,data=SVIVA2_01)
tmod_waste_full_12 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(INFORMATION_waste+SYMBOL),data=SVIVA2_01)

tmod_waste_haifa_11 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1))
tmod_waste_haifa_12 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(INFORMATION_waste+SYMBOL),data=filter(SVIVA2_01,AREA==1))

tmod_waste_shfela_11 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0))
tmod_waste_shfela_12 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(INFORMATION_waste+SYMBOL),data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_waste_full_11,tmod_waste_full_12,
        tmod_waste_haifa_11,tmod_waste_haifa_12,
        tmod_waste_shfela_11,tmod_waste_shfela_12,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE, 
              pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "Relevance treatment",
                       "Relevance treatment*Information",
                       "Relevance treatment*SYMBOL (fake)",
                       "Relevance treatment*SYMBOL (real)"),
       string.dv = "Trust in waste policy",
       depvar.labels = paste0("(",1:6,")"," ",c(rep(c("Full","Haifa","Shfela"),each=2))))

```

Area+relevance_man.
```{r}
tmod_waste_full_11 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL+RELEVANCE_exp,data=SVIVA2_01)
tmod_waste_full_12 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(INFORMATION_waste+SYMBOL),data=SVIVA2_01)

tmod_waste_haifa_11 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1))
tmod_waste_haifa_12 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(INFORMATION_waste+SYMBOL),data=filter(SVIVA2_01,AREA==1))

tmod_waste_shfela_11 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0))
tmod_waste_shfela_12 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(INFORMATION_waste+SYMBOL),data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_waste_full_11,tmod_waste_full_12,
        tmod_waste_haifa_11,tmod_waste_haifa_12,
        tmod_waste_shfela_11,tmod_waste_shfela_12,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))

```

Results are largely compatible with air policy, but the effects of information and symbols are weaker. Again, there is no interaction bewteen the relevance treatment and the information or the symbol manipulations. Slightly greater effect of information on relevance treatment group. Interaction is marginally significant in Shfela. No interaction between relevance manipulation and symbols.

I also analyzed the effect on extremely low trust, or distrust (<=2).

```{r}
SVIVA2_01=SVIVA2_01%>% 
  mutate(TRUST_waste_INDEX_low = ifelse(TRUST_waste_INDEX<=2,1,0)) 
```

```{r}
SVIVA2_01 %>%
    group_by(AREA_names,SYMBOL_n) %>%
    summarise(n=n(),
              mean = mean(TRUST_waste_INDEX_low),
              se = sd(TRUST_waste_INDEX_low)/sqrt(n()))%>%
    mutate(ci_95 = 1.96*se,
           ci_90 = 1.65*se) %>% 
    mutate(mean = paste0(round(mean*100,1),"%"),
           se = paste0(round(se*100,1),"%"),
           ci_95 = paste0(round(ci_95*100,1),"%"),
           ci_90 = paste0(round(ci_90*100,1),"%"))

```

```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), TRUST_waste_INDEX_low))+ 
  theme_bw()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_y_continuous(name = "Low trust waste",breaks = seq(0,0.4,by=0.05))

```

```{r}
tmod_trust_waste_low_full_1 = glm(TRUST_waste_INDEX_low~INFORMATION_waste+SYMBOL,data=SVIVA2_01,family="binomial")

tmod_trust_waste_low_haifa_1 = glm(TRUST_waste_INDEX_low~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==1),family="binomial")

tmod_trust_waste_low_shfela_1 = glm(TRUST_waste_INDEX_low~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==0),family="binomial")

sjt.glm(tmod_trust_waste_low_full_1,
       tmod_trust_waste_low_haifa_1,
       tmod_trust_waste_low_shfela_1,          
         separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Low trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))
```

Symbols decreased distrust, but only among Haifa subjects. The percentage of subjetcs in Shfela who reported very low levels of trust was very low, so there is probably a floor effect here.

##Trust aspects

```{r}
tmod_waste_competence_full = lm(TRUST_waste_competence~INFORMATION_waste+SYMBOL,data=SVIVA2_01)
tmod_waste_benevolence_full = lm(TRUST_waste_benevolence~INFORMATION_waste+SYMBOL,data=SVIVA2_01)
tmod_waste_integrity_full = lm(TRUST_waste_q5~INFORMATION_waste+SYMBOL,data=SVIVA2_01)

tmod_waste_competence_haifa = lm(TRUST_waste_competence~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==1))
tmod_waste_benevolence_haifa = lm(TRUST_waste_benevolence~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==1))
tmod_waste_integrity_haifa = lm(TRUST_waste_q5~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==1))

tmod_waste_competence_shfela = lm(TRUST_waste_competence~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==0))
tmod_waste_benevolence_shfela = lm(TRUST_waste_benevolence~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==0))
tmod_waste_integrity_shfela = lm(TRUST_waste_q5~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_waste_competence_full,tmod_waste_benevolence_full,tmod_waste_integrity_full,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real"),
       depvar.labels = c(rep(c("Competence","Benevolence","Integrity"),each=1)))

```

Again, symbols had greater effect on benevolence and integrity, and information had greater effect on competence.

##Elaboration

**perceived elaboration**
```{r}
ggplot(SVIVA2_01, aes(SYMBOL_n, ELABORATION_waste_INDEX,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration waste index", breaks = c(1:7))

```

**Elaboration time**
```{r}
ggplot(SVIVA2_01, aes(SYMBOL_n, ELABORATION_waste_time_log,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Elaboration time (log)", breaks = c(1:6),limits = c(0.5,6))

```

**Memory score**

Haifa
```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_waste_score[SVIVA2_01$AREA==1],
           SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==1],
           facet=T,
           ylim=c(0,80),
           show.prc =  F,
           title = "Haifa")

sjt.xtab(SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==1],
         SVIVA2_01$MEMORY_waste_score[SVIVA2_01$AREA==1],
         show.row.prc = T)
```

Shfela
```{r}
sjp.grpfrq(SVIVA2_01$MEMORY_waste_score[SVIVA2_01$AREA==0],
           SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==0],
           facet=T,
           ylim=c(0,60),
           show.prc =  F,
           title = "Shfela")

sjt.xtab(SVIVA2_01$SYMBOL_n[SVIVA2_01$AREA==0],
         SVIVA2_01$MEMORY_waste_score[SVIVA2_01$AREA==0],
         show.row.prc = T)
```

**models**

```{r}
tmod_elaboration_waste_index_full_1 = lm(ELABORATION_waste_INDEX~SYMBOL+INFORMATION_waste+RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_elaboration_waste_index_haifa_1 = lm(ELABORATION_waste_INDEX~SYMBOL+INFORMATION_waste+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_elaboration_waste_index_shfela_1 = lm(ELABORATION_waste_INDEX~SYMBOL+INFORMATION_waste+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

sjt.lm(tmod_elaboration_waste_index_full_1,
       tmod_elaboration_waste_index_haifa_1,
       tmod_elaboration_waste_index_shfela_1,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Fake",
                       "Real",
                       "INFORMATION (1=strong policy)",
                       "Relevance treatment"),
       show.header = TRUE,
       string.dv = "Elaboration in waste policy (perceived)",
       depvar.labels = c("Full","Haifa","Shfela"))
```
Symbols slightly increased perceived elaboration. However, as explained above, this measure is problematic due to its possible shaping by social desirability.

```{r}
tmod_elaboration_waste_time_full_1 = lm(ELABORATION_waste_time_log~SYMBOL+INFORMATION_waste+RELEVANCE_exp,data=SVIVA2_01,na.action = na.omit)
tmod_elaboration_waste_time_haifa_1 = lm(ELABORATION_waste_time_log~SYMBOL+INFORMATION_waste+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1),na.action = na.omit)
tmod_elaboration_waste_time_shfela_1 = lm(ELABORATION_waste_time_log~SYMBOL+INFORMATION_waste+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0),na.action = na.omit)

sjt.lm(tmod_elaboration_waste_time_full_1,
       tmod_elaboration_waste_time_haifa_1,
       tmod_elaboration_waste_time_shfela_1,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Fake",
                       "Real",
                       "INFORMATION (1=strong policy)",
                       "Relevance treatment"),
       show.header = TRUE,
       string.dv = "Elaboration in waste policy (Reaction time)",
       depvar.labels = c("Full","Haifa","Shfela"))

```
The real Symbols spent less time in watching the waste policy (by `r tmod_elaboration_waste_time_full_1[["coefficients"]][["SYMBOL2"]] %>% abs() %>% exp() %>% round(2)` seconds on average). Among Shfela subjects, the fake symbols had negative marginally significant effect on RT.

```{r,warning=F}
library(nnet)
library(stargazer)

tmod_elaboration_waste_memory_full_1 <- multinom(MEMORY_waste_score ~ SYMBOL+INFORMATION_waste+RELEVANCE_exp, data = SVIVA2_01)
tmod_elaboration_waste_memory_haifa_1=multinom(MEMORY_waste_score ~ SYMBOL+INFORMATION_waste+RELEVANCE_exp, data = filter(SVIVA2_01,AREA==1))
tmod_elaboration_waste_memory_shfela_1=multinom(MEMORY_waste_score ~ SYMBOL+INFORMATION_waste+RELEVANCE_exp, data = filter(SVIVA2_01,AREA==0))

stargazer(tmod_elaboration_waste_memory_full_1,
          tmod_elaboration_waste_memory_haifa_1,
          tmod_elaboration_waste_memory_shfela_1,
          type="text",
          report="vcsp",
          dep.var.caption  = "waste Memory score (multinomial logit)",
          dep.var.labels   = rep(c("1 vs. 0","2 vs. 0"),3),
          column.labels = rep(c("Full","Haifa", "Shfela"),each=2))

```
Subjects in the symbol condition were less likely to remember the issues in the policy plan.

##Moderated mediation
```{r}
xy_full = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste,data=SVIVA2_01)
xmy_full_3 = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste+INFORMATION_waste*(ELABORATION_waste_time_log+MEMORY_waste_score),data=SVIVA2_01)

xy_haifa = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste,data=filter(SVIVA2_01,AREA==1))
xmy_haifa_3 = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste+INFORMATION_waste*(ELABORATION_waste_time_log+MEMORY_waste_score),data=filter(SVIVA2_01,AREA==1))

xy_shfela = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste,data=filter(SVIVA2_01,AREA==0))
xmy_shfela_3 = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste+INFORMATION_waste*(ELABORATION_waste_time_log+MEMORY_waste_score),data=filter(SVIVA2_01,AREA==0))

sjt.lm(xy_full,xmy_full_3,
       xy_haifa,xmy_haifa_3,
       xy_shfela,xmy_shfela_3,
       separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
              pred.labels = c("Fake",
                              "Real",
                              "INFORMATION (1=strong policy)",
                               "INFORMATION*SYMBOL (fake)",
                              "INFORMATION*SYMBOL (real)",
                              "Elaboration time (log)",
                              "Memory score",
                              "INFORMATION*Elaboration time",
                              "INFORMATION*Memory score"),
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))

```
The effect of symbols is partly mediated by elaboration, in both areas. The coefficient of the real symbols decreases from `r xy_full[["coefficients"]][["SYMBOL2"]] %>% round(2)` to `r xmy_full_3[["coefficients"]][["SYMBOL2"]] %>% round(2)`, and is less significant. The coefficients of the fake symbols did not decrease.

<br>
Next, I conducted causal mediaion analysis, using `mediation` package.

Compared with control no logo.

```{r}
library(mediation)

med.fit_RT = lm(ELABORATION_total_time_log~SYMBOL*INFORMATION_waste,data=filter(SVIVA2_01,SYMBOL!=1))
med.out_RT = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste+ELABORATION_total_time_log*INFORMATION_waste,data=filter(SVIVA2_01,SYMBOL!=1))

med_RT_INFORMTION_0 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 0), sims = 100)

summary(med_RT_INFORMTION_0)
plot(med_RT_INFORMTION_0)

med_RT_INFORMTION_1 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 1), sims = 100)

summary(med_RT_INFORMTION_1)
plot(med_RT_INFORMTION_1)
```

Compared with control fake logo.

```{r}
library(mediation)

med.fit_RT = lm(ELABORATION_total_time_log~SYMBOL*INFORMATION_waste,data=filter(SVIVA2_01,SYMBOL!=0))
med.out_RT = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste+ELABORATION_total_time_log*INFORMATION_waste,data=filter(SVIVA2_01,SYMBOL!=0))

med_RT_INFORMTION_0 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 0), sims = 100)

summary(med_RT_INFORMTION_0)
plot(med_RT_INFORMTION_0)

med_RT_INFORMTION_1 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 1), sims = 100)

summary(med_RT_INFORMTION_1)
plot(med_RT_INFORMTION_1)
```

#Policies Combined
```{r}
xx0 = SVIVA2_01 %>% select(IP,AREA,AREA_names,
                      RELEVANCE_exp,RELEVANCE_exp_n,
                      SYMBOL,SYMBOL_n,
                      INFORMATION_air,INFORMATION_air_n,
                      INFORMATION_waste,INFORMATION_waste_n,
                      TRUST_air_INDEX,
                      TRUST_waste_INDEX,
                      ELABORATION_air_time_log,
                      ELABORATION_waste_time_log,
                      GOV_TRUST) %>% 
 gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
                              INFORMATION_waste),
         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
                              INFORMATION_waste_n),
         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
                              ELABORATION_waste_time_log))

```

##Descriptive results:

**All sample:** 
```{r}

xx0 %>%
    group_by(SYMBOL_n,INFORMATION_n) %>%
    summarise(n=n(),
              mean = round(mean(trust),3),
              se = round(sd(trust)/sqrt(n()),3))%>%
    mutate(ci_95 = round(1.96*se,3),
           ci_90 = round(1.65*se,3))

ggplot(xx0, aes(factor(INFORMATION_n), trust,fill=factor(INFORMATION_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Information",values=c("gray100","gray90"))+
  scale_x_discrete(name="",labels=c("",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

```{r}
ggplot(xx0, aes(factor(SYMBOL_n), trust,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  scale_fill_manual(name="Symbols",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="")+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))
```

There is a strong and significant main effect for information manipulation (`r filter(xx0,INFORMATION==1) %>% summarise(mean(trust)) %>% max() %>% round(2)` vs. `r filter(xx0,INFORMATION==0) %>% summarise(mean(trust)) %>% max() %>% round(2)`). t= `r t.test(trust~INFORMATION,data=xx0)[["statistic"]] %>% round(3)`). 
Significant main effect of symbol (`r filter(xx0,SYMBOL==2)%>%summarise(mean(trust))%>%round(3) %>% max()` [`r filter(xx0,SYMBOL==2)%>%summarise(mean(trust)+1.96*sd(trust)/sqrt(n()))%>%round(3) %>% max()`,`r filter(xx0,SYMBOL==2)%>%summarise(mean(trust)-1.96*sd(trust)/sqrt(n()))%>%round(3) %>% max()`] vs. `r filter(xx0,SYMBOL==1)%>%summarise(mean(trust))%>%round(3) %>% max()` and `r filter(xx0,SYMBOL==0)%>%summarise(mean(trust))%>%round(3) %>% max()` in control groups fake symbol and no symbol). Difference from fake symbol is marginally significant. But the effect is weaker compared with the effect in air policy (perhaps weaker symbol).

**INFORMATION x SYMBOL**

```{r}
ggplot(xx0, aes(factor(SYMBOL_n), trust,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~INFORMATION_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray90","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))

ggplot(xx0, aes(factor(SYMBOL_n),trust,color=factor(INFORMATION_n),linetype=factor(INFORMATION_n)))+ 
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.2,size=1,position=position_dodge(0.1),linetype=1) + 
  stat_summary(fun.y = mean, geom = "point", size=2,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=1, aes(group = INFORMATION_n),position=position_dodge(0.1))+
  scale_color_manual(name="Substantive information",values=c("gray35","gray1"))+
    scale_linetype(guide = FALSE)+
  scale_x_discrete(name="Symbolic elements",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Trust in policy",breaks = seq(3,5,by=0.1))
```

```{r}
ggplot(xx0, aes(factor(SYMBOL_n), trust,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~INFORMATION_n)+
  scale_fill_manual(name="Information",values=c("gray100","gray90","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "waste Trust index", breaks = c(1:7))

ggplot(xx0, aes(factor(SYMBOL_n),trust,color=factor(INFORMATION_n),linetype=factor(INFORMATION_n)))+ 
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.2,size=1,position=position_dodge(0.1),linetype=1) + 
  stat_summary(fun.y = mean, geom = "point", size=2,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=1, aes(group = INFORMATION_n),position=position_dodge(0.1))+
  scale_color_manual(name="Substantive information",values=c("gray35","gray1"))+
    scale_linetype(guide = FALSE)+
  scale_x_discrete(name="Symbolic elements",labels=c("no symbols","fake symbols","real symbols"))+
  scale_y_continuous(name = "Trust in policy",breaks = seq(3,5,by=0.1))+
  facet_grid(~AREA_names)
```

##Main Models

```{r}
library(lme4)

tmod_combined_full_1 = lmer(trust~policy+AREA+INFORMATION+SYMBOL+(1|IP),data=xx0)
tmod_combined_full_2 = lmer(trust~policy+AREA+SYMBOL*INFORMATION+(1|IP),data=xx0)
tmod_combined_full_3 = lmer(trust~policy+AREA*SYMBOL+INFORMATION*SYMBOL+(1|IP),data=xx0)
tmod_combined_full_4 = lmer(trust~policy+AREA*SYMBOL*INFORMATION+(1|IP),data=xx0)
tmod_combined_full_5 = lmer(trust~policy*AREA*SYMBOL+SYMBOL*INFORMATION+(1|IP),data=xx0)
tmod_combined_full_6 = lmer(trust~AREA*(SYMBOL+policy)+INFORMATION*SYMBOL+(1|IP),data=xx0)

sjt.lmer(tmod_combined_full_1,
       tmod_combined_full_2,
       tmod_combined_full_6,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("POLICY (1=waste reduction)",
                       "AREA (1=Haifa-bay)",
                       "INFORMATION (1=strong policy)",
                       "Fake symbols",
                       "Real symbols",
                       "INFORMATION*fake symbols",
                       "INFORMATION*real symbols",
                       "AREA*fake symbols",
                       "AREA*real symbols",
                       "AREA*POLICY"),
       show.header = TRUE,
       string.dv = "Trust in policy",
       depvar.labels = paste0("(",1:3,")"," ",c(rep(c(""),each=2))))
```
I also analyzed the effect on extremely low trust, or distrust (<=2).

```{r}
xx0=xx0%>% 
  mutate(trust_low = ifelse(trust<=2,1,0)) 
```

```{r}
xx0 %>%
    group_by(SYMBOL_n) %>%
    summarise(n=n(),
              mean = mean(trust_low),
              se = sd(trust_low)/sqrt(n()))%>%
    mutate(ci_95 = 1.96*se,
           ci_90 = 1.65*se) %>% 
    mutate(mean = paste0(round(mean*100,1),"%"),
           se = paste0(round(se*100,1),"%"),
           ci_95 = paste0(round(ci_95*100,1),"%"),
           ci_90 = paste0(round(ci_90*100,1),"%"))

```

```{r}
ggplot(xx0, aes(factor(SYMBOL_n), trust_low))+ 
  theme_bw()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 1))+
  facet_grid(~INFORMATION_n)+
  scale_y_continuous(name = "Low trust",breaks = seq(0,0.4,by=0.05))

```

```{r}
tmod_trust_low_full_1 = glm(trust_low~SYMBOL+INFORMATION+AREA,data=xx0,family="binomial")
tmod_trust_low_full_2 = glm(trust_low~SYMBOL*(INFORMATION+AREA),data=xx0,family="binomial")

sjt.glm(tmod_trust_low_full_1,
       tmod_trust_low_full_2,          
         separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Fake",
                       "Real",
                       "INFORMATION (1=strong policy)",
                       "AREA (1=Haifa)",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)",
                       "AREA*SYMBOL (fake)",
                       "AREA*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Low trust in policy")
```

##Trust aspects

##Moderated mediation

<br>
Next, I conducted causal mediaion analysis, using `mediation` package.

Compared with control no logo.

```{r}
library(mediation)
tmod_combined_full_2 = lmer(trust~policy+AREA+SYMBOL*INFORMATION+(1|IP),data=xx0)

med.fit_RT = lm(ELABORATION_time_log~SYMBOL*INFORMATION+policy+AREA,data=filter(xx0,SYMBOL!=1))
med.out_RT = lm(trust~SYMBOL*INFORMATION+policy+AREA+ELABORATION_time_log*INFORMATION,data=filter(xx0,SYMBOL!=1))

med_RT_INFORMTION_0 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_time_log", 
                      covariates = list(INFORMATION = 0), sims = 100)

summary(med_RT_INFORMTION_0)
plot(med_RT_INFORMTION_0)

med_RT_INFORMTION_1 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 1), sims = 100)

summary(med_RT_INFORMTION_1)
plot(med_RT_INFORMTION_1)
```

Compared with control fake logo.

```{r}
library(mediation)

med.fit_RT = lm(ELABORATION_total_time_log~SYMBOL*INFORMATION_waste,data=filter(SVIVA2_01,SYMBOL!=0))
med.out_RT = lm(TRUST_waste_INDEX~SYMBOL*INFORMATION_waste+ELABORATION_total_time_log*INFORMATION_waste,data=filter(SVIVA2_01,SYMBOL!=0))

med_RT_INFORMTION_0 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 0), sims = 100)

summary(med_RT_INFORMTION_0)
plot(med_RT_INFORMTION_0)

med_RT_INFORMTION_1 = mediate(med.fit_RT,
                       med.out_RT,
                      treat = "SYMBOL",
                      mediator = "ELABORATION_total_time_log", 
                      covariates = list(INFORMATION_waste = 1), sims = 100)

summary(med_RT_INFORMTION_1)
plot(med_RT_INFORMTION_1)
```

#Within subjects

An alternative way to examine the hypothesis that symbols decrease elaboration, and hence reduce the effect of substantive information, is by conducting a within subject analysis (as opposed to between subjects). For each subject, I took the delta between her trust in strong and weak policy plans.

First, I show that the delta is positively correlated with the elaboration measures:

```{r}
sjp.scatter(SVIVA2_01$ELABORATION_total_time_log,
            SVIVA2_01$WITHIN_DELTA,
            fit.line = TRUE,
            show.ci = TRUE,
            geom.size = 1,
            axis.titles=c("Elaboration time (log)","Within subject (Delta strong - weak policy)"))
```

```{r}
sjp.scatter(SVIVA2_01$MEMORY_total,
            SVIVA2_01$WITHIN_DELTA,
            fit.line = TRUE,
            show.ci = TRUE,
            geom.size = 1,
            jitter.dots = T,
            emph.dots = T,
            axis.titles=c("Memory test score","Within subject (Delta strong - weak policy)"))
```

Next, I compared this delta across symbol conditions.  
```{r}
ggplot(SVIVA2_01, aes(factor(SYMBOL_n), WITHIN_DELTA,fill=factor(SYMBOL_n)))+ 
  geom_boxplot()+
  theme_classic()+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", colour = "red",width=0.1,size=1) + 
  stat_summary(fun.y = mean, geom = "point", colour = "red",size=2)+
  stat_summary(fun.y = mean, geom = "line", colour = "red",size=1, aes(group = 
                                                                         1))+
  facet_grid(~AREA_names)+
  scale_fill_manual(name="Information",values=c("gray100","gray95","gray60"))+
  scale_x_discrete(name="",labels=c("","",""))+
  scale_y_continuous(name = "Delta (strong - weak policy)", breaks = c(-6:6))

```

```{r}
tmod_delta_full_1 = lm(WITHIN_DELTA~INFORMATION_air+SYMBOL+RELEVANCE_exp,data=SVIVA2_01)

tmod_delta_haifa_1 = lm(WITHIN_DELTA~INFORMATION_air+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==1))

tmod_delta_shfela_1 = lm(WITHIN_DELTA~INFORMATION_air+SYMBOL+RELEVANCE_exp,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_delta_full_1,
        tmod_delta_haifa_1,
        tmod_delta_shfela_1,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Air-strong & waste-weak",
                       "Fake",
                       "Real",
                       "Relevance treatment"),
       show.header = TRUE,
       string.dv = "Delta (strong - weak policy)",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=1)))

```
In both areas the real symbols increased the delta between strong and weak policy plans.

Next, I test whether this latter effect is mediated by elaboration:

```{r}
tmod_delta_full_11 = lm(WITHIN_DELTA~INFORMATION_air+SYMBOL+RELEVANCE_exp+ELABORATION_total_time_log+MEMORY_total,data=SVIVA2_01)

tmod_delta_haifa_11 = lm(WITHIN_DELTA~INFORMATION_air+SYMBOL+RELEVANCE_exp+ELABORATION_total_time_log+MEMORY_total,data=filter(SVIVA2_01,AREA==1))

tmod_delta_shfela_11 = lm(WITHIN_DELTA~INFORMATION_air+SYMBOL+RELEVANCE_exp+ELABORATION_total_time_log+MEMORY_total,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_delta_full_1,tmod_delta_full_11,
        tmod_delta_haifa_1,tmod_delta_haifa_11,
        tmod_delta_shfela_1,tmod_delta_shfela_11,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("Air-strong & waste-weak",
                       "Fake",
                       "Real",
                       "Relevance treatment",
                       "Elaboration time (log)",
                       "Memory score"),
       show.header = TRUE,
       string.dv = "Delta (strong - weak policy)",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))

```
In both areas, the effect of the real symbols gets weaker. This indicated that the effect is partly mediated by the negative effect of symbols on elaboration.

#Conclusions
The results indicate that:

+ In both policies, subjects reported higher trust in strong policy compared with weak policy. 
+ In both policies, subjects reported higher trust (and/or lower distrust) when the communication included symbols (compared with both control groups). The effect is greater among Haifa subjects, and marginally significant among shfela subjects, possibly due to ceiling effect. The fake symbols also had a positive, but weaker effect. 
+ In both policies, the effect of symbols was higher among those who were presented with weak policy. The interaction is sufficiently significant in the waste policy.
+ In both policies, no evidence that greater personal relevance (either operationalized via manipulation or via comparison between areas) moderates the effects of information and symbols, as expected. 
+ In both policies, symbols in communication decreased elaboration of the policy.
+ In both policies, the effect of the symbols of trust is partly mediated by its negative effect on elaboration.

#Robust analyses

Next, I show a series of robust analyses. In all these robust analyses, the results remain largely similar.

##Robust subset (symbols recognizability)
First, I screen out those subjects who did not recognize the real symbols.

```{r}
SVIVA2_robust_air_1 = SVIVA2_01 %>% 
  filter(RECOGNIZE_air_real>1)

SVIVA2_robust_waste_1 = SVIVA2_01 %>% 
  filter(RECOGNIZE_waste_real>1)

```

**Air policy**

```{r}
tmod_air_full_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=SVIVA2_robust_air_1)
tmod_air_full_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=SVIVA2_robust_air_1)

tmod_air_haifa_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_robust_air_1,AREA==1))
tmod_air_haifa_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_robust_air_1,AREA==1))

tmod_air_shfela_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_robust_air_1,AREA==0))
tmod_air_shfela_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_robust_air_1,AREA==0))

sjt.lm(tmod_air_full_1,tmod_air_full_2,
        tmod_air_haifa_1,tmod_air_haifa_2,
        tmod_air_shfela_1,tmod_air_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in Air policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))
```

The effect of the symbols slightly increases, as expected.

**waste policy**

```{r}
tmod_waste_full_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=SVIVA2_robust_waste_1)
tmod_waste_full_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=SVIVA2_robust_waste_1)

tmod_waste_haifa_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_robust_waste_1,AREA==1))
tmod_waste_haifa_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_robust_waste_1,AREA==1))

tmod_waste_shfela_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_robust_waste_1,AREA==0))
tmod_waste_shfela_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_robust_waste_1,AREA==0))

sjt.lm(tmod_waste_full_1,tmod_waste_full_2,
        tmod_waste_haifa_1,tmod_waste_haifa_2,
        tmod_waste_shfela_1,tmod_waste_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))
```
The effect of the symbol is weaker compared with the main models.

##1st order
Next, I only analyzed the first policy which was presented to subjects, to rule out carryover effect.

**Air policy**

```{r}
tmod_air_full_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AIR_order==1))
tmod_air_full_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_01,AIR_order==1))

tmod_air_haifa_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AIR_order==1,AREA==1))
tmod_air_haifa_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_01,AIR_order==1,AREA==1))

tmod_air_shfela_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AIR_order==1,AREA==0))
tmod_air_shfela_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_01,AIR_order==1,AREA==0))

sjt.lm(tmod_air_full_1,tmod_air_full_2,
        tmod_air_haifa_1,tmod_air_haifa_2,
        tmod_air_shfela_1,tmod_air_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in Air policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))
```

**Waste policy**

```{r}
tmod_waste_full_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,WASTE_order==1))
tmod_waste_full_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_01,WASTE_order==1))

tmod_waste_haifa_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,WASTE_order==1,AREA==1))
tmod_waste_haifa_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_01,WASTE_order==1,AREA==1))

tmod_waste_shfela_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_01,WASTE_order==1,AREA==0))
tmod_waste_shfela_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_01,WASTE_order==1,AREA==0))

sjt.lm(tmod_waste_full_1,tmod_waste_full_2,
        tmod_waste_haifa_1,tmod_waste_haifa_2,
        tmod_waste_shfela_1,tmod_waste_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))
```

In both models, there were no differences to main models.

##Unfiltered sample

Next, I analyzed the full sample, without any filters (N=`r N`).

**Air**

```{r}
tmod_air_full_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=SVIVA2_00)
tmod_air_full_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=SVIVA2_00)

tmod_air_haifa_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_00,AREA==1))
tmod_air_haifa_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_00,AREA==1))

tmod_air_shfela_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_00,AREA==0))
tmod_air_shfela_2 = lm(TRUST_air_INDEX~INFORMATION_air*SYMBOL,data=filter(SVIVA2_00,AREA==0))

sjt.lm(tmod_air_full_1,tmod_air_full_2,
        tmod_air_haifa_1,tmod_air_haifa_2,
        tmod_air_shfela_1,tmod_air_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in Air policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))
```

**Waste**

```{r}
tmod_waste_full_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=SVIVA2_00)
tmod_waste_full_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=SVIVA2_00)

tmod_waste_haifa_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_00,AREA==1))
tmod_waste_haifa_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_00,AREA==1))

tmod_waste_shfela_1 = lm(TRUST_waste_INDEX~INFORMATION_waste+SYMBOL,data=filter(SVIVA2_00,AREA==0))
tmod_waste_shfela_2 = lm(TRUST_waste_INDEX~INFORMATION_waste*SYMBOL,data=filter(SVIVA2_00,AREA==0))

sjt.lm(tmod_waste_full_1,tmod_waste_full_2,
        tmod_waste_haifa_1,tmod_waste_haifa_2,
        tmod_waste_shfela_1,tmod_waste_shfela_2,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
       pred.labels = c("INFORMATION (1=strong policy)",
                       "Fake",
                       "Real",
                       "INFORMATION*SYMBOL (fake)",
                       "INFORMATION*SYMBOL (real)"),
       show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = c(rep(c("Full","Haifa","Shfela"),each=2)))
```

##Haifa sample - air

Next, I conduct several analyses only on sample of Haifa-bay.

* Model1 - Excluding relatives working in factories (*n* = `r filter(SVIVA2_01,AREA==1,FACTORIES_relatives==0) %>% nrow`).
* Model2 - Control for subjects with young children (assuming that air pollution is most relevant to those with young children)
* Model3 = Control for interest in environmental issues.

```{r}
x2 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL,data=filter(SVIVA2_01,AREA==1,FACTORIES_relatives==0))
x3 = lm(TRUST_air_INDEX~CHILDREN_young*(INFORMATION_air+SYMBOL),data=filter(SVIVA2_01,AREA==1))
x4 = lm(TRUST_air_INDEX~ENVIRONMENT_INTEREST*(INFORMATION_air+SYMBOL),data=filter(SVIVA2_01,AREA==1))

sjt.lm(x2,x3,x4,separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05,
        show.header = TRUE,
       string.dv = "Trust in waste policy",
       depvar.labels = paste0("(",1:4,")"))

```

Removing those with relatives working in the industrial area does not change the results. Having young children and interest in environmental issues do not decrease the effect of the symbol.

##Perceived Relevance.

Next, I test the interaction between the manipulations and perceived personal relevance (instead of areas).
**Air**

```{r}
x2 = lm(TRUST_air_INDEX~RELEVANCE_air_obs+INFORMATION_air+SYMBOL,data=SVIVA2_01)
x3 = lm(TRUST_air_INDEX~RELEVANCE_air_obs*(INFORMATION_air+SYMBOL),data=SVIVA2_01)

sjt.lm(x2,x3,separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05)
```

**Waste**

```{r}
x2 = lm(TRUST_waste_INDEX~RELEVANCE_waste_obs+INFORMATION_waste+SYMBOL,data=SVIVA2_01)
x3 = lm(TRUST_waste_INDEX~RELEVANCE_waste_obs*(INFORMATION_waste+SYMBOL),data=SVIVA2_01)

sjt.lm(x2,x3,separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05)
```
No significant interaction between perceived personal relevance and the manipulations.

##Adding controls

```{r}
tmod_air_cov_full_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL+GOV_TRUST+IDEOLOGY+EDUCATION,data=SVIVA2_01)
tmod_air_cov_full_2 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL*(GOV_TRUST+IDEOLOGY+EDUCATION),data=SVIVA2_01)
tmod_air_cov_full_3 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL*GOV_TRUST+IDEOLOGY+EDUCATION,data=SVIVA2_01)

tmod_air_cov_haifa_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL+GOV_TRUST+IDEOLOGY+EDUCATION,data=filter(SVIVA2_01,AREA==1))
tmod_air_cov_haifa_2 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL*(GOV_TRUST+IDEOLOGY+EDUCATION),data=filter(SVIVA2_01,AREA==1))
tmod_air_cov_haifa_3 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL*GOV_TRUST+IDEOLOGY+EDUCATION,data=filter(SVIVA2_01,AREA==1))

tmod_air_cov_shfela_1 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL+GOV_TRUST+IDEOLOGY+EDUCATION,data=filter(SVIVA2_01,AREA==0))
tmod_air_cov_shfela_2 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL*(GOV_TRUST+IDEOLOGY+EDUCATION),data=filter(SVIVA2_01,AREA==0))
tmod_air_cov_shfela_3 = lm(TRUST_air_INDEX~INFORMATION_air+SYMBOL*GOV_TRUST+IDEOLOGY+EDUCATION,data=filter(SVIVA2_01,AREA==0))

sjt.lm(tmod_air_cov_full_1,tmod_air_cov_full_2,tmod_air_cov_full_3,
       #tmod_air_cov_haifa_1,tmod_air_cov_haifa_2,tmod_air_cov_haifa_3,
       #tmod_air_cov_shfela_1,tmod_air_cov_shfela_2,tmod_air_cov_shfela_3,
        separate.ci.col=F,show.ci=T,remove.spaces=T,cell.spacing=0.05)

```

The effect of symbols depends on subjects' trust vis-a-vis government. Symbols are more effective on those with higher trust in government.

#Summary statistics

```{r, warning = FALSE, message = FALSE}
sjt.df(SVIVA2_01)
```

```{r}
sjt.corr(SVIVA2_01[,c("AREA",
                      "INFORMATION_air",
                      "SYMBOL_bi",
                      "TRUST_air_INDEX",
                      "TRUST_air_INDEX_1",
                      "ELABORATION_air_INDEX",
                      "ELABORATION_air_time_log",
                      "MEMORY_air_score",
                      "RELEVANCE_air_obs",
                      "TRUST_waste_INDEX",
                      "TRUST_waste_INDEX_1",
                      "ELABORATION_waste_time_log",
                      "RELEVANCE_waste_obs",
                      "GOV_TRUST",
                      "IDEOLOGY",
                      "CHILDREN_young",
                      "AGE",
                      "EDUCATION",
                      "INCOME",
                      "GENDER")],
         na.deletion = "pairwise",
         triangle = "lower",
         remove.spaces=T,
         digits=2)
```

### 2018-03-09 SVIVA_exp2_dm_03.R

@@ -1,0 +1,529 @@
+### SVIVA experiment 2 data management ###
+
+# Hi there!
+
+#loading packages
+
+library(tidyverse)
+#library(psych)
+library(stargazer)
+library(car)
+library(sjPlot)
+library(stringr)
+library(lubridate)
+
+
+#loading raw data CSV file
+SVIVA2_raw_00 <- read.csv("SVIVA_exp2.csv")
+CITY_00 <- read.csv("CITY.csv")
+
+SVIVA2_raw <- SVIVA2_raw_00 %>% filter(V10==1)
+CITY <- CITY_00 %>% filter(V10==1)
+
+
+SVIVA2_raw[is.na(SVIVA2_raw)] <- 0
+
+SVIVA2_00 = SVIVA2_raw %>%
+  dplyr::select(V4,V5) %>%
+  mutate(IP = SVIVA2_raw$V6,
+         START_DATE = dmy_hm(SVIVA2_raw$V8),
+         END_DATE = dmy_hm(SVIVA2_raw$V9)) %>%  
+         mutate(TIMER_total = as.integer(END_DATE-START_DATE),
+         FINISHED = SVIVA2_raw$V10) %>%
+  dplyr::select(-c(1:2)) %>%
+  
+  ##Define variables####
+
+
+##interface
+mutate(MOBILE = if_else(SVIVA2_raw$Q23.1+SVIVA2_raw$Q22.1==1,1,0)) %>%
+  
+  #controls####
+mutate(ENVIRONMENT_INTEREST = Recode(SVIVA2_raw$Q3.2,"0=NA"),
+       ENVIRONMENT_FOLLOW = Recode(SVIVA2_raw$Q3.3,"0=NA"),
+       ENVIRONMENT_PREFERENCE = Recode(SVIVA2_raw$Q3.4,"0=NA"),
+       GOV_EVALUATION = SVIVA2_raw$Q2.3,
+       GOV_TRUST = SVIVA2_raw$Q2.4,
+       IDEOLOGY = SVIVA2_raw$Q2.5,
+       CHILDREN = if_else(SVIVA2_raw$Q313==5,0,1),
+       CHILDREN_young = if_else(SVIVA2_raw$Q313 %in% c(1,2),1,0),
+       FACTORIES_relatives = Recode(SVIVA2_raw$Q314,"0=NA;1=0;2=1"))%>%
+  
+  
+  ##demographics
[…]

### 2018-03-12 paper.Rmd
12.3.18_01

@@
 Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements have a greater effect on citizens' trust the less citizens perceive the issue as personally relevant.
-Second, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in ill-conceived policies.
+Also, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in in logically-unpersuasive policy plans.
 I put these hypotheses to test through a survey experiment, where I examine 859 Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
@@
 
-Public administration scholars are often concerned about the implications of citizens’ low trust in government, and their undervaluation of public-service performance.
+Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their undervaluation of public-service performance.
 One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens.
 Congruently, over the past generation, many economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
-In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].
+In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on contracts related to public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].
 
@@
 Congruently, public communications are expected to increase citizens' trust insofar as they provide citizens favorable information on organizations' performance and logically persuasive explanations for their policies.
-At the same time, experiment-based studies that explored the responses of citizens to variation in substantive information have revealed potential cognitive biases that may distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
+At the same time, experiment-based studies that explored the responses of citizens to variation in substantive information revealed potential cognitive biases that may distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
 
-Recently, a few studies also pointed to the potential effect of the *symbolic* elements entangled in government communications, such as brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016].
+Recently, a few studies also pointed to the potential effect of the *symbolic* elements entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
 These symbolic elements are strategically designed to evoke citizens’ positive associations and emotions.
@@
 
-Hence, in order to assess the positive and negative possible implications of government communications with citizens, we need to understand the nature of the psychological effect of symbolic elements on citizens' attitudes' formation, and its limitations.
+Hence, in order to assess the positive and negative possible implications of government communications with citizens, we need to better understand the nature of the psychological effect of symbolic elements on citizens' attitudes' formation, and its limitations.
 To date, public administration research still lacks theory and robust empirical evidence of the mechanisms through which symbolic elements in public communications can increase citizens trust, and their interaction with the substantive content of information in government communications, which is perceived as the basis for rational attitudes formation.
-Therefore, this study focuses on the following questions: *Under what conditions can symbolic elements in governemnt communication increase citizens' trust in governemnt policy?* Specifically, *does the effect of symbolic elements depend on the substantive information presented in the communication?* *Can these symbols offset the rational, negative effect of logically unpersuasive arguments?*
+Therefore, this study focuses on the following questions: *Under what conditions can symbolic elements in governemnt communication increase citizens' trust in governemnt policy?* Specifically, *does the effect of symbolic elements depend on the substantive information presented in the communication?* *Can these symbols offset the rational, negative effect of negative and logically unpersuasive information?*
 
-Given the theoretical gap in existing public administration literature, I address these research questions by introducing a theoretical framework from social psychology - the Elaboration Likelihood Model (ELM).
-ELM theorizes the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences on attitude change [@petty_1986; @petty_2011].
-Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that can be transferred to the government entity or policy, and thereby increasing their trust in it.
-This effect is likely to be attenuated the more citizens perceive the communication as personally relevant, and therefore motivated to elaborate on it.
-*Second*, symbolic elements may decrease citizens' inclination to elaborate on the communication and scrutinize it, thus causing them to disregard substantive information that would have affected their trust.
+Given the theoretical gap in existing public administration literature, I address these research questions by introducing the Elaboration Likelihood Model (ELM) from social psychology.
+ELM provides a comprehensive theoretical for the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences on attitude change  [@petty_1986; @petty_2011].
+Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that can be transferred to the government entities and policies, and thereby increasing their trust in them.
+I expect that this effect is attenuated the more citizens perceive the communications as personally relevant, because they are more motivated to think about their messages.
+*Second*, symbolic elements may decrease citizens' inclination to scrutinize the content of the communication, thus causing them to disregard substantive information that would have affected their trust.
 Congruently, symbols are likely to have greater effect when entangled in communications that describe logically unpersuasive policies or report poor performance.
@@
 To empirically test these theoretical expectations about the effect of symbolic elements on citizens' trust, and their interaction with the substantive information in the communication and the personal relevance of the issue, I conducted a large randomized survey experiment in a fairly realistic setting among `r SVIVA2_01%>%nrow()` Israeli citizens.
-The experiment focuses on the empirical case of the Israeli Environment Protection Ministry (hereafter EPM), and examines citizens' trust in two policy plans: reducing the air pollution in a specific area in the country - the Bay of Haifa, and reducing domestic waste and increasing recycling.
+The experiment focuses on the empirical case of the Israeli Environment Protection Ministry, and examines citizens' trust in two policy plans: reducing the air pollution in a specific area in the country - the Bay of Haifa, and reducing domestic waste and increasing recycling.
 In the experiment, the two policies are presented to subjects under different experimental conditions of substantive information (logically persuasive vs.
@@
 In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about the negative information.
-I did not find any support for the hypothesis that the effect of the symbolic elements is attenuated by the  perceived personal relevance of the policy issue.
+I did not find support for the hypothesis that the effect of the symbolic elements is attenuated by the  perceived personal relevance of the policy issue.
 I discuss the theoretical and normative implications of these findings.
@@
 Recently, however, a few experimental studies tackled the issue.
-@marvel_2015 analyzed US citizens' responses to a television advertisement of the public Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and upbeat background music.
+@marvel_2015 analyzed US citizens' responses to a television advertisement of the public Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music.
 His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
-Still, this study did not disentangle the effects of the symbolic and informational elements of the ad on participants’ attitudes.
-An additional study by @karens_2016 did examine the distinct effect of symbols on citizens' trust.
+@teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and affect, that can shape citizens' support in governemnt policy (depending on citizens' political party identification).
+These two studies provide examples for the role of symbols in shaping citizens' attitudes.
+Still, they did not effectively disentangle the effects of the symbolic and informational aspects of agency names and elements in the commercial.
+
+A study by @karens_2016 did examine the distinct effect of symbols in communications on citizens' trust.
 The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of the organization's logo in the communication of the policy plans.
 They found that including the organization’s logo significantly increased citizens' trust in these policies.
-Their results show an impressive effect size equivalent to 0.7 standard deviations [^1].
+Their results show an impressive effect size equivalent to 0.7 standard deviations.
+[^footnote_karens]
 
-[^1]: The effect size they found was smaller with regard to the "air quality" policy compared with the "digital skills" policy which were presented (Cohen's d = 0.7 vs.
+[^footnote_karens]: The effect size they found was smaller with regard to the "air quality" policy compared with the "digital skills" policy which were presented (Cohen's d = 0.7 vs.
 0.6).
@@
 They compared between citizens who were personally exposed to prolonged power outages, and others who were not.
-They found that the symbolic element had a positive effect on citizens' trust in the organization (a modest effect size equivalent to 0.25 standard deviations), including among those who personally experienced poor performance.
+They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations).
 Building on social psychology theory and marketing research, the scholars suggested that the effect occurs by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them (evaluative conditioning).
@@
 
-Although these studies linked between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this effect.
-Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective.
+Even though these studies linked between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this positive effect.
+Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust.
 Additionally, non of these studies has theorized and empirically tested the interaction between symbolic elements and citizens’ internalization of substantive information in communications.
 We do not know whether well-designed symbols reinforce, or offsets, citizens' rational responses to information.
-Specifically, as I explained above, it is essential to assess the possibility that symbols can compensate for negative or logically unpersuasive information, that would have yielded negative responses.
+Specifically, as I explained above, it is essential to assess the possibility that symbols can unduly compensate for negative or logically unpersuasive information, that would have yielded negative responses.
+
 To address this theoretical gap in public administration research, I propose a nuanced theoretical framework for the effects of symbols in communications and their interaction with information, building on social psychology theory on persuasive communication.
@@
 
-# The Elaboration Likelihood Model (ELM) of communication and persuasion
+# The Elaboration Likelihood Model and the various mechanisms of persuasion by elements in communications
 
-The Elaboration Likelihood Model (ELM), which has been developed in the social psychology literature to explain attitudinal responses to persuasive communication [@petty_1986; @petty_2011] provides a comprehensive theoretical framework for investigating peoples' varying responses to persuasive communications.
+The Elaboration Likelihood Model (ELM) from social psychology provides a comprehensive theoretical framework for investigating peoples' varying responses to persuasive communications [@petty_1986; @petty_2011].
 In addition to it's general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
@@
 
-According to ELM, people respond differently to persuasive communications, depending on the amount of thinking that they dedicate to the message content.
+According to ELM, people respond differently to different elements in persuasive communications, depending on the amount of thinking that they dedicate to the message content.
 Persuasion can occur when thinking is high or low, but the processes and consequences are likely to differ in each situation.
 This range between high and low degrees of thought is referred to as the "elaboration continuum".
-Along this continuum, there are numerous specific processes of persuasion or attitude change.
-At the high end of the elaboration continuum, people are likely to respond cognitively by scrutinizing the arguments central to the merits of the issue.
-At the low end, people may respond to simple cues automatically and unconsciously  through primitive psychological processes that require very little amount of cognitive effort.
-For instance, an attractive source would evoke positive emotions, that would be transferred to the evaluated object through evaluative conditioning, and lead to more favorable attitudes.
-These two different processes are referred to as the "central and peripheral routes for persuasion", a conceptualization that largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].
+Along this continuum, there are numerous specific processes of persuasion (or attitude change) that can occur.
+At the high end of the elaboration continuum, also called the "central route", people are likely to respond cognitively by scrutinizing the arguments central to the merits of the issue.
+At the low end, also called "the peripheral route" people may respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as a transfer of affect[^footnote_dual_process_theories].
+These different persuasion mechanisms are likely to cause different types of attitude change.
+Persuasion through the central route is expected to be relatively more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
+Of course, much of the time, people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.
 
-People's placement along the elaboration continuum is determined by their motivation and ability to think about the communication.
-For instance, a person that perceives the issue as personally relevant is motivated to invest in thinking about it, and accordingly is likely to process the communication through the central route [@petty_1979; @petty_1981; @petty_1983].
-On the other hand, a person that lacks profound knowledge about the subject in the communication, will not be able to scrutinize the content, and thus is more likely to rely on peripheral cues [For a review of motivational and ability factors affecting likelihood to elaborate see @petty_1986; @petty_1998].
-These different persuasion mechanisms are also likely to yield different types of attitude change.
-Persuasion through the central route is expected to be relatively more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
-Of course, much of the time, persuasion is determined by a mixture of these processes.
+[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].
 
-Overall, ELM identifies several mechanisms by which variables can affect attitudes.
-Variables can function as one or more of the following: (1) Providing potential arguments regarding the evaluated issue that can be scrutinized based on their logical persuasive quality (central route processing); (2) Affecting the direction of thinking (bias) by making positive or negative thoughts more likely to come to mind (in central route processing); (3) Serving as potential peripheral cues that affect attitudes in a direction consistent with their valence, such as in the abovementioned example of the attractive source; (4) Affecting the ammount of thinking people devote to the communication by affecting motivation or ability to think, thus locating them along the elaboration continuum; (5) Affecting people's confidence in their thoughts.
-The same variable can have different functions for people at different locations along the elaboration continuum.
-For instance, test...
-number of lines..
-Also, in principle, a variable can affect attitudes in multiple ways.
-For instance, @petty_1983 demonstrated in a lab experiment that a famous athlet endourser in an advertisment of a new disposable razor reduces the ammount of thinking about the content of the ad, and at the same time serves as a potential peripheral cue that increases positive attitudes towards the product by transferring the positive affect from the endourser to the product.
+People at different locations along the elaboration continuum may process the same element in a communication in different ways.
+Consider for instance a text that contains a series of logical arguments supporting a certain position.
+Those at the high end of the continuum would regard this text as arguments, and systematically scrutinize it based on its logical persuasive quality (central route processing).
+At the same time, those at the low end of the continuum are likely to disregard the content of the text, and instead, they may use the number of lines in the text as a cue for its strength (peripheral route processing).
+Some elements are potential cues that lack any logical quality at all, such as the attractiveness of the source.
+These latter elements may affect the attitudes of those at the low end, while they are not likely to persuade those at the high end [@petty_1986].
 
-# The multiple roles of symbols in government public communicatoins.
+ELM further postulates that the placement of people along the elaboration continuum in any given situation is determined by their motivation and ability to think about the message.
+For instance, people that perceive the issue as personally relevant are more motivated to invest in thinking about it, and accordingly, they are more likely to use the central route [@petty_1979; @petty_1981; @petty_1983].
+On the other hand, those who lack basic knowledge about the subject, will not be able to scrutinize the content, and thus they are likely to rely on peripheral cues [For a review of motivational and ability factors affecting likelihood to elaborate see @petty_1986; @petty_1998].
+People's motivation and/or ability to think can be also shaped by elements in communications, for instance, by a title that emphasizes the relevance of the message for people's lives.
+These elements can locate people higher or lower on the elaboration continuum, and thus they can cause attitude change in interaction with other elements that can function as arguments (when increasing the amount of thinking) or peripheral cues (when decreasing the amount of thinking).
+
+Finally, some elements in communications can function both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
+Thus, these elements can shape people's attitudes through more than one causal mechanism.
+@petty_1986 have argued that we are more likely to find these complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
+When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.
+
+<br>
+
+# ELM and the roles of symbolic elements and information in government public communications
+
+How can we apply the theoretical framework of ELM on the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?
+
+In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated to do so.
+Conversely, symbolic elements represent potential peripheral cues, which can affect attitudes through the peripheral route, by evoking positive emotions and associations attributed to government organizations and their policies [@alonbarkat_2017].
+Accordingly, the effect of symbolic elements on citizens' trust is likely to depend on citizens' motivation to cognitively invest and think about the policy issues.
+Specifically, I expect citizens to be more motivated to engage in the cognitive work necessary to evaluate the communication the more they perceive the policy as having significant consequences for their own personal lives [@petty_1981; @petty_1983; @petty_1986; @petty_2002; @petty_2011].
+The more they perceive the policy issue as personally relevant, the more they are likely to focus on scrutinizing the content of the message, and the less they are likely to rely on peripheral cues, such as the symbolic elements entangled in the communication.
+
+Accordingly, I expect that:
+
+>*H<sub>1</sub> - Symbolic elements in government organizations' public communications are likely to increase citizens' trust in the government organizations and the policies presented in the communication.*
+
+>*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be attenuated the more citizens perceive the policy issue in the communication as personally relevant.*
+
+However, we can also derive from ELM a second mechanism by which symbolic elements can increase citizens' trust.
+In addition to their direct positive effect on trust (via the peripheral route), symbols can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g.
+information on poor performance) and weak arguments (e.g.
+logically unpersuasive description of their policy plans).
+
+Symbolic elements can decrease citizens' ability and motivation to think about the message in several ways.
+First, they can distract citizens and absorb their  attention  and cognitive efforts, and thus make it more difficult for them to scrutinize the message, a general mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986].
+Second, symbols can decrease citizens' inclination to think through their positive affect that places citizens in a positive mood.
+It has been suggested that positive mood tends to weaken people's cognitive ability [@mackie_1989; @eagly_1993].
+Also, the positive mood is likely to attenuate people's motivation to scrutinize messages, due to their desire to maintain the mood and avoid message processing that would depress it [@bless_1990; @schwarz_1991].
+Congruently, studies have suggested that the use of humor in communications decreases message elaboration and reduces their ability to differentiate between logically strong and weak arguments [@nabi_2007; @young_2008].
+In the context of government communications, thinking about the content of the message - government organizations and policies - is likely to yield negative thoughts among most people [@marvel_2015; @marvel_2015a; @hvidman_2016].
+Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about these bureaucratic affairs, which would have bring negative thoughts that would have depressed that positive mood.
+
+The expectation that symbols will reduce the amount of thinking entails an interaction between symbols and negative or logically weak substantive information.
+Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize substantive information that would have decreased their trust.
+Accordingly, I expect that:
+
+>*H<sub>3</sub> - Symbolic elements in government public communications are likely to decrease the amount of thinking about the content of the communication.*
+
+>*H<sub>4</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
+
+>*H<sub>5</sub> - The abovementioned conditioned effect of symbolic elements on citizens' trust is likely to be mediated by the decrease in the amount of thinking (a moderated mediation hypothesis).*
+
+<br>
 
@@
 
+<br>
+
 ## *Empirical case background*
+
+<br>
 
@@
 
+<br>
+
 # Results
 
----
+<br>
 
@@
 
----
+<br>
 

### 2018-05-18 SVIVA_exp2_01.Rmd
12.3.18_01
Add files via upload

@@
 output:
-  pdf_document:
-    toc: yes
   html_document:
     code_folding: hide
+    always_allow_html: yes
     fig_captions: yes
@@
       toc_depth: 3
+  pdf_document:
+    toc: yes
 ---
@@
 ```{r , include=FALSE, echo=FALSE}
-load(".RData")
+load("SVIVA_R_ENV.RData")
 ```
@@
 
-```{r}
-t = SVIVA2_00 %>%
-  filter(TRUST_air_timer>=10|
-           TRUST_waste_timer>=10)
-```
-*	Answering the two sets of DV questions (trust in air pollution and waste policies) in less than 10 seconds each: `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)
-
-```{r}
-t = SVIVA2_00 %>%
-  filter(REPETITION_elaboration==0)
-```
-
-*	Repetition of the same value (except 4) in the elaboration questions (which include 2 reversed items, on a scale of 1 to 7): `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)
-
 ```{r,warning=FALSE,message=FALSE}
@@
          IMC==1,
-         TIMER_total>=3,TIMER_total<=30,  
-         TRUST_air_timer>=10|
-           TRUST_waste_timer>=10, 
-         REPETITION_elaboration==0)
+         TIMER_total>=3,TIMER_total<=30)#,  
+         #TRUST_air_timer>=10|
+          # TRUST_waste_timer>=10, 
+         #REPETITION_elaboration==0)
 ```
@@
                                  IMC==1&
-                                 TIMER_total>=3 & TIMER_total<=30 &  
-                                 (TRUST_air_timer>=10|
-                                   TRUST_waste_timer>=10)& 
-                                 REPETITION_elaboration==0,0,1))
+                                 TIMER_total>=3 & TIMER_total<=30,0,1))
 
@@
 sjt.grpmean(SVIVA2_01[,c("GENDER")],factor(SVIVA2_01$AREA))
+
+sjt.grpmean(SVIVA2_01[,c("INCOME")],factor(SVIVA2_01$AREA))
 
@@
 The first plot shows the distribution of the reaction time (RT) measured in seconds. To reduce skewness, I log transformed this measure, according to the following formula:
-$ELABORATION timelog = log(ELABORATIONtime+1)$
 
@@
 ```{r}
-xx0 = SVIVA2_01 %>% select(IP,AREA,AREA_names,
+xx0 = SVIVA2_01 %>% dplyr::select(IP,AREA,AREA_names,
                       RELEVANCE_exp,RELEVANCE_exp_n,

### 2018-05-18 paper.Rmd
Add files via upload

@@
 output:
-  word_document: default
-  pdf_document:
-    toc: yes
   html_document:
@@
       toc_depth: 3
+  pdf_document:
+    toc: yes
+  word_document: default
 link-citations: yes
@@
 ```{r , include=FALSE, echo=FALSE}
-load(".RData")
+#load("SVIVA_R_ENV.RData")
+source("SVIVA_exp2_dm_03.R")
+
+SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
+SVIVA2_01_center = filter(SVIVA2_01,AREA==0)
 ```
@@
 library(tidyverse)
+library(stargazer)
+library(car)
+library(broom)
+library(kableExtra)
+```
+
+```{r,echo=FALSE,warning=FALSE,message=FALSE}
+N_raw = nrow(SVIVA2_raw_00)
+N_0=SVIVA2_00%>%nrow()
+N_1=SVIVA2_01%>%nrow()
+
+filter_IP = N_0-(SVIVA2_00 %>%
+  distinct(IP,.keep_all=TRUE) %>% nrow())
+filter_age = N_0-(SVIVA2_00 %>%
+  filter(!(AGE%in% 1:17))%>% nrow())
+filter_IMC = N_0-(SVIVA2_00 %>%
+  filter(IMC==1)%>% nrow())
+filter_time = N_0-(SVIVA2_00 %>%
+  filter(TIMER_total>=3,TIMER_total<=30) %>% nrow())
+
+N_1_haifa = filter(SVIVA2_01,AREA==1) %>% nrow()
+N_1_center = filter(SVIVA2_01,AREA==0) %>% nrow()
+
 ```
@@
 Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements have a greater effect on citizens' trust the less citizens perceive the issue as personally relevant.
-Also, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in in logically-unpersuasive policy plans.
-I put these hypotheses to test through a survey experiment, where I examine 859 Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
+Also, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in logically-unpersuasive policy plans.
+I put these hypotheses to test through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
 The policies are presented to subjects under different conditions of substantive information (logically persuasive vs.
-unpersuasive policies) and symbolic elements (logo, green color, and celebrities endorsers).
-I operationalize personal relevance both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+unpersuasive policies) and symbolic elements (logo, color, and celebrities endorsers).
+I operationalize personal relevance by comparing between citizens from the polluted Haifa-Bay area and others.
 The results do not support the hypothesis that personal relevance attenuates the effect of symbols.
@@
 One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens.
-Congruently, over the past generation, many economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
+Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
 In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on contracts related to public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].
 
-The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
+The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017].
-Congruently, public communications are expected to increase citizens' trust insofar as they provide citizens favorable information on organizations' performance and logically persuasive explanations for their policies.
-At the same time, experiment-based studies that explored the responses of citizens to variation in substantive information revealed potential cognitive biases that may distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
+Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on organizations' performance and logically persuasive explanations for their policies.
+At the same time, experiment-based studies that explored the responses of citizens to substantive information revealed cognitive biases that distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
 
-Recently, a few studies also pointed to the potential effect of the *symbolic* elements entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-These symbolic elements are strategically designed to evoke citizens’ positive associations and emotions.
-Their processing requires relatively little cognitive effort, and is often unconscious and automatically activated without much thinking, as opposed to the processing of substantive information which requires elaboration.
-Whereas the responsiveness of citizens to substantive information is perceived as a positive phenomenon from a normative view of democratic theory, the potential effect of symbolic elements can be problematic.
-Shaping citizens' view of governments through symbols stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
-Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape from justified public criticism [@alonbarkat_2017].
+Recently, a few studies pointed to the additional effect of *symbolic* elements that are entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
+These studies demonstrated that government organizations may cause citizens to view them more favorably through familiar and well-designed symbolic elements that evoke positive associations and emotions.
+Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens trust.
+Additionally, these previous studies did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
 
-Hence, in order to assess the positive and negative possible implications of government communications with citizens, we need to better understand the nature of the psychological effect of symbolic elements on citizens' attitudes' formation, and its limitations.
-To date, public administration research still lacks theory and robust empirical evidence of the mechanisms through which symbolic elements in public communications can increase citizens trust, and their interaction with the substantive content of information in government communications, which is perceived as the basis for rational attitudes formation.
-Therefore, this study focuses on the following questions: *Under what conditions can symbolic elements in governemnt communication increase citizens' trust in governemnt policy?* Specifically, *does the effect of symbolic elements depend on the substantive information presented in the communication?* *Can these symbols offset the rational, negative effect of negative and logically unpersuasive information?*
+This research gap has normative significance.
+Whereas the responsiveness of citizens to substantive information is perceived favorably from a normative view of democratic theory, the potential effect of symbolic elements can be problematic.
+One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
+Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
+Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *under what conditions do symbolic elements  increase citizens' trust in governemnt policy?* And specifically, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
 
-Given the theoretical gap in existing public administration literature, I address these research questions by introducing the Elaboration Likelihood Model (ELM) from social psychology.
-ELM provides a comprehensive theoretical for the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences on attitude change  [@petty_1986; @petty_2011].
-Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that can be transferred to the government entities and policies, and thereby increasing their trust in them.
+To address these research questions, I draw upon the social psychology Elaboration Likelihood Model (ELM).
+ELM provides a comprehensive theoretical framework for the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change  [@petty_1986; @petty_2011].
+Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
 I expect that this effect is attenuated the more citizens perceive the communications as personally relevant, because they are more motivated to think about their messages.
-*Second*, symbolic elements may decrease citizens' inclination to scrutinize the content of the communication, thus causing them to disregard substantive information that would have affected their trust.
-Congruently, symbols are likely to have greater effect when entangled in communications that describe logically unpersuasive policies or report poor performance.
+*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
 
-To empirically test these theoretical expectations about the effect of symbolic elements on citizens' trust, and their interaction with the substantive information in the communication and the personal relevance of the issue, I conducted a large randomized survey experiment in a fairly realistic setting among `r SVIVA2_01%>%nrow()` Israeli citizens.
-The experiment focuses on the empirical case of the Israeli Environment Protection Ministry, and examines citizens' trust in two policy plans: reducing the air pollution in a specific area in the country - the Bay of Haifa, and reducing domestic waste and increasing recycling.
-In the experiment, the two policies are presented to subjects under different experimental conditions of substantive information (logically persuasive vs.
-unpersuasive policy plans) and symbolic elements (ministry’s logo, green color, and celebrities from public campaigns, compared with two control groups).
-To account for variation in perceived personal relevance, I compared citizens who reside in the polluted Haifa-Bay area with other citizens from selected cities with a similar profile.
-In addition, I tested the effect of personal relevance experimentally, by priming subjects to think about environmental issues in their area of residence.
+To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow() %>% round(-1)` Israeli citizens.
+The experiment focuses on the empirical case of the Israeli Environment Protection Ministry.
+I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information of the communications (logically persuasive vs.
+unpersuasive policy plans) and by symbolic elements in them (real symbols vs.
+fake symbols and no symbols conditions).
+In addition, I examine the moderating role of the perceived personal relevance of these policies.
 
-I find that the symbolic elements increased citizens' trust in both policies.
-In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about the negative information.
+I find that the symbolic elements increased citizens' trust in these policies.
+In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about its content.
 I did not find support for the hypothesis that the effect of the symbolic elements is attenuated by the perceived personal relevance of the policy issue.
@@
 These elements are widely used by businesses and political candidates to attract targeted consumers and voters.
-Yet, they can be also found in the communications  of government bureaucracies with citizens, including in their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.
+Yet, they can be also found in the communications of government bureaucracies with citizens, including their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.
 
@@
 His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
-@teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and affect, that can shape citizens' support in governemnt policy (depending on citizens' political party identification).
+@teodoro_2018 suggested that the name of US federal agencies not only represents information about their activities, but may also carry specific symbolic meaning and affect that can shape citizens' support for government policy (depending on citizens' political party identification).
 These two studies provide examples for the role of symbols in shaping citizens' attitudes.
-Still, they did not effectively disentangle the effects of the symbolic and informational aspects of agency names and elements in the commercial.
+Still, they did not effectively disentangle the effects of the symbolic and informational aspects of the studied public communications.
 
@@
 The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of the organization's logo in the communication of the policy plans.
-They found that including the organization’s logo significantly increased citizens' trust in these policies.
+They found that including the Commission’s logo significantly increased citizens' trust in these policies.
 Their results show an impressive effect size equivalent to 0.7 standard deviations.
@@
 
-@alonbarkat_2017 explored whether symbolic element can increase citizens' trust in poorly performing organizations.
-To do so, they examined Israeli citizens' trust in the Israel Electricity Corporation, a state owned company, and it's shaping by their exposure to comic cartoon figures which were routinely presented in the organization's public campaigns.
+@alonbarkat_2017 examined Israeli citizens' trust in the Israel Electricity Corporation, a state owned company, and it's shaping by their exposure to comic cartoon figures that were routinely presented in the organization's public campaigns.
 They compared between citizens who were personally exposed to prolonged power outages, and others who were not.
 They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations).
-Building on social psychology theory and marketing research, the scholars suggested that the effect occurs by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them (evaluative conditioning).
-They proposed that effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.
+Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them (evaluative conditioning).
+They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.
 
-The aforementioned studies tend to suggest that public communications can increase citizens' trust in government organizations and their policies, not only by delivering substantive information, but also symbolically, by incorporating elements that evoke positive associations and emotions.
-Moreover, the findings of @alonbarkat_2017 suggest that incorporating symbolic elements in public communications can unduly compensate for poor government performance, thus pointing to their potential negative implications.
+The aforementioned studies tend to suggest that public communications increase citizens' trust in government organizations and their policies, not only by conveying valuable substantive information, but also by incorporating symbolic elements that evoke positive associations and emotions.
+Moreover, the findings of @alonbarkat_2017 suggest that incorporating symbolic elements in public communications can unduly compensate for poor government performance, thus pointing to their potential detrimental implications.
 
-Even though these studies linked between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this positive effect.
+Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this effect.
 Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust.
-Additionally, non of these studies has theorized and empirically tested the interaction between symbolic elements and citizens’ internalization of substantive information in communications.
-We do not know whether well-designed symbols reinforce, or offsets, citizens' rational responses to information.
-Specifically, as I explained above, it is essential to assess the possibility that symbols can unduly compensate for negative or logically unpersuasive information, that would have yielded negative responses.
+Additionally, these studies neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications.
+We do not know whether well-designed symbols reinforce, or offset, citizens' rational responses to information.
+Specifically, as explained above, it is essential to assess the possibility that symbols can unduly compensate for unfavorable or logically unpersuasive information that should yield negative responses.
 
@@
 
-The Elaboration Likelihood Model (ELM) from social psychology provides a comprehensive theoretical framework for investigating peoples' varying responses to persuasive communications [@petty_1986; @petty_2011].
-In addition to it's general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
-Yet, thus far, the relevance of ELM has not been directly examined in public administration research, in relation to citizens' responses to government communication.
+The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" communications [@petty_1986; @petty_2011].
+In addition to its general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
+Yet, thus far, the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
 
-According to ELM, people respond differently to different elements in persuasive communications, depending on the amount of thinking that they dedicate to the message content.
-Persuasion can occur when thinking is high or low, but the processes and consequences are likely to differ in each situation.
+According to ELM, peoples' responses to different elements in persuasive communications depends on the amount of thinking that they dedicate to the message content.
+Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
 This range between high and low degrees of thought is referred to as the "elaboration continuum".
 Along this continuum, there are numerous specific processes of persuasion (or attitude change) that can occur.
-At the high end of the elaboration continuum, also called the "central route", people are likely to respond cognitively by scrutinizing the arguments central to the merits of the issue.
-At the low end, also called "the peripheral route" people may respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as a transfer of affect[^footnote_dual_process_theories].
-These different persuasion mechanisms are likely to cause different types of attitude change.
-Persuasion through the central route is expected to be relatively more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
+At the high end of the elaboration continuum, also called the "central route", people are likely to respond by cognitively scrutinizing the arguments central to the merits of the issue.
+At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as a transfer of affect[^footnote_dual_process_theories].
+These different persuasion mechanisms are likely to cause divergent types of attitudinal change.
+Persuasion through the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
 Of course, much of the time, people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.
@@
 Those at the high end of the continuum would regard this text as arguments, and systematically scrutinize it based on its logical persuasive quality (central route processing).
-At the same time, those at the low end of the continuum are likely to disregard the content of the text, and instead, they may use the number of lines in the text as a cue for its strength (peripheral route processing).
-Some elements are potential cues that lack any logical quality at all, such as the attractiveness of the source.
-These latter elements may affect the attitudes of those at the low end, while they are not likely to persuade those at the high end [@petty_1986].
+Conversely, those at the low end of the continuum are likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
+Some elements provide potential cues that lack any logical quality at all, such as the physical attractiveness of the source.
+These latter elements may affect the attitudes of those at the low end, but are less likely to persuade those at the high end [@petty_1986].
 
 ELM further postulates that the placement of people along the elaboration continuum in any given situation is determined by their motivation and ability to think about the message.
-For instance, people that perceive the issue as personally relevant are more motivated to invest in thinking about it, and accordingly, they are more likely to use the central route [@petty_1979; @petty_1981; @petty_1983].
-On the other hand, those who lack basic knowledge about the subject, will not be able to scrutinize the content, and thus they are likely to rely on peripheral cues [For a review of motivational and ability factors affecting likelihood to elaborate see @petty_1986; @petty_1998].
-People's motivation and/or ability to think can be also shaped by elements in communications, for instance, by a title that emphasizes the relevance of the message for people's lives.
-These elements can locate people higher or lower on the elaboration continuum, and thus they can cause attitude change in interaction with other elements that can function as arguments (when increasing the amount of thinking) or peripheral cues (when decreasing the amount of thinking).
+The literature proposes a variety of such motivational and ability factors.
+Most prominently, the more people perceive the issue as personally relevant, the more motivated they are to invest in thinking about it, and accordingly, they more likely they are to use the central route [@petty_1979; @petty_1981; @petty_1983].
+Also, studies have demonstrated that the more people are distracted, the more difficult it is  for them to scrutinize the message arguments, a mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986].
+People's location along the elaboration continuum is also determined by their affective state or mood.
+Positive mood (compared with neutral or negative moods) reduces people's cognitive ability and attenuates their motivation to think, due to their desire to maintain their positive mood and avoid message processing that would depress it [@worth_1987; @mackie_1989; @bless_1990; @schwarz_1991; @petty_2015; but see: @wegener_1995].[^footnote_elm_factors]
+
+[^footnote_elm_factors]: For a thorough review of motivational and ability factors affecting likelihood to elaborate see @petty_1998.
+
+People's motivation and/or ability to think is shaped not only by factors external to the communication, but also by elements in the communication itself.
+For example, using second-person pronouns in the message (i.e.
+"you", "your") increases people's perceived personal relevance, and motivation to elaborate [@burnkrant_1989]; Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986]; The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008].
+Affecting the amount of thinking can cause attitude change in interaction with elements in the communication that can function as arguments or peripheral cues.
+Accordingly, decreasing the amount of thinking enhances the effect of peripheral cues, whereas increasing the amount of thinking enhances the effect of the logical arguments.
 
@@
 Thus, these elements can shape people's attitudes through more than one causal mechanism.
-@petty_1986 have argued that we are more likely to find these complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
+Continuing with the above mentioned examples, background music and humor can function at the same time as factors that reduce elaboration and as peripheral cues.
+@petty_1986 have suggested that we are more likely to find these complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
 When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.
@@
 
-How can we apply the theoretical framework of ELM on the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?
+How may we apply the theoretical framework of ELM to the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?
 
 In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated to do so.
-Conversely, symbolic elements represent potential peripheral cues, which can affect attitudes through the peripheral route, by evoking positive emotions and associations attributed to government organizations and their policies [@alonbarkat_2017].
+Conversely, symbolic elements represent potential peripheral cues, which can affect attitudes through the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
 Accordingly, the effect of symbolic elements on citizens' trust is likely to depend on citizens' motivation to cognitively invest and think about the policy issues.
-Specifically, I expect citizens to be more motivated to engage in the cognitive work necessary to evaluate the communication the more they perceive the policy as having significant consequences for their own personal lives [@petty_1981; @petty_1983; @petty_1986; @petty_2002; @petty_2011].
-The more they perceive the policy issue as personally relevant, the more they are likely to focus on scrutinizing the content of the message, and the less they are likely to rely on peripheral cues, such as the symbolic elements entangled in the communication.
+Specifically, I expect that the more citizens perceive the policy issue as personally relevant, the more they are likely to focus on scrutinizing the content of the message, and the less they are likely to rely on the symbolic elements entangled in the communication.
 
@@
 
->*H<sub>1</sub> - Symbolic elements in government organizations' public communications are likely to increase citizens' trust in the government organizations and the policies presented in the communication.*
+>*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
 
->*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be attenuated the more citizens perceive the policy issue in the communication as personally relevant.*
+>*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be attenuated the more citizens perceive the policy issues in the communications as personally relevant.*
 
-However, we can also derive from ELM a second mechanism by which symbolic elements can increase citizens' trust.
+However, we can also derive from ELM a second mechanism by which symbolic elements may increase citizens' trust.
 In addition to their direct positive effect on trust (via the peripheral route), symbols can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g.
@@
 Symbolic elements can decrease citizens' ability and motivation to think about the message in several ways.
-First, they can distract citizens and absorb their  attention  and cognitive efforts, and thus make it more difficult for them to scrutinize the message, a general mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986].
-Second, symbols can decrease citizens' inclination to think through their positive affect that places citizens in a positive mood.
-It has been suggested that positive mood tends to weaken people's cognitive ability [@mackie_1989; @eagly_1993].
-Also, the positive mood is likely to attenuate people's motivation to scrutinize messages, due to their desire to maintain the mood and avoid message processing that would depress it [@bless_1990; @schwarz_1991].
-Congruently, studies have suggested that the use of humor in communications decreases message elaboration and reduces their ability to differentiate between logically strong and weak arguments [@nabi_2007; @young_2008].
-In the context of government communications, thinking about the content of the message - government organizations and policies - is likely to yield negative thoughts among most people [@marvel_2015; @marvel_2015a; @hvidman_2016].
-Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about these bureaucratic affairs, which would have bring negative thoughts that would have depressed that positive mood.
+First, they can cause elaboration disruption, by distracting citizens and absorbing their attention and cognitive efforts [@petty_1976; @petty_1986].
+Second, they can decrease citizens' motivation and ability to think about the message content by creating a positive affect and placing citizens in a positive mood.
+As explained above, the postulation that positive mood decreases elaboration has been explained, in part, by a mood maintenance mechanism [@mackie_1989; @bless_1990; @schwarz_1991].
+This mechanism is particularly relevant to the context of government communications, in which thinking about the content of the message - government organizations and policies - is likely to yield negative mood among most people [@marvel_2015; @marvel_2015a; @hvidman_2016].
+Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about tedious bureaucratic affairs, which would depress their positive mood.
 
-The expectation that symbols will reduce the amount of thinking entails an interaction between symbols and negative or logically weak substantive information.
-Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize substantive information that would have decreased their trust.
+The expectation that symbols will reduce the amount of thinking entails an interaction between symbols and the substantive information in the communications.
+Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize information that would have decreased their trust.
 Accordingly, I expect that:
 
->*H<sub>3</sub> - Symbolic elements in government public communications are likely to decrease the amount of thinking about the content of the communication.*
+>*H<sub>3</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
 
->*H<sub>4</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
+>*H<sub>4</sub> - The abovementioned conditioned effect of symbolic elements on citizens' trust is likely to be mediated by the decrease in the amount of thinking (a moderated mediation hypothesis).*
 
->*H<sub>5</sub> - The abovementioned conditioned effect of symbolic elements on citizens' trust is likely to be mediated by the decrease in the amount of thinking (a moderated mediation hypothesis).*
+The theoretical hypotheses are graphically displayed in **Figure 1**.
+
+<br>
+**Figure 1: Theoretical model**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model.png) 
+<br>
+
+Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
+On the other hand, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, for two reasons: First, citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2016; @james_2017b].
+Congruently, the effect of positive information (versus a medium level) is likely to be relatively small, and hence neutralizing this effect may not make much difference.
+Second, even when communications include favorable information, symbols can still have a positive effect on trust through the peripheral route (in accordance with my first hypothesis).
+Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction, which can be .
 
@@
 
-<br>
-
-## *Empirical case background*
+To empirically test the above mentioned hypotheses, I designed a randomized survey experiment, which simulates citizens' responses to government organizations' communications about their policy plans.
+Such communications can be found in publicized reports, pamphlets, websites, new media pages and ads.
+Focusing on communication of future policy plans, as opposed to communications on performance of existing policies, enables me to utilize a real-world empirical case without compromising the reliability  of the manipulation of the content.
+This is because most citizens do not have prior knowledge of organizations' future policy plans, and thus they will be more willing to trust a fictional communication of an organization with regard to its future policy.
 
@@
 
-## *Experimental design*
+##*The empirical case*
+
+Empirically, I focused on the case of the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, both at the national and local levels.
+I analyzed the effects of informative and symbolic elements in EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
+In the survey, the communications about the two policy plans, in which I manipulated the informative and symbolic elements, are presented to the participants as sections from the EPM's official publication of its annual work plan.
+Methodologically, EPM makes a good case study for two main reasons.
+
+*First*, EPM has invested greatly over the past years in public communications.
+In these various communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
+Here, I decided to focus on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**.
+The first symbolic element is the unique brand logo of the EPM (image a.
+in figure 1).
+This logo consists of pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second symbolic element in which I focused is the green color, which is strongly associated with taking care of the environment.
+The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity" [@vandenbosch_2005].
+The third element is celebrity endorsements.
+Specifically, I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, that previously endorsed two salient advertising campaigns of the EPM.
+The campaign starring the comedian Tal Friedman (image b.) was launched in 2010, and included a series of advertisements in which Friedman was presented with a green grass head, and accordingly the campaign's slogan was: "starting to think green".
+The campaign starring the comedian Ido Rosenblum (image c.) was launched in 2017, and was focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.
+
+In the course of the survey experiment, I confirmed that the EPA logo and the images of the celebrities from the campaigns are familiar to the participants.
+`r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize EPA logo to some extent and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`% , respectively).
+In robust analyses I further exclude those who do not recognize these symbols.[^footnote_prior_studies]
+
+[^footnote_campaigns]: Multimedia files of these campaigns are available in EPM's website: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/default.aspx.
+
+[^footnote_prior_studies]: In two prior online survey tests, which I conducted before the experiment, I collected further information about the affect and symbolic associations of these symbols.
+These results, which are reported in the supplementary appendix [##TBA##], substantiate my empirical assumption that these elements evoke positive emotions Israeli citizens, and that citizens automatically associate them with EPM and its policies.
+These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to position people in a positive mood.
+
+<br>
+**Figure 2: symbolic elements of EPM**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/EPM_symbols.png) 
+<font size="0.5">
+
+Notes:
+
+a. EPM logo.
+b.
+Tal Friedman, comedian,  EPM campaign “starting to think green” (2010): "Isn't money growing on trees?
+Moving to environmental consumption and saving at least 6,000 NIS per year!", "starting to think green", "The Environmental Protection Ministry".
+c.
+Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "The reusable bag is again left at home?
+A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".
+
+</font>
+
+<br>
+
+The *second* reason for selecting EPM regards its policy plan regarding the pollution in the Haifa-Bay area, which offers a fortunate case for examining the moderating role of perceived personal relevance.
+The Haifa-Bay area, located on the Mediterranean coast of northern Israel, is characterized by relatively high levels of air pollution, mainly due to the concentration of heavy industry.
+Beginning in the late 2000s, the Ministry of Environment protection has been implementing policy programs to reduce the high levels of pollution in the area.
+The uniqueness of this policy issue is rooted in the fact that it represents natural variation in citizens' perceived personal relevance (between those who reside in the polluted area, and others), which is not strongly confounded with differences in personal knowledge, as in most cases [@petty_1983].
+The air pollution in the Haifa-bay area  is an intangible, invisible, ambiguous and complicated policy issue.
+Those who reside in a polluted area, are not likely to have much greater knowledge and understanding of the issue.
+Accordingly, when they are exposed to a communication about this personally relevant issue, they are more motivated to scrutinize it, yet are not more capable to do so than others.
+Hence, this case enables to isolate the distinct effect of personal relevance.
+As explained below, the sample population of the experiment consists of residents of Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
+
+I supplemented the Haifa-bay air-pollution policy with a second policy plan, which is likely to be perceived as equally relevant for those Haifa-bay residents and others.
+This comparison further enables me to confirm that differences between the two groups, if found, are explained by differences in the perceived personal relevance of the policy issue.
+Furthermore, testing the effects of symbolic elements and information on two different policy plans provides a more rigorous test for the theory.
+Hence, I selected EPM's policy for reducing of domestic waste and increasing recycling, a tangible policy issue which I expect to be perceived as equally personally relevant by both groups of citizens.
+For the sake of simplicity, I henceforth refer to these two policy plans as "air-pollution" and "recycling" policies.
+
+Data from the survey experiment confirms the empirical assumption that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents (`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_air_obs))%>%max()%>%round(1)` [`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_air_obs)-1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`, `r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_air_obs)+1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`] compared with `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_air_obs))%>%max()%>%round(1)` [`r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_air_obs)-1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`, `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_air_obs)+1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`] on a scale of 1-7).
+As for the second, recycling policy, it is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them (`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_waste_obs))%>%max()%>%round(1)` versus `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_waste_obs))%>%max()%>%round(1)`).
+Participants were also asked to describe the most salient environmental issue in their particular area of residence.
+Indeed, most of the Haifa-Bay subjects regarded in their responses to the air-pollution generated from the industrial area, and many of them linked it to higher morbidity rates in the area.[^footnote_environment_concern] In a prior survey, I empirically confirmed the assumption that the Haifa-bay residents do not have significantly greater knowledge about the air-pollution policy (see supplementary appendix ##TBA##).
+
+[^footnote_environment_concern]: Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, whereas relatively few of them mentioned air-pollution as a prominent environmental concern in their area.
+
+<br>
+
+##*Sample selection and recruitment*
+
+The survey was conducted in late January 2018.
+To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
+I will henceforth refer to these two groups of cities as Haifa-bay and center.
+
+I conducted the survey experiment through Qualtrics Survey Software.
+To select and recruit residents of these specific cities, I was assisted by an Israeli internet research panel company *iPanel*.
+The online survey link was sent by iPanel, between 28.1-1.2.2018.
+A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+These filters are not significantly associated with the areas or the experimental conditions.
+Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r filter(SVIVA2_01,AREA_reside_haifa==1)%>%nrow()` reside in the Haifa-bay cities, and `r filter(SVIVA2_01,AREA_reside_haifa==0)%>%nrow()` reside in the center cities.
+
+[^footnote_responserate]: According to iPanel's reporting, 5,077 people were invited to fill the survey.
+Of these people, approximately 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
+Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
+
+<br>
+
+## *Procedure*
+
+To disguise the purpose of the experiment, the survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general, as opposed to attitudes about EPM or the specific two policies.
+The participants were first asked pre-manipulation questions about their political ideology and their trust in government ministries in general and evaluation of their performance.
+Thereafter, they were asked about their interest in environmental policy issues, the extent to which they follow these issues in the media, their preference for more/less government investment in this field.
+They were also asked to describe the most salient environmental issue in their particular area of residence.[^footnote_relevance_manipulation]
+
+[^footnote_relevance_manipulation]: The latter questions about environmental policy was initially designed as a manipulation of for perceived personal relevance (specifically for Haifa-Bay subjects with regard to the air-pollution policy).
+The questions which are mentioned above were included in the treatment group, whereas subjects in the control group were asked instead equivalent questions about their field of occupation.
+However, manipulation checks suggested that these priming questions did not enhance the perceived personal relevance of these policies for the participants (either from Haifa-Bay or center cities).
+Therefore, I will not regard to this treatment in the paper.
+
+Thereafter, participants were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
+Each policy plan included the title of the policy goal (i.e.
+"reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).
+
+The air-pollution and recycling policy plans were presented to each subject in a random order.
+Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
+logically persuasive policy plan) and weak policy (i.e.
+logically unpersuasive).
+The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
+The proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles in the Haifa-Bay area.
+The strong recycling policy regarded increasing the supervision of manufacturers and reducing the use of disposable bags.
+The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
+Accordingly, the weak policy plans regarded reducing of regulatory burden on the factories/ manufacturers, and raising citizens' awareness of the efforts to improve air quality/reduce waste.
+The full texts of the weak and strong conditions for the two policy plans is displayed in Appendix A.
+For each subject, one of the two policies was strong and the other was weak, which enables me to compare both between- and within-subjects.
+For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
+
+The participants are also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment, control no-symbols and control fake-symbols.
+In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
+Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy, given the relevance of the campaign to the policy plan; Friedman's image from the campaign of "starting to think green", which was more general and regarded to a variety of environmental issues, was attached to the air-pollution policy.
+In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
+Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
+The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
+Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.
+In that sense, it can be regarded as a placebo.
+In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM (supplementary appendix ##TBA##).
+The symbols conditions are displayed in the Appendix B.
+
+Each policy plan was followed by questions about respondents' trust in the policy.
+Afterwards, the subjects were asked about their perceived level of elaboration on the last policy that was presented to them, conducted a memory test.
+They were also asked about the extent to which they perceive the two policies as personally relevant to themselves.
+Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
+After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
+Finally, the participants are debriefed about the manipulations, and the possible deception.
+An English translation of the full survey
+is available from the supplementary appendix.
+
+Altogether, for each policy plan, the survey experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
+weak policy).
+The experimental groups are fairly balanced with respect to demographics, pre-manipulation variables and the two areas.
+The assignment to the different experimental groups is graphically presented in Figure 3.
+
+<br>
+**Figure 3: Experimental design for policy plan communications**
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow.png)
+
+##*Operationalization of variables*
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
+                               TRUST_air_q2,
+                               TRUST_air_q3,
+                               TRUST_air_q4,
+                               TRUST_air_q5,
+                               TRUST_air_q6))[["total"]][["raw_alpha"]] %>% round(2)
+
+alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
+                               TRUST_waste_q2,
+                               TRUST_waste_q3,
+                               TRUST_waste_q4,
+                               TRUST_waste_q5,
+                               TRUST_waste_q6))[["total"]][["raw_alpha"]] %>% round(2)
+
+cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate %>% mean() %>% round(2)
+
+cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate %>% mean() %>% round(2)
+
+cor_RT_delta = cor.test(SVIVA2_01$ELABORATION_total_time_log,
+                          SVIVA2_01$WITHIN_DELTA)$estimate %>% mean() %>% round(2)
+
+cor_memory_delta = cor.test(SVIVA2_01$MEMORY_total,
+                          SVIVA2_01$WITHIN_DELTA,method="spearman")$estimate %>% mean() %>% round(2)
+
+t_air_information = t.test(TRUST_air_INDEX~INFORMATION_air,SVIVA2_01)
+t_waste_information = t.test(TRUST_waste_INDEX~INFORMATION_waste,SVIVA2_01)
+
+```
+
+My outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
+This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
+Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
+
+To assess the levels of thinking or elaboration on the policy plans, I used two measures: First, I measure the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time or RT), log transformed to reduce skewness.
+Second, I used a memory test, asking participants whether a list of four items were included in the policy plan, of which two were/were not included (participants could also select "I don't know").
+The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
+Accordingly, participants could receive a score of 0, 1 or 2.[^footnote_elaboration] The two measures of elaboration are correlated with each other (Spearman rho = `r cor_elaboration_air` and `r cor_elaboration_waste` for the air-pollution and recycling policies respectively), which substantiates their validity.
+Higher reaction time and memory scores were also positively associated with lower delta (within-subjects) between trust in strong and weak policy plans, which indicates the extent to which subjects payed attention to the logical quality of the policy plans (correlations with reaction time and memory score, respectively, are r = `r cor_RT_delta` and rho = `r cor_memory_delta`).
+
+[^footnote_elaboration]: In addition, I included in the survey a battery of five items that measure participants' subjective perception of their level of elaboration.
+I initially sought to use these items as an additional measure for elaboration.
+However, I decided to forgo this subjective measure, due to its lack of correlation with the reaction time and memory test score, and its possible bias by people's disinclination to admit that they did not thoroughly read the policy plans.
+
+My main independent variables are the above mentioned manipulations for information and symbols, and the distinction between the Haifa-Bay and center, as a proxy for the extent to which they perceive the air-pollution policy as personally relevant.
+The latter was coded according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
 
@@
 
+**Figure 4** graphically shows the distributions of participants' trust in the air-pollution and recycling policy plans.
+Both distributions are left skewed, with the majority of subjects reporting 4 or more (on a 1-7 scale).
+Yet, participants were more likely to report low levels of trust in the air-pollution policy, and accordingly its mean is slightly lower than the recycling policy (`r SVIVA2_01%>%summarise(mean(TRUST_air_INDEX))%>%max()%>%round(2)` [`r SVIVA2_01%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r SVIVA2_01%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`], compared with `r SVIVA2_01%>%summarise(mean(TRUST_waste_INDEX))%>%max()%>%round(2)` [`r SVIVA2_01%>%summarise(mean(TRUST_waste_INDEX)-1.96*sd(TRUST_waste_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r SVIVA2_01%>%summarise(mean(TRUST_waste_INDEX)+1.96*sd(TRUST_waste_INDEX)/sqrt(n()))%>%max()%>%round(2)`]).
+Higher levels of trust are associated with high trust vis a vis government and left-wing ideology.
+
+**Figure 4: Distribution of trust in the two policies**
+
+```{r,echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'), fig.show='hold'}
+ggplot(SVIVA2_01, aes(x=TRUST_air_INDEX)) + 
+  geom_histogram(aes(y = (..count..)/sum(..count..)),binwidth = 1,color="black")+
+  scale_x_continuous(name = "Trust in air-pollution policy",breaks = c(1:7),labels = c("low","2","3","4","5","6","high"))+
+  scale_y_continuous(name = "Percentage",limits = c(0,0.4))+
+  guides(fill=FALSE)+
+  ggtitle("") +
+  theme_classic()
+
+ggplot(SVIVA2_01, aes(x=TRUST_waste_INDEX)) + 
+  geom_histogram(aes(y = (..count..)/sum(..count..)),binwidth = 1,color="black")+
+  scale_x_continuous(name = "Trust in recycling policy",breaks = c(1:7),labels = c("low","2","3","4","5","6","high"))+
+  scale_y_continuous(name = "",limits = c(0,0.4))+
+  guides(fill=FALSE)+
+  ggtitle("") +
+  theme_classic()
+```
+
+I now turn to examine my theoretical hypotheses.
+To reiterate, my first two hypotheses regard the role of symbolic elements as peripheral cues that evoke positive emotions, and thereby increase citizens' trust (H1), mainly among those who do not perceive the communication as personally relevant (H2).
+Thereafter, I theorize that symbols can increase trust, indirectly, by decreasing the amount of thinking and thus compensating for logically unpersuasive communications.
+Accordingly, hypothesis 3 focuses on the interaction between symbols and information, and hypothesis 4 focuses on its mediation by lower levels of elaboration.
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+
+x_realsymbol_air = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_air_INDEX)) %>% max()
+x_fakesymbol_air = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(TRUST_air_INDEX)) %>% max()
+x_nosymbol_air = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(TRUST_air_INDEX)) %>% max()
+x_realsymbol_waste = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_waste_INDEX)) %>% max()
+x_fakesymbol_waste = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(TRUST_waste_INDEX)) %>% max()
+x_nosymbol_waste = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(TRUST_waste_INDEX)) %>% max()
+
+t_air_symbol_nosymbol = t.test(TRUST_air_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
+t_air_symbol_fakesymbol = t.test(TRUST_air_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
+t_waste_symbol_nosymbol = t.test(TRUST_waste_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
+t_waste_symbol_fakesymbol = t.test(TRUST_waste_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
+
+d_nosymbol_air = ((x_realsymbol_air-x_nosymbol_air)/(filter(SVIVA2_01,SYMBOL!=1)%>%summarise(sd(TRUST_air_INDEX))%>%max())) %>% round(2)
+d_nosymbol_waste = ((x_realsymbol_waste-x_nosymbol_waste)/(filter(SVIVA2_01,SYMBOL!=1)%>%summarise(sd(TRUST_waste_INDEX))%>%max())) %>% round(2)
+
+t_symbol_fakesymbol = t.test(trust~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=0))
+
+```
+
+## *The effect of symbols on trust in policy*
+
+Beginning with my first hypothesis, I expect that subjects will report higher levels of trust in the policy plans, when they are presented with the real symbols, compared with the two control groups.
+**Figure 5** shows the descriptive comparison of trust between these experimental groups.
+The black points and error bars represent the mean and 95% confidence intervals, and the box-plots show the distribution (position of quartiles and outliers).
+In both policies, subjects in the real symbols condition reported higher levels of trust compared with the no-symbols condition (differences are `r (x_realsymbol_air-x_nosymbol_air)%>%round(2)` [`r t_air_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_air_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_waste-x_nosymbol_waste)%>%round(2)` [`r t_waste_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_waste_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] for the air-pollution and recycling policies, respectively).
+These differences are equivalent to `r d_nosymbol_air` and `r d_nosymbol_waste` standard deviations.
+The fake symbols also increased participants' trust in the policy plans, but to a lesser extent.
+Subjects in the real symbols reported higher trust compared with the fake symbols, but the differences are marginally significant (*p* = `r (t_air_symbol_fakesymbol[["p.value"]]/2)%>%round(2)`-`r (t_waste_symbol_fakesymbol[["p.value"]]/2)%>%round(2)`).
+Below, I also combine the trust in the two policies (i.e.
+2 observations per each subject).
+In these multilevel analyses, the effect of the real symbols compared with the fake symbols is significant at the 90% level.
+
+**Figure 5: The effect of symbolic elements on trust in policy**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.show='hold', fig.width=6,fig.height=4}
+SVIVA2_01_comb = SVIVA2_01_comb %>% 
+  mutate(POLICY_t = Recode(policy,"'TRUST_air_INDEX'='Air-pollution';'TRUST_waste_INDEX'='Recycling'"))
+
+ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust))+ 
+  theme_classic()+
+  geom_boxplot(width=0.25,color = "gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.5)+
+  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
+  facet_grid(~factor(POLICY_t))+
+  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
+  scale_y_continuous(name = "Trust in EPM policy",breaks = seq(1,7,by=0.5))
+
+```
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+
+q_diff = c(
+  ((quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==2])[3]- quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==0])[3])%>%max()),
+
+((quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==2])[3]- quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==0])[3])%>%max()),
+
+((quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==2])[4]- quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==0])[4])%>%max()),
+
+((quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==2])[4]- quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==0])[4])%>%max()))
+
+```
+
+Overall, the results are largely consistent with my hypothesis that familiar symbolic elements can increase trust by evoking positive associations that are transferred to government organizations and policies.
+The graphic elements in the fake symbols condition also increased participants' trust through the peripheral route, but to a lesser extent, presumably due to their unfamiliarity, and their lack of strong positive affect.
+
+**Figure 5** also shows that the distribution of trust in policy in the real symbols group is more concentrated.
+The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
+the lower 25% observations).
+Compared with the no symbols, the first quartile increased by `r (quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==2])[2]- quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==0])[2])%>%max()%>%round(1)` and `r (quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==2])[2]- quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==0])[2])%>%max()%>%round(1)`, with respect to the air-pollution and recycling policies, respectively.
+By comparison, the medians and 3rd quartiles increased only by `r q_diff %>% min() %>% round(1)`-`r q_diff %>% max() %>% round(1)`.
+On the face of it, this comparison suggests that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
+Stated otherwise, symbols may be more effective in reducing distrust, as opposed to increasing trust.
+If this explanation holds, it implies that symbols have a decreasing marginal effect, i.e., they are generally more effective when trust is low in the first place.
+
 <br>
 
-#Discussion
+## *The interaction bewteen symbols and personal relevance*
+
+According to my second hypothesis, I expect that symbols' effect on trust in air-pollution policy will be stronger among the center subjects, insofar as they do not perceive this issue personally relevant.
+Conversely, regarding the recycling policy, the effect of the symbols is expected to be similar for residents of both areas.
+
+Before analyzing the interaction, I explore the differences in the distribution of trust across the two areas.
+In general, participants from Haifa-Bay were more likely to report low levels of trust in the air-pollution policy (*MEAN* = `r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_air_INDEX))%>%max()%>%round(2)` [`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`], *Median* = `r filter(SVIVA2_01,AREA==1)%>%summarise(median(TRUST_air_INDEX))%>%max()%>%round(2)`), compared with participants from the center (*MEAN* = `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_air_INDEX))%>%max()%>%round(2)` [`r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`], *Median* = `r filter(SVIVA2_01,AREA==0)%>%summarise(median(TRUST_air_INDEX))%>%max()%>%round(2)`).
+The distribution among the Haifa-Bay subjects is also more dispersed (*SD* = `r filter(SVIVA2_01,AREA==1)%>%summarise(sd(TRUST_air_INDEX))%>%max()%>%round(2)` vs.
+`r filter(SVIVA2_01,AREA==0)%>%summarise(sd(TRUST_air_INDEX))%>%max()%>%round(2)`).
+The distribution of trust in the recycling policy is fairly similar in both areas, with slightly higher trust among center subjects (*Mean* = `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_waste_INDEX))%>%max()%>%round(2)` vs.
+`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_waste_INDEX))%>%max()%>%round(2)`, *p*<.1).
+These differences may suggest that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, but not towards EPM or environmental policy in general.
+
+In **Table 1**, I examine the interaction between symbols and the two areas using OLS regression analyses.
+With regard to each of the two policy plans, I regress the trust index on the symbols manipulation and the allocation to areas (Models 1.1 and 1.3), and thereafter I add the interaction between them (models 1.2 and 1.4).
+
+**Table 1: Regression analyses**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+
+mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb)
+mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
+mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*SYMBOL_t)
+
+mod_waste_1.1 = lm(TRUST_waste_INDEX~SYMBOL_t,data=SVIVA2_01_comb)
+mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
+mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*SYMBOL_t)
+
+stargazer(mod_air_1.2,mod_air_1.3,
+          mod_waste_1.2,mod_waste_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols"),
+          column.labels = c("(1.1)", "(1.2)","(1.3)","(1.4)"),
+          model.numbers=F,
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+mod_air_1.1.r = lm(TRUST_air_INDEX~SYMBOL_t.r,data=SVIVA2_01_comb)
+mod_air_1.2.r = update(mod_air_1.1.r,. ~ .+AREA_center)
+mod_air_1.3.r = update(mod_air_1.1.r,. ~ .+AREA_center*SYMBOL_t.r)
+
+mod_waste_1.1.r = lm(TRUST_waste_INDEX~SYMBOL_t.r,data=SVIVA2_01_comb)
+mod_waste_1.2.r = update(mod_waste_1.1.r,. ~ .+AREA_center)
+mod_waste_1.3.r = update(mod_waste_1.1.r,. ~ .+AREA_center*SYMBOL_t.r)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+These analyses suggest that the effect of the real symbols on the air-pollution policy was not weaker among the Haifa-bay subjects.
+If anything, the negative coefficient of the interaction term *Area x Real symbols* in Model 1.2 (*Coef* = `r mod_air_1.3[["coefficients"]][["SYMBOL_t1:AREA_center"]]%>%round(2)`, *p*<.1) indicates that the symbols were perhaps more effective on those who reside in the Haifa-bay.
+Furthermore, Model 1.4 also shows that the effect was greater among Haifa-Bay subjects for the recycling policy, which suggests that the differences between the areas is not explained by their varying levels of personal relevance.
+Rather, these differences could be linked to the predispositions of Haifa-Bay subjects to have lower levels of trust in the first place.[^footnote_higher_effect_haifa]
+
+In sum, the experimental results suggest that symbolic elements in communications increase citizens' trust in the policies presented in the communications, and that this effect is not moderated by the perceived personal relevance of the issue.
+In order to further explore the robustness of my null findings with regard to the interaction with personal relevance, I conducted additional analyses (see supplementary appendix).
+First, in addition to the distinction between the areas, I supplemented the above operationalization of perceived personal relevance with subjects' reporting of the perceived personal relevance of these policy plans.
+Second, I added a set of individual-level control variables, and other factors related to interest in environmental policy in general.
+Third, I further explored whether Haifa-bay subjects were more likely to scrutinize the air-pollution policy by testing the interaction between the areas and the information manipulation, and by comparing the levels of elaboration (reaction time and memory-test score) across the two areas, and finally the delta (within-subjects) between trust in strong and weak policy plans.
+All these analyses yielded null findings, which suggest that those who perceive these policies issues as more personally relevant were not more likely to elaborate on them, and were not less likely to be influenced by the symbolic elements.
+
+[^footnote_higher_effect_haifa]: This tentative explanation is supported by the observed decreased marginal reduction in the percentage of subjects who reported very low levels of trust in the policies.
+For example, in the Haifa-Bay, the percentage of those who reported a trust of less than 2 in the air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%, and in the center, it decreased from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
+With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% and in the center it decreased from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust)) %>% max()
+x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust)) %>% max()
+x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust)) %>% max()
+sd_trust = SVIVA2_01_comb%>%summarise(sd(trust))%>%max()
+
+x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA)) %>% max()
+x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA)) %>% max()
+x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA)) %>% max()
+sd_trust_delta = SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()
+
+```
+
+Given the lack of interaction between symbols and personal relevance, and in order to simplify the analyses of the remaining hypotheses, I continue the rest of my analyses while combining the two policies and the two areas together.
+Accordingly, I transformed the dataset into a multilevel structure of policies nested within subjects (N observations = `r SVIVA2_01_comb %>% nrow()`, N subjects = `r SVIVA2_01_comb%>%distinct(IP)%>%nrow()`).[^footnote_combined_analyses]
+
+[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while separating between the two policies.
+
+## *The interaction bewteen symbols and information*
+
+I now turn to test hypothesis 3, which regards the interaction between symbols and the substantive information in the communication.
+Empirically, I expect that the effect of the real symbols will be greater for the weak policy, compared with the strong policy.
+In **Table 2**, I examine this hypothesis via regression analyses.
+To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level (ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`).
+In Model 2.1 I regress the policy trust index on the symbols and information manipulations.
+Thereafter, in Model 2.2, I add the interaction between them.
+In Model 3.3, I also control for the different effects of the information manipulation on the air-pollution and recycling policies.
+
+**Table 2: Regression analyses**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+library(lme4)
+
+mod_2.1 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_2.2 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_2.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+stargazer(mod_2.1,mod_2.2,mod_2.3,
+          type="html",style = "apsr",
+          order = c(1,2,3,5,6,4,7),
+          dep.var.labels=c("Trust in policy (combined)"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Weak policy x Real symbols",
+                             "Weak policy x Fake symbols",
+                             "Recycling policy (0=air-pollution)",
+                             "Weak policy x Recycling policy"),
+          #omit.stat = c("aic","bic"),
+          column.labels = c("(2.1)", "(2.2)","(2.3)"),
+          initial.zero = FALSE,
+          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+mod_2.2.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_2.3.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+mod_2.2.r_2 = lmer(trust~SYMBOL_t*INFORMATION+(1|IP),data=SVIVA2_01_comb)
+mod_2.3.r_2 = lmer(trust~SYMBOL_t*INFORMATION+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+mod_2.2.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+(1|IP),data=SVIVA2_01_comb)
+mod_2.3.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+mod_2.2.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_2.3.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+The main effect of the weak policy in Model 2.1 is negative and significant, (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]).
+The interaction between weak policy and real symbols is positive and significant in Model 2.2 (*Coef* = `r mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]), whereas the interaction with the fake symbols is insignificant.
+The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively).
+When the symbols were added to the strong policy plan, they had a weaker effect, which was significant only compared with the no symbols condition (*Coef* = `r mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1).
+Congruently, the symbols decreased the differences between the strong and weak policies by `r ((mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/
+(mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100) %>% round(0)`%, compared with the no symbols group (from `r mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
+The interaction between symbols and information, in Model 2.2, significantly contributes to the model fit (Chi2 = `r anova(mod_2.2,mod_2.1)%>%tidy()%>%filter(term=="mod_2.2")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
+To facilitate the interpretation of this interaction, **Figure 6** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
+The coefficients of the manipulations and their interaction remains intact when controlling for the different policies, in Model 2.3, which suggests that in both policies the symbols had a greater effect when added to the a weak policy plan.[^footnote_interaction_symbols_policies]
+
+[^footnote_interaction_symbols_policies]: In additional models I also added the interaction between the symbols and the policies, and the triple interaction between symbols, policies and information.
+These interactions are insignificant.
+
+**Figure 6: The effect of symbolic elements on trust under weak vs. strong information**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=6,fig.height=4}
+ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(INFORMATION_n)))+ 
+  theme_classic()+
+  #geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.5,position=position_dodge(0.1))+
+  stat_summary(fun.y = mean, geom = "line", size=0.5, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
+  scale_shape_manual(guide=F,values=c(19,1))+
+  scale_linetype_manual(name="Information",values=c(1,4),labels=c("Weak policy","Strong policy"))+
+  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
+  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
+```
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+
+x_realsymbol_delta=filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
+x_fakesymbol_delta=filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
+x_nosymbol_delta=filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()
+
+t_delta_symbol_nosymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
+t_delta_symbol_fakesymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
+t_delta_nosymbol_fakesymbol = t.test(WITHIN_DELTA~SYMBOL,filter(SVIVA2_01,SYMBOL!=2))
+
+```
+
+The above analyses are based on *between-subject* comparisons for the same policy plan (i.e.
+strong vs.
+weak air-pollution policy, and strong vs.
+weak recycling policy).
+However, I can also utilize the fact that each subject received two policy plans (one strong and one weak) to assess the interaction between symbols and information, by analyzing the effect of symbols on the differences *within-subjects* - between their trust in the two policy plans.
+This analysis is graphically displayed in **Figure 6**.
+The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2] %>% round(2)`], respectively).
+The differences between the two control groups are insignificant.
+
+**Figure 6: The effect of symbolic elements on within-subject delta between strong and weak policies**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=4,fig.height=4}
+ggplot(SVIVA2_01, aes(factor(SYMBOL_n), WITHIN_DELTA))+
+  theme_classic()+
+  #geom_boxplot(width=0.25,color = "gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
+  stat_summary(fun.y = mean, geom = "point", size=2)+
+  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
+  scale_x_discrete(name="Symbolic elements",labels=c("no symbols","fake symbols","real symbols"))+
+  scale_y_continuous(name = "Within subject delta", breaks = seq(0,1,by=0.1))
+
+```
+
+In sum, my between- and within-subject comparisons largely support my third hypothesis, and suggest that symbolic elements increase citizens' trust, in part, by attenuating the negative effect of weak or logically unpersuasive information in communications.
+
+## *The mediating role of elaboration*
+
+Finally, I examine my fourth hypothesis, that the real symbols increase trust in weak policy plans by decreasing the amount of thinking on the communication.
+Empirically, based on this hypothesis, I first expect to find a negative effect of the real symbols on my two indicators of elaboration (reaction time and memory score).
+Thereafter, this effect is expected to mediate the effect of symbols of trust under the weak policy, but not under the strong policy (i.e.
+a second stage moderated mediation model, also see Figure 1).
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+x_realsymbol_RT=filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(ELABORATION_time))%>%max()
+x_fakesymbol_RT=filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(ELABORATION_time))%>%max()
+x_nosymbol_RT=filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(ELABORATION_time))%>%max()
+
+t_RT_symbol_nosymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=1))
+t_RT_symbol_fakesymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=0))
+t_RT_nosymbol_fakesymbol = t.test(ELABORATION_time~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=2))
+
+x_realsymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(ELABORATION_time_log))%>%max()
+x_fakesymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(ELABORATION_time_log))%>%max()
+x_nosymbol_RT_log=filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(ELABORATION_time_log))%>%max()
+
+cor_memory_nosymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=1)$SYMBOL),
+                               filter(SVIVA2_01_comb,SYMBOL!=1)$MEMORY_score, 
+                               method="spearman")$estimate %>% mean() %>% round(2)
+
+cor_memory_fakesymbol = cor.test(as.numeric(filter(SVIVA2_01_comb,SYMBOL!=0)$SYMBOL),
+                               filter(SVIVA2_01_comb,SYMBOL!=0)$MEMORY_score, 
+                               method="spearman")$estimate %>% mean() %>% round(2)
+```
+
+The effects of the real symbols on the elaboration measures are graphically displayed in **Figure 7**.
+The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.
+Subjects in the real symbols group spent `r (x_realsymbol_RT-x_nosymbol_RT)%>%abs()%>%round(1)`-`r (x_realsymbol_RT-x_fakesymbol_RT)%>%abs()%>%round(1)` second less on the pages of the policy plans in the online survey, compared with the two control groups.[^footnote_RT_symbols] With regard to the memory test, subjects in the real symbols group were less likely to select correct items which were included in the policy plans.
+`r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% of them received the minimum score of 0, compared with `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the no symbols and fake symbols control groups.
+The percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the control groups to only `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.[^footnote_memory_symbols] In sum, with respect to both measures, the mean of the symbols condition was significantly lower compared with both control groups, and the differences between the two control groups are insignificant.
+In additional analyses, not shown here, I also account for the two policies, with no change to the results.
+
+[^footnote_RT_symbols]: The differences in seconds as extracted from the differences in logs are: `r (x_realsymbol_RT_log-x_nosymbol_RT_log)%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`.
+Still, these differences are significant.
+
+[^footnote_memory_symbols]: Because each participant was asked with regard to the last policy plan which was presented, the memory score is measured with regard to half of the observations (*n*=`r filter(SVIVA2_01_comb,MEMORY_score>=0)%>%nrow()`).
+The measure of memory test score is ordinal with three categories, and therefore I also tested it's correlation with the symbols manipulation via Spearman test.
+Spearman rho = `r cor_memory_nosymbol` and `r cor_memory_fakesymbol`, compared with the no symbols and fake symbols control groups.
+
+**Figure 7: The effect of symbolic elements on elaboration**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold',, fig.width=4,fig.height=4}
+ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), ELABORATION_time_log))+
+  theme_classic()+
+  #geom_boxplot(width=0.25,color = "gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.5)+
+  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
+  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
+  scale_y_continuous(name = "Reaction Time (log)")
+
+ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), MEMORY_score))+
+  theme_classic()+
+  #geom_boxplot(width=0.25,color = "gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.5)+
+  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
+  scale_x_discrete(name="",labels=c("no symbols","fake symbols","real symbols"))+
+  scale_y_continuous(name = "Memory score")
+```
+
+The less subjects elaborate on the weak policy plans, the more they are likely to report higher levels of trust in them, which will be closer to the levels of trust in the strong policy.
+To test mediation mechanism, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al.
+[@imai_2010; @imai_2011].
+This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols).
+Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect.
+This method is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling.
+It is advantaged in terms of its accuracy as well as its ability to identify causality.
+The results of the causal analysis tables are summarized in **Table 3**.
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+library(mediation)
+set.seed(2018)
+
+#RT
+med.fit_RT_nosymbol = 
+  lm(ELABORATION_time_log~SYMBOL*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=1))
+
+med.out_RT_nosymbol = 
+  lm(trust~SYMBOL*INFORMATION+ELABORATION_time_log*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=1))
+
+med.fit_RT_fakesymbol = 
+  lm(ELABORATION_time_log~SYMBOL*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=0))
+
+med.out_RT_fakesymbol = 
+  lm(trust~SYMBOL*INFORMATION+ELABORATION_time_log*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=0))
+
+med_RT__nosymbol_INFORMTION_0 = mediate(med.fit_RT_nosymbol,
+                                med.out_RT_nosymbol,
+                                treat = "SYMBOL",
+                                mediator = "ELABORATION_time_log", 
+                                covariates = list(INFORMATION = 0), sims = 100)
+
+med_RT__fakesymbol_INFORMTION_0 = mediate(med.fit_RT_fakesymbol,
+                                  med.out_RT_fakesymbol,
+                                  treat = "SYMBOL",
+                                  mediator = "ELABORATION_time_log", 
+                                  covariates = list(INFORMATION = 0), sims = 100)
+
+med_RT__nosymbol_INFORMTION_1 = mediate(med.fit_RT_nosymbol,
+                                med.out_RT_nosymbol,
+                                treat = "SYMBOL",
+                                mediator = "ELABORATION_time_log", 
+                                covariates = list(INFORMATION = 1), sims = 100)
+
+med_RT__fakesymbol_INFORMTION_1 = mediate(med.fit_RT_fakesymbol,
+                                  med.out_RT_fakesymbol,
+                                  treat = "SYMBOL",
+                                  mediator = "ELABORATION_time_log", 
+                                  covariates = list(INFORMATION = 1), sims = 100)
+
+#memory
+med.fit_memory_nosymbol = 
+  lm(MEMORY_score~SYMBOL*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=1))
+
+med.out_memory_nosymbol = 
+  lm(trust~SYMBOL*INFORMATION+MEMORY_score*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=1))
+
+med.fit_memory_fakesymbol = 
+  lm(MEMORY_score~SYMBOL*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=0))
+
+med.out_memory_fakesymbol = 
+  lm(trust~SYMBOL*INFORMATION+MEMORY_score*INFORMATION,
+     data=filter(SVIVA2_01_comb,SYMBOL!=0))
+
+med_memory__nosymbol_INFORMTION_0 = mediate(med.fit_memory_nosymbol,
+                                med.out_memory_nosymbol,
+                                treat = "SYMBOL",
+                                mediator = "MEMORY_score", 
+                                covariates = list(INFORMATION = 0), sims = 100)
+
+med_memory__fakesymbol_INFORMTION_0 = mediate(med.fit_memory_fakesymbol,
+                                  med.out_memory_fakesymbol,
+                                  treat = "SYMBOL",
+                                  mediator = "MEMORY_score", 
+                                  covariates = list(INFORMATION = 0), sims = 100)
+
+med_memory__nosymbol_INFORMTION_1 = mediate(med.fit_memory_nosymbol,
+                                med.out_memory_nosymbol,
+                                treat = "SYMBOL",
+                                mediator = "MEMORY_score", 
+                                covariates = list(INFORMATION = 1), sims = 100)
+
+med_memory__fakesymbol_INFORMTION_1 = mediate(med.fit_memory_fakesymbol,
+                                  med.out_memory_fakesymbol,
+                                  treat = "SYMBOL",
+                                  mediator = "MEMORY_score", 
+                                  covariates = list(INFORMATION = 1), sims = 100)
+
+extract_mediation_summary <- function (x) {
+
+  clp <- 100 * x$conf.level
+  isLinear.y <- ((class(x$model.y)[1] %in% c("lm", "rq")) || 
+                   (inherits(x$model.y, "glm") && x$model.y$family$family == 
+                      "gaussian" && x$model.y$family$link == "identity") || 
+                   (inherits(x$model.y, "survreg") && x$model.y$dist == 
+                      "gaussian"))
+
+  printone <- !x$INT && isLinear.y
+
+  if (printone) {
+
+    smat <- c(x$d1, x$d1.ci, x$d1.p)
+    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
+    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
+    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))
+
+    rownames(smat) <- c("ACME", "ADE", "Total Effect", "Prop. Mediated")
+
+  } else {
+    smat <- c(x$d0, x$d0.ci, x$d0.p)
+    smat <- rbind(smat, c(x$d1, x$d1.ci, x$d1.p))
+    smat <- rbind(smat, c(x$z0, x$z0.ci, x$z0.p))
+    smat <- rbind(smat, c(x$z1, x$z1.ci, x$z1.p))
+    smat <- rbind(smat, c(x$tau.coef, x$tau.ci, x$tau.p))
+    smat <- rbind(smat, c(x$n0, x$n0.ci, x$n0.p))
+    smat <- rbind(smat, c(x$n1, x$n1.ci, x$n1.p))
+    smat <- rbind(smat, c(x$d.avg, x$d.avg.ci, x$d.avg.p))
+    smat <- rbind(smat, c(x$z.avg, x$z.avg.ci, x$z.avg.p))
+    smat <- rbind(smat, c(x$n.avg, x$n.avg.ci, x$n.avg.p))
+
+    rownames(smat) <- c("ACME (control)", "ACME (treated)", 
+                        "ADE (control)", "ADE (treated)", "Total Effect", 
+                        "Prop. Mediated (control)", "Prop. Mediated (treated)", 
+                        "ACME (average)", "ADE (average)", "Prop. Mediated (average)")
+
+  }
+
+  colnames(smat) <- c("Estimate", paste(clp, "% CI Lower", sep = ""), 
+                      paste(clp, "% CI Upper", sep = ""), "p-value")
+  smat
+
+}
+
+```
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+#RT
+table_med_RT__nosymbol_INFORMTION_0 = 
+summary(med_RT__nosymbol_INFORMTION_0) %>% 
+extract_mediation_summary()
+
+table_med_RT__fakesymbol_INFORMTION_0 = 
+summary(med_RT__fakesymbol_INFORMTION_0) %>% 
+extract_mediation_summary()
+
+table_med_RT__nosymbol_INFORMTION_1 = 
+summary(med_RT__nosymbol_INFORMTION_1) %>% 
+extract_mediation_summary()
+
+table_med_RT__fakesymbol_INFORMTION_1 = 
+summary(med_RT__fakesymbol_INFORMTION_1) %>% 
+extract_mediation_summary()
+
+#memory
+table_med_memory__nosymbol_INFORMTION_0 = 
+summary(med_memory__nosymbol_INFORMTION_0) %>% 
+extract_mediation_summary()
+
+table_med_memory__fakesymbol_INFORMTION_0 = 
+summary(med_memory__fakesymbol_INFORMTION_0) %>% 
+extract_mediation_summary()
+
+table_med_memory__nosymbol_INFORMTION_1 = 
+summary(med_memory__nosymbol_INFORMTION_1) %>% 
+extract_mediation_summary()
+
+table_med_memory__fakesymbol_INFORMTION_1 = 
+summary(med_memory__fakesymbol_INFORMTION_1) %>% 
+extract_mediation_summary()
+```
+
+**Table 3: Causal mediation analysis**
+
+*Mediator: Reaction time*
+3.1: Weak policy
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+table_med_RT_INFORMTION_0 = 
+  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_0,
+                   table_med_RT__fakesymbol_INFORMTION_0)
+library(kableExtra)
+
+kable(table_med_RT_INFORMTION_0, "html",digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
+```
+
+3.2: Strong policy
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+table_med_RT_INFORMTION_1 = 
+  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_1,
+                   table_med_RT__fakesymbol_INFORMTION_1)
+
+kable(table_med_RT_INFORMTION_1, "html",digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
+
+```
+
+*Mediator: Memory score*
+3.3: Weak policy
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+table_med_memory_INFORMTION_0 = 
+  cbind.data.frame(table_med_memory__nosymbol_INFORMTION_0,
+                   table_med_memory__fakesymbol_INFORMTION_0)
+
+kable(table_med_memory_INFORMTION_0, "html",digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
+```
+
+3.4: Strong policy
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+table_med_memory_INFORMTION_1 = 
+  cbind.data.frame(table_med_memory__nosymbol_INFORMTION_1,
+                   table_med_memory__fakesymbol_INFORMTION_1)
+
+kable(table_med_memory_INFORMTION_1, "html",digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
+```
+
+*Notes*: "ACME": Averaged causal mediated effect; "ADE": Averaged direct effect. Mediate function uses bootstrap to estimate the confidence intervals. In all these analyses I used `set.seed=2018`.
+
+The results suggest that the decreased reaction time significantly mediates the effect of the real symbols on trust in the weak policies.
+The estimated proportion of the mediation is `r (table_med_RT__nosymbol_INFORMTION_0["Prop.
+Mediated","Estimate"]*100) %>% round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_INFORMTION_0["Prop.
+Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
+The decreased memory score also mediates the effect (*p*<.1), but only compared with the no symbols group.[^footnote_mediation_memory] The effect of the real symbols on trust in the strong policies is not significantly mediated by the measures of elaboration.
+Altogether, these analyses are consistent with my H4, and suggest that subjects who saw the policy plans with the familiar symbols were less likely to scrutinize their content, which in turn increased their trust in the weak policies.
+
+[^footnote_mediation_memory]: The differences between the analyses of the two measures can be also explained by the fact that memory score is calculated with regard to half of the observations.
+
+<br>
+
+#Discussion and conclusion
+
+A growing body of public administration research seeks to assess whether and how government organizations can increse citizens' trust through direct communications with citizens.
+This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect on citizens' trust.
+Using a rigorous experimental design, embedded in a realistic setting of communication of policy plans of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of the communications and with their perceived personal relevance.
+The experimental results demonstrate that using familiar symbolic elements in communications about policy plans increase citizens' trust in these policies, via two mechanisms: First, they evoke positive fellings that are transferred to the policy plan.
+Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thus - they cause them to disregard its weaknesses, if exist.
+the latter mechanism entails an interaction between symbols and weak information.
+These theoretical mechanisms can be understood in light of the social psychology elaboration likelihood model.
+In addition, I theorized that the effect of symbols is attenuated the more the communication is personally relevant for citizens' lives, but the reults do not support this expectation.
+Rather, I found that citizens who perceived the policy issue as highly relevant for their lives (i.e.
+air-pollution in their area of residence), were similarly distracted by the graphic symbols, and persuaded to trust governmnet's actions, even when they were undoubtedly illogical.
+These findings are based on a large sample of more than `r (SVIVA2_01%>%nrow() %>% round(-2))-100` participants, and are robust for various model specifications.
+
+What are the implications of these findings for public administation resarch?
+First, they highlight the important role of strategically designed symbolic elements in communications in shaping citizens' attitudes about government.
+Citizens' responses to symbolic elements and branding thus far received relatively little attention in Public administration literature, compared with the the abounded research on responses to information.
+Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
+Furthermore, this study demostrates that symbols decrease the "rational", systematic processing of substantive information.
+This may suggest that government organizations may bypass the cognitive biases that often undermine the effectiveness of positive information, by employing symbolic communication.[^footnote_biases_ELM] This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance.
+On the other hand, it challenges the democratic ideal that citizens' form their attitudes about governments on the basis of rational thinking [###Dahl...].
+Moreover, it suggests that public organizations may use symbols in communications to compensate for their poor performance and inefficient policy plans.
+In turn, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which attenuates politicians' incentives to monitor and oversight them [##Busuioc_2016; Bertelli_2018##].
+Overall...
+something about democratic accountability...
+
+[^footnote_biases_ELM]: This posibility is supported, theoretically, by ELM.
+According to ELM, biased processing occures in the central route, whereby people give unproportional weight for strong or weak arguments.
+Accordingly, decresaing the ammount of thinking may also decrease biased processing [@petty_1986].
+Future research might put this expectation to test.
+
+Methodologically, these findings highlight that it is important to test the effectiveness of public communications, and not only the information.
+
+Almost any government communication involves design elements, and many of them include familiar symbols and brand elements.
+Conversely, some of the current studies that explored the effect of information, did so by comparing participants' responses to pieces of information (mainly favorable vs.
+unfavorable performance) which were presented in surveys in the form of plain text and data tables without design elements which would be normally included in  such communications [@baekgaard_2016; @hvidman_2016; ].
+This questions our ability to generalize from these experiments to citizens' responses to public communications in the real world.
+
+Finally, PA can also implement ELM...
+
+How can we explain the null findings about personal relevance %>%
+
+limitations...
+
+<br>
+
+##Appendix A: Information manipulation
+
+**Air-pollution policy** (Reducing the air-pollution in the Haifa-Bay)
+
+EPM is working to reduce the air-pollution in the Haifa-Bay through:
+
+*Strong*
+
+* **Increasing the supervision of the factories in Haifa-Bay**.
+In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways.
+The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the amount of fines for pollutants.
+
+* **Reduction of smoke emissions from vehicles in Haifa Bay**.
+The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area.
+The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and promotes the operation of a "clean-air area" that restricts the entry of polluting vehicles.
+
+*Weak*
+
+* **Decreasing the supervision of the factories in Haifa-Bay**.
+The Ministry is preparing for a change in the method of supervision of the factories.
+The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the amount of fines.
+The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.
+
+* **Raising citizens' awareness of the efforts to improve air quality**.
+In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful.
+The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents.
+To this end, the ministry has increased its investment in public relations and publicity in this subject.
+
+<br>
+
+**Recycling policy** (Reducing waste and increasing recycling)
+
+EPM is working to reduce the amount of waste and increase its recycling through:
+
+*Strong*
+
+* **Packaging recycling - Increased supervision of manufacturers**.
+In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, which imposes on manufacturers and importers the responsibility for recycling the packaging.
+The Ministry will work to increase enforcement by virtue of this act, and will enforce it with regard to additional manufacturers and importers.
+
+* **Reducing the usage of disposable bags**.
+In order to reduce the use of disposable plastic bags, the Ministry enforces the Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the chains.
+The Ministry works to implement the act, and encourages the transition to reusable grocery bags.
+
+*Weak*
+
+* **Packaging recycling - Decreased supervision of manufacturers**.
+The Ministry is preparing to a change in the method of supervision of the manufacturers, who are responsible for the recycling of product packaging by virtue of the act The ministry will reduce the number of inspections, rely on manufacturers' self-reports regarding their compliance with the requirements of the act, and reduce the amount of fines.
+The change is coordinated with members of the industry, which are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
+
+* **Reducing the usage of disposable bags**.
+In recent years, the Ministry has taken steps to encourage the reduction of waste, which have been partially successful.
+The Ministry works to raise awareness of the actions taken and to highlight their success in order to improve its image among the public.
+To this end, the ministry has increased its investment in public relations and publicity in this subject.
+
+<br>
+
+##Appendix B: Symbols manipulation
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/symbols_manipulation.png)
+
+<font size="0.5">
+
+*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*
+
+</font>
+
+<br>
 

### 2018-05-18 SVIVA_exp2_dm_03.R

@@ -6,9 +6,7 @@
 
 library(tidyverse)
 #library(psych)
-library(stargazer)
 library(car)
-library(sjPlot)
 library(stringr)
 library(lubridate)
 
@@ -126,7 +124,7 @@ SVIVA2_00 = SVIVA2_00 %>%
   mutate(AREA_reside_haifa = Recode(t2,"'HAIFA'=1;'SHFELA'=0"),
          AREA_work_haifa = if_else(AREA_work==2,1,0))%>%
   mutate(AREA = if_else(AREA_reside_haifa+AREA_work_haifa>0,1,0))%>%
-  mutate(AREA_names = Recode(AREA,"0='Shfela';1='Haifa'"))%>%
+  mutate(AREA_names = Recode(AREA,"0='Center';1='Haifa-Bay'"))%>%
   #ouctome vars####
 #trust in Haifa Bay policy
 mutate(TRUST_air_q1 =  SVIVA2_raw$Q8.5+
@@ -210,12 +208,6 @@ mutate(TRUST_air_q1 =  SVIVA2_raw$Q8.5+
                               TRUST_air_q4+
                               TRUST_air_q5+
                               TRUST_air_q6)/6)%>%
-  mutate(TRUST_air_INDEX_1 = (TRUST_air_q1+
-                                  TRUST_air_q2+
-                                  TRUST_air_q3+
-                                  TRUST_air_q4+
-                                  TRUST_air_q5)/5)%>%
-  mutate(TRUST_air_INDEX=TRUST_air_INDEX_1) %>% 
   mutate(TRUST_air_timer = SVIVA2_raw$Q8.11_3+
                            SVIVA2_raw$Q9.11_3+
                            SVIVA2_raw$Q12.11_3+
@@ -310,13 +302,7 @@ mutate(TRUST_air_q1 =  SVIVA2_raw$Q8.5+
                                 TRUST_waste_q4+
                                 TRUST_waste_q5+
                                 TRUST_waste_q6)/6)%>%
-  mutate(TRUST_waste_INDEX_1 = (TRUST_waste_q1+
-                                TRUST_waste_q2+
-                                TRUST_waste_q3+
-                                TRUST_waste_q4+
-                                TRUST_waste_q5)/6)%>%
-  mutate(TRUST_waste_INDEX=TRUST_waste_INDEX_1) %>% 
-  
+
[…]

### 2018-05-19 paper.Rmd
Add files via upload

@@
 
-A growing body of public administration research seeks to assess whether and how government organizations can increse citizens' trust through direct communications with citizens.
+A growing body of Public-Administration research seeks to assess whether and how government organizations can increase citizens' trust through direct communications with citizens.
 This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect on citizens' trust.
-Using a rigorous experimental design, embedded in a realistic setting of communication of policy plans of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of the communications and with their perceived personal relevance.
-The experimental results demonstrate that using familiar symbolic elements in communications about policy plans increase citizens' trust in these policies, via two mechanisms: First, they evoke positive fellings that are transferred to the policy plan.
-Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thus - they cause them to disregard its weaknesses, if exist.
-the latter mechanism entails an interaction between symbols and weak information.
-These theoretical mechanisms can be understood in light of the social psychology elaboration likelihood model.
-In addition, I theorized that the effect of symbols is attenuated the more the communication is personally relevant for citizens' lives, but the reults do not support this expectation.
+Using a rigorous experimental design, embedded in a realistic setting of the Israeli Environmental Protection Ministry's communication of policy plans, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of the communications and with their perceived personal relevance.
+To the best of my knowledge, this is the first study to test these interactions in the context of government communications.
+
+The experimental results demonstrate that using familiar symbolic elements in communications about policy plans increase citizens' trust in these policies, via two supplementary mechanisms: First, they evoke general positive feelings that are transferred to the specific policy plan.
+Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses.
+The second mechanism entails an interaction between symbols and weak information.
+These two mechanisms can be understood in light of the social psychology elaboration likelihood model.
+I theorized, based on ELM, that the effect of symbols is attenuated the more the communication is personally relevant for citizens' lives, but this expectation is not supported by the results.
 Rather, I found that citizens who perceived the policy issue as highly relevant for their lives (i.e.
-air-pollution in their area of residence), were similarly distracted by the graphic symbols, and persuaded to trust governmnet's actions, even when they were undoubtedly illogical.
+air-pollution in their area of residence), were similarly distracted by the symbols (and other peripheral cues), and persuaded to trust government's actions, even when they were undoubtedly illogical.
 These findings are based on a large sample of more than `r (SVIVA2_01%>%nrow() %>% round(-2))-100` participants, and are robust for various model specifications.
 
-What are the implications of these findings for public administation resarch?
-First, they highlight the important role of strategically designed symbolic elements in communications in shaping citizens' attitudes about government.
-Citizens' responses to symbolic elements and branding thus far received relatively little attention in Public administration literature, compared with the the abounded research on responses to information.
+How can we explain the null findings about personal relevance?  
+- very low motivation, even among Haifa-Bay subjects. Not new, existing problem. congruent with IEC study.
+
+Limitation of study:
+- one case...
+- personal relevance based on observational.
+
+What are the implications of these findings for public administration research?
+First, they highlight the important role of symbols and brands in shaping citizens' attitudes about government.
+Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the the abounded research on responses to information.
 Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-Furthermore, this study demostrates that symbols decrease the "rational", systematic processing of substantive information.
-This may suggest that government organizations may bypass the cognitive biases that often undermine the effectiveness of positive information, by employing symbolic communication.[^footnote_biases_ELM] This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance.
-On the other hand, it challenges the democratic ideal that citizens' form their attitudes about governments on the basis of rational thinking [###Dahl...].
-Moreover, it suggests that public organizations may use symbols in communications to compensate for their poor performance and inefficient policy plans.
-In turn, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which attenuates politicians' incentives to monitor and oversight them [##Busuioc_2016; Bertelli_2018##].
-Overall...
-something about democratic accountability...
-
-[^footnote_biases_ELM]: This posibility is supported, theoretically, by ELM.
-According to ELM, biased processing occures in the central route, whereby people give unproportional weight for strong or weak arguments.
-Accordingly, decresaing the ammount of thinking may also decrease biased processing [@petty_1986].
+Furthermore, this study shows that symbols decrease the "rational", systematic processing of substantive information.
+This may suggest that government organizations bypass or at least attenuate citizens' negative biases that undermine the effectiveness of positive information, by employing symbolic communication.[^footnote_biases_ELM] This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance.
+On the other hand, even if we assume that public organizations provide excellent outcomes, the emotive effect of government symbols on public opinion is still problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
+Moreover, it becomes especially problematic when symbols are used by poorly performing organizations,  or organizations that lack professional expertiese.
+It those cases, symbolic elements can mitigate justified public criticism of government failures.
+Organizations can use them deliberately to distort public opinion via propaganda, or - more likely - without being aware of the tention between the symbols and their substantive message.
+Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
+Hence, government communications with citizens can be a tool for enhancing democratic responsiveness and accountability, yet they can also use it as a means to undermine them.
+
+[^footnote_biases_ELM]: This possibility is supported, theoretically, by ELM.
+According to ELM, biased processing occurs in the central route, whereby people give proportional weight for strong or weak arguments.
+Accordingly, decreasing the amount of thinking may also decrease biased processing [@petty_1986].
 Future research might put this expectation to test.
 
-Methodologically, these findings highlight that it is important to test the effectiveness of public communications, and not only the information.
-
-Almost any government communication involves design elements, and many of them include familiar symbols and brand elements.
-Conversely, some of the current studies that explored the effect of information, did so by comparing participants' responses to pieces of information (mainly favorable vs.
-unfavorable performance) which were presented in surveys in the form of plain text and data tables without design elements which would be normally included in  such communications [@baekgaard_2016; @hvidman_2016; ].
-This questions our ability to generalize from these experiments to citizens' responses to public communications in the real world.
-
-Finally, PA can also implement ELM...
-
-How can we explain the null findings about personal relevance %>%
-
-limitations...
+This study also contributes to existing behavioral Public Administration resarch by intoroducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications.
+ELM has various postulations and implications, but most importantly, it stresses that people respond differently to different communications, depending on people's motivation and ability to think about the subject, and on the quality of arguments and the peripheral cues in the communication.
+In this study, I applyed ELM to distinguish bewteen the peripheral processing of symbolic elements versus the central processing of substantive information, and to exlore their moderation by citizens' motivation to elaborate on the message.
+Future studies may apply ELM and further explore the effects of other peripheral cues in government communications, and of other relevant motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
+
+In addition, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
+The participants of these studies, including this particular one, have relatively high motivation to elaborate on the information that scholars presented them, because they may assume that they will be asked about it afterwards.
+In case they receive payment or other compensation for their participation, this further increases their motivation.
+By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they probably also have lower ability to do so, given the high competition on their time and attention.
+Accordingly, their responses to performance information will less affected by asymetrical processing of information, because most of them are not likely to process this information in the first place.
+Instead, most of them will rely on simple cues and heuristic shortcuts.
+One can postulate that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2016; @olsen_2017].
+Future studies may empirically explore these interactions.
+Regardless, scholars should also take to account this methodological issue when designing survey experiments, and attempt to simulate real world conditions, as much as possible.
+For instance, they can add filler sections in the survey before the real manipulation to attenuate participants' motivation and ability to elaborate.
+In addition, because the graphic design of communications also affects motivation and ability to elborate, as shown here, scholars should simulate the design of real communications.
+
+Closing...
 

### 2018-05-21 paper.Rmd
Add files via upload

@@
 
-Preliminary draft. Last edited at `r Sys.Date()`
+<br>
+
+To be presented at the 2018 Transatlantic Dialogue (TAD 14) at Workshop 1: *Behavioral Public Administration and Psychological perspectives*.
+
+Preliminary draft (last edited at `r Sys.Date()`)[^footnote_scripts] - do not cite without author's permission.
+
+[^footnote_scripts]: Original R scripts available at:  https://github.com/saaralonbarkat/symbols_and_information
 
@@
 These filters are not significantly associated with the areas or the experimental conditions.
-Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r filter(SVIVA2_01,AREA_reside_haifa==1)%>%nrow()` reside in the Haifa-bay cities, and `r filter(SVIVA2_01,AREA_reside_haifa==0)%>%nrow()` reside in the center cities.
+Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
 
@@
 **Figure 3: Experimental design for policy plan communications**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow.png)
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow_long.png)
 
@@
 A growing body of Public-Administration research seeks to assess whether and how government organizations can increase citizens' trust through direct communications with citizens.
-This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect on citizens' trust.
-Using a rigorous experimental design, embedded in a realistic setting of the Israeli Environmental Protection Ministry's communication of policy plans, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of the communications and with their perceived personal relevance.
-To the best of my knowledge, this is the first study to test these interactions in the context of government communications.
-
-The experimental results demonstrate that using familiar symbolic elements in communications about policy plans increase citizens' trust in these policies, via two supplementary mechanisms: First, they evoke general positive feelings that are transferred to the specific policy plan.
+This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect.
+Using a rigorous experimental design, embedded in a realistic setting focused on the case of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications and with their perceived personal relevance.
+To the best of my knowledge, this is the first study to explore these interactions in the context of government communications.
+
+I found that participants' exposure to the familiar symbols of EPM increased their trust in its policy plans, and that the effect was greater when they were presented with a weak policy plan.
+The latter interaction is partly explained by the negative effect of the symbols on the elaboration of the policy plans.
+These findings are based on a large sample of more than `r (SVIVA2_01%>%nrow() %>% round(-2))-100` participants, and are robust for various model specifications.
+These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, they evoke general positive feelings that are transferred to the specific organizations and policies.
 Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses.
-The second mechanism entails an interaction between symbols and weak information.
-These two mechanisms can be understood in light of the social psychology elaboration likelihood model.
-I theorized, based on ELM, that the effect of symbols is attenuated the more the communication is personally relevant for citizens' lives, but this expectation is not supported by the results.
-Rather, I found that citizens who perceived the policy issue as highly relevant for their lives (i.e.
-air-pollution in their area of residence), were similarly distracted by the symbols (and other peripheral cues), and persuaded to trust government's actions, even when they were undoubtedly illogical.
-These findings are based on a large sample of more than `r (SVIVA2_01%>%nrow() %>% round(-2))-100` participants, and are robust for various model specifications.
-
-How can we explain the null findings about personal relevance?  
-- very low motivation, even among Haifa-Bay subjects. Not new, existing problem. congruent with IEC study.
-
-Limitation of study:
-- one case...
-- personal relevance based on observational.
-
-What are the implications of these findings for public administration research?
-First, they highlight the important role of symbols and brands in shaping citizens' attitudes about government.
-Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the the abounded research on responses to information.
+These two supplementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986].
+
+I further postulated, based on ELM, that the effect of symbols is attenuated the more the communication is personally relevant for citizens' lives.
+However, this latter expectation was not supported by the results.
+Residents of the polluted Haifa-Bay, who perceive EPM policy plan for reducing air-pollution in that area as highly relevant for their lives, were affected by the symbols not less than those who reside elsewhere.
+If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
+How can we reconcile these unexpected findings with the proposed theory?
+Given that the moderating role of personal relevance on peripheral cues was substantiated by numerous studies in social psychology, I would not argue that we should abandon this postulation based on this one study.
+One plausible explanation is that although Haifa-bay residents perceived the air-pollution policy as more relevant, their motivation to elaborate was not high enough to cause them to avoid peripheral cues.
+Certainly, the air-pollution in their area concerns them a great deal, as they point out themselves.
+However this issue represents a *continuous* concern that they may have got used to over the time, as opposed a new issue that emerged recently.
+If this explanation holds, this entails that citizens may resist the emotional effect of symbols only in rare circumbstances, which are charecterized by very high levels of personal relevance.
+These latter findings are also consistent with the findings of @alonbarkat_2017.
+In that study, the scholars assessed citizens' trust in the government electricity company, and its shaping by its familiar symbol, given citizens' recent personal experience of prolonged blackouts.
+Whilst their study was not purposly designed to test the interaction between symbols and personal relevance, one can assume that those who personally experienced blackouts perceived electricity service as more personally relevant.
+Still, they found that citizens who experienced blackouts were influenced by the symbol, as much as those who did not.
+
+Certainly, we must be cautious when drawing general conclusions from our findings, for several particular reasons.
+First, this study focuses, empirically, on one public organization, which invested greatly in symbolic communications, most prominently, the use of high-profile celebrity comedians in its public campaigns.
+Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas.
+Moreover, in the symbols treatment group, I used a bundle of symbols, without dissentangling their distinct effects.
+Future studies may compare the effectiveness of different types of symbolic elements.
+Finally, this study focuses on communication about policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
+Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction bewteen symbols and information on good/bad outcomes.
+
+Keeping these limitations in mind, this study has several important implications for public administration research.
+Most importantly, my findings highlight the significat role of branding and symbolic communication in shaping citizens' attitudes about government.
+Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abounded research on their responses to information.
 Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-Furthermore, this study shows that symbols decrease the "rational", systematic processing of substantive information.
-This may suggest that government organizations bypass or at least attenuate citizens' negative biases that undermine the effectiveness of positive information, by employing symbolic communication.[^footnote_biases_ELM] This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance.
-On the other hand, even if we assume that public organizations provide excellent outcomes, the emotive effect of government symbols on public opinion is still problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
+Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information.
+This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information.[^footnote_biases_ELM].
+On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
 Moreover, it becomes especially problematic when symbols are used by poorly performing organizations,  or organizations that lack professional expertiese.
@@
 Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
-Hence, government communications with citizens can be a tool for enhancing democratic responsiveness and accountability, yet they can also use it as a means to undermine them.
+Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, organizations can also use it as a means to undermine them.
 
@@
 
-In addition, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
+Finally, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
 The participants of these studies, including this particular one, have relatively high motivation to elaborate on the information that scholars presented them, because they may assume that they will be asked about it afterwards.
@@
 Instead, most of them will rely on simple cues and heuristic shortcuts.
-One can postulate that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2016; @olsen_2017].
+I would expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2016; @olsen_2017].
 Future studies may empirically explore these interactions.
@@
 
-Closing...
-
 <br>

### 2018-05-21 paper.Rmd
Add files via upload

@@
 ---
-title: 'The effects of symbols and information in government communication on citizens  trust in policy: Evidence from a survey experiment'
+title: 'The effects of symbols and information in government communications on citizens  trust: Evidence from a survey experiment'
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
 
-To be presented at the 2018 Transatlantic Dialogue (TAD 14) at Workshop 1: *Behavioral Public Administration and Psychological perspectives*.
+Paper presented at the 2018 Transatlantic Dialogue (TAD 14) at Workshop 1: *Behavioral Public Administration and Psychological perspectives*. June 2018, Bucharest, Romania.
 
@@
 Still, we lack theoretical understanding of the different mechanisms underlying citizens' responses to information and symbolic elements, and accordingly - the interaction between them.
-Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements have a greater effect on citizens' trust the less citizens perceive the issue as personally relevant.
-Also, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in logically-unpersuasive policy plans.
-I put these hypotheses to test through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policies for reducing the air pollution in a specific area (the Haifa-Bay) and reducing domestic waste.
-The policies are presented to subjects under different conditions of substantive information (logically persuasive vs.
-unpersuasive policies) and symbolic elements (logo, color, and celebrities endorsers).
-I operationalize personal relevance by comparing between citizens from the polluted Haifa-Bay area and others.
-The results do not support the hypothesis that personal relevance attenuates the effect of symbols.
-Rather, they suggest that symbolic elements increase citizens' trust in ill-perceived policies, by distracting them from scrutinizing their content.*
+Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in logically-unpersuasive policy plans.
+I also hypothesize that symbolic elements have a greater effect on citizens' trust the less citizens perceive the issue as personally relevant.
+To test these hypotheses, I conducted a survey experiment, focusing on communications of the Israeli Environment Protection Ministry, about its policy plans.
+The results confirm that symbolic elements in communications increase citizens' trust in ill-perceived policies, by distracting them from scrutinizing their content.
+In contrast with my expectation, the effect of symbols was not attenuated by personal relevance.
+I discuss the implications of these findings for democratic responsiveness and accountability.*
 
@@
 However this issue represents a *continuous* concern that they may have got used to over the time, as opposed a new issue that emerged recently.
-If this explanation holds, this entails that citizens may resist the emotional effect of symbols only in rare circumbstances, which are charecterized by very high levels of personal relevance.
+If this explanation holds, this entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by very high levels of personal relevance.
 These latter findings are also consistent with the findings of @alonbarkat_2017.
 In that study, the scholars assessed citizens' trust in the government electricity company, and its shaping by its familiar symbol, given citizens' recent personal experience of prolonged blackouts.
-Whilst their study was not purposly designed to test the interaction between symbols and personal relevance, one can assume that those who personally experienced blackouts perceived electricity service as more personally relevant.
+Whilst their study was not purposely designed to test the interaction between symbols and personal relevance, one can assume that those who personally experienced blackouts perceived electricity service as more personally relevant.
 Still, they found that citizens who experienced blackouts were influenced by the symbol, as much as those who did not.
@@
 Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas.
-Moreover, in the symbols treatment group, I used a bundle of symbols, without dissentangling their distinct effects.
+Moreover, in the symbols treatment group, I used a bundle of symbols, without disentangling their distinct effects.
 Future studies may compare the effectiveness of different types of symbolic elements.
 Finally, this study focuses on communication about policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
-Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction bewteen symbols and information on good/bad outcomes.
+Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information on good/bad outcomes.
 
 Keeping these limitations in mind, this study has several important implications for public administration research.
-Most importantly, my findings highlight the significat role of branding and symbolic communication in shaping citizens' attitudes about government.
+Most importantly, my findings highlight the significant role of branding and symbolic communication in shaping citizens' attitudes about government.
 Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abounded research on their responses to information.
@@
 On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
-Moreover, it becomes especially problematic when symbols are used by poorly performing organizations,  or organizations that lack professional expertiese.
+Moreover, it becomes especially problematic when symbols are used by poorly performing organizations,  or organizations that lack professional expertise.
 It those cases, symbolic elements can mitigate justified public criticism of government failures.
-Organizations can use them deliberately to distort public opinion via propaganda, or - more likely - without being aware of the tention between the symbols and their substantive message.
+Organizations can use them deliberately to distort public opinion via propaganda, or - more likely - without being aware of the tension between the symbols and their substantive message.
 Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
@@
 
-This study also contributes to existing behavioral Public Administration resarch by intoroducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications.
+This study also contributes to existing behavioral Public Administration research by introducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications.
 ELM has various postulations and implications, but most importantly, it stresses that people respond differently to different communications, depending on people's motivation and ability to think about the subject, and on the quality of arguments and the peripheral cues in the communication.
-In this study, I applyed ELM to distinguish bewteen the peripheral processing of symbolic elements versus the central processing of substantive information, and to exlore their moderation by citizens' motivation to elaborate on the message.
+In this study, I applied ELM to distinguish between the peripheral processing of symbolic elements versus the central processing of substantive information, and to explore their moderation by citizens' motivation to elaborate on the message.
 Future studies may apply ELM and further explore the effects of other peripheral cues in government communications, and of other relevant motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
@@
 By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they probably also have lower ability to do so, given the high competition on their time and attention.
-Accordingly, their responses to performance information will less affected by asymetrical processing of information, because most of them are not likely to process this information in the first place.
+Accordingly, their responses to performance information will less affected by asymmetrical processing of information, because most of them are not likely to process this information in the first place.
 Instead, most of them will rely on simple cues and heuristic shortcuts.
@@
 For instance, they can add filler sections in the survey before the real manipulation to attenuate participants' motivation and ability to elaborate.
-In addition, because the graphic design of communications also affects motivation and ability to elborate, as shown here, scholars should simulate the design of real communications.
+In addition, because the graphic design of communications also affects motivation and ability to elaborate, as shown here, scholars should simulate the design of real communications.
 

### 2018-06-12 paper2_information and symbols.Rmd
Add files via upload

--- 2018-05-21 paper.Rmd
@@
 ---
-title: 'The effects of symbols and information in government communications on citizens  trust: Evidence from a survey experiment'
+title: "The effect of symbols in government communications on citizens' trust, and its interaction with substantive information"
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
 
-Paper presented at the 2018 Transatlantic Dialogue (TAD 14) at Workshop 1: *Behavioral Public Administration and Psychological perspectives*. June 2018, Bucharest, Romania.
-
 Preliminary draft (last edited at `r Sys.Date()`)[^footnote_scripts] - do not cite without author's permission.
@@
 logos, images and celebrities).
-Still, we lack theoretical understanding of the different mechanisms underlying citizens' responses to information and symbolic elements, and accordingly - the interaction between them.
-Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements are likely to lead citizens to dedicate less attention to the substantive information in the communication, and accordingly, to increase their trust in logically-unpersuasive policy plans.
-I also hypothesize that symbolic elements have a greater effect on citizens' trust the less citizens perceive the issue as personally relevant.
-To test these hypotheses, I conducted a survey experiment, focusing on communications of the Israeli Environment Protection Ministry, about its policy plans.
-The results confirm that symbolic elements in communications increase citizens' trust in ill-perceived policies, by distracting them from scrutinizing their content.
-In contrast with my expectation, the effect of symbols was not attenuated by personal relevance.
+Still, we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information.
+Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
+Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
+I examine these hypotheses via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
+The results confirm that symbolic elements in communications increase citizens' trust.
+The effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to scrutinize their content.
 I discuss the implications of these findings for democratic responsiveness and accountability.*
@@
 The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @grimmelikhuijsen_2015; @ho_2017].
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
 Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on organizations' performance and logically persuasive explanations for their policies.
@@
 Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
-Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *under what conditions do symbolic elements  increase citizens' trust in governemnt policy?* And specifically, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
+Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
 
@@
 Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
-I expect that this effect is attenuated the more citizens perceive the communications as personally relevant, because they are more motivated to think about their messages.
 *Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
@@
 fake symbols and no symbols conditions).
-In addition, I examine the moderating role of the perceived personal relevance of these policies.
 
@@
 In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about its content.
-I did not find support for the hypothesis that the effect of the symbolic elements is attenuated by the perceived personal relevance of the policy issue.
 I discuss the theoretical and normative implications of these findings.
@@
 They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations).
-Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them (evaluative conditioning).
+Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them ("evaluative conditioning").
 They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.
@@
 Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust.
-Additionally, these studies neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications.
+Specifically, these studies neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications.
 We do not know whether well-designed symbols reinforce, or offset, citizens' rational responses to information.
@@
 
-According to ELM, peoples' responses to different elements in persuasive communications depends on the amount of thinking that they dedicate to the message content.
+According to ELM, the responses of individuals to persuasive communications depends on the amount of thinking that they dedicate to the message content.
 Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
 This range between high and low degrees of thought is referred to as the "elaboration continuum".
-Along this continuum, there are numerous specific processes of persuasion (or attitude change) that can occur.
+People's location along this continuum is associated with different psychological processes of persuasion.
 At the high end of the elaboration continuum, also called the "central route", people are likely to respond by cognitively scrutinizing the arguments central to the merits of the issue.
-At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as a transfer of affect[^footnote_dual_process_theories].
-These different persuasion mechanisms are likely to cause divergent types of attitudinal change.
+At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories].
+In turn, these different persuasion mechanisms are likely to cause divergent types of attitudinal change.
 Persuasion through the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
@@
 
-People at different locations along the elaboration continuum may process the same element in a communication in different ways.
+ELM enables to disentangle the distinct effects of different elements in communications.
+Some elements are processed differently by people at different locations along the elaboration continuum.
 Consider for instance a text that contains a series of logical arguments supporting a certain position.
@@
 Conversely, those at the low end of the continuum are likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
-Some elements provide potential cues that lack any logical quality at all, such as the physical attractiveness of the source.
+Some elements provide potential cues that lack any logical quality at all.
+For example, the physical attractiveness of the source normally does not represent any substantive argument, yet it can serve as a simple cue.
 These latter elements may affect the attitudes of those at the low end, but are less likely to persuade those at the high end [@petty_1986].
 
-ELM further postulates that the placement of people along the elaboration continuum in any given situation is determined by their motivation and ability to think about the message.
-The literature proposes a variety of such motivational and ability factors.
-Most prominently, the more people perceive the issue as personally relevant, the more motivated they are to invest in thinking about it, and accordingly, they more likely they are to use the central route [@petty_1979; @petty_1981; @petty_1983].
-Also, studies have demonstrated that the more people are distracted, the more difficult it is  for them to scrutinize the message arguments, a mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986].
-People's location along the elaboration continuum is also determined by their affective state or mood.
-Positive mood (compared with neutral or negative moods) reduces people's cognitive ability and attenuates their motivation to think, due to their desire to maintain their positive mood and avoid message processing that would depress it [@worth_1987; @mackie_1989; @bless_1990; @schwarz_1991; @petty_2015; but see: @wegener_1995].[^footnote_elm_factors]
+ELM further postulates that the placement of people along the elaboration continuum in any given situation is determined by their *motivation* and *ability* to think about the message.
+Accordingly, the literature proposes a variety of such motivational and ability factors.
+Among others, studies have demonstrated that the more people are distracted, the more difficult it is for them to scrutinize the message arguments, a mechanism that has been referred to as "elaboration disruption" [@petty_1976; @petty_1986].
+Another prominent factor that influences people's inclination to elaborate on the message is their affective state, or mood.
+Positive mood (compared with neutral or negative moods) reduces people's cognitive ability and attenuates their motivation to think, due to their desire to maintain their positive mood and avoid message processing that would depress it [@worth_1987; @mackie_1989; @bless_1990; @schwarz_1991; @petty_2015; but see: @wegener_1995].[^footnote_elm_factors] Affecting the amount of thinking can cause attitude change in interaction with elements in the communication that can function as arguments or peripheral cues.
+Decreasing the amount of thinking weakens the effect the substantive arguments and enhances the effect of peripheral cues (and vice versa).
 
@@
 
-People's motivation and/or ability to think is shaped not only by factors external to the communication, but also by elements in the communication itself.
-For example, using second-person pronouns in the message (i.e.
-"you", "your") increases people's perceived personal relevance, and motivation to elaborate [@burnkrant_1989]; Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986]; The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008].
-Affecting the amount of thinking can cause attitude change in interaction with elements in the communication that can function as arguments or peripheral cues.
-Accordingly, decreasing the amount of thinking enhances the effect of peripheral cues, whereas increasing the amount of thinking enhances the effect of the logical arguments.
-
-Finally, some elements in communications can function both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
-Thus, these elements can shape people's attitudes through more than one causal mechanism.
-Continuing with the above mentioned examples, background music and humor can function at the same time as factors that reduce elaboration and as peripheral cues.
-@petty_1986 have suggested that we are more likely to find these complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
+Elements in communications can also function as factors that affect people's motivation and/or ability to think.
+For example, Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986]; The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008].
+Hence, elements can have more than one function, and can shape attitudes through several mechanisms.
+They can serve both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
+Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persudate people directly through the peripheral route, yet at the same time they can also as factors that reduce elaboration.
+Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]
+
+[^footnote_multifunction_factors] : @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
 When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.
@@
 
-In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated to do so.
-Conversely, symbolic elements represent potential peripheral cues, which can affect attitudes through the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
-Accordingly, the effect of symbolic elements on citizens' trust is likely to depend on citizens' motivation to cognitively invest and think about the policy issues.
-Specifically, I expect that the more citizens perceive the policy issue as personally relevant, the more they are likely to focus on scrutinizing the content of the message, and the less they are likely to rely on the symbolic elements entangled in the communication.
-
-Accordingly, I expect that:
-
->*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
-
->*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be attenuated the more citizens perceive the policy issues in the communications as personally relevant.*
-
-However, we can also derive from ELM a second mechanism by which symbolic elements may increase citizens' trust.
-In addition to their direct positive effect on trust (via the peripheral route), symbols can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g.
+In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and capable to do so.
+Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust through the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
+However, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly.
+They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g.
 information on poor performance) and weak arguments (e.g.
@@
 
-Symbolic elements can decrease citizens' ability and motivation to think about the message in several ways.
+Symbolic elements may decrease citizens' ability and motivation to think about the message in several ways.
 First, they can cause elaboration disruption, by distracting citizens and absorbing their attention and cognitive efforts [@petty_1976; @petty_1986].
@@
 Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about tedious bureaucratic affairs, which would depress their positive mood.
-
-The expectation that symbols will reduce the amount of thinking entails an interaction between symbols and the substantive information in the communications.
+The latter expectation entails an interaction between symbols and the substantive information in the communications.
 Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize information that would have decreased their trust.
-Accordingly, I expect that:
-
->*H<sub>3</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
+
+In sum, I expect that:
+
+>*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
+
+>*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
+
+>*H<sub>3</sub> - Symbolic elements are likely to decrease the amount of thinking about the content of the communication.*
 
@@
 Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
-On the other hand, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, for two reasons: First, citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2016; @james_2017b].
+Nevertheless, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, since citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2016; @james_2017b].
 Congruently, the effect of positive information (versus a medium level) is likely to be relatively small, and hence neutralizing this effect may not make much difference.
-Second, even when communications include favorable information, symbols can still have a positive effect on trust through the peripheral route (in accordance with my first hypothesis).
-Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction, which can be .
+Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction.
 
@@
 
+In addition to the abovementioned hypotheses, the experiment is also designed to test an additional set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications.
+The selection of policy plans and the construction of the population sample were designed to account for variation in that variable.
+In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction bewteen symbols and information.[^footnote_relevance_paper]
+
+[^footnote_relevance_paper]: The methodological aspects which are relevant for examining the additional hypotheses (i.e.
+the interaction between symbols with personal relevance) are described in a seperate paper.
+An English translation of the full survey is available from the supplementary appendix.
+
 <br>
@@
 In the survey, the communications about the two policy plans, in which I manipulated the informative and symbolic elements, are presented to the participants as sections from the EPM's official publication of its annual work plan.
-Methodologically, EPM makes a good case study for two main reasons.
-
-*First*, EPM has invested greatly over the past years in public communications.
+
+Methodologically, EPM makes a good case for this study since has invested greatly over the past years in public communications.
 In these various communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
-Here, I decided to focus on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**.
+Here, I focused on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**.
 The first symbolic element is the unique brand logo of the EPM (image a.
@@
 
-The *second* reason for selecting EPM regards its policy plan regarding the pollution in the Haifa-Bay area, which offers a fortunate case for examining the moderating role of perceived personal relevance.
-The Haifa-Bay area, located on the Mediterranean coast of northern Israel, is characterized by relatively high levels of air pollution, mainly due to the concentration of heavy industry.
-Beginning in the late 2000s, the Ministry of Environment protection has been implementing policy programs to reduce the high levels of pollution in the area.
-The uniqueness of this policy issue is rooted in the fact that it represents natural variation in citizens' perceived personal relevance (between those who reside in the polluted area, and others), which is not strongly confounded with differences in personal knowledge, as in most cases [@petty_1983].
-The air pollution in the Haifa-bay area  is an intangible, invisible, ambiguous and complicated policy issue.
-Those who reside in a polluted area, are not likely to have much greater knowledge and understanding of the issue.
-Accordingly, when they are exposed to a communication about this personally relevant issue, they are more motivated to scrutinize it, yet are not more capable to do so than others.
-Hence, this case enables to isolate the distinct effect of personal relevance.
-As explained below, the sample population of the experiment consists of residents of Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
-
-I supplemented the Haifa-bay air-pollution policy with a second policy plan, which is likely to be perceived as equally relevant for those Haifa-bay residents and others.
-This comparison further enables me to confirm that differences between the two groups, if found, are explained by differences in the perceived personal relevance of the policy issue.
-Furthermore, testing the effects of symbolic elements and information on two different policy plans provides a more rigorous test for the theory.
-Hence, I selected EPM's policy for reducing of domestic waste and increasing recycling, a tangible policy issue which I expect to be perceived as equally personally relevant by both groups of citizens.
-For the sake of simplicity, I henceforth refer to these two policy plans as "air-pollution" and "recycling" policies.
-
-Data from the survey experiment confirms the empirical assumption that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents (`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_air_obs))%>%max()%>%round(1)` [`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_air_obs)-1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`, `r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_air_obs)+1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`] compared with `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_air_obs))%>%max()%>%round(1)` [`r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_air_obs)-1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`, `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_air_obs)+1.96*sd(RELEVANCE_air_obs)/sqrt(n()))%>%max()%>%round(1)`] on a scale of 1-7).
-As for the second, recycling policy, it is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them (`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(RELEVANCE_waste_obs))%>%max()%>%round(1)` versus `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(RELEVANCE_waste_obs))%>%max()%>%round(1)`).
-Participants were also asked to describe the most salient environmental issue in their particular area of residence.
-Indeed, most of the Haifa-Bay subjects regarded in their responses to the air-pollution generated from the industrial area, and many of them linked it to higher morbidity rates in the area.[^footnote_environment_concern] In a prior survey, I empirically confirmed the assumption that the Haifa-bay residents do not have significantly greater knowledge about the air-pollution policy (see supplementary appendix ##TBA##).
-
-[^footnote_environment_concern]: Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, whereas relatively few of them mentioned air-pollution as a prominent environmental concern in their area.
-
-<br>
-
-##*Sample selection and recruitment*
-
-The survey was conducted in late January 2018.
-To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
-I will henceforth refer to these two groups of cities as Haifa-bay and center.
-
-I conducted the survey experiment through Qualtrics Survey Software.
-To select and recruit residents of these specific cities, I was assisted by an Israeli internet research panel company *iPanel*.
-The online survey link was sent by iPanel, between 28.1-1.2.2018.
-A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-These filters are not significantly associated with the areas or the experimental conditions.
-Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
-
-[^footnote_responserate]: According to iPanel's reporting, 5,077 people were invited to fill the survey.
-Of these people, approximately 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
-Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
-
-<br>
-
-## *Procedure*
-
-To disguise the purpose of the experiment, the survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general, as opposed to attitudes about EPM or the specific two policies.
-The participants were first asked pre-manipulation questions about their political ideology and their trust in government ministries in general and evaluation of their performance.
-Thereafter, they were asked about their interest in environmental policy issues, the extent to which they follow these issues in the media, their preference for more/less government investment in this field.
-They were also asked to describe the most salient environmental issue in their particular area of residence.[^footnote_relevance_manipulation]
-
-[^footnote_relevance_manipulation]: The latter questions about environmental policy was initially designed as a manipulation of for perceived personal relevance (specifically for Haifa-Bay subjects with regard to the air-pollution policy).
-The questions which are mentioned above were included in the treatment group, whereas subjects in the control group were asked instead equivalent questions about their field of occupation.
-However, manipulation checks suggested that these priming questions did not enhance the perceived personal relevance of these policies for the participants (either from Haifa-Bay or center cities).
-Therefore, I will not regard to this treatment in the paper.
-
-Thereafter, participants were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
+## *Procedure and sample population*
+
+The survey was presented to the participants as a study about citizens' attitudes regarding environmental policy issues.
+The participants were first asked pre-manipulation questions about their political ideology and their perceptions about the pubic sector.[^footnote_relevance_manipulation] Thereafter, they were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
+The policy plans regarded to reducing air-pollution in the Bay of Haifa (an area in Israel) and reducing domestic waste and increasing recycling.
+The two policy plans were presented to each subject in a random order.
 Each policy plan included the title of the policy goal (i.e.
@@
 
-The air-pollution and recycling policy plans were presented to each subject in a random order.
+[^footnote_relevance_manipulation]: This section also included a manipulation of participants' perceived personal relevance.
+Participants in the treatment group were asked a series of questions about environmental governent policy, whereas participants in the control group were asked instead equivalent questions about their field of occupation.
+
 Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
-logically persuasive policy plan) and weak policy (i.e.
+logically persuasive policy plan) or weak policy (i.e.
 logically unpersuasive).
 The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
-The proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles in the Haifa-Bay area.
-The strong recycling policy regarded increasing the supervision of manufacturers and reducing the use of disposable bags.
 The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-Accordingly, the weak policy plans regarded reducing of regulatory burden on the factories/ manufacturers, and raising citizens' awareness of the efforts to improve air quality/reduce waste.
-The full texts of the weak and strong conditions for the two policy plans is displayed in Appendix A.
-For each subject, one of the two policies was strong and the other was weak, which enables me to compare both between- and within-subjects.
+For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were increasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
+The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
+For each subject, one of the two policies was strong and the other was weak.
 For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
 
-The participants are also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment, control no-symbols and control fake-symbols.
+In addition to information manipulation, the participants are randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment (real symbols), control no symbols and control fake symbols.
 In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
-Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy, given the relevance of the campaign to the policy plan; Friedman's image from the campaign of "starting to think green", which was more general and regarded to a variety of environmental issues, was attached to the air-pollution policy.
+Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy.
 In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
@@
 The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.
-In that sense, it can be regarded as a placebo.
-In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM (supplementary appendix ##TBA##).
-The symbols conditions are displayed in the Appendix B.
-
-Each policy plan was followed by questions about respondents' trust in the policy.
-Afterwards, the subjects were asked about their perceived level of elaboration on the last policy that was presented to them, conducted a memory test.
-They were also asked about the extent to which they perceive the two policies as personally relevant to themselves.
+Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo.
+The symbols conditions are displayed in **Appendix B**.
+That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
+one strong and one weak), enables me later to analyze the interaction between these two manipulations both via between- and within-subjects.
+
+[^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
+The results of these examinations are reported in the supplementary appendix (##TBA##).
+
+Each policy plan was followed by six questions questions about respondents' trust in the policy.
+Afterwards, the subjects conducted a memory test on the last policy that was presented to them, and were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans.
 Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
 After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
-Finally, the participants are debriefed about the manipulations, and the possible deception.
-An English translation of the full survey
-is available from the supplementary appendix.
+Finally, the participants were debriefed about the manipulations, and the possible deception.
+An English translation of the full survey is available from the supplementary appendix.
 
@@
 weak policy).
-The experimental groups are fairly balanced with respect to demographics, pre-manipulation variables and the two areas.
-The assignment to the different experimental groups is graphically presented in Figure 3.
+The assignment to the different experimental groups is graphically presented in **Figure 3**.
+The experimental groups are fairly balanced with respect to demographics, and pre-manipulation variables.
+Throughout the rest of the paper, I will analyze the results at the policy level, in order to simplify the analyses.
+Accordingly, I transformed the dataset into a multilevel structure of policies nested within subjects.[^footnote_combined_analyses]
+
+[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while separating between the two policies.
 
@@
 **Figure 3: Experimental design for policy plan communications**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow_long.png)
+![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow.png)
+
+The survey experiment was conducted online through Qualtrics Survey Software.
+To subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*.
+The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people.
+A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+These filters are not significantly associated with the experimental conditions.
+Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb %>% nrow()` observations nested within these `r N_1` subjects.
+
+[^footnote_responserate]: According to iPanel's reporting, 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
+Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
+
+[^footnote_sample_areas]: To capture variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country.
+The final sample consists of `r SVIVA2_01_haifa%>%nrow()` subjects from the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` from the center cities.
+The two areas received the exact same link to the online survey, and they were equally, randomly assigned to the experimental conditions.
 
@@
 
+alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2) %>% round(2)
+
 cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate %>% mean() %>% round(2)
@@
 cor_RT_delta = cor.test(SVIVA2_01$ELABORATION_total_time_log,
-                          SVIVA2_01$WITHIN_DELTA)$estimate %>% mean() %>% round(2)
+                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
 
 cor_memory_delta = cor.test(SVIVA2_01$MEMORY_total,
-                          SVIVA2_01$WITHIN_DELTA,method="spearman")$estimate %>% mean() %>% round(2)
+                          SVIVA2_01$WITHIN_DELTA)$estimate%>%mean()%>%round(2)
 
@@
 
+My main independent variables are the above mentioned manipulations for information and symbols, and the interaction bewteen them.
 My outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
-This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies respectively), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
+This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_waste_trust`), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-
-To assess the levels of thinking or elaboration on the policy plans, I used two measures: First, I measure the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time or RT), log transformed to reduce skewness.
+The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard variation is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`.
+Higher levels of trust are associated with high trust vis a vis government and left-wing ideology, as expected.
+In addition to measuring pariticipants trust in each policy, per each subpect, I also calculated the delta between her trust in the strong and weak policy plans which were presented to her (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`).
+I used this Trust in policy delta to analyze the interaction between symbols and information within subjects.
+
+To assess the levels of thinking or elaboration on the policy plans, I used two distinct measures: First, I counted the number of seconds participants spent on scanning each of the policy plans (hereafter – reaction time), log transformed to reduce skewness (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(ELABORATION_time_log))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(ELABORATION_time_log))%>%max()%>%round(2)`).
 Second, I used a memory test, asking participants whether a list of four items were included in the policy plan, of which two were/were not included (participants could also select "I don't know").
 The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
-Accordingly, participants could receive a score of 0, 1 or 2.[^footnote_elaboration] The two measures of elaboration are correlated with each other (Spearman rho = `r cor_elaboration_air` and `r cor_elaboration_waste` for the air-pollution and recycling policies respectively), which substantiates their validity.
-Higher reaction time and memory scores were also positively associated with lower delta (within-subjects) between trust in strong and weak policy plans, which indicates the extent to which subjects payed attention to the logical quality of the policy plans (correlations with reaction time and memory score, respectively, are r = `r cor_RT_delta` and rho = `r cor_memory_delta`).
+Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2) %>% round(2)`, which substantiates their validity.
 
@@
 
-My main independent variables are the above mentioned manipulations for information and symbols, and the distinction between the Haifa-Bay and center, as a proxy for the extent to which they perceive the air-pollution policy as personally relevant.
-The latter was coded according to respondents’ reporting on residence, work or studying in one of the Haifa-Bay cities.
-
 <br>
@@
 
-**Figure 4** graphically shows the distributions of participants' trust in the air-pollution and recycling policy plans.
-Both distributions are left skewed, with the majority of subjects reporting 4 or more (on a 1-7 scale).
-Yet, participants were more likely to report low levels of trust in the air-pollution policy, and accordingly its mean is slightly lower than the recycling policy (`r SVIVA2_01%>%summarise(mean(TRUST_air_INDEX))%>%max()%>%round(2)` [`r SVIVA2_01%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r SVIVA2_01%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`], compared with `r SVIVA2_01%>%summarise(mean(TRUST_waste_INDEX))%>%max()%>%round(2)` [`r SVIVA2_01%>%summarise(mean(TRUST_waste_INDEX)-1.96*sd(TRUST_waste_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r SVIVA2_01%>%summarise(mean(TRUST_waste_INDEX)+1.96*sd(TRUST_waste_INDEX)/sqrt(n()))%>%max()%>%round(2)`]).
-Higher levels of trust are associated with high trust vis a vis government and left-wing ideology.
-
-**Figure 4: Distribution of trust in the two policies**
-
-```{r,echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'), fig.show='hold'}
-ggplot(SVIVA2_01, aes(x=TRUST_air_INDEX)) + 
-  geom_histogram(aes(y = (..count..)/sum(..count..)),binwidth = 1,color="black")+
-  scale_x_continuous(name = "Trust in air-pollution policy",breaks = c(1:7),labels = c("low","2","3","4","5","6","high"))+
-  scale_y_continuous(name = "Percentage",limits = c(0,0.4))+
-  guides(fill=FALSE)+
-  ggtitle("") +
-  theme_classic()
-
-ggplot(SVIVA2_01, aes(x=TRUST_waste_INDEX)) + 
-  geom_histogram(aes(y = (..count..)/sum(..count..)),binwidth = 1,color="black")+
-  scale_x_continuous(name = "Trust in recycling policy",breaks = c(1:7),labels = c("low","2","3","4","5","6","high"))+
-  scale_y_continuous(name = "",limits = c(0,0.4))+
-  guides(fill=FALSE)+
-  ggtitle("") +
-  theme_classic()
-```
-
-I now turn to examine my theoretical hypotheses.
-To reiterate, my first two hypotheses regard the role of symbolic elements as peripheral cues that evoke positive emotions, and thereby increase citizens' trust (H1), mainly among those who do not perceive the communication as personally relevant (H2).
-Thereafter, I theorize that symbols can increase trust, indirectly, by decreasing the amount of thinking and thus compensating for logically unpersuasive communications.
-Accordingly, hypothesis 3 focuses on the interaction between symbols and information, and hypothesis 4 focuses on its mediation by lower levels of elaboration.
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-
-x_realsymbol_air = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_air_INDEX)) %>% max()
-x_fakesymbol_air = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(TRUST_air_INDEX)) %>% max()
-x_nosymbol_air = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(TRUST_air_INDEX)) %>% max()
-x_realsymbol_waste = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(TRUST_waste_INDEX)) %>% max()
-x_fakesymbol_waste = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(TRUST_waste_INDEX)) %>% max()
-x_nosymbol_waste = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(TRUST_waste_INDEX)) %>% max()
-
-t_air_symbol_nosymbol = t.test(TRUST_air_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
-t_air_symbol_fakesymbol = t.test(TRUST_air_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
-t_waste_symbol_nosymbol = t.test(TRUST_waste_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=1))
-t_waste_symbol_fakesymbol = t.test(TRUST_waste_INDEX~SYMBOL,filter(SVIVA2_01,SYMBOL!=0))
-
-d_nosymbol_air = ((x_realsymbol_air-x_nosymbol_air)/(filter(SVIVA2_01,SYMBOL!=1)%>%summarise(sd(TRUST_air_INDEX))%>%max())) %>% round(2)
-d_nosymbol_waste = ((x_realsymbol_waste-x_nosymbol_waste)/(filter(SVIVA2_01,SYMBOL!=1)%>%summarise(sd(TRUST_waste_INDEX))%>%max())) %>% round(2)
-
-t_symbol_fakesymbol = t.test(trust~SYMBOL,filter(SVIVA2_01_comb,SYMBOL!=0))
-
-```
-
-## *The effect of symbols on trust in policy*
-
-Beginning with my first hypothesis, I expect that subjects will report higher levels of trust in the policy plans, when they are presented with the real symbols, compared with the two control groups.
-**Figure 5** shows the descriptive comparison of trust between these experimental groups.
-The black points and error bars represent the mean and 95% confidence intervals, and the box-plots show the distribution (position of quartiles and outliers).
-In both policies, subjects in the real symbols condition reported higher levels of trust compared with the no-symbols condition (differences are `r (x_realsymbol_air-x_nosymbol_air)%>%round(2)` [`r t_air_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_air_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_waste-x_nosymbol_waste)%>%round(2)` [`r t_waste_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_waste_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] for the air-pollution and recycling policies, respectively).
-These differences are equivalent to `r d_nosymbol_air` and `r d_nosymbol_waste` standard deviations.
-The fake symbols also increased participants' trust in the policy plans, but to a lesser extent.
-Subjects in the real symbols reported higher trust compared with the fake symbols, but the differences are marginally significant (*p* = `r (t_air_symbol_fakesymbol[["p.value"]]/2)%>%round(2)`-`r (t_waste_symbol_fakesymbol[["p.value"]]/2)%>%round(2)`).
-Below, I also combine the trust in the two policies (i.e.
-2 observations per each subject).
-In these multilevel analyses, the effect of the real symbols compared with the fake symbols is significant at the 90% level.
-
-**Figure 5: The effect of symbolic elements on trust in policy**
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.show='hold', fig.width=6,fig.height=4}
-SVIVA2_01_comb = SVIVA2_01_comb %>% 
-  mutate(POLICY_t = Recode(policy,"'TRUST_air_INDEX'='Air-pollution';'TRUST_waste_INDEX'='Recycling'"))
-
-ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust))+ 
-  theme_classic()+
-  geom_boxplot(width=0.25,color = "gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5) + 
-  stat_summary(fun.y = mean, geom = "point", size=1.5)+
-  stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
-  facet_grid(~factor(POLICY_t))+
-  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in EPM policy",breaks = seq(1,7,by=0.5))
-
-```
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-
-q_diff = c(
-  ((quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==2])[3]- quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==0])[3])%>%max()),
-
-((quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==2])[3]- quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==0])[3])%>%max()),
-
-((quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==2])[4]- quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==0])[4])%>%max()),
-
-((quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==2])[4]- quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==0])[4])%>%max()))
-
-```
-
-Overall, the results are largely consistent with my hypothesis that familiar symbolic elements can increase trust by evoking positive associations that are transferred to government organizations and policies.
-The graphic elements in the fake symbols condition also increased participants' trust through the peripheral route, but to a lesser extent, presumably due to their unfamiliarity, and their lack of strong positive affect.
-
-**Figure 5** also shows that the distribution of trust in policy in the real symbols group is more concentrated.
-The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
-the lower 25% observations).
-Compared with the no symbols, the first quartile increased by `r (quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==2])[2]- quantile(SVIVA2_01$TRUST_air_INDEX[SVIVA2_01$SYMBOL==0])[2])%>%max()%>%round(1)` and `r (quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==2])[2]- quantile(SVIVA2_01$TRUST_waste_INDEX[SVIVA2_01$SYMBOL==0])[2])%>%max()%>%round(1)`, with respect to the air-pollution and recycling policies, respectively.
-By comparison, the medians and 3rd quartiles increased only by `r q_diff %>% min() %>% round(1)`-`r q_diff %>% max() %>% round(1)`.
-On the face of it, this comparison suggests that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
-Stated otherwise, symbols may be more effective in reducing distrust, as opposed to increasing trust.
-If this explanation holds, it implies that symbols have a decreasing marginal effect, i.e., they are generally more effective when trust is low in the first place.
-
-<br>
-
-## *The interaction bewteen symbols and personal relevance*
-
-According to my second hypothesis, I expect that symbols' effect on trust in air-pollution policy will be stronger among the center subjects, insofar as they do not perceive this issue personally relevant.
-Conversely, regarding the recycling policy, the effect of the symbols is expected to be similar for residents of both areas.
-
-Before analyzing the interaction, I explore the differences in the distribution of trust across the two areas.
-In general, participants from Haifa-Bay were more likely to report low levels of trust in the air-pollution policy (*MEAN* = `r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_air_INDEX))%>%max()%>%round(2)` [`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`], *Median* = `r filter(SVIVA2_01,AREA==1)%>%summarise(median(TRUST_air_INDEX))%>%max()%>%round(2)`), compared with participants from the center (*MEAN* = `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_air_INDEX))%>%max()%>%round(2)` [`r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_air_INDEX)-1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`, `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_air_INDEX)+1.96*sd(TRUST_air_INDEX)/sqrt(n()))%>%max()%>%round(2)`], *Median* = `r filter(SVIVA2_01,AREA==0)%>%summarise(median(TRUST_air_INDEX))%>%max()%>%round(2)`).
-The distribution among the Haifa-Bay subjects is also more dispersed (*SD* = `r filter(SVIVA2_01,AREA==1)%>%summarise(sd(TRUST_air_INDEX))%>%max()%>%round(2)` vs.
-`r filter(SVIVA2_01,AREA==0)%>%summarise(sd(TRUST_air_INDEX))%>%max()%>%round(2)`).
-The distribution of trust in the recycling policy is fairly similar in both areas, with slightly higher trust among center subjects (*Mean* = `r filter(SVIVA2_01,AREA==0)%>%summarise(mean(TRUST_waste_INDEX))%>%max()%>%round(2)` vs.
-`r filter(SVIVA2_01,AREA==1)%>%summarise(mean(TRUST_waste_INDEX))%>%max()%>%round(2)`, *p*<.1).
-These differences may suggest that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, but not towards EPM or environmental policy in general.
-
-In **Table 1**, I examine the interaction between symbols and the two areas using OLS regression analyses.
-With regard to each of the two policy plans, I regress the trust index on the symbols manipulation and the allocation to areas (Models 1.1 and 1.3), and thereafter I add the interaction between them (models 1.2 and 1.4).
-
-**Table 1: Regression analyses**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-
-mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb)
-mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
-mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*SYMBOL_t)
-
-mod_waste_1.1 = lm(TRUST_waste_INDEX~SYMBOL_t,data=SVIVA2_01_comb)
-mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
-mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*SYMBOL_t)
-
-stargazer(mod_air_1.2,mod_air_1.3,
-          mod_waste_1.2,mod_waste_1.3,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols"),
-          column.labels = c("(1.1)", "(1.2)","(1.3)","(1.4)"),
-          model.numbers=F,
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-mod_air_1.1.r = lm(TRUST_air_INDEX~SYMBOL_t.r,data=SVIVA2_01_comb)
-mod_air_1.2.r = update(mod_air_1.1.r,. ~ .+AREA_center)
-mod_air_1.3.r = update(mod_air_1.1.r,. ~ .+AREA_center*SYMBOL_t.r)
-
-mod_waste_1.1.r = lm(TRUST_waste_INDEX~SYMBOL_t.r,data=SVIVA2_01_comb)
-mod_waste_1.2.r = update(mod_waste_1.1.r,. ~ .+AREA_center)
-mod_waste_1.3.r = update(mod_waste_1.1.r,. ~ .+AREA_center*SYMBOL_t.r)
-```
-
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
-
-These analyses suggest that the effect of the real symbols on the air-pollution policy was not weaker among the Haifa-bay subjects.
-If anything, the negative coefficient of the interaction term *Area x Real symbols* in Model 1.2 (*Coef* = `r mod_air_1.3[["coefficients"]][["SYMBOL_t1:AREA_center"]]%>%round(2)`, *p*<.1) indicates that the symbols were perhaps more effective on those who reside in the Haifa-bay.
-Furthermore, Model 1.4 also shows that the effect was greater among Haifa-Bay subjects for the recycling policy, which suggests that the differences between the areas is not explained by their varying levels of personal relevance.
-Rather, these differences could be linked to the predispositions of Haifa-Bay subjects to have lower levels of trust in the first place.[^footnote_higher_effect_haifa]
-
-In sum, the experimental results suggest that symbolic elements in communications increase citizens' trust in the policies presented in the communications, and that this effect is not moderated by the perceived personal relevance of the issue.
-In order to further explore the robustness of my null findings with regard to the interaction with personal relevance, I conducted additional analyses (see supplementary appendix).
-First, in addition to the distinction between the areas, I supplemented the above operationalization of perceived personal relevance with subjects' reporting of the perceived personal relevance of these policy plans.
-Second, I added a set of individual-level control variables, and other factors related to interest in environmental policy in general.
-Third, I further explored whether Haifa-bay subjects were more likely to scrutinize the air-pollution policy by testing the interaction between the areas and the information manipulation, and by comparing the levels of elaboration (reaction time and memory-test score) across the two areas, and finally the delta (within-subjects) between trust in strong and weak policy plans.
-All these analyses yielded null findings, which suggest that those who perceive these policies issues as more personally relevant were not more likely to elaborate on them, and were not less likely to be influenced by the symbolic elements.
-
-[^footnote_higher_effect_haifa]: This tentative explanation is supported by the observed decreased marginal reduction in the percentage of subjects who reported very low levels of trust in the policies.
-For example, in the Haifa-Bay, the percentage of those who reported a trust of less than 2 in the air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%, and in the center, it decreased from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
-With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% and in the center it decreased from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
+I now turn to analyzing the experimental results.
+I begin by examining my first and second hypotheses, that regard the effect of symbols on trust and its interaction with information.
+Thereafter, I will exmaine hypotheses 3 and 4, that regard the mediating role on elaboration.
+For each section, I conducted both *between-subjects* and *within-subjects* analyses.
+
+##*The interaction bewteen symbols and information*
+
+According to my first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans.
+According to my second hypothesis, I expect a positive interaction between the real symbols and weak policy plan.
+Namely, the effect of the real symbols is expected to be greater among those subjects who were assigned to the weak policy.
+In **Table 1**, I test these two hypotheses via regression analyses.
+To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package.[^footnote_icc] In Model 1 I regress trust in policy on the symbols manipulation.
+Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them.
+In these models, I the reference category for the symbols manipulation is the no-symbols condition.
+
+[^footnote_icc]: ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`.
 
@@
 
-Given the lack of interaction between symbols and personal relevance, and in order to simplify the analyses of the remaining hypotheses, I continue the rest of my analyses while combining the two policies and the two areas together.
-Accordingly, I transformed the dataset into a multilevel structure of policies nested within subjects (N observations = `r SVIVA2_01_comb %>% nrow()`, N subjects = `r SVIVA2_01_comb%>%distinct(IP)%>%nrow()`).[^footnote_combined_analyses]
-
-[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while separating between the two policies.
-
-## *The interaction bewteen symbols and information*
-
-I now turn to test hypothesis 3, which regards the interaction between symbols and the substantive information in the communication.
-Empirically, I expect that the effect of the real symbols will be greater for the weak policy, compared with the strong policy.
-In **Table 2**, I examine this hypothesis via regression analyses.
-To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level (ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`).
-In Model 2.1 I regress the policy trust index on the symbols and information manipulations.
-Thereafter, in Model 2.2, I add the interaction between them.
-In Model 3.3, I also control for the different effects of the information manipulation on the air-pollution and recycling policies.
-
-**Table 2: Regression analyses**
+**Table 1: Regression analyses**
 
@@
 
-mod_2.1 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_2.2 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_2.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-stargazer(mod_2.1,mod_2.2,mod_2.3,
+mod_1.1 = lmer(trust~SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
+mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+stargazer(mod_1.1,mod_1.2,mod_1.3,
           type="html",style = "apsr",
-          order = c(1,2,3,5,6,4,7),
           dep.var.labels=c("Trust in policy (combined)"),
@@
                              "Weak policy x Real symbols",
-                             "Weak policy x Fake symbols",
-                             "Recycling policy (0=air-pollution)",
-                             "Weak policy x Recycling policy"),
-          #omit.stat = c("aic","bic"),
-          column.labels = c("(2.1)", "(2.2)","(2.3)"),
+                             "Weak policy x Fake symbols"),
           initial.zero = FALSE,
@@
 Standard errors are in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+The reference category for the symbols manipulation conditions is the control no-symbols.",
           notes.append = FALSE)
 
-mod_2.2.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_2.3.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-mod_2.2.r_2 = lmer(trust~SYMBOL_t*INFORMATION+(1|IP),data=SVIVA2_01_comb)
-mod_2.3.r_2 = lmer(trust~SYMBOL_t*INFORMATION+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-mod_2.2.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+(1|IP),data=SVIVA2_01_comb)
-mod_2.3.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-
-mod_2.2.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
-mod_2.3.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+policy*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_1.1.r_1 = lmer(trust~SYMBOL_t.r+(1|IP),data=SVIVA2_01_comb)
+mod_1.2.r_1 = lmer(trust~SYMBOL_t.r+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_1.3.r_1 = lmer(trust~SYMBOL_t.r*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+mod_1.3.r_2 = lmer(trust~SYMBOL_t*INFORMATION+(1|IP),data=SVIVA2_01_comb)
+
+mod_1.3.r_3 = lmer(trust~SYMBOL_t.r*INFORMATION+(1|IP),data=SVIVA2_01_comb)
+
+mod_1.3.r_4 = lmer(trust~SYMBOL_t.r_2*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
 ```
@@
 
-The main effect of the weak policy in Model 2.1 is negative and significant, (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]).
-The interaction between weak policy and real symbols is positive and significant in Model 2.2 (*Coef* = `r mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1:INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]), whereas the interaction with the fake symbols is insignificant.
-The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.2.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.2.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively).
-When the symbols were added to the strong policy plan, they had a weaker effect, which was significant only compared with the no symbols condition (*Coef* = `r mod_2.2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1).
-Congruently, the symbols decreased the differences between the strong and weak policies by `r ((mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/
-(mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100) %>% round(0)`%, compared with the no symbols group (from `r mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_2.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_2.2.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
-The interaction between symbols and information, in Model 2.2, significantly contributes to the model fit (Chi2 = `r anova(mod_2.2,mod_2.1)%>%tidy()%>%filter(term=="mod_2.2")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
+The real symbols condition has a positive main effect on trust in Model 1.1.
+The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), and at the 90% level compared with the fake symbols (`r mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`]).
+These differences are equivalent to `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` and `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` standard variations, respectively.
+The graphic elements in the fake symbols condition also increased participants' trust, but to a lesser extent, presumably due to their unfamiliarity, and their weaker positive affect.
+
+In Model 1.2, the effect of the symbols remains intact, and the effect of the weak policy condition is negative and significant (*Coef* = `r mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())-1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())+1.96*(mod_1.2%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%max()))%>%round(2)`]).
+In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant.
+The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively).
+When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1).
+Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100) %>% round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
+The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
 To facilitate the interpretation of this interaction, **Figure 6** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
-The coefficients of the manipulations and their interaction remains intact when controlling for the different policies, in Model 2.3, which suggests that in both policies the symbols had a greater effect when added to the a weak policy plan.[^footnote_interaction_symbols_policies]
-
-[^footnote_interaction_symbols_policies]: In additional models I also added the interaction between the symbols and the policies, and the triple interaction between symbols, policies and information.
-These interactions are insignificant.
 
@@
   #geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.5,position=position_dodge(0.1))+
-  stat_summary(fun.y = mean, geom = "line", size=0.5, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = INFORMATION_n,linetype=INFORMATION_n),position=position_dodge(0.1))+
   scale_shape_manual(guide=F,values=c(19,1))+
@@
 
-The above analyses are based on *between-subject* comparisons for the same policy plan (i.e.
-strong vs.
-weak air-pollution policy, and strong vs.
-weak recycling policy).
-However, I can also utilize the fact that each subject received two policy plans (one strong and one weak) to assess the interaction between symbols and information, by analyzing the effect of symbols on the differences *within-subjects* - between their trust in the two policy plans.
-This analysis is graphically displayed in **Figure 6**.
-The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2] %>% round(2)`], respectively).
+The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions.
+Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition.
+This comparison is graphically displayed in **Figure 6**.
+The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2] %>% round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]`, respectively).
 The differences between the two control groups are insignificant.
+These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.
 
@@
   stat_summary(fun.y = mean, aes(group = 1), geom = "line", size=0.5)+
-  scale_x_discrete(name="Symbolic elements",labels=c("no symbols","fake symbols","real symbols"))+
+  scale_x_discrete(name="Symbolic elements",labels=c("No symbols","Fake symbols","Real symbols"))+
   scale_y_continuous(name = "Within subject delta", breaks = seq(0,1,by=0.1))
@@
 
-In sum, my between- and within-subject comparisons largely support my third hypothesis, and suggest that symbolic elements increase citizens' trust, in part, by attenuating the negative effect of weak or logically unpersuasive information in communications.
-
-## *The mediating role of elaboration*
-
-Finally, I examine my fourth hypothesis, that the real symbols increase trust in weak policy plans by decreasing the amount of thinking on the communication.
-Empirically, based on this hypothesis, I first expect to find a negative effect of the real symbols on my two indicators of elaboration (reaction time and memory score).
-Thereafter, this effect is expected to mediate the effect of symbols of trust under the weak policy, but not under the strong policy (i.e.
-a second stage moderated mediation model, also see Figure 1).
+Altogether, the above between- and within-subject analyses largely support my first two hypothesis.
+They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications.
+Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.[^footnote_robust_analyses_1]
+
+[^footnote_robust_analyses_1]: In other statistical models, shown in the supplementary appendix, I tested additional specifications, including ##TBA##.
+In all these robust analyses, the effect of the real symbols condition on trust in policy remains positive and significant, and the interaction bewteen the real symbols and the weak information remains positive and signifcant [##TBA##].
+
+##*The mediating role of elaboration*
+
+In the following section, I test the postulation that the interaction between symbols and information is explained or mediated by a decrease in elaboration.
+To reiterate, in the survey, I used reaction time (log) and memory score as measures for participants' level of elaboration of the policy plans.
+Based on my third hypothesis, I expect to find a negative effect of the real symbols on these two measures.
+Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols of trust under the weak policy, but not under the strong policy (see Figure 1).
 
@@
 
-The effects of the real symbols on the elaboration measures are graphically displayed in **Figure 7**.
+In **Table 2**, I test the effects of the real symbols on the elaboration measures via regression analyses.
+I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4).
+The first two models, which refer to reaction time, are multilevel models which are similar to the analyses in table 1.
+As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression instead.
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_2.1 = lmer(ELABORATION_time_log~SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
+mod_2.2 = lmer(ELABORATION_time_log~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_2.3 = lm(MEMORY_score~SYMBOL_t,data=SVIVA2_01_comb)
+mod_2.4 = lm(MEMORY_score~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
+
+stargazer(mod_2.1,mod_2.2,mod_2.3,mod_2.4,
+          type="html",style = "apsr",
+          dep.var.labels=c("Reaction time (log)","Memory score"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)"),
+          initial.zero = FALSE,
+          omit.stat = c("f","ser","aic","bic"),
+          notes = "*Notes*: Table entries are non-standardized regression coefficients.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control no-symbols.",
+          notes.append = FALSE)
+
+mod_2.1.r_1 = lmer(ELABORATION_time~SYMBOL_t.r+(1|IP),data=SVIVA2_01_comb)
+
+mod_2.3.r_1 = lm(MEMORY_score~SYMBOL_t.r,data=SVIVA2_01_comb)
+
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+In all four models, the coefficients of the real symbols are negative and significant, and the coefficients of the fake symbols are insignificant.
+The real symbols decreased the number of second subjects spent on the pages of the policy plans in the online survey, compared with both control groups.[^footnote_RT_symbols] The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), yet it is not sufficiently significant compared with the fake symbols.
+The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the the effects of the information manipulation (in Models 2.2, 2.4).
+The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them.
+**Figure 7** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions.
 The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.
-Subjects in the real symbols group spent `r (x_realsymbol_RT-x_nosymbol_RT)%>%abs()%>%round(1)`-`r (x_realsymbol_RT-x_fakesymbol_RT)%>%abs()%>%round(1)` second less on the pages of the policy plans in the online survey, compared with the two control groups.[^footnote_RT_symbols] With regard to the memory test, subjects in the real symbols group were less likely to select correct items which were included in the policy plans.
-`r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% of them received the minimum score of 0, compared with `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the no symbols and fake symbols control groups.
-The percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the control groups to only `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.[^footnote_memory_symbols] In sum, with respect to both measures, the mean of the symbols condition was significantly lower compared with both control groups, and the differences between the two control groups are insignificant.
-In additional analyses, not shown here, I also account for the two policies, with no change to the results.
-
-[^footnote_RT_symbols]: The differences in seconds as extracted from the differences in logs are: `r (x_realsymbol_RT_log-x_nosymbol_RT_log)%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`.
-Still, these differences are significant.
-
-[^footnote_memory_symbols]: Because each participant was asked with regard to the last policy plan which was presented, the memory score is measured with regard to half of the observations (*n*=`r filter(SVIVA2_01_comb,MEMORY_score>=0)%>%nrow()`).
-The measure of memory test score is ordinal with three categories, and therefore I also tested it's correlation with the symbols manipulation via Spearman test.
+
+[^footnote_RT_symbols]: The difference in seconds compared with the no symbols group, as extracted from the coefficients in logs is: `r (mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`.
+The difference between the raw averages is `r (x_realsymbol_RT-x_fakesymbol_RT)%>%abs()%>%round(1)` seconds.
+
+[^footnote_memory_symbols]: Descriptively, `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% of those in the real symbols group received the minimum score of 0, compared with `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the no symbols and fake symbols control groups.
+Congruently, the percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the control groups to only `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.
+Given that the measure of memory score is ordinal, I also tested it's correlation with the symbols manipulation via Spearman test.
 Spearman rho = `r cor_memory_nosymbol` and `r cor_memory_fakesymbol`, compared with the no symbols and fake symbols control groups.
@@
 
-The less subjects elaborate on the weak policy plans, the more they are likely to report higher levels of trust in them, which will be closer to the levels of trust in the strong policy.
-To test mediation mechanism, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al.
-[@imai_2010; @imai_2011].
+Next, I tested the moderated mediation hypothesis.
+To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al.
+[@imai_2010; @imai_2011], and was also recently also implemented in Public Administration research [@porumbescu_2018].
 This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols).
 Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect.
-This method is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling.
+Causal mediation analysis is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling.
 It is advantaged in terms of its accuracy as well as its ability to identify causality.
@@
 The decreased memory score also mediates the effect (*p*<.1), but only compared with the no symbols group.[^footnote_mediation_memory] The effect of the real symbols on trust in the strong policies is not significantly mediated by the measures of elaboration.
-Altogether, these analyses are consistent with my H4, and suggest that subjects who saw the policy plans with the familiar symbols were less likely to scrutinize their content, which in turn increased their trust in the weak policies.
 
@@
 
-<br>
+Finally, I also tested my moderated mediation hypothesis within-subjects.
+Given that each subject represents one observation, the memory score remains the same, and for the reaction time, I summed the number of seconds subjects spent on both policies (log transformed).
+As expected, higher reaction time and memory scores were positively associated with lower within-subjects differences between trust in strong and weak policy plans (r = `r cor_RT_delta` and `r cor_memory_delta`, respectively).
+To assess the mediation model altogether I similarly used the causal mediation analysis method.
+The results of this analysis are summarized in **Table 4**.
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+med.fit_RT_nosymbol_delta = 
+  lm(ELABORATION_total_time_log~SYMBOL,
+     data=filter(SVIVA2_01,SYMBOL!=1))
+
+med.out_RT_nosymbol_delta = 
+  lm(WITHIN_DELTA~SYMBOL+ELABORATION_total_time_log,
+     data=filter(SVIVA2_01,SYMBOL!=1))
+
+med.fit_RT_fakesymbol_delta = 
+  lm(ELABORATION_total_time_log~SYMBOL,
+     data=filter(SVIVA2_01,SYMBOL!=0))
+
+med.out_RT_fakesymbol_delta = 
+  lm(WITHIN_DELTA~SYMBOL+ELABORATION_total_time_log,
+     data=filter(SVIVA2_01,SYMBOL!=0))
+
+med_RT__nosymbol_delta = mediate(med.fit_RT_nosymbol_delta,
+                                med.out_RT_nosymbol_delta,
+                                treat = "SYMBOL",
+                                mediator = "ELABORATION_total_time_log", 
+                                sims = 100)
+
+med_RT__fakesymbol_delta = mediate(med.fit_RT_fakesymbol_delta,
+                                med.out_RT_fakesymbol_delta,
+                                treat = "SYMBOL",
+                                mediator = "ELABORATION_total_time_log", 
+                                sims = 100)
+
+med.fit_memory_nosymbol_delta = 
+  lm(MEMORY_total~SYMBOL,
+     data=filter(SVIVA2_01,SYMBOL!=1))
+
+med.out_memory_nosymbol_delta = 
+  lm(WITHIN_DELTA~SYMBOL+MEMORY_total,
+     data=filter(SVIVA2_01,SYMBOL!=1))
+
+med.fit_memory_fakesymbol_delta = 
+  lm(MEMORY_total~SYMBOL,
+     data=filter(SVIVA2_01,SYMBOL!=1))
+
+med.out_memory_fakesymbol_delta = 
+  lm(WITHIN_DELTA~SYMBOL+MEMORY_total,
+     data=filter(SVIVA2_01,SYMBOL!=1))
+
+med_memory__nosymbol_delta = mediate(med.fit_memory_nosymbol_delta,
+                                med.out_memory_nosymbol_delta,
+                                treat = "SYMBOL",
+                                mediator = "MEMORY_total", 
+                                sims = 100)
+
+med_memory__fakesymbol_delta = mediate(med.fit_memory_fakesymbol_delta,
+                                med.out_memory_fakesymbol_delta,
+                                treat = "SYMBOL",
+                                mediator = "MEMORY_total", 
+                                sims = 100)
+```
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+#RT
+table_med_RT__nosymbol_delta = 
+summary(med_RT__nosymbol_delta) %>% 
+extract_mediation_summary()
+
+table_med_RT__fakesymbol_delta = 
+summary(med_RT__fakesymbol_delta) %>% 
+extract_mediation_summary()
+
+#memory
+table_med_memory__nosymbol_delta = 
+summary(med_memory__nosymbol_delta) %>% 
+extract_mediation_summary()
+
+table_med_memory__fakesymbol_delta = 
+summary(med_memory__fakesymbol_delta) %>% 
+extract_mediation_summary()
+```
+
+**Table 4: Causal mediation analysis (within subjects)**
+
+*Mediator: Reaction time*
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+table_med_RT_delta = 
+  cbind.data.frame(table_med_RT__nosymbol_delta,
+                   table_med_RT__fakesymbol_delta)
+
+kable(table_med_RT_delta, "html",digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
+```
+
+*Mediator: Memory score*
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+table_med_memory_delta = 
+  cbind.data.frame(table_med_memory__nosymbol_delta,
+                   table_med_memory__fakesymbol_delta)
+
+kable(table_med_memory_delta, "html",digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
+```
+<br>
+
+The results of the within subjects mediation analysis congrue with the above  results.
+The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction the time and the memory score.
+With respect to the reaction time, the estimated proportional mediation is `r (table_med_RT__nosymbol_delta["Prop.
+Mediated","Estimate"]*100) %>% round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_delta["Prop.
+Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
+Regarding the memory score,the estimated proportional mediation is `r (table_med_memory__nosymbol_delta["Prop.
+Mediated","Estimate"]*100) %>% round(1)`% and `r (table_med_memory__fakesymbol_delta["Prop.
+Mediated","Estimate"]*100)%>%round(1)`%, respectively.
+
+Altogether, the between- and within-subjects analyses are consistent with my third and fourth hypotheses.
+They demonstrate that subjects who saw the policy plans with the familiar symbols of EPM, were less likely to elaborate on the content of the EPM policies, which in turn attenuated the negative effect of the weak information, and increased their trust in the weak policies.
+Still, this indirect effect partly mediates the effect of symbols on trust in policy.
+In some of the causal mediation models, the familiar symbols also had a significant direct effect, which can be theoretically explained by the role of symbols as peripheral cues, in accordance with my first hypothesis.
+Congruently, symbols can increase trust directly by evoking positive associations that are transferred to government organizations and policies.
 

### 2018-06-12 SVIVA_exp2_dm_03.R

@@ -404,7 +404,7 @@ mutate(TRUST_air_q1 =  SVIVA2_raw$Q8.5+
            SVIVA2_raw$Q41.2_3)%>%
   mutate(ELABORATION_air_time_log = log(ELABORATION_air_time+1),
          ELABORATION_waste_time_log = log(ELABORATION_waste_time+1)) %>%
-  mutate(ELABORATION_total_time_log = ELABORATION_air_time_log+ELABORATION_waste_time_log) %>% 
+  mutate(ELABORATION_total_time_log = log(ELABORATION_air_time+ELABORATION_waste_time+1)) %>% 
 
 ###memory score  
   mutate(MEMORY_air_correct = ifelse(AIR_order==2,
@@ -523,6 +523,7 @@ SVIVA2_01_comb = SVIVA2_01 %>%
       MEMORY_air_score,
       MEMORY_waste_score,
       GOV_TRUST,
+      GENDER,
       AIR_order,
       WASTE_order) %>% 
   gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 

### 2018-06-14 paper2_information and symbols.Rmd
Add files via upload

@@
 filter_IP = N_0-(SVIVA2_00 %>%
-  distinct(IP,.keep_all=TRUE) %>% nrow())
+  distinct(IP,.keep_all=TRUE)%>%nrow())
 filter_age = N_0-(SVIVA2_00 %>%
@@
 filter_time = N_0-(SVIVA2_00 %>%
-  filter(TIMER_total>=3,TIMER_total<=30) %>% nrow())
-
-N_1_haifa = filter(SVIVA2_01,AREA==1) %>% nrow()
-N_1_center = filter(SVIVA2_01,AREA==0) %>% nrow()
+  filter(TIMER_total>=3,TIMER_total<=30)%>%nrow())
+
+N_1_haifa = filter(SVIVA2_01,AREA==1)%>%nrow()
+N_1_center = filter(SVIVA2_01,AREA==0)%>%nrow()
 
@@
 
-To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow() %>% round(-1)` Israeli citizens.
+To empirically test these theoretical expectations, I conducted a large randomized survey experiment among circa `r SVIVA2_01%>%nrow()%>%round(-1)` Israeli citizens.
 The experiment focuses on the empirical case of the Israeli Environment Protection Ministry.
@@
 These filters are not significantly associated with the experimental conditions.
-Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb %>% nrow()` observations nested within these `r N_1` subjects.
+Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb%>%nrow()` observations nested within these `r N_1` subjects.
 
@@
                                TRUST_air_q5,
-                               TRUST_air_q6))[["total"]][["raw_alpha"]] %>% round(2)
+                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)
 
@@
                                TRUST_waste_q5,
-                               TRUST_waste_q6))[["total"]][["raw_alpha"]] %>% round(2)
-
-alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2) %>% round(2)
-
-cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate %>% mean() %>% round(2)
-
-cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate %>% mean() %>% round(2)
+                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)
+
+alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)
+
+cor_elaboration_air = cor.test(SVIVA2_01$MEMORY_air_score,SVIVA2_01$ELABORATION_air_time_log,method="spearman")$estimate%>%mean()%>%round(2)
+
+cor_elaboration_waste = cor.test(SVIVA2_01$MEMORY_waste_score,SVIVA2_01$ELABORATION_waste_time_log,method="spearman")$estimate%>%mean()%>%round(2)
 
@@
 The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
-Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2) %>% round(2)`, which substantiates their validity.
+Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2)%>%round(2)`, which substantiates their validity.
 
@@
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
-x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust)) %>% max()
-x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust)) %>% max()
-x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust)) %>% max()
+x_realsymbol = filter(SVIVA2_01_comb,SYMBOL==2)%>%summarise(mean(trust))%>%max()
+x_fakesymbol = filter(SVIVA2_01_comb,SYMBOL==1)%>%summarise(mean(trust))%>%max()
+x_nosymbol = filter(SVIVA2_01_comb,SYMBOL==0)%>%summarise(mean(trust))%>%max()
 sd_trust = SVIVA2_01_comb%>%summarise(sd(trust))%>%max()
 
-x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA)) %>% max()
-x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA)) %>% max()
-x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA)) %>% max()
+x_realsymbol_delta = filter(SVIVA2_01,SYMBOL==2)%>%summarise(mean(WITHIN_DELTA))%>%max()
+x_fakesymbol_delta = filter(SVIVA2_01,SYMBOL==1)%>%summarise(mean(WITHIN_DELTA))%>%max()
+x_nosymbol_delta = filter(SVIVA2_01,SYMBOL==0)%>%summarise(mean(WITHIN_DELTA))%>%max()
 sd_trust_delta = SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()
@@
 When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1).
-Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100) %>% round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
+Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
 The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
@@
 This comparison is graphically displayed in **Figure 6**.
-The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2] %>% round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1] %>% round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2] %>% round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]`, respectively).
+The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively).
 The differences between the two control groups are insignificant.
@@
 They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications.
-Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.[^footnote_robust_analyses_1]
-
-[^footnote_robust_analyses_1]: In other statistical models, shown in the supplementary appendix, I tested additional specifications, including ##TBA##.
+Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.In other statistical models, shown in the supplementary appendix, I tested additional specifications, including ##TBA##.
 In all these robust analyses, the effect of the real symbols condition on trust in policy remains positive and significant, and the interaction bewteen the real symbols and the weak information remains positive and signifcant [##TBA##].
+
+How can we explain the finding that the real symbols did not increase participants' trust in the strong policy (Model 1.3)?
+One tentative explanation could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
+Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
+If this explanation holds, then result will be a cielling effect.
+This explantion can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
+Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceilling_effect]
+
+[^footnote_ceilling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
+The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
+the lower 25% observations).
+In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e.
+the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points.
+In the strong policy condition, we can find similar pattern of decreasing marginal effect.
+The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e.
+the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.
 
@@
                                filter(SVIVA2_01_comb,SYMBOL!=1)$MEMORY_score, 
-                               method="spearman")$estimate %>% mean() %>% round(2)
+                               method="spearman")$estimate%>%mean()%>%round(2)
 
@@
                                filter(SVIVA2_01_comb,SYMBOL!=0)$MEMORY_score, 
-                               method="spearman")$estimate %>% mean() %>% round(2)
+                               method="spearman")$estimate%>%mean()%>%round(2)
 ```
@@
 I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4).
-The first two models, which refer to reaction time, are multilevel models which are similar to the analyses in table 1.
-As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression instead.
+The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in table 1.
+As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression.
 
@@
 
-Next, I tested the moderated mediation hypothesis.
+Next, I tested the hypothesis that the decrease in reaction time and memory score mediate the effect of the real symbols on trust in the weak policy plans.
 To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al.
@@
 It is advantaged in terms of its accuracy as well as its ability to identify causality.
-The results of the causal analysis tables are summarized in **Table 3**.
+**Table 3** displays the results of the causal mediation of reaction time (log) and memory test, under the weak policy plans.
 
@@
 table_med_RT__nosymbol_INFORMTION_0 = 
-summary(med_RT__nosymbol_INFORMTION_0) %>% 
+summary(med_RT__nosymbol_INFORMTION_0)%>%
 extract_mediation_summary()
@@
 table_med_RT__fakesymbol_INFORMTION_0 = 
-summary(med_RT__fakesymbol_INFORMTION_0) %>% 
+summary(med_RT__fakesymbol_INFORMTION_0)%>%
 extract_mediation_summary()
@@
 table_med_RT__nosymbol_INFORMTION_1 = 
-summary(med_RT__nosymbol_INFORMTION_1) %>% 
+summary(med_RT__nosymbol_INFORMTION_1)%>%
 extract_mediation_summary()
@@
 table_med_RT__fakesymbol_INFORMTION_1 = 
-summary(med_RT__fakesymbol_INFORMTION_1) %>% 
+summary(med_RT__fakesymbol_INFORMTION_1)%>%
 extract_mediation_summary()
@@
 table_med_memory__nosymbol_INFORMTION_0 = 
-summary(med_memory__nosymbol_INFORMTION_0) %>% 
+summary(med_memory__nosymbol_INFORMTION_0)%>%
 extract_mediation_summary()
@@
 table_med_memory__fakesymbol_INFORMTION_0 = 
-summary(med_memory__fakesymbol_INFORMTION_0) %>% 
+summary(med_memory__fakesymbol_INFORMTION_0)%>%
 extract_mediation_summary()
@@
 table_med_memory__nosymbol_INFORMTION_1 = 
-summary(med_memory__nosymbol_INFORMTION_1) %>% 
+summary(med_memory__nosymbol_INFORMTION_1)%>%
 extract_mediation_summary()
@@
 table_med_memory__fakesymbol_INFORMTION_1 = 
-summary(med_memory__fakesymbol_INFORMTION_1) %>% 
+summary(med_memory__fakesymbol_INFORMTION_1)%>%
 extract_mediation_summary()
@@
 *Mediator: Reaction time*
-3.1: Weak policy
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 kable(table_med_RT_INFORMTION_0, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
   add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
@@
 
-3.2: Strong policy
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-table_med_RT_INFORMTION_1 = 
-  cbind.data.frame(table_med_RT__nosymbol_INFORMTION_1,
-                   table_med_RT__fakesymbol_INFORMTION_1)
-
-kable(table_med_RT_INFORMTION_1, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
-  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
-
-```
-
 *Mediator: Memory score*
-3.3: Weak policy
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 kable(table_med_memory_INFORMTION_0, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
-  add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
-```
-
-3.4: Strong policy
-```{r, echo=FALSE,warning=FALSE,message=FALSE}
-table_med_memory_INFORMTION_1 = 
-  cbind.data.frame(table_med_memory__nosymbol_INFORMTION_1,
-                   table_med_memory__fakesymbol_INFORMTION_1)
-
-kable(table_med_memory_INFORMTION_1, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
   add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
@@
 The estimated proportion of the mediation is `r (table_med_RT__nosymbol_INFORMTION_0["Prop.
-Mediated","Estimate"]*100) %>% round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_INFORMTION_0["Prop.
+Mediated","Estimate"]*100)%>%round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_INFORMTION_0["Prop.
 Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
-The decreased memory score also mediates the effect (*p*<.1), but only compared with the no symbols group.[^footnote_mediation_memory] The effect of the real symbols on trust in the strong policies is not significantly mediated by the measures of elaboration.
+The decreased memory score also mediates the effect (*p*<.1), but only compared with the no symbols group.[^footnote_mediation_memory]
 
@@
 
-Finally, I also tested my moderated mediation hypothesis within-subjects.
+Finally, I also tested this moderated mediation hypothesis via within-subjects analysis.
 Given that each subject represents one observation, the memory score remains the same, and for the reaction time, I summed the number of seconds subjects spent on both policies (log transformed).
-As expected, higher reaction time and memory scores were positively associated with lower within-subjects differences between trust in strong and weak policy plans (r = `r cor_RT_delta` and `r cor_memory_delta`, respectively).
-To assess the mediation model altogether I similarly used the causal mediation analysis method.
-The results of this analysis are summarized in **Table 4**.
+The results of this causal mediation analysis are summarized in **Table 4**.
 
@@
 table_med_RT__nosymbol_delta = 
-summary(med_RT__nosymbol_delta) %>% 
+summary(med_RT__nosymbol_delta)%>%
 extract_mediation_summary()
@@
 table_med_RT__fakesymbol_delta = 
-summary(med_RT__fakesymbol_delta) %>% 
+summary(med_RT__fakesymbol_delta)%>%
 extract_mediation_summary()
@@
 table_med_memory__nosymbol_delta = 
-summary(med_memory__nosymbol_delta) %>% 
+summary(med_memory__nosymbol_delta)%>%
 extract_mediation_summary()
@@
 table_med_memory__fakesymbol_delta = 
-summary(med_memory__fakesymbol_delta) %>% 
+summary(med_memory__fakesymbol_delta)%>%
 extract_mediation_summary()
@@
 kable(table_med_RT_delta, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
   add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
@@
 kable(table_med_memory_delta, "html",digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11) %>% 
+  kable_styling(bootstrap_options = c("striped","condensed"), full_width = F, position = "left", font_size = 11)%>%
   add_header_above(c(" " = 1, "real vs. no symbols" = 4, "real vs. fake symbols" = 4))
@@
 
-The results of the within subjects mediation analysis congrue with the above  results.
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+t1<- medsens(med_RT__nosymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect", 
+             sims = 100)
+t2<- medsens(med_RT__fakesymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect", 
+             sims = 100)
+
+t3<- medsens(med_memory__nosymbol_INFORMTION_0, rho.by = 0.1, effect.type = "indirect",              sims = 100)
+
+t4<- medsens(med_RT__nosymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
+
+t5<- medsens(med_RT__fakesymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
+
+t6<- medsens(med_memory__nosymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
+
+t7<- medsens(med_memory__fakesymbol_delta, rho.by = 0.1, effect.type = "indirect",              sims = 100)
+
+#summary(t1)
+```
+
+The results of the within subjects mediation analysis similarly supports the moderated mediation hypothesis.
 The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction the time and the memory score.
 With respect to the reaction time, the estimated proportional mediation is `r (table_med_RT__nosymbol_delta["Prop.
-Mediated","Estimate"]*100) %>% round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_delta["Prop.
+Mediated","Estimate"]*100)%>%round(1)`% compared with the no symbols, and `r (table_med_RT__fakesymbol_delta["Prop.
 Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
 Regarding the memory score,the estimated proportional mediation is `r (table_med_memory__nosymbol_delta["Prop.
-Mediated","Estimate"]*100) %>% round(1)`% and `r (table_med_memory__fakesymbol_delta["Prop.
-Mediated","Estimate"]*100)%>%round(1)`%, respectively.
+Mediated","Estimate"]*100)%>%round(1)`% and `r (table_med_memory__fakesymbol_delta["Prop.
+Mediated","Estimate"]*100)%>%round(1)`%, respectively.[^footnote_mediation_sensitivity]
+
+[^footnote_mediation_sensitivity]: I also conducted a robusteness test of "formal sensitivity" for the significant causal mediation models, as proposed by Imai et al.
+[-@imai_2010].
+The sensitivity test examines the extent to which the causal mediation would change as a result of a correlation between the error terms of the mediator and the outcome variable (the "sequential ignorability" assumption).
+With regard to mediation by reaction time, the sensitivity factors range bewteen 0.2-0.3, which suggest that a correlation greater than these values would violate the sequential ignorability assumption.
+Imai et al.
+did not offer any rule of thumb with regard to these factors.
+Yet, these results are consistent with sensitivity factors reported in previous studies, and therefore the mediation can be considered fairly reliable.
+The sensitivity factors for the mediation by the memory score are 0.1, which entails that it is less reliable.
 
@@
 They demonstrate that subjects who saw the policy plans with the familiar symbols of EPM, were less likely to elaborate on the content of the EPM policies, which in turn attenuated the negative effect of the weak information, and increased their trust in the weak policies.
-Still, this indirect effect partly mediates the effect of symbols on trust in policy.
-In some of the causal mediation models, the familiar symbols also had a significant direct effect, which can be theoretically explained by the role of symbols as peripheral cues, in accordance with my first hypothesis.
-Congruently, symbols can increase trust directly by evoking positive associations that are transferred to government organizations and policies.
+The partial mediation by reaction time is strongly significant, whereas the mediation by the memory test is notsufficiently significant in all models.
+In some of these models, the familiar symbols also had a significant direct positive effect, which can be theoretically explained by the peripheral effect of symbols via trasfer of affect, in accordance with my first hypothesis.
 
@@
 This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect.
-Using a rigorous experimental design, embedded in a realistic setting focused on the case of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications and with their perceived personal relevance.
-To the best of my knowledge, this is the first study to explore these interactions in the context of government communications.
+Using a rigorous experimental design, embedded in a realistic setting focused on the case of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications.
+To the best of my knowledge, this is the first study to explore this interactions in the context of government communications.
 
@@
 The latter interaction is partly explained by the negative effect of the symbols on the elaboration of the policy plans.
-These findings are based on a large sample of more than `r (SVIVA2_01%>%nrow() %>% round(-2))-100` participants, and are robust for various model specifications.
+These findings are based the analyses of the responses of more than `r (SVIVA2_01%>%nrow()%>%round(-2))-100` participants to two different policies, and are robust for various model specifications.
+Moreover, they are evidenced in both between- and within-subjects analysis.
 These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, they evoke general positive feelings that are transferred to the specific organizations and policies.
 Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses.
-These two supplementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986].
-
-I further postulated, based on ELM, that the effect of symbols is attenuated the more the communication is personally relevant for citizens' lives.
-However, this latter expectation was not supported by the results.
-Residents of the polluted Haifa-Bay, who perceive EPM policy plan for reducing air-pollution in that area as highly relevant for their lives, were affected by the symbols not less than those who reside elsewhere.
-If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
-How can we reconcile these unexpected findings with the proposed theory?
-Given that the moderating role of personal relevance on peripheral cues was substantiated by numerous studies in social psychology, I would not argue that we should abandon this postulation based on this one study.
-One plausible explanation is that although Haifa-bay residents perceived the air-pollution policy as more relevant, their motivation to elaborate was not high enough to cause them to avoid peripheral cues.
-Certainly, the air-pollution in their area concerns them a great deal, as they point out themselves.
-However this issue represents a *continuous* concern that they may have got used to over the time, as opposed a new issue that emerged recently.
-If this explanation holds, this entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by very high levels of personal relevance.
-These latter findings are also consistent with the findings of @alonbarkat_2017.
-In that study, the scholars assessed citizens' trust in the government electricity company, and its shaping by its familiar symbol, given citizens' recent personal experience of prolonged blackouts.
-Whilst their study was not purposely designed to test the interaction between symbols and personal relevance, one can assume that those who personally experienced blackouts perceived electricity service as more personally relevant.
-Still, they found that citizens who experienced blackouts were influenced by the symbol, as much as those who did not.
-
-Certainly, we must be cautious when drawing general conclusions from our findings, for several particular reasons.
-First, this study focuses, empirically, on one public organization, which invested greatly in symbolic communications, most prominently, the use of high-profile celebrity comedians in its public campaigns.
+These two supplementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986; @petty_2011].
+
+Certainly, we must be cautious when drawing general conclusions from our findings.
+This study focuses, empirically, on one public organization, charecterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
 Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas.
-Moreover, in the symbols treatment group, I used a bundle of symbols, without disentangling their distinct effects.
+In addition, this study focuses on policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
+Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information on good/bad outcomes.
+Another limitation of the study regards the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
 Future studies may compare the effectiveness of different types of symbolic elements.
-Finally, this study focuses on communication about policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
-Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information on good/bad outcomes.
 
@@
 It those cases, symbolic elements can mitigate justified public criticism of government failures.
-Organizations can use them deliberately to distort public opinion via propaganda, or - more likely - without being aware of the tension between the symbols and their substantive message.
 Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
@@
 ELM has various postulations and implications, but most importantly, it stresses that people respond differently to different communications, depending on people's motivation and ability to think about the subject, and on the quality of arguments and the peripheral cues in the communication.
-In this study, I applied ELM to distinguish between the peripheral processing of symbolic elements versus the central processing of substantive information, and to explore their moderation by citizens' motivation to elaborate on the message.
-Future studies may apply ELM and further explore the effects of other peripheral cues in government communications, and of other relevant motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
+In this study, I applied ELM to theorize the direct and indirect effects of symbolic elements on trust.
+Future Public-Administration studies may apply ELM and further explore the effects of other peripheral, heuristic cues in government communications, and the moderating role of motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
+Future studies may also examine the postulations of ELM that persuasion via arguments is more likely to be enduring,  and to increase citizens' cooperation with government policies, compared with persuasion via symbolic elements and heuristic cues.
 
@@
 Instead, most of them will rely on simple cues and heuristic shortcuts.
-I would expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2016; @olsen_2017].
+I expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2016; @olsen_2017].
 Future studies may empirically explore these interactions.

### 2018-06-15 paper2_APPENDIX.Rmd
Add files via upload

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

<br>

Last edited at `r Sys.Date()`.

<br>

```{r , include=FALSE, echo=FALSE}
load(".RData")
library(tidyverse)
library(sjPlot)
library(stargazer)

```

#Contents:

1. Supplementary information about the images.

2. The recognizability, affect and associations of the symbolic elements in the experiment

3. Summary statistics.

4. Supplementary analyses.

5. English translation of the survey experiment.

<br>

#1. Supplementary information about the images.

In this section, I provide additional information about the real and fake symbols (logos, and campaign images) which were used in the survey.

## Real symbols

The images of the real symbols were downloaded from EPM's official website, from the section that archives the Ministry's publications and public campaigns. Thereafter, I cropped these images (via GIMP software), and to remove the text. The sources of the images are detailed below:

**Air-pollution policy**

Endorser: Tal Friedman; Campaign: "Starting to think green".

Source: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/Publications/P0601-P0700/P0641.aspx

**Recycling policy**

Endorser: Ido Rosenblum; Campaign: "From now on, every bag is taken seriously".

Source: http://www.sviva.gov.il/InfoServices/NewsAndEvents/MessageDoverAndNews/Pages/2016/December2016/plastic-bags-campaign-2016-IR.aspx

## Fake symbols

To construct the images of the fake endorsers, I purchesed images of... from the website www.istockphoto.com. I sought to select modelers which resemble the general look of Friedman and Rosenblum, and their face expressions. Thereafter, I used these images to construct images which are aesthetically similar to the original images of Friedman and Rosenblum, without their symbolic aspects. For the recycling policy, I used the image from the EPM's campaign, while replacing Rosenblum's face with the face of the modeler, and changing the color of the bag from green to blue. For the The Air-pollution policy, I added a blue background (similar to the green background behind Friedman). Thereafter, to acount for the fact that Friedman's green hair represents a wierd and surprising element, that attracts attention, I also added the blue geometric object above his head. The original images and their sources are detailed below:

**Air-pollution policy**

Original image:

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_air_model.jpg")
```

Source: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336

**Recycling policy**
Original image:

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_waste_model.jpg")
```

Source: https://www.istockphoto.com/il/photo/young-man-smiling-portrait-gm516728601-48347532

<br>

#2. The recognizability, affect and associations of the symbolic elements in the experiment.

<br>

#3. Summary statistics.

```{r,results="asis", echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_01 %>% 
  select(TRUST_air_INDEX,
         TRUST_waste_INDEX,
         ELABORATION_air_time_log,
         ELABORATION_waste_time_log,
         GENDER) %>% 
  stargazer(type="html",digits = 2)
```

<br>

#4. Supplementary analyses.

<br>

#5. English translation of the survey experiment.

### 2018-06-15 paper2_information and symbols.Rmd
Add files via upload

@@
 output:
+  word_document: default
+  pdf_document:
+    toc: yes
   html_document:
@@
       toc_depth: 3
-  pdf_document:
-    toc: yes
-  word_document: default
 link-citations: yes
@@
 
-Preliminary draft (last edited at `r Sys.Date()`)[^footnote_scripts] - do not cite without author's permission.
+Last edited at `r Sys.Date()`)[^footnote_scripts].
 
@@
 Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
-I examine these hypotheses via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
+I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
 The results confirm that symbolic elements in communications increase citizens' trust.
@@
 The symbols conditions are displayed in **Appendix B**.
+Further details about the images in the real and fake symbols conditions are found in the supplementary appendix.
 That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
@@
 
+In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in governemnt, interest in environmental issues and residence in the Haifa-Bay area.
+Summary statistics for all our variables are available in the supplementary appendix.
+
 <br>
@@
 In **Table 1**, I test these two hypotheses via regression analyses.
-To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package.[^footnote_icc] In Model 1 I regress trust in policy on the symbols manipulation.
+To account for the multilevel structure of the data, I use GLS regressions with random intercept at the subject level via `lme4` R package (ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`).
+In Model 1 I regress trust in policy on the symbols manipulation.
 Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them.
 In these models, I the reference category for the symbols manipulation is the no-symbols condition.
-
-[^footnote_icc]: ICC1 = `r multilevel::ICC1(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`, ICC2 = `r multilevel::ICC2(aov(trust~as.factor(IP),data=SVIVA2_01_comb))%>%round(2)`.
 
@@
 The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
-To facilitate the interpretation of this interaction, **Figure 6** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
-
-**Figure 6: The effect of symbolic elements on trust under weak vs. strong information**
+To facilitate the interpretation of this interaction, **Figure 4** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
+
+**Figure 4: The effect of symbolic elements on trust under weak vs. strong information**
 
@@
   #geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.65),
+               width=0.2,size=0.5,position=position_dodge(0.1),color="gray70") + 
   stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
@@
 
+<font size="0.5">
+
+*Note*: Error bars represent 90% confidence intervals.
+
+</font>
+
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition.
-This comparison is graphically displayed in **Figure 6**.
+This comparison is graphically displayed in **Figure 5**.
 The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively).
@@
 
-**Figure 6: The effect of symbolic elements on within-subject delta between strong and weak policies**
+**Figure 5: The effect of symbolic elements on within-subject delta between strong and weak policies**
 
@@
   #geom_boxplot(width=0.25,color = "gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+                              fun.args = list(mult = 1.65),
+                              width=0.1,size=0.5,color="gray70") + 
   stat_summary(fun.y = mean, geom = "point", size=2)+
@@
 ```
+
+<font size="0.5">
+
+*Note*: Error bars represent 90% confidence intervals.
+
+</font>
 
@@
 The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them.
-**Figure 7** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions.
+**Figure 6** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions.
 The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.
@@
 
-**Figure 7: The effect of symbolic elements on elaboration**
+**Figure 6: The effect of symbolic elements on elaboration**
 
@@
   #geom_boxplot(width=0.25,color = "gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width=0.1,size=0.5,color="#9999CC",alpha=0.7) + 
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+                              fun.args = list(mult = 1.65),
+                              width=0.1,size=0.5,color="gray70") + 
   stat_summary(fun.y = mean, geom = "point", size=1.5)+

### 2018-06-16 paper2_APPENDIX.Rmd
Add files via upload

@@
 load(".RData")
+```
+
+```{r , include=FALSE, echo=FALSE}
 library(tidyverse)
@@
 library(stargazer)
-
 ```
@@
 
-#1. Supplementary information about the images.
+#1. Supplementary information about the images
 
-In this section, I provide additional information about the real and fake symbols (logos, and campaign images) which were used in the survey.
+In this section, I provide additional details about the creation of the "real" and "fake" symbolic elements that were included in the policy plans in the survey.
 
-## Real symbols
+##Real symbols
 
-The images of the real symbols were downloaded from EPM's official website, from the section that archives the Ministry's publications and public campaigns.
-Thereafter, I cropped these images (via GIMP software), and to remove the text.
+The campaign images which were included in the policy plans in the real symbols condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns.
+After downloading the images, I cropped them (via GIMP software).
 The sources of the images are detailed below:
@@
 
-Endorser: Tal Friedman; Campaign: "Starting to think green".
+Campaign name: "Starting to think green"; Endorser: Tal Friedman.
 
@@
 
-Endorser: Ido Rosenblum; Campaign: "From now on, every bag is taken seriously".
+Campaign name: "From now on, every bag is taken seriously"; Endorser: Ido Rosenblum.
 
@@
 
-## Fake symbols
+<br>
 
-To construct the images of the fake endorsers, I purchesed images of...
-from the website www.istockphoto.com.
-I sought to select modelers which resemble the general look of Friedman and Rosenblum, and their face expressions.
-Thereafter, I used these images to construct images which are aesthetically similar to the original images of Friedman and Rosenblum, without their symbolic aspects.
-For the recycling policy, I used the image from the EPM's campaign, while replacing Rosenblum's face with the face of the modeler, and changing the color of the bag from green to blue.
-For the The Air-pollution policy, I added a blue background (similar to the green background behind Friedman).
-Thereafter, to acount for the fact that Friedman's green hair represents a wierd and surprising element, that attracts attention, I also added the blue geometric object above his head.
-The original images and their sources are detailed below:
+##Fake symbols
+
+The fake logo and campaign images were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the real symbolic elements, as much as possible, while removing their symbolic aspects.
+
+The fake logo was created via MS paint software.
+I replaced the leaves/hands from the original logo with a shape of stars with rounded edges, and replaced the green color with blue.
+I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturaleness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].
+
+To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their face expressions in the campaign images.
+For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase.
+The original photos which I purchased from the website, and their sources are detailed below.
+Thereafter, I took these images of models, and edited them (via GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects.
+For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue.
+For the The Air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman).
+I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair.
+The latter addition was important, given that the green hair not only has a symbolic conotation, but also functions as an unusual, surprising element, that attracts people's attention.
 
@@
 **Recycling policy**
+
 Original image:
@@
 
-#2. The recognizability, affect and associations of the symbolic elements in the experiment.
+#2. The recognizability, affect and associations of the symbolic elements in the experiment
+
+In this section, I report the results from two prior surveys, with regard to the recognizability, affect and associations of the "real" and "fake" symbolic elements, which were included in the policy plans in the survey.
+I conducted these examinations before conducting the experiment in order to validate my empirical assumptions with regard to comparison between the real and fake symbols.
+I assume that the real symbols are recognized, and that they evoke positive feelings and associations which are related to carring for the environment.
+By comparison, I assume that the fake symbols are not recognized, and are more neutral.
+They do not have a strong positive or negative affect, or strong specific associations.
+
+The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants.
+This survey was specifically designed to assess the recognizability, affect and associations of the real vs.
+fake campaign images.
+In both surveys,
+
+##Prior survey 1
+
+The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, which were recruited by iPanel.
+This survey was designed as a survey experiment, which was a first attempt to test the moderating role of personal relevance on the effects of symbols and information (but not the interaction between symbols and information).
+The experimental procedure had several methodological problems.
+Mainly, the assignment to experimental conditions yielded imbalanced groups, and the manipulations of symbolic elements and information was too subtle.
+Still, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data.
+
+In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols.
+The real and fake symbols conditions included the same logos and colors which were eventually used in the final experiment (but not the campaign images).
+At the end of the survey, participants were asked about their familiarity with the logos and colors that appeared in their policy plans, and their affect.
+These items and their descriptive results are presented below.
+
+"How familiar are you with the symbol [that appeared in the policy plans]?" (1=not at all; 7=very much)
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+set_theme("scatterw")
+
+sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
+        geom.size = 0.9,
+        ylim=c(0,155),
+        axis.title="",
+        title = "Real logo")
+
+sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
+        geom.size = 0.9,
+        ylim=c(0,155),
+        axis.title="",
+        title = "Fake logo")
+
+```
+
+"When you see the symbol [that appeared in the policy plans], what does it make you feel??" (1=very negative feeling; 7=very positive feeling)
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+set_theme("scatterw")
+
+sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
+        geom.size = 0.9,
+        ylim=c(0,160),
+        axis.title="",
+        title = "Real logo")
+
+sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
+        geom.size = 0.9,
+        ylim=c(0,155),
+        axis.title="",
+        title = "Fake logo")
+
+```
 
@@
 
-#3. Summary statistics.
+#3. Summary statistics
 
@@
          TRUST_waste_INDEX,
+         WITHIN_DELTA,
          ELABORATION_air_time_log,
          ELABORATION_waste_time_log,
-         GENDER) %>% 
-  stargazer(type="html",digits = 2)
+         MEMORY_total,         GENDER,
+         AGE,
+         MOBILE,
+         GOV_TRUST,
+         IDEOLOGY,
+         CHILDREN,
+         EDUCATION,
+         INCOME,
+         HOME,
+         AREA_reside_haifa,
+         ENVIRONMENT_INTEREST) %>% 
+  stargazer(type="html",
+            digits = 3,
+            covariate.labels = c("1. Trust in Air-pollution policy",
+                                 "2. Trust in recycling policy",
+                                 "3. Delta (within subjects)",
+                                 "4. Reaction time (log) - Air-pollution policy",
+                                 "5. Reaction time (log) - recycling policy",
+                                 "6. Memory score - Air-pollution policy",
+                                 "7. Memory score - recycling policy",
+                                 "8. Gender (Woman=1)",
+                                 "9. Age",
+                                 "10. Interface (PC = 0; Mobile = 1)",
+                                 "11. Trust in government ministries",
+                                 "12. Political Ideology (10 = extreme left)",
+                                 "13. Having children",
+                                 "14. Education",
+                                 "15. Income",
+                                 "16. Home ownership",
+                                 "17. Residence in Haifa-Bay area",
+                                 "18. Interest in environmental issues"))
 ```
@@
 <br>
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+SVIVA2_01 %>% 
+  select(TRUST_air_INDEX,
+         TRUST_waste_INDEX,
+         WITHIN_DELTA,
+         ELABORATION_air_time_log,
+         ELABORATION_waste_time_log,
+         MEMORY_total,
+         GENDER,
+         AGE,
+         MOBILE,
+         GOV_TRUST,
+         IDEOLOGY,
+         CHILDREN,
+         EDUCATION,
+         INCOME,
+         HOME,
+         AREA_reside_haifa,
+         ENVIRONMENT_INTEREST) %>%
+  sjt.corr(triangle="lower",
+           remove.spaces=T,
+           digits = 2,
+           na.deletion="pairwise",
+           var.labels = c("1",
+                          "2",
+                          "3",
+                          "4",
+                          "5",
+                          "6+7",
+                          "8",
+                          "9",
+                          "10",
+                          "11",
+                          "12",
+                          "13",
+                          "14",
+                          "15",
+                          "16",
+                          "17",
+                          "18"))
+```
 
-#4. Supplementary analyses.
+#4. Supplementary analyses
 
@@
 
-#5. English translation of the survey experiment.
+#5. English translation of the survey experiment
+
+#References

### 2018-06-16 paper2_APPENDIX.Rmd
Add files via upload

@@
 I replaced the leaves/hands from the original logo with a shape of stars with rounded edges, and replaced the green color with blue.
-I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturaleness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].
+I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].
 
@@
 I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair.
-The latter addition was important, given that the green hair not only has a symbolic conotation, but also functions as an unusual, surprising element, that attracts people's attention.
+The latter addition was important, given that the green hair not only has a symbolic connotation, but also functions as an unusual, surprising element, that attracts people's attention.
 
@@
 I conducted these examinations before conducting the experiment in order to validate my empirical assumptions with regard to comparison between the real and fake symbols.
-I assume that the real symbols are recognized, and that they evoke positive feelings and associations which are related to carring for the environment.
+I assume that the real symbols are recognized, and that they evoke positive feelings and associations which are related to caring for the environment.
 By comparison, I assume that the fake symbols are not recognized, and are more neutral.
@@
 
-The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants.
-This survey was specifically designed to assess the recognizability, affect and associations of the real vs.
-fake campaign images.
-In both surveys,
-
-##Prior survey 1
+##Logos (prior survey 1)
 
@@
 Still, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data.
-
 In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols.
@@
 
-"When you see the symbol [that appeared in the policy plans], what does it make you feel??" (1=very negative feeling; 7=very positive feeling)
+"When you see the symbol [that appeared in the policy plans], what does it make you feel?" (1=very negative feeling; 7=very positive feeling)
 
@@
 sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
-        geom.size = 0.9,
+        type="hist",
+        show.mean = T,
         ylim=c(0,160),
@@
 sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
-        geom.size = 0.9,
-        ylim=c(0,155),
+        type="hist",
+        show.mean = T,
+        ylim=c(0,160),
         axis.title="",
@@
 
+Overall, these results show that the real logo is relatively recognizable and has a fairly positive affect, whereas the fake logo is unrecognized and neutral.
+Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?"  With regard to the real logo, many of the participants filled associations related to carting for the environment.
+Representative examples for such answers are: "environmental protection", "a desire to protect nature and the environment", "green policy", "together for the sake of nature", "connection between nature and man".
+The participants were similarly asked about the first thought / association that comes to their mind when they see the color.
+Representative answers for the green color were: "nature", "a green and healthy environment", "environment protection".
+The responses for the fake logo and the blue color were more diverse, and mostly unrelated to environmental issues.
+
+##Campaign images (prior survey 2)
+
+The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants, which were similarly recruited via iPanel.
+This survey was designed as a pre-test that was aimed at assessing the recognizability, affect and associations of the real vs.
+fake campaign images.
+Participants were presented with the four campaign images (two real and two fake), in a random order.
+After every image, they were asked a series of questions regarding the familiarity and affect of the image and of the person presented.
+The items and their descriptive results are presented below.
+
+"The person presented in the image is familiar to me" (1=weakly agree; 7=strongly agree)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real celeb (Tal Friedman)")
+
+sjp.frq(CELEBS_00$air_fake_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Unfamiliar model")
+
+```
+
+Waste policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real celeb (Ido Rosenblum)")
+
+sjp.frq(CELEBS_00$waste_fake_person_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        xlim=c(0,110),
+        axis.title="",
+        title = "Unfamiliar model")
+
+```
+
+"The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?" (1=not at all; 7=very much)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real campaign (starting to think green)")
+
+sjp.frq(CELEBS_00$air_fake_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+Waste policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Real campaign (reusable bags)")
+
+sjp.frq(CELEBS_00$waste_fake_ad_familiar,
+        geom.size = 0.9,
+        ylim=c(0,110),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+"The image evokes a positive feeling" (1=weakly agree; 7=strongly agree)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_positive_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Real campaign (starting to think green)")
+
+sjp.frq(CELEBS_00$air_fake_positive_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+Waste policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_positive_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Real campaign (reusable bags)")
+
+sjp.frq(CELEBS_00$waste_fake_positive_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,40),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+"The image evokes a negative feeling" (1=weakly agree; 7=strongly agree)
+
+Air-pollution policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$air_real_negative_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,80),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Real campaign (starting to think green)")
+
+sjp.frq(CELEBS_00$air_fake_negative_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,80),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+Waste policy
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
+sjp.frq(CELEBS_00$waste_real_negative_affect,
+        type="hist",
+        show.mean = T,
+        ylim=c(0,80),xlim=c(0.5,7.5),
+        axis.title="",
+        title = "Real campaign (reusable bags)")
+
+sjp.frq(CELEBS_00$waste_fake_negative_affect,
+         type="hist",
+        show.mean = T,
+        ylim=c(0,80),
+        axis.title="",
+        title = "Fake campaign")
+
+```
+
+These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative of positive feelings.
+Finally, I similarly asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text).
+Most of the participants associated Rosenblum's image to the reducing the use of disposable grocery bags, in line with the campaign's message (e.g.
+"reusable bag", "reusable instead of disposable bag for protecting the environment").
+With regard to Friedman's grass-head image from his "starting to think green" campaign, participants mostly mentioned associations related to environmental awareness (e.g.
+"green head, thinking about the environment", "green environment", "think green"), and to the humoristic aspect (e.g.
+"funny", "comedian", "Funny advertisement", "hahaha").
+
 <br>
@@
 #3. Summary statistics
+
+**Table A1: summary statistics of research variables**
 
@@
 <br>
+
+**Table A2: Correlation matrix**
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 
+**Table A3: Regression table - unfiltered sample**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+library(lme4)
+library(car)
+
+SVIVA2_comb_robust_1 = SVIVA2_00 %>%
+  filter(!(AGE %in% 1:17)) %>% 
+  dplyr::select(IP,USER_ID,AREA,AREA_names,
+      RELEVANCE_exp,RELEVANCE_exp_n,
+      SYMBOL,SYMBOL_n,
+      INFORMATION_air,INFORMATION_air_n,
+      INFORMATION_waste,INFORMATION_waste_n,
+      TRUST_air_INDEX,
+      TRUST_waste_INDEX,
+      ELABORATION_air_time_log,
+      ELABORATION_waste_time_log,
+      ELABORATION_air_time,
+      ELABORATION_waste_time,
+      MEMORY_air_score,
+      MEMORY_waste_score,
+      GOV_TRUST,
+      GENDER,
+      AIR_order,
+      WASTE_order) %>% 
+  gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
+  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
+                              INFORMATION_waste),
+         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
+                                INFORMATION_waste_n),
+         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
+                                       ELABORATION_waste_time_log),
+         MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
+                               MEMORY_waste_score),
+         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
+                                       ELABORATION_waste_time)) %>% 
+  mutate(TRUST_air_INDEX = ifelse(policy=="TRUST_air_INDEX",trust,NA),
+         TRUST_waste_INDEX = ifelse(policy=="TRUST_waste_INDEX",trust,NA),
+         INFORMATION_weak = Recode(INFORMATION,"0=1;1=0"),
+         AREA_center = Recode(AREA,"0=1;1=0"),
+         SYMBOL_t = factor(Recode(SYMBOL,"1=2;2=1")),
+         SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
+         SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")),
+         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order))
+
+mod_1.1 = lmer(trust~SYMBOL_t+(1|USER_ID),data=SVIVA2_comb_robust_1)
+mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|USER_ID),data=SVIVA2_comb_robust_1)
+mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|USER_ID),data=SVIVA2_comb_robust_1)
+
+stargazer(mod_1.1,mod_1.2,mod_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in policy (combined)"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Weak policy x Real symbols",
+                             "Weak policy x Fake symbols"),
+          initial.zero = FALSE,
+          omit.stat = c("aic","bic"),
+          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control no-symbols.",
+          notes.append = FALSE)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+<br>
+
+**Table A4: Regression table - adding control variables**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+library(lme4)
+
+mod_1.1 = lmer(trust~SYMBOL_t+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION+AREA+(1|IP),data=SVIVA2_01_comb)
+mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION+AREA+(1|IP),data=SVIVA2_01_comb)
+mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION+AREA+(1|IP),data=SVIVA2_01_comb)
+
+stargazer(mod_1.1,mod_1.2,mod_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in policy (combined)"),
+          initial.zero = FALSE,
+          omit.stat = c("aic","bic"),
+          order = c(1,2,3,10,11,4,5,6,7,8,9),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Weak policy x Real symbols",
+                             "Weak policy x Fake symbols",
+                             "Gender (1=Woman)",
+                             "Ideology",
+                             "Trust in government ministries",
+                             "Income",
+                             "Education",
+                             "Residence in Haifa-Bay area"),
+          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control no-symbols.",
+          notes.append = FALSE)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+<br>
+
+**Table A5: Regression table - excluding participants who did not recognize EPM campaigns**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+SVIVA2_comb_robust_3 = SVIVA2_01_comb %>%
+  filter(#RECOGNIZE_SVIVA_logo>1,
+         RECOGNIZE_campaign>1)
+
+mod_1.1 = lmer(trust~SYMBOL_t+(1|IP),data=SVIVA2_comb_robust_3)
+mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_comb_robust_3)
+mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_comb_robust_3)
+
+stargazer(mod_1.1,mod_1.2,mod_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in policy (combined)"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Weak policy x Real symbols",
+                             "Weak policy x Fake symbols"),
+          initial.zero = FALSE,
+          omit.stat = c("aic","bic"),
+          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control no-symbols.",
+          notes.append = FALSE)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+<br>
+
+**Table A6: Regression table - excluding participants who did not recognize EPM logo**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+SVIVA2_comb_robust_4 = SVIVA2_01_comb %>%
+  filter(RECOGNIZE_SVIVA_logo>1)
+
+mod_1.1 = lmer(trust~SYMBOL_t+(1|IP),data=SVIVA2_comb_robust_4)
+mod_1.2 = lmer(trust~SYMBOL_t+INFORMATION_weak+(1|IP),data=SVIVA2_comb_robust_4)
+mod_1.3 = lmer(trust~SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_comb_robust_4)
+
+stargazer(mod_1.1,mod_1.2,mod_1.3,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in policy (combined)"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Weak policy x Real symbols",
+                             "Weak policy x Fake symbols"),
+          initial.zero = FALSE,
+          omit.stat = c("aic","bic"),
+           notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control no-symbols.",
+          notes.append = FALSE)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
+<br>
+
+**Table A7: Regression table - adding interaction with the policy plans**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+
+mod_1.1 = lmer(trust~policy*SYMBOL_t+(1|IP),data=SVIVA2_01_comb)
+mod_1.2 = lmer(trust~policy*(SYMBOL_t+INFORMATION_weak)+(1|IP),data=SVIVA2_01_comb)
+mod_1.3 = lmer(trust~policy*SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+mod_1.4 = lmer(trust~policy*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*INFORMATION_weak+(1|IP),data=SVIVA2_01_comb)
+
+stargazer(mod_1.1,mod_1.2,mod_1.3,mod_1.4,
+          type="html",style = "apsr",
+          dep.var.labels=c("Trust in policy (combined)"),
+          order = c(2,3,4,8,9,1,5,6,7,10,11),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak policy (0=strong policy)",
+                             "Weak policy x Real symbols",
+                             "Weak policy x Fake symbols",
+                             "Policy (1=recycling)",
+                             "Policy x Real symbols",
+                             "Policy x Fake symbols",
+                             "Policy x Weak policy",
+                             "Policy x Weak policy x Real symbols",
+                             "Policy x Weak policy x Fake symbols"),
+          initial.zero = FALSE,
+          omit.stat = c("aic","bic"),
+          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+Standard errors are in parentheses.
+The reference category for the symbols manipulation conditions is the control no-symbols.",
+          notes.append = FALSE)
+```
+
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+
 <br>

### 2018-06-16 paper2_information and symbols_01.Rmd
Add files via upload

--- 2018-06-15 paper2_information and symbols.Rmd
@@
 
-Last edited at `r Sys.Date()`)[^footnote_scripts].
+Last edited at `r Sys.Date()`.[^footnote_scripts]
 
@@
 They can serve both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
-Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persudate people directly through the peripheral route, yet at the same time they can also as factors that reduce elaboration.
+Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuades people directly through the peripheral route, yet at the same time they can also as factors that reduce elaboration.
 Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]
 
-[^footnote_multifunction_factors] : @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
+[^footnote_multifunction_factors]: @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
 When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.
@@
 Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
-Nevertheless, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, since citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2016; @james_2017b].
+Nevertheless, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, since citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2017; @james_2017b].
 Congruently, the effect of positive information (versus a medium level) is likely to be relatively small, and hence neutralizing this effect may not make much difference.
@@
 
-In addition to the abovementioned hypotheses, the experiment is also designed to test an additional set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications.
+In addition to the above-mentioned hypotheses, the experiment is also designed to test an additional set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications.
 The selection of policy plans and the construction of the population sample were designed to account for variation in that variable.
-In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction bewteen symbols and information.[^footnote_relevance_paper]
+In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction between symbols and information.[^footnote_relevance_paper]
 
 [^footnote_relevance_paper]: The methodological aspects which are relevant for examining the additional hypotheses (i.e.
-the interaction between symbols with personal relevance) are described in a seperate paper.
+the interaction between symbols with personal relevance) are described in a separate paper.
 An English translation of the full survey is available from the supplementary appendix.
@@
 [^footnote_prior_studies]: In two prior online survey tests, which I conducted before the experiment, I collected further information about the affect and symbolic associations of these symbols.
-These results, which are reported in the supplementary appendix [##TBA##], substantiate my empirical assumption that these elements evoke positive emotions Israeli citizens, and that citizens automatically associate them with EPM and its policies.
+These results, which are reported in the supplementary appendix, substantiate my empirical assumption that these elements evoke positive emotions Israeli citizens, and that citizens automatically associate them with EPM and its policies.
 These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to position people in a positive mood.
@@
 [^footnote_relevance_manipulation]: This section also included a manipulation of participants' perceived personal relevance.
-Participants in the treatment group were asked a series of questions about environmental governent policy, whereas participants in the control group were asked instead equivalent questions about their field of occupation.
+Participants in the treatment group were asked a series of questions about environmental government policy, whereas participants in the control group were asked instead equivalent questions about their field of occupation.
 
@@
 [^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
-The results of these examinations are reported in the supplementary appendix (##TBA##).
+The results of these examinations are reported in the supplementary appendix.
 
@@
 
-[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while separating between the two policies.
+[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while adding the interactions between the manipulations and the policy plans.
+In these models, the interactions between the policy plans and the symbols are far from significance, with no major changes to the results.
 
@@
 
-My main independent variables are the above mentioned manipulations for information and symbols, and the interaction bewteen them.
+My main independent variables are the above mentioned manipulations for information and symbols, and the interaction between them.
 My outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
@@
 The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard variation is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`.
-Higher levels of trust are associated with high trust vis a vis government and left-wing ideology, as expected.
-In addition to measuring pariticipants trust in each policy, per each subpect, I also calculated the delta between her trust in the strong and weak policy plans which were presented to her (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`).
+Higher levels of trust are associated with higher trust in government, left-wing ideology and lower levels of education.
+In addition to measuring participants trust in each policy, per each subject, I also calculated the delta between her trust in the strong and weak policy plans which were presented to her (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`).
 I used this Trust in policy delta to analyze the interaction between symbols and information within subjects.
@@
 
-In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in governemnt, interest in environmental issues and residence in the Haifa-Bay area.
-Summary statistics for all our variables are available in the supplementary appendix.
+In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in government, interest in environmental issues and residence in the Haifa-Bay area.
+Summary statistics and correlation matrix for all variables are available in the supplementary appendix.
 
@@
 I begin by examining my first and second hypotheses, that regard the effect of symbols on trust and its interaction with information.
-Thereafter, I will exmaine hypotheses 3 and 4, that regard the mediating role on elaboration.
+Thereafter, I will examine hypotheses 3 and 4, that regard the mediating role on elaboration.
 For each section, I conducted both *between-subjects* and *within-subjects* analyses.
@@
 
-**Table 1: Regression analyses**
+**Table 1: Regression analyses – the effect of symbols on trust in policy**
 
@@
           initial.zero = FALSE,
+          omit.stat = c("aic","bic"),
           notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
@@
 
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
 
@@
 The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively).
-When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1).
+When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1, one-tailed).
 Congruently, the symbols decreased the differences in trust between the strong and weak policies by `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())/(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())*100)%>%round(0)`%, compared with the no symbols group (from `r mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`] to `r mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max()%>%round(2)` [`r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())-1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`, `r ((mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%abs()%>%max())+1.96*(mod_1.3.r_4%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(std.error)%>%abs()%>%max()))%>%round(2)`]).
@@
 They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications.
-Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.In other statistical models, shown in the supplementary appendix, I tested additional specifications, including ##TBA##.
-In all these robust analyses, the effect of the real symbols condition on trust in policy remains positive and significant, and the interaction bewteen the real symbols and the weak information remains positive and signifcant [##TBA##].
-
-How can we explain the finding that the real symbols did not increase participants' trust in the strong policy (Model 1.3)?
+Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.
+In other statistical models, shown in the supplementary appendix, I tested additional specifications, including analyzing the unfilterred sample, adding control variables, excluding subjects who did not recognize the real symbols and adding interactions with the policy plans.
+In all these robust analyses, the main effect of the real symbols remains positive and significant, and the interaction between the real symbols and the weak information remains positive and significant.
+
+How can we explain the finding that the real symbols only had a marginally significant effect on participants' trust in the strong policy, compared with the no logo, and did not increase their trust compared with the fake logo (Model 1.3)?
 One tentative explanation could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
 Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
-If this explanation holds, then result will be a cielling effect.
-This explantion can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
-Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceilling_effect]
-
-[^footnote_ceilling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
+If this explanation holds, then result will be a ceiling effect.
+This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
+Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceiling_effect]
+
+[^footnote_ceiling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
 The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
@@
 As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression.
+
+**Table 2: Regression analyses – the effect of symbols on elaboration**
 
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold',, fig.width=4,fig.height=4}
+```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=4,fig.height=4}
 ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n), ELABORATION_time_log))+
@@
 
-[^footnote_mediation_sensitivity]: I also conducted a robusteness test of "formal sensitivity" for the significant causal mediation models, as proposed by Imai et al.
+[^footnote_mediation_sensitivity]: I also conducted a robustness test of "formal sensitivity" for the significant causal mediation models, as proposed by Imai et al.
 [-@imai_2010].
 The sensitivity test examines the extent to which the causal mediation would change as a result of a correlation between the error terms of the mediator and the outcome variable (the "sequential ignorability" assumption).
-With regard to mediation by reaction time, the sensitivity factors range bewteen 0.2-0.3, which suggest that a correlation greater than these values would violate the sequential ignorability assumption.
+With regard to mediation by reaction time, the sensitivity factors range between 0.2-0.3, which suggest that a correlation greater than these values would violate the sequential ignorability assumption.
 Imai et al.
@@
 They demonstrate that subjects who saw the policy plans with the familiar symbols of EPM, were less likely to elaborate on the content of the EPM policies, which in turn attenuated the negative effect of the weak information, and increased their trust in the weak policies.
-The partial mediation by reaction time is strongly significant, whereas the mediation by the memory test is notsufficiently significant in all models.
-In some of these models, the familiar symbols also had a significant direct positive effect, which can be theoretically explained by the peripheral effect of symbols via trasfer of affect, in accordance with my first hypothesis.
+The partial mediation by reaction time is strongly significant, whereas the mediation by the memory test is not sufficiently significant in all models.
+In some of these models, the familiar symbols also had a significant direct positive effect, which can be theoretically explained by the peripheral effect of symbols via transfer of affect, in accordance with my first hypothesis.
 
@@
 Certainly, we must be cautious when drawing general conclusions from our findings.
-This study focuses, empirically, on one public organization, charecterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
+This study focuses, empirically, on one public organization, characterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
 Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas.
@@
 Instead, most of them will rely on simple cues and heuristic shortcuts.
-I expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2016; @olsen_2017].
+I expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2017; @olsen_2017].
 Future studies may empirically explore these interactions.

### 2018-06-19 paper2_APPENDIX.Rmd
Add files via upload

@@
 ```{r , include=FALSE, echo=FALSE}
-load("SVIVA_R_ENV.RData")
+source("SVIVA_exp2_dm_03.R")
+
+SVIVA1_01 = read.csv("SVIVA1_01.csv")
+CELEBS_00 = read.csv("CELEBS.csv")
 ```
@@
 
+[Introduction]
+
+Greetings,
+
+We are researchers from the Department of Political Science at the Hebrew University.
+The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy.
+Therefore, it is important for us that you answer the questionnaire seriously and honestly.
+
+The questionnaire filling time is about 5-10 minutes.
+
+It is important for us to clarify that the questionnaire is being voluntarily filled out. Filling out the questionnaire and submitting it are an agreement to participate in the research.
+
+In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only.
+Non-consent to participate will be expressed in non-filling of the questionnaire.
+
+The questionnaire is phrased in masculine form but addresses both men and women.
+
+Thank you for your cooperation!
+
+---
+
+[Pre-manipulation items]
+
+First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.
+
+**How would you evaluate the functioning of National Government Ministries in Israel?**
+
+1. Very poor
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very good
+
+**To what extent do you do you have confidence/trust in Israeli Government Ministries?**
+
+1. I have no confidence/trust
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. I have great confidence/trust
+
+**How would you rate your ideological standpoint on a left-right continuum?**
+
+1. Extreme right
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7.
+
+8.
+
+9.
+
+10. Extreme Left
+
+---
+
+[Manipulation of perceived personal relevance of policy plans: participants are randomly assigned to treatment and control conditions].
+
+[Treatment]
+
+Now, we would like to ask you a few general questions about your interest in environmental issues.
+
+**To what extent are you interested in environmental issues?**
+
+1. Little interested
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very interested
+
+**To what extent do you follow environmental issues in the media and/or in social networks?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**Compared to the current situation, do you think the government should invest more or less in dealing with environmental issues?**
+
+1. Invest much less
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Invest much more
+
+**In which residential area do you currently live?**
+1. North
+
+2. Haifa and the Krayot
+
+3. Center
+
+4. Tel Aviv
+
+5. Lower Galilee
+
+6. Jerusalem
+
+7. Judea and Samaria
+
+8. South
+
+**What is the name of the locality where you live today?**
+
+**In your opinion, what is the most disturbing environmental problem in your area?**
+
+[Control]
+
+Now, we would like to ask you a few general questions about your area of occupation
+
+**In which sector are you currently employed:?**
+
+1. Private sector
+
+2. Public sector
+
+3. Third Sector
+
+4. Other
+
+**What is your field of profession/study?**
+
+**To what extent do you think your profession is interesting?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**To what extent do you follow topics related to your area of occupation in the media and/or social networks?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**Compared to the current situation, do you think the government should assist more or less to promote your field of occupation?**
+
+1. Assist much less
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Assist much more
+
+**What, in your opinion, might attract people to choose your occupation??**
+
+---
+
+Next, we will present you two policy plans on specific environmental issues.
+The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.
+
+At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.
+
+[Participants are presented with the two policy plans. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]
+
+Now, we'd like to ask you a few questions about your position on the policy for ["Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay"]:
+
+**State to what extent do you agree with each of the following sentences.**
+
+**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the actions mentioned in the policy plan were designed in a professional manner**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the policy plan is in the interest of citizens**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens.**
+
+**I believe that EPM made an honest attempt to design a good policy plan**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+---
+
+[Questions about elaboration and personal relevance]
+
+The following sentences describe the way in which you read the latest policy plan that regarded to ["Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay"].
+
+**State to what extent do you agree with each of the following sentences.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I paid much attention to reading the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I skimmed the actions in the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I tried to thoroughly understand the the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**While going through the policy plan I was thinking about other things which are not related to it.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I tried to think how the policy plan will personally affect me.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+Try recalling the content of the latest policy plan.
+[Each subjects was asked about the latest policy plan presenter to her]
+
+**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce air pollution in Haifa Bay?**
+
+1. Supervision on the factories
+
+2. Clean air area
+
+3. Investment in public relations
+
+4. The ammonia tank
+
+5. I can not remember
+
+**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce waste and increase recycling?**
+
+1. Supervision on the manufacturers
+
+2. compulsory charge on bags
+
+3. Investment in public relations
+
+4. plastic bottles
+
+5. I can not remember
+
+**To what extent did you feel that the policy on "reducing waste and increasing recycling" is personally relevant to you?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**To what extent did you feel that the policy on "Reducing the air-pollution in the Haifa-Bay" is personally relevant to you?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**In order to make sure you read the question carefully, please type the number 9 under "Other"?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+8. Other: ___
+
+---
+
+[Demographic questions]
+
+We would like to ask you a few general questions:
+
+**How old are you?**
+
+**What is your highest level of education?**
+
+1.	Primary education or less
+
+2.	Partial secondary education
+
+3.	High education without high school diploma
+
+4.	High education with high school diploma
+
+5.	Non-academic tertiary education
+
+6.	Partial academic degree
+
+7.	Full academic degree (first degree)
+
+8.	Full academic degree (second degree or higher).
+
+**According to Israel's Central Bureau of Statistics the monthly average net income per household is approximately 15,500 NIS. Is your income: **
+
+1.	Far below average
+
+2.	Slightly below average
+
+3.	Near average
+
+4.	Slightly above average
+
+5.	Far above average
+
+**Are you a home owner?**
+
+1. Yes
+
+2. No
+
+**In which residential area do you currently live?**
+1. North
+
+2. Haifa and the Krayot
+
+3. Center
+
+4. Tel Aviv
+
+5. Lower Galilee
+
+6. Jerusalem
+
+7. Judea and Samaria
+
+8. South
+
+**What is your place of residence?**
+
+**Are you or one of your first-degree relatives working (or worked) in one of the factories in the Haifa Bay industrial area?**
+
+1. No
+
+2. Yes
+
+**State the name of the place where you lived at high-school graduation**
+
+**Area where you are currently working/studying?**
+
+1. North
+
+2. Haifa and the Krayot
+
+3. Center
+
+4. Tel Aviv
+
+5. Lower Galilee
+
+6. Jerusalem
+
+7. Judea and Samaria
+
+8. South
+
+**Gender**
+
+1.	Man
+
+2. Woman
+
+3.	I prefer not to answer
+
+**What is the age of your oldest son/daughter?**
+
+1. 0-6
+
+2. 7-12
+
+3. 13-18
+
+4. 19 or more
+
+5. I don't have any children
+
+**Is Hebrew your native language?**
+
+1. Yes
+
+2. No
+
+---
+
+[Manipulation check for symbols]
+
+[For real symbols]:
+Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.
+
+This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much:
+
+[For fake symbols]:
+Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.
+
+This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.
+
+[Respondents are displayed with the two "real" images, and then asked the following two questions]
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much:
+
+[For no symbols]:
+
+Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.
+
+[Respondents are displayed with the two "real" images, and then asked the following two questions]
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much:
+
+---
+
+[Debrief]
+
+Thank you very much for participating in the study.
+
+Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently.
+The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy.
+[For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]
+
+You can review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.
+
 #References

### 2018-06-19 paper2_APPENDIX.Rmd
Add files via upload

@@
 
-**Table A3: Regression table - unfiltered sample**
-
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
@@
 
+SVIVA2_comb_robust_3 = SVIVA2_01_comb %>%
+  filter(#RECOGNIZE_SVIVA_logo>1,
+         RECOGNIZE_campaign>1)
+
+SVIVA2_comb_robust_4 = SVIVA2_01_comb %>%
+  filter(RECOGNIZE_SVIVA_logo>1)
+```
+
+In the tables below, I present additional robust analyses for the effect of symbols on trust in policy and its interaction with the information of the policy plans.
+In **Table A3**, I replicate table 1 of the main paper on the full, unfiltered sample, excluding subjects who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
+In **Table A4**, I add a set of control variables.
+In **Table A5** and **Table A6**, I exclude those subjects who did not recognize the real symbols which were included in the communications.
+Table A5 excludes those who did not recognize the campaign images (n_subjects = `r SVIVA2_comb_robust_3 %>%distinct(IP) %>% nrow()`) and Table A6 excludes those who did not recognize EPM's logo (n_subjects = `r SVIVA2_comb_robust_4 %>%distinct(IP) %>% nrow()`).
+Finally, in **Table A7**, I add interactions with the policy plan, to examine whether the effect of the symbols were significanly different for these two policies.
+All these analyses are random-effect GLS regressions clustered at the subject level, similarly to the main models presented in the paper.
+
+In all these supplementary analyses, the main effect of the real symbols on trust in policy is significant, and the interaction bewteen the real symbols and the weak inforamtion remains positive and significant.
+
+**Table A3: Regression table - unfiltered sample**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+
 mod_1.1 = lmer(trust~SYMBOL_t+(1|USER_ID),data=SVIVA2_comb_robust_1)
@@
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-SVIVA2_comb_robust_3 = SVIVA2_01_comb %>%
-  filter(#RECOGNIZE_SVIVA_logo>1,
-         RECOGNIZE_campaign>1)
 
@@
           omit.stat = c("aic","bic"),
-          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level.
+          notes = "*Notes*: Table entries are non-standardized coefficients.
 Standard errors are in parentheses.
@@
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-SVIVA2_comb_robust_4 = SVIVA2_01_comb %>%
-  filter(RECOGNIZE_SVIVA_logo>1)
 
@@
 
-[Introduction]
-
-Greetings,
-
-We are researchers from the Department of Political Science at the Hebrew University.
+Below is the full text of the survey.
+Additional comments are presented in square beackets.
+The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here.
+The original Qualtrics file is available upon request.
+
+**Greetings, We are researchers from the Department of Political Science at the Hebrew University.
 The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy.
 Therefore, it is important for us that you answer the questionnaire seriously and honestly.
-
-The questionnaire filling time is about 5-10 minutes.
-
-It is important for us to clarify that the questionnaire is being voluntarily filled out. Filling out the questionnaire and submitting it are an agreement to participate in the research.
-
+The questionnaire filling time is about 5-10 minutes.**
+
+**It is important for us to clarify that the questionnaire is voluntary.
+Filling out the questionnaire and submitting it represent your agreement to participate in the research.
 In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only.
-Non-consent to participate will be expressed in non-filling of the questionnaire.
-
-The questionnaire is phrased in masculine form but addresses both men and women.
-
-Thank you for your cooperation!
+Non-consent to participate will be expressed in not filling of the questionnaire.
+The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**
+
+**Thank you for your cooperation!**
 
@@
 
-[Pre-manipulation items]
-
-First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.
+**First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.**
+
+<br>
 
@@
 
-[Manipulation of perceived personal relevance of policy plans: participants are randomly assigned to treatment and control conditions].
+[The following section includes a manipulation of perceived personal relevance of policy plans. Participants were randomly assigned to treatment and control conditions, as detailed below].
+
+<br>
 
@@
 
-Now, we would like to ask you a few general questions about your interest in environmental issues.
+**Now, we would like to ask you a few general questions about your interest in environmental issues.**
 
@@
 7. Invest much more
+
+**In which residential area do you currently live?**
+
+1. North
+
+2. Haifa and the Krayot
+
+3. Center
+
+4. Tel Aviv
+
+5. Lower Galilee
+
+6. Jerusalem
+
+7. Judea and Samaria
+
+8. South
+
+**What is the name of the locality where you live today? _________________**
+
+**In your opinion, what is the most disturbing environmental problem in your area? ________________________________________**
+
+[Control]
+
+<br>
+
+**Now, we would like to ask you a few general questions about your area of occupation**
+
+**In which sector are you currently employed:?**
+
+1. Private sector
+
+2. Public sector
+
+3. Third Sector
+
+4. Other
+
+**What is your field of profession/study? ______________**
+
+**To what extent do you think your profession is interesting?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**To what extent do you follow topics related to your area of occupation in the media and/or social networks?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**Compared to the current situation, do you think the government should assist more or less to promote your field of occupation?**
+
+1. Assist much less
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Assist much more
+
+**What, in your opinion, might attract people to choose your occupation?? _________________________________________**
+
+---
+
+**Next, we will present you two policy plans on specific environmental issues.
+The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.**
+
+**At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.**
+
+[Participants are then presented with the two policy plans (air-pollution and recycling), in a random order.
+See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]
+
+**Now, we'd like to ask you a few questions about your position on the policy for "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay":**
+
+**State to what extent do you agree with each of the following sentences.**
+
+**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the actions mentioned in the policy plan were designed in a professional manner**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the policy plan is in the interest of citizens**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens.**
+
+**I believe that EPM made an honest attempt to design a good policy plan**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+---
+
+**The following sentences describe the way in which you read the latest policy plan that regarded to "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay".**
+
+**State to what extent do you agree with each of the following sentences.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I paid much attention to reading the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I skimmed the actions in the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I tried to thoroughly understand the the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**While going through the policy plan I was thinking about other things which are not related to it.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**I tried to think how the policy plan will personally affect me.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
+**Try recalling the content of the latest policy plan.**
+[Each subjects was asked about the latest policy plan presenter to her]
+
+**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce air pollution in Haifa Bay?**
+
+1. Supervision on the factories
+
+2. Clean air area
+
+3. Investment in public relations
+
+4. The ammonia tank
+
+5. I can not remember
+
+**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce waste and increase recycling?**
+
+1. Supervision on the manufacturers
+
+2. compulsory charge on bags
+
+3. Investment in public relations
+
+4. plastic bottles
+
+5. I can not remember
+
+**To what extent did you feel that the policy on "reducing waste and increasing recycling" is personally relevant to you?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**To what extent did you feel that the policy on "Reducing the air-pollution in the Haifa-Bay" is personally relevant to you?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**In order to make sure you read the question carefully, please type the number 9 under "Other"?**
+
+1. Very little
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+8. Other: ______
+
+---
+
+**We would like to ask you a few general questions:**
+
+**HWhat is your age?**
+10----20----30----40----50----60----70----80
+
+**What is your highest level of education?**
+
+1.	Primary education or less
+
+2.	Partial secondary education
+
+3.	High education without high school diploma
+
+4.	High education with high school diploma
+
+5.	Non-academic tertiary education
+
+6.	Partial academic degree
+
+7.	Full academic degree (first degree)
+
+8.	Full academic degree (second degree or higher).
+
+**According to Israel's Central Bureau of Statistics the monthly average net income per household is approximately 15,500 NIS. Is your income: **
+
+1.	Far below average
+
+2.	Slightly below average
+
+3.	Near average
+
+4.	Slightly above average
+
+5.	Far above average
+
+**Are you a home owner?**
+
+1. Yes
+
+2. No
 
@@
 
-**What is the name of the locality where you live today?**
-
-**In your opinion, what is the most disturbing environmental problem in your area?**
-
-[Control]
-
-Now, we would like to ask you a few general questions about your area of occupation
-
-**In which sector are you currently employed:?**
-
-1. Private sector
-
-2. Public sector
-
-3. Third Sector
-
-4. Other
-
-**What is your field of profession/study?**
-
-**To what extent do you think your profession is interesting?**
-
-1. Very little
+**What is your place of residence? ___________**
+
+**Are you or one of your first-degree relatives working (or worked) in one of the factories in the Haifa Bay industrial area?**
+
+1. No
+
+2. Yes
+
+**State the name of the place where you lived at high-school graduation: ____________**
+
+**Area where you are currently working/studying?**
+
+1. North
+
+2. Haifa and the Krayot
+
+3. Center
+
+4. Tel Aviv
+
+5. Lower Galilee
+
+6. Jerusalem
+
+7. Judea and Samaria
+
+8. South
+
+**Gender**
+
+1.	Man
+
+2. Woman
+
+3.	I prefer not to answer
+
+**What is the age of your oldest son/daughter?**
+
+1. 0-6
+
+2. 7-12
+
+3. 13-18
+
+4. 19 or more
+
+5. I don't have any children
+
+**Is Hebrew your native language?**
+
+1. Yes
+
+2. No
+
+---
+
+[The following section is a manipulation check for the symbols]
+
+<br>
+
+[For subjects assigned to the real symbols]:
+**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**
+
+**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+
+1. Not at all
 
@@
 
-**To what extent do you follow topics related to your area of occupation in the media and/or social networks?**
-
-1. Very little
+**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**
+
+1. Not at all
 
@@
 
-**Compared to the current situation, do you think the government should assist more or less to promote your field of occupation?**
-
-1. Assist much less
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Assist much more
-
-**What, in your opinion, might attract people to choose your occupation??**
+**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much:
+
+<br>
+
+[For subjects assigned to the fake symbols]:
+**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**
+
+**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.**
+
+[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much:
+
+<br>
+
+[For subjets assigned to the no symbols]:
+
+**Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.**
+
+[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]
+
+**When you see the image, what does it make you feel?**
+
+1. Very negative feeling
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feeling
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much
+
+**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
+
+1. Not at all
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very much:
 
@@
 
-Next, we will present you two policy plans on specific environmental issues.
-The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.
-
-At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.
-
-[Participants are presented with the two policy plans. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]
-
-Now, we'd like to ask you a few questions about your position on the policy for ["Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay"]:
-
-**State to what extent do you agree with each of the following sentences.**
-
-**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I believe that the actions mentioned in the policy plan were designed in a professional manner**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I believe that the policy plan is in the interest of citizens**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens.**
-
-**I believe that EPM made an honest attempt to design a good policy plan**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
----
-
-[Questions about elaboration and personal relevance]
-
-The following sentences describe the way in which you read the latest policy plan that regarded to ["Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay"].
-
-**State to what extent do you agree with each of the following sentences.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I paid much attention to reading the policy plan.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I skimmed the actions in the policy plan.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I tried to thoroughly understand the the policy plan.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**While going through the policy plan I was thinking about other things which are not related to it.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-**I tried to think how the policy plan will personally affect me.**
-
-1. Weakly agree
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Strongly agree
-
-Try recalling the content of the latest policy plan.
-[Each subjects was asked about the latest policy plan presenter to her]
-
-**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce air pollution in Haifa Bay?**
-
-1. Supervision on the factories
-
-2. Clean air area
-
-3. Investment in public relations
-
-4. The ammonia tank
-
-5. I can not remember
-
-**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce waste and increase recycling?**
-
-1. Supervision on the manufacturers
-
-2. compulsory charge on bags
-
-3. Investment in public relations
-
-4. plastic bottles
-
-5. I can not remember
-
-**To what extent did you feel that the policy on "reducing waste and increasing recycling" is personally relevant to you?**
-
-1. Very little
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-**To what extent did you feel that the policy on "Reducing the air-pollution in the Haifa-Bay" is personally relevant to you?**
-
-1. Very little
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-**In order to make sure you read the question carefully, please type the number 9 under "Other"?**
-
-1. Very little
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-8. Other: ___
-
----
-
-[Demographic questions]
-
-We would like to ask you a few general questions:
-
-**How old are you?**
-
-**What is your highest level of education?**
-
-1.	Primary education or less
-
-2.	Partial secondary education
-
-3.	High education without high school diploma
-
-4.	High education with high school diploma
-
-5.	Non-academic tertiary education
-
-6.	Partial academic degree
-
-7.	Full academic degree (first degree)
-
-8.	Full academic degree (second degree or higher).
-
-**According to Israel's Central Bureau of Statistics the monthly average net income per household is approximately 15,500 NIS. Is your income: **
-
-1.	Far below average
-
-2.	Slightly below average
-
-3.	Near average
-
-4.	Slightly above average
-
-5.	Far above average
-
-**Are you a home owner?**
-
-1. Yes
-
-2. No
-
-**In which residential area do you currently live?**
-1. North
-
-2. Haifa and the Krayot
-
-3. Center
-
-4. Tel Aviv
-
-5. Lower Galilee
-
-6. Jerusalem
-
-7. Judea and Samaria
-
-8. South
-
-**What is your place of residence?**
-
-**Are you or one of your first-degree relatives working (or worked) in one of the factories in the Haifa Bay industrial area?**
-
-1. No
-
-2. Yes
-
-**State the name of the place where you lived at high-school graduation**
-
-**Area where you are currently working/studying?**
-
-1. North
-
-2. Haifa and the Krayot
-
-3. Center
-
-4. Tel Aviv
-
-5. Lower Galilee
-
-6. Jerusalem
-
-7. Judea and Samaria
-
-8. South
-
-**Gender**
-
-1.	Man
-
-2. Woman
-
-3.	I prefer not to answer
-
-**What is the age of your oldest son/daughter?**
-
-1. 0-6
-
-2. 7-12
-
-3. 13-18
-
-4. 19 or more
-
-5. I don't have any children
-
-**Is Hebrew your native language?**
-
-1. Yes
-
-2. No
-
----
-
-[Manipulation check for symbols]
-
-[For real symbols]:
-Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.
-
-This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"
-
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"
-
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much:
-
-[For fake symbols]:
-Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.
-
-This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"
-
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"
-
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.
-
-[Respondents are displayed with the two "real" images, and then asked the following two questions]
-
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much:
-
-[For no symbols]:
-
-Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.
-
-[Respondents are displayed with the two "real" images, and then asked the following two questions]
-
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much
-
-**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**
-
-1. Not at all
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very much:
-
----
-
-[Debrief]
-
-Thank you very much for participating in the study.
-
+**Thank you very much for participating in the study.
 Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently.
 The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy.
-[For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]
+[For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]**
 

### 2018-07-01 paper2_APPENDIX.Rmd
Add files via upload

@@
 
+---
+
 #Contents:
@@
 5. English translation of the survey experiment.
+
+---
 
@@
 
-In the tables below, I present additional robust analyses for the effect of symbols on trust in policy and its interaction with the information of the policy plans.
-In **Table A3**, I replicate table 1 of the main paper on the full, unfiltered sample, excluding subjects who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
-In **Table A4**, I add a set of control variables.
+In the tables below, I report the results of additional robust analyses testing the effect of the manipulation of symbols on trust in policy and its interaction with the manipulation of information in policy plans.
+**Table A3** replicates table 1 of from the paper, while adding those subjects who were filttered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
+In **Table A4**, replicate Table 1 while adding a set of control variables.
 In **Table A5** and **Table A6**, I exclude those subjects who did not recognize the real symbols which were included in the communications.
 Table A5 excludes those who did not recognize the campaign images (n_subjects = `r SVIVA2_comb_robust_3 %>%distinct(IP) %>% nrow()`) and Table A6 excludes those who did not recognize EPM's logo (n_subjects = `r SVIVA2_comb_robust_4 %>%distinct(IP) %>% nrow()`).
-Finally, in **Table A7**, I add interactions with the policy plan, to examine whether the effect of the symbols were significanly different for these two policies.
+Finally, in **Table A7**, I examine whether the effect of the symbols were significanly different for the two policies, by adding the interactions with the policy plan.
 All these analyses are random-effect GLS regressions clustered at the subject level, similarly to the main models presented in the paper.
-
-In all these supplementary analyses, the main effect of the real symbols on trust in policy is significant, and the interaction bewteen the real symbols and the weak inforamtion remains positive and significant.
+In all these supplementary analyses, the effects of the real symbols and their interaction with information are consistent with the main models presented in the paper.
+The main effect of the real symbols on trust in policy is significant, and the interaction bewteen the real symbols and the weak inforamtion remains positive and significant.
 
@@
           type="html",style = "apsr",
-          dep.var.labels=c("Trust in policy (combined)"),
+          dep.var.labels=c("Trust in policy"),
           covariate.labels=c("Real symbols",
@@
           type="html",style = "apsr",
-          dep.var.labels=c("Trust in policy (combined)"),
+          dep.var.labels=c("Trust in policy"),
           initial.zero = FALSE,
@@
           type="html",style = "apsr",
-          dep.var.labels=c("Trust in policy (combined)"),
+          dep.var.labels=c("Trust in policy"),
           order = c(2,3,4,8,9,1,5,6,7,10,11),
@@
 
-**Greetings, We are researchers from the Department of Political Science at the Hebrew University.
+**Greetings,**
+
+**We are researchers from the Department of Political Science at the Hebrew University.
 The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy.
@@
 
-**Now, we would like to ask you a few general questions about your area of occupation**
-
-**In which sector are you currently employed:?**
+**Now, we would like to ask you a few general questions about your area of occupation.**
+
+**In which sector are you currently employed?**
 
@@
 
-**What, in your opinion, might attract people to choose your occupation?? _________________________________________**
+**What, in your opinion, might attract people to choose your occupation? _________________________________________**
 
@@
 
-**HWhat is your age?**
+**What is your age?**
+
 10----20----30----40----50----60----70----80
@@
 **In which residential area do you currently live?**
+
 1. North
@@
 
-You can review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.
+**You may review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.**
 

### 2018-07-01 paper2_information and symbols_01.Rmd
Add files via upload

@@
 Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
-Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
+Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard the content of logically unpersuasive information that would have otherwise decreased their trust.
 I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
 The results confirm that symbolic elements in communications increase citizens' trust.
-The effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to scrutinize their content.
+The effect was stronger among those who were exposed to the logically unpersuasive policy plans, yet distracted by the symbols and thus less inclined to scrutinize their content.
 I discuss the implications of these findings for democratic responsiveness and accountability.*
@@
 
-Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their undervaluation of public-service performance.
+Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their underestimation of public-service performance.
 One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens.
@@
 
-The public administration research on the effect of government public communications on citizens attitudes has focused mostly on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
+Extant public administration research on the effect of government public communications on citizens attitudes has mostly focused on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
@@
 This research gap has normative significance.
-Whereas the responsiveness of citizens to substantive information is perceived favorably from a normative view of democratic theory, the potential effect of symbolic elements can be problematic.
+Whereas the responsiveness of citizens to substantive information is perceived favorably from a democratic theory standpoint, the effect of symbolic elements can be problematic.
 One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
@@
 Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
-*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard negative of logically unpersuasive content that would have otherwise decreased their trust.
+*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard the content of logically unpersuasive information that would have otherwise decreased their trust.
 
@@
 I find that the symbolic elements increased citizens' trust in these policies.
-In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, who were distracted by the symbols and thus were less inclined to think about its content.
+In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, yet less inclined to think about the policy content due to distraction by the symbols.
 I discuss the theoretical and normative implications of these findings.
@@
 28-29].
-My focus is on those symbols that are strategically used by government organizations in their public communications, and are designed to distinguish organizations and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
+My focus is on those symbols that are strategically used by government organizations in their public communications, are designed to distinguish them and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
 Prominent examples are unique logos, colors associated with specific meanings, icons, images, and the use of celebrities as endorsers.
@@
 His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
-@teodoro_2018 suggested that the name of US federal agencies not only represents information about their activities, but may also carry specific symbolic meaning and affect that can shape citizens' support for government policy (depending on citizens' political party identification).
+@teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and affect that can shape citizens' support for government policies (depending on citizens' political party identification).
 These two studies provide examples for the role of symbols in shaping citizens' attitudes.
@@
 @alonbarkat_2017 examined Israeli citizens' trust in the Israel Electricity Corporation, a state owned company, and it's shaping by their exposure to comic cartoon figures that were routinely presented in the organization's public campaigns.
-They compared between citizens who were personally exposed to prolonged power outages, and others who were not.
+They compared citizens who were personally exposed to prolonged power outages and others who were not.
 They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations).
@@
 Consider for instance a text that contains a series of logical arguments supporting a certain position.
-Those at the high end of the continuum would regard this text as arguments, and systematically scrutinize it based on its logical persuasive quality (central route processing).
+Those at the high end of the continuum would regard this text as argumentation, and systematically scrutinize it based on its logical persuasive quality (central route processing).
 Conversely, those at the low end of the continuum are likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
@@
 Positive mood (compared with neutral or negative moods) reduces people's cognitive ability and attenuates their motivation to think, due to their desire to maintain their positive mood and avoid message processing that would depress it [@worth_1987; @mackie_1989; @bless_1990; @schwarz_1991; @petty_2015; but see: @wegener_1995].[^footnote_elm_factors] Affecting the amount of thinking can cause attitude change in interaction with elements in the communication that can function as arguments or peripheral cues.
-Decreasing the amount of thinking weakens the effect the substantive arguments and enhances the effect of peripheral cues (and vice versa).
+Decreasing the amount of thinking weakens the effect of substantive arguments and enhances the effect of peripheral cues (and vice versa).
 
@@
 Elements in communications can also function as factors that affect people's motivation and/or ability to think.
-For example, Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986]; The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008].
+For example, Background music in commercials can distract people and prevent them from scrutinizing their content [@park_1986].
+The use of humor in television shows stimulates positive mood and reduces people's ability and motivation to scrutinize their substantive arguments [@nabi_2007; @young_2008].
 Hence, elements can have more than one function, and can shape attitudes through several mechanisms.
 They can serve both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
-Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuades people directly through the peripheral route, yet at the same time they can also as factors that reduce elaboration.
+Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuades people directly through the peripheral route, yet at the same time they can also act as factors that reduce elaboration.
 Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]
@@
 information on poor performance) and weak arguments (e.g.
-logically unpersuasive description of their policy plans).
+logically unpersuasive description of their policy plans).[^footnote_interaction_strong_information]
 
@@
 The latter expectation entails an interaction between symbols and the substantive information in the communications.
-Symbolic elements are likely to increase citizens' trust insofar as they reduce citizens' inclination to scrutinize information that would have decreased their trust.
+
+[^footnote_interaction_strong_information]: Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
+Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction.
 
@@
 
->*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
-
->*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
-
->*H<sub>3</sub> - Symbolic elements are likely to decrease the amount of thinking about the content of the communication.*
-
->*H<sub>4</sub> - The abovementioned conditioned effect of symbolic elements on citizens' trust is likely to be mediated by the decrease in the amount of thinking (a moderated mediation hypothesis).*
+*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
+
+*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
+
+*H<sub>3</sub> - Symbolic elements are likely to decrease the amount of thinking about the content of the communication.*
+
+*H<sub>4</sub> - The abovementioned moderated effect of symbolic elements on citizens' trust H<sub>2</sub> is likely to be mediated by their decreasing effect on citizens’ amount of thinking H<sub>3</sub> (a moderated mediation hypothesis).*
 
@@
 <br>
-
-Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
-Nevertheless, one can make the argument that neutralizing the effect of "positive" information with symbols may not actually yield significant differences, since citizens are more likely to "punish" bureaucracies for publishing negative information than to "praise" them for publishing positive information [@james_2011; @nielsen_2017; @james_2017b].
-Congruently, the effect of positive information (versus a medium level) is likely to be relatively small, and hence neutralizing this effect may not make much difference.
-Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction.
 
@@
 
-In addition to the above-mentioned hypotheses, the experiment is also designed to test an additional set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications.
+In addition to the above-mentioned hypotheses, the experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and the perceived personal relevance of communications.
 The selection of policy plans and the construction of the population sample were designed to account for variation in that variable.
-In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction between symbols and information.[^footnote_relevance_paper]
+In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the interaction between symbols and information.[^footnote_relevance_paper]
 
@@
 
-Empirically, I focused on the case of the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, both at the national and local levels.
+The empirical setting of this experiment relates to the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, at the national and local levels.
 I analyzed the effects of informative and symbolic elements in EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
@@
 
-Methodologically, EPM makes a good case for this study since has invested greatly over the past years in public communications.
+Methodologically, EPM makes a good case for this study due to its significant investment, over the past years, in public communications.
 In these various communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
@@
 The first symbolic element is the unique brand logo of the EPM (image a.
-in figure 1).
-This logo consists of pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second symbolic element in which I focused is the green color, which is strongly associated with taking care of the environment.
+in figure 2).
+This logo consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second symbolic element on which I focused is the green color, which is strongly associated with taking care of the environment.
 The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity" [@vandenbosch_2005].
@@
 The survey was presented to the participants as a study about citizens' attitudes regarding environmental policy issues.
-The participants were first asked pre-manipulation questions about their political ideology and their perceptions about the pubic sector.[^footnote_relevance_manipulation] Thereafter, they were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
-The policy plans regarded to reducing air-pollution in the Bay of Haifa (an area in Israel) and reducing domestic waste and increasing recycling.
+The participants were first asked to respond to pre-manipulation questions about their political ideology and their perceptions of the pubic sector.[^footnote_relevance_manipulation] Thereafter, they were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
+The policy plans regarded reducing air-pollution in the Bay of Haifa (an area in the north of Israel) and reducing domestic waste and increasing recycling.
 The two policy plans were presented to each subject in a random order.
@@
 
-Per each policy, the subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
+Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
 logically persuasive policy plan) or weak policy (i.e.
 logically unpersuasive).
-The policy activities which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
-The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures which are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were increasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
+Each subject, moreover, was exposed to one strong and one weak policy communication.
+For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
+The actions which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
+The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures that are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
+For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were decreasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
 The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
-For each subject, one of the two policies was strong and the other was weak.
-For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
-
-In addition to information manipulation, the participants are randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment (real symbols), control no symbols and control fake symbols.
+
+In addition to information manipulation, the participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
 In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
@@
 The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols to that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo.
+Accordingly, I specifically designed the "fake" symbols so that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo.
 The symbols conditions are displayed in **Appendix B**.
@@
 The survey experiment was conducted online through Qualtrics Survey Software.
-To subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*.
+The subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*.
 The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people.
@@
 These filters are not significantly associated with the experimental conditions.
-Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subjects evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb%>%nrow()` observations nested within these `r N_1` subjects.
+Ultimately, following this rigorous screening, I ended up with a sizable sample of `r N_1` subjects (Mean age = `r SVIVA2_01%>%summarise(mean(AGE,na.rm=T))%>%max()%>%round(1)`, `r SVIVA2_01%>%summarise(mean(GENDER,na.rm=T)*100)%>%max()%>%round(1)`% women).[^footnote_sample_areas] Because each subject evaluated two different policy plans, my dataset has a multilevel structure of `r SVIVA2_01_comb%>%nrow()` observations nested within these `r N_1` subjects.
 
@@
 
-My main independent variables are the above mentioned manipulations for information and symbols, and the interaction between them.
-My outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
+The main independent variables are the above mentioned manipulations for information and symbols, and the interaction between them.
+The outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
 This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_waste_trust`), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard variation is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`.
+The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard Deviations is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`.
 Higher levels of trust are associated with higher trust in government, left-wing ideology and lower levels of education.
-In addition to measuring participants trust in each policy, per each subject, I also calculated the delta between her trust in the strong and weak policy plans which were presented to her (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`).
-I used this Trust in policy delta to analyze the interaction between symbols and information within subjects.
+In addition to measuring participants trust in each policy, I also calculated the delta of each subject’s trust in the strong and weak policy plans that were presented to them (*Mean* = `r SVIVA2_01%>%summarise(mean(WITHIN_DELTA))%>%max()%>%round(2)`, *SD* = `r SVIVA2_01%>%summarise(sd(WITHIN_DELTA))%>%max()%>%round(2)`, *Median* = `r SVIVA2_01%>%summarise(median(WITHIN_DELTA))%>%max()%>%round(2)`).
+I use this Trust in policy delta to analyze the interaction between symbols and information within subjects.
 
@@
 I begin by examining my first and second hypotheses, that regard the effect of symbols on trust and its interaction with information.
-Thereafter, I will examine hypotheses 3 and 4, that regard the mediating role on elaboration.
-For each section, I conducted both *between-subjects* and *within-subjects* analyses.
+Thereafter, I will examine hypotheses 3 and 4, that regard the mediating role of elaboration.
+For each section, I conduct both *between-subjects* and *within-subjects* analyses.
 
@@
 
-According to my first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans.
+According to the first hypothesis, I expect that the real symbols condition will have a positive main effect on subjects' trust in the policy plans.
 According to my second hypothesis, I expect a positive interaction between the real symbols and weak policy plan.
@@
 The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), and at the 90% level compared with the fake symbols (`r mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`]).
-These differences are equivalent to `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` and `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` standard variations, respectively.
+These differences are equivalent to `r ((mod_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` and `r ((mod_1.1.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())/sd_trust)%>%round(2)%>%abs()` standard deviations, respectively.
 The graphic elements in the fake symbols condition also increased participants' trust, but to a lesser extent, presumably due to their unfamiliarity, and their weaker positive affect.
@@
 In Model 1.3, the interaction between weak policy and real symbols is positive and significant, whereas the interaction with the fake symbols is insignificant.
-The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] Compared with the no symbols and fake symbols, respectively).
+The interpretation of this model suggests that the real symbols had a greater effect on trust when the policy plan was weak (*Coef* = `r mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_2%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`] and `r mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_1.3.r_3%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`] compared with the no symbols and fake symbols, respectively).
 When added to the strong policy plan, the effect of the real symbols is weaker, and significant only compared with the no symbols condition (*Coef* = `r mod_1.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)`, *p*<.1, one-tailed).
@@
 Altogether, the above between- and within-subject analyses largely support my first two hypothesis.
-They suggest that familiar symbolic elements in communications increase citizens' trust in policies which are presented, and that the effect is greater the less logically persuasive is the information in the communications.
-Symbols attenuate the negative effect of weak or logically unpersuasive information in communications.
+They suggest that familiar, and to a lesser extent none familiar, symbolic elements in communications increase citizens' trust in policies, and that the effect is greater for logically unpersuasive information.
 In other statistical models, shown in the supplementary appendix, I tested additional specifications, including analyzing the unfilterred sample, adding control variables, excluding subjects who did not recognize the real symbols and adding interactions with the policy plans.
 In all these robust analyses, the main effect of the real symbols remains positive and significant, and the interaction between the real symbols and the weak information remains positive and significant.
-
-How can we explain the finding that the real symbols only had a marginally significant effect on participants' trust in the strong policy, compared with the no logo, and did not increase their trust compared with the fake logo (Model 1.3)?
-One tentative explanation could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
-Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
-If this explanation holds, then result will be a ceiling effect.
-This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
-Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceiling_effect]
-
-[^footnote_ceiling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
-The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
-the lower 25% observations).
-In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e.
-the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points.
-In the strong policy condition, we can find similar pattern of decreasing marginal effect.
-The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e.
-the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.
 
@@
 Based on my third hypothesis, I expect to find a negative effect of the real symbols on these two measures.
-Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols of trust under the weak policy, but not under the strong policy (see Figure 1).
+Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols on trust under the weak policy, but not under the strong policy (see Figure 1).
 
@@
 In **Table 2**, I test the effects of the real symbols on the elaboration measures via regression analyses.
-I regressed each measure on the symbols manipulation (Models 2.1, 2.3), and than added the information manipulation (Models 2.2, 2.4).
+I regressed each elaboration measure on the symbols manipulation (Models 2.1, 2.3), and then added the information manipulation (Models 2.2, 2.4).
 The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in table 1.
@@
   theme_classic()+
-  #geom_boxplot(width=0.25,color = "gray70")+
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
@@
 **Table 3** displays the results of the causal mediation of reaction time (log) and memory test, under the weak policy plans.
+The analyses of reaction time includes those observations where subjects received a weak policy plan (i.e.
+one observation per each subject, *n* = `r SVIVA2_01_comb%>%filter(INFORMATION_weak==1)%>%nrow()`).
+The sample for the analyses of the memory test is smaller, due to its restriction to those weak policy plans which were presented second in order (*n* = `r SVIVA2_01_comb%>%filter(INFORMATION_weak==1,ORDER==2)%>%nrow()`).
 
@@
 The results of the within subjects mediation analysis similarly supports the moderated mediation hypothesis.
-The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction the time and the memory score.
+The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction time and the memory score.
 With respect to the reaction time, the estimated proportional mediation is `r (table_med_RT__nosymbol_delta["Prop.
@@
 A growing body of Public-Administration research seeks to assess whether and how government organizations can increase citizens' trust through direct communications with citizens.
-This study contributes to this discussion, by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect.
-Using a rigorous experimental design, embedded in a realistic setting focused on the case of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications.
-To the best of my knowledge, this is the first study to explore this interactions in the context of government communications.
+This study contributes to this discussion by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect.
+Using a rigorous experimental design, embedded in a realistic setting of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications.
+To the best of my knowledge, this is the first study to explore this interaction in the context of government communications.
 
@@
 The latter interaction is partly explained by the negative effect of the symbols on the elaboration of the policy plans.
-These findings are based the analyses of the responses of more than `r (SVIVA2_01%>%nrow()%>%round(-2))-100` participants to two different policies, and are robust for various model specifications.
-Moreover, they are evidenced in both between- and within-subjects analysis.
+These findings are based on analyses of the responses of more than `r (SVIVA2_01%>%nrow()%>%round(-2))-100` participants to two different policies, and are robust for various model specifications.
+Moreover, they are evidenced in both between- and within-subjects analyses.
 These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, they evoke general positive feelings that are transferred to the specific organizations and policies.
 Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses.
-These two supplementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986; @petty_2011].
-
-Certainly, we must be cautious when drawing general conclusions from our findings.
+These two complementary mechanisms are theorized using the framework of the social psychology elaboration likelihood model [@petty_1986; @petty_2011].
+
+Still, one limitation on the experimental findings regards the effect of the symbols on citizens' trust in the strong policy plan, which was relatively weak and marginally significant (Regression model 1.3).
+One tentative explanation for this could be that symbolic elements are more effective in shifting people from low to medium levels of trust, than shifting them from medium to high levels.
+Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
+If this explanation holds, then result will be a ceiling effect.
+This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
+Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceiling_effect]
+
+[^footnote_ceiling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
+The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
+the lower 25% observations).
+In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e.
+the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points.
+In the strong policy condition, we can find similar pattern of decreasing marginal effect.
+The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e.
+the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.
+
+Certainly, we must be cautious when drawing general conclusions from these findings.
 This study focuses, empirically, on one public organization, characterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
@@
 In addition, this study focuses on policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
-Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information on good/bad outcomes.
+Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information about good/bad outcomes.
 Another limitation of the study regards the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
@@
 Most importantly, my findings highlight the significant role of branding and symbolic communication in shaping citizens' attitudes about government.
-Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abounded research on their responses to information.
+Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abundant research on their responses to information.
 Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
@@
 Moreover, it becomes especially problematic when symbols are used by poorly performing organizations, or organizations that lack professional expertise.
-It those cases, symbolic elements can mitigate justified public criticism of government failures.
-Ultimately, by preserving citizens' trust in them and escaping from public blame, organizations can nurture their long-term positive reputation, which provides them political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
+In those cases, symbolic elements can mitigate justified public criticism of government failures.
+Ultimately, by preserving citizens' trust in them and escaping public blame, organizations can nurture their long-term positive reputation, which provides them with political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
 Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, organizations can also use it as a means to undermine them.
@@
 Finally, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
-The participants of these studies, including this particular one, have relatively high motivation to elaborate on the information that scholars presented them, because they may assume that they will be asked about it afterwards.
+The participants of these studies, including this study, have relatively high motivation to elaborate on the information that scholars present them, because they may assume that they will be asked about it afterwards.
 In case they receive payment or other compensation for their participation, this further increases their motivation.
 By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they probably also have lower ability to do so, given the high competition on their time and attention.
-Accordingly, their responses to performance information will less affected by asymmetrical processing of information, because most of them are not likely to process this information in the first place.
-Instead, most of them will rely on simple cues and heuristic shortcuts.
-I expect, tentatively, that these differences exacerbate biases due to partisan and political ideology [@james_2017a; @baekgaard_2016] and implicit attitudes about the public-sector [@marvel_2015; @marvel_2015a; @hvidman_2016], while attenuating the role of negativity bias [@nielsen_2017; @olsen_2017].
-Future studies may empirically explore these interactions.
+Accordingly, whereas previous studies have emphasized the effects of cognitive biases in citizens' processing of information [@james_2017a; @baekgaard_2016; @marvel_2015; @marvel_2015a; @hvidman_2016; @nielsen_2017; @olsen_2017], one could question the generalizability of these effects to real world settings, where people are less inclined to process the information in the first place.
 Regardless, scholars should also take to account this methodological issue when designing survey experiments, and attempt to simulate real world conditions, as much as possible.

### 2018-07-01 SVIVA_exp2_dm_03.R

@@ -24,6 +24,7 @@ SVIVA2_raw[is.na(SVIVA2_raw)] <- 0
 SVIVA2_00 = SVIVA2_raw %>%
   dplyr::select(V4,V5) %>%
   mutate(IP = SVIVA2_raw$V6,
+         USER_ID = SVIVA2_raw$i.user3,
          START_DATE = dmy_hm(SVIVA2_raw$V8),
          END_DATE = dmy_hm(SVIVA2_raw$V9)) %>%  
          mutate(TIMER_total = as.integer(END_DATE-START_DATE),
@@ -509,7 +510,7 @@ SVIVA2_01 = SVIVA2_00 %>%
        
 
 SVIVA2_01_comb = SVIVA2_01 %>% 
-  dplyr::select(IP,AREA,AREA_names,
+  dplyr::select(IP,USER_ID,AREA,AREA_names,
       RELEVANCE_exp,RELEVANCE_exp_n,
       SYMBOL,SYMBOL_n,
       INFORMATION_air,INFORMATION_air_n,
@@ -525,7 +526,13 @@ SVIVA2_01_comb = SVIVA2_01 %>%
       GOV_TRUST,
       GENDER,
       AIR_order,
-      WASTE_order) %>% 
+      WASTE_order,
+      IDEOLOGY,
+      INCOME,
+      EDUCATION,
+      RECOGNIZE_SVIVA_logo,
+      RECOGNIZE_air_real,
+      RECOGNIZE_waste_real) %>% 
   gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
   mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
                               INFORMATION_waste),
@@ -544,7 +551,8 @@ SVIVA2_01_comb = SVIVA2_01 %>%
          SYMBOL_t = factor(Recode(SYMBOL,"1=2;2=1")),
          SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
          SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")),
-         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order))
+         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order),
[…]

### 2018-07-21 paper2_information and symbols_02.Rmd
Add files via upload

--- 2018-07-01 paper2_information and symbols_01.Rmd
@@
 *Effective public communications have been proposed as a remedy for citizens' distrust in government.
-The studies that explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies.
+Those studies that have explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies.
 Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g.
 logos, images and celebrities).
-Still, we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information.
-Building on the Elaboration Likelihood Model (ELM) from social psychology, I hypothesize that symbolic elements can increase citizens' trust via two mechanisms: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
-Second, indirectly, by leading citizens to dedicate less attention to the substantive information in the communication, and thus causing them to disregard the content of logically unpersuasive information that would have otherwise decreased their trust.
+Still we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information.
+Building on the Elaboration Likelihood Model (ELM) from social psychology I hypothesize that symbolic elements can increase citizens' trust in two ways: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
+Second, indirectly, by conducing citizens to pay less attention to the substantive information in the communication.
+As a result citizens disregard logically unpersuasive information that could decrease their trust.
 I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
 The results confirm that symbolic elements in communications increase citizens' trust.
-The effect was stronger among those who were exposed to the logically unpersuasive policy plans, yet distracted by the symbols and thus less inclined to scrutinize their content.
+The effect was stronger among those who were exposed to the logically unpersuasive policy plans.
+The latter were also distracted by the symbols and thus less inclined to scrutinize their content.
 I discuss the implications of these findings for democratic responsiveness and accountability.*
@@
 Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their underestimation of public-service performance.
-One of the main remedies which has been proposed for this problem is greater investment in direct government communications with citizens.
+One of the main remedies proposed for this is greater investment in direct government communications to citizens.
 Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
@@
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
-Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on organizations' performance and logically persuasive explanations for their policies.
+Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
 At the same time, experiment-based studies that explored the responses of citizens to substantive information revealed cognitive biases that distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
@@
 These studies demonstrated that government organizations may cause citizens to view them more favorably through familiar and well-designed symbolic elements that evoke positive associations and emotions.
-Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens trust.
-Additionally, these previous studies did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
+Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens’ trust.
+These previous studies also did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
 
@@
 Whereas the responsiveness of citizens to substantive information is perceived favorably from a democratic theory standpoint, the effect of symbolic elements can be problematic.
-One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands in tension with the normative expectation that citizens' judgments should be based on their critical thinking.
-Mainly, we should be concerned about the possibility that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
-Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in governemnt communications affect citizens' trust in government organizations and their policies?* Accordingly, *does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
+One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands against the normative expectation that citizens' judgments should be based on their critical thinking.
+We need to be aware that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
+Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in government communications affect citizens' trust in government organizations and their policies?
+Does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
 
 To address these research questions, I draw upon the social psychology Elaboration Likelihood Model (ELM).
-ELM provides a comprehensive theoretical framework for the varying psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change  [@petty_1986; @petty_2011].
-Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust via two mechanisms: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
-*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard the content of logically unpersuasive information that would have otherwise decreased their trust.
+ELM provides a comprehensive theoretical framework for various psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change  [@petty_1986; @petty_2011].
+Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust in two ways: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
+*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard the content of logically unpersuasive information that could otherwise decreased their trust.
 
@@
 
-I find that the symbolic elements increased citizens' trust in these policies.
-In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans, yet less inclined to think about the policy content due to distraction by the symbols.
+I found that the symbolic elements increased citizens' trust in these policies.
+In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans.
+They were also less inclined to think about the policy content because they were distracted by the symbols.
 I discuss the theoretical and normative implications of these findings.
@@
 These elements are widely used by businesses and political candidates to attract targeted consumers and voters.
-Yet, they can be also found in the communications of government bureaucracies with citizens, including their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.
+Yet, they can also be found in the communications of government bureaucracies with citizens, including their mass-media advertising campaigns, social media accounts, internet pages, official publications, signboards in public places and personal mail notifications to citizens.
 
@@
 His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
-@teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and affect that can shape citizens' support for government policies (depending on citizens' political party identification).
+@teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and positive/negative "affect" that can shape citizens' support for government policies (depending on citizens' political party identification).
 These two studies provide examples for the role of symbols in shaping citizens' attitudes.
-Still, they did not effectively disentangle the effects of the symbolic and informational aspects of the studied public communications.
+However, they did not effectively disentangle the effects of the symbolic and informational aspects of the public communications studied.
 
@@
 
-According to ELM, the responses of individuals to persuasive communications depends on the amount of thinking that they dedicate to the message content.
+According to ELM, the responses of individuals to persuasive communications depends on how much effort they devote to think about the content of the message (or "the amount of thinking" according to ELM terminology).
 Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
@@
 At the high end of the elaboration continuum, also called the "central route", people are likely to respond by cognitively scrutinizing the arguments central to the merits of the issue.
-At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little amount of cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories].
+At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories].
 In turn, these different persuasion mechanisms are likely to cause divergent types of attitudinal change.
-Persuasion through the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route persuasion.
-Of course, much of the time, people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.
+Persuasion via the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route.
+Of course, often people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.
 
@@
 
-ELM enables to disentangle the distinct effects of different elements in communications.
+ELM enables us to disentangle the distinct effects of different elements in communications.
 Some elements are processed differently by people at different locations along the elaboration continuum.
 Consider for instance a text that contains a series of logical arguments supporting a certain position.
-Those at the high end of the continuum would regard this text as argumentation, and systematically scrutinize it based on its logical persuasive quality (central route processing).
-Conversely, those at the low end of the continuum are likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
+Those at the high end of the continuum would regard this text as argumentation, systematically scrutinizing it based on its logical persuasive quality (central route processing).
+Conversely, those at the low end of the continuum are more likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
 Some elements provide potential cues that lack any logical quality at all.
@@
 They can serve both as variables that affect the amount of thinking and as potential peripheral cues or arguments.
-Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuades people directly through the peripheral route, yet at the same time they can also act as factors that reduce elaboration.
+Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuade people directly through the peripheral route, yet at the same time they can also act as factors that reduce elaboration.
 Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]
@@
 [^footnote_multifunction_factors]: @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
-When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide if the message is worth or needs considering.
+When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide whether the message is worth or needs considering.
 
@@
 In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and capable to do so.
-Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust through the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
+Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust via the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
 However, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly.
@@
 Symbolic elements may decrease citizens' ability and motivation to think about the message in several ways.
-First, they can cause elaboration disruption, by distracting citizens and absorbing their attention and cognitive efforts [@petty_1976; @petty_1986].
+First, they can cause elaboration disruption, by distracting citizens and capturing their attention and cognitive efforts [@petty_1976; @petty_1986].
 Second, they can decrease citizens' motivation and ability to think about the message content by creating a positive affect and placing citizens in a positive mood.
 As explained above, the postulation that positive mood decreases elaboration has been explained, in part, by a mood maintenance mechanism [@mackie_1989; @bless_1990; @schwarz_1991].
-This mechanism is particularly relevant to the context of government communications, in which thinking about the content of the message - government organizations and policies - is likely to yield negative mood among most people [@marvel_2015; @marvel_2015a; @hvidman_2016].
+This mechanism is particularly relevant to the context of government communications, in which thinking about the content of the message – government organizations and policies – is likely to yield a negative mood among most people [@marvel_2015; @marvel_2015a; @hvidman_2016].
 Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about tedious bureaucratic affairs, which would depress their positive mood.
@@
 
-In sum, I expect that:
-
-*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in the organizations and in the policies presented in the communications.*
-
-*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that would have decreased citizens' trust.*
+In summary, I expect that:
+
+*H<sub>1</sub> - Symbolic elements in public organizations' communications are likely to increase citizens' trust in those organizations and in the policies presented in their communications.*
+
+*H<sub>2</sub> - The positive effect of symbolic elements on citizens' trust is likely to be enhanced when the communication includes negative or logically unpersuasive information that could otherwise have decreased citizens' trust.*
 
@@
 
-*H<sub>4</sub> - The abovementioned moderated effect of symbolic elements on citizens' trust H<sub>2</sub> is likely to be mediated by their decreasing effect on citizens’ amount of thinking H<sub>3</sub> (a moderated mediation hypothesis).*
+*H<sub>4</sub> - The abovementioned moderated effect of symbolic elements on citizens' trust H<sub>2</sub> is likely to be mediated by their negative effect on citizens’ amount of thinking H<sub>3</sub> (a moderated mediation hypothesis).*
 
@@
 Such communications can be found in publicized reports, pamphlets, websites, new media pages and ads.
-Focusing on communication of future policy plans, as opposed to communications on performance of existing policies, enables me to utilize a real-world empirical case without compromising the reliability of the manipulation of the content.
+I focus on communication of future policy plans, as opposed to communications on performance of existing policies.
+This allows me to utilize a real-world empirical case without compromising the reliability of the manipulation of the content.
 This is because most citizens do not have prior knowledge of organizations' future policy plans, and thus they will be more willing to trust a fictional communication of an organization with regard to its future policy.
@@
 the interaction between symbols with personal relevance) are described in a separate paper.
-An English translation of the full survey is available from the supplementary appendix.
+An English translation of the full survey is available in the paper's supplementary appendix.
 
@@
 
-The empirical setting of this experiment relates to the Israeli Environment Protection Ministry (hereafter: EPM), a national level bureau responsible for the formulation, co-ordination and execution of environmental policy in Israel, at the national and local levels.
+The empirical setting of this experiment relates to the Israeli Environment Protection Ministry (hereafter: EPM) that is responsible for the formulation, co-ordination and execution of environmental policy in Israel, at the national and local levels.
 I analyzed the effects of informative and symbolic elements in EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
@@
 
-Methodologically, EPM makes a good case for this study due to its significant investment, over the past years, in public communications.
-In these various communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
+Methodologically, EPM is a good candidate for this study due to its significant investment, over the past years, in public communications.
+In these communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
 Here, I focused on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**.
-The first symbolic element is the unique brand logo of the EPM (image a.
-in figure 2).
-This logo consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second symbolic element on which I focused is the green color, which is strongly associated with taking care of the environment.
-The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity" [@vandenbosch_2005].
+The first symbolic element is the unique brand logo of the EPM (Figure 2a).
+This logo consists of a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second symbolic element which I focused on, is the color green, which is strongly associated with environmental protection.
+The EPM logo and the green color are used in almost all of EPM’s visual communications, and they represent key elements of its unique "visual identity" [@vandenbosch_2005].
 The third element is celebrity endorsements.
-Specifically, I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, that previously endorsed two salient advertising campaigns of the EPM.
-The campaign starring the comedian Tal Friedman (image b.) was launched in 2010, and included a series of advertisements in which Friedman was presented with a green grass head, and accordingly the campaign's slogan was: "starting to think green".
-The campaign starring the comedian Ido Rosenblum (image c.) was launched in 2017, and was focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.
-
-In the course of the survey experiment, I confirmed that the EPA logo and the images of the celebrities from the campaigns are familiar to the participants.
-`r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize EPA logo to some extent and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`% , respectively).
+Specifically, I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, who previously endorsed two salient advertising campaigns of the EPM.
+The campaign starring the comedian Tal Friedman (Figure 2b) was launched in 2010, and included a series of advertisements in which Friedman was presented with a head covered in green grass, and accordingly the campaign's slogan was: "starting to think green".
+The campaign starring the comedian Ido Rosenblum (Figure 2c) was launched in 2017, and focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.
+
+In the course of the survey experiment, I was able to confirm that the EPA logo and the images of the celebrities from the campaigns were familiar to the participants.
+A total of `r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize the EPA logo to some extent, and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`% , respectively).
 In robust analyses I further exclude those who do not recognize these symbols.[^footnote_prior_studies]
@@
 [^footnote_prior_studies]: In two prior online survey tests, which I conducted before the experiment, I collected further information about the affect and symbolic associations of these symbols.
-These results, which are reported in the supplementary appendix, substantiate my empirical assumption that these elements evoke positive emotions Israeli citizens, and that citizens automatically associate them with EPM and its policies.
-These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to position people in a positive mood.
-
-<br>
-**Figure 2: symbolic elements of EPM**
+These results are reported in the supplementary appendix and substantiate my empirical assumption that these elements evoke positive emotions in Israeli citizens, and that citizens automatically associate them with EPM and its policies.
+These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to evoke a positive mood in citizens.
+
+<br>
+**Figure 2: Symbolic elements of EPM**
 ![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/EPM_symbols.png) 
@@
 
-Notes:
+*Notes:*
 
@@
 c.
-Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "The reusable bag is again left at home?
+Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "Did you for forget your reusable carrier bag at home again?
 A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".
@@
 The survey was presented to the participants as a study about citizens' attitudes regarding environmental policy issues.
-The participants were first asked to respond to pre-manipulation questions about their political ideology and their perceptions of the pubic sector.[^footnote_relevance_manipulation] Thereafter, they were told that they will be presented with two government policy plans regarding specific environmental issues, obtained from EPM's official publication of its annual work plan for the year 2018.
-The policy plans regarded reducing air-pollution in the Bay of Haifa (an area in the north of Israel) and reducing domestic waste and increasing recycling.
+The participants were first asked to respond to pre-manipulation questions about their political ideology and their perceptions of the public sector.[^footnote_relevance_manipulation] Thereafter, they were told that they would be presented with two government policy plans regarding specific environmental issues, extracted from EPM's official 2018 annual work plan.
+The policy plans included reducing air-pollution in Haifa bay area in the north of Israel, reducing domestic waste and increasing recycling.
 The two policy plans were presented to each subject in a random order.
-Each policy plan included the title of the policy goal (i.e.
+Each policy plan included the title of the policy goal (e.g.
 "reducing the levels of air pollution in the Haifa bay"), followed by short descriptions of two actions to be taken by EPM in order to fulfill this goal (30-50 words each).
@@
 Each subject, moreover, was exposed to one strong and one weak policy communication.
-For example, a subject who first received a strong air-pollution policy, later received the weak recycling policy, and vice versa.
-The actions which were mentioned in the strong policy plans condition were taken from the real EPM work plan and from other reports and official sources of EPM.
+So for example a subject who first received a strong air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
+The actions which were mentioned in the condition of the strong policy plans were taken from the real EPM work plan and from other reports and official EPM sources.
 The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures that are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were decreasing the supervision of polluting factories, and raising citizens' awareness of the Ministry's efforts to improve air quality.
-The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
+For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were to decrease the supervision of polluting factories, and raise citizens' awareness of the Ministry's efforts to improve air quality.
+The full texts of the weak and strong conditions for the two policy plans is included in **Appendix A**.
 
 In addition to information manipulation, the participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the symbol treatment condition, the two policies (again, one weak and one strong) are displayed with the above-mentioned three symbolic elements: the titles and the footer are colored with green, EPM logo is displayed at the top of the page, and the celebrities' images from the campaigns are attached and labeled "EPM advertisement".
-Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags is attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy.
-In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities images.
-Finally, in the control fake-symbols condition, the green color is replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.
-The purpose of the fake-logo condition is to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols so that they will resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which can be attached to the government ministry and environmental issues.[^footnote_symbols_manipulation_checks] In that sense, it can be regarded as a placebo.
+In the symbol treatment condition, the two policies (again, one weak and one strong) were displayed with the above-mentioned three symbolic elements: the titles and the footer were colored green, the EPM logo was displayed at the top of the page, and the celebrities' images from the campaigns were attached and labeled "EPM advertisement".
+Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags was attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy.
+In the control no-symbols condition, the two policies were displayed in a minimal black and white design, and without the logo and the celebrities’ images.
+Finally, in the control fake-symbols condition, the green color was replaced with blue, the EPM logo was replaced by a fake logo and the images of celebrities from the campaigns were replaced with two edited images of unfamiliar people.
+The purpose of the fake-logo condition was to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
+Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating emotions and associations which could be attached to the government ministry and environmental issues.
+In that sense, the "fake" symbols could be regarded as a placebo.
 The symbols conditions are displayed in **Appendix B**.
 Further details about the images in the real and fake symbols conditions are found in the supplementary appendix.
-That each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
-one strong and one weak), enables me later to analyze the interaction between these two manipulations both via between- and within-subjects.
-
-[^footnote_symbols_manipulation_checks]: In two prior surveys, I empirically confirmed that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
+Each subject received two policies which were presented under the same symbol condition, but under different information conditions (i.e.
+one strong and one weak).
+This allowed me later to analyze the interaction between these two manipulations both between and within-subjects.
+
+[^footnote_symbols_manipulation_checks]: In two prior surveys, I confirmed, empirically, that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
 The results of these examinations are reported in the supplementary appendix.
 
-Each policy plan was followed by six questions questions about respondents' trust in the policy.
-Afterwards, the subjects conducted a memory test on the last policy that was presented to them, and were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans.
-Thereafter, I included an instructional manipulation check (IMC) item, which aims to assess participants’ diligence.
-After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two images of the celebrities.
+Each policy plan was followed by six questions about respondents' trust in the policy.
+Next, the subjects underwent a memory test on the last policy that was presented to them, and they were asked about the extent to which they elaborated on it and about the personal relevance of the policy plans.
+The following step included an Instructional Manipulation Check (IMC) item, intended to assess participants’ diligence.
+After a set of demographic questions, I conducted a manipulation check, in which I asked the participants whether they recognize the Ministry's logo, and the two celebrities’ images.
 Finally, the participants were debriefed about the manipulations, and the possible deception.
-An English translation of the full survey is available from the supplementary appendix.
+An English translation of the full survey is available in the supplementary appendix.
 
@@
 
-The survey experiment was conducted online through Qualtrics Survey Software.
-The subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company - *iPanel*.
-The online survey link was sent by iPanel, between 28.1-1.2.2018 to 5,077 people.
-A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+The survey experiment was conducted online using Qualtrics Survey Software.
+The subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company called *iPanel.* The online survey link was sent by iPanel, between the dates 28.1-1.2.2018 to 5,077 people.
+A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`); failure at the instructional manipulation test (n=`r filter_IMC`); surveys that were submitted in less than 3 or more than 30 minutes (n=`r filter_time`); and respondents under the age of 18 (n=`r filter_age`).
 These filters are not significantly associated with the experimental conditions.
@@
 
-[^footnote_responserate]: According to iPanel's reporting, 330 women entered the survey, but were eventually denied of access, to avoid the over-representation of women in the sample.
-Hence, the response rate, when reducing those who were denied of access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
-
-[^footnote_sample_areas]: To capture variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country.
+[^footnote_responserate]: According to iPanel's reporting, 330 women entered the survey, but were eventually denied access, to avoid the over-representation of women in the sample.
+Hence, the response rate, when reducing those who were denied access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
+
+[^footnote_sample_areas]: To capture variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country.
 The final sample consists of `r SVIVA2_01_haifa%>%nrow()` subjects from the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` from the center cities.
@@
 The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
-Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2)%>%round(2)`, which substantiates their validity.
+Accordingly, participants could receive the scores of 0 (`r filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==0)%>%nrow())/N_1*100)%>%round(1)`%), 1 (`r filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==1)%>%nrow())/N_1*100)%>%round(1)`%) or 2 (`r filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow()`, `r ((filter(SVIVA2_01_comb,MEMORY_score==2)%>%nrow())/N_1*100)%>%round(1)`%).[^footnote_elaboration] These two measures are correlated with each other (Spearman rho = `r ((cor_elaboration_air+cor_elaboration_waste)/2)%>%round(2)`), which substantiates their validity.
 
@@
 
-In addition to the above independent variables, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in government, interest in environmental issues and residence in the Haifa-Bay area.
+In addition to the independent variables above, the survey also included control items regarding respondents’ age, gender, education, income, home ownership, age of their children, political ideology, trust in government, interest in environmental issues and residence in the Haifa-bay area.
 Summary statistics and correlation matrix for all variables are available in the supplementary appendix.

### 2018-07-29 paper2_information and symbols_02.Rmd
Add files via upload

@@
 ---
-title: "The effect of symbols in government communications on citizens' trust, and its interaction with substantive information"
+title: "Can government public communications elicit undue trust? Exploring the interaction between symbols and substantive information in communications"
 author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
@@
 Still we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information.
-Building on the Elaboration Likelihood Model (ELM) from social psychology I hypothesize that symbolic elements can increase citizens' trust in two ways: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
+Building on the social psychology Elaboration Likelihood Model I hypothesize that symbols increase citizens' trust in two ways: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
 Second, indirectly, by conducing citizens to pay less attention to the substantive information in the communication.
-As a result citizens disregard logically unpersuasive information that could decrease their trust.
-I examine these expectations via a survey experiment, focusing on communications of the Israeli Environment Protection Ministry about its policy plans.
-The results confirm that symbolic elements in communications increase citizens' trust.
-The effect was stronger among those who were exposed to the logically unpersuasive policy plans.
-The latter were also distracted by the symbols and thus less inclined to scrutinize their content.
+As a result, citizens disregard logically unpersuasive information that could decrease their trust.
+I examine these expectations via a survey experiment, focusing on the Israeli Environment Protection Ministry.
+The results support the hypotheses and suggest that the effect of symbolic elements is stronger when communications include logically unpersuasive information.
 I discuss the implications of these findings for democratic responsiveness and accountability.*
@@
 One of the main remedies proposed for this is greater investment in direct government communications to citizens.
-Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@deacon_2001; @eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
+Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
 In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on contracts related to public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].
@@
 Extant public administration research on the effect of government public communications on citizens attitudes has mostly focused on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
+@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
 Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
@@
 The experiment focuses on the empirical case of the Israeli Environment Protection Ministry.
-I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information of the communications (logically persuasive vs.
+I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information in the communications (logically persuasive vs.
 unpersuasive policy plans) and by symbolic elements in them (real symbols vs.
@@
 
-By comparison with the abundant research on citizens’ responses to informative elements in public communications [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements.
+In comparison with the abundant research on citizens’ responses to informative elements in public communications [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements.
 Recently, however, a few experimental studies tackled the issue.
-@marvel_2015 analyzed US citizens' responses to a television advertisement of the public Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music.
+@marvel_2015 analyzed US citizens' responses to a television advertisement of the public US Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music.
 His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
 @teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and positive/negative "affect" that can shape citizens' support for government policies (depending on citizens' political party identification).
-These two studies provide examples for the role of symbols in shaping citizens' attitudes.
-However, they did not effectively disentangle the effects of the symbolic and informational aspects of the public communications studied.
+While these two studies provide examples for the role of symbols in shaping citizens' attitudes, they did not effectively disentangle the effects of the symbolic and informational aspects of the public communications studied.
 
@@
 They found that including the Commission’s logo significantly increased citizens' trust in these policies.
-Their results show an impressive effect size equivalent to 0.7 standard deviations.
-[^footnote_karens]
-
-[^footnote_karens]: The effect size they found was smaller with regard to the "air quality" policy compared with the "digital skills" policy which were presented (Cohen's d = 0.7 vs.
-0.6).
-Also, the effect was smaller among subjects from the Netherlands, compared with those from Belgium and Poland (Cohen's d = 0.5 vs.
-0.7).
+Their results show an impressive effect size equivalent to 0.7 standard deviations, on average.
 
@@
 Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them ("evaluative conditioning").
-They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the assessed government quality.
+They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the government quality assessed.
 
@@
 The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" communications [@petty_1986; @petty_2011].
-In addition to its general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [@petty_1983; @swasy_1985; @dotson_2000; @drge_1989; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
-Yet, thus far, the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
-
-According to ELM, the responses of individuals to persuasive communications depends on how much effort they devote to think about the content of the message (or "the amount of thinking" according to ELM terminology).
+In addition to its general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [e.g.
+@petty_1983; @dotson_2000; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
+So far however the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
+
+According to ELM, the responses of individuals to persuasive communications depends on how much effort they devote to thinking about the content of the message (or "the amount of thinking" according to ELM terminology).
 Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
@@
 In turn, these different persuasion mechanisms are likely to cause divergent types of attitudinal change.
-Persuasion via the central route is expected to be more enduring, resistant and predictive of behavior, compared with peripheral route.
-Of course, often people are located in between the two ends of the continuum, and thus persuasion is determined by a mixture of these processes.
-
-[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980], and systems 1 and 2 [@kahneman_2011].
+Persuasion via the central route is expected to be more enduring, resistant and predictive of behavior, compared with the peripheral route.
+Of course, often people are located in between the two ends of the continuum, and thus persuasion is determined by a combination of these processes.
+
+[^footnote_dual_process_theories]: The conceptual distinction between the "central and peripheral routes for persuasion" largely resembles the distinctions between heuristic and systematic processing [@chaiken_1980].
 
@@
 Continuing with the above-mentioned examples, background music and humor can serve as simple cues that persuade people directly through the peripheral route, yet at the same time they can also act as factors that reduce elaboration.
-Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).[^footnote_multifunction_factors]
-
-[^footnote_multifunction_factors]: @petty_1986 have suggested that we are more likely to find complex relations of multiple mechanisms in those situations where people are located in the middle of the elaboration continuum.
-When people are neither extremely motivated or unmotivated to think, they may rely on different elements in the communications to decide whether the message is worth or needs considering.
+Accordingly, they can affect people both directly (as peripheral cues) and indirectly (by decreasing elaboration and thus attenuating the effect of arguments and enhancing the effect of peripheral cues).
 
@@
 
-In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and capable to do so.
+In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and able to do so.
 Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust via the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
@@
 [^footnote_interaction_strong_information]: Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
-Given the focus of this study on the interaction between symbols and ill-conceived policies, the research design does not directly addresses this latter interaction.
 
@@
 
-*H<sub>4</sub> - The abovementioned moderated effect of symbolic elements on citizens' trust H<sub>2</sub> is likely to be mediated by their negative effect on citizens’ amount of thinking H<sub>3</sub> (a moderated mediation hypothesis).*
+*H<sub>4</sub> - The abovementioned moderated effect of symbolic elements on citizens' trust (H<sub>2</sub>) is likely to be mediated by their negative effect on citizens’ amount of thinking (H<sub>3</sub>) - a moderated mediation hypothesis.*
 
@@
 I focus on communication of future policy plans, as opposed to communications on performance of existing policies.
-This allows me to utilize a real-world empirical case without compromising the reliability of the manipulation of the content.
-This is because most citizens do not have prior knowledge of organizations' future policy plans, and thus they will be more willing to trust a fictional communication of an organization with regard to its future policy.
+This allows me to utilize a real-world empirical case, yet still to manipulate the content of the communication in a reliable manner.
+Most citizens do not have prior knowledge of organizations' future policy plans, and will therefore be more willing to trust a fictional communication of an organization with regard to its future policy.
 
@@
 
-[^footnote_relevance_paper]: The methodological aspects which are relevant for examining the additional hypotheses (i.e.
-the interaction between symbols with personal relevance) are described in a separate paper.
-An English translation of the full survey is available in the paper's supplementary appendix.
+[^footnote_relevance_paper]: The methodological aspects which are relevant for examining the interaction between symbols with personal relevance are described in a separate paper.
 
@@
 The empirical setting of this experiment relates to the Israeli Environment Protection Ministry (hereafter: EPM) that is responsible for the formulation, co-ordination and execution of environmental policy in Israel, at the national and local levels.
-I analyzed the effects of informative and symbolic elements in EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
+I analyzed the effects of informative and symbolic elements in the EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
 In the survey, the communications about the two policy plans, in which I manipulated the informative and symbolic elements, are presented to the participants as sections from the EPM's official publication of its annual work plan.
 
-Methodologically, EPM is a good candidate for this study due to its significant investment, over the past years, in public communications.
+Methodologically, the EPM is a good candidate for this study due to its significant investment, over the past years, in public communications.
 In these communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
@@
 In the course of the survey experiment, I was able to confirm that the EPA logo and the images of the celebrities from the campaigns were familiar to the participants.
-A total of `r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize the EPA logo to some extent, and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`% , respectively).
+A total of `r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize the EPA logo to some extent, and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`%, respectively).
 In robust analyses I further exclude those who do not recognize these symbols.[^footnote_prior_studies]
@@
 
-[^footnote_prior_studies]: In two prior online survey tests, which I conducted before the experiment, I collected further information about the affect and symbolic associations of these symbols.
-These results are reported in the supplementary appendix and substantiate my empirical assumption that these elements evoke positive emotions in Israeli citizens, and that citizens automatically associate them with EPM and its policies.
-These results also indicate that the images of the celebrity comedians from EPM campaigns are perceived as humoristic, and accordingly, they are expected to evoke a positive mood in citizens.
+[^footnote_prior_studies]: In two prior surveys, I collected further information about the affect and symbolic associations of these symbols.
+These results are reported in the supplementary appendix and substantiate my empirical assumption that these elements evoke positive emotions, and that citizens automatically associate them with the EPM.
 
@@
 c.
-Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "Did you for forget your reusable carrier bag at home again?
+Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "Did you forget your reusable carrier bag at home again?
 A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".
@@
 [^footnote_relevance_manipulation]: This section also included a manipulation of participants' perceived personal relevance.
-Participants in the treatment group were asked a series of questions about environmental government policy, whereas participants in the control group were asked instead equivalent questions about their field of occupation.
+Participants in the treatment group were asked a series of questions about environmental government policy, whereas participants in the control group were asked equivalent questions about their field of occupation.
 
@@
 The activities that were included in the weak policy plans condition were fictional, and were designed to represent measures that are likely to be perceived by subjects as extremely incompatible with achieving the policy goals, yet still sufficiently reliable.
-For instance, the proposed actions for the air-pollution strong policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were to decrease the supervision of polluting factories, and raise citizens' awareness of the Ministry's efforts to improve air quality.
+For instance, the proposed actions for the strong air-pollution policy involved increasing the supervision of polluting factories, and reducing diesel smoke emissions by vehicles, whereas the actions for the weak policy were to decrease the supervision of polluting factories, and raise citizens' awareness of the Ministry's efforts to improve air quality.
 The full texts of the weak and strong conditions for the two policy plans is included in **Appendix A**.
@@
 Each communication included the image of one celebrity: Rosenblum's image from the campaign for reducing the use of disposable bags was attached to the recycling policy; Friedman's image from the "starting to think green" campaign was attached to the air-pollution policy.
+
 In the control no-symbols condition, the two policies were displayed in a minimal black and white design, and without the logo and the celebrities’ images.
-Finally, in the control fake-symbols condition, the green color was replaced with blue, the EPM logo was replaced by a fake logo and the images of celebrities from the campaigns were replaced with two edited images of unfamiliar people.
+In the control fake-symbols condition, the green color was replaced with blue, the EPM logo was replaced by a fake logo and the images of celebrities from the campaigns were replaced with two edited images of unfamiliar people.
 The purpose of the fake-logo condition was to isolate the symbolic meaning of the EPM's graphic identifiers and distinguish it from the possible effect of their aesthetic design.
@@
 In that sense, the "fake" symbols could be regarded as a placebo.
+
 The symbols conditions are displayed in **Appendix B**.
@@
 Finally, the participants were debriefed about the manipulations, and the possible deception.
-An English translation of the full survey is available in the supplementary appendix.
+An English translation of the full survey is available in the supplementary Appendix.
 
@@
 The assignment to the different experimental groups is graphically presented in **Figure 3**.
-The experimental groups are fairly balanced with respect to demographics, and pre-manipulation variables.
+The experimental groups are balanced with respect to demographics, and pre-manipulation variables.
 Throughout the rest of the paper, I will analyze the results at the policy level, in order to simplify the analyses.
@@
 
-[^footnote_combined_analyses]: In the supplementary appendix I further replicate the analyses below, while adding the interactions between the manipulations and the policy plans.
-In these models, the interactions between the policy plans and the symbols are far from significance, with no major changes to the results.
+[^footnote_combined_analyses]: In the supplementary Appendix I further replicate the analyses below, while adding the interactions between the manipulations and the policy plans.
+The interactions between the policy plans and the symbols are far from significance, with no major changes to the results.
 
@@
 The subjects, adult Israeli citizens, were recruited via an Israeli internet research panel company called *iPanel.* The online survey link was sent by iPanel, between the dates 28.1-1.2.2018 to 5,077 people.
-A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).[^footnote_responserate] Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`); failure at the instructional manipulation test (n=`r filter_IMC`); surveys that were submitted in less than 3 or more than 30 minutes (n=`r filter_time`); and respondents under the age of 18 (n=`r filter_age`).
+A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
+Of these, I later filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`); failure at the instructional manipulation test (n=`r filter_IMC`); surveys that were submitted in less than 3 or more than 30 minutes (n=`r filter_time`); and respondents under the age of 18 (n=`r filter_age`).
 These filters are not significantly associated with the experimental conditions.
@@
 
-[^footnote_responserate]: According to iPanel's reporting, 330 women entered the survey, but were eventually denied access, to avoid the over-representation of women in the sample.
-Hence, the response rate, when reducing those who were denied access, is slightly higher  and reaches `r round((N_0)/(5077-330)*100,1)`%.
-
 [^footnote_sample_areas]: To capture variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country.
-The final sample consists of `r SVIVA2_01_haifa%>%nrow()` subjects from the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` from the center cities.
-The two areas received the exact same link to the online survey, and they were equally, randomly assigned to the experimental conditions.
 
@@
 
-[^footnote_elaboration]: In addition, I included in the survey a battery of five items that measure participants' subjective perception of their level of elaboration.
-I initially sought to use these items as an additional measure for elaboration.
-However, I decided to forgo this subjective measure, due to its lack of correlation with the reaction time and memory test score, and its possible bias by people's disinclination to admit that they did not thoroughly read the policy plans.
+[^footnote_elaboration]: In addition, I included in the survey an index for participants' perceived elaboration.
+However, I decided to forgo this subjective measure, due to its lack of correlation with the other measures, and its possible bias by social desirability.
 
@@
 I begin by examining my first and second hypotheses, that regard the effect of symbols on trust and its interaction with information.
-Thereafter, I will examine hypotheses 3 and 4, that regard the mediating role of elaboration.
+Thereafter, I will examine hypotheses 3 and 4, that deal with the mediating role of elaboration.
 For each section, I conduct both *between-subjects* and *within-subjects* analyses.
 
-##*The interaction bewteen symbols and information*
+##*The interaction between symbols and information*
 
@@
 Thereafter, in Models 2 and 3, I add the information manipulation, and the interaction between them.
-In these models, I the reference category for the symbols manipulation is the no-symbols condition.
+The reference category for the symbols manipulation is the no-symbols condition.
 
@@
           covariate.labels=c("Real symbols",
-                             "Fake-symbols",
+                             "Fake symbols",
                              "Weak policy (0=strong policy)",
@@
 
-The interaction between between symbols can be also tested *within-subjects*, by comparing the averaged delta across the different symbols conditions.
+The interaction between symbols and information can also be tested *within-subjects*, by comparing the averaged delta across the different symbols conditions.
 Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition.
@@
 The differences between the two control groups are insignificant.
-These results further support my above finding that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.
+These results further support my findings above that familiar symbols decrease subjects' inclination to differentiate between the strong and weak policy plans.
 
@@
 
-Altogether, the above between- and within-subject analyses largely support my first two hypothesis.
-They suggest that familiar, and to a lesser extent none familiar, symbolic elements in communications increase citizens' trust in policies, and that the effect is greater for logically unpersuasive information.
-In other statistical models, shown in the supplementary appendix, I tested additional specifications, including analyzing the unfilterred sample, adding control variables, excluding subjects who did not recognize the real symbols and adding interactions with the policy plans.
+Altogether, the above between- and within-subject analyses largely support my first two hypotheses.
+They suggest that familiar, and to a lesser extent unfamiliar, symbolic elements in communications increase citizens' trust in policies, and that the effect is greater for logically unpersuasive information.
+In other statistical models, shown in the supplementary appendix, I tested additional specifications, including analyzing the unfiltered sample, adding control variables, excluding subjects who did not recognize the real symbols and adding interactions with the policy plans.
 In all these robust analyses, the main effect of the real symbols remains positive and significant, and the interaction between the real symbols and the weak information remains positive and significant.
@@
 I regressed each elaboration measure on the symbols manipulation (Models 2.1, 2.3), and then added the information manipulation (Models 2.2, 2.4).
-The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in table 1.
+The first two models, which refer to reaction time, are random intercept models which are similar to the statistical models in **Table 1**.
 As for the memory score analyses, given that each subject was asked only about one policy (the second in order), I used an OLS regression.
@@
           covariate.labels=c("Real symbols",
-                             "Fake-symbols",
+                             "Fake symbols",
                              "Weak policy (0=strong policy)"),
@@
 The real symbols decreased the number of second subjects spent on the pages of the policy plans in the online survey, compared with both control groups.[^footnote_RT_symbols] The effect is significant at the 95% level compared with the no symbols condition (*Coef* = `r mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`]), yet it is not sufficiently significant compared with the fake symbols.
-The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the the effects of the information manipulation (in Models 2.2, 2.4).
+The averaged memory score of subjects who saw the real symbols was significantly lower, compared with both the no logo and the fake logo groups (*Coef* = `r mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())-1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())+1.96*(mod_2.3%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(std.error)%>%max()))%>%round(2)`], and `r mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max()%>%round(2)` [`r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())-1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`, `r ((mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(estimate)%>%max())+1.96*(mod_2.3.r_1%>%tidy()%>%filter(term=="SYMBOL_t.r1")%>%select(std.error)%>%max()))%>%round(2)`], respectively).[^footnote_memory_symbols] There is no significant change to the results when adding the effects of the information manipulation (in Models 2.2, 2.4).
 The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them.
-**Figure 6** graphically displays the descriptive comparison of the elaboration measures across the symbols conditions.
+**Figure 6** displays the descriptive comparison of the elaboration measures across the symbols conditions.
 The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.
 
-[^footnote_RT_symbols]: The difference in seconds compared with the no symbols group, as extracted from the coefficients in logs is: `r (mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`.
+[^footnote_RT_symbols]: The difference in time, in seconds compared with the no symbols group, as extracted from the coefficients in logs is: `r (mod_2.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())%>%abs()%>%exp()%>%round(1)`-`r (x_realsymbol_RT_log-x_fakesymbol_RT_log)%>%abs()%>%exp()%>%round(1)`.
 The difference between the raw averages is `r (x_realsymbol_RT-x_fakesymbol_RT)%>%abs()%>%round(1)` seconds.
@@
 [^footnote_memory_symbols]: Descriptively, `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% of those in the real symbols group received the minimum score of 0, compared with `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==0)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the no symbols and fake symbols control groups.
-Congruently, the percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% in the control groups to only `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.
-Given that the measure of memory score is ordinal, I also tested it's correlation with the symbols manipulation via Spearman test.
-Spearman rho = `r cor_memory_nosymbol` and `r cor_memory_fakesymbol`, compared with the no symbols and fake symbols control groups.
+Congruently, the percentage of those who managed to correctly identify the two items dropped from `r (((filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==0,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% and `r (((filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==1,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`% to `r (((filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score==2)%>%nrow())/(filter(SVIVA2_01_comb,SYMBOL==2,MEMORY_score>=0)%>%nrow()))*100)%>%round(0)`%.
+I also tested the correlation between the memory score and the symbols via Spearman test for ordinal variables (rho = `r cor_memory_nosymbol` and `r cor_memory_fakesymbol`).
 
@@
 Next, I tested the hypothesis that the decrease in reaction time and memory score mediate the effect of the real symbols on trust in the weak policy plans.
-To do so, I used the causal mediation analysis method via `mediate` R package, which was developed by Imai et al.
-[@imai_2010; @imai_2011], and was also recently also implemented in Public Administration research [@porumbescu_2018].
+To do so, I used the causal mediation analysis method in the `mediate` R package, which was developed by Imai et al.
+[@imai_2010; @imai_2011], and was also recently implemented in Public Administration research [@porumbescu_2018].
 This method predicts the change in the outcome variable (here: trust in policy) given the causal change in the mediator that would be induced by the treatment (here: decreased elaboration inducted by the real symbols).
-Accordingly, it enables to decipher the proportion of the causal mediation effect from the total effect.
+Accordingly, it allows me to decipher the proportion of the causal mediation effect from the total effect.
 Causal mediation analysis is based on counter-factual comparisons, as opposed to the traditional method of @baron_1986, which is based on linear structural equation modeling.
-It is advantaged in terms of its accuracy as well as its ability to identify causality.
+It has an advantage due to its accuracy as well as its ability to identify causality.
 **Table 3** displays the results of the causal mediation of reaction time (log) and memory test, under the weak policy plans.
@@
 
-[^footnote_mediation_memory]: The differences between the analyses of the two measures can be also explained by the fact that memory score is calculated with regard to half of the observations.
-
-Finally, I also tested this moderated mediation hypothesis via within-subjects analysis.
-Given that each subject represents one observation, the memory score remains the same, and for the reaction time, I summed the number of seconds subjects spent on both policies (log transformed).
+[^footnote_mediation_memory]: The differences between the analyses of the two measures can be also explained by the fact that the memory score is calculated for half of the observations.
+
+Finally, I also tested this moderated mediation hypothesis via the within-subjects analysis.
+Given that each subject represents one observation, the memory score remains the same.
+For the reaction time, I summed the number of seconds subjects spent on both policies (log transformed).
 The results of this causal mediation analysis are summarized in **Table 4**.
@@
 
-The results of the within subjects mediation analysis similarly supports the moderated mediation hypothesis.
+The results of the within-subjects mediation analysis similarly supports the moderated mediation hypothesis.
 The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction time and the memory score.
@@
 Mediated","Estimate"]*100)%>%round(1)`% compared with the fake symbols.
-Regarding the memory score,the estimated proportional mediation is `r (table_med_memory__nosymbol_delta["Prop.
+Regarding the memory score, the estimated proportional mediation is `r (table_med_memory__nosymbol_delta["Prop.
 Mediated","Estimate"]*100)%>%round(1)`% and `r (table_med_memory__fakesymbol_delta["Prop.
@@
 [-@imai_2010].
-The sensitivity test examines the extent to which the causal mediation would change as a result of a correlation between the error terms of the mediator and the outcome variable (the "sequential ignorability" assumption).
-With regard to mediation by reaction time, the sensitivity factors range between 0.2-0.3, which suggest that a correlation greater than these values would violate the sequential ignorability assumption.
-Imai et al.
-did not offer any rule of thumb with regard to these factors.
-Yet, these results are consistent with sensitivity factors reported in previous studies, and therefore the mediation can be considered fairly reliable.
+Regarding mediation by reaction time, the sensitivity factors range between 0.2-0.3.
+These results are consistent with sensitivity factors reported in previous studies, and therefore the mediation can be considered fairly reliable.
 The sensitivity factors for the mediation by the memory score are 0.1, which entails that it is less reliable.
@@
 This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
-Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations up until a certain degree.[^footnote_ceiling_effect]
+Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations only to a certain degree.[^footnote_ceiling_effect]
 
 [^footnote_ceiling_effect]: This explanation is partly supported by a descriptive comparison of the distributions of the different groups.
-The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile (i.e.
-the lower 25% observations).
+The comparison of the quartiles in the different groups indicates that the increase in the average was mainly due to the increase in the first quartile.
 In the weak policy condition, the first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[2])%>%max()%>%round(1)` points compared with the no symbols, whereas the third quartile (i.e.
 the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==0])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==0])[4])%>%max()%>%round(1)` points.
-In the strong policy condition, we can find similar pattern of decreasing marginal effect.
-The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile (i.e.
-the higher 25% observations) increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.
+In the strong policy condition, I find a similar pattern of decreasing marginal effect.
+The first quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[2]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[2])%>%max()%>%round(1)` points, whereas the third quartile increased by `r (quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==2&SVIVA2_01_comb$INFORMATION==1])[4]- quantile(SVIVA2_01_comb$trust[SVIVA2_01_comb$SYMBOL==0&SVIVA2_01_comb$INFORMATION==1])[4])%>%max()%>%round(1)` points.
 
@@
 Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information about good/bad outcomes.
-Another limitation of the study regards the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
+Another limitation of the study is the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
 Future studies may compare the effectiveness of different types of symbolic elements.
@@
 Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information.
-This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information.[^footnote_biases_ELM].
+This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information.
 On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
@@
 
-[^footnote_biases_ELM]: This possibility is supported, theoretically, by ELM.
-According to ELM, biased processing occurs in the central route, whereby people give proportional weight for strong or weak arguments.
-Accordingly, decreasing the amount of thinking may also decrease biased processing [@petty_1986].
-Future research might put this expectation to test.
-
 This study also contributes to existing behavioral Public Administration research by introducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications.
@@
 In this study, I applied ELM to theorize the direct and indirect effects of symbolic elements on trust.
-Future Public-Administration studies may apply ELM and further explore the effects of other peripheral, heuristic cues in government communications, and the moderating role of motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
+Future Public-Administration studies may apply ELM and further explore the effects of other peripheral, heuristic cues in government communications.
+They may also examine the moderating role of motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
 Future studies may also examine the postulations of ELM that persuasion via arguments is more likely to be enduring,  and to increase citizens' cooperation with government policies, compared with persuasion via symbolic elements and heuristic cues.
@@
 Finally, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
-The participants of these studies, including this study, have relatively high motivation to elaborate on the information that scholars present them, because they may assume that they will be asked about it afterwards.
-In case they receive payment or other compensation for their participation, this further increases their motivation.
-By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they probably also have lower ability to do so, given the high competition on their time and attention.
-Accordingly, whereas previous studies have emphasized the effects of cognitive biases in citizens' processing of information [@james_2017a; @baekgaard_2016; @marvel_2015; @marvel_2015a; @hvidman_2016; @nielsen_2017; @olsen_2017], one could question the generalizability of these effects to real world settings, where people are less inclined to process the information in the first place.
+The participants of all these studies, including this one, are quite motivated to elaborate on the information that scholars present to them, since they assume that they will be asked questions about it afterwards.
+When participants receive payment or other compensation for taking part in the survey, their motivation is even higher.
+By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they are probably also less able to do so, given their lack of time and low attention span.
+Accordingly, whereas previous studies have emphasized the effects of cognitive biases in citizens' processing of information [@james_2017a; @baekgaard_2016; @marvel_2015; @marvel_2015a; @hvidman_2016; @nielsen_2017; @olsen_2017], one could question the generalizability of these effects and their relation to real-world settings, where people are less inclined to process the information in the first place.
 Regardless, scholars should also take to account this methodological issue when designing survey experiments, and attempt to simulate real world conditions, as much as possible.
-For instance, they can add filler sections in the survey before the real manipulation to attenuate participants' motivation and ability to elaborate.
+For instance, they can add filler sections in the survey, before the real manipulation, to attenuate participants' motivation and ability to elaborate.
 In addition, because the graphic design of communications also affects motivation and ability to elaborate, as shown here, scholars should simulate the design of real communications.

### 2018-07-30 paper2_information and symbols_02.Rmd
Add files via upload

@@
 
-EPM is working to reduce the air-pollution in the Haifa-Bay through:
+EPM is working to reduce the air-pollution in the Haifa-Bay by:
 
@@
 In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways.
-The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the amount of fines for pollutants.
-
-* **Reduction of smoke emissions from vehicles in Haifa Bay**.
+The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the level of fines for polluters.
+
+* **Reduction of emissions from vehicles in Haifa Bay**.
 The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area.
-The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and promotes the operation of a "clean-air area" that restricts the entry of polluting vehicles.
+The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and the designation of a "clean-air district" from which polluting vehicles are banned.
 
@@
 
-* **Decreasing the supervision of the factories in Haifa-Bay**.
+* **Decreasing the supervision of factories in Haifa-Bay**.
 The Ministry is preparing for a change in the method of supervision of the factories.
-The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the amount of fines.
+The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the level of fines.
 The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.
@@
 The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents.
-To this end, the ministry has increased its investment in public relations and publicity in this subject.
+To this end, the ministry has increased its investment in public relations and publicity on this subject.
 
@@
 
-EPM is working to reduce the amount of waste and increase its recycling through:
+EPM is working to reduce the amount of waste and increase recycling through:
 
@@
 * **Packaging recycling - Increased supervision of manufacturers**.
-In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, which imposes on manufacturers and importers the responsibility for recycling the packaging.
-The Ministry will work to increase enforcement by virtue of this act, and will enforce it with regard to additional manufacturers and importers.
+In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, under which manufacturers and importers are responsible for recycling their packaging materials.
+The Ministry will work to increase enforcement by virtue of this act, and will enforce it for additional manufacturers and importers.
 
 * **Reducing the usage of disposable bags**.
-In order to reduce the use of disposable plastic bags, the Ministry enforces the Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the chains.
-The Ministry works to implement the act, and encourages the transition to reusable grocery bags.
+In order to reduce the use of disposable plastic bags, the Ministry has enforced the Carrier Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the retail chains themselves.
+The Ministry is working to implement the act, and to encourage the transition to reusable grocery bags.
 
@@
 * **Packaging recycling - Decreased supervision of manufacturers**.
-The Ministry is preparing to a change in the method of supervision of the manufacturers, who are responsible for the recycling of product packaging by virtue of the act The ministry will reduce the number of inspections, rely on manufacturers' self-reports regarding their compliance with the requirements of the act, and reduce the amount of fines.
-The change is coordinated with members of the industry, which are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
+The Ministry is preparing to a change in the way manufacturers, who are responsible for the recycling of product packaging, are supervised.
+The ministry will reduce the number of inspections, rely on manufacturers' own reporting regarding their compliance with the requirements of the act, and will reduce the level of fines.
+The change is coordinated with industry representatives, who are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
 

### 2018-07-31 paper2_APPENDIX.Rmd
Add files via upload

@@
 
-1. Supplementary information about the images.
+1. Supplementary information about the images
 
@@
 
-3. Summary statistics.
-
-4. Supplementary analyses.
-
-5. English translation of the survey experiment.
+3. Summary statistics
+
+4. Supplementary analyses
+
+5. English translation of the survey experiment
 
@@
 
-In this section, I provide additional details about the creation of the "real" and "fake" symbolic elements that were included in the policy plans in the survey.
+In this section, I provide additional details about how I created the "real" and "fake" symbolic elements that were included in the policy plans in the survey.
 
@@
 
-The campaign images which were included in the policy plans in the real symbols condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns.
-After downloading the images, I cropped them (via GIMP software).
+The campaign images which were included in the policy plans in the "real symbols" condition were downloaded from EPM's official website (http://www.sviva.gov.il), from the section that archives the Ministry's publications and public campaigns.
+After downloading the images, I cropped them (using GIMP software).
 The sources of the images are detailed below:
@@
 
-The fake logo was created via MS paint software.
-I replaced the leaves/hands from the original logo with a shape of stars with rounded edges, and replaced the green color with blue.
-I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].
-
-To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their face expressions in the campaign images.
-For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase.
+The fake logo and campaign images were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the real symbolic elements, as much as possible, while removing their symbolic aspects.
+The fake logo was created using the MS paint software.
+I replaced the leaves/hands of the original logo, with stars with rounded edges, and replaced the green color with blue.
+I deliberately selected a natural element – a star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].
+
+To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their facial expressions in the campaign images.
+For this purpose, I used the website www.istockphoto.com where multiple collections of professional images can be purchased.
 The original photos which I purchased from the website, and their sources are detailed below.
@@
 In this section, I report the results from two prior surveys, with regard to the recognizability, affect and associations of the "real" and "fake" symbolic elements, which were included in the policy plans in the survey.
-I conducted these examinations before conducting the experiment in order to validate my empirical assumptions with regard to comparison between the real and fake symbols.
+I conducted these examinations before conducting the experiment, in order to validate my empirical assumptions about comparing the real and fake symbols.
 I assume that the real symbols are recognized, and that they evoke positive feelings and associations which are related to caring for the environment.
@@
 
-The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, which were recruited by iPanel.
+The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, recruited using the internet panel company iPanel.
 This survey was designed as a survey experiment, which was a first attempt to test the moderating role of personal relevance on the effects of symbols and information (but not the interaction between symbols and information).
@@
 Overall, these results show that the real logo is relatively recognizable and has a fairly positive affect, whereas the fake logo is unrecognized and neutral.
-Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?"  With regard to the real logo, many of the participants filled associations related to carting for the environment.
+Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?" With regard to the real logo, many of the participants mentioned associations related to caring for the environment.
 Representative examples for such answers are: "environmental protection", "a desire to protect nature and the environment", "green policy", "together for the sake of nature", "connection between nature and man".
 The participants were similarly asked about the first thought / association that comes to their mind when they see the color.
-Representative answers for the green color were: "nature", "a green and healthy environment", "environment protection".
+Representative answers for the green color were: "nature", "a green and healthy environment", "environmental protection".
 The responses for the fake logo and the blue color were more diverse, and mostly unrelated to environmental issues.
@@
 
-The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants, which were similarly recruited via iPanel.
+The second prior survey was conducted in January 2018 among `r CELEBS_00%>%nrow()` participants, also recruited using iPanel.
 This survey was designed as a pre-test that was aimed at assessing the recognizability, affect and associations of the real vs.
 fake campaign images.
-Participants were presented with the four campaign images (two real and two fake), in a random order.
+Participants were presented with the four campaign images (two real and two fake), in random order.
 After every image, they were asked a series of questions regarding the familiarity and affect of the image and of the person presented.
@@
 
-These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative of positive feelings.
-Finally, I similarly asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text).
+These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative or positive feelings.
+Finally, I also asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text).
 Most of the participants associated Rosenblum's image to the reducing the use of disposable grocery bags, in line with the campaign's message (e.g.
@@
 Below is the full text of the survey.
-Additional comments are presented in square beackets.
+Additional comments are presented in square brackets.
 The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here.
@@
 Therefore, it is important for us that you answer the questionnaire seriously and honestly.
-The questionnaire filling time is about 5-10 minutes.**
+You have around 5-10 minutes to complete the questionnaire.**
 
 **It is important for us to clarify that the questionnaire is voluntary.
-Filling out the questionnaire and submitting it represent your agreement to participate in the research.
+Filling out the questionnaire and submitting it represents your agreement to participate in the research.
 In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only.
-Non-consent to participate will be expressed in not filling of the questionnaire.
+You can express non-consent to participate by not filling in the questionnaire.
 The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**
@@
 
-7. I have great confidence/trust
+7. I have full confidence/trust
 
@@
 
-1. Little interested
+1. Hardly interested
 
@@
 
-**Now, we would like to ask you a few general questions about your area of occupation.**
+**Now, we would like to ask you a few general questions about your occupation.**
 
@@
 
-3. Third Sector
+3. 3.	Civic Sector
 
@@
 
-**What is your field of profession/study? ______________**
+**What is your profession/field of study? ______________**
 
@@
 
-**Compared to the current situation, do you think the government should assist more or less to promote your field of occupation?**
+**Compared to the current situation, do you think the government should assist more, or less to promote your field of occupation?**
 
@@
 
-**What, in your opinion, might attract people to choose your occupation? _________________________________________**
+**What, in your opinion, might attract others to choose your occupation? _________________________________________**
 
@@
 
-**Next, we will present you two policy plans on specific environmental issues.
-The programs are taken from the publication of the "Work Plans for 2018" of the Ministry of Environmental Protection, which is published in the Ministry's website.**
-
-**At the top of each policy plan presented the specific policy issue, followed by the main actions taken by the Ministry to promote the issue.**
-
-[Participants are then presented with the two policy plans (air-pollution and recycling), in a random order.
+**Next, we will present to you two policy plans on specific environmental issues.
+The policy plans are taken from the publication “Work Plans for 2018” of the Ministry of Environmental Protection, which can be downloaded from the Ministry’s website.**
+
+**The specific policy issue is presented at the top of each policy plan, and is followed by the main actions taken by the Ministry to promote the issue.**
+
+[Participants are then presented with the two policy plans (air-pollution and recycling), in random order.
 See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]
 
-**Now, we'd like to ask you a few questions about your position on the policy for "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay":**
+**Now, we’d like to ask you a few questions about your position on the policy for “Reducing the air-pollution in the Haifa-Bay”:**
 
@@
 
-**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal**
+**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal.**
 
@@
 
-**I believe that the policy plan is in the interest of citizens**
+**I believe that the policy plan is in the citizens’ interest.**
 
@@
 
-**I believe that EPM made an honest attempt to design a good policy plan**
-
 1. Weakly agree
@@
 
-**I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.**
+**I believe that EPM made an honest attempt to design a good policy plan.**
 
@@
 
+**I believe that the Ministry of Environmental Protection aims to keep its commitments as laid out in the policy plan.**
+
+1. Weakly agree
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Strongly agree
+
 ---
 
-**The following sentences describe the way in which you read the latest policy plan that regarded to "Reducing waste and increase recycling" / "Reducing the air-pollution in the Haifa-Bay".**
+**The following sentences describe the way in which you read the latest policy plan regarding “Reducing the air-pollution in the Haifa-Bay”.**
 
@@
 
-**I paid much attention to reading the policy plan.**
+**I paid full attention to reading the policy plan [I read the policy plan in depth].**
 
@@
 
-**I skimmed the actions in the policy plan.**
+**I only skimmed the actions in the policy plan.**
 
@@
 
-**I tried to thoroughly understand the the policy plan.**
+**I tried to thoroughly understand the policy plan.**
 
@@
 
-**While going through the policy plan I was thinking about other things which are not related to it.**
+**While going through the policy plan I was distracted by unrelated thoughts.**
 
@@
 **Try recalling the content of the latest policy plan.**
-[Each subjects was asked about the latest policy plan presenter to her]
+[Each subject was asked about the latest policy plan presented to her]
 
@@
 
-1. Supervision on the factories
+1. Supervision of factories
 
@@
 
-5. I can not remember
+5. I cannot remember
 
@@
 
-1. Supervision on the manufacturers
-
-2. compulsory charge on bags
+1. Supervision of manufacturers
+
+2. compulsory charge on carrier bags
 
@@
 
-4. plastic bottles
-
-5. I can not remember
+4. Plastic bottles
+
+5. I cannot remember
 
@@
 
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+**When you see the image, what feelings does it invoke?**
+
+1. Very negative feelings
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feelings
+
+**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**
 
@@
 
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
+**When you see the image, what feelings does it invoke?**
+
+1. Very negative feelings
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feelings
 
@@
 
-**When you see the image, what does it make you feel?**
-
-1. Very negative feeling
-
-2.
-
-3.
-
-4.
-
-5.
-
-6.
-
-7. Very positive feeling
-
-**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?**
+**When you see the image, what feelings does it invoke?**
+
+1. Very negative feelings
+
+2.
+
+3.
+
+4.
+
+5.
+
+6.
+
+7. Very positive feelings
+
+**The image is taken from an advertisement of the Environmental Protection Ministry. To what extent do you remember the advertisement?**
 
@@
 Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently.
-The tasks related to "raising awareness" and "reducing supervision" are invented tasks that are not part of the Ministry of Environmental Protection's policy.
-[For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry's broadcasts, and their characters were used only for research purposes.]**
+The tasks related to “raising awareness” and “reducing supervision” are fictional tasks that are not part of the Ministry of Environmental Protection’s policy.
+[For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry’s broadcasts, and their characters were used only for research purposes.]**
 

### 2019-03-08 paper2_JPART_rev_01.Rmd
Add files via upload

--- 2018-07-30 paper2_information and symbols_02.Rmd
@@
 bibliography: phd_paper_2.bib
+csl: apa.csl
 urlcolor: blue
@@
 #load("SVIVA_R_ENV.RData")
-source("SVIVA_exp2_dm_03.R")
+source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")
 
@@
 
-Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their underestimation of public-service performance.
+Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their underestimation of public-service performance. ##ADD more about trust.##
+
 One of the main remedies proposed for this is greater investment in direct government communications to citizens.
-Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014].
+Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014; @canel_2013].
 In the US, for example, federal government agencies spend approximately 1.5 Billion dollars annually on contracts related to public relations and advertising activities in traditional and digital media [@unitedstatesgovernmentaccountabilityoffice_2017].
 
-Extant public administration research on the effect of government public communications on citizens attitudes has mostly focused on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
+Extant research on the effect of government public communications on citizens attitudes has mostly focused on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
-Public communications are expected to increase citizens' trust insofar as they provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
-At the same time, experiment-based studies that explored the responses of citizens to substantive information revealed cognitive biases that distort their processing of information in communications, and undermine its effectiveness [@baekgaard_2016; @grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @hvidman_2016; @james_2011; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @grimmelikhuijsen_2017].
+This theoretical and empirical focus on information and transparency congrues with the normative view of government public communication as a means for accomplishing democratic accountability, facilitating the effective implementation of their missions, and aligning citizens' perceptions of public organizations with their actual performance [@canel_2013; @lee_2012; @lee_2001; @lee_2008; @lee_2011].
+According to this view, public communications are expected to increase citizens' trust in bureaucracies mainly insofar as these communications provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
 
@@
 
-The theoretical hypotheses are graphically displayed in **Figure 1**.
-
-<br>
-**Figure 1: Theoretical model**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/theoretical_model.png) 
-<br>
-
 <br>
@@
 In these communications, the EPM used an array of symbolic elements, which became widely recognized by the public.
-Here, I focused on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 2**.
-The first symbolic element is the unique brand logo of the EPM (Figure 2a).
+Here, I focused on three prominent symbolic elements used in the EPM's public communications, and displayed below in **Figure 1**.
+The first symbolic element is the unique brand logo of the EPM (Figure 1a).
 This logo consists of a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
@@
 Specifically, I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, who previously endorsed two salient advertising campaigns of the EPM.
-The campaign starring the comedian Tal Friedman (Figure 2b) was launched in 2010, and included a series of advertisements in which Friedman was presented with a head covered in green grass, and accordingly the campaign's slogan was: "starting to think green".
-The campaign starring the comedian Ido Rosenblum (Figure 2c) was launched in 2017, and focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.
+The campaign starring the comedian Tal Friedman (Figure 1b) was launched in 2010, and included a series of advertisements in which Friedman was presented with a head covered in green grass, and accordingly the campaign's slogan was: "starting to think green".
+The campaign starring the comedian Ido Rosenblum (Figure 1c) was launched in 2017, and focused on reducing the use of disposable bags.[^footnote_campaigns] The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.
 
@@
 <br>
-**Figure 2: Symbolic elements of EPM**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/EPM_symbols.png) 
+**Figure 1: Symbolic elements of EPM**
+![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/EPM_symbols.png) 
 <font size="0.5">
@@
 weak policy).
-The assignment to the different experimental groups is graphically presented in **Figure 3**.
+The assignment to the different experimental groups is graphically presented in **Figure 2**.
 The experimental groups are balanced with respect to demographics, and pre-manipulation variables.
@@
 <br>
-**Figure 3: Experimental design for policy plan communications**
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/experiment_flow.png)
+**Figure 2: Experimental design for policy plan communications**
+![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/experiment_flow.png)
 
@@
 The interaction between symbols and information significantly contributes to the model fit (Chi2 = `r anova(mod_1.3,mod_1.2)%>%tidy()%>%filter(term=="mod_1.3")%>%select(statistic)%>%max()%>%round(2)`, *p*<.05).
-To facilitate the interpretation of this interaction, **Figure 4** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
-
-**Figure 4: The effect of symbolic elements on trust under weak vs. strong information**
+To facilitate the interpretation of this interaction, **Figure 3** provides a descriptive demonstration of the effects of the real symbols on trust in policy, under weak and strong information quality.
+
+**Figure 3: The effect of symbolic elements on trust under weak vs. strong information**
 
@@
 Based on my second hypothesis, I expect that the averaged delta will be lower among subjects in the real symbols condition.
-This comparison is graphically displayed in **Figure 5**.
+This comparison is graphically displayed in **Figure 4**.
 The averaged delta in the real symbols is significantly lower than in the no symbols and fake symbols control groups (differences are `r (x_realsymbol_delta-x_nosymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_nosymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_nosymbol[["conf.int"]][2]%>%round(2)`] and `r (x_realsymbol_delta-x_fakesymbol_delta)%>%abs()%>%round(2)` [`r t_delta_symbol_fakesymbol[["conf.int"]][1]%>%round(2)`,`r t_delta_symbol_fakesymbol[["conf.int"]][2]%>%round(2)`], *t*= `r t_delta_symbol_nosymbol[["statistic"]][["t"]]%>%round(3)` and `r t_delta_symbol_fakesymbol[["statistic"]][["t"]]%>%round(3)`, respectively).
@@
 
-**Figure 5: The effect of symbolic elements on within-subject delta between strong and weak policies**
+**Figure 4: The effect of symbolic elements on within-subject delta between strong and weak policies**
 
@@
 Based on my third hypothesis, I expect to find a negative effect of the real symbols on these two measures.
-Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols on trust under the weak policy, but not under the strong policy (see Figure 1).
+Thereafter, my fourth hypothesis entails moderated mediation relations: the decrease in elaboration mediates the effect of symbols on trust under the weak policy, but not under the strong policy.
 
@@
 The coefficients of the weak policy in these models suggest that those who saw the fictitious, weak policy plans, spent more time on their pages, yet were less likely to state items that were included in them.
-**Figure 6** displays the descriptive comparison of the elaboration measures across the symbols conditions.
+**Figure 5** displays the descriptive comparison of the elaboration measures across the symbols conditions.
 The left side shows its effect on reaction time (logged), and the right side shows its effect on the memory-test scores.
@@
 
-**Figure 6: The effect of symbolic elements on elaboration**
+**Figure 5: The effect of symbolic elements on elaboration**
 
@@
 
-The results of the within-subjects mediation analysis similarly supports the moderated mediation hypothesis.
+The results of the within-subjects mediation analysis similarly support the moderated mediation hypothesis.
 The negative effect of the real symbols on the delta within subjects (between trust in the strong and weak policies) is significantly mediated by the negative effect of the real symbols on reaction time and the memory score.
@@
 Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
+
 Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information.
-This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information.
+This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information [@baekgaard_2016; @hvidman_2016; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @james_2017b; @christensen_2018; @hvidman_2018].
 On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
@@
 In those cases, symbolic elements can mitigate justified public criticism of government failures.
-Ultimately, by preserving citizens' trust in them and escaping public blame, organizations can nurture their long-term positive reputation, which provides them with political power and attenuates elected politicians' incentives to monitor and oversight them [@busuioc_2016; @bertelli_2018].
-Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, organizations can also use it as a means to undermine them.
+The potency to manipulate public opinion via symbols could be used for promoting the narrow political interests of parties and individual politicians controling the bureaucracies, as suggested by case studies of governemnt public relations [@holtzbacha_2013; @sanders_2013; @young_2013].
+At the same time, it could also be used for promoting the interests of the bureaucracies themselves, namely nurturing their long-term positive reputation, which provides them with political power and autonomy [@busuioc_2016; @bertelli_2018].
+Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, it can also be use it as a means to undermine them.
 
@@
 ##Appendix B: Symbols manipulation
-![](D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/symbols_manipulation.png)
+![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/symbols_manipulation.png)
 
@@
 
-*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*
+*Note: The policy plans presented here are the strong policies, in the version adjusted for a mobile interface.*
 

### 2019-03-15 paper2_JPART_rev_01.Rmd
Add files via upload

@@
 
-Public administration scholars are highly concerned about the implications of citizens’ low trust in government, and their underestimation of public-service performance. ##ADD more about trust.##
+Scholars of Political-Science and Public-Administration are long concerned about citizens’ low trust in government, and their underestimation of public-service performance [@alford_2001; @nye_1997; @levi_2000; @vandewalle_2008; @vigodagadot_2006; @vanryzin_2011].
+Distrust in public organizations has a negative impact of government performance and capacity.
+It may hamper citizens' collaboration with organizations' policies, which, in turn, affect their successful implementation.
+It is also said to encourage citizens' tax evasion and selection of private over public service providers, and it could make it more difficult for public sector organizations to attract and keep high-quality employees [@hvidman_2018].
 
@@
 
-Extant research on the effect of government public communications on citizens attitudes has mostly focused on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
+Extant research on the effect of government public communications on citizens trust has mostly focused on the *informative* aspects of these communications, whereby government organizations provide citizens with evidence about their performance and details and explanations about their policies and actions [e.g.
 @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017].
-This theoretical and empirical focus on information and transparency congrues with the normative view of government public communication as a means for accomplishing democratic accountability, facilitating the effective implementation of their missions, and aligning citizens' perceptions of public organizations with their actual performance [@canel_2013; @lee_2012; @lee_2001; @lee_2008; @lee_2011].
-According to this view, public communications are expected to increase citizens' trust in bureaucracies mainly insofar as these communications provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
-
-Recently, a few studies pointed to the additional effect of *symbolic* elements that are entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-These studies demonstrated that government organizations may cause citizens to view them more favorably through familiar and well-designed symbolic elements that evoke positive associations and emotions.
+This focus on information and transparency is in line with the positive normative view of government public communication and public relations, as articulated by the public administration literature on this topic, led by the works of Merdechai Lee.
+Communications with citizens are perceived as a means for accomplishing democratic accountability, facilitating the effective implementation of their missions, and aligning citizens' perceptions of public organizations with their actual performance [@canel_2013; @lee_2000; @lee_2012; @lee_2001; @lee_2008; @lee_2011].
+Importantly, according to this view, public communications are expected to increase citizens' trust in bureaucracies mainly insofar as these communications provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
+
+Recently, however, a few studies pointed to the additional effect of *symbolic* elements that are entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
+These studies experimentally demonstrated that government organizations may cause citizens to view them more favorably and trust them through familiar and well-designed symbolic elements that evoke positive associations and emotions.
 Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens’ trust.
-These previous studies also did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
+These studies also did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
 
 This research gap has normative significance.
-Whereas the responsiveness of citizens to substantive information is perceived favorably from a democratic theory standpoint, the effect of symbolic elements can be problematic.
-One can argue that shaping citizens' perceptions of governments by evoking associations and emotions stands against the normative expectation that citizens' judgments should be based on their critical thinking.
-We need to be aware that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
+Whereas the responsiveness of citizens to substantive information is perceived favorably from a democratic standpoint (assuming that it is accurate), establishing trust through symbolic elements can be highly problematic.
+Shaping citizens' perceptions of governments by evoking associations and emotions stands against the normative expectation that citizens' judgments should be based on their critical thinking.
+Furthermore, we need to be aware that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
 Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in government communications affect citizens' trust in government organizations and their policies?
-Does the effect of symbolic elements depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
+Does the effect of symbolic elements on trust depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
 
@@
 The experiment focuses on the empirical case of the Israeli Environment Protection Ministry.
-I explore citizens' responses to public communications about two policy plans of the Ministry, and specifically the extent to which their trust in these policies are affected by the substantive information in the communications (logically persuasive vs.
-unpersuasive policy plans) and by symbolic elements in them (real symbols vs.
-fake symbols and no symbols conditions).
+I explore citizens' responses to public communications about two policy plans of the Ministry.
+Specifically, I examine how their trust in these public policies is affected by the symbolic elements in the communications (real symbols vs.
+fake symbols and no symbols conditions) as well as by the substantive information in them (logically persuasive vs.
+unpersuasive policy plans).
 
@@
 In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans.
-They were also less inclined to think about the policy content because they were distracted by the symbols.
+The latter were less inclined to think about the weak, unpersuasive content, because they were distracted by the symbols.
 I discuss the theoretical and normative implications of these findings.
@@
 
-Symbols are fundamental for almost any form of human interaction, as acknowledged by early scholars of social science [@blumer_1986].
 A symbol can be broadly defined as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
 28-29].
-My focus is on those symbols that are strategically used by government organizations in their public communications, are designed to distinguish them and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
+Symbols are fundamental for almost any form of human interaction, and specifically in the context of politics and public affairs [@edelman_1964; @edelman_1988; @elder_1983].
+Conselletions of symbols in discourse form consolidated narratives, which play an key role in shaping people's perceptions of policy problems and solutions [@miller_2012; @miller_2015].
+
+My focus in this study is on those symbols that are strategically used by government organizations in their public communications, are designed to distinguish them and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
 Prominent examples are unique logos, colors associated with specific meanings, icons, images, and the use of celebrities as endorsers.
@@
 
-In comparison with the abundant research on citizens’ responses to informative elements in public communications [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements.
+In comparison with the abundant research on the effect of informative elements in public communications on public trust [for reviews see: @cucciniello_2016; @grimmelikhuijsen_2017; @james_2017], public administration literature has devoted relatively little attention to the effect of symbolic elements.
 Recently, however, a few experimental studies tackled the issue.
-@marvel_2015 analyzed US citizens' responses to a television advertisement of the public US Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music.
+@marvel_2015a analyzed US citizens' responses to a television advertisement of the public US Postal Service, which involved various symbolic elements, including the organization's logo, workers' images and background music.
 His study shows that participants who watched the advertisement evaluated the organization's performance more positively.
 @teodoro_2018 suggested that the names of US federal agencies not only represent information about their activities, but may also carry specific symbolic meaning and positive/negative "affect" that can shape citizens' support for government policies (depending on citizens' political party identification).
-While these two studies provide examples for the role of symbols in shaping citizens' attitudes, they did not effectively disentangle the effects of the symbolic and informational aspects of the public communications studied.
-
-A study by @karens_2016 did examine the distinct effect of symbols in communications on citizens' trust.
-The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of the organization's logo in the communication of the policy plans.
+While these two studies provide examples for the role of symbols in shaping citizens' trust and performance evaluation, they did not effectively disentangle the effects of the symbolic and informational aspects of the public communications studied.
+
+A study by @karens_2016 did examine the distinct effect of symbols in communications on citizens' trust in bureaucracies.
+The scholars surveyed university students from three European countries and examined their trust in two policy plans of the European Commission, and it's shaping by the appearance of its logo in the communication.
 They found that including the Commission’s logo significantly increased citizens' trust in these policies.
@@
 
-Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' favorable attitudes, they did not directly investigate the causal mechanisms that underlie this effect.
+Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' greater trust in public organizations and policies, they did not directly investigate the causal mechanisms that underlie this effect.
 Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust.
@@
 The social psychology Elaboration Likelihood Model (ELM) provides a comprehensive theoretical framework for investigating peoples' varying responses to "persuasive" communications [@petty_1986; @petty_2011].
-In addition to its general theoretical application in psychological research, this model has been applied to studies on persuasion in various areas, including commercial advertising [e.g.
+It theorizes when and how individuals are more/less likely to change their attitudes following a communication or a message.
+Accordingly, ELM can be applied to various settings, types of attitudes and forms of communications.
+It has been specifically applied to studies on persuasion or attitudinal change in various areas, including commercial advertising [e.g.
 @petty_1983; @dotson_2000; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
-So far however the relevance of ELM has not been directly examined in relation to citizens' responses to government communications.
+So far however the relevance of ELM has not been directly examined in relation to changes in citizens' trust in public organizations in response to their public communications.
 
 According to ELM, the responses of individuals to persuasive communications depends on how much effort they devote to thinking about the content of the message (or "the amount of thinking" according to ELM terminology).
-Persuasion can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
+Persuasion, or attitudinal change, can occur when thinking is "high" or "low", but the processes and consequences are likely to differ in each situation.
 This range between high and low degrees of thought is referred to as the "elaboration continuum".
@@
 At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories].
-In turn, these different persuasion mechanisms are likely to cause divergent types of attitudinal change.
+In turn, these two mechanisms are likely to cause divergent types of persuasion.
 Persuasion via the central route is expected to be more enduring, resistant and predictive of behavior, compared with the peripheral route.
@@
 Consider for instance a text that contains a series of logical arguments supporting a certain position.
-Those at the high end of the continuum would regard this text as argumentation, systematically scrutinizing it based on its logical persuasive quality (central route processing).
-Conversely, those at the low end of the continuum are more likely to disregard the content of the text, and instead, rely on the number of lines in the text, for example, as a cue for its strength (peripheral route processing).
+Those at the high end of the continuum would regard this element as argumentation.
+They would systematically scrutinize it and form their attitudes about the position based on its logical persuasive quality (central route processing).
+Stronger arguments would increase their inclination to support the position (i.e.
+to form positive attitudes about it).
+Conversely, those at the low end of the continuum are more likely to disregard the content of the text, and instead, rely on the number of lines in it, for example, as a cue for its strength (peripheral route processing).
 Some elements provide potential cues that lack any logical quality at all.
 For example, the physical attractiveness of the source normally does not represent any substantive argument, yet it can serve as a simple cue.
-These latter elements may affect the attitudes of those at the low end, but are less likely to persuade those at the high end [@petty_1986].
+Accordingly, they may affect the attitudes of those at the low end, but are less likely to persuade those at the high end [@petty_1986].
 
@@
 
-How may we apply the theoretical framework of ELM to the study of the effects of symbolic elements in government communications with citizens and their interaction with substantive information?
+How may we apply the theoretical framework of ELM to the study of the effects of symbolic elements in government communications on citizens' trust and their interaction with substantive information?
 
 In light of the conceptualization of ELM, substantive information elements in government public communications represent issue-related arguments, which can be scrutinized or processed systematically based on their logical quality (via the central route), at least by those who are sufficiently motivated and able to do so.
-Conversely, symbolic elements are potential peripheral cues, which can affect citizens' trust via the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
+More positive information about organizations' performance and more logically persuasive arguments supporting their actions would increase citizens' trust in these organizations and their actions and vice versa.
+Conversely, symbolic elements are potential peripheral cues.
+they can increase citizens' trust via the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
 However, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly.
-They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing negative information (e.g.
+They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing substantive information that would otherwise decrease their trust, namely negative information (e.g.
 information on poor performance) and weak arguments (e.g.
-logically unpersuasive description of their policy plans).[^footnote_interaction_strong_information]
-
-Symbolic elements may decrease citizens' ability and motivation to think about the message in several ways.
+logically unpersuasive arguments supporting their actions and policies).
+The latter assertion entails an interaction between symbols and the substantive information in communications: symbolic elements in public communications are more likely to affect citizens' trust when communications include negative information or weak logical arguments.[^footnote_interaction_strong_information]
+
+[^footnote_interaction_strong_information]: Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
+
+How can symbolic elements decrease citizens' ability and motivation to think about the message?
+According to social psychology theory, they can do so in two main ways.
 First, they can cause elaboration disruption, by distracting citizens and capturing their attention and cognitive efforts [@petty_1976; @petty_1986].
@@
 Therefore, when citizens are exposed to symbolic elements that evoke positive feelings, they may seek to avoid thinking about tedious bureaucratic affairs, which would depress their positive mood.
-The latter expectation entails an interaction between symbols and the substantive information in the communications.
-
-[^footnote_interaction_strong_information]: Analytically, the expectation that symbolic elements decrease message elaboration also entails that symbols may decrease citizens' trust in communications about highly positive performance and persuasive policy plans.
 
@@
 Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abundant research on their responses to information.
-Yet, this study, and others, demonstrated that symbols can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
+The latter body of literature emphasizes the cognitive biases that distort citizens' processing of information in government communications, and suggests that citizens tend to be sceptic about their positive information [@baekgaard_2016; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017b; @christensen_2018; @james_2017a; @james_2017c].
+Hence, it undermines the effectiveness of the communication of substantive information.
+Yet, this study, and others, demonstrated that symbolic communication, which requires little cognitive effort, can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
 
 Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information.
-This is good news as far as we are concerned mainly about citizens' *undervaluation* of government performance, and the negative biases that undermine the effectiveness of positive information [@baekgaard_2016; @hvidman_2016; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017a; @james_2017b; @christensen_2018; @hvidman_2018].
-On the other hand, the emotive effect of government symbols on public opinion is highly problematic, insofar as it challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking [@dahl_1973; @soroka_2010].
-Moreover, it becomes especially problematic when symbols are used by poorly performing organizations, or organizations that lack professional expertise.
+This is good news as far as we are concerned mainly about the negative biases of citizens and the media regarding public organizations [@hvidman_2016; @hvidman_2018; @marvel_2015a], resulting in citizens' *undervaluation* of government performance.
+On the other hand, the emotive effect of government symbols on public opinion is highly problematic.
+It challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking, rooted in healthy skepticism.
+Congruently, it contrasts with the main objective of public communication to enhance bureaucracies’ accountability to citizens [@canel_2013; @lee_2012; @lee_2001; @lee_2008; @lee_2011], and with the basic moral “obligation of the public administrator to keep the public informed” [@lee_2000, 459].
+
+Moreover, the effect of symbolic elements becomes especially problematic when they are used by poorly performing organizations, or organizations that lack professional expertise.
 In those cases, symbolic elements can mitigate justified public criticism of government failures.
-The potency to manipulate public opinion via symbols could be used for promoting the narrow political interests of parties and individual politicians controling the bureaucracies, as suggested by case studies of governemnt public relations [@holtzbacha_2013; @sanders_2013; @young_2013].
+Theoretically, this distortion could be either the unconscious result of an honest attemt by the bureaucracy to promote good causes, or worse - a satrategically planned "propaganda".
+This could be used for promoting the narrow political interests of parties and individual politicians controlling bureaucracies - for instance, the Minister of Environment Protection and/or his party [For exmaples of politicians' exploitation of public communications see @sanders_2013a].
 At the same time, it could also be used for promoting the interests of the bureaucracies themselves, namely nurturing their long-term positive reputation, which provides them with political power and autonomy [@busuioc_2016; @bertelli_2018].
-Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, it can also be use it as a means to undermine them.
+In any case, it may result in undermining the accountability of bureaucrats and politicians to the public, and a deviation from the model of democratic responsiveness [@dahl_1973; @soroka_2010].
 
@@
 
+Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, it can also be use it as a means to undermine them.
+##work on that##
+
 <br>

### 2019-04-13 paper2_APPENDIX_rev_01.Rmd
Add files via upload

--- 2018-07-31 paper2_APPENDIX.Rmd
@@
 ```{r , include=FALSE, echo=FALSE}
-source("SVIVA_exp2_dm_03.R")
-
-SVIVA1_01 = read.csv("SVIVA1_01.csv")
-CELEBS_00 = read.csv("CELEBS.csv")
+source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")
+
+SVIVA1_01 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
+CELEBS_00 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")
 ```
@@
 library(stargazer)
+library(ggthemes)
+
 ```
@@
 ```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
-knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_air_model.jpg")
+knitr::include_graphics("C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/fake_air_model.jpg")
 ```
@@
 ```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
-knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_waste_model.jpg")
+knitr::include_graphics("C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/fake_waste_model.jpg")
 ```
@@
 ```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-set_theme("scatterw")
+
+set_theme(
+  base=theme_tufte(),
+  geom.outline.size = 0.01,
+  geom.outline.color = "white", 
+  geom.label.size = 2,
+  geom.label.color = "grey50")
 
 sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,155),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real logo")
@@
 sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,155),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake logo")
@@
 ```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-set_theme("scatterw")
-
 sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real logo")
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake logo")
@@
 sjp.frq(CELEBS_00$air_real_person_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real celeb (Tal Friedman)")
@@
 sjp.frq(CELEBS_00$air_fake_person_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Unfamiliar model")
@@
 sjp.frq(CELEBS_00$waste_real_person_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real celeb (Ido Rosenblum)")
@@
 sjp.frq(CELEBS_00$waste_fake_person_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Unfamiliar model")
@@
 sjp.frq(CELEBS_00$air_real_ad_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (starting to think green)")
@@
 sjp.frq(CELEBS_00$air_fake_ad_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
@@
 sjp.frq(CELEBS_00$waste_real_ad_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (reusable bags)")
@@
 sjp.frq(CELEBS_00$waste_fake_ad_familiar,
-        geom.size = 0.9,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (starting to think green)")
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (reusable bags)")

### 2019-04-13 paper2_JPART_rev_01.Rmd
Add files via upload

@@
 title: "Can government public communications elicit undue trust? Exploring the interaction between symbols and substantive information in communications"
-author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
+author: '**Saar Alon-Barkat**, Ph.D.; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
 date: " "
 output:
+  word_document: default
+  pdf_document:
+    toc: yes
   html_document:
@@
       toc_depth: 3
-  pdf_document:
-    toc: yes
-  word_document: default
 link-citations: yes
 bibliography: phd_paper_2.bib
-csl: apa.csl
+csl: ajps.csl
 urlcolor: blue
@@
 *Effective public communications have been proposed as a remedy for citizens' distrust in government.
-Those studies that have explored the effectiveness of government communications have focused mainly on the extent to which they provide substantive information about bureaucracies' performance and policies.
-Recently, a few studies pointed to the effect of symbolic elements, entangled in these communications (e.g.
+Recent studies pointed to the emotional effect of symbolic elements, entangled in government public communications (e.g.
 logos, images and celebrities).
-Still we lack theoretical understanding of the mechanisms underlying citizens' responses to symbolic elements, and the interaction between symbols and substantive information.
-Building on the social psychology Elaboration Likelihood Model I hypothesize that symbols increase citizens' trust in two ways: First, directly, by evoking positive feelings that are transferred to the organizations and policies presented in the communication.
-Second, indirectly, by conducing citizens to pay less attention to the substantive information in the communication.
-As a result, citizens disregard logically unpersuasive information that could decrease their trust.
-I examine these expectations via a survey experiment, focusing on the Israeli Environment Protection Ministry.
-The results support the hypotheses and suggest that the effect of symbolic elements is stronger when communications include logically unpersuasive information.
+Still, they did not examine the interaction between these symbols and the substantive information in communications about bureaucracies’ performance and policies.
+Exploring this interaction is important for understanding the theoretical mechanisms underlying the effect of symbolic communication on citizens’ trust.
+Also, it is essential to assess symbols' potency to unduly compensate for unfavorable or logically unpersuasive information, and enable public organizations to escape justified public criticism.
+Building on the social psychology Elaboration Likelihood Model, I theorize that symbols may increase citizens' trust by conducing citizens to pay less attention to logically unpersuasive information, and thus offsetting its negative effect.
+I test this indirect mechanism via a large survey experiment, focusing on the Israeli Environment Protection Ministry.
+The experimental results support the research hypotheses and suggest that the effect of symbolic elements is stronger when communications include logically unpersuasive information.
 I discuss the implications of these findings for democratic responsiveness and accountability.*
@@
 
-One of the main remedies proposed for this is greater investment in direct government communications to citizens.
+One of the main remedies proposed for this concern is greater investment in direct government communications to citizens.
 Congruently, over the past generation, economically-developed democratic countries have witnessed an increase in government public communications, specifically through advertising, social media, and e-government platforms [@eshuis_2012; @marland_2017; @mergel_2013; @mickoleit_2014; @canel_2013].
@@
 Communications with citizens are perceived as a means for accomplishing democratic accountability, facilitating the effective implementation of their missions, and aligning citizens' perceptions of public organizations with their actual performance [@canel_2013; @lee_2000; @lee_2012; @lee_2001; @lee_2008; @lee_2011].
-Importantly, according to this view, public communications are expected to increase citizens' trust in bureaucracies mainly insofar as these communications provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
+Importantly, according to this view, public communications are expected to enhance citizens' trust in bureaucracies mainly insofar as these communications provide citizens with favorable information on the performance of organizations and logically persuasive explanations for their policies.
 
 Recently, however, a few studies pointed to the additional effect of *symbolic* elements that are entangled in government communications, such as  agencies' names and brand logos, figures, images and celebrity endorsements [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-These studies experimentally demonstrated that government organizations may cause citizens to view them more favorably and trust them through familiar and well-designed symbolic elements that evoke positive associations and emotions.
-Still, we lack a theory and robust empirical evidence of the exact mechanisms through which these symbols increase citizens’ trust.
-These studies also did not examine the interaction between the symbolic elements and the substantive content of information in public communications.
-
-This research gap has normative significance.
-Whereas the responsiveness of citizens to substantive information is perceived favorably from a democratic standpoint (assuming that it is accurate), establishing trust through symbolic elements can be highly problematic.
+These studies demonstrated that employing familiar and well-designed symbolic elements that evoke positive associations and emotions may cause citizens to view government organizations more favorably and trust them.
+They suggested that the influence of symbols occurs unconsciously through a psychological mechanism of transfer of affect or "evaluative conditioning".
+
+The distinction between the effects of symbolic elements and substantive information in public communications has significant normative implications.
+Whereas the responsiveness of citizens to substantive information is perceived favorably from a democratic standpoint (assuming that the information is accurate indeed), establishing trust through symbolic elements can be highly problematic.
 Shaping citizens' perceptions of governments by evoking associations and emotions stands against the normative expectation that citizens' judgments should be based on their critical thinking.
 Furthermore, we need to be aware that symbolic communication may elicit undue trust in poorly performing organizations and in ill-conceived policies, and enable public organizations to escape justified public criticism [@alonbarkat_2017].
-Therefore, this study focuses on the following questions: *What are the psychological mechanisms by which symbolic elements in government communications affect citizens' trust in government organizations and their policies?
-Does the effect of symbolic elements on trust depend on the substantive content of communications?* *Do symbols offset the rational, negative effect of unfavorable or logically unpersuasive information?*
-
-To address these research questions, I draw upon the social psychology Elaboration Likelihood Model (ELM).
-ELM provides a comprehensive theoretical framework for various psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change [@petty_1986; @petty_2011].
-Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust in two ways: *First*, they may evoke positive feelings and associations that are transferred from the symbols to the relevant government entities and policies, and thereby increase citizens' trust in them.
-*Second*, symbolic elements may increase citizens' trust in government entities and policies by causing them to disregard the content of logically unpersuasive information that could otherwise decreased their trust.
+
+Whilst previous studies explored the distinct effect of symbolic elements on trust, they did not examine its interaction with the substantive information in the communication.
+Exploring this latter interaction is important for understanding the theoretical mechanisms underlying the effect of symbolic communication on citizens’ trust.
+Also, it is essential to assess the possibility that symbols can attenuate the effect of substantive information on trust, and specifically - to attenuate the rational negative responses of citizens to unfavorable or logically unpersuasive information.
+
+To theoretically address the latter research gap, I draw upon the social psychology Elaboration Likelihood Model (ELM), which provides a comprehensive theoretical framework for various psychological processes underlying individuals' responses to persuasive communication, and their consequences for attitude change [@petty_1986; @petty_2011].
+Based on ELM, I suggest that symbolic elements in public communications can affect citizens' trust not only through evaluative conditioning, as suggested by previous studies, but also by conducing citizens to pay less attention to logically unpersuasive information that could otherwise decreased their trust.
+According to the latter mechanism, symbols are expected to be more effective when used in communications that include logically unpersuasive information.
 
@@
 I explore citizens' responses to public communications about two policy plans of the Ministry.
-Specifically, I examine how their trust in these public policies is affected by the symbolic elements in the communications (real symbols vs.
-fake symbols and no symbols conditions) as well as by the substantive information in them (logically persuasive vs.
+Specifically, I examine how their trust in these policies is affected by the symbolic elements in the communications (real symbols vs.
+fake symbols and no symbols conditions) and its interaction with the substantive information in them (logically persuasive vs.
 unpersuasive policy plans).
@@
 In line with my theoretical expectations, the effect was greater among those who saw the logically unpersuasive policy plans.
-The latter were less inclined to think about the weak, unpersuasive content, because they were distracted by the symbols.
+The latter were less inclined to think about the weak, unpersuasive content, since they were distracted by the symbols.
 I discuss the theoretical and normative implications of these findings.
@@
 Symbols are fundamental for almost any form of human interaction, and specifically in the context of politics and public affairs [@edelman_1964; @edelman_1988; @elder_1983].
-Conselletions of symbols in discourse form consolidated narratives, which play an key role in shaping people's perceptions of policy problems and solutions [@miller_2012; @miller_2015].
-
-My focus in this study is on those symbols that are strategically used by government organizations in their public communications, are designed to distinguish them and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
+Constellations of symbols in discourse form consolidated narratives, which play an key role in shaping people's perceptions of policy problems and solutions [@miller_2012; @miller_2015].
+
+My focus in this study is on those symbols that are strategically used by government organizations in their public communications, and designed to distinguish them and to evoke associations and emotions that stimulate audiences’ positive affect towards organizations and their operations.
 Prominent examples are unique logos, colors associated with specific meanings, icons, images, and the use of celebrities as endorsers.
@@
 They found that the symbolic element had a positive effect on citizens' trust in the organization, including among those who personally experienced poor performance (a modest effect size equivalent to 0.25 standard deviations).
-Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations and policies associated with them ("evaluative conditioning").
+Building on social psychology theory and marketing research, they suggested that the symbols enhance trust by inducing an unconscious transfer of affect from the symbols to the organizations, after repeated linkage between them ("evaluative conditioning").
 They proposed that the effectiveness of government symbolic elements depends on their familiarity, and aesthetic design, as well as on the ambiguity of the government quality assessed.
@@
 
-Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' greater trust in public organizations and policies, they did not directly investigate the causal mechanisms that underlie this effect.
-Therefore, we still lack understanding of the circumstances under which symbols are likely to be more/less effective in shaping citizens' trust.
-Specifically, these studies neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications.
-We do not know whether well-designed symbols reinforce, or offset, citizens' rational responses to information.
-Specifically, as explained above, it is essential to assess the possibility that symbols can unduly compensate for unfavorable or logically unpersuasive information that should yield negative responses.
-
+Even though these studies substantiate a link between the appearance of symbolic elements in communications and citizens' greater trust in public organizations and policies, they neither theorized nor empirically tested the interaction between symbolic elements and citizens’ processing of substantive information in communications.
+We do not know whether well-designed symbols reinforce, or offset, citizens' responses to information.
 To address this theoretical gap in public administration research, I propose a nuanced theoretical framework for the effects of symbols in communications and their interaction with information, building on social psychology theory on persuasive communication.
@@
 Accordingly, ELM can be applied to various settings, types of attitudes and forms of communications.
-It has been specifically applied to studies on persuasion or attitudinal change in various areas, including commercial advertising [e.g.
-@petty_1983; @dotson_2000; @wheeler_2005; @moore_1987], public health campaigns [@wilson_2007; @angst_2009; @ruiter_2001; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and media entertainment [@young_2008; @slater_2002].
-So far however the relevance of ELM has not been directly examined in relation to changes in citizens' trust in public organizations in response to their public communications.
+The theory has been applied mainly in relation to commercial advertising and marketing [for a review see: @schumann_2012], but also to other communication settings, including public health campaigns [@petty_2009; @briol_2006], media coverage [@petty_2002; @vanderwurff_2016] and entertainment [@young_2008; @slater_2002].[^footnote_elm_critique] So far however the relevance of ELM has not been directly examined in relation to changes in citizens' trust in public organizations in response to their public communications.
+
+[^footnote_elm_critique]: For a summary of the ELM literature, and its main critique, see: @kitchen_2014.
 
@@
 At the high end of the elaboration continuum, also called the "central route", people are likely to respond by cognitively scrutinizing the arguments central to the merits of the issue.
-At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little cognitive effort, such as an unconscious transfer of affect[^footnote_dual_process_theories].
-In turn, these two mechanisms are likely to cause divergent types of persuasion.
+At the low end, also called "the peripheral route" people respond to simple cues automatically and unconsciously through primitive psychological processes that require very little cognitive effort.
+One of these latter processes is evaluative conditioning.[^footnote_dual_process_theories] In turn, these two mechanisms are likely to cause divergent types of persuasion.
 Persuasion via the central route is expected to be more enduring, resistant and predictive of behavior, compared with the peripheral route.
@@
 Conversely, symbolic elements are potential peripheral cues.
-they can increase citizens' trust via the peripheral route, by evoking positive emotions and associations that are attributed to government organizations and their policies [@alonbarkat_2017].
-However, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly.
-They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing substantive information that would otherwise decrease their trust, namely negative information (e.g.
+They can increase citizens' trust via the peripheral route, through evaluative conditioning.
+Importantly, in addition to their direct effect as peripheral cues, symbolic elements may also increase citizens' trust indirectly.
+They can decrease the amount of thought citizens dedicate to the communication, and thus prevent them from scrutinizing substantive information that would otherwise decrease their trust, namely unfavorable information (e.g.
 information on poor performance) and weak arguments (e.g.
 logically unpersuasive arguments supporting their actions and policies).
-The latter assertion entails an interaction between symbols and the substantive information in communications: symbolic elements in public communications are more likely to affect citizens' trust when communications include negative information or weak logical arguments.[^footnote_interaction_strong_information]
+The latter assertion entails an interaction between symbols and the substantive information in communications: symbolic elements in public communications are more likely to affect citizens' trust when communications include unfavorable information or weak logical arguments.[^footnote_interaction_strong_information]
 
@@
 
-To empirically test the above mentioned hypotheses, I designed a randomized survey experiment, which simulates citizens' responses to government organizations' communications about their policy plans.
-Such communications can be found in publicized reports, pamphlets, websites, new media pages and ads.
+To empirically test the above mentioned hypotheses, I designed a randomized survey experiment, which simulates the effects of symbols and information in government organizations' communications about their policy plans.
 I focus on communication of future policy plans, as opposed to communications on performance of existing policies.
@@
 I analyzed the effects of informative and symbolic elements in the EPM's communications of two policy plans on citizens' trust in these policies, and the extent to which they elaborated on them.
-In the survey, the communications about the two policy plans, in which I manipulated the informative and symbolic elements, are presented to the participants as sections from the EPM's official publication of its annual work plan.
+In the survey, the communications about the two policy plans are presented to the participants as sections from the EPM's official publication of its annual work plan.
 
@@
 A total of `r round((nrow(filter(SVIVA2_01,RECOGNIZE_SVIVA_logo>1))/N_1)*100,0)`% of the participants reported that they recognize the EPA logo to some extent, and a vast majority of them reported that they recognize the campaign images of Friedman and Rosenblum (`r round((nrow(filter(SVIVA2_01,RECOGNIZE_air_real>1))/N_1)*100,0)`% and `r round((nrow(filter(SVIVA2_01,RECOGNIZE_waste_real>1))/N_1)*100,0)`%, respectively).
-In robust analyses I further exclude those who do not recognize these symbols.[^footnote_prior_studies]
+In robust analyses I further exclude those who do not recognize these symbols.
+Additionally, in two prior surveys, I collected further information about the affect and symbolic associations of these symbols.
+The results of these tests, reported in the supplementary appendix, substantiate my empirical assumption that these elements evoke positive emotions, and that citizens automatically associate them with environmental protection policy and the Ministry.
 
 [^footnote_campaigns]: Multimedia files of these campaigns are available in EPM's website: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/default.aspx.
-
-[^footnote_prior_studies]: In two prior surveys, I collected further information about the affect and symbolic associations of these symbols.
-These results are reported in the supplementary appendix and substantiate my empirical assumption that these elements evoke positive emotions, and that citizens automatically associate them with the EPM.
 
@@
 In that sense, the "fake" symbols could be regarded as a placebo.
+In two prior surveys, I confirmed, empirically, that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
+The results of these examinations are reported in the supplementary appendix.
 
@@
 This allowed me later to analyze the interaction between these two manipulations both between and within-subjects.
-
-[^footnote_symbols_manipulation_checks]: In two prior surveys, I confirmed, empirically, that the fake symbols are unfamiliar, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.
-The results of these examinations are reported in the supplementary appendix.
 
@@
 The outcome variable is citizens' trust in policy (or the perceived trustworthiness of the policy).
-This variable is measured in the survey for each policy plan using a composite index of six likert scale items (Cronbach’s alpha = `r alpha_waste_trust`), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
-Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7(strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
+Trust in policy is also closely related to the concept of policy credibility [@gilardi_2002; @greasley_2014].
+It is measured in the survey for each policy plan using a composite index of six Likert scale items (Cronbach’s alpha = `r alpha_waste_trust`), which were adopted and slightly modified from validated trust scales used by previous public administration studies on trust in government [@grimmelikhuijsen_2013; @grimmelikhuijsen_2014; @karens_2016; @porumbescu_2016; @grimmelikhuijsen_2017].
+Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
 The mean of this trust index is `r SVIVA2_01_comb%>%summarise(mean(trust))%>%max()%>%round(2)`, the standard Deviations is `r SVIVA2_01_comb%>%summarise(sd(trust))%>%max()%>%round(2)` and the median is `r SVIVA2_01_comb%>%summarise(median(trust))%>%max()%>%round(2)`.
@@
 
+<br>
+
 #Discussion and conclusion
 
-A growing body of Public-Administration research seeks to assess whether and how government organizations can increase citizens' trust through direct communications with citizens.
-This study contributes to this discussion by pointing to the influence of symbolic elements in public communications, and unpacking the theoretical mechanisms underlying their effect.
-Using a rigorous experimental design, embedded in a realistic setting of the Israeli Environmental Protection Ministry, I tested the effect of symbolic elements on trust, and its interactions with the substantive content of communications.
+A growing body of Public-Administration research seeks to assess whether and how government organizations can mitigate citizens' distrust in them through direct communications with citizens.
+This study contributes to this discussion by theorizing and testing the direct and indirect mechanisms through which symbolic elements in communications can affect citizens' trust.
+Using a rigorous experimental design, embedded in a realistic setting of the Israeli Environmental Protection Ministry, I tested the interaction between symbolic elements and the substantive content of communications.
 To the best of my knowledge, this is the first study to explore this interaction in the context of government communications.
 
-I found that participants' exposure to the familiar symbols of EPM increased their trust in its policy plans, and that the effect was greater when they were presented with a weak policy plan.
-The latter interaction is partly explained by the negative effect of the symbols on the elaboration of the policy plans.
+I found that participants' exposure to the familiar symbols of EPM increased their trust in its policy plans, compared with two control groups, and that the effect was greater when participants were presented with a weak, logically unpersuasive, policy plan.
+This interaction between symbols and information is explained, in part, by the negative effect of the symbols on participants' elaboration of the information on policy plans.
+In other words, the symbols distracted participants from scrutinizing the content of the communication, thus offsetting its negative impact.
 These findings are based on analyses of the responses of more than `r (SVIVA2_01%>%nrow()%>%round(-2))-100` participants to two different policies, and are robust for various model specifications.
 Moreover, they are evidenced in both between- and within-subjects analyses.
-These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, they evoke general positive feelings that are transferred to the specific organizations and policies.
+These results, if generalizable, suggest that incorporating familiar symbolic elements in public communications increase citizens' trust in government organizations and their actions, via two mechanisms: First, symbols evoke general positive feelings that are transferred to the specific organizations and policies.
 Second, by putting citizens in a positive mood, they distract them from thinking about the substantive content of the communication, and thereby, they cause them to disregard its weaknesses.
@@
 Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.
-If this explanation holds, then result will be a ceiling effect.
-This explanation can be also linked, theoretically, to the notion of public sector negative bias, which is well established in the Public Administration.
-Since most citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations only to a certain degree.[^footnote_ceiling_effect]
+This explanation can be also linked, theoretically, to the notion of public sector negative bias [@hvidman_2018; @hvidman_2016; @marvel_2015a].
+Since many citizens tend to have implicit negative attitudes towards the public sector, they can trust public organizations only to a certain degree.[^footnote_ceiling_effect] Still, the latter tentative explanation merits further empirical testing in future research.
 
@@
 Certainly, we must be cautious when drawing general conclusions from these findings.
-This study focuses, empirically, on one public organization, characterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
+This study focused, empirically, on one public organization, characterized by relatively high investment in symbolic communications, including the use of salient public campaigns with high-profile celebrity comedians.
 Future studies may further examine the proposed theory by focusing on additional cases of public organizations and policy areas.
-In addition, this study focuses on policy plans, and therefore we must be cautious about generalizing from these findings to other types of communications.
-Specifically, future studies may seek to test my theory with regard to communications that include evidence about performance, and examine the interaction between symbols and information about good/bad outcomes.
-Another limitation of the study is the fact that it examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
-Future studies may compare the effectiveness of different types of symbolic elements.
+In addition, this study examines the accumulated effect of a bundle of symbolic elements, without disentangling the distinct effect of each symbol.
+Future studies may investigate the effectiveness of different types of symbolic elements.
+Specifically, they may directly compare symbols associated with agencies in general, specific policy programs and the policy agenda as a whole.
+
+Another important limitation of the study relates to the type of content in communications.
+This experiment utilized communications involving details and explanations about an organization's future policy plans.
+This type of content can be found in various forms of public communications, including publicized reports, pamphlets, websites, new media pages and ads.
+Still, we must be cautious about generalizing from these findings to other types of information, namely communications that include information regarding existing and previous policies or actions, and evidence about their costs and outcomes (i.e.
+performance information).
+Future studies should examine the validity of the findings in relation to these different types of content.
+Public-Administration scholars may also examine the proposed theory in relation to citizens' trust in organizations in general, rather than with regard to their specific policies.
+One can argue that altering citizens' perceptions regarding previous policies and regarding organizations in general through branding would be more difficult, since many citizens would already have formed solid opinions about them.
+Still, I tentatively expect symbols to attenuate the effect of information on poor performance, holding all else constant.
+
+Finally, this study did not directly account for the role of citizens' subjective prior attitudes about the organization.
+It might be the case that these attitudes not only affect their trust in policy, but also condition the impact of symbols.
+Indeed, previous studies suggested that citizens' negative versus positive perceptions - whether rooted in their political ideology [@teodoro_2018] or personal experience of performance [@alonbarkat_2017] - moderate the effect of agencies' branding.
+Yet, these studies regarded only the direct effect of symbols, while overlooking their indirect effect in interaction with the information.
+Also, they operationalized citizens' prior beliefs observationally, and did not directly account for their pre-manipulation attitudes about the agencies.
+Hence, future studies may rigorously examine the moderating role of prior perceptions in relation to the proposed mechanisms.
 
@@
 Citizens' responses to symbolic elements in communications thus far received relatively little attention in Public administration literature, compared with the abundant research on their responses to information.
-The latter body of literature emphasizes the cognitive biases that distort citizens' processing of information in government communications, and suggests that citizens tend to be sceptic about their positive information [@baekgaard_2016; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017b; @christensen_2018; @james_2017a; @james_2017c].
-Hence, it undermines the effectiveness of the communication of substantive information.
-Yet, this study, and others, demonstrated that symbolic communication, which requires little cognitive effort, can be fairly effective in increasing citizens' trust, and mitigating their negative attitudes [@alonbarkat_2017; @karens_2016; @teodoro_2018].
-
-Furthermore, my findings suggest that symbols decrease citizens' "rational", systematic processing of substantive information.
-This is good news as far as we are concerned mainly about the negative biases of citizens and the media regarding public organizations [@hvidman_2016; @hvidman_2018; @marvel_2015a], resulting in citizens' *undervaluation* of government performance.
-On the other hand, the emotive effect of government symbols on public opinion is highly problematic.
-It challenges the democratic ideal that citizens form their opinions about their government and its actions on the basis of rational thinking, rooted in healthy skepticism.
+The latter body of literature emphasizes the cognitive biases that distort citizens' processing of information in government communications, and suggests that citizens tend to be skeptic about positive information [@baekgaard_2016; @james_2014; @james_2017; @marvel_2015; @olsen_2017; @james_2017b; @christensen_2018; @james_2017a; @james_2017c].
+In that sense, it undermines the effectiveness of government public communications.
+Yet, this study, and others, demonstrated that branding and symbolic communications, which requires little cognitive effort, can be fairly effective in mitigating citizens’ distrust of governemnt organizations [@alonbarkat_2017; @karens_2016; @teodoro_2018].
+
+Additionally, my findings suggest that symbolic elements not only evoke positive feelings that cause citizens to view public organizations more favorably, but also decrease citizens' elaborate processing of the substantive content in their messages.
+This is good news as far as we are concerned mainly about the negative biases of citizens and the media regarding public organizations, and their *undervaluation* of government performance [@hvidman_2016; @hvidman_2018; @marvel_2015a].
+On the other hand, the decreased attention to substantive information and logical arguments and the shaping of public opinion by the emotive effect of symbols can also be highly problematic.
+To begin with, it contrasts with the normative expectation that citizens in a democracy should form their judgments about government on the basis of rational critical thinking and healthy skepticism.
 Congruently, it contrasts with the main objective of public communication to enhance bureaucracies’ accountability to citizens [@canel_2013; @lee_2012; @lee_2001; @lee_2008; @lee_2011], and with the basic moral “obligation of the public administrator to keep the public informed” [@lee_2000, 459].
 
-Moreover, the effect of symbolic elements becomes especially problematic when they are used by poorly performing organizations, or organizations that lack professional expertise.
-In those cases, symbolic elements can mitigate justified public criticism of government failures.
-Theoretically, this distortion could be either the unconscious result of an honest attemt by the bureaucracy to promote good causes, or worse - a satrategically planned "propaganda".
-This could be used for promoting the narrow political interests of parties and individual politicians controlling bureaucracies - for instance, the Minister of Environment Protection and/or his party [For exmaples of politicians' exploitation of public communications see @sanders_2013a].
-At the same time, it could also be used for promoting the interests of the bureaucracies themselves, namely nurturing their long-term positive reputation, which provides them with political power and autonomy [@busuioc_2016; @bertelli_2018].
-In any case, it may result in undermining the accountability of bureaucrats and politicians to the public, and a deviation from the model of democratic responsiveness [@dahl_1973; @soroka_2010].
-
-This study also contributes to existing behavioral Public Administration research by introducing ELM and applying it as a comprehensive theoretical framework for studying citizens' attitudes formation, and citizens' responses to government communications.
-ELM has various postulations and implications, but most importantly, it stresses that people respond differently to different communications, depending on people's motivation and ability to think about the subject, and on the quality of arguments and the peripheral cues in the communication.
-In this study, I applied ELM to theorize the direct and indirect effects of symbolic elements on trust.
-Future Public-Administration studies may apply ELM and further explore the effects of other peripheral, heuristic cues in government communications.
-They may also examine the moderating role of motivation and ability factors, to enhance our understanding of the conditions under which government communications are likely to be more/less effective.
-Future studies may also examine the postulations of ELM that persuasion via arguments is more likely to be enduring,  and to increase citizens' cooperation with government policies, compared with persuasion via symbolic elements and heuristic cues.
-
-Finally, ELM has important methodological implications regarding the external validity of survey experiment studies of citizens' responses to government communications.
-The participants of all these studies, including this one, are quite motivated to elaborate on the information that scholars present to them, since they assume that they will be asked questions about it afterwards.
-When participants receive payment or other compensation for taking part in the survey, their motivation is even higher.
-By comparison, in the "real world", citizens are far less motivated to invest in thinking about government messages, and they are probably also less able to do so, given their lack of time and low attention span.
-Accordingly, whereas previous studies have emphasized the effects of cognitive biases in citizens' processing of information [@james_2017a; @baekgaard_2016; @marvel_2015; @marvel_2015a; @hvidman_2016; @nielsen_2017; @olsen_2017], one could question the generalizability of these effects and their relation to real-world settings, where people are less inclined to process the information in the first place.
-Regardless, scholars should also take to account this methodological issue when designing survey experiments, and attempt to simulate real world conditions, as much as possible.
-For instance, they can add filler sections in the survey, before the real manipulation, to attenuate participants' motivation and ability to elaborate.
-In addition, because the graphic design of communications also affects motivation and ability to elaborate, as shown here, scholars should simulate the design of real communications.
-
-Hence, whereas government communication with citizens is normally perceived as a tool for enhancing democratic responsiveness and accountability, it can also be use it as a means to undermine them.
-##work on that##
-
-<br>
-
-##Appendix A: Information manipulation
+Moreover, altering citizens' perceptions through symbols becomes especially problematic when done by organizations that are poorly performing or that lack professional expertise.
+In those cases, symbolic elements may mitigate justified public criticism of government failures.
+For instance, they could cause citizens' to disregard information indicating that an agency did not accomplish its targets, while signaling an overall positive message about its functioning.
+Or, as illustrated by this survey experiment, they may help to build public trust in careless policy initiatives that are more likely to cause harm than good.
+Theoretically, these distortions could be either the unintended, unconscious result of an honest attempt by the bureaucracy to promote legitimate causes, or worse - a strategically planned "propaganda".
+The latter could be used for promoting the narrow political interests of parties and individual politicians controlling bureaucracies - for instance, the Minister of Environment Protection and/or his party [For empirical cases of politicians' exploitation of public communications see @sanders_2013a].
+At the same time, it could be also beneficial for the interests of the bureaucracies themselves, namely nurturing their long-term positive reputation, which would provide them with political power and autonomy [@busuioc_2016; @bertelli_2018].
+
+Regardless of the perceptions and motivations behind their employment, the results of this study suggest that symbolic elements may mitigate distrust in public organizations, but at the same time it may undermine their democratic responsiveness and accountability.
+The later concern, if valid, necessitates the development of new ethical guidelines and/or regulations for the use of symbols and brand elements in government public communications.
+
+<br>
+
+#Appendix A: Information manipulation
 
@@
 
-##Appendix B: Symbols manipulation
+#Appendix B: Symbols manipulation
 ![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/symbols_manipulation.png)

### 2019-06-20 paper3_APPENDIX_revision_01.Rmd
Add files via upload

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

<br>

Last edited at `r Sys.Date()`.

<br>

```{r , include=FALSE, echo=FALSE}
source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")

SVIVA1_01 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
CELEBS_00 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")

SVIVA2_01 = SVIVA2_01 %>%  
mutate(AREA_center = Recode(AREA,"0=1;1=0"))

SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
SVIVA2_01_center = filter(SVIVA2_01,AREA==0)

```

```{r , include=FALSE, echo=FALSE}
library(tidyverse)
library(sjPlot)
library(stargazer)
```

---

# Contents:

1. Supplementary information about the symbolic elements

2. Manipulation and validity checks

3. Summary statistics

4. Supplementary analyses

5. English translation of the survey experiment

---

<br>

# 1. Supplementary information about the symbolic elements

In this section, I provide additional details about the of EPM's "real" symbols which were used in the experiment, as well as on the fictional, "fake", symbols.

## Real symbols

The three EPM symbols which were used in the experiment are displayed in **Figure A1**. The first element is the unique brand logo of the EPM (Figure A1a). This logo consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second symbol is the color green, which is strongly associated with taking care of the environment. The EPM's logo and the green color are used in almost all of EPM's visual communications, and they represent key elements of its unique "visual identity". The third element is celebrity endorsements. The EPM's logo and the green color can be seen in almost all of the visual communications of the EPM, and they represent key elements of its unique "visual identity". The third element is celebrity endorsements. I selected two high-profile celebrity comedians, *Tal Friedman* and *Ido Rosenblum*, who previously endorsed two salient advertising campaigns of the EPM. The campaign starring the comedian Tal Friedman (Figure A1b) was launched in 2010, and included a series of advertisements in which Friedman was presented with a head covered in green grass, and accordingly the campaign's slogan was: "starting to think green". The campaign starring the comedian Ido Rosenblum (image c.) was launched in 2017, and focused on reducing the use of disposable bags. The two campaigns were highly successful in terms of their recognizability and likability, as suggested by their evaluation reports by the Government advertising agency.[^footnote_lapam_reports] The campaign images were downloaded from EPM's website, and thereafter were cropped, to remove any text (using GIMP software).

<br>
**Figure A1: symbolic elements of EPM**
![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/EPM_symbols.png) 
<font size="0.5">

Notes:

a. EPM logo.
b. Tal Friedman, comedian,  EPM campaign “starting to think green” (2010): "Isn't money growing on trees? Moving to environmental consumption and saving at least 6,000 NIS per year!", "starting to think green", "The Environmental Protection Ministry".
c. Ido Rosenblum, comedian, EPM campaign  “taking every bag seriously” (2017): "Did you forget your reusable carrier bag at home again? A tip from Ido: Hang it on the door handle and you will not leave without it", "Taking every bag seriously", "The Environmental Protection Ministry".

</font>

[^footnote_lapam_reports]: The Multimedia files and evaluation reports for the  "starting to think green" campaign, starring Tal Friedman, are available in the following link: http://www.sviva.gov.il/InfoServices/ReservoirInfo/ResearchAndPublications/Pages/Publications/P0601-P0700/P0641.aspx The media files for the "reusable bags" campaign, starring Ido Rosenblum, are available at: http://www.sviva.gov.il/InfoServices/NewsAndEvents/MessageDoverAndNews/Pages/2016/December2016/plastic-bags-campaign-2016-IR.aspx. The evaluation report for this campaign is available at: https://cdn.the7eye.org.il/uploads/2017/09/plastic-bags2017.pdf. All these materials are available in Hebrew [last entered: July 2017].

<br>

## Fake symbols

The fake symbols were specifically designed to represent graphical elements that resemble the look and aesthetic qualities of the familiar EPM symbols, as much as possible, while removing their symbolic aspects (i.e. without activating emotions and associations which can be attached to the government ministry and environmental issues). Accordingly, the green color was replaced with blue, the EPM logo is replaced by a fake logo and the images of celebrities from the campaigns are replaced with two edited images of unfamiliar people.

The fake logo was created using MS Paint software. I replaced the leaves/hands from the original logo with a shape of stars with rounded edges and replaced the green color with blue. I deliberately selected a natural element - star - as opposed to an abstract geometric element, since marketing studies have pointed to the "naturalness" of logos, as one of the key aesthetic characteristics rendering logos more memorable and favorable [@henderson_1998].

To create the fake campaign images, I searched for photos of unfamiliar male models that resemble the look of the real endorsers, Tal Friedman and Ido Rosenblum, and their face expressions in the campaign images. For this purpose, I used the website www.istockphoto.com that offers multiple collections of professional images for purchase.[^footnote_sources_fake_models] Thereafter, I took these images of models, and edited them (using GIMP software) to create images which are aesthetically similar to the original campaign images, yet without their symbolic aspects. For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue. For the Air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman). I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair. The latter addition was important, given that the green hair not only has a symbolic connotation, but also functions as an unusual, surprising element, that attracts people's attention. The original and edited photos are displayed below:

<br>

**Figure A2: fake symbolic elements.**
![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/fake_symbols_appendix.png)

<br>

[^footnote_sources_fake_models]: The original photo for the air-pollution policy was purchased from the following link: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336, The original photo for the recycling policy was purchased from the following link:
https://www.istockphoto.com/il/photo/young-man-smiling-portrait-gm516728601-48347532

<br>

# 2. Manipulation and validity checks

In this section, I report the results of the manipulation checks for the symbols and relevance manipulations, and analyses regarding the validity of the comparison between the two areas. These analyses are based on the survey data, and on two prior surveys, as described below.

## Symbols manipulation

In two prior surveys, I confirmed that the real EPM symbols are recognizable and have a positive affect, whereas the fake logo is unrecognizable, do not have strong positive or negative affect, and are not strongly associated with environment policy and EPM.

The first prior survey was conducted on May 2017 among `r SVIVA1_01 %>% nrow()` participants, which were recruited by iPanel. This survey was designed as a survey experiment, which was a first attempt to test the moderating role of personal relevance on the effects of symbols and information. However, after analyzing the results, I came to the conclusion that the experimental procedure had several methodological problems. Mainly, the assignment to experimental conditions yielded imbalanced groups, and the manipulations of symbolic elements and information ware too subtle. In addition, perceived personal relevance was measured only through the comparison between the areas (i.e. without the relevance manipulation), and the information was manipulated only with regard to the air-pollution policy. Despite these weaknesses, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data.[^footnote_prior_survey_1] In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols. The real and fake symbols conditions included the same logos and colors which were eventually used in the final experiment (but not the campaign images). At the end of the survey, participants were asked about their familiarity with the logos and colors that appeared in their policy plans, and their affect. These items and their descriptive results are presented below.

[^footnote_prior_survey_1]: Overall, the findings of this limited prior study are consistent Consistent with the findings of the main experiment, reported in the paper. The effect of the real symbols were greater among those who reside in the Haifa-Bay. Congruently, the statistical analyses yielded a negative and significant interaction between the real symbols and residence in the center. Also consistent with the main experiment, the interaction between the areas and the information manipulation was not significant.

"How familiar are you with the symbol [that appeared in the policy plans]?" (1=not at all; 7=very much)

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
set_theme("scatterw")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
        geom.size = 0.9,
        ylim=c(0,155),
        axis.title="",
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
        geom.size = 0.9,
        ylim=c(0,155),
        axis.title="",
        title = "Fake logo")

```

"When you see the symbol [that appeared in the policy plans], what does it make you feel?" (1=very negative feeling; 7=very positive feeling)

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
set_theme("scatterw")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
       title = "Fake logo")

```

Overall, these results show that the real logo is relatively recognizable and has a fairly positive affect, whereas the fake logo is unrecognized and neutral. Participants were also asked "What is the first thought / association that comes to mind when you see the symbol?"  With regard to the real logo, many of the participants filled associations related to carting for the environment. Representative examples for such answers are: "environmental protection", "a desire to protect nature and the environment", "green policy", "together for the sake of nature", "connection between nature and man". The participants were similarly asked about the first thought / association that comes to their mind when they see the color. Representative answers for the green color were: "nature", "a green and healthy environment", "environment protection". The responses for the fake logo and the blue color were more diverse, and mostly unrelated to environmental issues.

The second prior survey was conducted on January 2018 among `r CELEBS_00%>%nrow()` participants, which were similarly recruited via iPanel. This survey was designed as a pre-test that was aimed at assessing the recognizability, affect and associations of the real vs. fake campaign images. Participants were presented with the four campaign images (two real and two fake), in a random order. After every image, they were asked a series of questions regarding the familiarity and affect of the image and of the person presented. The items and their descriptive results are presented below.

"The person presented in the image is familiar to me" (1=weakly agree; 7=strongly agree)

Air-pollution policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real celeb (Tal Friedman)")

sjp.frq(CELEBS_00$air_fake_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Unfamiliar model")

```

Recycling policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real celeb (Ido Rosenblum)")

sjp.frq(CELEBS_00$waste_fake_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        xlim=c(0,110),
        axis.title="",
        title = "Unfamiliar model")

```

"The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?" (1=not at all; 7=very much)

Air-pollution policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Fake campaign")

```

Recycling policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Fake campaign")

```

"The image evokes a positive feeling" (1=weakly agree; 7=strongly agree)

Air-pollution policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Fake campaign")

```

Recycling policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Fake campaign")

```

"The image evokes a negative feeling" (1=weakly agree; 7=strongly agree)

Air-pollution policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        title = "Fake campaign")

```

Recycling policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        title = "Fake campaign")

```

These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative of positive feelings. Finally, I similarly asked subjects to describe their first thoughts/associations regarding the images of Friedman and Rosenblum from their campaigns (without any text). Most of the participants associated Rosenblum's image to the reducing the use of disposable grocery bags, in line with the campaign's message (e.g. "reusable bag", "reusable instead of disposable bag for protecting the environment"). With regard to Friedman's grass-head image from his "starting to think green" campaign, participants mostly mentioned associations related to environmental awareness (e.g. "green head, thinking about the environment", "green environment", "think green"), and to the humoristic aspect (e.g. "funny", "comedian", "Funny advertisement", "hahaha").

<br>

## Comparison between Haifa-Bay and Center

The comparison between the two areas is based on the assumption that the Air-pollution policy is perceived as more personally relevant by Haifa-Bay subjects, whereas the recycling policy is perceived as equally relevant by both groups. To test that assumption, I relied on the following question, which was included in the survey, regarding both policy plans:

"To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").

The air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents. As for the recycling policy, it is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them. The distribution of the perceived personal relevance variable of the two policies, across the two areas, is displayed in the following figures.

Air-pollution policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_air_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Center")

sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_air_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Haifa-bay")

```

Recycling policy

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_waste_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Center")

sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_waste_obs,
        type="hist",
        show.mean = T,
        ylim=c(0,600),xlim=c(0.5,7.5),
        axis.title="",
        title = "Haifa-bay")

```

Moreover, Participants in the relevance treatment group were asked to describe the most salient environmental issue in their area of residence. Indeed, most of the Haifa-Bay subjects regarded in their responses to the air-pollution generated from the industrial area, and many of them linked it to higher morbidity rates in the area. Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, whereas relatively few of them mentioned air-pollution as a prominent environmental concern in their area.

In the first prior survey, I also tested the empirical assumption that Haifa-bay subjects do not have greater knowledge on the air-pollution in their area issue, compared with the participants who reside in the Center. *First*, I assessed participants prior knowledge about the causes of the air-pollution in that area. Participants were given a list of three causes, and were asked to rank them based on their contribution to air-pollution.[^footnote_air-pollution_causes] There were no significant differences between the two areas regarding the performance in this task. *Second*, I examined participants knowledge of the effectiveness of the previous EPM policy by asking participants whether air-pollution during the past years has decreased (the correct answer), increased, or remained the same, according to EPM reports. In both groups, the vast majority of subjects were incorrect. Haifa-bay residents were only slightly more likely to state that it had decreased (`r filter(SVIVA1_01,AREA==1)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`% compared with `r filter(SVIVA1_01,AREA==0)%>%summarise(mean(HAIFA_knowledge_2)*100)%>%max()%>%round(0)`%). *Third*, subjects were asked about the frequency in which they monitor the air quality (in their area of residence). Haifa-bay subjects reported that they tend to monitor air pollution more frequently. Congruently, 48.9% of them reported that they tend to monitor it occasionally ("from time to time", but less than once a week), compared with only 28.2% of Center subjects. 34.6% of Center subjects reported that they do not monitor air pollution at all, compared with only 18.7% of Center subjects. Still, in both areas, only 2-3% of subjects reported that they monitor air pollution once a week or more frequently. Taken together, these comparisons indicate that in both areas, most people tend to have relatively little prior knowledge of the air-pollution. At the same time, some Haifa-bay subjects do have greater knowledge about it. This might suggest that on average, Haifa-bay subjects not only have greater motivation to scrutinize the communication on the policy, but also slightly greater ability to do so.

[^footnote_air-pollution_causes]: The three causes are: emissions of pollutants from the factories and refineries in the area; emissions of diesel smoke from vehicles in the area; emissions of pollutants from unauthorized coal production sites. 
<br>

## Relevance manipulation

I tested whether the priming questions in the relevance treatment condition increased the perceived personal relevance of the two policy plans (in each of the two areas). For this purpose, I relied on the above perceived personal relevance items. Table A1 shows the results of regression analyses. For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafter I add their interaction. Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans. Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative (model 2). The interpretation of this interaction suggests that the priming questions decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, but increased it among those who reside in the Center. Regarding the recycling policy, the interaction is insignificant.

**Table A1: Regression table - effect of relevance manipulation, across areas, on perceived personal relevance**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_relevance_air_1.1_apx = lm(RELEVANCE_air_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_relevance_air_1.2_apx = update(mod_relevance_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

mod_relevance_waste_1.1_apx = lm(RELEVANCE_waste_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_relevance_waste_1.2_apx = update(mod_relevance_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_relevance_air_1.1_apx,mod_relevance_air_1.2_apx,
          mod_relevance_waste_1.1_apx,mod_relevance_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)
```

<br>

# 3. Summary statistics

**Table A2: summary statistics of research variables**

```{r,results="asis", echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_01 %>% 
  select(TRUST_air_INDEX,
         TRUST_waste_INDEX,
         WITHIN_DELTA,
         AREA_center,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs,
         ENVIRONMENT_INTEREST,
         CHILDREN,
         CHILDREN_young,
         GENDER,
         AGE,
         GOV_TRUST,
         IDEOLOGY,
         EDUCATION,
         INCOME,
         HOME) %>% 
  stargazer(type="html",
            digits = 3,
            covariate.labels = c("1. Trust in Air-pollution policy",
                                 "2. Trust in recycling policy",
                                 "3. Delta (within subjects)",
                                 "4. Area (0=Haifa-Bay; 1=center)",
                                 "5. Perceived personal relevance - air-pollution",
                                 "6. Perceived personal relevance - recycling",
                                 "7. Interest in environmental issues",
                                 "8. Having children",
                                 "9. Having young children (under 12)",
                                 "10. Gender (Woman=1)",
                                 "11. Age",
                                 "12. Trust in government ministries",
                                 "13. Political Ideology (10 = extreme left)",
                                 "14. Education",
                                 "15. Income (5=high)",
                                 "16. Home ownership"))
```

<br>

**Table A3: Correlation matrix**

<font size="0.5">

```{r, echo=FALSE,warning=FALSE,message=FALSE}
SVIVA2_01 %>% 
  select(TRUST_air_INDEX,
         TRUST_waste_INDEX,
         WITHIN_DELTA,
         AREA_center,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs,
         ENVIRONMENT_INTEREST,
         CHILDREN,
         CHILDREN_young,
         GENDER,
         AGE,
         GOV_TRUST,
         IDEOLOGY,
         EDUCATION,
         INCOME,
         HOME) %>% 
  sjt.corr(triangle="lower",
           remove.spaces=T,
           digits = 2,
           na.deletion="pairwise",
           var.labels = c("1",
                          "2",
                          "3",
                          "4",
                          "5",
                          "6",
                          "7",
                          "8",
                          "9",
                          "10",
                          "11",
                          "12",
                          "13",
                          "14",
                          "15",
                          "16"))
```

</font>

# 4. Supplementary analyses

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
library(car)

SVIVA2_comb_robust_1 = SVIVA2_00 %>%
  filter(!(AGE %in% 1:17)) %>% 
  dplyr::select(IP,USER_ID,AREA,AREA_names,
      RELEVANCE_exp,RELEVANCE_exp_n,
      SYMBOL,SYMBOL_n,
      INFORMATION_air,INFORMATION_air_n,
      INFORMATION_waste,INFORMATION_waste_n,
      TRUST_air_INDEX,
      TRUST_waste_INDEX,
      ELABORATION_air_time_log,
      ELABORATION_waste_time_log,
      ELABORATION_air_time,
      ELABORATION_waste_time,
      MEMORY_air_score,
      MEMORY_waste_score,
      GOV_TRUST,
      GENDER,
      AIR_order,
      WASTE_order) %>% 
  gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
                              INFORMATION_waste),
         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
                                INFORMATION_waste_n),
         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
                                       ELABORATION_waste_time_log),
         MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
                               MEMORY_waste_score),
         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
                                       ELABORATION_waste_time)) %>% 
  mutate(TRUST_air_INDEX = ifelse(policy=="TRUST_air_INDEX",trust,NA),
         TRUST_waste_INDEX = ifelse(policy=="TRUST_waste_INDEX",trust,NA),
         INFORMATION_weak = Recode(INFORMATION,"0=1;1=0"),
         AREA_center = Recode(AREA,"0=1;1=0"),
         SYMBOL_t = factor(Recode(SYMBOL,"1=2;2=1")),
         SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
         SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")),
         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order))

```

In the tables below, I report the results of additional robust analyses testing the moderating role of the perceived personal relevance of the communications.

In **Tables A4 - A6**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures. The first measure is the number of seconds participants spent on scanning the policy plans, log transformed (hereafter: reaction time). The second measure is participants' score in a memory test, which was conducted during the survey. Participants were asked to indicate whether a list of four items were included in the second policy plan which was presented to them, of which two were/were not included (participants could also select “I don’t know”). The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero. Accordingly, participants could receive the scores of 0, 1 or 2. The third measure is the delta between trust in the strong and weak policy plans presented to each subject. This within-subject analysis utilizes the research design in which every participant was presented with one weak and one strong policies. Neither residing in the Haifa-bay nor the relevance treatment increase the elaboration of policy plans, based on these three measures.

In **Tables A7 and A8**, I replicate the main analyses while adding additional control variables. In Tables A7, I control for demographics and additional individual-level covariates, including ideology and trust in government ministries in general. In Table A8 I further control for factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media. The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (*n* = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`). Finally, in **Table A9**, I add those subjects who were filtered, except for those who are under the age of 18 (*n* = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`). In all these analyses, the effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models.

In **Table A10** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas. These analyses show that higher scores of perceived personal relevance did not attenuate the positive effect of the real symbols. However, it did slightly increase the effect of the weak information with regard to the air-pollution policy, consistent with Hypothesis 2.

<br>

<br>

**Table A4: Regression table - effect of personal relevance on reaction time**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_RT_air_1.1_apx = lm(ELABORATION_air_time_log~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_RT_air_1.2_apx = update(mod_RT_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

mod_RT_waste_1.1_apx = lm(ELABORATION_waste_time_log~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_RT_waste_1.2_apx = update(mod_RT_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_RT_air_1.1_apx,mod_RT_air_1.2_apx,
          mod_RT_waste_1.1_apx,mod_RT_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table A5: Regression table - effect of personal relevance on memory score**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_memory_air_1.1_apx = lm(MEMORY_air_score~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_memory_air_1.2_apx = update(mod_memory_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

mod_memory_waste_1.1_apx = lm(MEMORY_waste_score~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_memory_waste_1.2_apx = update(mod_memory_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_memory_air_1.1_apx,mod_memory_air_1.2_apx,
          mod_memory_waste_1.1_apx,mod_memory_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table A6: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_delta_1.1_apx = lm(WITHIN_DELTA~AREA_center+RELEVANCE_exp,data=SVIVA2_01)
mod_delta_1.2_apx = update(mod_delta_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_delta_1.1_apx,mod_delta_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Within-subject delta"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table A7: Regression table - adding control variables**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION,data=SVIVA2_01_comb)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION,data=SVIVA2_01_comb)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))

stargazer(mod_air_1.1_apx,mod_air_1.2_apx,
          mod_waste_1.1_apx,mod_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Gender (1=Woman)",
                             "Ideology",
                             "Trust in government ministries",
                             "Income",
                             "Education",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table A8: Regression table - adding personal relevance and motivational control variables**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+CHILDREN_young,data=SVIVA2_01_comb)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
mod_air_1.3_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+ENVIRONMENT_INTEREST+ENVIRONMENT_FOLLOW+CHILDREN_young,data=SVIVA2_01_comb)
mod_air_1.4_apx = update(mod_air_1.3_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak))

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+ENVIRONMENT_INTEREST+ENVIRONMENT_FOLLOW+CHILDREN_young,data=SVIVA2_01_comb)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak))

stargazer(mod_air_1.1_apx,mod_air_1.2_apx,mod_air_1.3_apx,mod_air_1.4_apx,
          mod_waste_1.1_apx,mod_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Interest in environmental issues",
                             "Follows environmental issues in media",
                             "Having young children (under 12)",
                              "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table A9: Regression table - unfiltered sample**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp,data=SVIVA2_comb_robust_1)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp,data=SVIVA2_comb_robust_1)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))

stargazer(mod_air_1.1_apx,mod_air_1.2_apx,
          mod_waste_1.1_apx,mod_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

**Table A10: Regression table - subjective reporting of perceived personal relevance**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
mod_air_1.3_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)

mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
mod_waste_1.3_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)

stargazer(mod_air_1.2_apx,mod_air_1.3_apx,
          mod_waste_1.2_apx,mod_waste_1.3_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Reported relevance",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Reported relevance x Real symbols",
                             "Reported relevance x Fake symbols",
                             "Reported relevance x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

<br>

# 5. English translation of the survey experiment

Below is the full text of the survey. Additional comments are presented in square brackets. The different experimental conditions of the two policy plans are included in the appendix of the main paper, and therefore were not included here. The original Qualtrics file is available upon request.

**Greetings,**

**We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. You have around 5-10 minutes to complete the questionnaire.**

**It is important for us to clarify that the questionnaire is voluntary. Filling out the questionnaire and submitting it represents your agreement to participate in the research. In addition, we wish to emphasize that the personal details of all the participants will remain confidential and that the data collected in the research will be used for research purposes only. You can express non-consent to participate by not filling in the questionnaire. The questionnaire is phrased in masculine form [in Hebrew] but addresses both men and women.**

**Thank you for your cooperation!**

---

**First, we would like to ask you a few general questions about your attitudes towards Israeli government ministries.**

<br>

**How would you evaluate the functioning of National Government Ministries in Israel?**

1. Very poor

2.

3.

4.

5.

6.

7. Very good

**To what extent do you do you have confidence/trust in Israeli Government Ministries?**

1. I have no confidence/trust

2.

3.

4.

5.

6.

7. I have full confidence/trust

**How would you rate your ideological standpoint on a left-right continuum?**

1. Extreme right

2.

3.

4.

5.

6.

7.

8.

9.

10. Extreme Left

---

[The following section includes a manipulation of perceived personal relevance of policy plans. Participants were randomly assigned to treatment and control conditions, as detailed below].

<br>

[Treatment]

**Now, we would like to ask you a few general questions about your interest in environmental issues.**

**To what extent are you interested in environmental issues?**

1. Hardly interested

2.

3.

4.

5.

6.

7. Very interested

**To what extent do you follow environmental issues in the media and/or in social networks?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**Compared to the current situation, do you think the government should invest more or less in dealing with environmental issues?**

1. Invest much less

2.

3.

4.

5.

6.

7. Invest much more

**In which residential area do you currently live?**

1. North

2. Haifa and the Krayot

3. Center

4. Tel Aviv

5. Lower Galilee

6. Jerusalem

7. Judea and Samaria

8. South

**What is the name of the locality where you live today? _________________**

**In your opinion, what is the most disturbing environmental problem in your area? ________________________________________**

[Control]

<br>

**Now, we would like to ask you a few general questions about your occupation.**

**In which sector are you currently employed?**

1. Private sector

2. Public sector

3. 3.	Civic Sector

4. Other

**What is your profession/field of study? ______________**

**To what extent do you think your profession is interesting?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**To what extent do you follow topics related to your area of occupation in the media and/or social networks?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**Compared to the current situation, do you think the government should assist more, or less to promote your field of occupation?**

1. Assist much less

2.

3.

4.

5.

6.

7. Assist much more

**What, in your opinion, might attract others to choose your occupation? _________________________________________**

---

**Next, we will present to you two policy plans on specific environmental issues. The policy plans are taken from the publication “Work Plans for 2018” of the Ministry of Environmental Protection, which can be downloaded from the Ministry’s website.**

**The specific policy issue is presented at the top of each policy plan, and is followed by the main actions taken by the Ministry to promote the issue.**

[Participants are then presented with the two policy plans (air-pollution and recycling), in random order. See description about the manipulations and the procedure in the main paper; Each policy plan is followed by the following questions]

**Now, we’d like to ask you a few questions about your position on the policy for “Reducing the air-pollution in the Haifa-Bay”:**

**State to what extent do you agree with each of the following sentences.**

**I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the actions mentioned in the policy plan were designed in a professional manner**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the policy plan is in the citizens’ interest.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that EPM made an honest attempt to design a good policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I believe that the Ministry of Environmental Protection aims to keep its commitments as laid out in the policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

---

**The following sentences describe the way in which you read the latest policy plan regarding “Reducing the air-pollution in the Haifa-Bay”.**

**State to what extent do you agree with each of the following sentences.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I paid full attention to reading the policy plan [I read the policy plan in depth].**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I only skimmed the actions in the policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I tried to thoroughly understand the policy plan.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**While going through the policy plan I was distracted by unrelated thoughts.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**I tried to think how the policy plan will personally affect me.**

1. Weakly agree

2.

3.

4.

5.

6.

7. Strongly agree

**Try recalling the content of the latest policy plan.**
[Each subject was asked about the latest policy plan presented to her]

**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce air pollution in Haifa Bay?**

1. Supervision of factories

2. Clean air area

3. Investment in public relations

4. The ammonia tank

5. I cannot remember

**Which of the following issues was mentioned in the framework of the Ministry's actions to reduce waste and increase recycling?**

1. Supervision of manufacturers

2. compulsory charge on carrier bags

3. Investment in public relations

4. Plastic bottles

5. I cannot remember

**To what extent did you feel that the policy on "reducing waste and increasing recycling" is personally relevant to you?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**To what extent did you feel that the policy on "Reducing the air-pollution in the Haifa-Bay" is personally relevant to you?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

**In order to make sure you read the question carefully, please type the number 9 under "Other"?**

1. Very little

2.

3.

4.

5.

6.

7. Very much

8. Other: ______

---

**We would like to ask you a few general questions:**

**What is your age?**

10----20----30----40----50----60----70----80

**What is your highest level of education?**

1.	Primary education or less

2.	Partial secondary education

3.	High education without high school diploma

4.	High education with high school diploma

5.	Non-academic tertiary education

6.	Partial academic degree

7.	Full academic degree (first degree)

8.	Full academic degree (second degree or higher).

**According to Israel's Central Bureau of Statistics the monthly average net income per household is approximately 15,500 NIS. Is your income: **

1.	Far below average

2.	Slightly below average

3.	Near average

4.	Slightly above average

5.	Far above average

**Are you a home owner?**

1. Yes

2. No

**In which residential area do you currently live?**

1. North

2. Haifa and the Krayot

3. Center

4. Tel Aviv

5. Lower Galilee

6. Jerusalem

7. Judea and Samaria

8. South

**What is your place of residence? ___________**

**Are you or one of your first-degree relatives working (or worked) in one of the factories in the Haifa Bay industrial area?**

1. No

2. Yes

**State the name of the place where you lived at high-school graduation: ____________**

**Area where you are currently working/studying?**

1. North

2. Haifa and the Krayot

3. Center

4. Tel Aviv

5. Lower Galilee

6. Jerusalem

7. Judea and Samaria

8. South

**Gender**

1.	Man

2. Woman

3.	I prefer not to answer

**What is the age of your oldest son/daughter?**

1. 0-6

2. 7-12

3. 13-18

4. 19 or more

5. I don't have any children

**Is Hebrew your native language?**

1. Yes

2. No

---

[The following section is a manipulation check for the symbols]

<br>

[For subjects assigned to the real symbols]:
**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**

**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

2.

3.

4.

5.

6.

7. Very positive feelings

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

2.

3.

4.

5.

6.

7. Very positive feelings

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much:

<br>

[For subjects assigned to the fake symbols]:
**Finally, we would like to ask you a few questions about the design of the policies that have been presented to you.**

**This is the image that appeared in the policy program "Reducing Waste and Increasing Recycling"**

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

2.

3.

4.

5.

6.

7. Very positive feelings

**This is the image that appeared in the policy program "Reducing the air-pollution in the Haifa-Bay"**

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

2.

3.

4.

5.

6.

7. Very positive feelings

**We would like to show you additional images, taken from advertisements of the Environmental Protection Ministry.**

[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

2.

3.

4.

5.

6.

7. Very positive feelings

**The image is taken from an advertisement of the Environmental Protection Ministry. To what extent do you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much:

<br>

[For subjets assigned to the no symbols]:

**Finally, we would like to show you a few images which were taken from advertisements of the Environmental Protection Ministry.**

[Respondents are displayed with the two "real" images, and then asked for each of them the following two questions]

**When you see the image, what feelings does it invoke?**

1. Very negative feelings

2.

3.

4.

5.

6.

7. Very positive feelings

**The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent do you remember the advertisement?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much

**This is the symbol of the Ministry of Environmental Protection, which appeared in the policy program. To what extent are you familiar with the symbol?**

1. Not at all

2.

3.

4.

5.

6.

7. Very much:

---

**Thank you very much for participating in the study. Some of the policy programs presented to you during the questionnaire included content that was different from the original work plan or was presented differently. The tasks related to “raising awareness” and “reducing supervision” are fictional tasks that are not part of the Ministry of Environmental Protection’s policy. [For the fake symbols: In addition, the pictures of the people presented in the programs were not taken from the ministry’s broadcasts, and their characters were used only for research purposes.]**

**You may review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.**

<br>

# References

### 2019-06-20 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

---
title: "The persuasion of symbolic elements in government public communications, and their moderation by personal relevance"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
urlcolor: blue
---

<br>

Draft, last edited at `r Sys.Date()`.

```{r , include=FALSE, echo=FALSE}
#load("SVIVA_R_ENV.RData")
source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")

SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
SVIVA2_01_center = filter(SVIVA2_01,AREA==0)
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
N_raw = nrow(SVIVA2_raw_00)
N_0=SVIVA2_00%>%nrow()
N_1=SVIVA2_01%>%nrow()

filter_IP = N_0-(SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE)%>%nrow())
filter_age = N_0-(SVIVA2_00 %>%
  filter(!(AGE%in% 1:17))%>% nrow())
filter_IMC = N_0-(SVIVA2_00 %>%
  filter(IMC==1)%>% nrow())
filter_time = N_0-(SVIVA2_00 %>%
  filter(TIMER_total>=3,TIMER_total<=30)%>%nrow())

N_1_haifa = filter(SVIVA2_01,AREA==1)%>%nrow()
N_1_center = filter(SVIVA2_01,AREA==0)%>%nrow()

```

<br>

---

# Abstract

*Recent studies demonstrated that symbolic elements in government communications can enhance citizens' trust in government organizations and policies. The emotive effect of symbols can further compensate for organizations' poor functioning, thereby eliciting undue trust. This study explores the boundaries of governments' persuasion of citizens through symbolic communication. Building on social psychology, I hypothesize that citizens are less susceptible to symbols, the more they perceive the policy issue in the communication as personally relevant. I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted area. The policy's perceived personal relevance is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere. The results indicate that even high levels of perceived personal relevance do not attenuate the symbols' effect, which entails that the boundaries of persuasion through symbols are wider than expected.*

<br>

*Keywords: Government communications; Government branding; Trust; Experiment*

---

<br>

# Introduction

A growing public administration literature explores whether government public communications can enhance citizens' trust in public organizations and policies. Most studies have focused on the *informative* aspects of government communications [e.g. @marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011]. Recent studies, however, further pointed to the emotive effect of symbolic elements entangled in communications, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017]. Such symbols and others exist in almost every government communication, and most prominently in public campaigns and branding activities,[^footnote_branding] which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].

Governments' employment of symbolic communications and branding can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016]. Accordingly, it can mitigate citizens' distrust in government organizations and enhance their collaboration with their policies. On the other hand, one can argue that the persuasion of citizens through symbols is problematic, since the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment. Furthermore, symbols can compensate for organizations' poor performance and for logically unpersuasive informative content, as empirically demonstrated by previous studies [@alonbarkat_2017; @alonbarkat_2018]. They can yield a misalignment between citizens' positive perceptions and the "real world". This raises the concern that government organizations will strategically exploit symbols to manipulate public opinion and mitigate justified public criticism of their failures.

[^footnote_branding]: A symbol can be as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp. 28-29]. Eshuis and Klijn [-@eshuis_2012, p. 19] define brand as *a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it*. Brand elements, therefore, can be regarded as symbolic elements.

To assess the above concern, this study explores the boundaries of governments' persuasion of citizens through symbolic communication. Namely, I seek to examine the conditions under which symbolic elements are likely to be more, or less, effective in shaping (and possibly manipulating) citizens' trust. Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I theorize that citizens are less susceptible to symbols, and more inclined to scrutinize the substantive content of communication, the more they perceive the policy issue at hand as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information. Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay). I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others. The results indicate that even high levels of perceived personal relevance do not attenuate the effect of symbols on citizens' trust, contrary to my expectations. These findings may suggest that the boundaries of the effect of symbolic communication are wider than expected. I discuss the theoretical and normative implications of these findings.

<br>

# The persuasion of symbols and information in government public communications.

The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a comprehensive theoretical framework for investigating the effects of communications on people's attitudes [@petty_1986; @petty_2011]. According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it. When people have high motivation and ability to elaborate on a message, they are likely to focus on the arguments in the communication that are central to the merits of the issue, and scrutinize them ("central route"). Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route"). These two routes for persuasion are regarded as two ends of an "elaboration continuum". People may also be located between these two ends of the continuum, and then a mixture of these processes will determine their persuasion.

Viewed against the above theoretical framework, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route). Conversely, symbolic elements can be regarded as peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route). Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on substantive information. Conversely, the less motivated and capable they are to elaborate, the more susceptible they are to symbolic elements in the communication.

This literature has pointed to a variety of factors that shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues. Among others, scholars have theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater. This postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989]. These studies have demonstrated that increasing the perceived personal relevance of a communication enhances the effect of its argumentation and attenuates the effect of peripheral cues. Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors]

[^footnote_elm_factors]: For a thorough review of motivational and ability factors affecting likelihood to elaborate see @petty_1998.

Connecting the above public administration literature on citizens' responses to government public communications with the social psychology ELM literature, I theorize that:

*H<sub>1</sub> - Symbolic elements in communications are less (more) likely to increase citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*

*H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*

These theoretical hypotheses are graphically displayed in **Figure 1**.

<br>

[Figure 1 about here]

<br>

# Research design

In this paper, the above-mentioned theoretical expectations are tested via a randomized survey experiment, building on the methodology of @petty_1983. Focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM), I examine citizens' responses to communications of EPM regarding two of its current policy plans. The first policy regards *reducing the air pollution in the highly polluted Haifa-Bay area*, located in the north of Israel. This policy issue offers a fortunate case for examining the moderating role of perceived personal relevance. The distinction between those who reside in the polluted area and those who do not represents natural variation in personal relevance. Moreover, because this policy issue is intangible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as is the case in many other policy issues [@petty_1983]. Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize the communication about the air-pollution in their area of residence, yet are no more capable of doing so than those who reside elsewhere. As explained below, the sample population of the study consists of residents of the Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile. The second policy plan regards *reducing domestic waste and increasing recycling*. This topic is assumed to be equally relevant for Haifa-bay residents and others. Therefore, adding this policy plan is intended to confirm that respondents’ divergent responses to the symbolic elements in the communication regarding the air-pollution policy, if found, may be attributed to differences in perceived personal relevance. I henceforth refer to these two policy plans as "air-pollution" and "recycling".

I exploited three symbolic elements, which have been used in the EPM's public communications, and became widely recognized by the public. The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment. The second element is the green color, which is strongly associated with taking care of the environment. The third element are the images of two high-profile celebrity comedians which were taken from advertising campaigns of the EPM. Further details about these symbolic elements are found in the supplementary appendix.

<br>

## *Data collection*

The survey was conducted online through Qualtrics Survey Software. To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country (hereafter "center").[^footnote_cities] To select and recruit residents of the selected cities, I was assisted by an Israeli internet research panel company *iPanel*. The online survey link was sent by iPanel, between 28.1-1.2.2018. A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%). After filtering,[^footnote_filters] I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.

[^footnote_cities]: The cities from the Haifa-Bay area are: *Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*. The matched cities from the center are: *Natania*, *Petach-Tikva* and *Rishon-Lezion*. The socioeconomic characteristics of the cities are summarized in the supplementary appendix.

[^footnote_filters]: I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`). These filters are neither associated with the areas nor with the experimental conditions.

<br>

## *Procedure*

The survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general. After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance). Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field. These questions were designed to prime subjects to think about the impact of environmental issues to their own lives. Subjects were also asked to describe the most salient environmental issue in their particular area of residence. The latter open question was specifically designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area. Subjects in the relevance control group were asked equivalent questions about their field of occupation.

Participants were then presented with the two policy plans of EPM, and informed that these were obtained from EPM's annual work plan. Each policy plan was followed by questions about respondents' trust in them. Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e. logically persuasive policy plan) or weak policy (i.e. logically unpersuasive). Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order. The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals. The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.

The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols". In the symbol treatment condition, the two policies (as explained, one weak and one strong) are displayed with the EPM logo, green color and celebrity images from campaigns. In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images. In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with images of unfamiliar people. The symbols conditions are displayed in **Appendix B**. Further details about the real and fake symbols are found in the supplementary appendix.

Altogether, per each policy plan, the experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs. weak policy) x 2 (relevance: treatment vs. control).[^footnote_information_symbols_paper]  The assignment to the different experimental groups, across the two areas, is graphically presented in **Figure 2**. The experimental groups are fairly balanced with respect to the two areas, as well as to demographics, and pre-manipulation variables.

[^footnote_information_symbols_paper]: In addition to the above-mentioned hypotheses, the experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration. In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance. The methodological aspects which are relevant for examining the additional hypotheses are described in a separate paper.

<br>

[Figure 2 about here]

<br>

## *Variables*

```{r, echo=FALSE, warning=FALSE, message=F}
alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
                               TRUST_air_q2,
                               TRUST_air_q3,
                               TRUST_air_q4,
                               TRUST_air_q5,
                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)

alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
                               TRUST_waste_q2,
                               TRUST_waste_q3,
                               TRUST_waste_q4,
                               TRUST_waste_q5,
                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)

alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)

```

The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies, respectively). This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018]. Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan. Participants reported, on average, lower trust in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).

The key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The latter is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation). I coded living in Haifa-bay area according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities. My data confirms that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant. Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects made reference to air-pollution. As for the relevance priming questions, however, manipulation checks suggest that those in the relevance treatment group did not perceive either of the two policies as more personally relevant. This limitation should be kept in mind when interpreting the results regarding this manipulation. The results of all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.

[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.

<br>

# Results

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
sd_trust_air = SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
sd_trust_waste = SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max()

mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))

mod_waste_1.1 = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))

mod_air_1.1_r1 = lm(TRUST_air_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)
mod_waste_1.1_r1 = lm(TRUST_waste_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)

```

**Table 1** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policy plans, and their interaction with the two areas. Models 1.1-1.3 regard the Air-pollution policy, and Models 1.4 - 1.6 regard the recycling policy. I regress trust in policy on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).

The real symbols had positive main effects on both policies compared with the no symbols condition (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations for the air-pollution and recycling policies, respectively). Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, and only marginally significant compared with the recycling policy (*p* = `r (summary(mod_waste_1.1_r1)$coefficients["SYMBOL_t.r1",4]/2)%>%round(2)`, one-tailed). The weak (versus strong) information manipulation also has a significant main effect in both policy plans, as expected (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations, respectively). Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in both the air-pollution policy, and, to a lower degree, the recycling policy. The latter effect suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, which to some extent extends towards EPM or environmental policy in general.

Keeping in mind these main effects, I now turn to analyze the interactions between the manipulations and the areas. With regard to the air-pollution policy, my first hypothesis entails a positive coefficient to the interaction between residence in the center (i.e. low personal relevance) and the real symbols. Based on my second hypothesis, I expect to find a positive interaction between center residents and weak information. Counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative (*p*<.1), and the interaction with the weak information is insignificant. I also found similar patterns regarding the recycling policy: in Model 1.6, the interaction between residing in the center and the weak information is insignificant, and the interaction with the real symbols is negative and significant. Figure 3 provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies. The findings, as illustrated in **Figure 3**, suggest that the real symbols were more effective in increasing the trust of those residing in the polluted area and that the latter were no more likely to scrutinize the content of the communication.

<br>

[Table 1 about here]

<br>

[Figure 3 about here]

<br>

Next, I examine whether those subjects who were primed to think about the personal relevance of these policy plans were more likely to scrutinize them, and less likely to be affected by the familiar symbols. The interaction between the relevance manipulation and the symbols and information manipulations is presented in **Table 2**. Again, the first three models regard the Air-pollution policy, and the remaining models regard the recycling policy. Models 2.1, 2.4 replicate models 1.1, 1.4 while adding the relevance manipulation. Thereafter, I add the interactions between the relevance manipulation and the symbols and information manipulations (Models 2.2, 2.5). Finally, to test the moderation of the relevance manipulation within each area, I add three-way interactions with the areas (Models 2.3, 2.6). In all these models, the relevance treatment did not yield significant effects, and there are no significant interactions with the symbols and information manipulations. The triple interactions with the areas are also insignificant (in Models 2.3, 2.6), which indicates that the relevance treatment did not moderate the effects of the symbols and information manipulations across the two areas.

<br>

[Table 2 about here]

<br>

I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix. *First*, I also relied on subjects' subjective reporting of the personal relevance of the policy plans, in addition to the above operationalizations. *Second*, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey, which were again insignificant: the time participants spent on scanning the policy plans and their score in a memory test. I also tested whether personal relevance decreased the delta (within-subjects) between trust in the strong and weak policy plans presented to each subject. *Third*, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues. Finally, I replicated my analyses on the unfiltered sample. None of these multiple robust analyses supports the theoretical hypotheses regarding the moderation of personal relevance on the effect of symbols. The interaction between personal relevance and information is confirmed only by the analysis of participants' subjective reporting of the personal relevance, and only with regard to the air-pollution policy.

<br>

# Discussion and conclusion

Public communications have been proposed as a remedy for citizens’ low trust in government, and for their underestimation of public-service performance. Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries. This study contributes to the growing Public-Administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications. I explored the expectation, derived from social psychology, that citizens are less affected by symbols and more likely to scrutinize the content of the communication the more they perceive it as relevant to their own lives. I put these hypotheses to rigorous empirical testing, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry. I exploited the natural variation in citizens' perceptions of the personal relevance of the ministry’s policy plan regarding air pollution in a specific area. In addition to utilizing these natural differences, I also manipulated the personal relevance of the policy plans. To the best of my knowledge, this is the first study to assess the moderating role of perceived personal relevance on citizens' responses to government symbolic communications or branding.

Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that high levels of perceived personal relevance attenuate the effect of symbols on citizens' trust. Subjects residing in the polluted Haifa-Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center. However, despite these significant differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication. If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects. Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also failed to moderate the effects of the symbols and information in the communications. These findings are also consistent with the findings of @alonbarkat_2017, where they found that the trust of citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) was nonetheless significantly affected by a symbol of the government-owned electricity company.

How can we explain the finding that the positive effect of the real symbols was stronger among Haifa-Bay residents? Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance. Rather, it might be explained by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM. Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e. as in the case of Haifa-Bay subjects), than shifting them from medium to high levels (i.e. as in the case of center subjects), indicating a ceiling effect. Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] A related explanation is that the symbols distracted the subjects and decreased their inclination to think about the topic. As a result, they caused Haifa-bay subjects to disregard their prior beliefs about EPM and its failure regarding air-pollution.[^footnote_mediation_elaboration]:

[^footnote_ceiling_effect]: This tentative explanation is supported by the fact that the interaction remains intact when controlling for demographic differences between the areas. It is also supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies. This comparison shows a pattern of decreased marginal reduction. In the Haifa-Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased by from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%. In the center, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group. With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa-bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.

[^footnote_mediation_elaboration]: This explanation is further supported by the survey data. The real symbols had a negative effect on the elaboration of these policies,  as measured by reaction time and memory test. The decrease in elaboration mediates the effect of symbols on trust.

How can we reconcile the findings of this study with the proposed theory? One plausible explanation is that despite the relatively high involvement of Haifa-bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues. If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance. Indeed, Petty and Cacioppo have admitted that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p. 206].

The results of this study, if generalizable, have significant implications. They challenge the rationalistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability. Instead, they suggest that more often than not, citizens rely on brands and other symbolic elements in public communications, even with regard to policy issues that have direct implications on their own lives. Altogether, this study highlights the role played by government branding and other forms of symbolic communication in shaping citizens view of governments. It suggests that the boundaries of persuasion via symbols and branding are much wider than expected, based on previous social psychology and marketing studies. From the practical point of view of government organizations, this entails that organizations can overcome citizens distrust by investing in symbolic communications. Nonetheless, employing a broader perspective of democratic theory, these conclusions are disturbing insofar as they buttress the concern that government organizations will deliberately use symbolic communications to cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements, namely as "propaganda". For good or for ill, citizens are affected by the emotional connections and associations of symbols.

Notwithstanding these conclusions, the limitations of this study should be acknowledged. The study focuses, empirically, on one specific case. Future studies may put these findings to further test by examining additional cases of public organizations and policy areas, as well as different forms of communications. Additionally, the comparison between the two areas is imperfect, insofar as the differences in personal relevance are confounded with differences in prior beliefs about the subject, which I cannot effectively control. A comparison between two groups that have similar prior beliefs would be more reliable. Finally, one can question the validity of the relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications. Still, the main results are robust to different model specifications, and operationalizations of personal relevance and message elaboration, which substantiate their validity.

## Appendix A: Information manipulation

**Air-pollution policy** (Reducing the air-pollution in the Haifa-Bay)

EPM is working to reduce the air-pollution in the Haifa-Bay by:

*Strong*

* **Increasing the supervision of the factories in Haifa-Bay**.
In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways. The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the level of fines for polluters.

* **Reduction of emissions from vehicles in Haifa Bay**.
The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area. The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and the designation of a "clean-air district" from which polluting vehicles are banned.

*Weak*

* **Decreasing the supervision of factories in Haifa-Bay**.
The Ministry is preparing for a change in the method of supervision of the factories. The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the level of fines. The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.

* **Raising citizens' awareness of the efforts to improve air quality**.
In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful. The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents. To this end, the ministry has increased its investment in public relations and publicity on this subject.

<br>

**Recycling policy** (Reducing waste and increasing recycling)

EPM is working to reduce the amount of waste and increase recycling through:

*Strong*

* **Packaging recycling - Increased supervision of manufacturers**.
In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, under which manufacturers and importers are responsible for recycling their packaging materials. The Ministry will work to increase enforcement by virtue of this act, and will enforce it for additional manufacturers and importers.

* **Reducing the usage of disposable bags**.
In order to reduce the use of disposable plastic bags, the Ministry has enforced the Carrier Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the retail chains themselves. The Ministry is working to implement the act, and to encourage the transition to reusable grocery bags.

*Weak*

* **Packaging recycling - Decreased supervision of manufacturers**.
The Ministry is preparing to a change in the way manufacturers, who are responsible for the recycling of product packaging, are supervised. The ministry will reduce the number of inspections, rely on manufacturers' own reporting regarding their compliance with the requirements of the act, and will reduce the level of fines. The change is coordinated with industry representatives, who are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.

* **Reducing the usage of disposable bags**.
In recent years, the Ministry has taken steps to encourage the reduction of waste, which have been partially successful. The Ministry works to raise awareness of the actions taken and to highlight their success in order to improve its image among the public. To this end, the ministry has increased its investment in public relations and publicity in this subject.

<br>

## Appendix B: Symbols manipulation
![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/symbols_manipulation.png)

<font size="0.5">

*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*

</font>

<br>

# References

<br>

# Figures and tables

<br>
**Figure 1: Theoretical model**
![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/theoretical_model_relevance.png)

<br>

**Figure 2: Experimental design for policy plan communications**
![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/experiment_flow_relevance.png)

<br>

**Table 1: Regression analyses – observational measure for perceived personal relevance.**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
stargazer(mod_air_1.1,mod_air_1.2,mod_air_1.3,
          mod_waste_1.1,mod_waste_1.2,mod_waste_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

```

&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).

<br>

**Figure 3: The effect of symbolic elements on trust across areas**

```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
SVIVA2_01_comb = SVIVA2_01_comb %>% 
  mutate(POLICY_n = Recode(policy,"'TRUST_air_INDEX'='Air-pollution'; 'TRUST_waste_INDEX'='Recycling'"))

ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
  theme_classic()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.65),
               width=0.2,size=0.5,position=position_dodge(0.2),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.2))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.2),alpha=0.8)+
  scale_shape_manual(guide=F,values=c(19,1))+
  scale_linetype_manual(name="Area",values=c(1,4))+
  facet_grid(~POLICY_n)+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))

```

<font size="0.5">

*Note*: Error bars represent 90% confidence intervals.

</font>

<br>

**Table 2: Regression analyses – experimental manipulation of perceived personal relevance.**

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_air_2.1 = lm(TRUST_air_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
mod_air_2.2 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
mod_air_2.3 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
mod_air_2.4 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)

mod_waste_2.1 = lm(TRUST_waste_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
mod_waste_2.2 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
mod_waste_2.3 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
mod_waste_2.4 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)

stargazer(mod_air_2.1,mod_air_2.2,mod_air_2.4,
          mod_waste_2.1,mod_waste_2.2,mod_waste_2.4,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Relevance treatment",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information",
                             "Area (0=Haifa-Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment x Area",
                             "Relevance treatment x Area x Real symbols",
                             "Relevance treatment x Area x Fake symbols",
                             "Relevance treatment x Area x Weak Information"),
          omit.stat = c("rsq","ser", "f"),
          order = c(1,2,4,3,6:8,5,9,10,12,11,13:15),
          initial.zero = FALSE,
          notes = "",
          notes.append = FALSE)

```

<br>

### 2019-06-20 power_estimate_01.Rmd
Add files via upload

---
title: "power calculations"
author: "Saar Alon-Barkat"
date: "6/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r , include=FALSE, echo=FALSE}
library(dummies)
library(plyr)
library(tidyverse)
library(pwr)

set.seed(2018)
```

```{r , include=FALSE, echo=FALSE}
source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")

SVIVA1_01 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
CELEBS_00 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")

SVIVA2_01 = SVIVA2_01 %>%  
mutate(AREA_center = Recode(AREA,"0=1;1=0"))

SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
SVIVA2_01_center = filter(SVIVA2_01,AREA==0)

```

I sought to get a sample of 800 respondents

# Power for main effects

Main effect for symbols:
```{r}
pwr.t.test(power = 0.8,
           n=nrow(SVIVA2_01)/3,
           #d=0.22,
           sig.level = 0.1)
```

For sample of 286 subjects in each group, detectable effect (sig. = 0.05, one-tailed test, power = 0.8) is Cohen's D = 0.20.

<br>
Main effect for information:
```{r}
pwr.t.test(power = 0.8,
           n=nrow(SVIVA2_01)/2,
           #d=0.18,
           sig.level = 0.1)
```
For sample of 430 subjects in each group, detectable effect (sig. = 0.05, one-tailed test, power = 0.8) is Cohen's D = 0.17.

<br>

# Power for conditional effects (within each area)

## symbols

Conditional effect for symbols in Haifa-bay area:
```{r}
pwr.t.test(power = 0.8,
           n=nrow(SVIVA2_01_haifa)/3,
           #d=0.22,
           sig.level = 0.1)
```
For sample of 165 subjects in each group, detectable effect (sig. = 0.05, one-tailed test, power = 0.8) is Cohen's D = 0.27.

Conditional effect for symbols in Center area:
```{r}
pwr.t.test(power = 0.8,
           n=nrow(SVIVA2_01_center)/3,
           #d=0.22,
           sig.level = 0.1)
```
For sample of 121 subjects in each group, detectable effect (sig. = 0.05, one-tailed test, power = 0.8) is Cohen's D = 0.32.

<br>

## Information

Conditional effect for information in Haifa-bay area:
```{r}
pwr.t.test(power = 0.8,
           n=nrow(SVIVA2_01_haifa)/2,
           #d=0.18,
           sig.level = 0.1)
```
For sample of 248 subjects in each group, detectable effect (sig. = 0.05, one-tailed test, power = 0.8) is Cohen's D = 0.22.

<br>

Conditional effect for information in center area:
```{r}
pwr.t.test(power = 0.8,
           n=nrow(SVIVA2_01_center)/2,
           #d=0.18,
           sig.level = 0.1)
```
For sample of 248 subjects in each group, detectable effect (sig. = 0.05, one-tailed test, power = 0.8) is Cohen's D = 0.26.

<br>

# Power for interactions

<br>

the code is based on http://disjointedthinking.jeffhughes.ca/2017/09/power-simulations-r/

<br>

## Actual models

First - creating models (for air pollution policy)
```{r}
mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
```

```{r}
n.mod_air_1.3=mod_air_1.3$fitted.values %>% length()

#intercept
b0.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="(Intercept)") %>% 
  select("estimate") %>% 
  max()

#effect of real symbols 
b1.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="SYMBOL_t1") %>% 
  select("estimate") %>% 
  max()

#effect of fake symbols 
b2.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="SYMBOL_t2") %>% 
  select("estimate") %>% 
  max()

#effect of weak information
b3.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="INFORMATION_weak") %>% 
  select("estimate") %>% 
  max()

#effect of center area
b4.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="AREA_center") %>% 
  select("estimate") %>% 
  max()

#real symbols x area
b5.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="SYMBOL_t1:AREA_center") %>% 
  select("estimate") %>% 
  max()

#fake symbols x area
b6.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="SYMBOL_t2:AREA_center") %>% 
  select("estimate") %>% 
  max()

b7.mod_air_1.3 = mod_air_1.3 %>% broom::tidy() %>% 
  filter(term=="INFORMATION_weak:AREA_center") %>% 
  select("estimate") %>% 
  max()

# p = character, which variable do you want to test for? for interactions, specify x1:x2. See below.

# err_mean = mean of residuals. Worth checking in your data. Using 0 for now.
err_mean.mod_air_1.3 = mean(mod_air_1.3$residuals)

# err_sd = sd of residuals. Using 1 for now. Even more important, if you can add this based on your data, your power calculations will be most accurate
err_sd.mod_air_1.3 = sd(mod_air_1.3$residuals)
```

```{r}
regression_simT1 <- function(simNum, 
                             n, 
                             b0, 
                             b1, 
                             b2, 
                             b3, 
                             b4, 
                             b5, 
                             b6, 
                             b7, 
                             p,
                             err_mean, 
                             err_sd) {
  # create independent variables that match your data
  symbols <- sample(1:3, n, replace=TRUE)
  symbols <- dummy(symbols) # this is because we need two separate b's
  symbols1 <- symbols[,1]
  symbols2 <- symbols[,2]
  info <- sample(0:1, n, replace=TRUE)
  area <- sample(0:1, n, prob = c(1-mean(SVIVA2_01$AREA_center),mean(SVIVA2_01$AREA_center)), replace=TRUE)

  # DV is based on your variables, coefficients and a random error
  # if you have the mean and sd of your residuals, according to your model,
  # plug them into argument err_mean and err_sd; will be more accurate.
  y <- b0 + (b1 * symbols1) + (b2 * symbols2) + (b3 * info) + 
    (b4 * area) + (b5 * area * symbols1) + (b6 * area * symbols2) +
    (b7 * area * info) + rnorm(n, mean=err_mean, sd=err_sd)

  model <- lm(y ~ area*symbols1 + area*symbols2 + area*info)
  summary(model)

  output <- summary(model)$coefficients
  ps <- output[which(row.names(output)==p), 4]
  names(ps) <- "p"
  return(ps)
}

```

Power for real symbols versus control no symbols
```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT1, 
              n = n.mod_air_1.3, 
              b0 = b0.mod_air_1.3,
              b1 = b1.mod_air_1.3,
              b2 = b2.mod_air_1.3, 
              b3 = b3.mod_air_1.3, 
              b4 = b4.mod_air_1.3, 
              b5 = b5.mod_air_1.3, 
              b6 = b6.mod_air_1.3, 
              b7 = b7.mod_air_1.3, 
              p = "area:symbols1", # must specify this exactly as it would appear in the table of coefficients
              err_mean=err_mean.mod_air_1.3, 
              err_sd=err_sd.mod_air_1.3)
(power_air <- sum(sims$p < .05) / nrow(sims))

```

Power for weak information
```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT1, 
              n = n.mod_air_1.3, 
              b0 = b0.mod_air_1.3,
              b1 = b1.mod_air_1.3,
              b2 = b2.mod_air_1.3, 
              b3 = b3.mod_air_1.3, 
              b4 = b4.mod_air_1.3, 
              b5 = b5.mod_air_1.3, 
              b6 = b6.mod_air_1.3, 
              b7 = b7.mod_air_1.3, 
              p = "area:info", # must specify this exactly as it would appear in the table of coefficients
              err_mean=err_mean.mod_air_1.3, 
              err_sd=err_sd.mod_air_1.3)
(power_air <- sum(sims$p < .05) / nrow(sims))

```

<br>

## Effects from Petty et al. 1983

Petty, R. E., Cacioppo, J. T., & Schumann, D. (1983). Central and Peripheral Routes to Advertising Effectiveness: The Moderating Role of Involvement. The Journal of Consumer Research, 10(2), 135. doi:10.1086/208954

Table in p. 141

```{r}
b0.petty <- 1.98
b1.petty <- (1.80-1.63)/2 - (1.98-1.10)/2
b2.petty <- 0
b3.petty <- (-1.10+(-1.36))/2 - (1.98+1.80)/2
b4.petty <- 0.98 - 1.98
b5.petty <- ((1.21+1.85)/2 - (-0.12+0.98)/2) - b1.petty
b6.petty <- 0
b7.petty <- ((-0.12+1.21)/2 - (0.98+1.85)/2) - b3.petty

sd.petty.dv <- (1.81+1.52+1.66+1.25+2.28+1.59+1.65+1.07)/8
```

DV = ~ 1.60

Coefficients:
Conditional effect of symbols on low involvment group = `r b1.petty+b5.petty` (1.1).
coefficient of interaction symbols*involvement = `r b5.petty` (1.455).

Conditional effect of information on high involvement group = `r b3.petty` (-3.12)
coefficient of interaction weak_information*involvement = `r b7.petty` (2.25).

Power for real_symbols*low_involvement
```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT1, 
              n = n.mod_air_1.3, 
              b0 = b0.petty,
              b1 = b1.petty,
              b2 = b2.petty, 
              b3 = b3.petty, 
              b4 = b4.petty, 
              b5 = b5.petty, 
              b6 = b6.petty, 
              b7 = b7.petty, 
              p = "area:symbols1", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .05) / nrow(sims))
```

Power for weak_information*low_involvement
```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT1, 
              n = n.mod_air_1.3, 
              b0 = b0.petty,
              b1 = b1.petty,
              b2 = b2.petty, 
              b3 = b3.petty, 
              b4 = b4.petty, 
              b5 = b5.petty, 
              b6 = b6.petty, 
              b7 = b7.petty, 
              p = "area:info", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .05) / nrow(sims))

```

##Simulating other interactions

```{r}
sd.trust.air = sd(SVIVA2_01_comb$TRUST_air_INDEX,na.rm = T)
```

SD of Trust in air-pollution = 1.54

### interactions with area

Simulations show that an interaction (symbol*area) coefficient of more than 0.27 SDs is detectible (sig. = 0.05, one-tailed test, minimum power = 0.8).

```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT1, 
              n = n.mod_air_1.3, 
              b0 = b0.mod_air_1.3,
              b1 = sd.trust.air*0.5,
              b2 = 0, 
              b3 = 0, 
              b4 = b4.mod_air_1.3, 
              b5 = sd.trust.air*0.27, 
              b6 = 0, 
              b7 = 0, 
              p = "area:symbols1", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .1) / nrow(sims))

```

Simulations show that an interaction (information*area) coefficient of more than 0.23 SDs is detectible (sig. = 0.05, one-tailed test, minimum power = 0.8).

```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT1, 
              n = n.mod_air_1.3, 
              b0 = b0.mod_air_1.3,
              b1 = 0,
              b2 = 0, 
              b3 = sd.trust.air*0, 
              b4 = b4.mod_air_1.3, 
              b5 = 0, 
              b6 = 0, 
              b7 = -sd.trust.air*0.23, 
              p = "area:info", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .1) / nrow(sims))

```

# Relevance manipulation

```{r}
regression_simT2 <- function(simNum, 
                             n, 
                             b0, #intercept
                             b1, #real symbols
                             b2, #fake symbols
                             b3, #weak information
                             b4, #relevance manipulation
                             b5, #real symbols*relevance manipulation
                             b6, #fake symbols*relevance manipulation
                             b7, #weak information*relevance manipulation
                             p,
                             err_mean, 
                             err_sd) {
  # create independent variables that match your data
  symbols <- sample(1:3, n, replace=TRUE)
  symbols <- dummy(symbols) # this is because we need two separate b's
  symbols1 <- symbols[,1]
  symbols2 <- symbols[,2]
  info <- sample(0:1, n, replace=TRUE)
  relevance <- sample(0:1, n, replace=TRUE)

  # DV is based on your variables, coefficients and a random error
  # if you have the mean and sd of your residuals, according to your model,
  # plug them into argument err_mean and err_sd; will be more accurate.
  y <- b0 + (b1 * symbols1) + (b2 * symbols2) + (b3 * info) + 
    (b4 * relevance) + (b5 * relevance * symbols1) + (b6 * relevance * symbols2) +
    (b7 * relevance * info) + rnorm(n, mean=err_mean, sd=err_sd)

  model <- lm(y ~ relevance*symbols1 + relevance*symbols2 + relevance*info)
  summary(model)

  output <- summary(model)$coefficients
  ps <- output[which(row.names(output)==p), 4]
  names(ps) <- "p"
  return(ps)
}

```

```{r}
mod_air_relevance = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=filter(SVIVA2_01_comb,AREA_center==0))

#summary(mod_air_2.4)

n.mod_air_relevance=mod_air_relevance$fitted.values %>% length()

#intercept
b0.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="(Intercept)") %>% 
  select("estimate") %>% 
  max()

#effect of real symbols 
b1.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="SYMBOL_t1") %>% 
  select("estimate") %>% 
  max()

#effect of fake symbols 
b2.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="SYMBOL_t2") %>% 
  select("estimate") %>% 
  max()

#effect of weak information
b3.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="INFORMATION_weak") %>% 
  select("estimate") %>% 
  max()

#effect of RELEVANCE_exp
b4.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="RELEVANCE_exp") %>% 
  select("estimate") %>% 
  max()

#real symbols x RELEVANCE_exp
b5.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="RELEVANCE_exp:SYMBOL_t1") %>% 
  select("estimate") %>% 
  max()

#fake symbols x RELEVANCE_exp
b6.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="RELEVANCE_exp:SYMBOL_t2") %>% 
  select("estimate") %>% 
  max()

b7.mod_air_relevance = mod_air_relevance %>% broom::tidy() %>% 
  filter(term=="RELEVANCE_exp:INFORMATION_weak") %>% 
  select("estimate") %>% 
  max()

# p = character, which variable do you want to test for? for interactions, specify x1:x2. See below.

# err_mean = mean of residuals. Worth checking in your data. Using 0 for now.
err_mean.mod_air_relevance = mean(mod_air_relevance$residuals)

# err_sd = sd of residuals. Using 1 for now. Even more important, if you can add this based on your data, your power calculations will be most accurate
err_sd.mod_air_relevance = sd(mod_air_relevance$residuals)

```

```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT2, 
              n = n.mod_air_relevance, 
              b0 = b0.mod_air_relevance,
              b1 = b1.mod_air_relevance,
              b2 = b2.mod_air_relevance, 
              b3 = b3.mod_air_relevance, 
              b4 = b4.mod_air_relevance, 
              b5 = b5.mod_air_relevance, 
              b6 = b6.mod_air_relevance, 
              b7 = b7.mod_air_relevance, 
              p = "relevance:symbols1", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .1) / nrow(sims))

```

Coefficient of interaction between relevance manipulation and symbols is -0.127. Power is 0.15.

```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT2, 
              n = n.mod_air_relevance, 
              b0 = b0.mod_air_relevance,
              b1 = b1.mod_air_relevance,
              b2 = b2.mod_air_relevance, 
              b3 = b3.mod_air_relevance, 
              b4 = b4.mod_air_relevance, 
              b5 = b5.mod_air_relevance, 
              b6 = b6.mod_air_relevance, 
              b7 = b7.mod_air_relevance, 
              p = "relevance:info", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .1) / nrow(sims))

```

In Haifa-bay area, coefficient of interaction between relevance manipulation and weak information is 0.24. Power is 0.421.

Other simulations:

```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT2, 
              n = n.mod_air_relevance, 
              b0 = b0.mod_air_relevance,
              b1 = sd.trust.air*0.5,
              b2 = 0, 
              b3 = 0, 
              b4 = b4.mod_air_relevance, 
              b5 = -sd.trust.air*0.36, 
              b6 = 0, 
              b7 = 0, 
              p = "relevance:symbols1", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .1) / nrow(sims))

```

Simulations show that an interaction (real symbols*relavance) coefficient (in haifa area) of more than 0.36 SDs is detectible (sig. = 0.05, one-tailed test, minimum power = 0.8).

```{r}
num_sims <- 1000

# Air Pollution, power for area * symbols1:
# ldply comes from plyr, allows for repeating and storing results
sims <- ldply(1:num_sims,regression_simT2, 
              n = n.mod_air_relevance, 
              b0 = b0.mod_air_relevance,
              b1 = 0,
              b2 = 0, 
              b3 = 0, 
              b4 = b4.mod_air_relevance, 
              b5 = 0, 
              b6 = 0, 
              b7 = sd.trust.air*0.29, 
              p = "relevance:info", # must specify this exactly as it would appear in the table of coefficients
              err_mean=0, 
              err_sd=1)
(power_air <- sum(sims$p < .1) / nrow(sims))

```

Simulations show that an interaction (real symbols*relavance) coefficient (in haifa area) of more than 0.29 SDs is detectible (sig. = 0.05, one-tailed test, minimum power = 0.8).

```{r}
effect_sizes <- sd.trust.air*seq(0.2,0.5,0.1)
results <- NULL
for (val in effect_sizes) {
    sims <- ldply(1:1000, regression_simT2, 
                  n=n.mod_air_relevance, 
                  b0=b0.mod_air_relevance, 
                  b1=sd.trust.air*0.5, 
                  b2=0, 
                  b3=0,
                  b4 = b4.mod_air_relevance, 
                  b5 = 0, 
                  b6 = 0, 
                  b7 = val,
                  err_mean=0, 
              err_sd=1,
              p = "relevance:info")

    sims$effect_sizes <- val  # add the sample size in as a separate column to our results
    results <- rbind(results, sims)
}

library('dplyr')
library('ggplot2')

power_ests <- results %>%
    group_by(effect_sizes) %>%
    summarize(power=sum(p < .1) / n())

ggplot(power_ests, aes(x=effect_sizes, y=power)) +
    geom_point() +
    geom_line() +
    ylim(c(0, 1)) +
    theme_minimal()
```

### 2019-06-28 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 ```{r , include=FALSE, echo=FALSE}
+#load("C:/SAAR/UNIVERSITY/R/SVIVA/.RData")
+
 source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")
@@
 
-# 3. Summary statistics
+# 3. Power estimations
+
+In this section, I report the results of power estimations, which I conducted after collecting and analyzing the data.
+I have conducted seperate analyses for: (1) Main effects of the symbols and weak information manipulations; (2) Conditional effects of manipulations within each of the two areas (Haifa-Bay and Center); (3) Two-way interactions bewteen areas and the manipulations; and (4) Two-way interactions bewteen the relevance manipulation and the manipulations (in the Haifa-Bay area).
+
+These power estimations were conducted in R software, through regression models simulations with 1,000 interations for each effect size [code adopted from @hughes_website_2017].
+All these tests refer to a *p-value* of .05 (one-tailed), with `set.seed(2018)`.
+These analyses refer to a the analytical sample size (*N* = `r nrow(SVIVA2_01)`, *N*<sub>*Haifa-Bay*</sub>=`r nrow(SVIVA2_01_haifa)`, *N*<sub>*Center*</sub>=`r nrow(SVIVA2_01_center)`).
+Finally, I assumed that the error term is normally distributed (Mean = 0, SD = 1).
+
+<br>
+
+**Figure XX: Power of conditional effects**
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+
+results.main %>%
+    group_by(main.effect,
+             effect_sizes) %>%
+    summarize(power=sum(p < .1) / n()) %>%
+
+ggplot(aes(x=effect_sizes, y=power,color = main.effect)) +
+    geom_point() +
+    geom_line() +
+    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
+    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
+  scale_x_continuous(name = "Main effect (SDs)",limits = c(0.05,0.3),breaks = seq(0,0.3,0.05))+
+  scale_colour_manual(name = "Manipulation",
+                      values = c("dodgerblue3","orange2"),
+                      labels = c("Information", "Symbols"))+
+  theme_bw()
+```
+
+<br>
+
+**Figure XX: Power of conditional effects**
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+results.conditional %>%
+    group_by(cond.effect,
+             area,
+             effect_sizes) %>%
+    summarize(power=sum(p < .1) / n()) %>%
+
+ggplot(aes(x=effect_sizes, y=power,color = cond.effect)) +
+    geom_point() +
+    geom_line() +
+  facet_grid(cols = vars(area)) +
+    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
+    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
+  scale_x_continuous(name = "Conditional effect (SDs)",limits = c(0.05,0.3),breaks = seq(0,0.3,0.05))+
+  scale_colour_manual(name = "Manipulation",
+                      values = c("dodgerblue3","orange2"),
+                      labels = c("Information", "Symbols"))+
+theme_bw()
+```
+
+<br>
+
+**Figure XX: Power of Interactions with area**
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+results.area %>%
+    group_by(Interaction,
+             effect_sizes) %>%
+    summarize(power=sum(p < .1) / n()) %>%
+
+ggplot(aes(x=effect_sizes, y=power,color = Interaction)) +
+    geom_point() +
+    geom_line() +
+    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
+    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
+  scale_x_continuous(name = "Interaction coefficient (SDs)",limits = c(0.1,0.5),breaks = seq(0,0.5,0.1))+
+    scale_colour_manual(name = "Interaction",
+                      values = c("dodgerblue3","orange2"),
+                      labels = c("Information", "Symbols"))+
+  theme_bw()
+```
+
+<br>
+
+**Figure XX: Power of Interactions with relevance manipulation**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+results.relevance %>%
+    group_by(Interaction,
+             effect_sizes) %>%
+    summarize(power=sum(p < .1) / n()) %>% 
+ ggplot(aes(x=effect_sizes, y=power,color = Interaction)) +
+    geom_point() +
+    geom_line() +
+    geom_hline(yintercept = 0.80, colour = "grey60", linetype = 2) +
+    scale_y_continuous(name = "Power",limits = c(0,1),breaks = seq(0,1,0.1))+
+    scale_x_continuous(name = "Interaction coefficient (SDs)",limits = c(0.1,0.5),breaks = seq(0,0.5,0.1))+
+    scale_colour_manual(name = "Interaction",
+                      values = c("dodgerblue3","orange2"),
+                      labels = c("Information", "Symbols"))+
+  theme_bw()
+```
+
+<br>
+
+# 4. Summary statistics
 
@@
 
-# 4. Supplementary analyses
+<br>
+
+# X raw experimental results
+
+```{r}
+t3.comb <- rbind(t3.haifa,
+                 t3.center) %>%
+  filter(str_detect(variable,"policy")==T) %>%
+  select(-starts_with("statistic")) %>%
+
+  mutate(AREA_Center = rep(c("Haifa-Bay","Center"),each=2)) %>% 
+  arrange(desc(AREA_Center)) %>% 
+  select(AREA_Center,1:11)
+
+```
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+#labels of vars
+vars.lab = c(
+         "Gender (Woman=1)",
+         "Age",
+         "Trust in government ministries",
+         "Political Ideology (10 = extreme left)",
+         "Education",
+         "Income (5=high)",
+         "Parents",
+         "Parents of young children (under 12)",
+         "Interest in environmental issues",
+         "Air-pollution policy",
+         "Recycling policy"
+)
+
+vars <- c(var1 = "GENDER", 
+          var2 ="AGE",
+          var3 ="GOV_TRUST",
+          var4 = "IDEOLOGY", 
+          var5 ="EDUCATION",
+          var6 ="INCOME",
+          var7 = "CHILDREN", 
+          var8 ="CHILDREN_young",
+          var9 ="ENVIRONMENT_INTEREST",
+          var91 ="TRUST_air_INDEX",
+          var92 ="TRUST_waste_INDEX")
+
+t11.all <- SVIVA2_01 %>% 
+  select(TRUST_air_INDEX,
+         TRUST_waste_INDEX) %>% 
+  gather(key = variable, value = value) %>% 
+  group_by(variable) %>% 
+  summarise(mean.var = mean(value,na.rm = T) %>% round(3),
+            sd.var = sd(value,na.rm = T) %>% round(3)) %>% 
+  mutate(all = str_c(mean.var, " (",sd.var,")")) %>% 
+  as.data.frame() %>% 
+  select(-mean.var,-sd.var)
+
+t11.symbol <- SVIVA2_01 %>%
+  mutate(symbols.t = Recode(SYMBOL,"0='no';1='fake';2='real'")) %>% 
+  select(symbols.t,
+         TRUST_air_INDEX,
+         TRUST_waste_INDEX) %>%
+  gather(key = variable, value = value, -symbols.t) %>% 
+  group_by(symbols.t, variable) %>% 
+  summarise(value = list(value)) %>% 
+  spread(symbols.t, value) %>% 
+  group_by(variable) %>%
+
+  mutate(mean_no = round(mean(unlist(no),na.rm = T),3),
+         mean_fake = round(mean(unlist(fake),na.rm = T),3),
+         mean_real = round(mean(unlist(real),na.rm = T),3),
+         sd_no = round(sd(unlist(no),na.rm = T),3),
+         sd_fake = round(sd(unlist(fake),na.rm = T),3),
+         sd_real = round(sd(unlist(real),na.rm = T),3)) %>%
+  mutate(no = str_c(mean_no, " (",sd_no,")"),
+         fake = str_c(mean_fake, " (",sd_fake,")"),
+         real = str_c(mean_real, " (",sd_real,")")) %>% 
+  select(variable,
+         no,
+         fake,
+         real) %>% 
+  as.data.frame()
+
+t11.info <- SVIVA2_01 %>% 
+  mutate(info.t = ifelse(INFORMATION_air==1,"air_strong","air_weak")) %>% 
+  select(info.t,
+         TRUST_air_INDEX,
+         TRUST_waste_INDEX) %>%
+  gather(key = variable, value = value, -info.t) %>% 
+  group_by(info.t, variable) %>% 
+  summarise(value = list(value)) %>% 
+  spread(info.t, value) %>% 
+  group_by(variable) %>%
+
+  mutate(mean_strong = round(mean(unlist(air_strong),na.rm = T),3),
+         mean_weak = round(mean(unlist(air_weak),na.rm = T),3),
+         sd_strong = round(sd(unlist(air_strong),na.rm = T),3),
+         sd_weak = round(sd(unlist(air_weak),na.rm = T),3),
+         t_value.info = round(t.test(unlist(air_strong), unlist(air_weak))$statistic,3)) %>% 
+  mutate(air_strong = str_c(mean_strong, " (",sd_strong,")"),
+         air_weak = str_c(mean_weak, " (",sd_weak,")")) %>% 
+  select(variable,
+         air_strong,
+         air_weak) %>% 
+  as.data.frame() %>% 
+  arrange(variable)
+
+t11.relevance <- SVIVA2_01 %>%
+  mutate(relevance.t = ifelse(RELEVANCE_exp==1,"treatment","control")) %>% 
+  select(relevance.t,
+         TRUST_air_INDEX,
+         TRUST_waste_INDEX) %>%
+  gather(key = variable, value = value, -relevance.t) %>% 
+  group_by(relevance.t, variable) %>% 
+  summarise(value = list(value)) %>% 
+  spread(relevance.t, value) %>% 
+  group_by(variable) %>%
+
+  mutate(mean_treatment = round(mean(unlist(treatment),na.rm = T),3),
+         mean_control = round(mean(unlist(control),na.rm = T),3),
+         sd_treatment = round(sd(unlist(treatment),na.rm = T),3),
+         sd_control = round(sd(unlist(control),na.rm = T),3),
+         t_value.relevance = round(t.test(unlist(treatment), unlist(control))$statistic,3)) %>% 
+  mutate(treatment = str_c(mean_treatment, " (",sd_treatment,")"),
+         control = str_c(mean_control, " (",sd_control,")")) %>% 
+  select(variable,
+         treatment,
+         control) %>% 
+  as.data.frame() %>% 
+  arrange(variable)
+
+t11.comb <- t11.all %>% 
+  cbind(t11.symbol  %>% 
+          select(-variable)) %>% 
+  cbind(t11.info %>% 
+          select(-variable)) %>%
+  cbind(t1.relevance %>% 
+          select(-variable)) %>% 
+  mutate(variable = c("Air-pollution policy","Recycling policy"))
+
+t13.haifa <- t3.haifa %>% 
+  filter(str_detect(variable,"policy")==T) %>%
+  select(-starts_with("statistic"),
+         -starts_with("t_"))
+
+t13.center <- t3.center %>% 
+  filter(str_detect(variable,"policy")==T) %>%
+  select(-starts_with("statistic"),
+         -starts_with("t_"))
+
+t11.all <- rbind(
+  t11.comb,
+  t13.haifa,
+  t13.center
+) %>% 
+  mutate(area = rep(c("All","Haifa-Bay","Center"),each=2)) %>% 
+  select(area,1:9)
+
+```
+
+```{r}
+t11.all %>% 
+  kable(col.names = c("Area",
+                      "Policy",
+                    "All sample",
+                    "No symbols",
+                    "Fake symbols",
+                    "Real symbols",
+                    "Strong Air-pollution (Weak recycling)",
+                    "Weak air-pollution (Strong recycling)",
+                    "Treatment",
+                    "Control"))%>%
+  kable_styling(bootstrap_options = c("condensed"),
+                full_width = F,
+                position = "left",
+                font_size = 9) %>%
+  add_header_above(c(" " = 3, 
+                     "Symbols groups" = 3,  
+                     "Information groups" = 2, 
+                     "Relevance groups" = 2))  %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+
+<br>
+
+# 5. Supplementary analyses
 
@@
 
-# 5. English translation of the survey experiment
+# 6. English translation of the survey experiment
 

### 2019-06-28 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 
-SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
-SVIVA2_01_center = filter(SVIVA2_01,AREA==0)
+SVIVA2_01 <- SVIVA2_01%>%  
+mutate(AREA_center = Recode(AREA,"0=1;1=0"))
+
+SVIVA2_01_haifa <- filter(SVIVA2_01,AREA==1)
+SVIVA2_01_center <- filter(SVIVA2_01,AREA==0)
 ```
@@
 
+```
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+#Figures and tables
+table.x=0
+figure.x=0
 ```
@@
 
-These theoretical hypotheses are graphically displayed in **Figure 1**.
+These theoretical hypotheses are graphically displayed in `r figure.x=figure.x+1`**Figure `r figure.x`**.
 
@@
 
-[Figure 1 about here]
+[**Figure `r figure.x`** about here]
 
@@
 
-## *Data collection*
+## *Data collection and Procedure*
 
 The survey was conducted online through Qualtrics Survey Software.
-To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area, and matched them with citizens from cities with a similar profile and population size at the center of the country (hereafter "center").[^footnote_cities] To select and recruit residents of the selected cities, I was assisted by an Israeli internet research panel company *iPanel*.
+To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
+To select and recruit residents of these selected cities, I was assisted by an Israeli internet research panel company *iPanel*.
 The online survey link was sent by iPanel, between 28.1-1.2.2018.
 A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
-After filtering,[^footnote_filters] I ended up with a sizable sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
-
-[^footnote_cities]: The cities from the Haifa-Bay area are: *Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*.
-The matched cities from the center are: *Natania*, *Petach-Tikva* and *Rishon-Lezion*.
-The socioeconomic characteristics of the cities are summarized in the supplementary appendix.
-
-[^footnote_filters]: I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-These filters are neither associated with the areas nor with the experimental conditions.
-
-<br>
-
-## *Procedure*
+I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+Importantly, these filters are neither associated with the areas nor with the experimental conditions.
+Following this screening, I ended up with a sizable analytical sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
 
@@
 Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
+Subjects were also asked to describe the most salient environmental issue in their particular area of residence.
 These questions were designed to prime subjects to think about the impact of environmental issues to their own lives.
-Subjects were also asked to describe the most salient environmental issue in their particular area of residence.
-The latter open question was specifically designed to prime Haifa-bay residents to think about the personal relevance of the air pollution in their area.
+Specifically, it was desigend to prime those residing in the Haifa-bay area to think about the personal relevance of air-pollution in their area.
 Subjects in the relevance control group were asked equivalent questions about their field of occupation.
@@
 weak policy) x 2 (relevance: treatment vs.
-control).[^footnote_information_symbols_paper]  The assignment to the different experimental groups, across the two areas, is graphically presented in **Figure 2**.
-The experimental groups are fairly balanced with respect to the two areas, as well as to demographics, and pre-manipulation variables.
+control).
+In line with the abovementioned hypotheses, my focus in this study is on the two-way interactions between the two areas and the manipulations of symbols and information.
+In addition, within the Haifa-Bay respondents, I also explore the two-way interactions between the latter manipulations, and the relevance priming manipulation.[^footnote_information_symbols_paper] I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects (i.e.
+within each area) and the aformentioned two-way interactions, based on the analytical sample size.
+These estimations suggest that the detectible interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
+As for the interactions with the relevance manipulation (within the sample of Haifa-Bay respondents), I estimate that their detectible coefficients with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
+Full details about these estimations, which were conducted after data collection and analysis, are reported in the Section ## of the supplementary appendix.
 
-[^footnote_information_symbols_paper]: In addition to the above-mentioned hypotheses, the experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration.
+[^footnote_information_symbols_paper]: The experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration.
 In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
@@
 
-<br>
-
-[Figure 2 about here]
+[**Tables `r table.x`** about here]
 
@@
 
+library(effsize)
+
+relevance.areas.d <- cohen.d(SVIVA2_01$RELEVANCE_air_obs~SVIVA2_01$AREA_center)
+relevance.exp.d <- cohen.d(RELEVANCE_air_obs~RELEVANCE_exp, SVIVA2_01_haifa)
+
+relevance.exp.t <- t.test(RELEVANCE_air_obs~RELEVANCE_exp, SVIVA2_01_haifa)
+
 ```
@@
 I coded living in Haifa-bay area according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
-My data confirms that the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents, whereas the recycling policy is perceived by both groups as equally relevant.
-Moreover, when directly asked about the most salient environmental issue in their area of residence, most of the Haifa-Bay subjects made reference to air-pollution.
-As for the relevance priming questions, however, manipulation checks suggest that those in the relevance treatment group did not perceive either of the two policies as more personally relevant.
+
+To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
+`r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas.
+As expected, the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]).
+By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them.
+Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e.
+before presenting the policy plans).
+Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa-Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r (t1/t2*100) %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa-Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
+Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.
+
+[^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa-Bay area, as related to air-pollution.
+
+<br>
+
+[**Figure `r figure.x`** about here]
+
+<br>
+
+As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa-Bay respondents' perceptions of personal relevance of the air-pollution policy.
+On average, respondents in treatment group reported sightly lower level of personal relevance, yet these differences are not statistically significant (*t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
@@
 [^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
+
+`r table.x=table.x+1`**Tables `r table.x`** compares between the different experimental conditions, within each of the two areas, on demographic variables and premanipulation covariates.
+These comparisons confirm that these random assignements yielded fairely balanced groups, within the two areas.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues.
+Yet, Haifa-Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.
+
+[^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups - regarding education levels and the percetage of parents; and between the information groups - regarding the percetage of parents for young children.
+To adjust for small finite-sample imbalances, as well as for differences between the areas, I control for covariates.
 
@@
 
-**Table 1** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policy plans, and their interaction with the two areas.
+`r table.x=table.x+1`**Table `r table.x`** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policy plans, and their interaction with the two areas.
 Models 1.1-1.3 regard the Air-pollution policy, and Models 1.4 - 1.6 regard the recycling policy.
@@
 I also found similar patterns regarding the recycling policy: in Model 1.6, the interaction between residing in the center and the weak information is insignificant, and the interaction with the real symbols is negative and significant.
-Figure 3 provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies.
+`r figure.x=figure.x+1`**Figure `r figure.x`** provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies.
 The findings, as illustrated in **Figure 3**, suggest that the real symbols were more effective in increasing the trust of those residing in the polluted area and that the latter were no more likely to scrutinize the content of the communication.
@@
 
-[Table 1 about here]
+[**Table `r table.x`** about here]
 
@@
 
-[Figure 3 about here]
+[**Figure `r figure.x`** about here]
 
@@
 Next, I examine whether those subjects who were primed to think about the personal relevance of these policy plans were more likely to scrutinize them, and less likely to be affected by the familiar symbols.
-The interaction between the relevance manipulation and the symbols and information manipulations is presented in **Table 2**.
+The interaction between the relevance manipulation and the symbols and information manipulations is presented in `r table.x=table.x+1`**Table `r table.x`**.
 Again, the first three models regard the Air-pollution policy, and the remaining models regard the recycling policy.
@@
 
-[Table 2 about here]
+[**Table `r table.x`** about here]
 
@@
 
+```{r, echo=FALSE, warning=FALSE, message=F}
+#Figures and tables
+table.x=0
+figure.x=0
+```
+
 <br>
-**Figure 1: Theoretical model**
+`r figure.x=figure.x+1`**Figure `r figure.x`: Theoretical model**
 ![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/theoretical_model_relevance.png)
@@
 
-**Figure 2: Experimental design for policy plan communications**
-![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/experiment_flow_relevance.png)
+`r table.x=table.x+1`**Table `r table.x`: Balancing of experimental groups across areas**
 
@@
 
-**Table 1: Regression analyses – observational measure for perceived personal relevance.**
+```{r, echo=FALSE, warning=FALSE, message=F}
 
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-stargazer(mod_air_1.1,mod_air_1.2,mod_air_1.3,
-          mod_waste_1.1,mod_waste_1.2,mod_waste_1.3,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
+#labels of vars
+vars.lab = c(
+         "Gender (Woman=1)",
+         "Age",
+         "Trust in government ministries",
+         "Political Ideology (10 = extreme left)",
+         "Education",
+         "Income (5=high)",
+         "Parents",
+         "Parents of young children (under 12)",
+         "Interest in environmental issues",
+         "Air-pollution policy",
+         "Recycling policy"
+)
+
+vars <- c(var1 = "GENDER", 
+          var2 ="AGE",
+          var3 ="GOV_TRUST",
+          var4 = "IDEOLOGY", 
+          var5 ="EDUCATION",
+          var6 ="INCOME",
+          var7 = "CHILDREN", 
+          var8 ="CHILDREN_young",
+          var9 ="ENVIRONMENT_INTEREST",
+          var91 ="TRUST_air_INDEX",
+          var92 ="TRUST_waste_INDEX")
+
+t1.all <- SVIVA2_01 %>% 
+  select(AREA_center,
+         !!vars) %>% 
+  gather(key = variable, value = value,-AREA_center) %>% 
+  group_by(AREA_center,variable) %>% 
+  summarise(mean.var = mean(value,na.rm = T) %>% round(3),
+            sd.var = sd(value,na.rm = T) %>% round(3)) %>% 
+  mutate(all = str_c(mean.var, " (",sd.var,")")) %>% 
+  as.data.frame() %>% 
+  mutate(variable = rep(vars,2)) %>% 
+  select(-mean.var,-sd.var)
+
+t1.symbol <- SVIVA2_01 %>%
+  mutate(symbols.t = Recode(SYMBOL,"0='no';1='fake';2='real'")) %>% 
+  select(AREA_center,
+         symbols.t,
+         !!vars) %>%
+  gather(key = variable, value = value, -symbols.t,-AREA_center) %>% 
+  group_by(symbols.t, variable,AREA_center) %>% 
+  summarise(value = list(value)) %>% 
+  spread(symbols.t, value) %>% 
+  group_by(AREA_center,variable) %>%
+
+  mutate(mean_no = round(mean(unlist(no),na.rm = T),3),
+         mean_fake = round(mean(unlist(fake),na.rm = T),3),
+         mean_real = round(mean(unlist(real),na.rm = T),3),
+         sd_no = round(sd(unlist(no),na.rm = T),3),
+         sd_fake = round(sd(unlist(fake),na.rm = T),3),
+         sd_real = round(sd(unlist(real),na.rm = T),3)) %>%
+  mutate(no = str_c(mean_no, " (",sd_no,")"),
+         fake = str_c(mean_fake, " (",sd_fake,")"),
+         real = str_c(mean_real, " (",sd_real,")")) %>% 
+  select(AREA_center,
+         variable,
+         no,
+         fake,
+         real) %>% 
+  as.data.frame() %>% 
+  arrange(AREA_center,variable)
+
+t2.symbol <- SVIVA2_01 %>% 
+  select(AREA_center,
+         SYMBOL,
+         !!vars) %>% 
+  gather(key = variable, value = value, -SYMBOL,-AREA_center) %>% 
+  group_by(variable,AREA_center) %>% 
+  do(tidy(aov(value~SYMBOL, data=.))) %>% 
+  as.data.frame() %>% 
+  filter(term=="SYMBOL") %>% 
+  select(AREA_center,
+         variable,
+         statistic) %>% 
+  mutate_at(c("statistic"), funs(round(.,3)))%>% 
+  arrange(AREA_center,variable)
+
+t3.symbol <- cbind(t1.symbol,
+                   t2.symbol %>% select(statistic))
+
+t1.info <- SVIVA2_01 %>% 
+  mutate(info.t = ifelse(INFORMATION_air==1,"air_strong","air_weak")) %>% 
+  select(AREA_center,
+         info.t,
+         !!vars) %>%
+  gather(key = variable, value = value, -info.t, -AREA_center) %>% 
+  group_by(info.t, variable,AREA_center) %>% 
+  summarise(value = list(value)) %>% 
+  spread(info.t, value) %>% 
+  group_by(AREA_center,variable) %>%
+
+  mutate(mean_strong = round(mean(unlist(air_strong),na.rm = T),3),
+         mean_weak = round(mean(unlist(air_weak),na.rm = T),3),
+         sd_strong = round(sd(unlist(air_strong),na.rm = T),3),
+         sd_weak = round(sd(unlist(air_weak),na.rm = T),3),
+         t_value.info = round(t.test(unlist(air_strong), unlist(air_weak))$statistic,3)) %>% 
+  mutate(air_strong = str_c(mean_strong, " (",sd_strong,")"),
+         air_weak = str_c(mean_weak, " (",sd_weak,")")) %>% 
+  select(AREA_center,
+         variable,
+         air_strong,
+         air_weak,
+         t_value.info) %>% 
+  as.data.frame() %>% 
+  arrange(AREA_center,variable)
+
+t1.relevance <- SVIVA2_01 %>%
+  mutate(relevance.t = ifelse(RELEVANCE_exp==1,"treatment","control")) %>% 
+  select(AREA_center,
+         relevance.t,
+         !!vars) %>%
+  select(-var9) %>%
+  mutate(var9 = SVIVA2_01$SYMBOL_bi) %>% 
+  gather(key = variable, value = value, -relevance.t, -AREA_center) %>% 
+  group_by(relevance.t, variable,AREA_center) %>% 
+  summarise(value = list(value)) %>% 
+  spread(relevance.t, value) %>% 
+  group_by(AREA_center,variable) %>%
+
+  mutate(mean_treatment = round(mean(unlist(treatment),na.rm = T),3),
+         mean_control = round(mean(unlist(control),na.rm = T),3),
+         sd_treatment = round(sd(unlist(treatment),na.rm = T),3),
+         sd_control = round(sd(unlist(control),na.rm = T),3),
+         t_value.relevance = round(t.test(unlist(treatment), unlist(control))$statistic,3)) %>% 
+  mutate(treatment = str_c(mean_treatment, " (",sd_treatment,")"),
+         control = str_c(mean_control, " (",sd_control,")")) %>% 
+  select(AREA_center,
+         variable,
+         treatment,
+         control,
+         t_value.relevance) %>% 
+  as.data.frame() %>% 
+  arrange(AREA_center,variable)
+
+t1.relevance[t1.relevance$variable=="var9",-c(1,2)]="-"
+
+t3.haifa <- t1.all %>% 
+  filter(AREA_center==0) %>% 
+  select(-AREA_center) %>% 
+  cbind(t3.symbol  %>% 
+          filter(AREA_center==0) %>% 
+          select(-AREA_center,-variable)) %>% 
+  cbind(t1.info %>% 
+          filter(AREA_center==0) %>% 
+          select(-AREA_center,-variable)) %>%
+  cbind(t1.relevance %>% 
+          filter(AREA_center==0) %>% 
+          select(-AREA_center,-variable)) %>% 
+  mutate(variable = vars.lab)
+
+t3.center <- t1.all %>% 
+  filter(AREA_center==1) %>% 
+  select(-AREA_center) %>% 
+  cbind(t3.symbol  %>% 
+          filter(AREA_center==1) %>% 
+          select(-AREA_center,-variable)) %>% 
+  cbind(t1.info %>% 
+          filter(AREA_center==1) %>% 
+          select(-AREA_center,-variable)) %>%
+  cbind(t1.relevance %>% 
+          filter(AREA_center==1) %>% 
+          select(-AREA_center,-variable)) %>%  
+  mutate(variable = vars.lab)
 
@@
 
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
+**Haifa-Bay**
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+t3.haifa %>%
+  filter(str_detect(variable,"policy")==F) %>%
+  kable(col.names = c("",
+                    str_c("All sample (n=",SVIVA2_01_haifa %>% nrow(),")"),
+                    str_c("No symbols (n=",SVIVA2_01_haifa %>% filter(SYMBOL==0) %>%  nrow(),")"),
+                    str_c("Fake symbols (n=",SVIVA2_01_haifa %>% filter(SYMBOL==1) %>%  nrow(),")"),
+                    str_c("Real symbols (n=",SVIVA2_01_haifa %>% filter(SYMBOL==2) %>%  nrow(),")"),
+                    "f-test",
+                    str_c("Strong Air-pollution (Weak recycling) (n=",SVIVA2_01_haifa %>% filter(INFORMATION_air==1) %>% nrow(),")"),
+                    str_c("Weak air-pollution (Strong recycling) (n=",SVIVA2_01_haifa %>% filter(INFORMATION_air==0) %>% nrow(),")"),
+                     "t-test",
+                    str_c("Treatment (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
+                    str_c("Control (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
+                    "t-test"))%>%
+  kable_styling(bootstrap_options = c("condensed"),
+                full_width = F,
+                position = "left",
+                font_size = 9) %>%
+  add_header_above(c(" " = 2, 
+                     "Symbols groups" = 4,  
+                     "Information groups" = 3, 
+                     "Relevance groups" = 3))
+```
+<font size="0.5">
+
+*Notes*: 
+Table entries are means with SDs in parentheses.
+
+</font>
+
+<br>
+**Center**
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+t3.center %>%
+    filter(str_detect(variable,"policy")==F) %>%
+    kable(col.names = c("",
+                    str_c("All sample (n=",SVIVA2_01_center %>% nrow(),")"),
+                    str_c("No symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==0) %>%  nrow(),")"),
+                    str_c("Fake symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==1) %>%  nrow(),")"),
+                    str_c("Real symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==2) %>%  nrow(),")"),
+                    "f-test",
+                    str_c("Strong Air-pollution (Weak recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==1) %>% nrow(),")"),
+                    str_c("Weak air-pollution (Strong recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==0) %>% nrow(),")"),
+                     "t-test",
+                    str_c("Treatment (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
+                    str_c("Control (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
+                    "t-test"))%>%
+  kable_styling(bootstrap_options = c("condensed"),
+                full_width = F,
+                position = "left",
+                font_size = 9) %>%
+  add_header_above(c(" " = 2, 
+                     "Symbols groups" = 4,  
+                     "Information groups" = 3, 
+                     "Relevance groups" = 3))
+```
+<font size="0.5">
+
+*Notes*: 
+Table entries are means with SDs in parentheses.
+
+</font>
+
+<br>
+`r figure.x=figure.x+1`**Figure `r figure.x`: Perceived personal relevance of policy issues accross areas**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
+SVIVA2_01 %>%
+  select(AREA_names,
+         RELEVANCE_air_obs,
+         RELEVANCE_waste_obs) %>% 
+  gather(key = policy, value = relevance, -AREA_names) %>%
+  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
+ggplot(aes(AREA_names,relevance))+ 
+  theme_classic()+
+  geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.96),
+               width=0.05,size=0.5) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6)+
+  facet_grid(~policy)+
+  xlab("")+
+  scale_y_continuous(name = "Perceived personal relevance",limits=c(1,7),breaks = seq(1,7,by=1))
+```
+<font size="0.5">
+
+*Note*: Error bars represent 95% confidence intervals.
+
+</font>
 
@@
 
-**Figure 3: The effect of symbolic elements on trust across areas**
+`r figure.x=figure.x+1`**Figure `r figure.x`: The effect of symbolic elements on trust across areas**
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
-SVIVA2_01_comb = SVIVA2_01_comb %>% 
-  mutate(POLICY_n = Recode(policy,"'TRUST_air_INDEX'='Air-pollution'; 'TRUST_waste_INDEX'='Recycling'"))
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=8}
+library(ggpubr)
 
-ggplot(SVIVA2_01_comb, aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
+p1 <- SVIVA2_01_comb %>%
+  filter(policy=="TRUST_air_INDEX") %>% 
+ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
   theme_classic()+
@@
                fun.args = list(mult = 1.65),
-               width=0.2,size=0.5,position=position_dodge(0.2),color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.2))+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.2),alpha=0.8)+
-  scale_shape_manual(guide=F,values=c(19,1))+
+               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
+  scale_shape_manual(guide=F, values=c(19,1))+
+  scale_linetype_manual(guide=F, values=c(1,4))+
+  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
+  scale_y_continuous(name = "Trust in air-pollution policy",breaks = seq(1,7,by=0.5))+
+  ggtitle("Symbols")
+
+p2 <- SVIVA2_01_comb %>%
+  filter(policy=="TRUST_air_INDEX") %>% 
+ggplot(aes(factor(INFORMATION_weak),trust,shape=factor(AREA_names)))+ 
+  theme_classic()+
+  #geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.65),
+               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
+  scale_shape_manual(name="Area",values=c(19,1))+
   scale_linetype_manual(name="Area",values=c(1,4))+
-  facet_grid(~POLICY_n)+
-  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.1))
+  scale_x_discrete(name="",labels=c("Strong policy","Weak policy"))+
+  scale_y_continuous(name = "",breaks = seq(1,7,by=0.5))+
+  ggtitle("Information")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1,
+          widths = c(4,5))
 ```
@@
 
-**Table 2: Regression analyses – experimental manipulation of perceived personal relevance.**
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – observational measure for perceived personal relevance.**
 
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_2.1 = lm(TRUST_air_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_air_2.2 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
-mod_air_2.3 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
-mod_air_2.4 = lm(TRUST_air_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
+control.vars <- c("GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN",
+                   "CHILDREN_young")
 
-mod_waste_2.1 = lm(TRUST_waste_INDEX~SYMBOL_t+RELEVANCE_exp+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_waste_2.2 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak),data=SVIVA2_01_comb)
-mod_waste_2.3 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center,data=SVIVA2_01_comb)
-mod_waste_2.4 = lm(TRUST_waste_INDEX~RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak)+SYMBOL_t*AREA_center+RELEVANCE_exp*SYMBOL_t*AREA_center+RELEVANCE_exp*INFORMATION_weak*AREA_center,data=SVIVA2_01_comb)
+mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
+mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+
+                   INFORMATION_weak+
+                   GENDER+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                   CHILDREN+
+                   CHILDREN_young,data=SVIVA2_01_comb)
+mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
+mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
 
-stargazer(mod_air_2.1,mod_air_2.2,mod_air_2.4,
-          mod_waste_2.1,mod_waste_2.2,mod_waste_2.4,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+## Adjust standard errors & F statistic
+library(lmtest)
+library(sandwich)
+mod_air_1.1.robust_se    <- sqrt(diag(vcovHC(mod_air_1.1, type = "HC1")))
+mod_air_1.1.wald_results <- waldtest(mod_air_1.1, vcov = vcovHC(mod_air_1.1, type = "HC1"))
+
+mod_air_1.2.robust_se    <- sqrt(diag(vcovHC(mod_air_1.2, type = "HC1")))
+mod_air_1.2.wald_results <- waldtest(mod_air_1.2, vcov = vcovHC(mod_air_1.2, type = "HC1"))
+
+mod_air_1.3.robust_se    <- sqrt(diag(vcovHC(mod_air_1.3, type = "HC1")))
+mod_air_1.3.wald_results <- waldtest(mod_air_1.3, vcov = vcovHC(mod_air_1.3, type = "HC1"))
+
+stargazer(mod_air_1.1,mod_air_null,
+          mod_air_1.2,mod_air_null,
+          mod_air_1.3, mod_air_null,
+          type = "html",
+          se  = list(mod_air_1.1.robust_se,NULL,
+                     mod_air_1.2.robust_se,NULL,
+                     mod_air_1.3.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(",1:3,")"),
+          column.separate = c(2,2,2),
+          dep.var.labels="Trust in air-pollution policy",
+          omit = control.vars,
           covariate.labels=c("Real symbols",
@@
                              "Weak Information",
-                             "Relevance treatment",
-                             "Relevance treatment x Real symbols",
-                             "Relevance treatment x Fake symbols",
-                             "Relevance treatment x Weak Information",
                              "Area (0=Haifa-Bay; 1=center)",
@@
                              "Area x Fake symbols",
-                             "Area x Weak Information",
-                             "Relevance treatment x Area",
-                             "Relevance treatment x Area x Real symbols",
-                             "Relevance treatment x Area x Fake symbols",
-                             "Relevance treatment x Area x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          order = c(1,2,4,3,6:8,5,9,10,12,11,13:15),
-          initial.zero = FALSE,
-          notes = "",
-          notes.append = FALSE)
-
+                             "Area x Weak Information"),
+          p.auto = F,
+          add.lines = list(
+                           c("Controls",rep(c("Yes",""),3)),
+                           c("F Statistic", 
+                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.3.wald_results[2,3] %>% round(2),NA)))
 ```
 
+&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
+
 <br>
+
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – experimental manipulation of perceived personal relevance.**
+
+<br>

### 2019-07-02 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 SVIVA2_01 <- SVIVA2_01%>%  
-mutate(AREA_center = Recode(AREA,"0=1;1=0"))
+mutate(AREA_center = Recode(AREA,"0=1;1=0"),
+       SYMBOL_t = Recode(SYMBOL,"1=2;2=1"))
 
@@
 library(kableExtra)
+library(ggthemes)
 ```
@@
 
+sd.air <- SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
+
 ```
@@
 
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-sd_trust_air = SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
-sd_trust_waste = SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max()
-
-mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
+```{r, echo=FALSE, warning=FALSE, message=F}
+mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
+mod_air_1.1.symbol = update(mod_air_null,. ~ .+
+                       SYMBOL_t,
+                     data=SVIVA2_01_comb)
+
+mod_air_1.1.info = update(mod_air_null,. ~ .+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
+
+mod_air_1.1 = update(mod_air_null,. ~ .+
+                       SYMBOL_t+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
 mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
 mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
-
-mod_waste_1.1 = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
-mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
-
-mod_air_1.1_r1 = lm(TRUST_air_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_waste_1.1_r1 = lm(TRUST_waste_INDEX~SYMBOL_t.r+INFORMATION_weak,data=SVIVA2_01_comb)
-
-```
+mod_air_1.4 = update(mod_air_1.3,. ~ .+
+                      GENDER+
+                       GOV_TRUST+
+                       IDEOLOGY+
+                       EDUCATION+
+                       INCOME+
+                       CHILDREN+
+                       CHILDREN_young)
+## Adjust standard errors & F statistic
+library(lmtest)
+library(sandwich)
+mod_air_1.1.robust_se    <- sqrt(diag(vcovHC(mod_air_1.1, type = "HC1")))
+mod_air_1.1.wald_results <- waldtest(mod_air_1.1, vcov = vcovHC(mod_air_1.1, type = "HC1"))
+
+mod_air_1.2.robust_se    <- sqrt(diag(vcovHC(mod_air_1.2, type = "HC1")))
+mod_air_1.2.wald_results <- waldtest(mod_air_1.2, vcov = vcovHC(mod_air_1.2, type = "HC1"))
+
+mod_air_1.3.robust_se    <- sqrt(diag(vcovHC(mod_air_1.3, type = "HC1")))
+mod_air_1.3.wald_results <- waldtest(mod_air_1.3, vcov = vcovHC(mod_air_1.3, type = "HC1"))
+
+mod_air_1.4.robust_se    <- sqrt(diag(vcovHC(mod_air_1.4, type = "HC1")))
+mod_air_1.4.wald_results <- waldtest(mod_air_1.4, vcov = vcovHC(mod_air_1.4, type = "HC1"))
+
+main.symbols <- emmeans::emmeans(mod_air_1.1, specs = pairwise ~ SYMBOL_t)
+t.symbols.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2))
+t.symbols.fake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0))
+t.symbols.nofake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1))
+
+library(emmeans)
+
+main.info <- emmeans::emmeans(mod_air_1.1, specs = pairwise ~ SYMBOL_t)
+t.info <- t.test(TRUST_air_INDEX~INFORMATION_weak,data=SVIVA2_01_comb, alternative = "less")
+
+```
+
+I begin with the air-pollution policy.
+I examine how the appearance of symbols and the differences in the substantive information affect respondents' trust in that policy, and compare these effects between the two areas.
+To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center cities, who do not percive it as personally relevant.
+On the other hand, I expect Haifa-bay residents to be more affected by the differences in the content (strong versus weak information).
+
+The real symbols condition had a positive and significant main effect on trust in the policy compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+That effect ammounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
+Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received the "fake" symbols, yet these differences (among the entire sample population) were smaller and not sufficiently significant (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+
+[**Figure `r figure.x`** about here]
+
+Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in both the air-pollution policy, and, to a lower degree, the recycling policy.
+The latter effect suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, which to some extent extends towards EPM or environmental policy in general.
 
@@
 I regress trust in policy on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
-
-The real symbols had positive main effects on both policies compared with the no symbols condition (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="SYMBOL_t1")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations for the air-pollution and recycling policies, respectively).
-Compared with the fake symbols, the increase is significant at the 90% (one-tailed) regarding the air-pollution policy, and only marginally significant compared with the recycling policy (*p* = `r (summary(mod_waste_1.1_r1)$coefficients["SYMBOL_t.r1",4]/2)%>%round(2)`, one-tailed).
-The weak (versus strong) information manipulation also has a significant main effect in both policy plans, as expected (equivalent to `r ((mod_air_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_air)%>%round(2)%>%abs()` and `r ((mod_waste_1.1%>%tidy()%>%filter(term=="INFORMATION_weak")%>%select(estimate)%>%max())/sd_trust_waste)%>%round(2)%>%abs()` standard deviations, respectively).
-Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in both the air-pollution policy, and, to a lower degree, the recycling policy.
-The latter effect suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, which to some extent extends towards EPM or environmental policy in general.
 
@@
 <br>
-
-[**Figure `r figure.x`** about here]
 
@@
 ggplot(aes(AREA_names,relevance))+ 
-  theme_classic()+
+  theme_tufte()+
   geom_boxplot(width=0.25,color="gray70")+
@@
 ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
-  theme_classic()+
+  theme_tufte()+
   #geom_boxplot(width=0.25,color="gray70")+
@@
 ggplot(aes(factor(INFORMATION_weak),trust,shape=factor(AREA_names)))+ 
-  theme_classic()+
+  theme_tufte()+
   #geom_boxplot(width=0.25,color="gray70")+
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – observational measure for perceived personal relevance.**
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – Trust in Air-pollution policy.**
 
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-control.vars <- c("GOV_TRUST",
+control.vars <- c("GENDER",
+                  "GOV_TRUST",
                    "IDEOLOGY",
@@
 
-mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
-mod_air_1.1 = lm(TRUST_air_INDEX~SYMBOL_t+
-                   INFORMATION_weak+
+stargazer(mod_air_1.1,mod_air_null,
+          mod_air_1.2,mod_air_null,
+          mod_air_1.3, mod_air_null,
+          mod_air_1.4, mod_air_null,
+          type = "html",
+          se  = list(mod_air_1.1.robust_se,NULL,
+                     mod_air_1.2.robust_se,NULL,
+                     mod_air_1.3.robust_se,NULL,
+                     mod_air_1.4.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(",1:4,")"),
+          column.separate = c(2,2,2,2),
+          dep.var.labels="Trust in air-pollution policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information"),
+          p.auto = F,
+          add.lines = list(
+                           c("Controls",rep(c("No",""),3),"Yes"),
+                           c("F Statistic", 
+                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+<br>
+
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – trust in recycling policy.**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+control.vars <- c("GENDER",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN",
+                   "CHILDREN_young")
+
+mod_waste_null = lm(TRUST_waste_INDEX~1,data=SVIVA2_01_comb)
+mod_waste_1.1 = update(mod_waste_null,. ~ .+
+                       SYMBOL_t+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
+mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
+mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+mod_waste_1.4 = update(mod_waste_1.3,. ~ .+
                       GENDER+
@@
                        CHILDREN+
-                   CHILDREN_young,data=SVIVA2_01_comb)
-mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
-mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
-
+                       CHILDREN_young)
 ## Adjust standard errors & F statistic
@@
 library(sandwich)
-mod_air_1.1.robust_se    <- sqrt(diag(vcovHC(mod_air_1.1, type = "HC1")))
-mod_air_1.1.wald_results <- waldtest(mod_air_1.1, vcov = vcovHC(mod_air_1.1, type = "HC1"))
-
-mod_air_1.2.robust_se    <- sqrt(diag(vcovHC(mod_air_1.2, type = "HC1")))
-mod_air_1.2.wald_results <- waldtest(mod_air_1.2, vcov = vcovHC(mod_air_1.2, type = "HC1"))
-
-mod_air_1.3.robust_se    <- sqrt(diag(vcovHC(mod_air_1.3, type = "HC1")))
-mod_air_1.3.wald_results <- waldtest(mod_air_1.3, vcov = vcovHC(mod_air_1.3, type = "HC1"))
-
-stargazer(mod_air_1.1,mod_air_null,
-          mod_air_1.2,mod_air_null,
-          mod_air_1.3, mod_air_null,
+mod_waste_1.1.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.1, type = "HC1")))
+mod_waste_1.1.wald_results <- waldtest(mod_waste_1.1, vcov = vcovHC(mod_waste_1.1, type = "HC1"))
+
+mod_waste_1.2.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.2, type = "HC1")))
+mod_waste_1.2.wald_results <- waldtest(mod_waste_1.2, vcov = vcovHC(mod_waste_1.2, type = "HC1"))
+
+mod_waste_1.3.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.3, type = "HC1")))
+mod_waste_1.3.wald_results <- waldtest(mod_waste_1.3, vcov = vcovHC(mod_waste_1.3, type = "HC1"))
+
+mod_waste_1.4.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.4, type = "HC1")))
+mod_waste_1.4.wald_results <- waldtest(mod_waste_1.4, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
+stargazer(mod_waste_1.1,mod_waste_null,
+          mod_waste_1.2,mod_waste_null,
+          mod_waste_1.3, mod_waste_null,
+          mod_waste_1.4, mod_waste_null,
           type = "html",
-          se  = list(mod_air_1.1.robust_se,NULL,
-                     mod_air_1.2.robust_se,NULL,
-                     mod_air_1.3.robust_se,NULL),
+          se  = list(mod_waste_1.1.robust_se,NULL,
+                     mod_waste_1.2.robust_se,NULL,
+                     mod_waste_1.3.robust_se,NULL,
+                     mod_waste_1.4.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(",1:4,")"),
+          column.separate = c(2,2,2,2),
+          dep.var.labels="Trust in recycling policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information"),
+          p.auto = F,
+          add.lines = list(
+                           c("Controls",rep(c("No",""),3),"Yes"),
+                           c("F Statistic", 
+                             mod_waste_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+<br>
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+control.vars <- c("GENDER",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN",
+                   "CHILDREN_young")
+
+SVIVA2_01_comb.haifa = SVIVA2_01_comb %>% filter(AREA_center==0)
+
+mod_relevance_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb.haifa)
+mod_relevance_1.1 = update(mod_relevance_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   RELEVANCE_exp)
+mod_relevance_1.2 = update(mod_relevance_1.1,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+mod_relevance_1.3 = update(mod_relevance_1.2,. ~ .+
+                   GENDER+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                   CHILDREN+
+                   CHILDREN_young)
+
+## Adjust standard errors & F statistic
+mod_relevance_1.1.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1, type = "HC1")))
+mod_relevance_1.1.wald_results <- waldtest(mod_relevance_1.1, vcov = vcovHC(mod_relevance_1.1, type = "HC1"))
+
+mod_relevance_1.2.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2, type = "HC1")))
+mod_relevance_1.2.wald_results <- waldtest(mod_relevance_1.2, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))
+
+mod_relevance_1.3.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3, type = "HC1")))
+mod_relevance_1.3.wald_results <- waldtest(mod_relevance_1.3, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+stargazer(mod_relevance_1.1,mod_relevance_null,
+          mod_relevance_1.2,mod_relevance_null,
+          mod_relevance_1.3, mod_relevance_null,
+          type = "html",
+          se  = list(mod_relevance_1.1.robust_se,NULL,
+                     mod_relevance_1.2.robust_se,NULL,
+                     mod_relevance_1.3.robust_se,NULL),
           style = "apsr",
@@
                              "Weak Information",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information"),
+                             "Relevance treatment",
+                             "Relevance treatment x Real symbols",
+                             "Relevance treatment x Fake symbols",
+                             "Relevance treatment x Weak Information"),
           p.auto = F,
           add.lines = list(
-                           c("Controls",rep(c("Yes",""),3)),
+                           c("Controls","No","No","Yes"),
                            c("F Statistic", 
-                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.3.wald_results[2,3] %>% round(2),NA)))
-```
-
-&ast;*p*<.1; &ast;&ast;*p*<.05; &ast;&ast;&ast;*p*<.01 (two-tailed).
-
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – experimental manipulation of perceived personal relevance.**
-
-<br>
+                             mod_relevance_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+```
+
+<br>
+
+# References

### 2019-07-03 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
+
 mod_air_1.1.symbol = update(mod_air_null,. ~ .+
@@
                      data=SVIVA2_01_comb)
+
+mod_air_1.1.symbol.haifa = update(mod_air_null,. ~ .+
+                       SYMBOL_t,
+                     data=SVIVA2_01_comb %>% filter(AREA_center==0))
+
+mod_air_1.1.symbol.center = update(mod_air_null,. ~ .+
+                       SYMBOL_t,
+                     data=SVIVA2_01_comb %>% filter(AREA_center==1))
+
+mod_air_1.1.info = update(mod_air_null,. ~ .+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
+mod_air_1.1.info.haifa = update(mod_air_null,. ~ .+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb%>% filter(AREA_center==0))
+mod_air_1.1.info.center = update(mod_air_null,. ~ .+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb%>% filter(AREA_center==1))
 
@@
 mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+
 mod_air_1.4 = update(mod_air_1.3,. ~ .+
@@
                        CHILDREN_young)
+
+SVIVA2_01_comb_air_first <- SVIVA2_01_comb %>% filter(AIR_order==1)
+mod_air_1.5 = update(mod_air_1.3,. ~ .,data=SVIVA2_01_comb_air_first)
+
 ## Adjust standard errors & F statistic
@@
 
-main.symbols <- emmeans::emmeans(mod_air_1.1, specs = pairwise ~ SYMBOL_t)
+mod_air_1.5.robust_se    <- sqrt(diag(vcovHC(mod_air_1.5, type = "HC1")))
+mod_air_1.5.wald_results <- waldtest(mod_air_1.5, vcov = vcovHC(mod_air_1.5, type = "HC1"))
+
+main.symbols <- emmeans::emmeans(mod_air_1.1.symbol, specs = pairwise ~ SYMBOL_t)
 t.symbols.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2))
@@
 
+cond.symbols.haifa <- emmeans::emmeans(mod_air_1.1.symbol.haifa, specs = pairwise ~ SYMBOL_t)
+t.symbols.no.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2,AREA_center==0))
+t.symbols.fake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0,AREA_center==0))
+t.symbols.nofake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1,AREA_center==0))
+
 library(emmeans)
 
-main.info <- emmeans::emmeans(mod_air_1.1, specs = pairwise ~ SYMBOL_t)
-t.info <- t.test(TRUST_air_INDEX~INFORMATION_weak,data=SVIVA2_01_comb, alternative = "less")
-
-```
-
-I begin with the air-pollution policy.
-I examine how the appearance of symbols and the differences in the substantive information affect respondents' trust in that policy, and compare these effects between the two areas.
-To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center cities, who do not percive it as personally relevant.
-On the other hand, I expect Haifa-bay residents to be more affected by the differences in the content (strong versus weak information).
-
-The real symbols condition had a positive and significant main effect on trust in the policy compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+main.info <- mod_air_1.1.info %>% tidy()
+t.info <- t.test(TRUST_air_INDEX~INFORMATION_weak,data=SVIVA2_01_comb)
+
+```
+
+I begin by exploring respondents trust in the *air-pollution policy*.
+To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H1).
+Likewise, I expect Haifa-bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H2).
+I first examine the manipulations' main effects (among the entire sample), and then turn to compare their conditional effects (within each of the two areas).
+
+The real symbols condition has a positive and significant main effect on trust in the policy compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
 That effect ammounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
-Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received the "fake" symbols, yet these differences (among the entire sample population) were smaller and not sufficiently significant (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received the "fake" symbols, yet these differences (among the entire sample population) were smaller and not sufficiently significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+The main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+That effect ammounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
+
+`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.
+As shown by the figure, participants from Haifa-Bay reported significanly lower levels of trust in the air-pollution policy, in all the experimental conditions.
+The lower intercept of Haifa-Bay respondents suggests that they tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
+I now turn to analyze the different slopes of the two manipulations, across the two areas.
+As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater impact on those living in the polluted Haifa-Bay area, who perceived that policy as highly personally relevant.
+Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] comapred with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] comapred to the fake symbols group.
+The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups.
+However, these differences were smaller compared with the effect among the Haifa-Bay subjects, and not sufficiently significant.
+As for the effect of the information manipulation (presented in the right panel), the negative, roughly similar slopes among the two areas suggest that the weak information had a similar effect on both groups.
 
@@
 
-Regarding the two areas, as shown by the coefficients of this factor in Models 1.2 and 1.5, participants from Haifa-Bay reported lower levels of trust in both the air-pollution policy, and, to a lower degree, the recycling policy.
-The latter effect suggests that Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area, which to some extent extends towards EPM or environmental policy in general.
-
-`r table.x=table.x+1`**Table `r table.x`** presents the results of OLS regression analyses for the effects of the symbols and information manipulations on trust in the two policy plans, and their interaction with the two areas.
-Models 1.1-1.3 regard the Air-pollution policy, and Models 1.4 - 1.6 regard the recycling policy.
-I regress trust in policy on the manipulations (Models 1.1, 1.4), then I add the areas (Models 1.2, 1.5) and the interaction between them (Models 1.3, 1.6).
-
-Keeping in mind these main effects, I now turn to analyze the interactions between the manipulations and the areas.
-With regard to the air-pollution policy, my first hypothesis entails a positive coefficient to the interaction between residence in the center (i.e.
-low personal relevance) and the real symbols.
-Based on my second hypothesis, I expect to find a positive interaction between center residents and weak information.
-Counter to these expectations, in Model 1.3, the interaction between residence in the center and the real symbols is negative (*p*<.1), and the interaction with the weak information is insignificant.
-I also found similar patterns regarding the recycling policy: in Model 1.6, the interaction between residing in the center and the weak information is insignificant, and the interaction with the real symbols is negative and significant.
-`r figure.x=figure.x+1`**Figure `r figure.x`** provides a descriptive demonstration of the interaction between the areas and the symbols manipulation for the two policies.
-The findings, as illustrated in **Figure 3**, suggest that the real symbols were more effective in increasing the trust of those residing in the polluted area and that the latter were no more likely to scrutinize the content of the communication.
+I further examined the interactions between the manipulations and the two areas via a series of multivariate linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
+I regress trust in air-pollution policy on the manipulations (Model 1.1), then I add the areas (Models 1.2) and the interaction between them (Models 1.3).[^footnote_raw_means] Model 1.4 replicates Model 1.3, while adding control variables, to adjust for small imbalances between the experiment groups, as well as for differences between the areas.
+This model controls for all variables included in the balancing tables, except for interest in environmental issues, which was reported by only half of the sample [##TBA in other analyses I did it with no change##].
+Finally, Model 1.5 replicates the interaction model, while restricting the sample to those who received first the air-pollution policy.
+The latter test eliminates the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the that policy (a priming effect).
+The results of the interaction models are largely consistent with the raw findings presented above.
+In Models 1.3 and 1.4, the interactions between living in the center and the real symbols are negative, but weak (*p*<.1), and the interactions with the weak information are negative, but small and far from significance.
+A comparison bewteen models 1.2 and 1.3 via anova reveals that adding these interactions does not significantly improve the models fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
+
+[^footnote_raw_means]: Raw means and SDs of outcome variables are reported in section XX of the supplementary appendix.
 
@@
 
-<br>
-
-Next, I examine whether those subjects who were primed to think about the personal relevance of these policy plans were more likely to scrutinize them, and less likely to be affected by the familiar symbols.
-The interaction between the relevance manipulation and the symbols and information manipulations is presented in `r table.x=table.x+1`**Table `r table.x`**.
+These results are at odds with the theoretical hypotheses.
+They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
+Additionally, the above analyses do not provide any evidence that the more engaged Haifa-Bay were more likely than others to scrutinize the content of the communication.
+The differences in the content affected the evaluations of both groups in a very similar manner.
+Overall, the findings with regard to the air-polution policy indicate, tentatively, that the higher levels of perceived personal relevance of the communciation neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
+Still, an important limitation of this analysis regards the fact that it is based on an observational, natural comparison between two populations.
+Therefore, differences in perceived personal relevance can be confounded by other, unobserved covariates, that cannot be controlled.
+
+However, as explained in the methods section, the experimental design provides two additional tests which enable to address this limitation.
+*First*, we are able to comapre the effects on the air-polluation policy, with the recycling policy, for which there are no relevance differences between the two groups.
+`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy.
+Overall, these models show relatively similar patterns to those found in the air-pollution policy.
+The directions of most of the coefficients are similar, while the effects are smaller and less significant.
+Notice that Haifa-Bay subjects reported lower trust on that policy as well, which may indicate that they hold negative prior beliefs towards EPM in general, and not only with regard to its actions and policies concerning the air-pollution in their area.
+Haifa-Bay subjects were more affected by the symbolic elements for this policy as well.
+The real symbols had a positive effect among the Haifa-Bay subjects, yet the effect it significant only compared with the no symbols group.
+It did not increase the trust of the center subjects.
+Finally, similarly to the air-pollution policy, there were no meaningful differences in the effect of the information manipulation between the two areas.
+The similarities between the two very different policies further repudiates the assumption about the role of personal relevance.
+
+<br>
+
+[**Table `r table.x`** about here]
+
+<br>
+
+*Second*, I examine whether those subjects who were primed to think about the personal relevance of these policy plans were more likely to scrutinize them, and less likely to be affected by the familiar symbols.
+The interaction between the relevance manipulation and the symbols and information manipulations is presented in Table 2.
 Again, the first three models regard the Air-pollution policy, and the remaining models regard the recycling policy.
@@
 
-<br>
-
-[**Table `r table.x`** about here]
-
-<br>
-
-I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
+Finally, I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
 *First*, I also relied on subjects' subjective reporting of the personal relevance of the policy plans, in addition to the above operationalizations.
@@
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.65),
+               fun.args = list(mult = 1.96),
                width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
@@
 
-*Note*: Error bars represent 90% confidence intervals.
+*Note*: Error bars represent 95% confidence intervals.
 
@@
           mod_air_1.4, mod_air_null,
+          mod_air_1.5, mod_air_null,
           type = "html",
@@
                      mod_air_1.3.robust_se,NULL,
-                     mod_air_1.4.robust_se,NULL),
+                     mod_air_1.4.robust_se,NULL,
+                     mod_air_1.5.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(",1:4,")"),
-          column.separate = c(2,2,2,2),
+          column.labels   = str_c("(1.",1:5,")"),
+          column.separate = c(2,2,2,2,2),
           dep.var.labels="Trust in air-pollution policy",
@@
           add.lines = list(
-                           c("Controls",rep(c("No",""),3),"Yes"),
+                           c("Controls",rep(c("No",""),4),"Yes"),
                            c("F Statistic", 
@@
                              mod_air_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
+                             mod_air_1.4.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.5.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
@@
                        CHILDREN_young)
+SVIVA2_01_comb_recycling_first <- SVIVA2_01_comb %>% filter(AIR_order==2)
+mod_waste_1.5 = update(mod_waste_1.3,. ~ .,data=SVIVA2_01_comb_recycling_first)
+
 ## Adjust standard errors & F statistic
@@
 
+mod_waste_1.5.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.5, type = "HC1")))
+mod_waste_1.5.wald_results <- waldtest(mod_waste_1.5, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
 stargazer(mod_waste_1.1,mod_waste_null,
@@
           mod_waste_1.4, mod_waste_null,
+          mod_waste_1.5, mod_waste_null,
           type = "html",
@@
                      mod_waste_1.3.robust_se,NULL,
-                     mod_waste_1.4.robust_se,NULL),
+                     mod_waste_1.4.robust_se,NULL,
+                     mod_waste_1.5.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(",1:4,")"),
-          column.separate = c(2,2,2,2),
+          column.labels   = str_c("(2.",1:5,")"),
+          column.separate = c(2,2,2,2,2),
           dep.var.labels="Trust in recycling policy",
@@
                              mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
+                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.

### 2019-07-12 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 
-SVIVA2_01_haifa <- filter(SVIVA2_01,AREA==1)
-SVIVA2_01_center <- filter(SVIVA2_01,AREA==0)
+SVIVA2_01_haifa <- filter(SVIVA2_01,AREA_center==0)
+SVIVA2_01_center <- filter(SVIVA2_01,AREA_center==1)
+
+SVIVA2_01_comb.haifa = SVIVA2_01_comb %>% filter(AREA_center==0)
+
 ```
@@
 library(ggthemes)
+library(lmtest)
+library(sandwich)
 ```
@@
 
-# Research design
-
-In this paper, the above-mentioned theoretical expectations are tested via a randomized survey experiment, building on the methodology of @petty_1983.
-Focusing on the case of the Israeli Environment Protection Ministry (hereafter: EPM), I examine citizens' responses to communications of EPM regarding two of its current policy plans.
-The first policy regards *reducing the air pollution in the highly polluted Haifa-Bay area*, located in the north of Israel.
-This policy issue offers a fortunate case for examining the moderating role of perceived personal relevance.
-The distinction between those who reside in the polluted area and those who do not represents natural variation in personal relevance.
-Moreover, because this policy issue is intangible, ambiguous and complicated, the differences in personal relevance are not strongly confounded with differences in personal knowledge, as is the case in many other policy issues [@petty_1983].
-Congruently, those who reside in the polluted Haifa-Bay area are more motivated to scrutinize the communication about the air-pollution in their area of residence, yet are no more capable of doing so than those who reside elsewhere.
-As explained below, the sample population of the study consists of residents of the Haifa-bay area, matched with residents of cities at the center of Israel with similar aggregate socio-economic profile.
-The second policy plan regards *reducing domestic waste and increasing recycling*.
-This topic is assumed to be equally relevant for Haifa-bay residents and others.
-Therefore, adding this policy plan is intended to confirm that respondents’ divergent responses to the symbolic elements in the communication regarding the air-pollution policy, if found, may be attributed to differences in perceived personal relevance.
+# Methodology
+
+The above-mentioned theoretical expectations are tested via a randomized survey experiment, building on the methodology of @petty_1983.
+The experiment focuses, empirically, on the case of the Israeli Environmental Protection Ministry (hereafter: EPM), and its policy for reducing the air pollution in the highly polluted Haifa-Bay area.
+In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.[^footnote_information_symbols_paper]
+
+[^footnote_information_symbols_paper]: The experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration.
+In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
+The methodological aspects which are relevant for examining the additional hypotheses are described in a separate paper.
+
+EPM is a national-level bureau responsible for the formulation, coordination, and execution of environmental policy in Israel.
+Among others, EPM is responsible for monitoring and regulating the air quality across the country.
+The Haifa Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the concentration of heavy industry in that area, including large oil refineries, power plants, and chemical factories.
+Beginning in Mid 2000s, EPM has been developing and implementing a series of policy programs to monitor and reduce the high levels of pollution specifically in that area [@theministryofenvironmentprotection_2015; @theministryofenvironmentprotection_2015a; @theministryofenvironmentprotection_2019].
+While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019].
+Specifically, the issue recevied much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa-Bay.
+In 2015, the Ministry of Health published statistical data indicating that Haifa-Bay residents experience significanly higher rates of cancer and asthma, compared to other areas of the country.
+The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015].
+Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa-Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babys in the Haifa-Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
+These publications, and others, caused much panic among the local population, and especially among young parents.
+
+[^footnote_epidemiological_study]: The epidemiological study was originally sponsored by Ministry of Health.
+The study, which was  conducted by researchers from Haifa University, was planned to be conducted over five years, between 2015-2020.
+The findings, which leaked to the media, regarded the interim results of the first year of the study.
+Following that publication, the study has been significantly criticized by the local research community as well as the professional steering committee of the research.
+As a result, in 2017, the Ministry decided to cancel its involvement in that research.
+
+The air-pollution in the Haifa-Bay offers a fortunate case for examining the moderating role of perceived personal relevance.
+The distinction between those who reside in the polluted area and those who do not entails a significant natural variation in that moderating vatiable.
+Importantly, because this policy issue is intangible and scientifically complicated, the variation in personal relevance is not strongly confounded with personal knowledge about the issue, as is normally the case [@petty_1983].
+Accordingly, those residing in the polluted Haifa-Bay area are likely to be more motivated to scrutinize a governemnt communication about the air-pollution in their area, yet they are not necessarily more capable of critically evaluating its content.
+That latter assumption was the main reason for selecting that case.
+
+While comparing those residing in the Haifa-Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison.
+The differences in personal relevance can be theoretically confounded by unobserved covariates, that cannot be effectively controlled in the analyses.
+I address this limitation in the research design in three main ways.
+*First*, in the selection of the research popultion, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa-Bay, and their comparison group.
+Accordingly, I selected the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
+I also searched EPM documents and news websites for any reporting about high air-pollution levels in the three center cities, to ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies.
+*Second*, in addition to the policy regarding the air-pollution in Haifa-Bay, I also included in the experiment a second policy plan that is expected to be percevied by the two groups as equally relevant.
+For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
+The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements and variation in substantive information in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates.
 I henceforth refer to these two policy plans as "air-pollution" and "recycling".
-
-I exploited three symbolic elements, which have been used in the EPM's public communications, and became widely recognized by the public.
-The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second element is the green color, which is strongly associated with taking care of the environment.
-The third element are the images of two high-profile celebrity comedians which were taken from advertising campaigns of the EPM.
-Further details about these symbolic elements are found in the supplementary appendix.
+*Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa-Bay residents.
 
@@
 
-The survey was conducted online through Qualtrics Survey Software.
-To capture natural variation in the personal relevance of the air-pollution policy, I sampled citizens from the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
 To select and recruit residents of these selected cities, I was assisted by an Israeli internet research panel company *iPanel*.
-The online survey link was sent by iPanel, between 28.1-1.2.2018.
+The survey experiment was conducted online through Qualtrics Survey Software.
+The online survey link was sent by iPanel between 28.1-1.2.2018.
 A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
-I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-Importantly, these filters are neither associated with the areas nor with the experimental conditions.
-Following this screening, I ended up with a sizable analytical sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.
-
-The survey was presented to the participants as a study about citizens' attitudes regarding environmental policies in general.
-After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance).
+Thereafter, I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+These filters are neither associated with the areas nor with the experimental conditions.
+Following this screening, I ended up with a sizable analytical sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.[^footnote_unfiltered_sample]
+
+[^footnote_unfiltered_sample]: In the supplementary appendix, I replicate the main models on the unfiltered sample, with no significant change to the results.
+
+The survey was presented to the participants as an academic study about citizens' attitudes regarding environmental policies in general.
+After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance manipulation).
 Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
-Subjects were also asked to describe the most salient environmental issue in their particular area of residence.
-These questions were designed to prime subjects to think about the impact of environmental issues to their own lives.
-Specifically, it was desigend to prime those residing in the Haifa-bay area to think about the personal relevance of air-pollution in their area.
-Subjects in the relevance control group were asked equivalent questions about their field of occupation.
-
-Participants were then presented with the two policy plans of EPM, and informed that these were obtained from EPM's annual work plan.
-Each policy plan was followed by questions about respondents' trust in them.
-Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information): strong policy (i.e.
+Then, they were asked to describe the most salient environmental issue in their area of residence.
+These treatment questions were designed to prime those residing in the Haifa-bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
+
+[^footnote_relevance_manipulation]: The first three treatment questions were also designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
+In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa-Bay citizens' responses to the air-pollution policy.
+In other analyses, presented in the supplementary appendix, I also examine the effect of that variable for the recycling policy, for both populations.[##ADD##]
+
+Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order).
+They were informed that these plans were obtained from EPM's annual work plan.
+Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information manipulation): strong policy (i.e.
 logically persuasive policy plan) or weak policy (i.e.
@@
 Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order.
+For instance, a subject who first received a strong air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
 The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
@@
 
-The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the symbol treatment condition, the two policies (as explained, one weak and one strong) are displayed with the EPM logo, green color and celebrity images from campaigns.
+The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
+In the real symbols condition, the two policies (as explained, one weak and one strong) are displayed with three symbolic elements, which have been used in EPM's public communications, and became widely recognized by the public.
+The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second element is the green color, which is strongly associated with taking care of the environment.
+The third element is an image of a celebrity comedian from an advertising campaign of the EPM.
+The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
+The recycling policy in the real symbols condition was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum.
 In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images.
-In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with images of unfamiliar people.
+In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people.
+The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic identifiers (i.e.
+the symbolic effect) from a possible effect of their aesthetic design.
+Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy.
 The symbols conditions are displayed in **Appendix B**.
-Further details about the real and fake symbols are found in the supplementary appendix.
-
-Altogether, per each policy plan, the experiment has a factorial design of 3 (symbols: real symbols, fake-symbols, no-symbols) x 2 (information: strong vs.
-weak policy) x 2 (relevance: treatment vs.
-control).
-In line with the abovementioned hypotheses, my focus in this study is on the two-way interactions between the two areas and the manipulations of symbols and information.
-In addition, within the Haifa-Bay respondents, I also explore the two-way interactions between the latter manipulations, and the relevance priming manipulation.[^footnote_information_symbols_paper] I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects (i.e.
-within each area) and the aformentioned two-way interactions, based on the analytical sample size.
-These estimations suggest that the detectible interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
-As for the interactions with the relevance manipulation (within the sample of Haifa-Bay respondents), I estimate that their detectible coefficients with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
-Full details about these estimations, which were conducted after data collection and analysis, are reported in the Section ## of the supplementary appendix.
-
-[^footnote_information_symbols_paper]: The experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration.
-In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
-The methodological aspects which are relevant for examining the additional hypotheses are described in a separate paper.
-
-[**Tables `r table.x`** about here]
+Further details about the real and fake symbols are found in section ## of the supplementary appendix.
+
+Each policy plan was followed by six questions about respondents' trust in the policy.
+After the trust questions of the second policy, the subjects were asked additional questions about the two policies, including the degree to which they perceive each of them as personally relevant.
+These questions were followed by an Instructional Manipulation Check (IMC) item, intended to assess participants’ diligence.
+The last sections included a set of demographic questions including questions about their place of residence and work, and manipulation checks for participants' familiarity with the real symbols.
+At the end of the survey, the participants were debriefed about the manipulations, and the possible deception.
+An English translation of the full survey is available in section ## of the supplementary Appendix.
+
+In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa-Bay and the symbols and information manipulations of that policy.
+I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions.
+Additionally, within the Haifa-Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.
+I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the relevant two-way interactions.
+I conducted these estimations after the data collection and analyses, based on the analytical sample size.
+The estimated detectible interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
+As for the interactions with the relevance manipulation (among Haifa-Bay respondents), I estimate that the detectible coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
+The power estimations are reported in details in Section ## of the supplementary appendix.
 
@@
 sd.air <- SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
-
-```
-
-The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` and `r alpha_waste_trust` for the air-pollution and waste policies, respectively).
+sd.air.haifa <- SVIVA2_01_comb %>% filter(AREA_center==0)%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
+```
+
+The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for air-pollution policy, and `r alpha_waste_trust` for the recycling policy).
 This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
 Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-Participants reported, on average, lower trust in the air-pollution policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`) compared with the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
-
-The key independent variables are the manipulations of symbols and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.[^footnote_symbols_manipulation_check] The latter is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
-I coded living in Haifa-bay area according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
-
+
+The key independent variables are the manipulations of symbols[^footnote_symbols_manipulation_check] and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.
+The latter is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
+
+[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
+
+Living in Haifa-bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
 To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
@@
 As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa-Bay respondents' perceptions of personal relevance of the air-pollution policy.
-On average, respondents in treatment group reported sightly lower level of personal relevance, yet these differences are not statistically significant (*t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
+In fact, those assigned to the treatment group reported sightly lower level of personal relevance on average, yet these differences are not statistically significant (*t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
@@
 
-[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
+<br>
+
+# Results
 
@@
 To adjust for small finite-sample imbalances, as well as for differences between the areas, I control for covariates.
-
-<br>
-
-# Results
 
@@
                       GENDER+
+                       AGE+
                        GOV_TRUST+
@@
                        INCOME+
-                       CHILDREN+
                        CHILDREN_young)
@@
 
-I begin by exploring respondents trust in the *air-pollution policy*.
+I now turn to exploring respondents trust in the *air-pollution policy*.
 To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H1).
 Likewise, I expect Haifa-bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H2).
-I first examine the manipulations' main effects (among the entire sample), and then turn to compare their conditional effects (within each of the two areas).
-
-The real symbols condition has a positive and significant main effect on trust in the policy compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+
+This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
+The real symbols condition has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
 That effect ammounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
-Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received the "fake" symbols, yet these differences (among the entire sample population) were smaller and not sufficiently significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test).
 The main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
@@
 
-`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.
-As shown by the figure, participants from Haifa-Bay reported significanly lower levels of trust in the air-pollution policy, in all the experimental conditions.
+`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As shown by the figure, participants from Haifa-Bay reported significanly lower levels of trust in the air-pollution policy, in all the experimental conditions.
 The lower intercept of Haifa-Bay respondents suggests that they tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
-I now turn to analyze the different slopes of the two manipulations, across the two areas.
-As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater impact on those living in the polluted Haifa-Bay area, who perceived that policy as highly personally relevant.
+As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa-Bay area.
 Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] comapred with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] comapred to the fake symbols group.
@@
 However, these differences were smaller compared with the effect among the Haifa-Bay subjects, and not sufficiently significant.
-As for the effect of the information manipulation (presented in the right panel), the negative, roughly similar slopes among the two areas suggest that the weak information had a similar effect on both groups.
+The effects of the information manipulation on the two groups are presented in the right panel.
+This comparison shows that the differences bewteen participants' trust in the weak and strong policies were roughly similar in both groups.
+
+[^footnote_raw_means]: In addition, raw means and SDs of outcome variables across the two areas are reported in section XX of the supplementary appendix.
 
@@
 
-I further examined the interactions between the manipulations and the two areas via a series of multivariate linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
-I regress trust in air-pollution policy on the manipulations (Model 1.1), then I add the areas (Models 1.2) and the interaction between them (Models 1.3).[^footnote_raw_means] Model 1.4 replicates Model 1.3, while adding control variables, to adjust for small imbalances between the experiment groups, as well as for differences between the areas.
-This model controls for all variables included in the balancing tables, except for interest in environmental issues, which was reported by only half of the sample [##TBA in other analyses I did it with no change##].
-Finally, Model 1.5 replicates the interaction model, while restricting the sample to those who received first the air-pollution policy.
-The latter test eliminates the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the that policy (a priming effect).
-The results of the interaction models are largely consistent with the raw findings presented above.
-In Models 1.3 and 1.4, the interactions between living in the center and the real symbols are negative, but weak (*p*<.1), and the interactions with the weak information are negative, but small and far from significance.
-A comparison bewteen models 1.2 and 1.3 via anova reveals that adding these interactions does not significantly improve the models fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
-
-[^footnote_raw_means]: Raw means and SDs of outcome variables are reported in section XX of the supplementary appendix.
+These results are at odds with the two theoretical hypotheses.
+They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
+Additionally, these analyses do not provide evidence that the more engaged Haifa-Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
+
+I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
+I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Models `r table.x`.2) and the interaction between them (Models `r table.x`.3).
+The final two models are designed to test the robustness of the interaction model, by controlling for individual-level covariates (Model `r table.x`.4),[^footnote_control_variables] and restricting the sample to those who saw that policy first before the recycling policy (Model `r table.x`.5).
+The latter test rules out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the that policy (assimilation or contrust effects).
+The results of these models are largely consistent with the raw findings presented above.
+In Models `r table.x`.3, `r table.x`.4, `r table.x`.5   the interactions between living in the center and the real symbols are negative and marginally significant.
+The interactions with the weak information are insignificat in all these three models.
+A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
+Finally, notice that in `r table.x`.5, the effect of the real symbols is greater (but not the fake symbols), which may suggest that the impact of symbols diminishes between the first and the second time participants see them.
+
+[^footnote_control_variables]: I control for all the variables that are included in the balancing tables, except for interest in environmental issues, which was reported by only half of the sample.
+[##TBA in other analyses I did it with no change##].
 
@@
 
-These results are at odds with the theoretical hypotheses.
-They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
-Additionally, the above analyses do not provide any evidence that the more engaged Haifa-Bay were more likely than others to scrutinize the content of the communication.
-The differences in the content affected the evaluations of both groups in a very similar manner.
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+mod_waste_null = lm(TRUST_waste_INDEX~1,data=SVIVA2_01_comb)
+mod_waste_1.1 = update(mod_waste_null,. ~ .+
+                       SYMBOL_t+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
+mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
+mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+mod_waste_1.4 = update(mod_waste_1.3,. ~ .+
+                      GENDER+
+                       AGE+
+                       GOV_TRUST+
+                       IDEOLOGY+
+                       EDUCATION+
+                       INCOME+
+                       CHILDREN_young)
+SVIVA2_01_comb_recycling_first <- SVIVA2_01_comb %>% filter(AIR_order==2)
+mod_waste_1.5 = update(mod_waste_1.3,. ~ .,data=SVIVA2_01_comb_recycling_first)
+
+## Adjust standard errors & F statistic
+
+mod_waste_1.1.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.1, type = "HC1")))
+mod_waste_1.1.wald_results <- waldtest(mod_waste_1.1, vcov = vcovHC(mod_waste_1.1, type = "HC1"))
+
+mod_waste_1.2.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.2, type = "HC1")))
+mod_waste_1.2.wald_results <- waldtest(mod_waste_1.2, vcov = vcovHC(mod_waste_1.2, type = "HC1"))
+
+mod_waste_1.3.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.3, type = "HC1")))
+mod_waste_1.3.wald_results <- waldtest(mod_waste_1.3, vcov = vcovHC(mod_waste_1.3, type = "HC1"))
+
+mod_waste_1.4.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.4, type = "HC1")))
+mod_waste_1.4.wald_results <- waldtest(mod_waste_1.4, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
+mod_waste_1.5.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.5, type = "HC1")))
+mod_waste_1.5.wald_results <- waldtest(mod_waste_1.5, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
+SVIVA2_01_comb <- SVIVA2_01_comb %>% 
+  mutate(SYMBOL_t.r = Recode(SYMBOL_t,"0=2;2=0"))
+
+mod_waste_1.1.r = update(mod_waste_null,. ~ .+
+                       SYMBOL_t.r+
+                       INFORMATION_weak)
+mod_waste_1.1.r.robust_se <- sqrt(diag(vcovHC(mod_waste_1.1.r, type = "HC1")))
+
+mod_waste_1.3.r = update(mod_waste_null,. ~ .+
+                       AREA_center*(SYMBOL_t.r+INFORMATION_weak))
+mod_waste_1.3.r.robust_se <- sqrt(diag(vcovHC(mod_waste_1.3.r, type = "HC1")))
+```
+
 Overall, the findings with regard to the air-polution policy indicate, tentatively, that the higher levels of perceived personal relevance of the communciation neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
-Still, an important limitation of this analysis regards the fact that it is based on an observational, natural comparison between two populations.
-Therefore, differences in perceived personal relevance can be confounded by other, unobserved covariates, that cannot be controlled.
-
-However, as explained in the methods section, the experimental design provides two additional tests which enable to address this limitation.
-*First*, we are able to comapre the effects on the air-polluation policy, with the recycling policy, for which there are no relevance differences between the two groups.
+Still, as discussed in the Methodology secion, an important limitation of this analysis regards the fact that it is based on observational comparison, which may raise a concern of endogeneity.
+Accordingly, the lack of intereactions between the areas may be explained by other, unobserved differences between the two populations.
+As explained in the methods section, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
+I now discuss the results of these two tests.
+
 `r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy.
-Overall, these models show relatively similar patterns to those found in the air-pollution policy.
-The directions of most of the coefficients are similar, while the effects are smaller and less significant.
-Notice that Haifa-Bay subjects reported lower trust on that policy as well, which may indicate that they hold negative prior beliefs towards EPM in general, and not only with regard to its actions and policies concerning the air-pollution in their area.
-Haifa-Bay subjects were more affected by the symbolic elements for this policy as well.
-The real symbols had a positive effect among the Haifa-Bay subjects, yet the effect it significant only compared with the no symbols group.
-It did not increase the trust of the center subjects.
-Finally, similarly to the air-pollution policy, there were no meaningful differences in the effect of the information manipulation between the two areas.
-The similarities between the two very different policies further repudiates the assumption about the role of personal relevance.
+Overall, these models reveal relatively similar patterns to those found in the air-pollution policy.
+Notice that Haifa-Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
+The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Accordingly, similarly to the air-pollution policy, Haifa-Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
+The fact that similar petterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance.
+It also rules out a possible argument that greater relevance enhances (rathen then reduces) the effect of symbols.
+If this was the case, then there should have been no interaction between symbols and the areas for the recycling policy.
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+symbols.waste <- emmeans::emmeans(mod_waste_1.1, specs = pairwise ~ SYMBOL_t)
+
+diff1 <- (symbols.waste$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)) %>% abs() %>% round(3)
+se1 <- (mod_waste_1.1.robust_se %>% tidy() %>% filter(names=="SYMBOL_t1") %>% select(x)) %>% max()
+
+diff2 <- (symbols.waste$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)) %>% abs() %>% round(3)
+se2 <- (mod_waste_1.1.r.robust_se %>% tidy() %>% filter(names=="SYMBOL_t.r1") %>% select(x)) %>% max()
+
+diff3 <- (mod_waste_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
+se3 <- (mod_waste_1.3.robust_se %>% tidy() %>% filter(names=="SYMBOL_t1") %>% select(x)) %>% max()
+
+diff4 <- (mod_waste_1.3.r %>% tidy() %>% filter(term=="SYMBOL_t.r1") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
+se4 <- (mod_waste_1.3.r.robust_se %>% tidy() %>% filter(names=="SYMBOL_t.r1") %>% select(x)) %>% max()
+
+```
+
+[^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`) but not compared with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`).
+As shown in Model 2.3, the real symbols significanty increased Haifa-Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`).
+The differences between the sybmols groups among the center subjects are small and insignificant.
+In model 2.5, the interaction between weak information and the center area is positive, but far from significance.
 
@@
 
-*Second*, I examine whether those subjects who were primed to think about the personal relevance of these policy plans were more likely to scrutinize them, and less likely to be affected by the familiar symbols.
-The interaction between the relevance manipulation and the symbols and information manipulations is presented in Table 2.
-Again, the first three models regard the Air-pollution policy, and the remaining models regard the recycling policy.
-Models 2.1, 2.4 replicate models 1.1, 1.4 while adding the relevance manipulation.
-Thereafter, I add the interactions between the relevance manipulation and the symbols and information manipulations (Models 2.2, 2.5).
-Finally, to test the moderation of the relevance manipulation within each area, I add three-way interactions with the areas (Models 2.3, 2.6).
-In all these models, the relevance treatment did not yield significant effects, and there are no significant interactions with the symbols and information manipulations.
-The triple interactions with the areas are also insignificant (in Models 2.3, 2.6), which indicates that the relevance treatment did not moderate the effects of the symbols and information manipulations across the two areas.
-
-Finally, I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
-*First*, I also relied on subjects' subjective reporting of the personal relevance of the policy plans, in addition to the above operationalizations.
-*Second*, I further explored the effect of personal relevance on subjects inclination to scrutinize the policy plans, using additional measures for message elaboration available in the survey, which were again insignificant: the time participants spent on scanning the policy plans and their score in a memory test.
-I also tested whether personal relevance decreased the delta (within-subjects) between trust in the strong and weak policy plans presented to each subject.
-*Third*, I added a set of individual-level controls, and factors related to personal relevance of air-pollution, and to personal interest in environmental issues.
-Finally, I replicated my analyses on the unfiltered sample.
-None of these multiple robust analyses supports the theoretical hypotheses regarding the moderation of personal relevance on the effect of symbols.
-The interaction between personal relevance and information is confirmed only by the analysis of participants' subjective reporting of the personal relevance, and only with regard to the air-pollution policy.
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+mod_relevance_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb.haifa)
+mod_relevance_1.1 = update(mod_relevance_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   RELEVANCE_exp)
+mod_relevance_1.2 = update(mod_relevance_1.1,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+mod_relevance_1.3 = update(mod_relevance_1.2,. ~ .+
+                   GENDER+
+                   AGE+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                   CHILDREN_young)
+
+SVIVA2_01_comb.haifa_air_first <- SVIVA2_01_comb %>%
+                                    filter(AREA_center==0, AIR_order==1)
+mod_relevance_1.4 = update(mod_relevance_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
+
+## Adjust standard errors & F statistic
+mod_relevance_1.1.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1, type = "HC1")))
+mod_relevance_1.1.wald_results <- waldtest(mod_relevance_1.1, vcov = vcovHC(mod_relevance_1.1, type = "HC1"))
+
+mod_relevance_1.2.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2, type = "HC1")))
+mod_relevance_1.2.wald_results <- waldtest(mod_relevance_1.2, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))
+
+mod_relevance_1.3.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3, type = "HC1")))
+mod_relevance_1.3.wald_results <- waldtest(mod_relevance_1.3, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+mod_relevance_1.4.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3, type = "HC1")))
+mod_relevance_1.4.wald_results <- waldtest(mod_relevance_1.3, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+```
+
+Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations.
+In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations.
+Similarly to the regression tables presented above, the final two models are robust analyses where I add controls (Model `r table.x`.3) and restrict the sample to the policy presented first in order (Model `r table.x`.4).
+In all these models, the coefficient of the relevance treatment is negative but far from significance.
+The interactions between the real symbols and the relevance manipulation are positive, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the averaged differences between those who saw the symbols and those who did not were slightly smaller.
+However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`-`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`-`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect) and far from significance.
+The interactions between the relevance treatment and weak information manipulations are weakly positive and insignificant.
+Consistently with the observational comparisons, these experimentla tests also do not lend support for the hypotheses.
+However, two limitations about these analyses should be acknowledged.
+First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succedded in priming those subjects.
+Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa-Bay subjects.
+
+<br>
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+mod_closedness_null = lm(TRUST_air_INDEX~+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                     AGE,data=SVIVA2_01_comb.haifa)
+
+mod_closedness_1.1 = update(mod_closedness_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   close.industrial.area+
+                     CHILDREN_young)
+
+mod_closedness_1.2 = update(mod_closedness_1.1,. ~ .
+                            +close.industrial.area*(SYMBOL_t+INFORMATION_weak)+
+                              CHILDREN_young*(SYMBOL_t+INFORMATION_weak)+
+                              GENDER*(SYMBOL_t+INFORMATION_weak))
+
+mod_closedness_1.3 = update(mod_closedness_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
+
+## Adjust standard errors & F statistic
+mod_closedness_1.1.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.1, type = "HC1")))
+mod_closedness_1.1.wald_results <- waldtest(mod_closedness_1.1, vcov = vcovHC(mod_closedness_1.1, type = "HC1"))
+
+mod_closedness_1.2.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.2, type = "HC1")))
+mod_closedness_1.2.wald_results <- waldtest(mod_closedness_1.2, vcov = vcovHC(mod_closedness_1.2, type = "HC1"))
+
+mod_closedness_1.3.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.3, type = "HC1")))
+mod_closedness_1.3.wald_results <- waldtest(mod_closedness_1.3, vcov = vcovHC(mod_closedness_1.3, type = "HC1"))
+
+library(effsize)
+
+relevance.areas.close.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area) 
+relevance.areas.close.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area)
+
+relevance.areas.children.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young) 
+relevance.areas.children.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young)
+
+```
+
+Finally, as an additional test for the robustness of my findings, I further compare between Haifa-Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
+First, I rely on subjects specific place of residence, and its geographical proximity to the polluting industrial area.
+According to epidemiological studies that have been published in the Israeli national and local media, cities and residential areas that are geographically closer to the industrial area, were associated with higher rates of certain types of cancer disease (##ynet 2016##, Svechkinaa et a l.
+2016).##move to methods## Congruently, I selected the three cities/suberbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa-Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
+The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
+Second, since young children are more vulnerable to air-pollution effects, and since the effect on young children has been highlighted in media coverage of the epidemiological studies, I expect parents for young children (under 12 years) to be more engaged with this issue, although that assumption is not supported by differences in self-reported perceived personal relevance.[^footnote_post_treatment_control] ##TBA It should be noted that these tests were not planned in the first place.##
+
+`r table.x=table.x+1`**Table `r table.x`** presents the interactions between these two variables and information manipulations.
+Model `r table.x`.1 presents the effect of these variables with the manipulations, and thereafter Model `r table.x`.2 adds their interactions, and finally Model `r table.x`.3 restrics the analysis to the first policy presented.
+All three models include control variables.
+The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols.
+As for parents for young children, there is no evidence they respond differently to the appearance of symbols or differences in the content.[^footnote_proxies_models]
+
+[^footnote_post_treatment_control]: In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
+In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
+However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable (##Gelman and Hill 2007; p.
+188-189##).
+
+[^footnote_proxies_models]: The interaction between proximity and the real symbols is positive and significant in Model `r table.x`.2, in Model `r table.x`.3  it is positive but insignificant; The interaction between parents for young children and the fake symbols is positive and significant in Model `r table.x`.2.
 
@@
 control.vars <- c("GENDER",
+                  "AGE",
                   "GOV_TRUST",
@@
           add.lines = list(
-                           c("Controls",rep(c("No",""),4),"Yes"),
+                           c("Controls","No","","No","","No","","Yes","","No",""),
                            c("F Statistic", 
@@
                    "INCOME",
-                   "CHILDREN",
                    "CHILDREN_young")
-
-mod_waste_null = lm(TRUST_waste_INDEX~1,data=SVIVA2_01_comb)
-mod_waste_1.1 = update(mod_waste_null,. ~ .+
-                       SYMBOL_t+
-                       INFORMATION_weak,
-                     data=SVIVA2_01_comb)
-mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
-mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
-mod_waste_1.4 = update(mod_waste_1.3,. ~ .+
-                      GENDER+
-                       GOV_TRUST+
-                       IDEOLOGY+
-                       EDUCATION+
-                       INCOME+
-                       CHILDREN+
-                       CHILDREN_young)
-SVIVA2_01_comb_recycling_first <- SVIVA2_01_comb %>% filter(AIR_order==2)
-mod_waste_1.5 = update(mod_waste_1.3,. ~ .,data=SVIVA2_01_comb_recycling_first)
-
-## Adjust standard errors & F statistic
-library(lmtest)
-library(sandwich)
-mod_waste_1.1.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.1, type = "HC1")))
-mod_waste_1.1.wald_results <- waldtest(mod_waste_1.1, vcov = vcovHC(mod_waste_1.1, type = "HC1"))
-
-mod_waste_1.2.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.2, type = "HC1")))
-mod_waste_1.2.wald_results <- waldtest(mod_waste_1.2, vcov = vcovHC(mod_waste_1.2, type = "HC1"))
-
-mod_waste_1.3.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.3, type = "HC1")))
-mod_waste_1.3.wald_results <- waldtest(mod_waste_1.3, vcov = vcovHC(mod_waste_1.3, type = "HC1"))
-
-mod_waste_1.4.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.4, type = "HC1")))
-mod_waste_1.4.wald_results <- waldtest(mod_waste_1.4, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
-
-mod_waste_1.5.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.5, type = "HC1")))
-mod_waste_1.5.wald_results <- waldtest(mod_waste_1.5, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
 
@@
           add.lines = list(
-                           c("Controls",rep(c("No",""),3),"Yes"),
+                           c("Controls","No","","No","","No","","Yes","","No",""),
                            c("F Statistic", 
@@
 
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – experimental manipulation of perceived personal relevance.**
+
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
 control.vars <- c("GENDER",
+                  "AGE",
                   "GOV_TRUST",
@@
                    "INCOME",
-                   "CHILDREN",
                    "CHILDREN_young")
-
-SVIVA2_01_comb.haifa = SVIVA2_01_comb %>% filter(AREA_center==0)
-
-mod_relevance_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb.haifa)
-mod_relevance_1.1 = update(mod_relevance_null,. ~ .+
-                             SYMBOL_t+
-                   INFORMATION_weak+
-                   RELEVANCE_exp)
-mod_relevance_1.2 = update(mod_relevance_1.1,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-mod_relevance_1.3 = update(mod_relevance_1.2,. ~ .+
-                   GENDER+
-                   GOV_TRUST+
-                   IDEOLOGY+
-                   EDUCATION+
-                   INCOME+
-                   CHILDREN+
-                   CHILDREN_young)
-
-## Adjust standard errors & F statistic
-mod_relevance_1.1.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1, type = "HC1")))
-mod_relevance_1.1.wald_results <- waldtest(mod_relevance_1.1, vcov = vcovHC(mod_relevance_1.1, type = "HC1"))
-
-mod_relevance_1.2.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2, type = "HC1")))
-mod_relevance_1.2.wald_results <- waldtest(mod_relevance_1.2, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))
-
-mod_relevance_1.3.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3, type = "HC1")))
-mod_relevance_1.3.wald_results <- waldtest(mod_relevance_1.3, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
 
@@
           mod_relevance_1.3, mod_relevance_null,
+          mod_relevance_1.4, mod_relevance_null,
           type = "html",
@@
                      mod_relevance_1.2.robust_se,NULL,
-                     mod_relevance_1.3.robust_se,NULL),
+                     mod_relevance_1.3.robust_se,NULL,
+                     mod_relevance_1.4.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(",1:3,")"),
+          column.labels   = str_c("(3.",1:4,")"),
           column.separate = c(2,2,2),
@@
           add.lines = list(
-                           c("Controls","No","No","Yes"),
+                           c("Controls","No","","No","","Yes","","No",""),
                            c("F Statistic", 
@@
                              mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
+                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
@@
 
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area.**
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+control.vars <- c("GENDER",
+                  "AGE",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME")
+
+stargazer(mod_closedness_1.1,mod_closedness_null,
+          mod_closedness_1.2,mod_closedness_null,
+          mod_closedness_1.3, mod_closedness_null,
+          type = "html",
+          se  = list(mod_closedness_1.1.robust_se,NULL,
+                     mod_closedness_1.2.robust_se,NULL,
+                     mod_closedness_1.3.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(4.",1:4,")"),
+          column.separate = c(2,2,2),
+          dep.var.labels="Trust in air-pollution policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Proximity to industrial area",
+                             "Young children",
+                             "Proximity x Real symbols",
+                             "Proximity x Fake symbols",
+                             "Proximity x Weak Information",
+                             "Young children x Real symbols",
+                             "Young children x Fake symbols",
+                             "Young children x Weak Information"),          
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","Yes","","Yes","","Yes",""),
+                           c("F Statistic", 
+                             mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+```
+
+<br>
+
 # References

### 2019-07-15 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
     theme: flatly
+    number_sections: yes
     toc: yes
@@
 ```{r , include=FALSE, echo=FALSE}
-#load("C:/SAAR/UNIVERSITY/R/SVIVA/.RData")
+load("C:/SAAR/UNIVERSITY/R/SVIVA/.RData")
 
@@
 
-SVIVA1_01 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
-CELEBS_00 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")
-
-SVIVA2_01 = SVIVA2_01 %>%  
-mutate(AREA_center = Recode(AREA,"0=1;1=0"))
-
-SVIVA2_01_haifa = filter(SVIVA2_01,AREA==1)
-SVIVA2_01_center = filter(SVIVA2_01,AREA==0)
+SVIVA1_01 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
+CELEBS_00 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")
+CITIES_table <- read_csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CITIES_table.csv")
+CITIES_table[is.na(CITIES_table)] <- ""
 
@@
 ```{r , include=FALSE, echo=FALSE}
+library(knitr)
 library(tidyverse)
+library(stargazer)
+library(car)
+library(broom)
+library(kableExtra)
 library(sjPlot)
-library(stargazer)
+library(ggthemes)
+library(ggpubr)
 ```
@@
 
-# Contents:
+**Contents:**
+
+<br>
 
@@
 
-# 1. Supplementary information about the symbolic elements
+# Properties of the selected cities
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
+CITIES_table %>% 
+  kable(col.names = c("Area",
+                      "City",
+                    "Population",
+                    "Socio-economic rank (10=highest)",
+                    "Average income per employee (NIS)",
+                    "GINI",
+                    "% children (0-14)",
+                    "N participants in analytical sample"))%>%
+  kable_styling(bootstrap_options = c("condensed"),
+                full_width = F,
+                position = "left",
+                font_size = 9) %>%
+  collapse_rows(columns = 1, valign = "top")
+```
+<font size="0.5">
+
+Notes:
+Data for all cities, except for Qiryat-Hayiim, is retrived from the Central Bureau of Statistics data file of local authorities in Israel of 2015.
+Qiryat-Hayiim is considered, formally, a neighborhood within the jurisdiction of Haifa, although it is geographically seperated from the rest of the city.
+Therefore, it is included in the official statistical data within Haifa.
+The population of Qiryat-Hayiim is based on a document of statistical data for neighborhoods in Haifa for 2015, retrived from the website of the municipality of Haifa.
+
+</font>
+
+<br>
+
+# Supplementary information about the symbolic elements
 
@@
 
-# 2. Manipulation and validity checks
+# Manipulation and validity checks
 
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-set_theme("scatterw")
-
-sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
-        geom.size = 0.9,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+
+set_theme(
+  base=theme_tufte(),
+  geom.outline.size = 0.01,
+  geom.outline.color = "white", 
+  geom.label.size = 3,
+  geom.label.color = "grey50")
+
+p1 <- sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
+        geom.size = 0.75,
         ylim=c(0,155),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real logo")
 
-sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
-        geom.size = 0.9,
+p2 <- sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
+        geom.size = 0.75,
         ylim=c(0,155),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake logo")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1) 
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-set_theme("scatterw")
-
-sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+
+p1 <- sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
         type="hist",
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real logo")
 
-sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
+p2 <- sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
         type="hist",
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake logo")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1) 
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$air_real_person_familiar,
-        geom.size = 0.9,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$air_real_person_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real celeb (Tal Friedman)")
 
-sjp.frq(CELEBS_00$air_fake_person_familiar,
-        geom.size = 0.9,
+p2 <- sjp.frq(CELEBS_00$air_fake_person_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Unfamiliar model")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1)
+
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$waste_real_person_familiar,
-        geom.size = 0.9,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$waste_real_person_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real celeb (Ido Rosenblum)")
 
-sjp.frq(CELEBS_00$waste_fake_person_familiar,
-        geom.size = 0.9,
+p2 <- sjp.frq(CELEBS_00$waste_fake_person_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Unfamiliar model")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1)
+
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$air_real_ad_familiar,
-        geom.size = 0.9,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+
+p1 <- sjp.frq(CELEBS_00$air_real_ad_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (starting to think green)")
 
-sjp.frq(CELEBS_00$air_fake_ad_familiar,
-        geom.size = 0.9,
+p2 <- sjp.frq(CELEBS_00$air_fake_ad_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1) 
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$waste_real_ad_familiar,
-        geom.size = 0.9,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$waste_real_ad_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (reusable bags)")
 
-sjp.frq(CELEBS_00$waste_fake_ad_familiar,
-        geom.size = 0.9,
+p2 <- sjp.frq(CELEBS_00$waste_fake_ad_familiar,
+        geom.size = 0.75,
         ylim=c(0,110),
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1) 
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$air_real_positive_affect,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$air_real_positive_affect,
         type="hist",
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (starting to think green)")
 
-sjp.frq(CELEBS_00$air_fake_positive_affect,
+p2 <- sjp.frq(CELEBS_00$air_fake_positive_affect,
          type="hist",
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1)
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$waste_real_positive_affect,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$waste_real_positive_affect,
         type="hist",
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (reusable bags)")
 
-sjp.frq(CELEBS_00$waste_fake_positive_affect,
+p2 <- sjp.frq(CELEBS_00$waste_fake_positive_affect,
          type="hist",
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$air_real_negative_affect,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$air_real_negative_affect,
         type="hist",
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (starting to think green)")
 
-sjp.frq(CELEBS_00$air_fake_negative_affect,
+p2 <- sjp.frq(CELEBS_00$air_fake_negative_affect,
          type="hist",
@@
         axis.title="",
+        geom.colors = alpha("dodgerblue4",0.8),
         title = "Fake campaign")
 
+ggarrange(p1,p2,
+          ncol = 2,nrow = 1)
+
 ```
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(CELEBS_00$waste_real_negative_affect,
+```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.show='hold', fig.width=8,fig.height=4}
+p1 <- sjp.frq(CELEBS_00$waste_real_negative_affect,
         type="hist",
@@
         axis.title="",
+        geom.colors = alpha("springgreen3",0.8),
         title = "Real campaign (reusable bags)")
 
-sjp.frq(CELEBS_00$waste_fake_negative_affect,
+p2 <- sjp.frq(CELEBS_00$waste_fake_negative_affect,
          type="hist",
@@
 ## Comparison between Haifa-Bay and Center
-
-The comparison between the two areas is based on the assumption that the Air-pollution policy is perceived as more personally relevant by Haifa-Bay subjects, whereas the recycling policy is perceived as equally relevant by both groups.
-To test that assumption, I relied on the following question, which was included in the survey, regarding both policy plans:
-
-"To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
-
-The air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents.
-As for the recycling policy, it is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them.
-The distribution of the perceived personal relevance variable of the two policies, across the two areas, is displayed in the following figures.
-
-Air-pollution policy
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_air_obs,
-        type="hist",
-        show.mean = T,
-        ylim=c(0,600),xlim=c(0.5,7.5),
-        axis.title="",
-        title = "Center")
-
-sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_air_obs,
-        type="hist",
-        show.mean = T,
-        ylim=c(0,600),xlim=c(0.5,7.5),
-        axis.title="",
-        title = "Haifa-bay")
-
-```
-
-Recycling policy
-
-```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
-sjp.frq(filter(SVIVA2_01_comb,AREA==0)$RELEVANCE_waste_obs,
-        type="hist",
-        show.mean = T,
-        ylim=c(0,600),xlim=c(0.5,7.5),
-        axis.title="",
-        title = "Center")
-
-sjp.frq(filter(SVIVA2_01_comb,AREA==1)$RELEVANCE_waste_obs,
-        type="hist",
-        show.mean = T,
-        ylim=c(0,600),xlim=c(0.5,7.5),
-        axis.title="",
-        title = "Haifa-bay")
-
-```
-
-Moreover, Participants in the relevance treatment group were asked to describe the most salient environmental issue in their area of residence.
-Indeed, most of the Haifa-Bay subjects regarded in their responses to the air-pollution generated from the industrial area, and many of them linked it to higher morbidity rates in the area.
-Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, whereas relatively few of them mentioned air-pollution as a prominent environmental concern in their area.
 
@@
 
-# 3. Power estimations
+# Power estimations
 
@@
 
-# 4. Summary statistics
+# Summary statistics
 
@@
 
-# X raw experimental results
-
-```{r}
+# Raw experimental results
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
 t3.comb <- rbind(t3.haifa,
@@
           select(-variable)) %>%
-  cbind(t1.relevance %>% 
+  cbind(t11.relevance %>% 
           select(-variable)) %>% 
@@
   mutate(area = rep(c("All","Haifa-Bay","Center"),each=2)) %>% 
-  select(area,1:9)
-
-```
-
-```{r}
+  select(area,1:9) %>% 
+  mutate(variable = variable %>% str_remove(" policy"))
+
+```
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE}
 t11.all %>% 
@@
 
-# 5. Supplementary analyses
+# Supplementary analyses
+
+- models for relevance for center (air-pollution).
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+
+mod_relevance_null.a = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb %>% filter(AREA_center==1))
+mod_relevance_1.1.a = update(mod_relevance_null.a,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   RELEVANCE_exp)
+mod_relevance_1.2.a = update(mod_relevance_1.1.a,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+mod_relevance_1.3.a = update(mod_relevance_1.2.a,. ~ .+
+                   GENDER+
+                   AGE+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                   CHILDREN_young)
+
+mod_relevance_1.4.a = update(mod_relevance_1.2.a,. ~ .,data=SVIVA2_01_comb.center_air_first)
+
+## Adjust standard errors & F statistic
+mod_relevance_1.1.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1.a, type = "HC1")))
+mod_relevance_1.1.a.wald_results <- waldtest(mod_relevance_1.1.a, vcov = vcovHC(mod_relevance_1.1.a, type = "HC1"))
+
+mod_relevance_1.2.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2.a, type = "HC1")))
+mod_relevance_1.2.a.wald_results <- waldtest(mod_relevance_1.2.a, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))
+
+mod_relevance_1.3.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3.a, type = "HC1")))
+mod_relevance_1.3.a.wald_results <- waldtest(mod_relevance_1.3.a, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+mod_relevance_1.4.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.4.a, type = "HC1")))
+mod_relevance_1.4.a.wald_results <- waldtest(mod_relevance_1.4.a, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+```
+
+```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+control.vars <- c("GENDER",
+                  "AGE",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN_young")
+
+stargazer(mod_relevance_1.1.a,mod_relevance_null.a,
+          mod_relevance_1.2.a,mod_relevance_null.a,
+          mod_relevance_1.3.a, mod_relevance_null.a,
+          mod_relevance_1.4.a, mod_relevance_null.a,
+          type = "html",
+          se  = list(mod_relevance_1.1.a.robust_se,NULL,
+                     mod_relevance_1.2.a.robust_se,NULL,
+                     mod_relevance_1.3.a.robust_se,NULL,
+                     mod_relevance_1.4.a.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(3.",1:4,")"),
+          column.separate = c(2,2,2),
+          dep.var.labels="Trust in air-pollution policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Relevance treatment",
+                             "Relevance treatment x Real symbols",
+                             "Relevance treatment x Fake symbols",
+                             "Relevance treatment x Weak Information"),
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","No","","No","","Yes","","No",""),
+                           c("F Statistic", 
+                             mod_relevance_1.1.a.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.2.a.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.3.a.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.4.a.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+```
+
+- Models for relevance for both groups for recycling. 
+- replicating all regression tables for upfilterred sample.
 
@@
 
-# 6. English translation of the survey experiment
+# English translation of the survey experiment
 

### 2019-07-15 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 
+```{r set-global-options, echo = FALSE}
+knitr::opts_chunk$set(eval = TRUE, 
+                      echo = FALSE, 
+                      message=FALSE,
+                      warning = FALSE,
+                      cache = FALSE)
+
+```
+
 ```{r , include=FALSE, echo=FALSE}
@@
 source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")
-
-SVIVA2_01 <- SVIVA2_01%>%  
-mutate(AREA_center = Recode(AREA,"0=1;1=0"),
-       SYMBOL_t = Recode(SYMBOL,"1=2;2=1"))
-
-SVIVA2_01_haifa <- filter(SVIVA2_01,AREA_center==0)
-SVIVA2_01_center <- filter(SVIVA2_01,AREA_center==1)
-
-SVIVA2_01_comb.haifa = SVIVA2_01_comb %>% filter(AREA_center==0)
 
@@
 library(sandwich)
+library(ggpubr)
+library(effsize)
+library(emmeans)
 ```
@@
 The experiment focuses, empirically, on the case of the Israeli Environmental Protection Ministry (hereafter: EPM), and its policy for reducing the air pollution in the highly polluted Haifa-Bay area.
-In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.[^footnote_information_symbols_paper]
-
-[^footnote_information_symbols_paper]: The experiment was also designed to test a different set of hypotheses regarding the interaction between symbols and information, and its moderation by the effect of symbols on elaboration.
-In this paper, however, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
-The methodological aspects which are relevant for examining the additional hypotheses are described in a separate paper.
+In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.
+
+It should be noted that the experiment was additionally designed to test a set of hypotheses regarding the interaction between symbols and information in communications.
+The methodological aspects which are relevant for examining the additional hypotheses are described in a separate publication.
+In the following sections, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
+An English translation of the full survey is available in section ## of the supplementary Appendix.
 
@@
 Among others, EPM is responsible for monitoring and regulating the air quality across the country.
-The Haifa Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the concentration of heavy industry in that area, including large oil refineries, power plants, and chemical factories.
+The Haifa-Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa-Bay industrial zone, which is located in proximity of a number of urban residential areas.
+It is considered the largest industrial zone in the country, with concentration of multiple oil refineries, power plants, and chemical factories.
 Beginning in Mid 2000s, EPM has been developing and implementing a series of policy programs to monitor and reduce the high levels of pollution specifically in that area [@theministryofenvironmentprotection_2015; @theministryofenvironmentprotection_2015a; @theministryofenvironmentprotection_2019].
 While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019].
-Specifically, the issue recevied much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa-Bay.
-In 2015, the Ministry of Health published statistical data indicating that Haifa-Bay residents experience significanly higher rates of cancer and asthma, compared to other areas of the country.
+Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa-Bay.
+In 2015, the Ministry of Health published statistical data indicating that Haifa-Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
 The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015].
-Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa-Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babys in the Haifa-Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
+Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa-Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa-Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
+Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
 These publications, and others, caused much panic among the local population, and especially among young parents.
@@
 The air-pollution in the Haifa-Bay offers a fortunate case for examining the moderating role of perceived personal relevance.
-The distinction between those who reside in the polluted area and those who do not entails a significant natural variation in that moderating vatiable.
+The distinction between those who reside in the polluted area and those who do not entails a significant natural variation in that moderating variable.
 Importantly, because this policy issue is intangible and scientifically complicated, the variation in personal relevance is not strongly confounded with personal knowledge about the issue, as is normally the case [@petty_1983].
-Accordingly, those residing in the polluted Haifa-Bay area are likely to be more motivated to scrutinize a governemnt communication about the air-pollution in their area, yet they are not necessarily more capable of critically evaluating its content.
+Accordingly, those residing in the polluted Haifa-Bay area are likely to be more motivated to scrutinize a government communication about the air-pollution in their area, yet they are not necessarily more capable of critically evaluating its content.
 That latter assumption was the main reason for selecting that case.
@@
 I address this limitation in the research design in three main ways.
-*First*, in the selection of the research popultion, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa-Bay, and their comparison group.
-Accordingly, I selected the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*, *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
-I also searched EPM documents and news websites for any reporting about high air-pollution levels in the three center cities, to ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies.
-*Second*, in addition to the policy regarding the air-pollution in Haifa-Bay, I also included in the experiment a second policy plan that is expected to be percevied by the two groups as equally relevant.
+*First*, in the selection of the research population, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa-Bay, and their comparison group.
+Accordingly, I selected the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
+The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##).
+I also searched relevant EPM documents and news websites for any reporting about high air-pollution levels in the three center cities, to ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies.
+
+*Second*, in addition to the policy regarding the air-pollution in Haifa-Bay, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
 For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
@@
 *Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa-Bay residents.
+
+[^footnote_qiryat-Hayiim]: Qiryat-Hayiim is considered a neighborhood within the jurisdiction of Haifa, although it is geographically separated from the rest of the city, and people tend to distinguish it, informally.
 
@@
 In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa-Bay citizens' responses to the air-pollution policy.
-In other analyses, presented in the supplementary appendix, I also examine the effect of that variable for the recycling policy, for both populations.[##ADD##]
 
@@
 At the end of the survey, the participants were debriefed about the manipulations, and the possible deception.
-An English translation of the full survey is available in section ## of the supplementary Appendix.
 
@@
 I conducted these estimations after the data collection and analyses, based on the analytical sample size.
-The estimated detectible interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
-As for the interactions with the relevance manipulation (among Haifa-Bay respondents), I estimate that the detectible coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
+The estimated detectable interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
+As for the interactions with the relevance manipulation (among Haifa-Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
 The power estimations are reported in details in Section ## of the supplementary appendix.
@@
 
-library(effsize)
-
 relevance.areas.d <- cohen.d(SVIVA2_01$RELEVANCE_air_obs~SVIVA2_01$AREA_center)
@@
 [^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
+##add check reliability of information.
+##
 
@@
 
-`r table.x=table.x+1`**Tables `r table.x`** compares between the different experimental conditions, within each of the two areas, on demographic variables and premanipulation covariates.
-These comparisons confirm that these random assignements yielded fairely balanced groups, within the two areas.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues.
+`r table.x=table.x+1`**Tables `r table.x`** compares between the different experimental conditions, within each of the two areas, on demographic variables and pre-manipulation covariates.
+These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues.
 Yet, Haifa-Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.
 
-[^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups - regarding education levels and the percetage of parents; and between the information groups - regarding the percetage of parents for young children.
+[^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups -- regarding education levels and the percentage of parents; and between the information groups -- regarding the percentage of parents for young children.
 To adjust for small finite-sample imbalances, as well as for differences between the areas, I control for covariates.
+
+<br>
+
+[**Table `r table.x`** about here]
+
+<br>
 
@@
 
+main.symbols <- emmeans::emmeans(mod_air_1.1.symbol, specs = pairwise ~ SYMBOL_t)
+t.symbols.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2))
+t.symbols.fake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0))
+t.symbols.nofake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1))
+
+cond.symbols.haifa <- emmeans::emmeans(mod_air_1.1.symbol.haifa, specs = pairwise ~ SYMBOL_t)
+t.symbols.no.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2,AREA_center==0))
+t.symbols.fake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0,AREA_center==0))
+t.symbols.nofake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1,AREA_center==0))
+
+mod_air_1.1.areas = update(mod_air_null,. ~ .+
+                       AREA_center,
+                     data=SVIVA2_01_comb)
+
+main.info <- mod_air_1.1.info %>% tidy()
+t.info <- t.test(TRUST_air_INDEX~INFORMATION_weak,data=SVIVA2_01_comb)
+
+main.areas <- mod_air_1.1.areas %>% tidy()
+t.areas <- t.test(TRUST_air_INDEX~AREA_center,data=SVIVA2_01_comb)
+
+```
+
+I now turn to exploring respondents trust in the *air-pollution policy*.
+This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
+`r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas.
+The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
+Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test).
+The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score.
+Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a very low score of 2 or less, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group.
+As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
+Finally, as presented in the right panel, participants from Haifa-Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+`r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa-Bay subjects have a trust-index score lower than the middle point 4 (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
+This indicates that the majority of the sampled Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
+
+<br>
+
+[**Figure `r figure.x`** about here]
+
+<br>
+
+Next, I examine the interactions between the symbols and information manipulation, and the two areas.
+To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>).
+Likewise, I expect Haifa-bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H<sub>2</sub>).
+`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa-Bay area.
+Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group.
+The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups.
+However, these differences were smaller compared with the effect among the Haifa-Bay subjects, and not sufficiently significant.
+The effects of the information manipulation on the two groups are presented in the right panel.
+This comparison shows that the differences between participants' trust in the weak and strong policies were roughly similar in both groups.
+
+[^footnote_raw_means]: In addition, raw means and SDs of outcome variables across the two areas are reported in section XX of the supplementary appendix.
+
+<br>
+
+[**Figure `r figure.x`** about here]
+
+<br>
+
+These results are at odds with the two theoretical hypotheses.
+They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
+Additionally, these analyses do not provide evidence that the more engaged Haifa-Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
+
+```{r, echo=FALSE, warning=FALSE, message=F}
+
 mod_air_1.1 = update(mod_air_null,. ~ .+
@@
 
-SVIVA2_01_comb_air_first <- SVIVA2_01_comb %>% filter(AIR_order==1)
 mod_air_1.5 = update(mod_air_1.3,. ~ .,data=SVIVA2_01_comb_air_first)
@@
 ## Adjust standard errors & F statistic
-library(lmtest)
-library(sandwich)
 mod_air_1.1.robust_se    <- sqrt(diag(vcovHC(mod_air_1.1, type = "HC1")))
@@
 
-main.symbols <- emmeans::emmeans(mod_air_1.1.symbol, specs = pairwise ~ SYMBOL_t)
-t.symbols.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2))
-t.symbols.fake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0))
-t.symbols.nofake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1))
-
-cond.symbols.haifa <- emmeans::emmeans(mod_air_1.1.symbol.haifa, specs = pairwise ~ SYMBOL_t)
-t.symbols.no.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2,AREA_center==0))
-t.symbols.fake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0,AREA_center==0))
-t.symbols.nofake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1,AREA_center==0))
-
-library(emmeans)
-
-main.info <- mod_air_1.1.info %>% tidy()
-t.info <- t.test(TRUST_air_INDEX~INFORMATION_weak,data=SVIVA2_01_comb)
-
-```
-
-I now turn to exploring respondents trust in the *air-pollution policy*.
-To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H1).
-Likewise, I expect Haifa-bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H2).
-
-This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
-The real symbols condition has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-That effect ammounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
-Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test).
-The main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-That effect ammounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
-
-`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As shown by the figure, participants from Haifa-Bay reported significanly lower levels of trust in the air-pollution policy, in all the experimental conditions.
-The lower intercept of Haifa-Bay respondents suggests that they tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
-As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa-Bay area.
-Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] comapred with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] comapred to the fake symbols group.
-The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups.
-However, these differences were smaller compared with the effect among the Haifa-Bay subjects, and not sufficiently significant.
-The effects of the information manipulation on the two groups are presented in the right panel.
-This comparison shows that the differences bewteen participants' trust in the weak and strong policies were roughly similar in both groups.
-
-[^footnote_raw_means]: In addition, raw means and SDs of outcome variables across the two areas are reported in section XX of the supplementary appendix.
-
-[**Figure `r figure.x`** about here]
-
-These results are at odds with the two theoretical hypotheses.
-They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
-Additionally, these analyses do not provide evidence that the more engaged Haifa-Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
+```
 
 I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
-I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Models `r table.x`.2) and the interaction between them (Models `r table.x`.3).
-The final two models are designed to test the robustness of the interaction model, by controlling for individual-level covariates (Model `r table.x`.4),[^footnote_control_variables] and restricting the sample to those who saw that policy first before the recycling policy (Model `r table.x`.5).
-The latter test rules out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the that policy (assimilation or contrust effects).
-The results of these models are largely consistent with the raw findings presented above.
-In Models `r table.x`.3, `r table.x`.4, `r table.x`.5   the interactions between living in the center and the real symbols are negative and marginally significant.
-The interactions with the weak information are insignificat in all these three models.
+I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3).
+The final two models are designed to test the robustness of the interaction model by controlling for individual-level covariates (Model `r table.x`.4),[^footnote_control_variables] and restricting the sample to those who saw that policy first before the recycling policy (Model `r table.x`.5).
+The latter analysis rules out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
+In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
+In Models `r table.x`.3, `r table.x`.4, `r table.x`.5 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant.
 A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
-Finally, notice that in `r table.x`.5, the effect of the real symbols is greater (but not the fake symbols), which may suggest that the impact of symbols diminishes between the first and the second time participants see them.
+Notice that in `r table.x`.5, the effect of the real symbols is greater, which may indicate that the impact of symbols diminishes between the first and the second time participants see them.
+
+[^footnote_heteroskedacity]: Breusch-Pagan test confirms that the null hypotheses that the variance of the residuals is constant.
+For Model 1.3, Breusch-Pagan test =  `r bptest(mod_air_1.3)[["statistic"]][["BP"]] %>% round(3)`, *p*=`r bptest(mod_air_1.3)[["p.value"]][["BP"]] %>% round(3)`.
+Robust standard errors are estimated using R sandwich package with estimation type "HC1".
 
 [^footnote_control_variables]: I control for all the variables that are included in the balancing tables, except for interest in environmental issues, which was reported by only half of the sample.
-[##TBA in other analyses I did it with no change##].
+In other analyses, I also included that variable, with no significant change to the main results.
 
@@
 ## Adjust standard errors & F statistic
-
 mod_waste_1.1.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.1, type = "HC1")))
@@
 
-Overall, the findings with regard to the air-polution policy indicate, tentatively, that the higher levels of perceived personal relevance of the communciation neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
-Still, as discussed in the Methodology secion, an important limitation of this analysis regards the fact that it is based on observational comparison, which may raise a concern of endogeneity.
-Accordingly, the lack of intereactions between the areas may be explained by other, unobserved differences between the two populations.
-As explained in the methods section, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
+Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
+Accordingly, they do not support the research hypotheses.
+Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence I cannot rule out a concern of endogeneity.
+Accordingly, the null findings regarding the interactions between the areas and the manipulations can be a result by other, unobserved differences between the two populations.
+As explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
 I now discuss the results of these two tests.
@@
 Notice that Haifa-Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
-The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Accordingly, similarly to the air-pollution policy, Haifa-Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
-The fact that similar petterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance.
-It also rules out a possible argument that greater relevance enhances (rathen then reduces) the effect of symbols.
+The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa-Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
+The fact that similar patterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance.
+It also rules out a possible argument that greater relevance enhances (rather then reduces) the effect of symbols.
 If this was the case, then there should have been no interaction between symbols and the areas for the recycling policy.
@@
 [^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`) but not compared with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`).
-As shown in Model 2.3, the real symbols significanty increased Haifa-Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`).
-The differences between the sybmols groups among the center subjects are small and insignificant.
+As shown in Model 2.3, the real symbols significantly increased Haifa-Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`).
+The differences between the symbols groups among the center subjects are small and insignificant.
+The smaller effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy.
 In model 2.5, the interaction between weak information and the center area is positive, but far from significance.
@@
 
-SVIVA2_01_comb.haifa_air_first <- SVIVA2_01_comb %>%
-                                    filter(AREA_center==0, AIR_order==1)
 mod_relevance_1.4 = update(mod_relevance_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
@@
 
-mod_relevance_1.4.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3, type = "HC1")))
-mod_relevance_1.4.wald_results <- waldtest(mod_relevance_1.3, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+mod_relevance_1.4.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.4, type = "HC1")))
+mod_relevance_1.4.wald_results <- waldtest(mod_relevance_1.4, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+SVIVA2_01_comb.haifa <- SVIVA2_01_comb.haifa %>% 
+  mutate(RELEVANCE_exp.r = Recode(RELEVANCE_exp,"0=1;1=0"))
+
+mod_relevance_1.2.r = update(mod_relevance_null,. ~ .+RELEVANCE_exp.r*(SYMBOL_t+INFORMATION_weak))
+
+mod_relevance_1.2.r.robust_se <- sqrt(diag(vcovHC(mod_relevance_1.2.r, type = "HC1")))
+
+diff5 <- (mod_relevance_1.2.r %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
+se5 <- (mod_relevance_1.2.r.robust_se %>% tidy() %>% filter(names=="SYMBOL_t1") %>% select(x)) %>% max()
+
+tab.t1 <- SVIVA2_01_comb.haifa %>% 
+  group_by(RELEVANCE_exp,
+           INFORMATION_weak) %>% 
+  summarise(n = n(),
+            mean = mean(TRUST_air_INDEX,na.rm = T),
+            sd = sd(TRUST_air_INDEX,na.rm = T),
+            q1 = quantile(TRUST_air_INDEX,0.25,na.rm=T),
+            median = quantile(TRUST_air_INDEX,0.5,na.rm=T),
+            q3 = quantile(TRUST_air_INDEX,0.75,na.rm=T)) %>% 
+  mutate(se = sd/sqrt(n)) %>% 
+  mutate(ci.low = mean - 1.96*se,
+         ci.high = mean + 1.96*se)
+
 ```
@@
 In all these models, the coefficient of the relevance treatment is negative but far from significance.
-The interactions between the real symbols and the relevance manipulation are positive, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the averaged differences between those who saw the symbols and those who did not were slightly smaller.
-However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`-`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`-`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect) and far from significance.
-The interactions between the relevance treatment and weak information manipulations are weakly positive and insignificant.
-Consistently with the observational comparisons, these experimentla tests also do not lend support for the hypotheses.
-However, two limitations about these analyses should be acknowledged.
-First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succedded in priming those subjects.
+The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the averaged differences between those who saw the symbols and those who did not were slightly smaller.
+However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group) and far from significance.
+The interactions between the relevance treatment and weak information manipulations are positive but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
+
+[^footnote_relevance_manipulation_1]: In additional analyses, I also examine the moderating effect of the relevance treatment for center subjects' responses to air-pollution policy, as well as for the recycling policy (for the entire sample).
+In all these analyses, the interactions with the relevance treatment are insignificant.
+
+Two limitations about these analyses should be acknowledged.
+First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in priming those subjects.
 Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa-Bay subjects.
-
-<br>
+Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs (lower 95% CI = `r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`--`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`).
+This indicates that even Haifa-Bay residents that were reminded in a subtle way about the relevance of the air-pollution to their lives area are affected, at least to some degree, by familiar symbols.
+As for the information manipulation, descriptively, only `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1,TRUST_air_INDEX<=2) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`% of the participants assigned to relevance treatment reported a low score of 2 or less for the weak policy plan, while `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1,TRUST_air_INDEX>=4) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1)))*100)%>% round(0)`% of them reported a trust score of 4 or more (percentages for the control group are `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1,TRUST_air_INDEX<=2) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`% and `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1,TRUST_air_INDEX>=4) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`%, respectively).
+This entials that a vast majority of subjects within the polluted area tended to trust, to some degree, a policy plan whose chances of reducing the air-pollution are extremely low, even after reminding them about the relevance of the issue.
 
@@
 Finally, as an additional test for the robustness of my findings, I further compare between Haifa-Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
-First, I rely on subjects specific place of residence, and its geographical proximity to the polluting industrial area.
-According to epidemiological studies that have been published in the Israeli national and local media, cities and residential areas that are geographically closer to the industrial area, were associated with higher rates of certain types of cancer disease (##ynet 2016##, Svechkinaa et a l.
-2016).##move to methods## Congruently, I selected the three cities/suberbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa-Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
+First, I rely on subjects city of residence, and its geographical proximity to the polluting industrial area.
+Congruently, I selected the three cities/suburbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa-Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
 The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
-Second, since young children are more vulnerable to air-pollution effects, and since the effect on young children has been highlighted in media coverage of the epidemiological studies, I expect parents for young children (under 12 years) to be more engaged with this issue, although that assumption is not supported by differences in self-reported perceived personal relevance.[^footnote_post_treatment_control] ##TBA It should be noted that these tests were not planned in the first place.##
+Second, since young children are relatively vulnerable to air-pollution effects, and since the consequences of air-pollution on infants and young children has been highlighted in media, I expect parents for young children (under 12 years) to be more engaged with this issue, although that assumption is not supported by differences in self-reported perceived personal relevance.[^footnote_post_treatment_control]
 
 `r table.x=table.x+1`**Table `r table.x`** presents the interactions between these two variables and information manipulations.
-Model `r table.x`.1 presents the effect of these variables with the manipulations, and thereafter Model `r table.x`.2 adds their interactions, and finally Model `r table.x`.3 restrics the analysis to the first policy presented.
+Model `r table.x`.1 presents the effect of these variables with the manipulations, and thereafter Model `r table.x`.2 adds their interactions, and finally Model `r table.x`.3 restricts the analysis to the first policy presented.
 All three models include control variables.
-The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols.
-As for parents for young children, there is no evidence they respond differently to the appearance of symbols or differences in the content.[^footnote_proxies_models]
+The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols (the interaction is significant in Model `r table.x`.2, but not in Model `r table.x`.3).
+As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.[^footnote_proxies_models]
 
@@
 In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
-However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable (##Gelman and Hill 2007; p.
-188-189##).
+However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
+188-9].
 
@@
 <br>
-`r figure.x=figure.x+1`**Figure `r figure.x`: Perceived personal relevance of policy issues accross areas**
+`r figure.x=figure.x+1`**Figure `r figure.x`: Perceived personal relevance of policy issues across areas**
 
@@
 
+`r figure.x=figure.x+1`**Figure `r figure.x`: The distribution of Trust in air-pollution across the different conditions of symbols and information**
+
+```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
+p1 <- SVIVA2_01_comb %>%
+ggplot(aes(SYMBOL_n,TRUST_air_INDEX))+ 
+  theme_tufte()+
+  geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.96),
+               width=0.05,size=0.5) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6)+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
+  scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
+  scale_y_continuous(name = "Trust in air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
+  ggtitle("Symbols")
+
+p2 <- SVIVA2_01_comb %>%
+ggplot(aes(factor(INFORMATION_weak),TRUST_air_INDEX))+ 
+  theme_tufte()+
+  geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.96),
+               width=0.05,size=0.5) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6)+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
+  scale_x_discrete(name = "",labels = c("Strong policy","Weak policy"))+
+  scale_y_continuous(name = "",limits=c(1,7),breaks = seq(1,7,by=1))+
+  ggtitle("Information")
+
+p3 <- SVIVA2_01_comb %>%
+ggplot(aes(factor(AREA_center),TRUST_air_INDEX))+ 
+  theme_tufte()+
+  geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.96),
+               width=0.05,size=0.5) + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6)+
+  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
+  scale_x_discrete(name = "",labels = c("Haifa-Bay","Center"))+
+  scale_y_continuous(name = "",limits=c(1,7),breaks = seq(1,7,by=1))+
+  ggtitle("Areas")
+
+ggarrange(p1,p2,p3,
+          ncol = 3,nrow = 1,
+          widths = c(3,2,2))
+```
+<font size="0.5">
+
+*Note*: Error bars represent 95% confidence intervals.
+
+</font>
+
+<br>
+
 `r figure.x=figure.x+1`**Figure `r figure.x`: The effect of symbolic elements on trust across areas**
@@
 ```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=8}
-library(ggpubr)
-
 p1 <- SVIVA2_01_comb %>%
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area.**
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area and young children.**
 

### 2019-07-15 SVIVA_exp2_dm_03.R

@@ -12,12 +12,14 @@ library(lubridate)
 
 
 #loading raw data CSV file
-SVIVA2_raw_00 <- read.csv("SVIVA_exp2.csv")
-CITY_00 <- read.csv("CITY.csv")
+SVIVA2_raw_00 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA_exp2.csv",encoding = "UTF-8")
+CITY_00 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CITY.csv",encoding = "UTF-8")
+relevance.coding_00 <- read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/relevance.manual.coding.csv",encoding = "UTF-8") %>% 
+  rename(IP=X.U.FEFF.IP)
 
 SVIVA2_raw <- SVIVA2_raw_00 %>% filter(V10==1)
 CITY <- CITY_00 %>% filter(V10==1)
-
+relevance.coding <- relevance.coding_00 %>%  filter(V10==1)
 
 SVIVA2_raw[is.na(SVIVA2_raw)] <- 0
 
@@ -495,7 +497,14 @@ mutate(RECOGNIZE_waste_real = SVIVA2_raw$Q25.6+
   
   mutate(WITHIN_DELTA = if_else(INFORMATION_air==1,
                          TRUST_air_INDEX-TRUST_waste_INDEX,
-                         TRUST_waste_INDEX-TRUST_air_INDEX))
+                         TRUST_waste_INDEX-TRUST_air_INDEX)) %>% 
+  mutate(air.content = relevance.coding$air.content,
+         recycling.content = relevance.coding$recycling.content) %>% 
+ 
+  mutate(close.industrial.area = ifelse(CITY_reside_en %in% c("NESHER","QIRYAT HAIM","QIRYAT BIALIK"),1,0)) %>%  
+  mutate(AREA_center = Recode(AREA,"0=1;1=0"),
+         SYMBOL_t = Recode(SYMBOL,"1=2;2=1"))
+
 
 ####Datasets#####
 
@@ -510,9 +519,12 @@ SVIVA2_01 = SVIVA2_00 %>%
        
 
 SVIVA2_01_comb = SVIVA2_01 %>% 
-  dplyr::select(IP,USER_ID,AREA,AREA_names,
+  dplyr::select(IP,USER_ID,
[…]

### 2019-07-16 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 
-```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
+```{r silent-packages}
 library(knitr)
@@
 
-```{r,echo=FALSE,warning=FALSE,message=FALSE}
+```{r}
 N_raw = nrow(SVIVA2_raw_00)
@@
 
-```{r, echo=FALSE, warning=FALSE, message=F}
+```{r}
 #Figures and tables
@@
 The Haifa-Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa-Bay industrial zone, which is located in proximity of a number of urban residential areas.
-It is considered the largest industrial zone in the country, with concentration of multiple oil refineries, power plants, and chemical factories.
+It is considered the largest industrial zone in the country, with concentration of petrochemical industries, including oil refineries, power plants, and chemical factories.
 Beginning in Mid 2000s, EPM has been developing and implementing a series of policy programs to monitor and reduce the high levels of pollution specifically in that area [@theministryofenvironmentprotection_2015; @theministryofenvironmentprotection_2015a; @theministryofenvironmentprotection_2019].
@@
 
-```{r, echo=FALSE, warning=FALSE, message=F}
+```{r}
 alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
@@
 before presenting the policy plans).
-Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa-Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r (t1/t2*100) %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa-Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
+Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa-Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa-Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
 Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.
 
+```{r}
+library(irr)
+
+df.air.content.reliability <- relevance.coding[1:231,] %>% 
+  select(air.content,
+         air.content.coder2) %>% 
+  drop_na(air.content.coder2) %>% 
+  as.matrix() %>% 
+  t()
+
+```
+
 [^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa-Bay area, as related to air-pollution.
+To confirm inter-coder reliability, a second coder independently coded 70 observations (Krippendorff’s alpha = `r kripp.alpha(df.air.content.reliability)[["value"]] %>% round(2)`).
 
@@
 
-```{r, echo=FALSE, warning=FALSE, message=F}
+```{r}
 mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
@@
 
-```{r, echo=FALSE, warning=FALSE, message=F}
+```{r}
 
@@
 SVIVA2_01_comb.haifa <- SVIVA2_01_comb.haifa %>% 
-  mutate(RELEVANCE_exp.r = Recode(RELEVANCE_exp,"0=1;1=0"))
+  mutate(RELEVANCE_exp.r = Recode(RELEVANCE_exp,"0=1;1=0"),
+         SYMBOL_t.r = Recode(SYMBOL_t,"0=2;2=0"))
 
@@
 se5 <- (mod_relevance_1.2.r.robust_se %>% tidy() %>% filter(names=="SYMBOL_t1") %>% select(x)) %>% max()
+
+mod_relevance_1.2.r.r = update(mod_relevance_null,. ~ .+RELEVANCE_exp.r*(SYMBOL_t.r+INFORMATION_weak))
 
@@
 
+mod_symbols_relevance_aircontent = lm(TRUST_air_INDEX ~ SYMBOL_t,SVIVA2_01_haifa.relevance.aircontent)
+
+mod_symbols_relevance_aircontent.r = lm(TRUST_air_INDEX ~ SYMBOL_t.r,SVIVA2_01_haifa.relevance.aircontent)
+
+main.symbols.relevance.aircontent <- emmeans::emmeans(mod_symbols_relevance_aircontent, specs = pairwise ~ SYMBOL_t)
+
+t.symbols.relevance.aircontent.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_haifa.relevance.aircontent %>% filter(SYMBOL_t!=2))
+t.symbols.relevance.aircontent.fake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_haifa.relevance.aircontent %>% filter(SYMBOL_t!=0))
+
 ```
@@
 Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa-Bay subjects.
-Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs (lower 95% CI = `r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`--`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`).
-This indicates that even Haifa-Bay residents that were reminded in a subtle way about the relevance of the air-pollution to their lives area are affected, at least to some degree, by familiar symbols.
-As for the information manipulation, descriptively, only `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1,TRUST_air_INDEX<=2) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`% of the participants assigned to relevance treatment reported a low score of 2 or less for the weak policy plan, while `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1,TRUST_air_INDEX>=4) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==1,INFORMATION_weak==1)))*100)%>% round(0)`% of them reported a trust score of 4 or more (percentages for the control group are `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1,TRUST_air_INDEX<=2) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`% and `r ((filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1,TRUST_air_INDEX>=4) %>% nrow())/(nrow(filter(SVIVA2_01_comb.haifa,RELEVANCE_exp==0,INFORMATION_weak==1)))*100)%>% round(0)`%, respectively).
-This entials that a vast majority of subjects within the polluted area tended to trust, to some degree, a policy plan whose chances of reducing the air-pollution are extremely low, even after reminding them about the relevance of the issue.
-
-```{r, echo=FALSE, warning=FALSE, message=F}
+Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
+Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] This indicates that even Haifa-Bay residents that were reminded about the relevance of the air-pollution to their lives area are positively affected, at least to some degree, by familiar symbols.
+
+[^footnote_relevance_significance_fakesymbols]: Consistently with the previous models, subjects in the real symbols group also reported higher trust compared with the fake symbols, but these differences are not sufficiently significant.
+The differences between the two control groups are insignificant.
+
+```{r}
 mod_closedness_null = lm(TRUST_air_INDEX~+
@@
 mod_closedness_1.3.wald_results <- waldtest(mod_closedness_1.3, vcov = vcovHC(mod_closedness_1.3, type = "HC1"))
-
-library(effsize)
 
@@
 **Haifa-Bay**
-```{r, echo=FALSE, warning=FALSE, message=F}
+```{r}
 
@@
 **Center**
-```{r, echo=FALSE, warning=FALSE, message=F}
+```{r}
 
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
+```{r, fig.width=8,fig.height=4}
 SVIVA2_01 %>%
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE, fig.width=8,fig.height=4}
+```{r, fig.width=8, fig.height=4}
 p1 <- SVIVA2_01_comb %>%
@@
 
-```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=8}
+```{r, fig.width=8}
 p1 <- SVIVA2_01_comb %>%
@@
 
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+```{r,results="asis"}
 control.vars <- c("GENDER",

### 2019-07-16 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 
+```{r set-global-options, echo = FALSE}
+knitr::opts_chunk$set(eval = TRUE, 
+                      echo = FALSE, 
+                      message=FALSE,
+                      warning = FALSE,
+                      cache = FALSE)
+
+```
+
 <br>
@@
 library(ggpubr)
+library(lmtest)
+library(sandwich)
+
 ```
@@
 
-- models for relevance for center (air-pollution).
-
-```{r, echo=FALSE, warning=FALSE, message=F}
-
-mod_relevance_null.a = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb %>% filter(AREA_center==1))
-mod_relevance_1.1.a = update(mod_relevance_null.a,. ~ .+
+```{r}
+SVIVA2_00_comb = SVIVA2_00 %>% 
+  filter(!(AGE %in% 1:17)) %>% 
+  dplyr::select(IP,USER_ID,
+                AREA,
+                AREA_names,
+                AREA_center,
+      RELEVANCE_exp,RELEVANCE_exp_n,
+      SYMBOL,SYMBOL_n,SYMBOL_t,
+      INFORMATION_air,INFORMATION_air_n,
+      INFORMATION_waste,INFORMATION_waste_n,
+      TRUST_air_INDEX,
+      TRUST_waste_INDEX,
+      ELABORATION_air_time_log,
+      ELABORATION_waste_time_log,
+      ELABORATION_air_time,
+      ELABORATION_waste_time,
+      MEMORY_air_score,
+      MEMORY_waste_score,
+      GOV_TRUST,
+      GENDER,
+      AGE,
+      AIR_order,
+      WASTE_order,
+      IDEOLOGY,
+      INCOME,
+      EDUCATION,
+      RECOGNIZE_SVIVA_logo,
+      RECOGNIZE_air_real,
+      RECOGNIZE_waste_real,
+      RELEVANCE_air_obs,
+      RELEVANCE_waste_obs,
+      ENVIRONMENT_INTEREST,
+      ENVIRONMENT_FOLLOW,
+      CHILDREN,
+      CHILDREN_young,
+      close.industrial.area) %>% 
+  gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
+  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
+                              INFORMATION_waste),
+         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
+                                INFORMATION_waste_n),
+         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
+                                       ELABORATION_waste_time_log),
+         MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
+                               MEMORY_waste_score),
+         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",RELEVANCE_air_obs,
+                                   RELEVANCE_waste_obs),
+         RELEVANCE_obs = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
+                                ELABORATION_waste_time)) %>% 
+  mutate(TRUST_air_INDEX = ifelse(policy=="TRUST_air_INDEX",trust,NA),
+         TRUST_waste_INDEX = ifelse(policy=="TRUST_waste_INDEX",trust,NA),
+         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order),
+         RECOGNIZE_campaign = ifelse(policy=="TRUST_air_INDEX",RECOGNIZE_air_real,RECOGNIZE_waste_real),
+         INFORMATION_weak = Recode(INFORMATION,"0=1;1=0"))
+
+SVIVA2_00_comb_air_first <- SVIVA2_00_comb %>% filter(AIR_order==1)
+
+```
+
+```{r}
+mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_00_comb)
+
+mod_air_1.1 = update(mod_air_null,. ~ .+
                        SYMBOL_t+
-                   INFORMATION_weak+
-                   RELEVANCE_exp)
-mod_relevance_1.2.a = update(mod_relevance_1.1.a,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-mod_relevance_1.3.a = update(mod_relevance_1.2.a,. ~ .+
+                       INFORMATION_weak,
+                     data=SVIVA2_00_comb)
+mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
+mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+
+mod_air_1.4 = update(mod_air_1.3,. ~ .+
                       GENDER+
@@
 
-mod_relevance_1.4.a = update(mod_relevance_1.2.a,. ~ .,data=SVIVA2_01_comb.center_air_first)
+mod_air_1.5 = update(mod_air_1.3,. ~ .,data=SVIVA2_00_comb_air_first)
 
 ## Adjust standard errors & F statistic
-mod_relevance_1.1.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1.a, type = "HC1")))
-mod_relevance_1.1.a.wald_results <- waldtest(mod_relevance_1.1.a, vcov = vcovHC(mod_relevance_1.1.a, type = "HC1"))
-
-mod_relevance_1.2.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2.a, type = "HC1")))
-mod_relevance_1.2.a.wald_results <- waldtest(mod_relevance_1.2.a, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))
-
-mod_relevance_1.3.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3.a, type = "HC1")))
-mod_relevance_1.3.a.wald_results <- waldtest(mod_relevance_1.3.a, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
-
-mod_relevance_1.4.a.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.4.a, type = "HC1")))
-mod_relevance_1.4.a.wald_results <- waldtest(mod_relevance_1.4.a, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
-
-```
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
+mod_air_1.1.robust_se    <- sqrt(diag(vcovHC(mod_air_1.1, type = "HC1")))
+mod_air_1.1.wald_results <- waldtest(mod_air_1.1, vcov = vcovHC(mod_air_1.1, type = "HC1"))
+
+mod_air_1.2.robust_se    <- sqrt(diag(vcovHC(mod_air_1.2, type = "HC1")))
+mod_air_1.2.wald_results <- waldtest(mod_air_1.2, vcov = vcovHC(mod_air_1.2, type = "HC1"))
+
+mod_air_1.3.robust_se    <- sqrt(diag(vcovHC(mod_air_1.3, type = "HC1")))
+mod_air_1.3.wald_results <- waldtest(mod_air_1.3, vcov = vcovHC(mod_air_1.3, type = "HC1"))
+
+mod_air_1.4.robust_se    <- sqrt(diag(vcovHC(mod_air_1.4, type = "HC1")))
+mod_air_1.4.wald_results <- waldtest(mod_air_1.4, vcov = vcovHC(mod_air_1.4, type = "HC1"))
+
+mod_air_1.5.robust_se    <- sqrt(diag(vcovHC(mod_air_1.5, type = "HC1")))
+mod_air_1.5.wald_results <- waldtest(mod_air_1.5, vcov = vcovHC(mod_air_1.5, type = "HC1"))
+
+```
+
+```{r,results="asis"}
+control.vars <- c("GENDER",
+                  "AGE",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN",
+                   "CHILDREN_young")
+
+stargazer(mod_air_1.1,mod_air_null,
+          mod_air_1.2,mod_air_null,
+          mod_air_1.3, mod_air_null,
+          mod_air_1.4, mod_air_null,
+          mod_air_1.5, mod_air_null,
+          type = "html",
+          se  = list(mod_air_1.1.robust_se,NULL,
+                     mod_air_1.2.robust_se,NULL,
+                     mod_air_1.3.robust_se,NULL,
+                     mod_air_1.4.robust_se,NULL,
+                     mod_air_1.5.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(1.",1:5,")"),
+          column.separate = c(2,2,2,2,2),
+          dep.var.labels="Trust in air-pollution policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information"),
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","No","","No","","No","","Yes","","No",""),
+                           c("F Statistic", 
+                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.4.wald_results[2,3] %>% round(2),NA,
+                             mod_air_1.5.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+```{r}
+
+mod_waste_null = lm(TRUST_waste_INDEX~1,data=SVIVA2_00_comb)
+mod_waste_1.1 = update(mod_waste_null,. ~ .+
+                       SYMBOL_t+
+                       INFORMATION_weak,
+                     data=SVIVA2_00_comb)
+mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
+mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+mod_waste_1.4 = update(mod_waste_1.3,. ~ .+
+                      GENDER+
+                       AGE+
+                       GOV_TRUST+
+                       IDEOLOGY+
+                       EDUCATION+
+                       INCOME+
+                       CHILDREN_young)
+SVIVA2_00_comb_recycling_first <- SVIVA2_00_comb %>% filter(AIR_order==2)
+mod_waste_1.5 = update(mod_waste_1.3,. ~ .,data=SVIVA2_00_comb_recycling_first)
+
+## Adjust standard errors & F statistic
+mod_waste_1.1.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.1, type = "HC1")))
+mod_waste_1.1.wald_results <- waldtest(mod_waste_1.1, vcov = vcovHC(mod_waste_1.1, type = "HC1"))
+
+mod_waste_1.2.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.2, type = "HC1")))
+mod_waste_1.2.wald_results <- waldtest(mod_waste_1.2, vcov = vcovHC(mod_waste_1.2, type = "HC1"))
+
+mod_waste_1.3.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.3, type = "HC1")))
+mod_waste_1.3.wald_results <- waldtest(mod_waste_1.3, vcov = vcovHC(mod_waste_1.3, type = "HC1"))
+
+mod_waste_1.4.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.4, type = "HC1")))
+mod_waste_1.4.wald_results <- waldtest(mod_waste_1.4, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
+mod_waste_1.5.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.5, type = "HC1")))
+mod_waste_1.5.wald_results <- waldtest(mod_waste_1.5, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
+```
+
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – trust in recycling policy.**
+
+```{r,results="asis"}
 control.vars <- c("GENDER",
@@
 
-stargazer(mod_relevance_1.1.a,mod_relevance_null.a,
-          mod_relevance_1.2.a,mod_relevance_null.a,
-          mod_relevance_1.3.a, mod_relevance_null.a,
-          mod_relevance_1.4.a, mod_relevance_null.a,
+stargazer(mod_waste_1.1,mod_waste_null,
+          mod_waste_1.2,mod_waste_null,
+          mod_waste_1.3, mod_waste_null,
+          mod_waste_1.4, mod_waste_null,
+          mod_waste_1.5, mod_waste_null,
           type = "html",
-          se  = list(mod_relevance_1.1.a.robust_se,NULL,
-                     mod_relevance_1.2.a.robust_se,NULL,
-                     mod_relevance_1.3.a.robust_se,NULL,
-                     mod_relevance_1.4.a.robust_se,NULL),
+          se  = list(mod_waste_1.1.robust_se,NULL,
+                     mod_waste_1.2.robust_se,NULL,
+                     mod_waste_1.3.robust_se,NULL,
+                     mod_waste_1.4.robust_se,NULL,
+                     mod_waste_1.5.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("(2.",1:5,")"),
+          column.separate = c(2,2,2,2,2),
+          dep.var.labels="Trust in recycling policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information"),
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","No","","No","","No","","Yes","","No",""),
+                           c("F Statistic", 
+                             mod_waste_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
+The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes.append = FALSE)
+
+```
+
+<br>
+
+```{r}
+
+SVIVA2_00_comb.haifa = SVIVA2_00_comb %>% filter(AREA_center==0)
+
+mod_relevance_null = lm(TRUST_air_INDEX~1,data=SVIVA2_00_comb.haifa)
+mod_relevance_1.1 = update(mod_relevance_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   RELEVANCE_exp)
+mod_relevance_1.2 = update(mod_relevance_1.1,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+mod_relevance_1.3 = update(mod_relevance_1.2,. ~ .+
+                   GENDER+
+                   AGE+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                   CHILDREN_young)
+
+SVIVA2_00_comb.haifa_air_first <- SVIVA2_00_comb %>%
+  filter(AREA_center==0, AIR_order==1)
+
+mod_relevance_1.4 = update(mod_relevance_1.2,. ~ .,data=SVIVA2_00_comb.haifa_air_first)
+
+## Adjust standard errors & F statistic
+mod_relevance_1.1.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.1, type = "HC1")))
+mod_relevance_1.1.wald_results <- waldtest(mod_relevance_1.1, vcov = vcovHC(mod_relevance_1.1, type = "HC1"))
+
+mod_relevance_1.2.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.2, type = "HC1")))
+mod_relevance_1.2.wald_results <- waldtest(mod_relevance_1.2, vcov = vcovHC(mod_relevance_1.2, type = "HC1"))
+
+mod_relevance_1.3.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.3, type = "HC1")))
+mod_relevance_1.3.wald_results <- waldtest(mod_relevance_1.3, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+mod_relevance_1.4.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.4, type = "HC1")))
+mod_relevance_1.4.wald_results <- waldtest(mod_relevance_1.4, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+```
+
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – experimental manipulation of perceived personal relevance.**
+
+```{r,results="asis"}
+control.vars <- c("GENDER",
+                  "AGE",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN_young")
+
+stargazer(mod_relevance_1.1,mod_relevance_null,
+          mod_relevance_1.2,mod_relevance_null,
+          mod_relevance_1.3, mod_relevance_null,
+          mod_relevance_1.4, mod_relevance_null,
+          type = "html",
+          se  = list(mod_relevance_1.1.robust_se,NULL,
+                     mod_relevance_1.2.robust_se,NULL,
+                     mod_relevance_1.3.robust_se,NULL,
+                     mod_relevance_1.4.robust_se,NULL),
           style = "apsr",
@@
                            c("F Statistic", 
-                             mod_relevance_1.1.a.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.2.a.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.3.a.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.4.a.wald_results[2,3] %>% round(2),NA)),
+                             mod_relevance_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
@@
           notes.append = FALSE)
-```
-
-- Models for relevance for both groups for recycling. 
-- replicating all regression tables for upfilterred sample.
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-library(car)
-
-SVIVA2_comb_robust_1 = SVIVA2_00 %>%
-  filter(!(AGE %in% 1:17)) %>% 
-  dplyr::select(IP,USER_ID,AREA,AREA_names,
-      RELEVANCE_exp,RELEVANCE_exp_n,
-      SYMBOL,SYMBOL_n,
-      INFORMATION_air,INFORMATION_air_n,
-      INFORMATION_waste,INFORMATION_waste_n,
-      TRUST_air_INDEX,
-      TRUST_waste_INDEX,
-      ELABORATION_air_time_log,
-      ELABORATION_waste_time_log,
-      ELABORATION_air_time,
-      ELABORATION_waste_time,
-      MEMORY_air_score,
-      MEMORY_waste_score,
-      GOV_TRUST,
-      GENDER,
-      AIR_order,
-      WASTE_order) %>% 
-  gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
-  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
-                              INFORMATION_waste),
-         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
-                                INFORMATION_waste_n),
-         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
-                                       ELABORATION_waste_time_log),
-         MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
-                               MEMORY_waste_score),
-         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
-                                       ELABORATION_waste_time)) %>% 
-  mutate(TRUST_air_INDEX = ifelse(policy=="TRUST_air_INDEX",trust,NA),
-         TRUST_waste_INDEX = ifelse(policy=="TRUST_waste_INDEX",trust,NA),
-         INFORMATION_weak = Recode(INFORMATION,"0=1;1=0"),
-         AREA_center = Recode(AREA,"0=1;1=0"),
-         SYMBOL_t = factor(Recode(SYMBOL,"1=2;2=1")),
-         SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
-         SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")),
-         ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order))
-
-```
-
-In the tables below, I report the results of additional robust analyses testing the moderating role of the perceived personal relevance of the communications.
-
-In **Tables A4 - A6**, I examine the effects of relevance treatment and the differences between the areas on subjects elaboration of the two policy plans, using three additional measures.
-The first measure is the number of seconds participants spent on scanning the policy plans, log transformed (hereafter: reaction time).
-The second measure is participants' score in a memory test, which was conducted during the survey.
-Participants were asked to indicate whether a list of four items were included in the second policy plan which was presented to them, of which two were/were not included (participants could also select “I don’t know”).
-The memory score is calculated as the number of correct items selected by the participant minus the number of incorrect items, with a minimum score of zero.
-Accordingly, participants could receive the scores of 0, 1 or 2.
-The third measure is the delta between trust in the strong and weak policy plans presented to each subject.
-This within-subject analysis utilizes the research design in which every participant was presented with one weak and one strong policies.
-Neither residing in the Haifa-bay nor the relevance treatment increase the elaboration of policy plans, based on these three measures.
-
-In **Tables A7 and A8**, I replicate the main analyses while adding additional control variables.
-In Tables A7, I control for demographics and additional individual-level covariates, including ideology and trust in government ministries in general.
-In Table A8 I further control for factors that can be related to participants' motivation to elaborate, including having young children, general interest in environmental issues and following environmental issues in the media.
-The two final variables are based on survey items which were presented only to those subjects assigned to the relevance treatment condition, and therefore, their analysis is based only on that sample (*n* = `r SVIVA2_01 %>% filter(RELEVANCE_exp==1) %>% nrow()`).
-Finally, in **Table A9**, I add those subjects who were filtered, except for those who are under the age of 18 (*n* = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`).
-In all these analyses, the effects of the symbols and information manipulations and their interaction with the areas and the relevance manipulation are consistent with the main models.
-
-In **Table A10** I analyze subjects' subjective reporting on the personal relevance of each of the two policy plans, and its interaction with the symbols and information manipulations, controlling for the areas.
-These analyses show that higher scores of perceived personal relevance did not attenuate the positive effect of the real symbols.
-However, it did slightly increase the effect of the weak information with regard to the air-pollution policy, consistent with Hypothesis 2.
-
-<br>
-
-<br>
-
-**Table A4: Regression table - effect of personal relevance on reaction time**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_RT_air_1.1_apx = lm(ELABORATION_air_time_log~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
-mod_RT_air_1.2_apx = update(mod_RT_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-mod_RT_waste_1.1_apx = lm(ELABORATION_waste_time_log~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
-mod_RT_waste_1.2_apx = update(mod_RT_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-stargazer(mod_RT_air_1.1_apx,mod_RT_air_1.2_apx,
-          mod_RT_waste_1.1_apx,mod_RT_waste_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
-          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
-                             "Relevance treatment",
-                             "Area x Relevance treatment"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A5: Regression table - effect of personal relevance on memory score**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_memory_air_1.1_apx = lm(MEMORY_air_score~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
-mod_memory_air_1.2_apx = update(mod_memory_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-mod_memory_waste_1.1_apx = lm(MEMORY_waste_score~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
-mod_memory_waste_1.2_apx = update(mod_memory_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-stargazer(mod_memory_air_1.1_apx,mod_memory_air_1.2_apx,
-          mod_memory_waste_1.1_apx,mod_memory_waste_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
-          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
-                             "Relevance treatment",
-                             "Area x Relevance treatment"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A6: Regression table - effect of personal relevance on within-subject delta between strong and weak policies**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_delta_1.1_apx = lm(WITHIN_DELTA~AREA_center+RELEVANCE_exp,data=SVIVA2_01)
-mod_delta_1.2_apx = update(mod_delta_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-stargazer(mod_delta_1.1_apx,mod_delta_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Within-subject delta"),
-          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
-                             "Relevance treatment",
-                             "Area x Relevance treatment"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A7: Regression table - adding control variables**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION,data=SVIVA2_01_comb)
-mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-
-mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+GENDER+IDEOLOGY+GOV_TRUST+INCOME+EDUCATION,data=SVIVA2_01_comb)
-mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-
-stargazer(mod_air_1.1_apx,mod_air_1.2_apx,
-          mod_waste_1.1_apx,mod_waste_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak policy (0=strong policy)",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Relevance treatment",
-                             "Gender (1=Woman)",
-                             "Ideology",
-                             "Trust in government ministries",
-                             "Income",
-                             "Education",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information",
-                             "Relevance treatment x Real symbols",
-                             "Relevance treatment x Fake symbols",
-                             "Relevance treatment x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A8: Regression table - adding personal relevance and motivational control variables**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp+CHILDREN_young,data=SVIVA2_01_comb)
-mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-mod_air_1.3_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+ENVIRONMENT_INTEREST+ENVIRONMENT_FOLLOW+CHILDREN_young,data=SVIVA2_01_comb)
-mod_air_1.4_apx = update(mod_air_1.3_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak))
-
-mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+ENVIRONMENT_INTEREST+ENVIRONMENT_FOLLOW+CHILDREN_young,data=SVIVA2_01_comb)
-mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak))
-
-stargazer(mod_air_1.1_apx,mod_air_1.2_apx,mod_air_1.3_apx,mod_air_1.4_apx,
-          mod_waste_1.1_apx,mod_waste_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak policy (0=strong policy)",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Relevance treatment",
-                             "Interest in environmental issues",
-                             "Follows environmental issues in media",
-                             "Having young children (under 12)",
-                              "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information",
-                             "Relevance treatment x Real symbols",
-                             "Relevance treatment x Fake symbols",
-                             "Relevance treatment x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A9: Regression table - unfiltered sample**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp,data=SVIVA2_comb_robust_1)
-mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-
-mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak+AREA_center+RELEVANCE_exp,data=SVIVA2_comb_robust_1)
-mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ . +AREA_center*(SYMBOL_t+INFORMATION_weak)+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
-
-stargazer(mod_air_1.1_apx,mod_air_1.2_apx,
-          mod_waste_1.1_apx,mod_waste_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak policy (0=strong policy)",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Relevance treatment",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information",
-                             "Relevance treatment x Real symbols",
-                             "Relevance treatment x Fake symbols",
-                             "Relevance treatment x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-**Table A10: Regression table - subjective reporting of perceived personal relevance**
-
-```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_air_1.1_apx = lm(TRUST_air_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_air_1.2_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
-mod_air_1.3_apx = update(mod_air_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)
-
-mod_waste_1.1_apx = lm(TRUST_waste_INDEX~SYMBOL_t+INFORMATION_weak,data=SVIVA2_01_comb)
-mod_waste_1.2_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs+AREA_center)
-mod_waste_1.3_apx = update(mod_waste_1.1_apx,. ~ .+RELEVANCE_obs*(SYMBOL_t+INFORMATION_weak)+AREA_center)
-
-stargazer(mod_air_1.2_apx,mod_air_1.3_apx,
-          mod_waste_1.2_apx,mod_waste_1.3_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Reported relevance",
-                             "Area (0=Haifa-Bay; 1=center)",
-                             "Reported relevance x Real symbols",
-                             "Reported relevance x Fake symbols",
-                             "Reported relevance x Weak Information"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
 ```

### 2019-07-16 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 title: "The persuasion of symbolic elements in government public communications, and their moderation by personal relevance"
-author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
+author: '**Saar Alon-Barkat**'
 date: " "
@@
 Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I theorize that citizens are less susceptible to symbols, and more inclined to scrutinize the substantive content of communication, the more they perceive the policy issue at hand as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
-Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa-Bay).
-I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa-Bay area and others.
+Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa Bay).
+I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa Bay area and others.
 The results indicate that even high levels of perceived personal relevance do not attenuate the effect of symbols on citizens' trust, contrary to my expectations.
@@
 The above-mentioned theoretical expectations are tested via a randomized survey experiment, building on the methodology of @petty_1983.
-The experiment focuses, empirically, on the case of the Israeli Environmental Protection Ministry (hereafter: EPM), and its policy for reducing the air pollution in the highly polluted Haifa-Bay area.
+The experiment focuses, empirically, on the case of the Israeli Environmental Protection Ministry (hereafter: EPM), and its policy for reducing the air pollution in the highly polluted Haifa Bay area.
 In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.
@@
 Among others, EPM is responsible for monitoring and regulating the air quality across the country.
-The Haifa-Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa-Bay industrial zone, which is located in proximity of a number of urban residential areas.
+The Haifa Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa Bay industrial zone, which is located in proximity of a number of urban residential areas.
 It is considered the largest industrial zone in the country, with concentration of petrochemical industries, including oil refineries, power plants, and chemical factories.
@@
 While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019].
-Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa-Bay.
-In 2015, the Ministry of Health published statistical data indicating that Haifa-Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
+Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa Bay.
+In 2015, the Ministry of Health published statistical data indicating that Haifa Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
 The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015].
-Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa-Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa-Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
+Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
 Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
@@
 
-The air-pollution in the Haifa-Bay offers a fortunate case for examining the moderating role of perceived personal relevance.
+The air-pollution in the Haifa Bay offers a fortunate case for examining the moderating role of perceived personal relevance.
 The distinction between those who reside in the polluted area and those who do not entails a significant natural variation in that moderating variable.
 Importantly, because this policy issue is intangible and scientifically complicated, the variation in personal relevance is not strongly confounded with personal knowledge about the issue, as is normally the case [@petty_1983].
-Accordingly, those residing in the polluted Haifa-Bay area are likely to be more motivated to scrutinize a government communication about the air-pollution in their area, yet they are not necessarily more capable of critically evaluating its content.
+Accordingly, those residing in the polluted Haifa Bay area are likely to be more motivated to scrutinize a government communication about the air-pollution in their area, yet they are not necessarily more capable of critically evaluating its content.
 That latter assumption was the main reason for selecting that case.
 
-While comparing those residing in the Haifa-Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison.
+While comparing those residing in the Haifa Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison.
 The differences in personal relevance can be theoretically confounded by unobserved covariates, that cannot be effectively controlled in the analyses.
 I address this limitation in the research design in three main ways.
-*First*, in the selection of the research population, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa-Bay, and their comparison group.
-Accordingly, I selected the major cities in the Haifa-Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
+*First*, in the selection of the research population, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa Bay, and their comparison group.
+Accordingly, I selected the major cities in the Haifa Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
 The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##).
@@
 
-*Second*, in addition to the policy regarding the air-pollution in Haifa-Bay, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
+*Second*, in addition to the policy regarding the air-pollution in Haifa Bay, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
 For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
@@
 I henceforth refer to these two policy plans as "air-pollution" and "recycling".
-*Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa-Bay residents.
+*Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa Bay residents.
 
@@
 These filters are neither associated with the areas nor with the experimental conditions.
-Following this screening, I ended up with a sizable analytical sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa-bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.[^footnote_unfiltered_sample]
+Following this screening, I ended up with a sizable analytical sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa Bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.[^footnote_unfiltered_sample]
 
@@
 Then, they were asked to describe the most salient environmental issue in their area of residence.
-These treatment questions were designed to prime those residing in the Haifa-bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
+These treatment questions were designed to prime those residing in the Haifa Bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
 
 [^footnote_relevance_manipulation]: The first three treatment questions were also designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
-In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa-Bay citizens' responses to the air-pollution policy.
+In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.
 
@@
 
-In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa-Bay and the symbols and information manipulations of that policy.
+In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy.
 I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions.
-Additionally, within the Haifa-Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.
+Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.
 I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the relevant two-way interactions.
@@
 The estimated detectable interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
-As for the interactions with the relevance manipulation (among Haifa-Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
+As for the interactions with the relevance manipulation (among Haifa Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
 The power estimations are reported in details in Section ## of the supplementary appendix.
@@
 sd.air.haifa <- SVIVA2_01_comb %>% filter(AREA_center==0)%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max()
+
+sd.waste <- SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max()
+
 ```
@@
 The key independent variables are the manipulations of symbols[^footnote_symbols_manipulation_check] and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.
-The latter is operationalized observationally (through the distinction between the two areas: Haifa-Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
+The latter is operationalized observationally (through the distinction between the two areas: Haifa Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
 
@@
 
-Living in Haifa-bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa-Bay cities.
-To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa-Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
+Living in Haifa Bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa Bay cities.
+To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas.
@@
 before presenting the policy plans).
-Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa-Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa-Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
+Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
 Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.
@@
 
-[^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa-Bay area, as related to air-pollution.
+[^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa Bay area, as related to air-pollution.
 To confirm inter-coder reliability, a second coder independently coded 70 observations (Krippendorff’s alpha = `r kripp.alpha(df.air.content.reliability)[["value"]] %>% round(2)`).
@@
 
-As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa-Bay respondents' perceptions of personal relevance of the air-pollution policy.
+As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa Bay respondents' perceptions of personal relevance of the air-pollution policy.
 In fact, those assigned to the treatment group reported sightly lower level of personal relevance on average, yet these differences are not statistically significant (*t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
@@
 These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues.
-Yet, Haifa-Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.
+Yet, Haifa Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.
 
@@
 I now turn to exploring respondents trust in the *air-pollution policy*.
-This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
+This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas.
@@
 That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
-Finally, as presented in the right panel, participants from Haifa-Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-`r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa-Bay subjects have a trust-index score lower than the middle point 4 (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
-This indicates that the majority of the sampled Haifa-Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
+Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+`r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than the middle point 4 (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
+This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
 
@@
 Next, I examine the interactions between the symbols and information manipulation, and the two areas.
-To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa-Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>).
-Likewise, I expect Haifa-bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H<sub>2</sub>).
-`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa-Bay area.
+To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>).
+Likewise, I expect Haifa Bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H<sub>2</sub>).
+`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa Bay area.
 Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group.
 The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups.
-However, these differences were smaller compared with the effect among the Haifa-Bay subjects, and not sufficiently significant.
+However, these differences were smaller compared with the effect among the Haifa Bay subjects, and not sufficiently significant.
 The effects of the information manipulation on the two groups are presented in the right panel.
@@
 They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
-Additionally, these analyses do not provide evidence that the more engaged Haifa-Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
+Additionally, these analyses do not provide evidence that the more engaged Haifa Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
 
@@
 
-`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy.
+`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
 Overall, these models reveal relatively similar patterns to those found in the air-pollution policy.
-Notice that Haifa-Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
-The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa-Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
+Notice that Haifa Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
+The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
 The fact that similar patterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance.
@@
 
-```
-
-[^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`) but not compared with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`).
-As shown in Model 2.3, the real symbols significantly increased Haifa-Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`).
+diff5 <- (mod_waste_1.1 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
+se5 <- (mod_waste_1.1.robust_se %>% tidy() %>% filter(names=="INFORMATION_weak") %>% select(x)) %>% max()
+```
+
+[^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`).
+That effect amounts to `r (diff1/sd.waste) %>% round(3)` SDs [`r ((diff1-1.96*se1)/sd.waste) %>% round(3)`-`r ((diff1+1.96*se1)/sd.waste) %>% round(3)`].
+Yet, the increase is not significant not with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`).
+As shown in Model 2.3, the real symbols significantly increased Haifa Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`).
 The differences between the symbols groups among the center subjects are small and insignificant.
 The smaller effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy.
+The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
 In model 2.5, the interaction between weak information and the center area is positive, but far from significance.
@@
 First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in priming those subjects.
-Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa-Bay subjects.
+Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa Bay subjects.
 Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
-Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] This indicates that even Haifa-Bay residents that were reminded about the relevance of the air-pollution to their lives area are positively affected, at least to some degree, by familiar symbols.
+Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] This indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area are positively affected, at least to some degree, by familiar symbols.
 
@@
 
-Finally, as an additional test for the robustness of my findings, I further compare between Haifa-Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
+Finally, as an additional test for the robustness of my findings, I further compare between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
 First, I rely on subjects city of residence, and its geographical proximity to the polluting industrial area.
-Congruently, I selected the three cities/suburbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa-Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
+Congruently, I selected the three cities/suburbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
 The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
@@
 Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that high levels of perceived personal relevance attenuate the effect of symbols on citizens' trust.
-Subjects residing in the polluted Haifa-Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
-However, despite these significant differences, Haifa-bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
-If anything, the results suggest that the symbols had a greater effect on Haifa-bay subjects.
+Subjects residing in the polluted Haifa Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
+However, despite these significant differences, Haifa Bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
+If anything, the results suggest that the symbols had a greater effect on Haifa Bay subjects.
 Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also failed to moderate the effects of the symbols and information in the communications.
@@
 
-How can we explain the finding that the positive effect of the real symbols was stronger among Haifa-Bay residents?
+How can we explain the finding that the positive effect of the real symbols was stronger among Haifa Bay residents?
 Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
-Rather, it might be explained by the lower baseline of Haifa-Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
+Rather, it might be explained by the lower baseline of Haifa Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
 Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
-as in the case of Haifa-Bay subjects), than shifting them from medium to high levels (i.e.
+as in the case of Haifa Bay subjects), than shifting them from medium to high levels (i.e.
 as in the case of center subjects), indicating a ceiling effect.
 Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] A related explanation is that the symbols distracted the subjects and decreased their inclination to think about the topic.
-As a result, they caused Haifa-bay subjects to disregard their prior beliefs about EPM and its failure regarding air-pollution.[^footnote_mediation_elaboration]:
+As a result, they caused Haifa Bay subjects to disregard their prior beliefs about EPM and its failure regarding air-pollution.[^footnote_mediation_elaboration]
 
@@
 This comparison shows a pattern of decreased marginal reduction.
-In the Haifa-Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased by from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
+In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased by from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
 In the center, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
-With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa-bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
+With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa Bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
 
@@
 How can we reconcile the findings of this study with the proposed theory?
-One plausible explanation is that despite the relatively high involvement of Haifa-bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
+One plausible explanation is that despite the relatively high involvement of Haifa Bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
 If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance.
@@
 
-**Air-pollution policy** (Reducing the air-pollution in the Haifa-Bay)
-
-EPM is working to reduce the air-pollution in the Haifa-Bay by:
+**Air-pollution policy** (Reducing the air-pollution in the Haifa Bay)
+
+EPM is working to reduce the air-pollution in the Haifa Bay by:
 
@@
 
-* **Increasing the supervision of the factories in Haifa-Bay**.
+* **Increasing the supervision of the factories in Haifa Bay**.
 In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways.
@@
 
-* **Decreasing the supervision of factories in Haifa-Bay**.
+* **Decreasing the supervision of factories in Haifa Bay**.
 The Ministry is preparing for a change in the method of supervision of the factories.
@@
 * **Raising citizens' awareness of the efforts to improve air quality**.
-In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful.
+In recent years, the Ministry has taken steps to reduce air pollution in Haifa Bay, which have been partially successful.
 The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents.
@@
 
-**Haifa-Bay**
+**Haifa Bay**
 ```{r}
@@
   stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
-  scale_x_discrete(name = "",labels = c("Haifa-Bay","Center"))+
+  scale_x_discrete(name = "",labels = c("Haifa Bay","Center"))+
   scale_y_continuous(name = "",limits=c(1,7),breaks = seq(1,7,by=1))+
@@
                              "Weak Information",
-                             "Area (0=Haifa-Bay; 1=center)",
+                             "Area (0=Haifa Bay; 1=center)",
                              "Area x Real symbols",

### 2019-07-17 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 
+The following regression tables replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`).
+
+<br>
+
+`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – trust in air-pollution policy (unfilterred sample).**
+
 ```{r}
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(1.",1:5,")"),
+          column.labels   = str_c("(a1.",1:5,")"),
           column.separate = c(2,2,2,2,2),
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – trust in recycling policy.**
+<br>
+
+`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – trust in recycling policy (unfilterred sample).**
 
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(2.",1:5,")"),
+          column.labels   = str_c("a(2.",1:5,")"),
           column.separate = c(2,2,2,2,2),
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – experimental manipulation of perceived personal relevance.**
+`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – experimental manipulation of perceived personal relevance (unfilterred sample).**
 
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(3.",1:4,")"),
+          column.labels   = str_c("a(3.",1:4,")"),
           column.separate = c(2,2,2),

### 2019-07-17 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 ---
-title: "The persuasion of symbolic elements in government public communications, and their moderation by personal relevance"
+title: "Does personal relevance attenuate the effect of government branding? Evidence from a survey experiment on air-pollution policy"
 author: '**Saar Alon-Barkat**'
@@
 
-A growing public administration literature explores whether government public communications can enhance citizens' trust in public organizations and policies.
-Most studies have focused on the *informative* aspects of government communications [e.g.
-@marvel_2015; @im_2014; @porumbescu_2017; @porumbescu_2016; @porumbescu_2017a; @porumbescu_2017b; @porumbescu_2018; @grimmelikhuijsen_2015; @ho_2017; @james_2014; @james_2011].
-Recent studies, however, further pointed to the emotive effect of symbolic elements entangled in communications, such as brand names [@teodoro_2018], logos [@karens_2016], and figures [@alonbarkat_2017].
-Such symbols and others exist in almost every government communication, and most prominently in public campaigns and branding activities,[^footnote_branding] which have been increasingly used by public-sector organizations [@eshuis_2012; @marland_2017].
-
-Governments' employment of symbolic communications and branding can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016].
+Public Administration scholars have recently shown a growing interest in government branding, and its potency to influence citizens' perceptions and steer their behaviour[@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015; @karens_2016; @alonbarkat_2017; @teodoro_2018].
+Recent experimental studies established that symbolic, brand elements[^footnote_branding] entangled in government communications (e.g.
+logos, brand names, figures, celebs) can have an emotional effect on citizens, which may significantly enhance their trust in government organizations and policies [@karens_2016; @alonbarkat_2017; @teodoro_2018], and positively affect their evaluation of services [@marvel_2015a].
+This scholarly interest corresponds with an overall increase in the use of branding by public-sector organizations [@eshuis_2012; ].
+
+[^footnote_branding]: A symbol can be as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
+28-29].
+Eshuis and Klijn [-@eshuis_2012, p.
+19] define brand as *a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it*.
+Brand elements, therefore, can be regarded as symbolic elements.
+
+The employment of symbolic communications by government organizations can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016].
 Accordingly, it can mitigate citizens' distrust in government organizations and enhance their collaboration with their policies.
@@
 
-[^footnote_branding]: A symbol can be as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
-28-29].
-Eshuis and Klijn [-@eshuis_2012, p.
-19] define brand as *a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it*.
-Brand elements, therefore, can be regarded as symbolic elements.
-
-To assess the above concern, this study explores the boundaries of governments' persuasion of citizens through symbolic communication.
-Namely, I seek to examine the conditions under which symbolic elements are likely to be more, or less, effective in shaping (and possibly manipulating) citizens' trust.
-Building on the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], I theorize that citizens are less susceptible to symbols, and more inclined to scrutinize the substantive content of communication, the more they perceive the policy issue at hand as having personal relevance for themselves, which enhances their motivation to engage in elaborate processing of information.
-Employing a survey experiment, I test these hypotheses in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific area (the Haifa Bay).
-I operationalize the perceived personal relevance of the policy plan both experimentally, and by comparing between citizens from the polluted Haifa Bay area and others.
-The results indicate that even high levels of perceived personal relevance do not attenuate the effect of symbols on citizens' trust, contrary to my expectations.
-These findings may suggest that the boundaries of the effect of symbolic communication are wider than expected.
+The latter concern is the main motivation of this study.
+Accordingly, in this study I explore the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, to asses the scope of the risk that symbolic communication practices pose for democratic accountability.
+Specifically, I explore whether citizens are susceptible to symbolic communication also when the issue at hand is highly relevant for them, and may have a salient impact on their lives.
+This is particularly important, since we tend to expect these "vulnerable" groups, both positively and normatively, to be aware of government actions that concern their interests, and hold them to account.
+That positive expectation can be supported by the social psychology theory.
+The Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], postulates that people are more likely to focus on the substantive content of the communication and ignore "peripheral" symbolic elements, the more they perceive the policy issue at hand as having personal relevance for themselves.
+
+Employing a survey experiment, I test this theoretical expectation in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific geographical area (the Haifa Bay).
+The population of the study (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to air-pollution.
+Participants are presented with a policy plan regarding the air-pollution in that area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and content (logically versus logical plan).
+I examine the effects of these manipulations on participants' trust in the policy plan in interaction with the two areas, to test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the different in the substantive content).
+I also test the moderating role of personal relevance experimentally by priming participants to think about accut environmental policy issues in their area of residence.
+Contrary to my expectations, The results indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols on citizens' trust.
+These findings tend to suggest that the boundaries of the effect of symbolic communication are wider than expected.
 I discuss the theoretical and normative implications of these findings.
@@
 
-# The persuasion of symbols and information in government public communications.
+# The persuasive effect of symbols and its moderation by the perceived personal relevance of the communication.
 
@@
 
-Viewed against the above theoretical framework, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
-Conversely, symbolic elements can be regarded as peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
-Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on substantive information.
-Conversely, the less motivated and capable they are to elaborate, the more susceptible they are to symbolic elements in the communication.
+Viewed against the above theoretical framework, symbolic elements can be regarded as peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
+Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on elaborate processing about the substantive content, and the less susceptible they are to symbolic elements in the communication.
 
@@
 This postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-These studies have demonstrated that increasing the perceived personal relevance of a communication enhances the effect of its argumentation and attenuates the effect of peripheral cues.
-Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors]
+These studies have demonstrated that increasing the perceived personal relevance of a communication attenuates the effect of peripheral cues.
+For intance, petty et al.
+1983
+Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors] ## add quote ##
 
@@
 
+<br>
+
+# The moderating effect of perceived personal relevance on argument quality.
+
+Most of the research on government communications and its effect on citizens' attitudes focuses on the substantive information in communications...
+the implicit assumption is that logically persuasive arguments would have a positive effect on citizens' attitudes.
+
+One limitation, that this literature highlights is biased processing.
+
+Yet, a second, understudies limitation, regards citizens' motivation to elaborate and process the substantive content of the communication.
+
+In light of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
+Therefore, while greater perceived personal relevance is expected to attentuate the effect of symbols, it is likely to enhance the effect of substantive information.
+
 *H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 
-These theoretical hypotheses are graphically displayed in `r figure.x=figure.x+1`**Figure `r figure.x`**.
+The two theoretical hypotheses are graphically displayed in `r figure.x=figure.x+1`**Figure `r figure.x`**.
 

### 2019-07-18 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 
-Public Administration scholars have recently shown a growing interest in government branding, and its potency to influence citizens' perceptions and steer their behaviour[@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015; @karens_2016; @alonbarkat_2017; @teodoro_2018].
-Recent experimental studies established that symbolic, brand elements[^footnote_branding] entangled in government communications (e.g.
-logos, brand names, figures, celebs) can have an emotional effect on citizens, which may significantly enhance their trust in government organizations and policies [@karens_2016; @alonbarkat_2017; @teodoro_2018], and positively affect their evaluation of services [@marvel_2015a].
-This scholarly interest corresponds with an overall increase in the use of branding by public-sector organizations [@eshuis_2012; ].
+Public Administration scholarship has recently shown a growing interest in public sector branding, and its potency to influence citizens' perceptions and direct their behaviour [@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015].
+Behavioural studies established that symbolic, brand elements[^footnote_branding] entangled in government communications (e.g.
+brand names, logos, colors and figures) can have an emotional effect on citizens, which leads them to view public organizations and their policies and services more favourably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
+This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade, in part due to the expension of social media and ditigal communication platforms [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
 
@@
 
-The employment of symbolic communications by government organizations can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016].
-Accordingly, it can mitigate citizens' distrust in government organizations and enhance their collaboration with their policies.
-On the other hand, one can argue that the persuasion of citizens through symbols is problematic, since the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
-Furthermore, symbols can compensate for organizations' poor performance and for logically unpersuasive informative content, as empirically demonstrated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
-They can yield a misalignment between citizens' positive perceptions and the "real world".
-This raises the concern that government organizations will strategically exploit symbols to manipulate public opinion and mitigate justified public criticism of their failures.
-
-The latter concern is the main motivation of this study.
-Accordingly, in this study I explore the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, to asses the scope of the risk that symbolic communication practices pose for democratic accountability.
-Specifically, I explore whether citizens are susceptible to symbolic communication also when the issue at hand is highly relevant for them, and may have a salient impact on their lives.
-This is particularly important, since we tend to expect these "vulnerable" groups, both positively and normatively, to be aware of government actions that concern their interests, and hold them to account.
-That positive expectation can be supported by the social psychology theory.
-The Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], postulates that people are more likely to focus on the substantive content of the communication and ignore "peripheral" symbolic elements, the more they perceive the policy issue at hand as having personal relevance for themselves.
-
-Employing a survey experiment, I test this theoretical expectation in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific geographical area (the Haifa Bay).
-The population of the study (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to air-pollution.
-Participants are presented with a policy plan regarding the air-pollution in that area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and content (logically versus logical plan).
-I examine the effects of these manipulations on participants' trust in the policy plan in interaction with the two areas, to test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the different in the substantive content).
-I also test the moderating role of personal relevance experimentally by priming participants to think about accut environmental policy issues in their area of residence.
-Contrary to my expectations, The results indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols on citizens' trust.
+The ability of government organizations to affect citizens via symbolic communications can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their unjustified negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
+Accordingly, it can mitigate citizens' distrust in government organizations and underevaluation of their performance, which represent a serious concern.
+
+Nonetheless, the persuasion of citizens through symbols is also highly problematic.
+Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather then on uncontious emotive responses, produced by government agencies themselves.
+A yet more serious concern regards the potency of symbolic elements in government communications to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
+They can yield a misalignment between citizens' positive perceptions and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
+Moreover, government organizations (or politicians controlling them) could strategically exploit such symbolic communication to manipulate public opinion and mitigate justified public criticism of agencies' failures.
+
+The abovementioned concerns of the negative implications of branding are the main motivation of this study.
+These concerns necessitate a better understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication.
+Understanding the limitations of symbolic persuasion would enable to asses the scope of the risk that these practices pose for democracy.
+
+For this purpose, in this study I explore whether the effect of symbols is restricted to policy issues that are not perceived by citizens as having a significant consequence for their personal lives, or rather, that citizens can be similarly persuaded by symbols even with regard to such personally relevant issues.
+This question is particularly important, since we tend to expect these affected groups to pay more attention to government actions that concern their interests, and to hold them to account for their consequences to a greater extent.
+That expectation can be supported, theoretically, by the social psychology theory Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
+The model postulates that people are more likely to focus on the substantive content of the communication and ignore "peripheral" symbolic elements, the more they perceive the policy issue at hand as having personal relevance for themselves.
+
+Employing a survey experiment, I test this latter theoretical expectation in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific geographical area -- the Haifa Bay.
+The research sample (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to air-pollution.
+I present all participants a policy plan regarding the air-pollution in the Haifa Bay area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and content (logically persuasive versus unpersuasive policy plans).
+I examine the effects of these manipulations on participants' trust in the policy plan accross the two areas, and test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the different in the substantive content).
+I further supplement this observational comparison between the areas with an experimental treatment for the perceived personal relevance of the policy, and with additional robustness tests.
+
+Contrary to my initial expectations, the results indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols on citizens' trust.
 These findings tend to suggest that the boundaries of the effect of symbolic communication are wider than expected.
@@
 
-The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a comprehensive theoretical framework for investigating the effects of communications on people's attitudes [@petty_1986; @petty_2011].
-According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
+Symbolic elements, that evoke particular associations and emotions, are included in almost every government communication with citizens, and most most prominently in government advertising and marketing [@eshuis_2012].
+These symbols can affect citizens' attitudes unconsciously through a psychological mechanism of evaluative conditioning -- the positive associations towards the symbolic element is transferred to the public organization, following repeated appearance of the symbol in the organization's public communications [@alonbarkat_2017; @dehouwer_2012].
+This mechanism is considerred a primitive form of persuasion which requires very little cognitive effort, as opposed to persuasion resulted by thoughtful consideration of substantive arguments (in the administrative context, for instance - evaluating organizations and policies based on performance information).
+The question under which circumbstances are citizens' more/less susceptible to persuasion via branding, falls within a more general theoretical question of what determines the ways in which individuals process communication messeges.
+
+According to the Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo [@petty_1986; @petty_2011], people may use different processing mechanisms in response to a communication, and accordingly persuasion can occure in different ways.
+depending on the amount of thinking that they dedicate to it.
 When people have high motivation and ability to elaborate on a message, they are likely to focus on the arguments in the communication that are central to the merits of the issue, and scrutinize them ("central route").

### 2019-07-19 paper3_relevance and symbols_revision_01.Rmd
Add files via upload

@@
 date: " "
+always_allow_html: yes
 output:
@@
 brand names, logos, colors and figures) can have an emotional effect on citizens, which leads them to view public organizations and their policies and services more favourably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
-This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade, in part due to the expension of social media and ditigal communication platforms [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
+This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade, in part due to the expension of ditigal communication platforms and the use of social media [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
 
@@
 The ability of government organizations to affect citizens via symbolic communications can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their unjustified negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
-Accordingly, it can mitigate citizens' distrust in government organizations and underevaluation of their performance, which represent a serious concern.
+Accordingly, it can mitigate citizens' distrust in government organizations and underevaluation of their performance.
 
@@
 A yet more serious concern regards the potency of symbolic elements in government communications to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
-They can yield a misalignment between citizens' positive perceptions and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
-Moreover, government organizations (or politicians controlling them) could strategically exploit such symbolic communication to manipulate public opinion and mitigate justified public criticism of agencies' failures.
+Congruently, government branding can yield a misalignment between citizens' positive perceptions and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
+Moreover, government agencies (or politicians controlling them) could strategically use such symbolic communication as a propaganda, seeking to manipulate public opinion and mitigate justified public criticism of agencies' failures.
 
@@
 These concerns necessitate a better understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication.
-Understanding the limitations of symbolic persuasion would enable to asses the scope of the risk that these practices pose for democracy.
+Understanding the limitations of symbolic persuasion would enable to asses more effectively the scope of the risk that these practices pose for democracy.
 
@@
 
-# The persuasive effect of symbols and its moderation by the perceived personal relevance of the communication.
-
-Symbolic elements, that evoke particular associations and emotions, are included in almost every government communication with citizens, and most most prominently in government advertising and marketing [@eshuis_2012].
-These symbols can affect citizens' attitudes unconsciously through a psychological mechanism of evaluative conditioning -- the positive associations towards the symbolic element is transferred to the public organization, following repeated appearance of the symbol in the organization's public communications [@alonbarkat_2017; @dehouwer_2012].
-This mechanism is considerred a primitive form of persuasion which requires very little cognitive effort, as opposed to persuasion resulted by thoughtful consideration of substantive arguments (in the administrative context, for instance - evaluating organizations and policies based on performance information).
-The question under which circumbstances are citizens' more/less susceptible to persuasion via branding, falls within a more general theoretical question of what determines the ways in which individuals process communication messeges.
-
-According to the Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo [@petty_1986; @petty_2011], people may use different processing mechanisms in response to a communication, and accordingly persuasion can occure in different ways.
-depending on the amount of thinking that they dedicate to it.
-When people have high motivation and ability to elaborate on a message, they are likely to focus on the arguments in the communication that are central to the merits of the issue, and scrutinize them ("central route").
-Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route").
-These two routes for persuasion are regarded as two ends of an "elaboration continuum".
-People may also be located between these two ends of the continuum, and then a mixture of these processes will determine their persuasion.
-
-Viewed against the above theoretical framework, symbolic elements can be regarded as peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
-Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on elaborate processing about the substantive content, and the less susceptible they are to symbolic elements in the communication.
-
-This literature has pointed to a variety of factors that shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
-Among others, scholars have theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater.
-This postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-These studies have demonstrated that increasing the perceived personal relevance of a communication attenuates the effect of peripheral cues.
-For intance, petty et al.
-1983
-Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors] ## add quote ##
+# The effect of government branding on citizens' attitudes and its moderation by the perceived personal relevance of the communication.
+
+Symbolic elements that are strategically selected and designed to evoke positive emotions and associations, are included in almost every government communication with citizens, and most most prominently in government advertising and marketing [@eshuis_2012].
+These symbols can affect citizens' attitudes unconsciously through a psychological mechanism of evaluative conditioning, whereby the positive associations triggerred by the symbolic element are transferred to the public organization [@alonbarkat_2017; @dehouwer_2012].
+So for instance, when a public organization uses a popular celebrity endorser in a campaign, the positive connotations for the celebrity (e.g.
+physically attractive, funny, talented) can be extended to the organization, which would lead citizens to also view the organization more favorably.
+This mechanism is considerred a primitive form of persuasion which requires very little cognitive effort, as opposed to persuasion resulted by thoughtful consideration of substantive arguments.
+Thus, the question of under which circumbstances are citizens' more/less susceptible to persuasion via branding, is linked to a more theoretical discussion in social psychology regarding the relations between different psychological processes of persuasion or modification of people's attitudes or judgements in response to communications or messages, and the determinants of these different processes.
+
+According to the Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], persuasion can occur via different process that can be placed along an "elaboration continuum".
+At the high end of that continuum, also called "central route", persuasion occurs through processes that require high degrees of thought and cognitive effort.
+This type of processing involves thoughtful scrutiny of arguments in the communication that are central to the merits of the issue.
+People located at the high end are more likely to form their judgements on the matter based on the logical quality of the arguments, and are more likely to be persuaded by strong, logically persuasive arguments.
+As for those who are located at the low end of that continuum, also called "peripheral route", persuasion may occur mainly through processes that require little ammount of thinking, including evaluative conditioning, and the reliance on other heuristic cues like the message source [@james_2017a].
+When people are located between these two ends of the continuum, a mixture of these processes will operate and determine their persuasion, depending on their relative position.
+
+In any given situation, the position of people along that continuum would be determined, according to ELM, by their motivation and ability to scrutinize the message.
+The more motivated people are to elaborate on the message and the more capable they are of doing so, the more likely they are to focus on the substative arguments, and likewise the less susceptible they are to persuasion via peripheral route processes.
+
+ELM literature has pointed to a variety of factors that shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
+Perhaps the most studied factor in this regard is the perceived personal relevance of the communication (or "issue involvement"), namely the extent to which they perceive the issue at hand as having significant consequences for their own lives.
+That variable has been considered the most important determinant of motivation to scrutinize the message [@petty_2002; @petty_2011].[^footnote_elm_factors] It has been theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
+Studies have established that individuals are more affected by peripheral cues and less affected by argument quality, the less they perceive the issue as personally relevant.
+For instance, in an experimental marketing study by @petty_1983, participants were asked to express their attitudes about a new product (disposable razor), after being exposed to a magazine ad, which contained either strong or weak arguments about
+the product, and involved either a non-famous endorser or a celebrity endorser (a symbolic peripheral cue).
+To manipulate the personal relevance of the product, subjects were either told that the product would soon be available in their local area (high relevance), or in other areas (low relevance).
+The results showed the effect of the celebrity endorser was higher among the low personal relevance group, whereas the effect of argument quality was significantly weaker for that group.
 
@@
 
-Connecting the above public administration literature on citizens' responses to government public communications with the social psychology ELM literature, I theorize that:
-
-*H<sub>1</sub> - Symbolic elements in communications are less (more) likely to increase citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
-
-<br>
-
-# The moderating effect of perceived personal relevance on argument quality.
+Viewed against the above theoretical framework, symbolic elements can be regarded as peripheral cues, which can affect attitudes by a peripheral route process of evaluative conditioning.[##add footnote, in rare occations, symbolic elements could also serve as arguments, e.g.
+a slogan that both has a symbolic meaning and also contains an argument##].
+Hence, ELM postulates that citizens' are more likely to be affected by symbols the less motivated and capable they are to critically think about the message, which likely to be determined by the perceived personal relevnace of the policy issue.
+
+*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the more citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+
+*H<sub>2</sub> - The logical quality of the substantive arguments in the communication is more likely to affect citizens' attitudes about government organizations and policies, the more citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+
+<br>
+
+# The effect of substantive information in moderating effect of perceived personal relevance on argument quality.
 
@@
 Therefore, while greater perceived personal relevance is expected to attentuate the effect of symbols, it is likely to enhance the effect of substantive information.
-
-*H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 

### 2019-07-21 paper3_revision_tables.Rmd
Add files via upload

--- 2019-07-17 paper3_relevance and symbols_revision_01.Rmd
@@
 ---
-title: "Does personal relevance attenuate the effect of government branding? Evidence from a survey experiment on air-pollution policy"
+title: "Does personal relevance attenuate citizens' persuasion by government branding? Evidence from a survey experiment on air-pollution policy"
 author: '**Saar Alon-Barkat**'
 date: " "
+always_allow_html: yes
 output:
@@
     theme: flatly
-    toc: yes
-    toc_float:
-      collapsed: no
-      smooth_scroll: yes
-      toc_depth: 3
   pdf_document:
@@
 
----
-
-# Abstract
-
-*Recent studies demonstrated that symbolic elements in government communications can enhance citizens' trust in government organizations and policies.
-The emotive effect of symbols can further compensate for organizations' poor functioning, thereby eliciting undue trust.
-This study explores the boundaries of governments' persuasion of citizens through symbolic communication.
-Building on social psychology, I hypothesize that citizens are less susceptible to symbols, the more they perceive the policy issue in the communication as personally relevant.
-I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted area.
-The policy's perceived personal relevance is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
-The results indicate that even high levels of perceived personal relevance do not attenuate the symbols' effect, which entails that the boundaries of persuasion through symbols are wider than expected.*
-
-<br>
-
-*Keywords: Government communications; Government branding; Trust; Experiment*
-
----
-
-<br>
-
-# Introduction
-
-Public Administration scholars have recently shown a growing interest in government branding, and its potency to influence citizens' perceptions and steer their behaviour[@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015; @karens_2016; @alonbarkat_2017; @teodoro_2018].
-Recent experimental studies established that symbolic, brand elements[^footnote_branding] entangled in government communications (e.g.
-logos, brand names, figures, celebs) can have an emotional effect on citizens, which may significantly enhance their trust in government organizations and policies [@karens_2016; @alonbarkat_2017; @teodoro_2018], and positively affect their evaluation of services [@marvel_2015a].
-This scholarly interest corresponds with an overall increase in the use of branding by public-sector organizations [@eshuis_2012; ].
-
-[^footnote_branding]: A symbol can be as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
-28-29].
-Eshuis and Klijn [-@eshuis_2012, p.
-19] define brand as *a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it*.
-Brand elements, therefore, can be regarded as symbolic elements.
-
-The employment of symbolic communications by government organizations can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016].
-Accordingly, it can mitigate citizens' distrust in government organizations and enhance their collaboration with their policies.
-On the other hand, one can argue that the persuasion of citizens through symbols is problematic, since the emotive effect of symbols undermines the fundamental normative expectation that citizens' evaluation of their government should be based on their critical judgment.
-Furthermore, symbols can compensate for organizations' poor performance and for logically unpersuasive informative content, as empirically demonstrated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
-They can yield a misalignment between citizens' positive perceptions and the "real world".
-This raises the concern that government organizations will strategically exploit symbols to manipulate public opinion and mitigate justified public criticism of their failures.
-
-The latter concern is the main motivation of this study.
-Accordingly, in this study I explore the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, to asses the scope of the risk that symbolic communication practices pose for democratic accountability.
-Specifically, I explore whether citizens are susceptible to symbolic communication also when the issue at hand is highly relevant for them, and may have a salient impact on their lives.
-This is particularly important, since we tend to expect these "vulnerable" groups, both positively and normatively, to be aware of government actions that concern their interests, and hold them to account.
-That positive expectation can be supported by the social psychology theory.
-The Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011], postulates that people are more likely to focus on the substantive content of the communication and ignore "peripheral" symbolic elements, the more they perceive the policy issue at hand as having personal relevance for themselves.
-
-Employing a survey experiment, I test this theoretical expectation in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific geographical area (the Haifa Bay).
-The population of the study (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to air-pollution.
-Participants are presented with a policy plan regarding the air-pollution in that area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and content (logically versus logical plan).
-I examine the effects of these manipulations on participants' trust in the policy plan in interaction with the two areas, to test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the different in the substantive content).
-I also test the moderating role of personal relevance experimentally by priming participants to think about accut environmental policy issues in their area of residence.
-Contrary to my expectations, The results indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols on citizens' trust.
-These findings tend to suggest that the boundaries of the effect of symbolic communication are wider than expected.
-I discuss the theoretical and normative implications of these findings.
-
-<br>
-
-# The persuasive effect of symbols and its moderation by the perceived personal relevance of the communication.
-
-The Elaboration Likelihood Model (ELM), developed in the late 1970s by social psychology scholars Richard Petty and John Cacioppo, provides a comprehensive theoretical framework for investigating the effects of communications on people's attitudes [@petty_1986; @petty_2011].
-According to ELM, people may respond differently to a communication, depending on the amount of thinking that they dedicate to it.
-When people have high motivation and ability to elaborate on a message, they are likely to focus on the arguments in the communication that are central to the merits of the issue, and scrutinize them ("central route").
-Conversely, when they are unmotivated or unable to elaborate, they may rely on available heuristic cues that require relatively little amount of cognitive effort ("peripheral route").
-These two routes for persuasion are regarded as two ends of an "elaboration continuum".
-People may also be located between these two ends of the continuum, and then a mixture of these processes will determine their persuasion.
-
-Viewed against the above theoretical framework, symbolic elements can be regarded as peripheral cues, which can affect attitudes by evoking emotions and associations attributed to government organizations and their policies (peripheral route).
-Accordingly, the more citizens are motivated to think about the content of the communication, and the more capable they are of doing so, the more they are likely to form their attitudes based on elaborate processing about the substantive content, and the less susceptible they are to symbolic elements in the communication.
-
-This literature has pointed to a variety of factors that shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
-Among others, scholars have theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater.
-This postulation has been empirically tested, and largely confirmed, by numerous ELM based experimental studies in social psychology and marketing [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-These studies have demonstrated that increasing the perceived personal relevance of a communication attenuates the effect of peripheral cues.
-For intance, petty et al.
-1983
-Later reviews of ELM literature considered the factor of perceived personal relevance as the most important determinant of motivation to process a message [@petty_2002; @petty_2011].[^footnote_elm_factors] ## add quote ##
-
-[^footnote_elm_factors]: For a thorough review of motivational and ability factors affecting likelihood to elaborate see @petty_1998.
-
-Connecting the above public administration literature on citizens' responses to government public communications with the social psychology ELM literature, I theorize that:
-
-*H<sub>1</sub> - Symbolic elements in communications are less (more) likely to increase citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
-
-<br>
-
-# The moderating effect of perceived personal relevance on argument quality.
-
-Most of the research on government communications and its effect on citizens' attitudes focuses on the substantive information in communications...
-the implicit assumption is that logically persuasive arguments would have a positive effect on citizens' attitudes.
-
-One limitation, that this literature highlights is biased processing.
-
-Yet, a second, understudies limitation, regards citizens' motivation to elaborate and process the substantive content of the communication.
-
-In light of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
-Therefore, while greater perceived personal relevance is expected to attentuate the effect of symbols, it is likely to enhance the effect of substantive information.
-
-*H<sub>2</sub> - The logical quality of the communication is more (less) likely to affect citizens' trust in government organizations and policies, the more (less) citizens perceive the policy issue in the communication as having personal relevance for themselves.*
-
-The two theoretical hypotheses are graphically displayed in `r figure.x=figure.x+1`**Figure `r figure.x`**.
-
-<br>
-
-[**Figure `r figure.x`** about here]
-
-<br>
-
-# Methodology
-
-The above-mentioned theoretical expectations are tested via a randomized survey experiment, building on the methodology of @petty_1983.
-The experiment focuses, empirically, on the case of the Israeli Environmental Protection Ministry (hereafter: EPM), and its policy for reducing the air pollution in the highly polluted Haifa Bay area.
-In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.
-
-It should be noted that the experiment was additionally designed to test a set of hypotheses regarding the interaction between symbols and information in communications.
-The methodological aspects which are relevant for examining the additional hypotheses are described in a separate publication.
-In the following sections, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
-An English translation of the full survey is available in section ## of the supplementary Appendix.
-
-EPM is a national-level bureau responsible for the formulation, coordination, and execution of environmental policy in Israel.
-Among others, EPM is responsible for monitoring and regulating the air quality across the country.
-The Haifa Bay area, located in the north of Israel, has been characterized by relatively high levels of air pollution, mainly due to the Haifa Bay industrial zone, which is located in proximity of a number of urban residential areas.
-It is considered the largest industrial zone in the country, with concentration of petrochemical industries, including oil refineries, power plants, and chemical factories.
-Beginning in Mid 2000s, EPM has been developing and implementing a series of policy programs to monitor and reduce the high levels of pollution specifically in that area [@theministryofenvironmentprotection_2015; @theministryofenvironmentprotection_2015a; @theministryofenvironmentprotection_2019].
-While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019].
-Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa Bay.
-In 2015, the Ministry of Health published statistical data indicating that Haifa Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
-The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015].
-Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
-Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
-These publications, and others, caused much panic among the local population, and especially among young parents.
-
-[^footnote_epidemiological_study]: The epidemiological study was originally sponsored by Ministry of Health.
-The study, which was  conducted by researchers from Haifa University, was planned to be conducted over five years, between 2015-2020.
-The findings, which leaked to the media, regarded the interim results of the first year of the study.
-Following that publication, the study has been significantly criticized by the local research community as well as the professional steering committee of the research.
-As a result, in 2017, the Ministry decided to cancel its involvement in that research.
-
-The air-pollution in the Haifa Bay offers a fortunate case for examining the moderating role of perceived personal relevance.
-The distinction between those who reside in the polluted area and those who do not entails a significant natural variation in that moderating variable.
-Importantly, because this policy issue is intangible and scientifically complicated, the variation in personal relevance is not strongly confounded with personal knowledge about the issue, as is normally the case [@petty_1983].
-Accordingly, those residing in the polluted Haifa Bay area are likely to be more motivated to scrutinize a government communication about the air-pollution in their area, yet they are not necessarily more capable of critically evaluating its content.
-That latter assumption was the main reason for selecting that case.
-
-While comparing those residing in the Haifa Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison.
-The differences in personal relevance can be theoretically confounded by unobserved covariates, that cannot be effectively controlled in the analyses.
-I address this limitation in the research design in three main ways.
-*First*, in the selection of the research population, I sought to reduce differences in socioeconomic and demographic variables between residents of Haifa Bay, and their comparison group.
-Accordingly, I selected the major cities in the Haifa Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
-The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##).
-I also searched relevant EPM documents and news websites for any reporting about high air-pollution levels in the three center cities, to ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies.
-
-*Second*, in addition to the policy regarding the air-pollution in Haifa Bay, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
-For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
-The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements and variation in substantive information in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates.
-I henceforth refer to these two policy plans as "air-pollution" and "recycling".
-*Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa Bay residents.
-
-[^footnote_qiryat-Hayiim]: Qiryat-Hayiim is considered a neighborhood within the jurisdiction of Haifa, although it is geographically separated from the rest of the city, and people tend to distinguish it, informally.
-
-<br>
-
-## *Data collection and Procedure*
-
-To select and recruit residents of these selected cities, I was assisted by an Israeli internet research panel company *iPanel*.
-The survey experiment was conducted online through Qualtrics Survey Software.
-The online survey link was sent by iPanel between 28.1-1.2.2018.
-A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
-Thereafter, I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
-These filters are neither associated with the areas nor with the experimental conditions.
-Following this screening, I ended up with a sizable analytical sample of `r N_1` subjects, of whom `r SVIVA2_01_haifa%>%nrow()` live in the Haifa Bay cities, and `r SVIVA2_01_center%>%nrow()` live in the center cities.[^footnote_unfiltered_sample]
-
-[^footnote_unfiltered_sample]: In the supplementary appendix, I replicate the main models on the unfiltered sample, with no significant change to the results.
-
-The survey was presented to the participants as an academic study about citizens' attitudes regarding environmental policies in general.
-After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance manipulation).
-Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
-Then, they were asked to describe the most salient environmental issue in their area of residence.
-These treatment questions were designed to prime those residing in the Haifa Bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
-
-[^footnote_relevance_manipulation]: The first three treatment questions were also designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
-In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.
-
-Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order).
-They were informed that these plans were obtained from EPM's annual work plan.
-Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information manipulation): strong policy (i.e.
-logically persuasive policy plan) or weak policy (i.e.
-logically unpersuasive).
-Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order.
-For instance, a subject who first received a strong air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
-The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
-The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
-
-The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the real symbols condition, the two policies (as explained, one weak and one strong) are displayed with three symbolic elements, which have been used in EPM's public communications, and became widely recognized by the public.
-The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second element is the green color, which is strongly associated with taking care of the environment.
-The third element is an image of a celebrity comedian from an advertising campaign of the EPM.
-The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
-The recycling policy in the real symbols condition was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum.
-In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images.
-In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people.
-The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic identifiers (i.e.
-the symbolic effect) from a possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy.
-The symbols conditions are displayed in **Appendix B**.
-Further details about the real and fake symbols are found in section ## of the supplementary appendix.
-
-Each policy plan was followed by six questions about respondents' trust in the policy.
-After the trust questions of the second policy, the subjects were asked additional questions about the two policies, including the degree to which they perceive each of them as personally relevant.
-These questions were followed by an Instructional Manipulation Check (IMC) item, intended to assess participants’ diligence.
-The last sections included a set of demographic questions including questions about their place of residence and work, and manipulation checks for participants' familiarity with the real symbols.
-At the end of the survey, the participants were debriefed about the manipulations, and the possible deception.
-
-In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy.
-I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions.
-Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.
-I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the relevant two-way interactions.
-I conducted these estimations after the data collection and analyses, based on the analytical sample size.
-The estimated detectable interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
-As for the interactions with the relevance manipulation (among Haifa Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
-The power estimations are reported in details in Section ## of the supplementary appendix.
-
-<br>
-
-## *Variables*
-
-```{r}
-alpha_air_trust = psych::alpha(select(SVIVA2_01, TRUST_air_q1,
-                               TRUST_air_q2,
-                               TRUST_air_q3,
-                               TRUST_air_q4,
-                               TRUST_air_q5,
-                               TRUST_air_q6))[["total"]][["raw_alpha"]]%>%round(2)
-
-alpha_waste_trust = psych::alpha(select(SVIVA2_01, TRUST_waste_q1,
-                               TRUST_waste_q2,
-                               TRUST_waste_q3,
-                               TRUST_waste_q4,
-                               TRUST_waste_q5,
-                               TRUST_waste_q6))[["total"]][["raw_alpha"]]%>%round(2)
-
-alpha_trust_comb = ((alpha_air_trust+alpha_waste_trust)/2)%>%round(2)
-
-relevance.areas.d <- cohen.d(SVIVA2_01$RELEVANCE_air_obs~SVIVA2_01$AREA_center)
-relevance.exp.d <- cohen.d(RELEVANCE_air_obs~RELEVANCE_exp, SVIVA2_01_haifa)
-
-relevance.exp.t <- t.test(RELEVANCE_air_obs~RELEVANCE_exp, SVIVA2_01_haifa)
+```{r}
 
@@
 
-The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for air-pollution policy, and `r alpha_waste_trust` for the recycling policy).
-This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
-Participants were asked to indicate their agreement with the following statements, between 1 (weakly agree) and 7 (strongly agree): (1) I believe that the actions mentioned in the policy plan will assist in fulfilling the policy goal; (2) I believe that the actions mentioned in the policy plan were designed in a professional manner; (3) I believe that the policy plan is in the interest of citizens; (4) I believe that the policy plan reflects a genuine attempt to improve the well-being of citizens; (5) I believe that EPM made an honest attempt to design a good policy plan; (6) I believe that the Ministry of Environmental Protection aims to keep its commitments in that policy plan.
-
-The key independent variables are the manipulations of symbols[^footnote_symbols_manipulation_check] and information in the communication, as described above, and their interactions with the perceived personal relevance of the communication.
-The latter is operationalized observationally (through the distinction between the two areas: Haifa Bay and center) as well as experimentally (through the abovementioned relevance manipulation).
-
-[^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
-##add check reliability of information.
-##
-
-Living in Haifa Bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa Bay cities.
-To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
-`r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas.
-As expected, the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]).
-By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them.
-Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e.
-before presenting the policy plans).
-Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
-Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.
-
-```{r}
-library(irr)
-
-df.air.content.reliability <- relevance.coding[1:231,] %>% 
-  select(air.content,
-         air.content.coder2) %>% 
-  drop_na(air.content.coder2) %>% 
-  as.matrix() %>% 
-  t()
-
-```
-
-[^footnote_air_relevance_coding]: I coded any reference to either air-pollution or the chemical factories in the Haifa Bay area, as related to air-pollution.
-To confirm inter-coder reliability, a second coder independently coded 70 observations (Krippendorff’s alpha = `r kripp.alpha(df.air.content.reliability)[["value"]] %>% round(2)`).
-
-<br>
-
-[**Figure `r figure.x`** about here]
-
-<br>
-
-As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa Bay respondents' perceptions of personal relevance of the air-pollution policy.
-In fact, those assigned to the treatment group reported sightly lower level of personal relevance on average, yet these differences are not statistically significant (*t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
-This limitation should be kept in mind when interpreting the results regarding this manipulation.
-The results of all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
-
-<br>
-
-# Results
-
-`r table.x=table.x+1`**Tables `r table.x`** compares between the different experimental conditions, within each of the two areas, on demographic variables and pre-manipulation covariates.
-These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues.
-Yet, Haifa Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.
-
-[^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups -- regarding education levels and the percentage of parents; and between the information groups -- regarding the percentage of parents for young children.
-To adjust for small finite-sample imbalances, as well as for differences between the areas, I control for covariates.
-
-<br>
-
-[**Table `r table.x`** about here]
-
-<br>
-
 ```{r}
 mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
-
-mod_air_1.1.symbol = update(mod_air_null,. ~ .+
-                       SYMBOL_t,
-                     data=SVIVA2_01_comb)
-
-mod_air_1.1.info = update(mod_air_null,. ~ .+
-                       INFORMATION_weak,
-                     data=SVIVA2_01_comb)
-
-mod_air_1.1.symbol.haifa = update(mod_air_null,. ~ .+
-                       SYMBOL_t,
-                     data=SVIVA2_01_comb %>% filter(AREA_center==0))
-
-mod_air_1.1.symbol.center = update(mod_air_null,. ~ .+
-                       SYMBOL_t,
-                     data=SVIVA2_01_comb %>% filter(AREA_center==1))
-
-mod_air_1.1.info = update(mod_air_null,. ~ .+
-                       INFORMATION_weak,
-                     data=SVIVA2_01_comb)
-mod_air_1.1.info.haifa = update(mod_air_null,. ~ .+
-                       INFORMATION_weak,
-                     data=SVIVA2_01_comb%>% filter(AREA_center==0))
-mod_air_1.1.info.center = update(mod_air_null,. ~ .+
-                       INFORMATION_weak,
-                     data=SVIVA2_01_comb%>% filter(AREA_center==1))
-
-main.symbols <- emmeans::emmeans(mod_air_1.1.symbol, specs = pairwise ~ SYMBOL_t)
-t.symbols.no <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2))
-t.symbols.fake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0))
-t.symbols.nofake <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1))
-
-cond.symbols.haifa <- emmeans::emmeans(mod_air_1.1.symbol.haifa, specs = pairwise ~ SYMBOL_t)
-t.symbols.no.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=2,AREA_center==0))
-t.symbols.fake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=0,AREA_center==0))
-t.symbols.nofake.haifa <- t.test(TRUST_air_INDEX~SYMBOL_t,data=SVIVA2_01_comb %>% filter(SYMBOL_t!=1,AREA_center==0))
-
-mod_air_1.1.areas = update(mod_air_null,. ~ .+
-                       AREA_center,
-                     data=SVIVA2_01_comb)
-
-main.info <- mod_air_1.1.info %>% tidy()
-t.info <- t.test(TRUST_air_INDEX~INFORMATION_weak,data=SVIVA2_01_comb)
-
-main.areas <- mod_air_1.1.areas %>% tidy()
-t.areas <- t.test(TRUST_air_INDEX~AREA_center,data=SVIVA2_01_comb)
-
-```
-
-I now turn to exploring respondents trust in the *air-pollution policy*.
-This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
-`r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas.
-The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
-Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test).
-The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score.
-Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a very low score of 2 or less, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group.
-As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
-Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-`r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than the middle point 4 (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
-This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
-
-<br>
-
-[**Figure `r figure.x`** about here]
-
-<br>
-
-Next, I examine the interactions between the symbols and information manipulation, and the two areas.
-To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>).
-Likewise, I expect Haifa Bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H<sub>2</sub>).
-`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa Bay area.
-Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group.
-The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups.
-However, these differences were smaller compared with the effect among the Haifa Bay subjects, and not sufficiently significant.
-The effects of the information manipulation on the two groups are presented in the right panel.
-This comparison shows that the differences between participants' trust in the weak and strong policies were roughly similar in both groups.
-
-[^footnote_raw_means]: In addition, raw means and SDs of outcome variables across the two areas are reported in section XX of the supplementary appendix.
-
-<br>
-
-[**Figure `r figure.x`** about here]
-
-<br>
-
-These results are at odds with the two theoretical hypotheses.
-They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
-Additionally, these analyses do not provide evidence that the more engaged Haifa Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
-
-```{r}
 
@@
 ```
-
-I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
-I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3).
-The final two models are designed to test the robustness of the interaction model by controlling for individual-level covariates (Model `r table.x`.4),[^footnote_control_variables] and restricting the sample to those who saw that policy first before the recycling policy (Model `r table.x`.5).
-The latter analysis rules out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
-In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
-In Models `r table.x`.3, `r table.x`.4, `r table.x`.5 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant.
-A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
-Notice that in `r table.x`.5, the effect of the real symbols is greater, which may indicate that the impact of symbols diminishes between the first and the second time participants see them.
-
-[^footnote_heteroskedacity]: Breusch-Pagan test confirms that the null hypotheses that the variance of the residuals is constant.
-For Model 1.3, Breusch-Pagan test =  `r bptest(mod_air_1.3)[["statistic"]][["BP"]] %>% round(3)`, *p*=`r bptest(mod_air_1.3)[["p.value"]][["BP"]] %>% round(3)`.
-Robust standard errors are estimated using R sandwich package with estimation type "HC1".
-
-[^footnote_control_variables]: I control for all the variables that are included in the balancing tables, except for interest in environmental issues, which was reported by only half of the sample.
-In other analyses, I also included that variable, with no significant change to the main results.
-
-<br>
-
-[**Table `r table.x`** about here]
-
-<br>
 
@@
 
-SVIVA2_01_comb <- SVIVA2_01_comb %>% 
-  mutate(SYMBOL_t.r = Recode(SYMBOL_t,"0=2;2=0"))
-
-mod_waste_1.1.r = update(mod_waste_null,. ~ .+
-                       SYMBOL_t.r+
-                       INFORMATION_weak)
-mod_waste_1.1.r.robust_se <- sqrt(diag(vcovHC(mod_waste_1.1.r, type = "HC1")))
-
-mod_waste_1.3.r = update(mod_waste_null,. ~ .+
-                       AREA_center*(SYMBOL_t.r+INFORMATION_weak))
-mod_waste_1.3.r.robust_se <- sqrt(diag(vcovHC(mod_waste_1.3.r, type = "HC1")))
-```
-
-Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
-Accordingly, they do not support the research hypotheses.
-Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence I cannot rule out a concern of endogeneity.
-Accordingly, the null findings regarding the interactions between the areas and the manipulations can be a result by other, unobserved differences between the two populations.
-As explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
-I now discuss the results of these two tests.
-
-`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
-Overall, these models reveal relatively similar patterns to those found in the air-pollution policy.
-Notice that Haifa Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
-The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
-The fact that similar patterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance.
-It also rules out a possible argument that greater relevance enhances (rather then reduces) the effect of symbols.
-If this was the case, then there should have been no interaction between symbols and the areas for the recycling policy.
-
-```{r}
-
-symbols.waste <- emmeans::emmeans(mod_waste_1.1, specs = pairwise ~ SYMBOL_t)
-
-diff1 <- (symbols.waste$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)) %>% abs() %>% round(3)
-se1 <- (mod_waste_1.1.robust_se %>% tidy() %>% filter(names=="SYMBOL_t1") %>% select(x)) %>% max()
-
-diff2 <- (symbols.waste$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)) %>% abs() %>% round(3)
-se2 <- (mod_waste_1.1.r.robust_se %>% tidy() %>% filter(names=="SYMBOL_t.r1") %>% select(x)) %>% max()
-
-diff3 <- (mod_waste_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
-se3 <- (mod_waste_1.3.robust_se %>% tidy() %>% filter(names=="SYMBOL_t1") %>% select(x)) %>% max()
-
-diff4 <- (mod_waste_1.3.r %>% tidy() %>% filter(term=="SYMBOL_t.r1") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
-se4 <- (mod_waste_1.3.r.robust_se %>% tidy() %>% filter(names=="SYMBOL_t.r1") %>% select(x)) %>% max()
-
-diff5 <- (mod_waste_1.1 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.)) %>% abs() %>% round(3)
-se5 <- (mod_waste_1.1.robust_se %>% tidy() %>% filter(names=="INFORMATION_weak") %>% select(x)) %>% max()
-```
-
-[^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`).
-That effect amounts to `r (diff1/sd.waste) %>% round(3)` SDs [`r ((diff1-1.96*se1)/sd.waste) %>% round(3)`-`r ((diff1+1.96*se1)/sd.waste) %>% round(3)`].
-Yet, the increase is not significant not with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`).
-As shown in Model 2.3, the real symbols significantly increased Haifa Bay subjects' trust in that policy compared with the no symbols group (*Diff*=`r diff3` [`r (diff3-1.96*se3) %>% round(3)`-`r (diff3+1.96*se3) %>% round(3)`], *t*=`r (diff3/se3) %>% round(3)`), whereas the increase compared with the fake symbols group was not sufficiently significant (*Diff*=`r diff4` [`r (diff4-1.96*se4) %>% round(3)`-`r (diff4+1.96*se4) %>% round(3)`], *t*=`r (diff4/se4) %>% round(3)`).
-The differences between the symbols groups among the center subjects are small and insignificant.
-The smaller effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy.
-The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
-In model 2.5, the interaction between weak information and the center area is positive, but far from significance.
-
-<br>
-
-[**Table `r table.x`** about here]
-
-<br>
+```
 
@@
 
-Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations.
-In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations.
-Similarly to the regression tables presented above, the final two models are robust analyses where I add controls (Model `r table.x`.3) and restrict the sample to the policy presented first in order (Model `r table.x`.4).
-In all these models, the coefficient of the relevance treatment is negative but far from significance.
-The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the averaged differences between those who saw the symbols and those who did not were slightly smaller.
-However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group) and far from significance.
-The interactions between the relevance treatment and weak information manipulations are positive but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
-
-[^footnote_relevance_manipulation_1]: In additional analyses, I also examine the moderating effect of the relevance treatment for center subjects' responses to air-pollution policy, as well as for the recycling policy (for the entire sample).
-In all these analyses, the interactions with the relevance treatment are insignificant.
-
-Two limitations about these analyses should be acknowledged.
-First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in priming those subjects.
-Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa Bay subjects.
-Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
-Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] This indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area are positively affected, at least to some degree, by familiar symbols.
-
-[^footnote_relevance_significance_fakesymbols]: Consistently with the previous models, subjects in the real symbols group also reported higher trust compared with the fake symbols, but these differences are not sufficiently significant.
-The differences between the two control groups are insignificant.
-
 ```{r}
@@
 
-relevance.areas.close.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area) 
-relevance.areas.close.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area)
-
-relevance.areas.children.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young) 
-relevance.areas.children.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young)
-
-```
-
-Finally, as an additional test for the robustness of my findings, I further compare between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
-First, I rely on subjects city of residence, and its geographical proximity to the polluting industrial area.
-Congruently, I selected the three cities/suburbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
-The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
-Second, since young children are relatively vulnerable to air-pollution effects, and since the consequences of air-pollution on infants and young children has been highlighted in media, I expect parents for young children (under 12 years) to be more engaged with this issue, although that assumption is not supported by differences in self-reported perceived personal relevance.[^footnote_post_treatment_control]
-
-`r table.x=table.x+1`**Table `r table.x`** presents the interactions between these two variables and information manipulations.
-Model `r table.x`.1 presents the effect of these variables with the manipulations, and thereafter Model `r table.x`.2 adds their interactions, and finally Model `r table.x`.3 restricts the analysis to the first policy presented.
-All three models include control variables.
-The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols (the interaction is significant in Model `r table.x`.2, but not in Model `r table.x`.3).
-As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.[^footnote_proxies_models]
-
-[^footnote_post_treatment_control]: In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
-In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
-However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
-188-9].
-
-[^footnote_proxies_models]: The interaction between proximity and the real symbols is positive and significant in Model `r table.x`.2, in Model `r table.x`.3  it is positive but insignificant; The interaction between parents for young children and the fake symbols is positive and significant in Model `r table.x`.2.
-
-<br>
-
-# Discussion and conclusion
-
-Public communications have been proposed as a remedy for citizens’ low trust in government, and for their underestimation of public-service performance.
-Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries.
-This study contributes to the growing Public-Administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications.
-I explored the expectation, derived from social psychology, that citizens are less affected by symbols and more likely to scrutinize the content of the communication the more they perceive it as relevant to their own lives.
-I put these hypotheses to rigorous empirical testing, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
-I exploited the natural variation in citizens' perceptions of the personal relevance of the ministry’s policy plan regarding air pollution in a specific area.
-In addition to utilizing these natural differences, I also manipulated the personal relevance of the policy plans.
-To the best of my knowledge, this is the first study to assess the moderating role of perceived personal relevance on citizens' responses to government symbolic communications or branding.
-
-Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that high levels of perceived personal relevance attenuate the effect of symbols on citizens' trust.
-Subjects residing in the polluted Haifa Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
-However, despite these significant differences, Haifa Bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
-If anything, the results suggest that the symbols had a greater effect on Haifa Bay subjects.
-Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also failed to moderate the effects of the symbols and information in the communications.
-These findings are also consistent with the findings of @alonbarkat_2017, where they found that the trust of citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) was nonetheless significantly affected by a symbol of the government-owned electricity company.
-
-How can we explain the finding that the positive effect of the real symbols was stronger among Haifa Bay residents?
-Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
-Rather, it might be explained by the lower baseline of Haifa Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
-Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
-as in the case of Haifa Bay subjects), than shifting them from medium to high levels (i.e.
-as in the case of center subjects), indicating a ceiling effect.
-Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] A related explanation is that the symbols distracted the subjects and decreased their inclination to think about the topic.
-As a result, they caused Haifa Bay subjects to disregard their prior beliefs about EPM and its failure regarding air-pollution.[^footnote_mediation_elaboration]
-
-[^footnote_ceiling_effect]: This tentative explanation is supported by the fact that the interaction remains intact when controlling for demographic differences between the areas.
-It is also supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
-This comparison shows a pattern of decreased marginal reduction.
-In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased by from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
-In the center, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
-With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa Bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
-
-[^footnote_mediation_elaboration]: This explanation is further supported by the survey data.
-The real symbols had a negative effect on the elaboration of these policies,  as measured by reaction time and memory test.
-The decrease in elaboration mediates the effect of symbols on trust.
-
-How can we reconcile the findings of this study with the proposed theory?
-One plausible explanation is that despite the relatively high involvement of Haifa Bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
-If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance.
-Indeed, Petty and Cacioppo have admitted that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p.
-206].
-
-The results of this study, if generalizable, have significant implications.
-They challenge the rationalistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
-Instead, they suggest that more often than not, citizens rely on brands and other symbolic elements in public communications, even with regard to policy issues that have direct implications on their own lives.
-Altogether, this study highlights the role played by government branding and other forms of symbolic communication in shaping citizens view of governments.
-It suggests that the boundaries of persuasion via symbols and branding are much wider than expected, based on previous social psychology and marketing studies.
-From the practical point of view of government organizations, this entails that organizations can overcome citizens distrust by investing in symbolic communications.
-Nonetheless, employing a broader perspective of democratic theory, these conclusions are disturbing insofar as they buttress the concern that government organizations will deliberately use symbolic communications to cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements, namely as "propaganda".
-For good or for ill, citizens are affected by the emotional connections and associations of symbols.
-
-Notwithstanding these conclusions, the limitations of this study should be acknowledged.
-The study focuses, empirically, on one specific case.
-Future studies may put these findings to further test by examining additional cases of public organizations and policy areas, as well as different forms of communications.
-Additionally, the comparison between the two areas is imperfect, insofar as the differences in personal relevance are confounded with differences in prior beliefs about the subject, which I cannot effectively control.
-A comparison between two groups that have similar prior beliefs would be more reliable.
-Finally, one can question the validity of the relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
-Still, the main results are robust to different model specifications, and operationalizations of personal relevance and message elaboration, which substantiate their validity.
-
-## Appendix A: Information manipulation
-
-**Air-pollution policy** (Reducing the air-pollution in the Haifa Bay)
-
-EPM is working to reduce the air-pollution in the Haifa Bay by:
-
-*Strong*
-
-* **Increasing the supervision of the factories in Haifa Bay**.
-In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways.
-The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the level of fines for polluters.
-
-* **Reduction of emissions from vehicles in Haifa Bay**.
-The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area.
-The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and the designation of a "clean-air district" from which polluting vehicles are banned.
-
-*Weak*
-
-* **Decreasing the supervision of factories in Haifa Bay**.
-The Ministry is preparing for a change in the method of supervision of the factories.
-The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the level of fines.
-The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.
-
-* **Raising citizens' awareness of the efforts to improve air quality**.
-In recent years, the Ministry has taken steps to reduce air pollution in Haifa Bay, which have been partially successful.
-The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents.
-To this end, the ministry has increased its investment in public relations and publicity on this subject.
-
-<br>
-
-**Recycling policy** (Reducing waste and increasing recycling)
-
-EPM is working to reduce the amount of waste and increase recycling through:
-
-*Strong*
-
-* **Packaging recycling - Increased supervision of manufacturers**.
-In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, under which manufacturers and importers are responsible for recycling their packaging materials.
-The Ministry will work to increase enforcement by virtue of this act, and will enforce it for additional manufacturers and importers.
-
-* **Reducing the usage of disposable bags**.
-In order to reduce the use of disposable plastic bags, the Ministry has enforced the Carrier Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the retail chains themselves.
-The Ministry is working to implement the act, and to encourage the transition to reusable grocery bags.
-
-*Weak*
-
-* **Packaging recycling - Decreased supervision of manufacturers**.
-The Ministry is preparing to a change in the way manufacturers, who are responsible for the recycling of product packaging, are supervised.
-The ministry will reduce the number of inspections, rely on manufacturers' own reporting regarding their compliance with the requirements of the act, and will reduce the level of fines.
-The change is coordinated with industry representatives, who are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
-
-* **Reducing the usage of disposable bags**.
-In recent years, the Ministry has taken steps to encourage the reduction of waste, which have been partially successful.
-The Ministry works to raise awareness of the actions taken and to highlight their success in order to improve its image among the public.
-To this end, the ministry has increased its investment in public relations and publicity in this subject.
-
-<br>
-
-## Appendix B: Symbols manipulation
-![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/symbols_manipulation.png)
-
-<font size="0.5">
-
-*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*
-
-</font>
-
-<br>
-
-# References
-
-<br>
+```
 
@@
 
-<br>
-`r figure.x=figure.x+1`**Figure `r figure.x`: Theoretical model**
-![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/theoretical_model_relevance.png)
-
-<br>
+<br><br>
 
@@
 
-<br>
+<br><br>
+
 `r figure.x=figure.x+1`**Figure `r figure.x`: Perceived personal relevance of policy issues across areas**
@@
 
-<br>
+<br><br>
 
@@
                              mod_air_1.5.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
+          notes = "*Notes*: In all regression tables, entries are nonstandardized OLS-regression coefficients.
 Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
@@
                              mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes = "",
           notes.append = FALSE)
@@
                              mod_relevance_1.4.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes = "",
           notes.append = FALSE)
@@
                              mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes = "",
           notes.append = FALSE)
@@
 <br>
-
-# References

### 2019-07-21 paper3_revision_text.Rmd
Add files via upload

--- 2019-07-19 paper3_relevance and symbols_revision_01.Rmd
@@
 ---
-title: "Does personal relevance attenuate the effect of government branding? Evidence from a survey experiment on air-pollution policy"
+title: "Does personal relevance attenuate citizens' persuasion by government branding? Evidence from a survey experiment on air-pollution policy"
 author: '**Saar Alon-Barkat**'
@@
 Public Administration scholarship has recently shown a growing interest in public sector branding, and its potency to influence citizens' perceptions and direct their behaviour [@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015].
-Behavioural studies established that symbolic, brand elements[^footnote_branding] entangled in government communications (e.g.
-brand names, logos, colors and figures) can have an emotional effect on citizens, which leads them to view public organizations and their policies and services more favourably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
+Recent behavioural studies established that symbolic, brand elements entangled in government communications (e.g.
+brand names, logos, colors and figures) can have a positive emotional effect on citizens, which leads them to view public organizations and their policies and services more favourably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
 This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade, in part due to the expension of ditigal communication platforms and the use of social media [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
 
-[^footnote_branding]: A symbol can be as *"any object used by human beings to index meanings that are not inherent in, nor discernible from, the object itself"* [@elder_1983, pp.
-28-29].
-Eshuis and Klijn [-@eshuis_2012, p.
-19] define brand as *a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it*.
-Brand elements, therefore, can be regarded as symbolic elements.
-
-The ability of government organizations to affect citizens via symbolic communications can be perceived favorably, insofar as it enables organizations to engage more effectively with citizens and overcome their unjustified negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
-Accordingly, it can mitigate citizens' distrust in government organizations and underevaluation of their performance.
-
-Nonetheless, the persuasion of citizens through symbols is also highly problematic.
-Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather then on uncontious emotive responses, produced by government agencies themselves.
-A yet more serious concern regards the potency of symbolic elements in government communications to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
-Congruently, government branding can yield a misalignment between citizens' positive perceptions and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
-Moreover, government agencies (or politicians controlling them) could strategically use such symbolic communication as a propaganda, seeking to manipulate public opinion and mitigate justified public criticism of agencies' failures.
-
-The abovementioned concerns of the negative implications of branding are the main motivation of this study.
-These concerns necessitate a better understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication.
-Understanding the limitations of symbolic persuasion would enable to asses more effectively the scope of the risk that these practices pose for democracy.
-
-For this purpose, in this study I explore whether the effect of symbols is restricted to policy issues that are not perceived by citizens as having a significant consequence for their personal lives, or rather, that citizens can be similarly persuaded by symbols even with regard to such personally relevant issues.
-This question is particularly important, since we tend to expect these affected groups to pay more attention to government actions that concern their interests, and to hold them to account for their consequences to a greater extent.
+The ability of government organizations to modify citizens' attitudes via such symbolic communications can be perceived favorably, insofar as it mitigates citizens' distrust in organizations and underevaluation of their performance.
+Accordingly, Symbolic communications, as opposed to mere factual information and substantive arguments, may enable organizations to overcome citizens' negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
+Nonetheless, this form of persuasion is also highly problematic.
+Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather then on uncontious emotive responses.
+A yet more serious concern regards the potency of symbolic communication to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
+Congruently, government branding can yield a misalignment between citizens' positive view and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
+Moreover, government agencies and/or politicians controlling them could use branding symbolic communication strategically as an instrument of propaganda, seeking to manipulate public opinion and mitigate justified public criticism of agencies' failures.
+
+The abovementioned concerns of the negative implications of branding for democracy are the main motivation of this study.
+These concerns necessitate a better theoretical understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, which would enable to asses more effectively the scope of the risk that these practices pose for democracy.
+In line with this motivation, this study focuses of an importnant potential limitation that regards the perceived personal relevance of the policy issue.
+I explore whether the effect of symbolic elements in communications is restricted to policy issues that are not perceived by citizens as having a significant consequence for their personal lives, or rather that citizens are similarly susceptible to persuasion via branding even with regard to such personally relevant issues.
+This factor is particularly important, since we tend to expect these affected groups to pay more attention to government actions that concern their interests, and to hold them to account for their consequences to a greater extent.
 That expectation can be supported, theoretically, by the social psychology theory Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
-The model postulates that people are more likely to focus on the substantive content of the communication and ignore "peripheral" symbolic elements, the more they perceive the policy issue at hand as having personal relevance for themselves.
+The model postulates that the more people perceive the communication as personally relevant, the more inclined they are to scrutinize its message, and accordingly the less likely they are to rely on peripheral, symbolic elements.
 
@@
 I present all participants a policy plan regarding the air-pollution in the Haifa Bay area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and content (logically persuasive versus unpersuasive policy plans).
-I examine the effects of these manipulations on participants' trust in the policy plan accross the two areas, and test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the different in the substantive content).
+I examine the effects of these manipulations on participants' trust in the policy plan accross the two areas, and test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the substantive differences).
 I further supplement this observational comparison between the areas with an experimental treatment for the perceived personal relevance of the policy, and with additional robustness tests.
@@
 
-# The effect of government branding on citizens' attitudes and its moderation by the perceived personal relevance of the communication.
-
-Symbolic elements that are strategically selected and designed to evoke positive emotions and associations, are included in almost every government communication with citizens, and most most prominently in government advertising and marketing [@eshuis_2012].
-These symbols can affect citizens' attitudes unconsciously through a psychological mechanism of evaluative conditioning, whereby the positive associations triggerred by the symbolic element are transferred to the public organization [@alonbarkat_2017; @dehouwer_2012].
-So for instance, when a public organization uses a popular celebrity endorser in a campaign, the positive connotations for the celebrity (e.g.
-physically attractive, funny, talented) can be extended to the organization, which would lead citizens to also view the organization more favorably.
+# Persuasion by symbols and its moderation by perceived personal relevance
+
+A brand can be defined as *"a symbolic construct that consists of a name, term, sign, symbol, or design, or combination of these, created deliberately to identify and phenomenon and differentiate it from similar phenomena by adding particular meaning to it"* [@eshuis_2012, p.
+19].
+Branding, therefore, can be considerred a form of symbolic communication.
+In practice, symbolic elements that are strategically selected and designed to evoke positive emotions and associations, can be found in almost every government communication with citizens.
+
+Symbolic elements entangled in communications can affect citizens' attitudes through a psychological mechanism of evaluative conditioning, whereby the positive associations triggerred by the symbols are unconsciously transferred to the public organization [@alonbarkat_2017; @dehouwer_2012].
+So for instance, when a public organization uses a celebrity endorser in a public campaign, the positive connotations for the celebrity (e.g.
+physically attractive, funny, talented) can be extended to the organization, which would lead citizens to also view the organization and its actions more favorably.
 This mechanism is considerred a primitive form of persuasion which requires very little cognitive effort, as opposed to persuasion resulted by thoughtful consideration of substantive arguments.
-Thus, the question of under which circumbstances are citizens' more/less susceptible to persuasion via branding, is linked to a more theoretical discussion in social psychology regarding the relations between different psychological processes of persuasion or modification of people's attitudes or judgements in response to communications or messages, and the determinants of these different processes.
+Thus, the question of under which circumbstances are citizens' more/less susceptible to persuasion via branding, is linked to a more general discussion in social psychology regarding the relations between different psychological processes of persuasion through communication, and the determinants and moderators of these different processes.
 
@@
 This type of processing involves thoughtful scrutiny of arguments in the communication that are central to the merits of the issue.
-People located at the high end are more likely to form their judgements on the matter based on the logical quality of the arguments, and are more likely to be persuaded by strong, logically persuasive arguments.
-As for those who are located at the low end of that continuum, also called "peripheral route", persuasion may occur mainly through processes that require little ammount of thinking, including evaluative conditioning, and the reliance on other heuristic cues like the message source [@james_2017a].
-When people are located between these two ends of the continuum, a mixture of these processes will operate and determine their persuasion, depending on their relative position.
-
-In any given situation, the position of people along that continuum would be determined, according to ELM, by their motivation and ability to scrutinize the message.
+People located at the high end tend are more likely to form their judgements on the matter based on the quality of the arguments.
+They are more likely to differentiate between strong and weak arguments, and would be persuaded mainly by strong, logically persuasive arguments.
+As for those who are located at the low end of that continuum, also called "peripheral route", persuasion may occur mainly through processes that require little ammount of thinking, such as evaluative conditioning.
+Another example for peripheral route processing is people's reliance on the message source as a heuristic cue [@james_2017a].
+When people are located between the two ends of the continuum, a mixture of these persuasion processes will operate.
+
+In any given situation, the position of people along that continuum (and accordingly the dominant type of processing) would be determined by their motivation and ability to scrutinize the message.
 The more motivated people are to elaborate on the message and the more capable they are of doing so, the more likely they are to focus on the substative arguments, and likewise the less susceptible they are to persuasion via peripheral route processes.
-
-ELM literature has pointed to a variety of factors that shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
+ELM literature has pointed to a variety of factors that may shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
 Perhaps the most studied factor in this regard is the perceived personal relevance of the communication (or "issue involvement"), namely the extent to which they perceive the issue at hand as having significant consequences for their own lives.
 That variable has been considered the most important determinant of motivation to scrutinize the message [@petty_2002; @petty_2011].[^footnote_elm_factors] It has been theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-Studies have established that individuals are more affected by peripheral cues and less affected by argument quality, the less they perceive the issue as personally relevant.
-For instance, in an experimental marketing study by @petty_1983, participants were asked to express their attitudes about a new product (disposable razor), after being exposed to a magazine ad, which contained either strong or weak arguments about
-the product, and involved either a non-famous endorser or a celebrity endorser (a symbolic peripheral cue).
-To manipulate the personal relevance of the product, subjects were either told that the product would soon be available in their local area (high relevance), or in other areas (low relevance).
-The results showed the effect of the celebrity endorser was higher among the low personal relevance group, whereas the effect of argument quality was significantly weaker for that group.
+Accordingly, experimental studies have showed that individuals are more affected by peripheral cues and less affected by argument quality, the less they perceive the issue as personally relevant.
+
+For instance, in a study by @petty_1983, participants were asked to express their attitudes about a new product (disposable razor), after being exposed to a magazine ad.
+The ad involved either a celebrity endorser or a non-famous endorser (a symbolic peripheral cue) and contained substantive information about the product that represent either strong or weak arguments about its quality.
+In addition, scholars manipulated the perceived personal relevance of the product by telling subjects either that the product would soon be available in their local area (high relevance), or that it would be available in other areas (low relevance).
+The results of the study indicated that the celebrity endorser had a positive effect on participants' attitudes about the product under the low personal relevance condition (estimated as roughly 0.7 SDs), but had no effect under the high personal relevance condition.
+Likewise, the effect of argument quality was greater for the high personal relevance group (1.95 SDs versus 0.54 SDs in the low personal relevance group).
 
@@
 
-Viewed against the above theoretical framework, symbolic elements can be regarded as peripheral cues, which can affect attitudes by a peripheral route process of evaluative conditioning.[##add footnote, in rare occations, symbolic elements could also serve as arguments, e.g.
-a slogan that both has a symbolic meaning and also contains an argument##].
-Hence, ELM postulates that citizens' are more likely to be affected by symbols the less motivated and capable they are to critically think about the message, which likely to be determined by the perceived personal relevnace of the policy issue.
-
-*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the more citizens perceive the policy issue in the communication as having personal relevance for themselves.*
-
-*H<sub>2</sub> - The logical quality of the substantive arguments in the communication is more likely to affect citizens' attitudes about government organizations and policies, the more citizens perceive the policy issue in the communication as having personal relevance for themselves.*
-
-<br>
-
-# The effect of substantive information in moderating effect of perceived personal relevance on argument quality.
-
-Most of the research on government communications and its effect on citizens' attitudes focuses on the substantive information in communications...
-the implicit assumption is that logically persuasive arguments would have a positive effect on citizens' attitudes.
-
-One limitation, that this literature highlights is biased processing.
-
-Yet, a second, understudies limitation, regards citizens' motivation to elaborate and process the substantive content of the communication.
-
-In light of ELM, substantive information in government public communications represent message arguments, which can be critically evaluated based on their logical quality (central route).
-Therefore, while greater perceived personal relevance is expected to attentuate the effect of symbols, it is likely to enhance the effect of substantive information.
-
-The two theoretical hypotheses are graphically displayed in `r figure.x=figure.x+1`**Figure `r figure.x`**.
-
-<br>
-
-[**Figure `r figure.x`** about here]
+Viewed against the above theoretical framework, symbolic elements in government communications can be regarded as peripheral cues, which can affect citizens' attitudes though a peripheral route process of evaluative conditioning.[^footnote_symbols_arguments] Hence, based on ELM, citizens judgements about public organizations are less likely to be affected by symbols (and more likely to be shaped by substantive arguments) the more motivated they are to critically think about the message.
+Their level of motivation is likely to be determined, to a great extent, by their perceived personal relevnace of the particular policy issue.
+
+[^footnote_symbols_arguments]: It should be noted that in certain cases, symbolic elements can be also regarded as arguments.
+For instance, slogans normally convey symbolic meaning, but also contain a substantive message.
+
+In sum, I derive from social psychology literature of persuasion through communication the following moderation hypotheses:
+
+*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the less citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+
+*H<sub>2</sub> - The argument quality of the information in communications is likely to have a lesser effect on citizens' attitudes about government organizations and policies, the less citizens perceive the policy issue in the communication as having personal relevance for themselves.*
 
@@
 The experiment focuses, empirically, on the case of the Israeli Environmental Protection Ministry (hereafter: EPM), and its policy for reducing the air pollution in the highly polluted Haifa Bay area.
-In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.
-
-It should be noted that the experiment was additionally designed to test a set of hypotheses regarding the interaction between symbols and information in communications.
+In the following section, I describe the empirical case, data collection, experimental design and operationalization of research variables.[^footnote_other_paper]
+
+[^footnote_other_paper]: The experiment was additionally designed to test a set of hypotheses regarding the interaction between symbols and information in communications.
 The methodological aspects which are relevant for examining the additional hypotheses are described in a separate publication.
-In the following sections, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
-An English translation of the full survey is available in section ## of the supplementary Appendix.
+In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
+A summary statistics and correlation of all variables, as well as the full survey are available in the supplementary Appendix, and replication materials are available in a github repository [url to be added upon publication].
 
@@
 While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019].
-Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings an media publications about the health consequences of the air-pollution in Haifa Bay.
+Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings and media publications about the health consequences of the air-pollution to Haifa Bay residents.
 In 2015, the Ministry of Health published statistical data indicating that Haifa Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
@@
 The air-pollution in the Haifa Bay offers a fortunate case for examining the moderating role of perceived personal relevance.
-The distinction between those who reside in the polluted area and those who do not entails a significant natural variation in that moderating variable.
+The distinction between those who reside in the polluted area and those who do not entails a natural variation in that moderating variable.
 Importantly, because this policy issue is intangible and scientifically complicated, the variation in personal relevance is not strongly confounded with personal knowledge about the issue, as is normally the case [@petty_1983].
@@
 The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##).
-I also searched relevant EPM documents and news websites for any reporting about high air-pollution levels in the three center cities, to ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies.
+To ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies, I searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.
 
@@
 For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
-The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements and variation in substantive information in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates.
+The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates.
 I henceforth refer to these two policy plans as "air-pollution" and "recycling".
@@
 
-To select and recruit residents of these selected cities, I was assisted by an Israeli internet research panel company *iPanel*.
+I was assisted by an Israeli internet research panel company *iPanel* for the selection and recruitment of residents of these selected cities.
 The survey experiment was conducted online through Qualtrics Survey Software.
@@
 A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
-Thereafter, I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and respondents under the age of 18 (n=`r filter_age`).
+Thereafter, I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to following criteria: multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and reported age under 18 (n=`r filter_age`).
 These filters are neither associated with the areas nor with the experimental conditions.
@@
 Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
-Then, they were asked to describe the most salient environmental issue in their area of residence.
+Then, they were asked to describe the most acute environmental issue in their area of residence.
 These treatment questions were designed to prime those residing in the Haifa Bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
 
-[^footnote_relevance_manipulation]: The first three treatment questions were also designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
+[^footnote_relevance_manipulation]: The first three treatment questions were also initially designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
 In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.
@@
 They were informed that these plans were obtained from EPM's annual work plan.
-Per each policy, subjects were randomly allocated to one of two conditions of substantive information (hereafter: information manipulation): strong policy (i.e.
+The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
+In the real symbols condition, the two policies are displayed with three symbolic elements, which have been used in EPM's public communications, and became widely recognized by the public.
+The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
+The second element is the green color, which is strongly associated with taking care of the environment.
+The third element is an image of a celebrity comedian from an advertising campaign of the EPM.
+The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
+The recycling policy (in the real symbols condition) was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum.
+In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images.
+Finally, in the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people.
+The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic brand elements (i.e.
+the symbolic effect) from a possible effect of their aesthetic design.
+Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy.
+The symbols conditions are displayed in **Appendix B**.
+Further details about the real and fake symbols are found in section ## of the supplementary appendix.
+
+In addition, I also included a manipulation of the argument quality of the information in the communication about the policy plan (hereafter: information manipulation).
+Per each policy, subjects were randomly allocated to one of two conditions of information: strong policy (i.e.
 logically persuasive policy plan) or weak policy (i.e.
@@
 For instance, a subject who first received a strong air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
-The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.
-The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
-
-The participants were also randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the real symbols condition, the two policies (as explained, one weak and one strong) are displayed with three symbolic elements, which have been used in EPM's public communications, and became widely recognized by the public.
-The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
-The second element is the green color, which is strongly associated with taking care of the environment.
-The third element is an image of a celebrity comedian from an advertising campaign of the EPM.
-The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
-The recycling policy in the real symbols condition was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum.
-In the control no-symbols condition, the two policies are displayed in a minimal black and white design, and without the logo and the celebrities’ images.
-In the control fake-symbols condition, the EPM logo is replaced by a fake logo, the green color is replaced with blue, and the images of celebrities from the campaigns are replaced with edited images of unfamiliar people.
-The purpose of the fake-logo condition was to distinguish the effect of the symbolic meaning of the EPM's graphic identifiers (i.e.
-the symbolic effect) from a possible effect of their aesthetic design.
-Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy.
-The symbols conditions are displayed in **Appendix B**.
-Further details about the real and fake symbols are found in section ## of the supplementary appendix.
+The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
+
+[^footnote_reliability_information_manipulation]: A possible concern about that design is that participants would question the reliability of the weak policy.
+I assess that concern in the supplementary appendix (section ##).
 
@@
 
-# Figures and tables
-
-```{r}
-#Figures and tables
-table.x=0
-figure.x=0
-```
-
-<br>
-`r figure.x=figure.x+1`**Figure `r figure.x`: Theoretical model**
-![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/theoretical_model_relevance.png)
-
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Balancing of experimental groups across areas**
-
-<br>
-
-```{r}
-
-#labels of vars
-vars.lab = c(
-         "Gender (Woman=1)",
-         "Age",
-         "Trust in government ministries",
-         "Political Ideology (10 = extreme left)",
-         "Education",
-         "Income (5=high)",
-         "Parents",
-         "Parents of young children (under 12)",
-         "Interest in environmental issues",
-         "Air-pollution policy",
-         "Recycling policy"
-)
-
-vars <- c(var1 = "GENDER", 
-          var2 ="AGE",
-          var3 ="GOV_TRUST",
-          var4 = "IDEOLOGY", 
-          var5 ="EDUCATION",
-          var6 ="INCOME",
-          var7 = "CHILDREN", 
-          var8 ="CHILDREN_young",
-          var9 ="ENVIRONMENT_INTEREST",
-          var91 ="TRUST_air_INDEX",
-          var92 ="TRUST_waste_INDEX")
-
-t1.all <- SVIVA2_01 %>% 
-  select(AREA_center,
-         !!vars) %>% 
-  gather(key = variable, value = value,-AREA_center) %>% 
-  group_by(AREA_center,variable) %>% 
-  summarise(mean.var = mean(value,na.rm = T) %>% round(3),
-            sd.var = sd(value,na.rm = T) %>% round(3)) %>% 
-  mutate(all = str_c(mean.var, " (",sd.var,")")) %>% 
-  as.data.frame() %>% 
-  mutate(variable = rep(vars,2)) %>% 
-  select(-mean.var,-sd.var)
-
-t1.symbol <- SVIVA2_01 %>%
-  mutate(symbols.t = Recode(SYMBOL,"0='no';1='fake';2='real'")) %>% 
-  select(AREA_center,
-         symbols.t,
-         !!vars) %>%
-  gather(key = variable, value = value, -symbols.t,-AREA_center) %>% 
-  group_by(symbols.t, variable,AREA_center) %>% 
-  summarise(value = list(value)) %>% 
-  spread(symbols.t, value) %>% 
-  group_by(AREA_center,variable) %>%
-
-  mutate(mean_no = round(mean(unlist(no),na.rm = T),3),
-         mean_fake = round(mean(unlist(fake),na.rm = T),3),
-         mean_real = round(mean(unlist(real),na.rm = T),3),
-         sd_no = round(sd(unlist(no),na.rm = T),3),
-         sd_fake = round(sd(unlist(fake),na.rm = T),3),
-         sd_real = round(sd(unlist(real),na.rm = T),3)) %>%
-  mutate(no = str_c(mean_no, " (",sd_no,")"),
-         fake = str_c(mean_fake, " (",sd_fake,")"),
-         real = str_c(mean_real, " (",sd_real,")")) %>% 
-  select(AREA_center,
-         variable,
-         no,
-         fake,
-         real) %>% 
-  as.data.frame() %>% 
-  arrange(AREA_center,variable)
-
-t2.symbol <- SVIVA2_01 %>% 
-  select(AREA_center,
-         SYMBOL,
-         !!vars) %>% 
-  gather(key = variable, value = value, -SYMBOL,-AREA_center) %>% 
-  group_by(variable,AREA_center) %>% 
-  do(tidy(aov(value~SYMBOL, data=.))) %>% 
-  as.data.frame() %>% 
-  filter(term=="SYMBOL") %>% 
-  select(AREA_center,
-         variable,
-         statistic) %>% 
-  mutate_at(c("statistic"), funs(round(.,3)))%>% 
-  arrange(AREA_center,variable)
-
-t3.symbol <- cbind(t1.symbol,
-                   t2.symbol %>% select(statistic))
-
-t1.info <- SVIVA2_01 %>% 
-  mutate(info.t = ifelse(INFORMATION_air==1,"air_strong","air_weak")) %>% 
-  select(AREA_center,
-         info.t,
-         !!vars) %>%
-  gather(key = variable, value = value, -info.t, -AREA_center) %>% 
-  group_by(info.t, variable,AREA_center) %>% 
-  summarise(value = list(value)) %>% 
-  spread(info.t, value) %>% 
-  group_by(AREA_center,variable) %>%
-
-  mutate(mean_strong = round(mean(unlist(air_strong),na.rm = T),3),
-         mean_weak = round(mean(unlist(air_weak),na.rm = T),3),
-         sd_strong = round(sd(unlist(air_strong),na.rm = T),3),
-         sd_weak = round(sd(unlist(air_weak),na.rm = T),3),
-         t_value.info = round(t.test(unlist(air_strong), unlist(air_weak))$statistic,3)) %>% 
-  mutate(air_strong = str_c(mean_strong, " (",sd_strong,")"),
-         air_weak = str_c(mean_weak, " (",sd_weak,")")) %>% 
-  select(AREA_center,
-         variable,
-         air_strong,
-         air_weak,
-         t_value.info) %>% 
-  as.data.frame() %>% 
-  arrange(AREA_center,variable)
-
-t1.relevance <- SVIVA2_01 %>%
-  mutate(relevance.t = ifelse(RELEVANCE_exp==1,"treatment","control")) %>% 
-  select(AREA_center,
-         relevance.t,
-         !!vars) %>%
-  select(-var9) %>%
-  mutate(var9 = SVIVA2_01$SYMBOL_bi) %>% 
-  gather(key = variable, value = value, -relevance.t, -AREA_center) %>% 
-  group_by(relevance.t, variable,AREA_center) %>% 
-  summarise(value = list(value)) %>% 
-  spread(relevance.t, value) %>% 
-  group_by(AREA_center,variable) %>%
-
-  mutate(mean_treatment = round(mean(unlist(treatment),na.rm = T),3),
-         mean_control = round(mean(unlist(control),na.rm = T),3),
-         sd_treatment = round(sd(unlist(treatment),na.rm = T),3),
-         sd_control = round(sd(unlist(control),na.rm = T),3),
-         t_value.relevance = round(t.test(unlist(treatment), unlist(control))$statistic,3)) %>% 
-  mutate(treatment = str_c(mean_treatment, " (",sd_treatment,")"),
-         control = str_c(mean_control, " (",sd_control,")")) %>% 
-  select(AREA_center,
-         variable,
-         treatment,
-         control,
-         t_value.relevance) %>% 
-  as.data.frame() %>% 
-  arrange(AREA_center,variable)
-
-t1.relevance[t1.relevance$variable=="var9",-c(1,2)]="-"
-
-t3.haifa <- t1.all %>% 
-  filter(AREA_center==0) %>% 
-  select(-AREA_center) %>% 
-  cbind(t3.symbol  %>% 
-          filter(AREA_center==0) %>% 
-          select(-AREA_center,-variable)) %>% 
-  cbind(t1.info %>% 
-          filter(AREA_center==0) %>% 
-          select(-AREA_center,-variable)) %>%
-  cbind(t1.relevance %>% 
-          filter(AREA_center==0) %>% 
-          select(-AREA_center,-variable)) %>% 
-  mutate(variable = vars.lab)
-
-t3.center <- t1.all %>% 
-  filter(AREA_center==1) %>% 
-  select(-AREA_center) %>% 
-  cbind(t3.symbol  %>% 
-          filter(AREA_center==1) %>% 
-          select(-AREA_center,-variable)) %>% 
-  cbind(t1.info %>% 
-          filter(AREA_center==1) %>% 
-          select(-AREA_center,-variable)) %>%
-  cbind(t1.relevance %>% 
-          filter(AREA_center==1) %>% 
-          select(-AREA_center,-variable)) %>%  
-  mutate(variable = vars.lab)
-
-```
-
-**Haifa Bay**
-```{r}
-
-t3.haifa %>%
-  filter(str_detect(variable,"policy")==F) %>%
-  kable(col.names = c("",
-                    str_c("All sample (n=",SVIVA2_01_haifa %>% nrow(),")"),
-                    str_c("No symbols (n=",SVIVA2_01_haifa %>% filter(SYMBOL==0) %>%  nrow(),")"),
-                    str_c("Fake symbols (n=",SVIVA2_01_haifa %>% filter(SYMBOL==1) %>%  nrow(),")"),
-                    str_c("Real symbols (n=",SVIVA2_01_haifa %>% filter(SYMBOL==2) %>%  nrow(),")"),
-                    "f-test",
-                    str_c("Strong Air-pollution (Weak recycling) (n=",SVIVA2_01_haifa %>% filter(INFORMATION_air==1) %>% nrow(),")"),
-                    str_c("Weak air-pollution (Strong recycling) (n=",SVIVA2_01_haifa %>% filter(INFORMATION_air==0) %>% nrow(),")"),
-                     "t-test",
-                    str_c("Treatment (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
-                    str_c("Control (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
-                    "t-test"))%>%
-  kable_styling(bootstrap_options = c("condensed"),
-                full_width = F,
-                position = "left",
-                font_size = 9) %>%
-  add_header_above(c(" " = 2, 
-                     "Symbols groups" = 4,  
-                     "Information groups" = 3, 
-                     "Relevance groups" = 3))
-```
-<font size="0.5">
-
-*Notes*: 
-Table entries are means with SDs in parentheses.
-
-</font>
-
-<br>
-**Center**
-```{r}
-
-t3.center %>%
-    filter(str_detect(variable,"policy")==F) %>%
-    kable(col.names = c("",
-                    str_c("All sample (n=",SVIVA2_01_center %>% nrow(),")"),
-                    str_c("No symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==0) %>%  nrow(),")"),
-                    str_c("Fake symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==1) %>%  nrow(),")"),
-                    str_c("Real symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==2) %>%  nrow(),")"),
-                    "f-test",
-                    str_c("Strong Air-pollution (Weak recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==1) %>% nrow(),")"),
-                    str_c("Weak air-pollution (Strong recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==0) %>% nrow(),")"),
-                     "t-test",
-                    str_c("Treatment (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
-                    str_c("Control (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
-                    "t-test"))%>%
-  kable_styling(bootstrap_options = c("condensed"),
-                full_width = F,
-                position = "left",
-                font_size = 9) %>%
-  add_header_above(c(" " = 2, 
-                     "Symbols groups" = 4,  
-                     "Information groups" = 3, 
-                     "Relevance groups" = 3))
-```
-<font size="0.5">
-
-*Notes*: 
-Table entries are means with SDs in parentheses.
-
-</font>
-
-<br>
-`r figure.x=figure.x+1`**Figure `r figure.x`: Perceived personal relevance of policy issues across areas**
-
-```{r, fig.width=8,fig.height=4}
-SVIVA2_01 %>%
-  select(AREA_names,
-         RELEVANCE_air_obs,
-         RELEVANCE_waste_obs) %>% 
-  gather(key = policy, value = relevance, -AREA_names) %>%
-  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
-ggplot(aes(AREA_names,relevance))+ 
-  theme_tufte()+
-  geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.96),
-               width=0.05,size=0.5) + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6)+
-  facet_grid(~policy)+
-  xlab("")+
-  scale_y_continuous(name = "Perceived personal relevance",limits=c(1,7),breaks = seq(1,7,by=1))
-```
-<font size="0.5">
-
-*Note*: Error bars represent 95% confidence intervals.
-
-</font>
-
-<br>
-
-`r figure.x=figure.x+1`**Figure `r figure.x`: The distribution of Trust in air-pollution across the different conditions of symbols and information**
-
-```{r, fig.width=8, fig.height=4}
-p1 <- SVIVA2_01_comb %>%
-ggplot(aes(SYMBOL_n,TRUST_air_INDEX))+ 
-  theme_tufte()+
-  geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.96),
-               width=0.05,size=0.5) + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6)+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
-  scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
-  ggtitle("Symbols")
-
-p2 <- SVIVA2_01_comb %>%
-ggplot(aes(factor(INFORMATION_weak),TRUST_air_INDEX))+ 
-  theme_tufte()+
-  geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.96),
-               width=0.05,size=0.5) + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6)+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
-  scale_x_discrete(name = "",labels = c("Strong policy","Weak policy"))+
-  scale_y_continuous(name = "",limits=c(1,7),breaks = seq(1,7,by=1))+
-  ggtitle("Information")
-
-p3 <- SVIVA2_01_comb %>%
-ggplot(aes(factor(AREA_center),TRUST_air_INDEX))+ 
-  theme_tufte()+
-  geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.96),
-               width=0.05,size=0.5) + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6)+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
-  scale_x_discrete(name = "",labels = c("Haifa Bay","Center"))+
-  scale_y_continuous(name = "",limits=c(1,7),breaks = seq(1,7,by=1))+
-  ggtitle("Areas")
-
-ggarrange(p1,p2,p3,
-          ncol = 3,nrow = 1,
-          widths = c(3,2,2))
-```
-<font size="0.5">
-
-*Note*: Error bars represent 95% confidence intervals.
-
-</font>
-
-<br>
-
-`r figure.x=figure.x+1`**Figure `r figure.x`: The effect of symbolic elements on trust across areas**
-
-```{r, fig.width=8}
-p1 <- SVIVA2_01_comb %>%
-  filter(policy=="TRUST_air_INDEX") %>% 
-ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
-  theme_tufte()+
-  #geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.96),
-               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
-  scale_shape_manual(guide=F, values=c(19,1))+
-  scale_linetype_manual(guide=F, values=c(1,4))+
-  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in air-pollution policy",breaks = seq(1,7,by=0.5))+
-  ggtitle("Symbols")
-
-p2 <- SVIVA2_01_comb %>%
-  filter(policy=="TRUST_air_INDEX") %>% 
-ggplot(aes(factor(INFORMATION_weak),trust,shape=factor(AREA_names)))+ 
-  theme_tufte()+
-  #geom_boxplot(width=0.25,color="gray70")+
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
-               fun.args = list(mult = 1.96),
-               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
-  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
-  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
-  scale_shape_manual(name="Area",values=c(19,1))+
-  scale_linetype_manual(name="Area",values=c(1,4))+
-  scale_x_discrete(name="",labels=c("Strong policy","Weak policy"))+
-  scale_y_continuous(name = "",breaks = seq(1,7,by=0.5))+
-  ggtitle("Information")
-
-ggarrange(p1,p2,
-          ncol = 2,nrow = 1,
-          widths = c(4,5))
-```
-
-<font size="0.5">
-
-*Note*: Error bars represent 95% confidence intervals.
-
-</font>
-
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – Trust in Air-pollution policy.**
-
-```{r,results="asis"}
-control.vars <- c("GENDER",
-                  "AGE",
-                  "GOV_TRUST",
-                   "IDEOLOGY",
-                   "EDUCATION",
-                   "INCOME",
-                   "CHILDREN",
-                   "CHILDREN_young")
-
-stargazer(mod_air_1.1,mod_air_null,
-          mod_air_1.2,mod_air_null,
-          mod_air_1.3, mod_air_null,
-          mod_air_1.4, mod_air_null,
-          mod_air_1.5, mod_air_null,
-          type = "html",
-          se  = list(mod_air_1.1.robust_se,NULL,
-                     mod_air_1.2.robust_se,NULL,
-                     mod_air_1.3.robust_se,NULL,
-                     mod_air_1.4.robust_se,NULL,
-                     mod_air_1.5.robust_se,NULL),
-          style = "apsr",
-          report = "vcsp",
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          column.labels   = str_c("(1.",1:5,")"),
-          column.separate = c(2,2,2,2,2),
-          dep.var.labels="Trust in air-pollution policy",
-          omit = control.vars,
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Area (0=Haifa Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information"),
-          p.auto = F,
-          add.lines = list(
-                           c("Controls","No","","No","","No","","Yes","","No",""),
-                           c("F Statistic", 
-                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.4.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.5.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – trust in recycling policy.**
-
-```{r,results="asis"}
-control.vars <- c("GENDER",
-                  "AGE",
-                  "GOV_TRUST",
-                   "IDEOLOGY",
-                   "EDUCATION",
-                   "INCOME",
-                   "CHILDREN_young")
-
-stargazer(mod_waste_1.1,mod_waste_null,
-          mod_waste_1.2,mod_waste_null,
-          mod_waste_1.3, mod_waste_null,
-          mod_waste_1.4, mod_waste_null,
-          mod_waste_1.5, mod_waste_null,
-          type = "html",
-          se  = list(mod_waste_1.1.robust_se,NULL,
-                     mod_waste_1.2.robust_se,NULL,
-                     mod_waste_1.3.robust_se,NULL,
-                     mod_waste_1.4.robust_se,NULL,
-                     mod_waste_1.5.robust_se,NULL),
-          style = "apsr",
-          report = "vcsp",
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          column.labels   = str_c("(2.",1:5,")"),
-          column.separate = c(2,2,2,2,2),
-          dep.var.labels="Trust in recycling policy",
-          omit = control.vars,
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Area (0=Haifa Bay; 1=center)",
-                             "Area x Real symbols",
-                             "Area x Fake symbols",
-                             "Area x Weak Information"),
-          p.auto = F,
-          add.lines = list(
-                           c("Controls","No","","No","","No","","Yes","","No",""),
-                           c("F Statistic", 
-                             mod_waste_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-
-```
-
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – experimental manipulation of perceived personal relevance.**
-
-```{r,results="asis"}
-control.vars <- c("GENDER",
-                  "AGE",
-                  "GOV_TRUST",
-                   "IDEOLOGY",
-                   "EDUCATION",
-                   "INCOME",
-                   "CHILDREN_young")
-
-stargazer(mod_relevance_1.1,mod_relevance_null,
-          mod_relevance_1.2,mod_relevance_null,
-          mod_relevance_1.3, mod_relevance_null,
-          mod_relevance_1.4, mod_relevance_null,
-          type = "html",
-          se  = list(mod_relevance_1.1.robust_se,NULL,
-                     mod_relevance_1.2.robust_se,NULL,
-                     mod_relevance_1.3.robust_se,NULL,
-                     mod_relevance_1.4.robust_se,NULL),
-          style = "apsr",
-          report = "vcsp",
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          column.labels   = str_c("(3.",1:4,")"),
-          column.separate = c(2,2,2),
-          dep.var.labels="Trust in air-pollution policy",
-          omit = control.vars,
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Relevance treatment",
-                             "Relevance treatment x Real symbols",
-                             "Relevance treatment x Fake symbols",
-                             "Relevance treatment x Weak Information"),
-          p.auto = F,
-          add.lines = list(
-                           c("Controls","No","","No","","Yes","","No",""),
-                           c("F Statistic", 
-                             mod_relevance_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-```
-
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area and young children.**
-
-```{r,results="asis"}
-control.vars <- c("GENDER",
-                  "AGE",
-                  "GOV_TRUST",
-                   "IDEOLOGY",
-                   "EDUCATION",
-                   "INCOME")
-
-stargazer(mod_closedness_1.1,mod_closedness_null,
-          mod_closedness_1.2,mod_closedness_null,
-          mod_closedness_1.3, mod_closedness_null,
-          type = "html",
-          se  = list(mod_closedness_1.1.robust_se,NULL,
-                     mod_closedness_1.2.robust_se,NULL,
-                     mod_closedness_1.3.robust_se,NULL),
-          style = "apsr",
-          report = "vcsp",
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          column.labels   = str_c("(4.",1:4,")"),
-          column.separate = c(2,2,2),
-          dep.var.labels="Trust in air-pollution policy",
-          omit = control.vars,
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Proximity to industrial area",
-                             "Young children",
-                             "Proximity x Real symbols",
-                             "Proximity x Fake symbols",
-                             "Proximity x Weak Information",
-                             "Young children x Real symbols",
-                             "Young children x Fake symbols",
-                             "Young children x Weak Information"),          
-          p.auto = F,
-          add.lines = list(
-                           c("Controls","Yes","","Yes","","Yes",""),
-                           c("F Statistic", 
-                             mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
-          notes.append = FALSE)
-```
-
-<br>
-
 # References

### 2019-07-22 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 "funny", "comedian", "Funny advertisement", "hahaha").
+
+<br>
+
+## Information manipulation
+
+This section aims to assess the concernt that participants did not accept the authenticity of the weak, fictional policy plan, and did not find it reliable, and as a results lost trust in the rest of the survey.
+To assess that risk, I took advantage of the fact that the order in which the strong and weak policies were presented was randomized.
+Accordingly, half of the participants saw a weak plan first, and thereafter a strong plan, and for the other half it was the opposite.
+Hence, I examined whether the the strong policy was evaluated differently when it was presented first (which means that participants at that point did not sea weak policy yet and did not question the reliability of the survey), then when it was presented second (after they already saw a fictional policy).
+This comparison, accross the two policies, is graphically presented in the following plot.
+It shows that the differences between the means and distributions of the first and the second policy are relatively small and insignificant.
+The small increase between the first and second round may be explained be the fact that participants used the first (weak) policy as a benchmark, and therefore compared the second policy with the first one.
+Altogether, these test tend to indicate that participants' exposure to the fictional weak policy did not have a strong influence on their answers to the subsequent questions.
+
+```{r}
+
+SVIVA2_01_comb %>%
+  filter(INFORMATION_weak==0) %>% 
+ggplot(aes(factor(policy),trust,shape=factor(ORDER)))+ 
+  theme_tufte()+
+  geom_boxplot(width=0.25,color="gray70")+
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               fun.args = list(mult = 1.96),
+               width=0.1,size=0.5,position=position_dodge(0.25),color="gray70") + 
+  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.25))+
+  scale_shape_manual(name="Order",values=c(19,1), labels = c("First","Second"))+
+  scale_x_discrete(name="Policy",labels=c("Air-pollution","Recycling"))+
+  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.5))#+
+  facet_grid(policy ~ .)
+  ggtitle("Information")
+```
 

### 2019-07-22 paper3_revision_text.Rmd
Add files via upload

@@
 The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
-In the real symbols condition, the two policies are displayed with three symbolic elements, which have been used in EPM's public communications, and became widely recognized by the public.
+In the real symbols condition, the two policies are displayed with three symbolic brand elements, which have been used in EPM's public communications, and became widely recognized by the public.
 The first symbolic element is the unique brand logo of the EPM, which consists a pair of green and orange leaves that resemble two hands, designed to symbolize peace and harmony with the environment.
@@
 The last sections included a set of demographic questions including questions about their place of residence and work, and manipulation checks for participants' familiarity with the real symbols.
-At the end of the survey, the participants were debriefed about the manipulations, and the possible deception.
+At the end of the survey, the participants were briefed about the manipulations, and the possible deception.
 
@@
 Additionally, within the Haifa Bay sample, I examine the two-way interactions between the relevance manipulation and the symbols and information manipulations.
-I conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the relevant two-way interactions.
+
+I further conducted power estimations for the main effects of the symbols and information manipulations, their conditional effects within each area and the aforementioned interactions.
 I conducted these estimations after the data collection and analyses, based on the analytical sample size.
-The estimated detectable interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
+The estimated detectable (power=0.8) interaction coefficient between areas and the real symbols treatment is 0.27 SDs, and between areas and weak information manipulation is 0.23 SDs.
 As for the interactions with the relevance manipulation (among Haifa Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
@@
 [^footnote_symbols_manipulation_check]: Manipulation checks for the symbols confirm that the subjects in both areas are fairly familiar with the EPM symbols, and these symbols evoke positive feelings.
-##add check reliability of information.
-##
+Analyses for the information manipulation largely confirm that participants perceived both conditions as reliable.
 
@@
 
-`r table.x=table.x+1`**Tables `r table.x`** compares between the different experimental conditions, within each of the two areas, on demographic variables and pre-manipulation covariates.
-These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The samples of the two areas are fairly balanced with regard to gender, overall trust in national level government ministries and reported interest in environmental policy issues.
-Yet, Haifa Bay respondents are somewhat older, more educated, and reported having more left-wing ideology.
+I begin by examining the random assignment to the different experimental conditions.
+`r table.x=table.x+1`**Tables `r table.x`** compares between the different conditions, within each of the two areas, on demographic variables and pre-manipulation covariates.
+These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The table furter suggests that the samples of Haifa Bay and Center residents are fairly balanced with regard to gender, trust in national-level government ministries and interest in environmental issues.
+Yet, Haifa Bay respondents are somewhat older, more educated, and have more left-wing ideology.
 
 [^footnote_balancing_groups_exceptions]: Within the center respondents, there were statistically significant differences between the symbols groups -- regarding education levels and the percentage of parents; and between the information groups -- regarding the percentage of parents for young children.
-To adjust for small finite-sample imbalances, as well as for differences between the areas, I control for covariates.
+To adjust for small finite-sample imbalances, as well as for differences between the areas, I also control for covariates in the regression analyses.
 
@@
 
-I now turn to exploring respondents trust in the *air-pollution policy*.
-This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), whereby more subjects reported very low levels of trust, than very high levels of trust in than policy.
+I now turn to exploring the main outcome variable of interest -- respondents trust in the *air-pollution policy*.
+This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), which entails that more subjects reported very low levels of trust, than very high levels of trust in than policy.
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas.
@@
 The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score.
-Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a very low score of 2 or less, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group.
+Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a score of 2 or less which indicates very low level of trust, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group.
 As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
@@
 Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-`r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than the middle point 4 (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
+Descriptively, `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than 4, the scale's middle point (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
 This indicates that the majority of the sampled Haifa Bay residents tend to have prior negative attitudes towards EPM's actions regarding the air-pollution in their area.
@@
 To reiterate, based on my theoretical hypotheses, I expect that subjects living in the Haifa Bay, who perceive this issue as personally relevant, would be less affected by the symbolic elements, compared with those living in the Center (H<sub>1</sub>).
-Likewise, I expect Haifa Bay respondents to be more affected by the differences in the content (strong versus weak information), compared with center respondents (H<sub>2</sub>).
-`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (presented in the left panel), the results show that the symbols had a greater effect on those living in the polluted Haifa Bay area.
+Likewise, I expect Haifa Bay respondents to be more affected by the differences in the argument quality of the communication (strong versus weak information), compared with center respondents (H<sub>2</sub>).
+`r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (displayed in the left panel), the results show that the symbols had a greater positive effect on those living in the polluted Haifa Bay area.
 Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group.
@@
 
-[^footnote_raw_means]: In addition, raw means and SDs of outcome variables across the two areas are reported in section XX of the supplementary appendix.
+[^footnote_raw_means]: Means and SDs of outcome variables across the two areas and the experimental conditions are reported in section XX of the supplementary appendix.
 
@@
 
-These results are at odds with the two theoretical hypotheses.
-They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication, and also to a lesser extent, by the unfamiliar graphical elements included in the fake symbols condition.
-Additionally, these analyses do not provide evidence that the more engaged Haifa Bay were more likely than others to scrutinize the content of the communication, and differentiate between strong and weak arguments.
+These results are at odds with the initial theoretical expectations.
+They suggest that that those residing in the polluted area were equally, and perhaps even more, likely to be influenced by symbolic elements in the communication (and to a lesser extent, by the unfamiliar graphical elements in the fake symbols).
+Similarly, these analyses do not provide evidence that Haifa Bay residents were more likely than others to scrutinize the communication, and differentiate between strong and weak arguments.
 
@@
 
-[^footnote_heteroskedacity]: Breusch-Pagan test confirms that the null hypotheses that the variance of the residuals is constant.
-For Model 1.3, Breusch-Pagan test =  `r bptest(mod_air_1.3)[["statistic"]][["BP"]] %>% round(3)`, *p*=`r bptest(mod_air_1.3)[["p.value"]][["BP"]] %>% round(3)`.
+[^footnote_heteroskedacity]: Breusch-Pagan test confirms the presence of heteroskedasticity (for Model 1.3, Breusch-Pagan test =  `r bptest(mod_air_1.3)[["statistic"]][["BP"]] %>% round(3)`, *p*=`r bptest(mod_air_1.3)[["p.value"]][["BP"]] %>% round(3)`).
 Robust standard errors are estimated using R sandwich package with estimation type "HC1".
@@
 Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
-Accordingly, they do not support the research hypotheses.
-Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence I cannot rule out a concern of endogeneity.
-Accordingly, the null findings regarding the interactions between the areas and the manipulations can be a result by other, unobserved differences between the two populations.
-As explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
+Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence a concern of endogeneity cannot be entirely ruled.
+Accordingly, the null findings regarding the interactions between the areas and the manipulations can be resulted by other, unobserved differences between the two populations.
+Yet, as explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
 I now discuss the results of these two tests.
@@
 Notice that Haifa Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
-The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbolic elements, and the respondents from the two areas responded similarly to the differences in the information.
-The fact that similar patterns are observed across the these policies further weakens the initial assumption regarding the moderating role of personal relevance.
+The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbols, and the two areas responded similarly to the differences in the information.
+The fact that similar patterns are observed across the these policies further weakens the hypotheses regarding the moderating role of personal relevance.
 It also rules out a possible argument that greater relevance enhances (rather then reduces) the effect of symbols.
-If this was the case, then there should have been no interaction between symbols and the areas for the recycling policy.
+If this was the case, then we should not have found a similar interaction in relation to the recycling policy.
 
@@
 In all these models, the coefficient of the relevance treatment is negative but far from significance.
-The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the averaged differences between those who saw the symbols and those who did not were slightly smaller.
+The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the incerase in trust due to the appearance of the symbols and those who did not were slightly smaller.
 However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group) and far from significance.
-The interactions between the relevance treatment and weak information manipulations are positive but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
+The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
 
@@
 
-Two limitations about these analyses should be acknowledged.
-First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in priming those subjects.
+Two limitations about these latter analyses should be acknowledged.
+First, since the treatment manipulation did not affect participants' self-reporting of the personal relevance, there is no certainty that the manipulation actually succeeded in modifying the perceptions of those subjects.
 Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa Bay subjects.
-Still, even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
-Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] This indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area are positively affected, at least to some degree, by familiar symbols.
+Still, we can assess that even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
+Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] Overall, this indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area were positively affected, at least to some degree, by familiar symbols of the ministry.
 
@@
 
-Public communications have been proposed as a remedy for citizens’ low trust in government, and for their underestimation of public-service performance.
-Congruently, governments' investments in public communications, and specifically in branding and advertising, has increased over the past generation in many economically-developed democratic countries.
-This study contributes to the growing Public-Administration research on citizens' responses to government public communications, and specifically to symbolic elements entangled in these communications.
-I explored the expectation, derived from social psychology, that citizens are less affected by symbols and more likely to scrutinize the content of the communication the more they perceive it as relevant to their own lives.
-I put these hypotheses to rigorous empirical testing, using a randomized survey experiment focusing on the Israeli Environmental Protection Ministry.
-I exploited the natural variation in citizens' perceptions of the personal relevance of the ministry’s policy plan regarding air pollution in a specific area.
-In addition to utilizing these natural differences, I also manipulated the personal relevance of the policy plans.
-To the best of my knowledge, this is the first study to assess the moderating role of perceived personal relevance on citizens' responses to government symbolic communications or branding.
+This study contributes to the growing Public-administration research on government branding and its potency to influence citizens' perceptions, and their inclination to trust organizations' policy plans.
+I explored whether persuasion through branding and symbolic communication can also ocure in policy matters that have significant, clear implications for citizens' well-being.
+I examined the hypothesis, derived from social psychology theory, that persuasion via symbols is attenuated the more citizens perceive the communication as personally relevant.
+I put this hypothesis to rigorous empirical testing using a randomized survey experiment focused on air-pollution policy, thus exploiting a natural variation in the perceived personal relevance between citizens residing in a polluted area and outside it.
+In addition to utilizing these natural differences, I also experimentally manipulated the personal relevance of the policy.
+To the best of my knowledge, this is the first study to explore the moderating role of perceived personal relevance on citizens' responses to government symbolic communications or branding.
 
-Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that high levels of perceived personal relevance attenuate the effect of symbols on citizens' trust.
-Subjects residing in the polluted Haifa Bay indeed reported that they perceive the policy plan for reducing air-pollution in that area as highly relevant for their lives, compared to those who reside in the center.
-However, despite these significant differences, Haifa Bay subjects did not pay more attention to the logical quality of the policy plan, and they were equally affected by the symbols in the communication.
-If anything, the results suggest that the symbols had a greater effect on Haifa Bay subjects.
-Furthermore, priming subjects to think about the personal relevance of environmental policy, and of the consequences of air-pollution in particular, also failed to moderate the effects of the symbols and information in the communications.
-These findings are also consistent with the findings of @alonbarkat_2017, where they found that the trust of citizens who recently personally experienced prolonged blackouts (and presumably perceived electricity services as personally relevant) was nonetheless significantly affected by a symbol of the government-owned electricity company.
+Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that higher levels of perceived personal relevance attenuate the effect of symbols.
+While subjects residing in the polluted Haifa Bay reported in the survey that they perceive the governmental policy for reducing air-pollution in that area as highly relevant for their lives, they were similarly, and perhaps even more affected by the appearance of familiar brand elements of the environmental protection ministry in the communication of that policy plan.
+Congruently, the study indicates that Haifa Bay subjects did not pay more attention to the logical quality of the policy plan.
+Furthermore, the results tend to indicate that priming Haifa Bay subjects to think about the personal relevance of the air-pollution did not significantly attenuate their susceptibility to persuasion by the symbols.
 
@@
 Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
-Rather, it might be explained by the lower baseline of Haifa Bay subjects' trust in both policies, presumably due to their negative prior attitudes towards EPM.
+Rather, I suggest, tentatively, that it might simply be due to the lower baseline of Haifa Bay subjects' trust in EPM policies.
 Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
@@
 
-[^footnote_ceiling_effect]: This tentative explanation is supported by the fact that the interaction remains intact when controlling for demographic differences between the areas.
-It is also supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
-This comparison shows a pattern of decreased marginal reduction.
-In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased by from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`%.
-In the center, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
+[^footnote_ceiling_effect]: This tentative explanation supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
+This comparison consistently shows a pattern of decreased marginal reduction.
+In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the real symbols.
+Among the center subjects, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
 With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa Bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
@@
 
+The limitations of this study should be acknowledged.
+The study focuses, empirically, on one local policy case.
+Future studies may put these findings to further test by testing cases of air-pollution policy in other countries, as well as by exploring additional cases of public organizations and policy areas.
+Additionally, as already acknowledged in the paper, I cannot entirely rule out the possibility that the differences in personal relevance between the two geographic areas are confounded with other differences associated with people's beliefs about the subject.
+Future studies may put these findings to a more rigorous test through natural experimental or quasi-experimental designs that take advantage of random allocation of citizens to varying levels of personal relevance.
+Finally, whereas this study includes an experimental manipulation for perceived personal relevance, I acknowledge the limitations of that test, namely its statistical power and the fact that the data does not confirm the its effectiveness in altering the moderating variable.
+Therefore, future studies may use different, possibly stronger experimental manipulations for testing that variable.
+
 How can we reconcile the findings of this study with the proposed theory?
 One plausible explanation is that despite the relatively high involvement of Haifa Bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
-If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance.
-Indeed, Petty and Cacioppo have admitted that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p.
+If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance, such as a policy that has immediate and tangible implications on citizens well-being.
+Indeed, social psychology ELM scholars Petty and Cacioppo have acknowledged that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p.
 206].
@@
 The results of this study, if generalizable, have significant implications.
-They challenge the rationalistic view of government direct communications with citizens as a means to inform citizens about government organizations actions and promote transparency and accountability.
-Instead, they suggest that more often than not, citizens rely on brands and other symbolic elements in public communications, even with regard to policy issues that have direct implications on their own lives.
-Altogether, this study highlights the role played by government branding and other forms of symbolic communication in shaping citizens view of governments.
-It suggests that the boundaries of persuasion via symbols and branding are much wider than expected, based on previous social psychology and marketing studies.
-From the practical point of view of government organizations, this entails that organizations can overcome citizens distrust by investing in symbolic communications.
-Nonetheless, employing a broader perspective of democratic theory, these conclusions are disturbing insofar as they buttress the concern that government organizations will deliberately use symbolic communications to cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements, namely as "propaganda".
+They suggest that citizens are susceptible to persuasion by government branding and symbolic communication, even with regard to salient, consested policy issues that have significant consequences for their own lives.
+Altogether, this study highlights the role played by government branding in shaping citizens view of governments.
+It suggests that the boundaries of persuasion via branding are much wider than expected.
+From the practical point of view of government organizations, this entails that they can perhaps overcome citizens automatic skepticism and distrust by investing in strategic symbolic communications.
+Nonetheless, as discussed in the introduction, employing a broader perspective of democratic theory, these conclusions are disturbing since they they buttress the concern that government organizations will deliberately exploit branding to cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
 For good or for ill, citizens are affected by the emotional connections and associations of symbols.
-
-Notwithstanding these conclusions, the limitations of this study should be acknowledged.
-The study focuses, empirically, on one specific case.
-Future studies may put these findings to further test by examining additional cases of public organizations and policy areas, as well as different forms of communications.
-Additionally, the comparison between the two areas is imperfect, insofar as the differences in personal relevance are confounded with differences in prior beliefs about the subject, which I cannot effectively control.
-A comparison between two groups that have similar prior beliefs would be more reliable.
-Finally, one can question the validity of the relevance manipulation, which has not yielded significant effect on subjects' subjective reporting on the perceived personal relevance of the communications.
-Still, the main results are robust to different model specifications, and operationalizations of personal relevance and message elaboration, which substantiate their validity.
 

### 2019-07-22 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 ```{r}
-
 SVIVA2_01_comb %>%
@@
   scale_x_discrete(name="Policy",labels=c("Air-pollution","Recycling"))+
-  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.5))#+
-  facet_grid(policy ~ .)
-  ggtitle("Information")
+  scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.5))
 ```
@@
 # Supplementary analyses
+
+```{r}
+mod_air_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb)
+
+mod_air_1.1 = update(mod_air_null,. ~ .+
+                       SYMBOL_t+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
+mod_air_1.2 = update(mod_air_1.1,. ~ .+AREA_center)
+mod_air_1.3 = update(mod_air_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+
+mod_air_1.4 = update(mod_air_1.3,. ~ .+
+                      GENDER+
+                       AGE+
+                       GOV_TRUST+
+                       IDEOLOGY+
+                       EDUCATION+
+                       INCOME+
+                       CHILDREN_young)
+
+mod_air_1.5 = update(mod_air_1.3,. ~ .,data=SVIVA2_01_comb_air_first)
+
+mod_air_1.5.robust_se    <- sqrt(diag(vcovHC(mod_air_1.5, type = "HC1")))
+mod_air_1.5.wald_results <- waldtest(mod_air_1.5, vcov = vcovHC(mod_air_1.5, type = "HC1"))
+
+mod_waste_null = lm(TRUST_waste_INDEX~1,data=SVIVA2_01_comb)
+mod_waste_1.1 = update(mod_waste_null,. ~ .+
+                       SYMBOL_t+
+                       INFORMATION_weak,
+                     data=SVIVA2_01_comb)
+mod_waste_1.2 = update(mod_waste_1.1,. ~ .+AREA_center)
+mod_waste_1.3 = update(mod_waste_1.1,. ~ .+AREA_center*(SYMBOL_t+INFORMATION_weak))
+mod_waste_1.4 = update(mod_waste_1.3,. ~ .+
+                      GENDER+
+                       AGE+
+                       GOV_TRUST+
+                       IDEOLOGY+
+                       EDUCATION+
+                       INCOME+
+                       CHILDREN_young)
+SVIVA2_01_comb_recycling_first <- SVIVA2_01_comb %>% filter(AIR_order==2)
+mod_waste_1.5 = update(mod_waste_1.3,. ~ .,data=SVIVA2_01_comb_recycling_first)
+
+mod_waste_1.5.robust_se    <- sqrt(diag(vcovHC(mod_waste_1.5, type = "HC1")))
+mod_waste_1.5.wald_results <- waldtest(mod_waste_1.5, vcov = vcovHC(mod_waste_1.4, type = "HC1"))
+
+mod_relevance_null = lm(TRUST_air_INDEX~1,data=SVIVA2_01_comb.haifa)
+mod_relevance_1.1 = update(mod_relevance_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   RELEVANCE_exp)
+mod_relevance_1.2 = update(mod_relevance_1.1,. ~ .+RELEVANCE_exp*(SYMBOL_t+INFORMATION_weak))
+mod_relevance_1.3 = update(mod_relevance_1.2,. ~ .+
+                   GENDER+
+                   AGE+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                   CHILDREN_young)
+
+mod_relevance_1.4 = update(mod_relevance_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
+
+mod_relevance_1.4.robust_se    <- sqrt(diag(vcovHC(mod_relevance_1.4, type = "HC1")))
+mod_relevance_1.4.wald_results <- waldtest(mod_relevance_1.4, vcov = vcovHC(mod_relevance_1.3, type = "HC1"))
+
+```
+
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – policy presented first of order.**
+
+```{r,results="asis"}
+stargazer(mod_air_1.5, mod_air_null,
+          mod_relevance_1.4, mod_relevance_null,
+          mod_waste_1.5, mod_waste_null,
+          type = "html",
+          se  = list(mod_air_1.5.robust_se,NULL,
+                     mod_relevance_1.4.robust_se,NULL,
+                     mod_waste_1.5.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("a(1.",1:3,")"),
+          column.separate = c(2,2,2),
+          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Area (0=Haifa Bay; 1=center)",
+                             "Area x Real symbols",
+                             "Area x Fake symbols",
+                             "Area x Weak Information",
+                             "Relevance treatment",
+                             "Relevance treatment x Real symbols",
+                             "Relevance treatment x Fake symbols",
+                             "Relevance treatment x Weak Information"),
+          omit = control.vars,
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","no","","no","","no",""),
+                           c("F Statistic", 
+                             mod_air_1.5.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA,
+                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
+          notes = "",
+          notes.append = FALSE)
+```
+
+<br><br>
+
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area and young children.**
+
+```{r}
+mod_closedness_null = lm(TRUST_air_INDEX~+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                     AGE,data=SVIVA2_01_comb.haifa)
+
+mod_closedness_1.1 = update(mod_closedness_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   close.industrial.area+
+                     CHILDREN_young)
+
+mod_closedness_1.2 = update(mod_closedness_1.1,. ~ .
+                            +close.industrial.area*(SYMBOL_t+INFORMATION_weak)+
+                              CHILDREN_young*(SYMBOL_t+INFORMATION_weak)+
+                              GENDER*(SYMBOL_t+INFORMATION_weak))
+
+mod_closedness_1.3 = update(mod_closedness_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
+
+## Adjust standard errors & F statistic
+mod_closedness_1.1.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.1, type = "HC1")))
+mod_closedness_1.1.wald_results <- waldtest(mod_closedness_1.1, vcov = vcovHC(mod_closedness_1.1, type = "HC1"))
+
+mod_closedness_1.2.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.2, type = "HC1")))
+mod_closedness_1.2.wald_results <- waldtest(mod_closedness_1.2, vcov = vcovHC(mod_closedness_1.2, type = "HC1"))
+
+mod_closedness_1.3.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.3, type = "HC1")))
+mod_closedness_1.3.wald_results <- waldtest(mod_closedness_1.3, vcov = vcovHC(mod_closedness_1.3, type = "HC1"))
+
+```
+
+```{r,results="asis"}
+control.vars <- c("GENDER",
+                  "AGE",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME")
+
+stargazer(mod_closedness_1.1,mod_closedness_null,
+          mod_closedness_1.2,mod_closedness_null,
+          mod_closedness_1.3, mod_closedness_null,
+          type = "html",
+          se  = list(mod_closedness_1.1.robust_se,NULL,
+                     mod_closedness_1.2.robust_se,NULL,
+                     mod_closedness_1.3.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("a(2.",1:4,")"),
+          column.separate = c(2,2,2),
+          dep.var.labels="Trust in air-pollution policy",
+          omit = control.vars,
+          covariate.labels=c("Real symbols",
+                             "Fake-symbols",
+                             "Weak Information",
+                             "Proximity to industrial area",
+                             "Young children",
+                             "Proximity x Real symbols",
+                             "Proximity x Fake symbols",
+                             "Proximity x Weak Information",
+                             "Young children x Real symbols",
+                             "Young children x Fake symbols",
+                             "Young children x Weak Information"),          
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","Yes","","Yes","","Yes",""),
+                           c("F Statistic", 
+                             mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
+                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA,
+                             mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
+          notes = "",
+          notes.append = FALSE)
+```
+
+<br>
 
@@
           mod_air_1.4, mod_air_null,
-          mod_air_1.5, mod_air_null,
           type = "html",
@@
                      mod_air_1.3.robust_se,NULL,
-                     mod_air_1.4.robust_se,NULL,
-                     mod_air_1.5.robust_se,NULL),
+                     mod_air_1.4.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(a1.",1:5,")"),
-          column.separate = c(2,2,2,2,2),
+          column.labels   = str_c("a(3.",1:4,")"),
+          column.separate = c(2,2,2,2),
           dep.var.labels="Trust in air-pollution policy",
@@
           add.lines = list(
-                           c("Controls","No","","No","","No","","Yes","","No",""),
+                           c("Controls","No","","No","","No","","Yes",""),
                            c("F Statistic", 
@@
                              mod_air_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.4.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.5.wald_results[2,3] %>% round(2),NA)),
+                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
@@
           mod_waste_1.4, mod_waste_null,
-          mod_waste_1.5, mod_waste_null,
           type = "html",
@@
                      mod_waste_1.3.robust_se,NULL,
-                     mod_waste_1.4.robust_se,NULL,
-                     mod_waste_1.5.robust_se,NULL),
+                     mod_waste_1.4.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(2.",1:5,")"),
-          column.separate = c(2,2,2,2,2),
+          column.labels   = str_c("a(4.",1:4,")"),
+          column.separate = c(2,2,2,2),
           dep.var.labels="Trust in recycling policy",
@@
                              mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
+                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
@@
           mod_relevance_1.3, mod_relevance_null,
-          mod_relevance_1.4, mod_relevance_null,
           type = "html",
@@
                      mod_relevance_1.2.robust_se,NULL,
-                     mod_relevance_1.3.robust_se,NULL,
-                     mod_relevance_1.4.robust_se,NULL),
+                     mod_relevance_1.3.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(3.",1:4,")"),
+          column.labels   = str_c("a(5.",1:3,")"),
           column.separate = c(2,2,2),
@@
           add.lines = list(
-                           c("Controls","No","","No","","Yes","","No",""),
+                           c("Controls","No","","No","","Yes",""),
                            c("F Statistic", 
@@
                              mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA)),
+                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.

### 2019-07-22 paper3_revision_tables.Rmd
Add files via upload

@@
           initial.zero = FALSE,
-          column.labels   = str_c("(1.",1:5,")"),
-          column.separate = c(2,2,2,2,2),
+          column.labels   = str_c("(1.",1:4,")"),
+          column.separate = c(2,2,2,2),
           dep.var.labels="Trust in air-pollution policy",
@@
                              mod_air_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.4.wald_results[2,3] %>% round(2),NA,
-                             mod_air_1.5.wald_results[2,3] %>% round(2),NA)),
+                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
           notes = "*Notes*: In all regression tables, entries are nonstandardized OLS-regression coefficients.
@@
           initial.zero = FALSE,
-          column.labels   = str_c("(2.",1:5,")"),
+          column.labels   = str_c("(2.",1:4,")"),
           column.separate = c(2,2,2,2,2),
@@
                              mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA,
-                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
+                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
           notes = "",
@@
                              mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA,
-                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA)),
+                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
           notes = "",
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area and young children.**
-
-```{r,results="asis"}
-control.vars <- c("GENDER",
-                  "AGE",
-                  "GOV_TRUST",
-                   "IDEOLOGY",
-                   "EDUCATION",
-                   "INCOME")
-
-stargazer(mod_closedness_1.1,mod_closedness_null,
-          mod_closedness_1.2,mod_closedness_null,
-          mod_closedness_1.3, mod_closedness_null,
-          type = "html",
-          se  = list(mod_closedness_1.1.robust_se,NULL,
-                     mod_closedness_1.2.robust_se,NULL,
-                     mod_closedness_1.3.robust_se,NULL),
-          style = "apsr",
-          report = "vcsp",
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          column.labels   = str_c("(4.",1:4,")"),
-          column.separate = c(2,2,2),
-          dep.var.labels="Trust in air-pollution policy",
-          omit = control.vars,
-          covariate.labels=c("Real symbols",
-                             "Fake-symbols",
-                             "Weak Information",
-                             "Proximity to industrial area",
-                             "Young children",
-                             "Proximity x Real symbols",
-                             "Proximity x Fake symbols",
-                             "Proximity x Weak Information",
-                             "Young children x Real symbols",
-                             "Young children x Fake symbols",
-                             "Young children x Weak Information"),          
-          p.auto = F,
-          add.lines = list(
-                           c("Controls","Yes","","Yes","","Yes",""),
-                           c("F Statistic", 
-                             mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
-          notes = "",
-          notes.append = FALSE)
-```
-
 <br>

### 2019-07-22 paper3_revision_text.Rmd
Add files via upload

@@
 
-This study contributes to the growing Public-administration research on government branding and its potency to influence citizens' perceptions, and their inclination to trust organizations' policy plans.
+This study contributes to the growing public-administration research on government branding and its potency to influence and possibly manipulate citizens' perceptions of government organizations and their policies and services.
 I explored whether persuasion through branding and symbolic communication can also ocure in policy matters that have significant, clear implications for citizens' well-being.
 I examined the hypothesis, derived from social psychology theory, that persuasion via symbols is attenuated the more citizens perceive the communication as personally relevant.
-I put this hypothesis to rigorous empirical testing using a randomized survey experiment focused on air-pollution policy, thus exploiting a natural variation in the perceived personal relevance between citizens residing in a polluted area and outside it.
-In addition to utilizing these natural differences, I also experimentally manipulated the personal relevance of the policy.
-To the best of my knowledge, this is the first study to explore the moderating role of perceived personal relevance on citizens' responses to government symbolic communications or branding.
+I put this hypothesis to rigorous empirical testing using a randomized survey experiment focused on air-pollution policy, utilizing a natural variation in the perceived personal relevance between citizens residing in a polluted area and others, residing elsewhere.
+To the best of my knowledge, this is the first study to explore, theoretically and empirically, the moderating role of perceived personal relevance on citizens' responses to government branding, and more generally to government public communications.
 
@@
 While subjects residing in the polluted Haifa Bay reported in the survey that they perceive the governmental policy for reducing air-pollution in that area as highly relevant for their lives, they were similarly, and perhaps even more affected by the appearance of familiar brand elements of the environmental protection ministry in the communication of that policy plan.
-Congruently, the study indicates that Haifa Bay subjects did not pay more attention to the logical quality of the policy plan.
-Furthermore, the results tend to indicate that priming Haifa Bay subjects to think about the personal relevance of the air-pollution did not significantly attenuate their susceptibility to persuasion by the symbols.
-
-How can we explain the finding that the positive effect of the real symbols was stronger among Haifa Bay residents?
-Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
-Rather, I suggest, tentatively, that it might simply be due to the lower baseline of Haifa Bay subjects' trust in EPM policies.
-Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
-as in the case of Haifa Bay subjects), than shifting them from medium to high levels (i.e.
-as in the case of center subjects), indicating a ceiling effect.
-Stated otherwise, symbols may be more effective in reducing citizens' distrust, as opposed to increasing their trust.[^footnote_ceiling_effect] A related explanation is that the symbols distracted the subjects and decreased their inclination to think about the topic.
-As a result, they caused Haifa Bay subjects to disregard their prior beliefs about EPM and its failure regarding air-pollution.[^footnote_mediation_elaboration]
-
-[^footnote_ceiling_effect]: This tentative explanation supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
-This comparison consistently shows a pattern of decreased marginal reduction.
-In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the real symbols.
-Among the center subjects, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
-With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa Bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
-
-[^footnote_mediation_elaboration]: This explanation is further supported by the survey data.
-The real symbols had a negative effect on the elaboration of these policies,  as measured by reaction time and memory test.
-The decrease in elaboration mediates the effect of symbols on trust.
-
-The limitations of this study should be acknowledged.
-The study focuses, empirically, on one local policy case.
-Future studies may put these findings to further test by testing cases of air-pollution policy in other countries, as well as by exploring additional cases of public organizations and policy areas.
-Additionally, as already acknowledged in the paper, I cannot entirely rule out the possibility that the differences in personal relevance between the two geographic areas are confounded with other differences associated with people's beliefs about the subject.
-Future studies may put these findings to a more rigorous test through natural experimental or quasi-experimental designs that take advantage of random allocation of citizens to varying levels of personal relevance.
-Finally, whereas this study includes an experimental manipulation for perceived personal relevance, I acknowledge the limitations of that test, namely its statistical power and the fact that the data does not confirm the its effectiveness in altering the moderating variable.
-Therefore, future studies may use different, possibly stronger experimental manipulations for testing that variable.
+Congruently, they did not pay more attention to the substantive content of the policy plan.
+Furthermore, the results indicate that even priming Haifa Bay residents to think about the personal relevance of the air-pollution did not significantly attenuate their susceptibility to persuasion by the symbols.
 
@@
 
+How can we explain the finding that the positive effect of the real symbols was stronger to some extent among Haifa Bay residents?
+Given that this pattern is also evident for the recycling policy, it is unlikely that it is linked to differences in perceived personal relevance.
+Rather, I tentatively suggest two other possible explanations for that.
+First, these patterns are resulted by the lower baseline of Haifa Bay residents' trust in EPM policies.
+Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
+as in the case of Haifa Bay subjects), than shifting them from medium to high levels (i.e.
+as in the case of center subjects), indicating a ceiling effect.
+In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A second explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' prior beliefs on their judgements of the policy plans, an effect that can be related to motivated reasoning [@taber_2006; @christensen_2018; @baekgaard_2016].
+It can be theorized that symbols attenuate motivated reasoning, when symbolic associations are not strongly related to identities of groups having strong prior positions on the policy or the organization (as in the case of the EPM symbols and the Haifa Bay local residents).
+On the other hand, when symbolic associations do activate such group identities, they are likely to exacerbate partisan motivated reasoning in that regard, and polarization [@teodoro_2018].
+Certainly, we must be cautious about these tentative explanations, which may be tested by future studies.
+
+[^footnote_ceiling_effect]: This explanation is supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
+This comparison consistently shows a pattern of decreased marginal reduction.
+In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the real symbols.
+Among the center subjects, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
+With regard to the recycling policy, the percentage decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the Haifa Bay and from `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_waste_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the center.
+
+Still, several limitations of this study should be acknowledged.
+The study focuses on one policy domain, and on a specific, local issue.
+Future studies may put these findings to further test by exploring cases of air-pollution in other locations, as well as by exploring cases of other environmental policies, and other domains.
+Additionally, I cannot entirely rule out the possibility that the differences in personal relevance between the two geographic areas are confounded with other differences associated with people's beliefs about the subject and the agency.
+Future studies may conduct more rigorous investigations through natural experimental or quasi-experimental designs that could take advantage of particular cases of citizens' random allocation to varying levels of personal relevance.
+Finally, whereas this study includes an experimental manipulation for perceived personal relevance, I acknowledge the limitations of that test, namely its limited statistical power and the fact that the survey data does not confirm the effectiveness of the manipulation in altering the moderating variable.
+Therefore, future studies may explore different, possibly stronger experimental manipulations for perceived personal relevance.
+
 The results of this study, if generalizable, have significant implications.
 They suggest that citizens are susceptible to persuasion by government branding and symbolic communication, even with regard to salient, consested policy issues that have significant consequences for their own lives.
-Altogether, this study highlights the role played by government branding in shaping citizens view of governments.
-It suggests that the boundaries of persuasion via branding are much wider than expected.
-From the practical point of view of government organizations, this entails that they can perhaps overcome citizens automatic skepticism and distrust by investing in strategic symbolic communications.
-Nonetheless, as discussed in the introduction, employing a broader perspective of democratic theory, these conclusions are disturbing since they they buttress the concern that government organizations will deliberately exploit branding to cause citizens to view them more favorably regardless (or even in contrast) to their actual capacities and achievements.
+Accordingly, these findings suggest that the boundaries of persuasion via branding are much wider than expected.
+This entails that public organizations can affect citizens in a broad array of policy domains and contexts by investing in symbolic communications.
+Alongside the benefits of this instrument in mitigating citizens' distrust, it also has the potency to yield a distorted, emotive, overoptimistic view of government organizations and their policies, which may undermine basic democratic accountability mechanisms.
 For good or for ill, citizens are affected by the emotional connections and associations of symbols.

### 2019-07-23 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 
+ and restricting the sample to those who saw that policy first before the recycling policy.
+The latter analysis rules out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
+
+Notice that the effect of the real symbols is greater, which may indicate that the impact of symbols diminishes between the first and the second time participants see them.
+
 ```{r}
@@
 <br><br>
+
+The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015].
+Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016]. 
+Finally, as an additional test for the robustness of my findings, I further compare between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
+First, I rely on subjects city of residence, and its geographical proximity to the polluting industrial area.
+Congruently, I selected the three cities/suburbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
+The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
+Second, since young children are relatively vulnerable to air-pollution effects, and since the consequences of air-pollution on infants and young children has been highlighted in media, I expect parents for young children (under 12 years) to be more engaged with this issue, although that assumption is not supported by differences in self-reported perceived personal relevance.[^footnote_post_treatment_control]
+
+`r table.x=table.x+1`**Table `r table.x`** presents the interactions between these two variables and information manipulations.
+Model `r table.x`.1 presents the effect of these variables with the manipulations, and thereafter Model `r table.x`.2 adds their interactions, and finally Model `r table.x`.3 restricts the analysis to the first policy presented.
+All three models include control variables.
+The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols (the interaction is significant in Model `r table.x`.2, but not in Model `r table.x`.3).
+As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.[^footnote_proxies_models]
+
+[^footnote_post_treatment_control]: In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
+In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
+However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
+188-9].
+
+[^footnote_proxies_models]: The interaction between proximity and the real symbols is positive and significant in Model `r table.x`.2, in Model `r table.x`.3  it is positive but insignificant; The interaction between parents for young children and the fake symbols is positive and significant in Model `r table.x`.2.
+
+<br>
 

### 2019-07-23 paper3_revision_text.Rmd
Add files via upload

@@
 In 2015, the Ministry of Health published statistical data indicating that Haifa Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
-The subsequent media reports specifically highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [@elroi_website_2015; @raavad_website_2015].
-Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly focused on the finding that babies in the Haifa Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
-Some reports also highlighted that the areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
+Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly highlighted a particular finding that babies in the Haifa Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
 These publications, and others, caused much panic among the local population, and especially among young parents.
@@
 I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3).
-The final two models are designed to test the robustness of the interaction model by controlling for individual-level covariates (Model `r table.x`.4),[^footnote_control_variables] and restricting the sample to those who saw that policy first before the recycling policy (Model `r table.x`.5).
-The latter analysis rules out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
-In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
-In Models `r table.x`.3, `r table.x`.4, `r table.x`.5 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant.
+In Model `r table.x`.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
+In Models `r table.x`.3, `r table.x`.4 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant.
 A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
-Notice that in `r table.x`.5, the effect of the real symbols is greater, which may indicate that the impact of symbols diminishes between the first and the second time participants see them.
 
@@
 [^footnote_recycling_model]: The main effect of the real symbols (as depicted from Model 2.1) is significant compared with the no symbols group (*Diff*=`r diff1` [`r (diff1-1.96*se1) %>% round(3)`-`r (diff1+1.96*se1) %>% round(3)`], *t*=`r (diff1/se1) %>% round(3)`).
-That effect amounts to `r (diff1/sd.waste) %>% round(3)` SDs [`r ((diff1-1.96*se1)/sd.waste) %>% round(3)`-`r ((diff1+1.96*se1)/sd.waste) %>% round(3)`].
 Yet, the increase is not significant not with the fake symbols group (*Diff*=`r diff2` [`r (diff2-1.96*se2) %>% round(3)`-`r (diff2+1.96*se2) %>% round(3)`], *t*=`r (diff2/se2) %>% round(3)`).
@@
 The differences between the symbols groups among the center subjects are small and insignificant.
-The smaller effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy.
+The weaker effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy.
 The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
@@
 Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations.
-In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations.
-Similarly to the regression tables presented above, the final two models are robust analyses where I add controls (Model `r table.x`.3) and restrict the sample to the policy presented first in order (Model `r table.x`.4).
+In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations, and in Model `r table.x`.3 I add controls.
 In all these models, the coefficient of the relevance treatment is negative but far from significance.
 The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the incerase in trust due to the appearance of the symbols and those who did not were slightly smaller.
-However, these interaction coefficients are relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group) and far from significance.
-The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.4 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
+However, these interaction coefficients are relatively weak and far from significance (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).
+The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
 
@@
 
-Finally, as an additional test for the robustness of my findings, I further compare between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies.
-First, I rely on subjects city of residence, and its geographical proximity to the polluting industrial area.
-Congruently, I selected the three cities/suburbs that are closest to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in other cities in the Haifa Bay area (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
-The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
-Second, since young children are relatively vulnerable to air-pollution effects, and since the consequences of air-pollution on infants and young children has been highlighted in media, I expect parents for young children (under 12 years) to be more engaged with this issue, although that assumption is not supported by differences in self-reported perceived personal relevance.[^footnote_post_treatment_control]
+<br>
 
-`r table.x=table.x+1`**Table `r table.x`** presents the interactions between these two variables and information manipulations.
-Model `r table.x`.1 presents the effect of these variables with the manipulations, and thereafter Model `r table.x`.2 adds their interactions, and finally Model `r table.x`.3 restricts the analysis to the first policy presented.
-All three models include control variables.
-The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols (the interaction is significant in Model `r table.x`.2, but not in Model `r table.x`.3).
-As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.[^footnote_proxies_models]
-
-[^footnote_post_treatment_control]: In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
-In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
-However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
-188-9].
-
-[^footnote_proxies_models]: The interaction between proximity and the real symbols is positive and significant in Model `r table.x`.2, in Model `r table.x`.3  it is positive but insignificant; The interaction between parents for young children and the fake symbols is positive and significant in Model `r table.x`.2.
+I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
+*First*, I replicate the main models while restricting the analyses to the first policy seen by the participants.
+This enables to rule out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
+*Second*, I restrict the analyses to Haifa Bay residents, and compare between those who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects city of residence, and its geographical proximity to the polluting industrial area; (b) parents for young children.
+*Third*, I replicated the analyses on the unfiltered sample.
+These additional analyses are consistent with the analyses presented in the paper, and do not provide evidence that greater levels of perceived personal relevance attenuates the effect of symbols.
 
@@
 This study contributes to the growing public-administration research on government branding and its potency to influence and possibly manipulate citizens' perceptions of government organizations and their policies and services.
-I explored whether persuasion through branding and symbolic communication can also ocure in policy matters that have significant, clear implications for citizens' well-being.
+I explored whether persuasion through branding and symbolic communication can also occur in policy matters that have significant, clear implications for citizens' well-being.
 I examined the hypothesis, derived from social psychology theory, that persuasion via symbols is attenuated the more citizens perceive the communication as personally relevant.
 I put this hypothesis to rigorous empirical testing using a randomized survey experiment focused on air-pollution policy, utilizing a natural variation in the perceived personal relevance between citizens residing in a polluted area and others, residing elsewhere.
-To the best of my knowledge, this is the first study to explore, theoretically and empirically, the moderating role of perceived personal relevance on citizens' responses to government branding, and more generally to government public communications.
+To the best of my knowledge, this is the first study to explore, theoretically and empirically, the moderating role of perceived personal relevance on citizens' responses to government branding, and to government public communications at large.
 
@@
 One plausible explanation is that despite the relatively high involvement of Haifa Bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
-If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance, such as a policy that has immediate and tangible implications on citizens well-being.
+If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance -- policies that have immediate, tangible and unambiguous consequences for citizens well-being.
 Indeed, social psychology ELM scholars Petty and Cacioppo have acknowledged that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p.
@@
 Rather, I tentatively suggest two other possible explanations for that.
-First, these patterns are resulted by the lower baseline of Haifa Bay residents' trust in EPM policies.
-Accordingly, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
+First, these patterns could be the result of the higher intercept of center residents' trust in EPM policies, or a ceiling effect.
+More generally, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
 as in the case of Haifa Bay subjects), than shifting them from medium to high levels (i.e.
-as in the case of center subjects), indicating a ceiling effect.
-In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A second explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' prior beliefs on their judgements of the policy plans, an effect that can be related to motivated reasoning [@taber_2006; @christensen_2018; @baekgaard_2016].
-It can be theorized that symbols attenuate motivated reasoning, when symbolic associations are not strongly related to identities of groups having strong prior positions on the policy or the organization (as in the case of the EPM symbols and the Haifa Bay local residents).
+as in the case of center subjects).
+In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A second explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' prior beliefs on their judgments of the policy plans, an effect that can be related to motivated reasoning [@taber_2006; @christensen_2018; @baekgaard_2016].
+It can be theorized that symbols attenuate motivated reasoning, when symbolic associations are not strongly related to identities of specific groups having strong prior positions on the policy or the organization (as in the case of the EPM symbols and the Haifa Bay locals).
 On the other hand, when symbolic associations do activate such group identities, they are likely to exacerbate partisan motivated reasoning in that regard, and polarization [@teodoro_2018].
+For instance, it is possible that EPM "green" symbols enhance partisan motivated reasoning among groups divided on their support for environmental policy.
 Certainly, we must be cautious about these tentative explanations, which may be tested by future studies.
@@
 The results of this study, if generalizable, have significant implications.
-They suggest that citizens are susceptible to persuasion by government branding and symbolic communication, even with regard to salient, consested policy issues that have significant consequences for their own lives.
+They suggest that citizens are susceptible to persuasion by government branding and symbolic communication, even with regard to salient, contested policy issues that have significant consequences for their own lives.
 Accordingly, these findings suggest that the boundaries of persuasion via branding are much wider than expected.
@@
 # References
-
-<br>
-
-# References

### 2019-07-24 paper3_APPENDIX_revision_01.Rmd
Add files via upload

--- 2019-07-22 paper3_APPENDIX_revision_01.Rmd
@@
 
+In the regression tables below, I report the results of additional robust analyses.
+
+*Table A1* replicates the interaction models in the paper (1.3, 3.2 and 2.3) while restricting the sample to those who saw that policy first before the recycling policy.
+The directions of the coefficients in these models remain intact.
+The effect of the real symbols is greater, compared with the full sample (in both policies).
+This may indicate that the impact of symbols diminishes between the first and the second time participants are exposed to them.
+
+*Table A2* compares between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects' city of residence, and its geographical proximity to the polluting industrial area; (b) Parents for young children.
+The selection of these two variables is driven by the media coverage of the reports published in 2015-6 regarding the air-pollution in the Haifa Bay.
+The media reports following the publication of the the statistical data of the Ministry of Health in 2015 mostly highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [e.g.
+@elroi_website_2015; @raavad_website_2015].
+Thereafter, reports of the epidemiological study both emphasized the finding regarding the small heads of babies in Haifa Bay, as well as that areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
+
+For the first proxi, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
+The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
+As for the second proxi, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise.
+However, while I expect parents for young children to be more engaged, that assumption is not supported by differences in self-reported perceived personal relevance.
+In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
+
+The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols.
+The interaction between proximity and the real symbols is positive and significant.
+As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.
+The interaction between parents for young children and the fake symbols is positive and significant.
+
+In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
+However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
+188-9].
+
+Finally, *Tables A3-A5* replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`).
+The results of these models latter models do not substantially diverge from the results of the main models.
+
 ```{r}
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – policy presented first of order.**
+`r table.x=table.x+1`**Table A`r table.x`: Regression analyses – policy presented first of order.**
 
@@
 <br><br>
+
+<br>
 
@@
 
-The following regression tables replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`).
-
 <br>

### 2019-07-24 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 title: "Supplementary appendix"
-author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
+author: '**Saar Alon-Barkat**'
 date: " "
@@
 library(sandwich)
-
+library(effsize)
 ```
@@
 
-# Properties of the selected cities
+# Characteristics of the selected cities
 
@@
 Data for all cities, except for Qiryat-Hayiim, is retrived from the Central Bureau of Statistics data file of local authorities in Israel of 2015.
-Qiryat-Hayiim is considered, formally, a neighborhood within the jurisdiction of Haifa, although it is geographically seperated from the rest of the city.
+Qiryat-Hayiim is considered, formally, a neighborhood within the jurisdiction of Haifa, although it is geographically separated from the rest of the city.
 Therefore, it is included in the official statistical data within Haifa.
-The population of Qiryat-Hayiim is based on a document of statistical data for neighborhoods in Haifa for 2015, retrived from the website of the municipality of Haifa.
+The population of Qiryat-Hayiim is based on a document of statistical data for neighborhoods in Haifa for 2015, retrieved from the website of the municipality of Haifa.
 
@@
 
+<br>
+
+**Figure A3**
+
 "How familiar are you with the symbol [that appeared in the policy plans]?" (1=not at all; 7=very much)
@@
 ```
+
+<br>
+
+**Figure A4**
 
@@
 
+<br>
+
+**Figure A5**
 "The person presented in the image is familiar to me" (1=weakly agree; 7=strongly agree)
@@
 
+<br>
+
+**Figure A6**
+
 "The image is taken from an advertisement commercial of the Environmental Protection Ministry. To what extent to you remember the advertisement?" (1=not at all; 7=very much)
@@
 ```
+
+<br>
+
+**Figure A7**
 
@@
 
+<br>
+
+**Figure A8**
+
 "The image evokes a negative feeling" (1=weakly agree; 7=strongly agree)
@@
 
+<br>
+
 These results similarly show that the real campaign images are relatively recognizable and have a fairly positive affect, whereas the fake images and models are unrecognized and do not evoke strong negative of positive feelings.
@@
 
-This section aims to assess the concernt that participants did not accept the authenticity of the weak, fictional policy plan, and did not find it reliable, and as a results lost trust in the rest of the survey.
+This section aims to assess the concern that participants did not accept the authenticity of the weak, fictional policy plan, and did not find it reliable, and as a results lost trust in the rest of the survey.
 To assess that risk, I took advantage of the fact that the order in which the strong and weak policies were presented was randomized.
-Accordingly, half of the participants saw a weak plan first, and thereafter a strong plan, and for the other half it was the opposite.
+To reiterate, half of the participants saw a weak plan first, and thereafter a strong plan, and for the other half it was the opposite.
 Hence, I examined whether the the strong policy was evaluated differently when it was presented first (which means that participants at that point did not sea weak policy yet and did not question the reliability of the survey), then when it was presented second (after they already saw a fictional policy).
-This comparison, accross the two policies, is graphically presented in the following plot.
+This comparison, across the two policies, is graphically presented in the following plot.
 It shows that the differences between the means and distributions of the first and the second policy are relatively small and insignificant.
@@
 Altogether, these test tend to indicate that participants' exposure to the fictional weak policy did not have a strong influence on their answers to the subsequent questions.
+
+<br>
+
+**Figure A9**
 
@@
 Table A1 shows the results of regression analyses.
-For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafter I add their interaction.
+For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafter I add their interaction, and add controls.
 Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans.
-Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative (model 2).
-The interpretation of this interaction suggests that the priming questions decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, but increased it among those who reside in the Center.
+Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative.
+The interpretation of this interaction suggests that the priming questions slightly decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, and increased it among those who reside in the Center.
 Regarding the recycling policy, the interaction is insignificant.
 
+<br>
+
 **Table A1: Regression table - effect of relevance manipulation, across areas, on perceived personal relevance**
@@
 ```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
-mod_relevance_air_1.1_apx = lm(RELEVANCE_air_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
+control.vars <- c("GENDER",
+                  "AGE",
+                  "GOV_TRUST",
+                   "IDEOLOGY",
+                   "EDUCATION",
+                   "INCOME",
+                   "CHILDREN",
+                   "CHILDREN_young")
+
+mod_relevance_air_null_apx = lm(RELEVANCE_air_obs~1,data=SVIVA2_01)
+mod_relevance_air_1.1_apx = lm(RELEVANCE_air_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01)
 mod_relevance_air_1.2_apx = update(mod_relevance_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-mod_relevance_waste_1.1_apx = lm(RELEVANCE_waste_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
-mod_relevance_waste_1.2_apx = update(mod_relevance_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
-
-stargazer(mod_relevance_air_1.1_apx,mod_relevance_air_1.2_apx,
-          mod_relevance_waste_1.1_apx,mod_relevance_waste_1.2_apx,
-          type="html",style = "apsr",
-          dep.var.labels=c("Air-pollution","Recycling"),
+mod_relevance_air_1.3_apx = update(mod_relevance_air_1.2_apx,. ~ .+
+                      GENDER+
+                       AGE+
+                       GOV_TRUST+
+                       IDEOLOGY+
+                       EDUCATION+
+                       INCOME+
+                       CHILDREN_young)
+
+mod_relevance_waste_null_apx = lm(RELEVANCE_waste_obs~1,data=SVIVA2_01)
+mod_relevance_waste_1.1_apx = update(mod_relevance_air_1.1_apx,RELEVANCE_waste_obs ~ .)
+mod_relevance_waste_1.2_apx = update(mod_relevance_air_1.2_apx,RELEVANCE_waste_obs ~ .)
+mod_relevance_waste_1.3_apx = update(mod_relevance_air_1.3_apx,RELEVANCE_waste_obs ~ .)
+
+## Adjust standard errors & F statistic
+mod_relevance_air_1.1_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_air_1.1_apx, type = "HC1")))
+mod_relevance_air_1.1_apx.wald_results <- waldtest(mod_relevance_air_1.1_apx, vcov = vcovHC(mod_relevance_air_1.1_apx, type = "HC1"))
+
+mod_relevance_air_1.2_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_air_1.2_apx, type = "HC1")))
+mod_relevance_air_1.2_apx.wald_results <- waldtest(mod_relevance_air_1.2_apx, vcov = vcovHC(mod_relevance_air_1.2_apx, type = "HC1"))
+
+mod_relevance_air_1.3_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_air_1.3_apx, type = "HC1")))
+mod_relevance_air_1.3_apx.wald_results <- waldtest(mod_relevance_air_1.3_apx, vcov = vcovHC(mod_relevance_air_1.3_apx, type = "HC1"))
+
+mod_relevance_waste_1.1_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_waste_1.1_apx, type = "HC1")))
+mod_relevance_waste_1.1_apx.wald_results <- waldtest(mod_relevance_waste_1.1_apx, vcov = vcovHC(mod_relevance_waste_1.1_apx, type = "HC1"))
+
+mod_relevance_waste_1.2_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_waste_1.2_apx, type = "HC1")))
+mod_relevance_waste_1.2_apx.wald_results <- waldtest(mod_relevance_waste_1.2_apx, vcov = vcovHC(mod_relevance_waste_1.2_apx, type = "HC1"))
+
+mod_relevance_waste_1.3_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_waste_1.3_apx, type = "HC1")))
+mod_relevance_waste_1.3_apx.wald_results <- waldtest(mod_relevance_waste_1.3_apx, vcov = vcovHC(mod_relevance_waste_1.3_apx, type = "HC1"))
+
+stargazer(mod_relevance_air_1.1_apx,mod_relevance_air_null_apx,
+          mod_relevance_air_1.2_apx,mod_relevance_air_null_apx,
+          mod_relevance_air_1.3_apx,mod_relevance_air_null_apx,
+          mod_relevance_waste_1.1_apx,mod_relevance_waste_null_apx,
+          mod_relevance_waste_1.2_apx,mod_relevance_waste_null_apx,
+          mod_relevance_waste_1.3_apx,mod_relevance_waste_null_apx,
+          type = "html",
+          se  = list(mod_relevance_air_1.1_apx.robust_se,NULL,
+                     mod_relevance_air_1.2_apx.robust_se,NULL,
+                     mod_relevance_air_1.3_apx.robust_se,NULL,
+                     mod_relevance_waste_1.1_apx.robust_se,NULL,
+                     mod_relevance_waste_1.2_apx.robust_se,NULL,
+                     mod_relevance_air_1.3_apx.robust_se,NULL),
+          style = "apsr",
+          report = "vcsp",
+          omit.stat = c("rsq","ser", "f"),
+          initial.zero = FALSE,
+          column.labels   = str_c("a(1.",1:6,")"),
+          column.separate = c(2,2,2,2,2,2),
+          dep.var.labels=c("Air-pollution policy","Recycling policy"),
+          omit = control.vars,
           covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
@@
                              "Area x Relevance treatment"),
-          omit.stat = c("rsq","ser", "f"),
-          initial.zero = FALSE,
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses.
+          p.auto = F,
+          add.lines = list(
+                           c("Controls","No","","No","","Yes","",
+                                        "No","","No","","Yes",""),
+                           c("F Statistic", 
+                             mod_relevance_air_1.1_apx.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_air_1.2_apx.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_air_1.3_apx.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_waste_1.1_apx.wald_results[2,3] %>% round(2),NA,
+                             mod_relevance_waste_1.2_apx.wald_results[2,3] %>% round(2),NA,
+
+mod_relevance_waste_1.3_apx.wald_results[2,3] %>% round(2),NA)),
+          notes = "*Notes*: In all regression tables, entries are nonstandardized OLS-regression coefficients.
+Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
 The reference category for the symbols manipulation conditions is the control (no symbols).",
           notes.append = FALSE)
+
 ```
@@
 In this section, I report the results of power estimations, which I conducted after collecting and analyzing the data.
-I have conducted seperate analyses for: (1) Main effects of the symbols and weak information manipulations; (2) Conditional effects of manipulations within each of the two areas (Haifa-Bay and Center); (3) Two-way interactions bewteen areas and the manipulations; and (4) Two-way interactions bewteen the relevance manipulation and the manipulations (in the Haifa-Bay area).
-
-These power estimations were conducted in R software, through regression models simulations with 1,000 interations for each effect size [code adopted from @hughes_website_2017].
+I have conducted separate analyses for: (1) Main effects of the symbols and weak information manipulations; (2) Conditional effects of manipulations within each of the two areas (Haifa-Bay and Center); (3) Two-way interactions between areas and the manipulations; and (4) Two-way interactions between the relevance manipulation and the manipulations (in the Haifa-Bay area).
+
+These power estimations were conducted in R software, through regression models simulations with 1,000 iterations for each effect size [code adopted from @hughes_website_2017].
 All these tests refer to a *p-value* of .05 (one-tailed), with `set.seed(2018)`.
@@
 
-**Figure XX: Power of conditional effects**
+**Figure A10: Power of conditional effects**
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 
-**Figure XX: Power of conditional effects**
+**Figure A11: Power of conditional effects**
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 
-**Figure XX: Power of Interactions with area**
+**Figure A12: Power of Interactions with area**
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 
-**Figure XX: Power of Interactions with relevance manipulation**
+**Figure A13: Power of Interactions with relevance manipulation**
 
@@
 
+*Table A4*
+
 ```{r, echo=FALSE,warning=FALSE,message=FALSE}
@@
 
-In the regression tables below, I report the results of additional robust analyses.
-
-*Table A1* replicates the interaction models in the paper (1.3, 3.2 and 2.3) while restricting the sample to those who saw that policy first before the recycling policy.
-The directions of the coefficients in these models remain intact.
-The effect of the real symbols is greater, compared with the full sample (in both policies).
-This may indicate that the impact of symbols diminishes between the first and the second time participants are exposed to them.
-
-*Table A2* compares between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects' city of residence, and its geographical proximity to the polluting industrial area; (b) Parents for young children.
-The selection of these two variables is driven by the media coverage of the reports published in 2015-6 regarding the air-pollution in the Haifa Bay.
-The media reports following the publication of the the statistical data of the Ministry of Health in 2015 mostly highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [e.g.
-@elroi_website_2015; @raavad_website_2015].
-Thereafter, reports of the epidemiological study both emphasized the finding regarding the small heads of babies in Haifa Bay, as well as that areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
-
-For the first proxi, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
-The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
-As for the second proxi, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise.
-However, while I expect parents for young children to be more engaged, that assumption is not supported by differences in self-reported perceived personal relevance.
-In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
-
-The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols.
-The interaction between proximity and the real symbols is positive and significant.
-As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.
-The interaction between parents for young children and the fake symbols is positive and significant.
-
-In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
-However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
-188-9].
-
-Finally, *Tables A3-A5* replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`).
-The results of these models latter models do not substantially diverge from the results of the main models.
-
 ```{r}
@@
 
-`r table.x=table.x+1`**Table A`r table.x`: Regression analyses – policy presented first of order.**
+```{r}
+mod_closedness_null = lm(TRUST_air_INDEX~+
+                   GOV_TRUST+
+                   IDEOLOGY+
+                   EDUCATION+
+                   INCOME+
+                     AGE,data=SVIVA2_01_comb.haifa)
+
+mod_closedness_1.1 = update(mod_closedness_null,. ~ .+
+                             SYMBOL_t+
+                   INFORMATION_weak+
+                   close.industrial.area+
+                     CHILDREN_young)
+
+mod_closedness_1.2 = update(mod_closedness_1.1,. ~ .
+                            +close.industrial.area*(SYMBOL_t+INFORMATION_weak)+
+                              CHILDREN_young*(SYMBOL_t+INFORMATION_weak)+
+                              GENDER*(SYMBOL_t+INFORMATION_weak))
+
+mod_closedness_1.3 = update(mod_closedness_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
+
+## Adjust standard errors & F statistic
+mod_closedness_1.1.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.1, type = "HC1")))
+mod_closedness_1.1.wald_results <- waldtest(mod_closedness_1.1, vcov = vcovHC(mod_closedness_1.1, type = "HC1"))
+
+mod_closedness_1.2.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.2, type = "HC1")))
+mod_closedness_1.2.wald_results <- waldtest(mod_closedness_1.2, vcov = vcovHC(mod_closedness_1.2, type = "HC1"))
+
+mod_closedness_1.3.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.3, type = "HC1")))
+mod_closedness_1.3.wald_results <- waldtest(mod_closedness_1.3, vcov = vcovHC(mod_closedness_1.3, type = "HC1"))
+
+relevance.areas.close.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area) 
+relevance.areas.close.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area)
+
+relevance.areas.children.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young) 
+relevance.areas.children.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young)
+
+```
+
+<br>
+
+In the regression tables below, I report the results of additional robust analyses.
+
+*Table A5* replicates the interaction models in the paper (1.3, 3.2 and 2.3) while restricting the sample to those who saw that policy first before the recycling policy.
+The directions of the coefficients in these models remain intact.
+The effect of the real symbols is greater, compared with the full sample (in both policies).
+This may indicate that the impact of symbols diminishes between the first and the second time participants are exposed to them.
+
+*Table A6* compares between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects' city of residence, and its geographical proximity to the polluting industrial area; (b) Parents for young children.
+The selection of these two variables is driven by the media coverage of the reports published in 2015-6 regarding the air-pollution in the Haifa Bay.
+The media reports following the publication of the the statistical data of the Ministry of Health in 2015 mostly highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [e.g.
+@elroi_website_2015; @raavad_website_2015].
+Thereafter, reports of the epidemiological study both emphasized the finding regarding the small heads of babies in Haifa Bay, as well as that areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].
+
+For the first proxy, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
+The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
+As for the second proxy, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise.
+However, while I expect parents for young children to be more engaged, that assumption is not supported by differences in self-reported perceived personal relevance.
+In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.
+
+The models tend to suggest that residing in the closer cities were not more likely to differentiate between the strong and weak plans, and were, to some extent, even more receptive to the emotional effect of the symbols.
+The interaction between proximity and the real symbols is positive and significant.
+As for parents for young children, the data does not show that they respond differently to the appearance of symbols or to variations in the content.
+The interaction between parents for young children and the fake symbols is positive and significant.
+
+In these models, the interactions with the symbols is insignificant and the interaction with weak information is negative and significant.
+However, these analysis can produce biased estimates since the perceived relevance measure is a post-manipulation variable [@gelman_2006, pp.
+188-9].
+
+Finally, *Tables A7-A9* replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`).
+The results of these models latter models do not substantially diverge from the results of the main models.
+
+<br>
+
+**Table A5: Regression analyses – policy presented first of order.**
 
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(1.",1:3,")"),
+          column.labels   = str_c("a(2.",1:3,")"),
           column.separate = c(2,2,2),
@@
 
-<br>
-
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area and young children.**
-
-```{r}
-mod_closedness_null = lm(TRUST_air_INDEX~+
-                   GOV_TRUST+
-                   IDEOLOGY+
-                   EDUCATION+
-                   INCOME+
-                     AGE,data=SVIVA2_01_comb.haifa)
-
-mod_closedness_1.1 = update(mod_closedness_null,. ~ .+
-                             SYMBOL_t+
-                   INFORMATION_weak+
-                   close.industrial.area+
-                     CHILDREN_young)
-
-mod_closedness_1.2 = update(mod_closedness_1.1,. ~ .
-                            +close.industrial.area*(SYMBOL_t+INFORMATION_weak)+
-                              CHILDREN_young*(SYMBOL_t+INFORMATION_weak)+
-                              GENDER*(SYMBOL_t+INFORMATION_weak))
-
-mod_closedness_1.3 = update(mod_closedness_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
-
-## Adjust standard errors & F statistic
-mod_closedness_1.1.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.1, type = "HC1")))
-mod_closedness_1.1.wald_results <- waldtest(mod_closedness_1.1, vcov = vcovHC(mod_closedness_1.1, type = "HC1"))
-
-mod_closedness_1.2.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.2, type = "HC1")))
-mod_closedness_1.2.wald_results <- waldtest(mod_closedness_1.2, vcov = vcovHC(mod_closedness_1.2, type = "HC1"))
-
-mod_closedness_1.3.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.3, type = "HC1")))
-mod_closedness_1.3.wald_results <- waldtest(mod_closedness_1.3, vcov = vcovHC(mod_closedness_1.3, type = "HC1"))
-
-```
+**Table A6: Regression analyses – moderation of proximity to industrial area and young children.**
 
@@
           mod_closedness_1.2,mod_closedness_null,
-          mod_closedness_1.3, mod_closedness_null,
           type = "html",
           se  = list(mod_closedness_1.1.robust_se,NULL,
-                     mod_closedness_1.2.robust_se,NULL,
-                     mod_closedness_1.3.robust_se,NULL),
+                     mod_closedness_1.2.robust_se,NULL),
           style = "apsr",
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(2.",1:4,")"),
-          column.separate = c(2,2,2),
+          column.labels   = str_c("a(3.",1:2,")"),
+          column.separate = c(2,2),
           dep.var.labels="Trust in air-pollution policy",
@@
           add.lines = list(
-                           c("Controls","Yes","","Yes","","Yes",""),
+                           c("Controls","Yes","","Yes",""),
                            c("F Statistic", 
                              mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
-                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA,
-                             mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
+                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA)),
           notes = "",
@@
 
-`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – trust in air-pollution policy (unfilterred sample).**
+**Table A7: Regression analyses – trust in air-pollution policy (unfiltered sample).**
 
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(3.",1:4,")"),
+          column.labels   = str_c("a(4.",1:4,")"),
           column.separate = c(2,2,2,2),
@@
                              mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes = "",
           notes.append = FALSE)
@@
 
-<br>
-
-`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – trust in recycling policy (unfilterred sample).**
+<br><br>
+
+**Table A8: Regression analyses – trust in recycling policy (unfiltered sample).**
 
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(4.",1:4,")"),
+          column.labels   = str_c("a(5.",1:4,")"),
           column.separate = c(2,2,2,2),
@@
                              mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes = "",
           notes.append = FALSE)
@@
 
-`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – experimental manipulation of perceived personal relevance (unfilterred sample).**
+**Table A9: Regression analyses – experimental manipulation of perceived personal relevance (unfiltered sample).**
 
@@
           initial.zero = FALSE,
-          column.labels   = str_c("a(5.",1:3,")"),
+          column.labels   = str_c("a(6.",1:3,")"),
           column.separate = c(2,2,2),
@@
 
-[For subjets assigned to the no symbols]:
+[For subjects assigned to the no symbols]:
 

### 2019-07-24 paper3_revision_text.Rmd
Add files via upload

@@
 
-*Recent studies demonstrated that symbolic elements in government communications can enhance citizens' trust in government organizations and policies.
-The emotive effect of symbols can further compensate for organizations' poor functioning, thereby eliciting undue trust.
-This study explores the boundaries of governments' persuasion of citizens through symbolic communication.
-Building on social psychology, I hypothesize that citizens are less susceptible to symbols, the more they perceive the policy issue in the communication as personally relevant.
-I test this expectation through a survey experiment, where I examine Israeli citizens' trust in the Environment Protection Ministry's policy plans for reducing air pollution in a highly polluted area.
-The policy's perceived personal relevance is operationalized both experimentally, and by comparing between citizens residing in the polluted area and elsewhere.
-The results indicate that even high levels of perceived personal relevance do not attenuate the symbols' effect, which entails that the boundaries of persuasion through symbols are wider than expected.*
+*Recent studies demonstrated the potency of government branding to positively affect citizens' judgments of government organizations and policies.
+This study explores the boundaries of governments' persuasion of citizens through branding and symbolic communications.
+The latter is important given the the detrimental implications of the emotive effect of symbols, mainly its ability to compensate for organizations' poor functioning, and to elicit undue trust.
+Building on social psychology, I hypothesize that citizens are less susceptible to persuasion by symbolic communication, the more they perceive the policy issue in the communication as personally relevant.
+I test this expectation through a survey experiment, focused on air-pollution policy, utilizing natural variation in the perceived personal relevance between citizens residing in a polluted area and elsewhere.
+Contrary to my expectations, the results indicate that even high levels of perceived personal relevance do not attenuate the symbols' effect, which entails that the boundaries of persuasion through symbols are wider than expected.*
 
@@
 That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
-Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]/2) %>% abs() %>% round(.,3)`, one-tailed test).
+Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]) %>% abs() %>% round(.,3)`).
 The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score.
@@
 
-```{r}
-mod_closedness_null = lm(TRUST_air_INDEX~+
-                   GOV_TRUST+
-                   IDEOLOGY+
-                   EDUCATION+
-                   INCOME+
-                     AGE,data=SVIVA2_01_comb.haifa)
-
-mod_closedness_1.1 = update(mod_closedness_null,. ~ .+
-                             SYMBOL_t+
-                   INFORMATION_weak+
-                   close.industrial.area+
-                     CHILDREN_young)
-
-mod_closedness_1.2 = update(mod_closedness_1.1,. ~ .
-                            +close.industrial.area*(SYMBOL_t+INFORMATION_weak)+
-                              CHILDREN_young*(SYMBOL_t+INFORMATION_weak)+
-                              GENDER*(SYMBOL_t+INFORMATION_weak))
-
-mod_closedness_1.3 = update(mod_closedness_1.2,. ~ .,data=SVIVA2_01_comb.haifa_air_first)
-
-## Adjust standard errors & F statistic
-mod_closedness_1.1.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.1, type = "HC1")))
-mod_closedness_1.1.wald_results <- waldtest(mod_closedness_1.1, vcov = vcovHC(mod_closedness_1.1, type = "HC1"))
-
-mod_closedness_1.2.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.2, type = "HC1")))
-mod_closedness_1.2.wald_results <- waldtest(mod_closedness_1.2, vcov = vcovHC(mod_closedness_1.2, type = "HC1"))
-
-mod_closedness_1.3.robust_se    <- sqrt(diag(vcovHC(mod_closedness_1.3, type = "HC1")))
-mod_closedness_1.3.wald_results <- waldtest(mod_closedness_1.3, vcov = vcovHC(mod_closedness_1.3, type = "HC1"))
-
-relevance.areas.close.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area) 
-relevance.areas.close.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area)
-
-relevance.areas.children.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young) 
-relevance.areas.children.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young)
-
-```
-
-<br>
-
 I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.

### 2019-07-25 paper3_revision_tables.Rmd
Add files via upload

@@
          "Interest in environmental issues",
-         "Air-pollution policy",
+         "Haifa Bay air-pollution policy",
          "Recycling policy"
@@
                      "t-test",
-                    str_c("Treatment (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
-                    str_c("Control (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
+                    str_c("Treatment (n=",SVIVA2_01_center %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
+                    str_c("Control (n=",SVIVA2_01_center %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
                     "t-test"))%>%
@@
   gather(key = policy, value = relevance, -AREA_names) %>%
-  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
+  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Haifa Bay air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
 ggplot(aes(AREA_names,relevance))+ 
@@
 
-`r figure.x=figure.x+1`**Figure `r figure.x`: The distribution of Trust in air-pollution across the different conditions of symbols and information**
+`r figure.x=figure.x+1`**Figure `r figure.x`**
 
@@
   scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
+  scale_y_continuous(name = "Trust in Haifa Bay air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
   ggtitle("Symbols")
@@
   scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
-  scale_y_continuous(name = "Trust in air-pollution policy",breaks = seq(1,7,by=0.5))+
+  scale_y_continuous(name = "Trust in Haifa Bay air-pollution policy",breaks = seq(1,7,by=0.5))+
   ggtitle("Symbols")
@@
 
-`r table.x=table.x+1`**Table `r table.x`: Regression analyses – Trust in Air-pollution policy.**
+`r table.x=table.x+1`**Table `r table.x`: Regression analyses – Trust in Haifa Bay air-pollution policy.**
 
@@
           column.separate = c(2,2,2,2),
-          dep.var.labels="Trust in air-pollution policy",
+          dep.var.labels="Trust in Haifa Bay air-pollution policy",
           omit = control.vars,
@@
           column.separate = c(2,2,2),
-          dep.var.labels="Trust in air-pollution policy",
+          dep.var.labels="Trust in Haifa Bay air-pollution policy",
           omit = control.vars,

### 2019-07-25 paper3_revision_text.Rmd
Add files via upload

@@
 Viewed against the above theoretical framework, symbolic elements in government communications can be regarded as peripheral cues, which can affect citizens' attitudes though a peripheral route process of evaluative conditioning.[^footnote_symbols_arguments] Hence, based on ELM, citizens judgements about public organizations are less likely to be affected by symbols (and more likely to be shaped by substantive arguments) the more motivated they are to critically think about the message.
-Their level of motivation is likely to be determined, to a great extent, by their perceived personal relevnace of the particular policy issue.
+Citizens' level of motivation is likely to be determined, to a great extent, by their the degree in which they perceive the policy issue in the communication as having personal relevance for themselves.
 
@@
 
-*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the less citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+*H<sub>1</sub> - Symbolic elements in communications are likely to have a greater positive effect on citizens' attitudes about government organizations and policies, the lower the perceived personal relevance of the communication.*
 
-*H<sub>2</sub> - The argument quality of the information in communications is likely to have a lesser effect on citizens' attitudes about government organizations and policies, the less citizens perceive the policy issue in the communication as having personal relevance for themselves.*
+*H<sub>2</sub> - The argument quality of the information in communications is likely to have a weaker effect on citizens' attitudes about government organizations and policies, the lower the perceived personal relevance of the communication.*
 
@@
 The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##).
-To ensure that the two groups would differ in relation to the their perceptions about the relevance air-pollution policies, I searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.
+I further searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.
 
-*Second*, in addition to the policy regarding the air-pollution in Haifa Bay, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
+*Second*, in addition to the policy regarding the Haifa Bay air-pollution, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
 For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
 The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates.
-I henceforth refer to these two policy plans as "air-pollution" and "recycling".
+I henceforth refer to these two policy plans as "Haifa Bay air-pollution" and "recycling".
 *Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa Bay residents.
@@
 [^footnote_relevance_manipulation]: The first three treatment questions were also initially designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
-In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.
+In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the Haifa Bay air-pollution policy.
 
@@
 The third element is an image of a celebrity comedian from an advertising campaign of the EPM.
-The air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
+The Haifa Bay air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
 The recycling policy (in the real symbols condition) was presented with an image from a campaign from 2017 for reducing the use of disposable bags ("taking every bag seriously"), starring the comedian Ido Rosenblum.
@@
 Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order.
-For instance, a subject who first received a strong air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
+For instance, a subject who first received a strong Haifa Bay air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
 The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
@@
 
-In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy.
+In line with the abovementioned hypotheses, my main focus in this paper is on participants' trust in the Haifa Bay air-pollution policy, and the two-way interactions between residence in Haifa Bay and the symbols and information manipulations of that policy.
 I also explore these interactions with regard to the recycling policy, and compare them to the air-pollution interactions.
@@
 
-The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for air-pollution policy, and `r alpha_waste_trust` for the recycling policy).
+The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for Haifa Bay air-pollution policy, and `r alpha_waste_trust` for the recycling policy).
 This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
@@
 Living in Haifa Bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa Bay cities.
-To confirm the empirical assumption that the air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
+To confirm the empirical assumption that the Haifa Bay air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas.
-As expected, the air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]).
+As expected, the Haifa Bay air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]).
 By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them.
@@
 
-I now turn to exploring the main outcome variable of interest -- respondents trust in the *air-pollution policy*.
+I now turn to exploring the main outcome variable of interest -- respondents trust in the *Haifa Bay air-pollution policy*.
 This outcome variable has a right-skewed distribution (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r sd.air %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_air_INDEX,na.rm=T))%>%max() %>% round(2)`), which entails that more subjects reported very low levels of trust, than very high levels of trust in than policy.
@@
 That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
-Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the Haifa Bay air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
 Descriptively, `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than 4, the scale's middle point (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
@@
 I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
-I regress trust in air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3).
+I regress trust in Haifa Bay air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3).
 In Model `r table.x`.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
@@
 
-Overall, the findings with regard to the air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
+Overall, the findings with regard to the Haifa Bay air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
 Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence a concern of endogeneity cannot be entirely ruled.
@@
 The differences between the symbols groups among the center subjects are small and insignificant.
-The weaker effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the air-pollution policy.
+The weaker effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the Haifa Bay air-pollution policy.
 The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
@@
 Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations.
-In Model `r table.x`.1, I regress trust in air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations, and in Model `r table.x`.3 I add controls.
+In Model `r table.x`.1, I regress trust in Haifa Bay air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations, and in Model `r table.x`.3 I add controls.
 In all these models, the coefficient of the relevance treatment is negative but far from significance.
@@
 
-[^footnote_relevance_manipulation_1]: In additional analyses, I also examine the moderating effect of the relevance treatment for center subjects' responses to air-pollution policy, as well as for the recycling policy (for the entire sample).
+[^footnote_relevance_manipulation_1]: In additional analyses, I also examine the moderating effect of the relevance treatment for center subjects' responses to Haifa Bay air-pollution policy, as well as for the recycling policy (for the entire sample).
 In all these analyses, the interactions with the relevance treatment are insignificant.
@@
 This comparison consistently shows a pattern of decreased marginal reduction.
-In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the real symbols.
+In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the Haifa Bay air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the real symbols.
 Among the center subjects, only `r ((filter(SVIVA2_01_center,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==0)%>%nrow())*100)%>%round(1)`% of the no symbols group reported a trust score lower than 2 in the first place, and this percentage dropped to `r ((filter(SVIVA2_01_center,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_center,SYMBOL==2)%>%nrow())*100)%>%round(1)`% among the real symbols group.
@@
 
-**Air-pollution policy** (Reducing the air-pollution in the Haifa Bay)
+**Haifa Bay air-pollution policy** (Reducing the air-pollution in the Haifa Bay)
 

### 2019-07-26 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 For the recycling policy, I used the same image from EPM's reusable bags campaign, while replacing Rosenblum's face with the face of the unfamiliar model, and changing the color of the bag from green to blue.
-For the Air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman).
+For the Haifa Bay air-pollution policy, I took the purchased image of the unfamiliar model, and added a blue rectangle behind him (instead of the green background behind Friedman).
 I also added a blue geometric shape above the person's head, which I took from a logo of an Israeli mortgage bank, against Friedman's green hair.
@@
 
-[^footnote_sources_fake_models]: The original photo for the air-pollution policy was purchased from the following link: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336, The original photo for the recycling policy was purchased from the following link:
+[^footnote_sources_fake_models]: The original photo for the Haifa Bay air-pollution policy was purchased from the following link: https://www.istockphoto.com/il/photo/smiling-forty-something-man-gm469597956-62477336, The original photo for the recycling policy was purchased from the following link:
 https://www.istockphoto.com/il/photo/young-man-smiling-portrait-gm516728601-48347532
@@
 In addition, perceived personal relevance was measured only through the comparison between the areas (i.e.
-without the relevance manipulation), and the information was manipulated only with regard to the air-pollution policy.
+without the relevance manipulation), and the information was manipulated only with regard to the Haifa Bay air-pollution policy.
 Despite these weaknesses, the survey included specific questions about the affect and symbolic associations of the logos and the colors, which provide valuable descriptive data.[^footnote_prior_survey_1] In this survey, the participants were assigned to one of three conditions of symbols: real symbols, fake symbols and no symbols.
@@
 
-[^footnote_prior_survey_1]: Overall, the findings of this limited prior study are consistent Consistent with the findings of the main experiment, reported in the paper.
+[^footnote_prior_survey_1]: Overall, the findings of this limited prior study are consistent with the findings of the main experiment, reported in the paper.
 The effect of the real symbols were greater among those who reside in the Haifa-Bay.
 Congruently, the statistical analyses yielded a negative and significant interaction between the real symbols and residence in the center.
-Also consistent with the main experiment, the interaction between the areas and the information manipulation was not significant.
+Also, consistently with the main experiment, the interaction between the areas and the information manipulation was not significant.
 
@@
 
-Air-pollution policy
+Haifa Bay air-pollution policy
 
@@
   scale_shape_manual(name="Order",values=c(19,1), labels = c("First","Second"))+
-  scale_x_discrete(name="Policy",labels=c("Air-pollution","Recycling"))+
+  scale_x_discrete(name="Policy",labels=c("Haifa Bay Air-pollution","Recycling"))+
   scale_y_continuous(name = "Trust in policy",breaks = seq(1,7,by=0.5))
@@
 Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans.
-Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative.
-The interpretation of this interaction suggests that the priming questions slightly decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, and increased it among those who reside in the Center.
+Regarding the Haifa Bay air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative.
+The interpretation of this interaction suggests that the priming questions slightly decreased the perceived personal relevance of the Haifa Bay air-pollution policy among Haifa-Bay subjects, and increased it among those who reside in the Center.
 Regarding the recycling policy, the interaction is insignificant.
@@
           column.separate = c(2,2,2,2,2,2),
-          dep.var.labels=c("Air-pollution policy","Recycling policy"),
+          dep.var.labels=c("Haifa Bay air-pollution policy","Recycling policy"),
           omit = control.vars,
@@
             digits = 3,
-            covariate.labels = c("1. Trust in Air-pollution policy",
+            covariate.labels = c("1. Trust in Haifa Bay air-pollution policy",
                                  "2. Trust in recycling policy",
@@
           select(-variable)) %>% 
-  mutate(variable = c("Air-pollution policy","Recycling policy"))
+  mutate(variable = c("Haifa Bay air-pollution policy","Recycling policy"))
 
@@
 
-*Table A4*
+**Table A4**
 
@@
 For the first proxy, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`).
-The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
+The data confirms that residents of these closer cities tended to perceive the Haifa Bay air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`).
 As for the second proxy, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise.
@@
 
-**Table A5: Regression analyses – policy presented first of order.**
+**Table A5: Regression analyses – policy presented first of order**
 
@@
           column.separate = c(2,2,2),
-          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
+          dep.var.labels=c("Trust in Haifa Bay air-pollution policy","Trust in recycling policy"),
           covariate.labels=c("Real symbols",
@@
           column.separate = c(2,2),
-          dep.var.labels="Trust in air-pollution policy",
+          dep.var.labels="Trust in Haifa Bay air-pollution policy",
           omit = control.vars,
@@
 
-**Table A7: Regression analyses – trust in air-pollution policy (unfiltered sample).**
+**Table A7: Regression analyses – trust in Haifa Bay air-pollution policy (unfiltered sample)**
 
@@
 
-**Table A8: Regression analyses – trust in recycling policy (unfiltered sample).**
+**Table A8: Regression analyses – trust in recycling policy (unfiltered sample)**
 
@@
 
-**Table A9: Regression analyses – experimental manipulation of perceived personal relevance (unfiltered sample).**
+**Table A9: Regression analyses – experimental manipulation of perceived personal relevance (unfiltered sample)**
 
@@
                              mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
-          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients.
-Robust standard errors are in parentheses and *p-values* (two-tailed) are reported.
-The reference category for the symbols manipulation conditions is the control (no symbols).",
+          notes = "",
           notes.append = FALSE)

### 2019-07-27 paper3_APPENDIX_revision_01.Rmd
Add files via upload

@@
 To reiterate, half of the participants saw a weak plan first, and thereafter a strong plan, and for the other half it was the opposite.
-Hence, I examined whether the the strong policy was evaluated differently when it was presented first (which means that participants at that point did not sea weak policy yet and did not question the reliability of the survey), then when it was presented second (after they already saw a fictional policy).
+Hence, I examined whether the strong policy was evaluated differently when it was presented first (which means that participants at that point did not see a weak policy yet and did not question the reliability of the survey), then when it was presented second (after they already saw a fictional policy).
 This comparison, across the two policies, is graphically presented in the following plot.

### 2019-07-27 paper3_revision_text.Rmd
Add files via upload

@@
       toc_depth: 3
-link-citations: yes
+  pdf_document:
+    toc: yes
+  word_document: default
+link-citations: no
 bibliography: phd_paper_2.bib
@@
 
-*Recent studies demonstrated the potency of government branding to positively affect citizens' judgments of government organizations and policies.
-This study explores the boundaries of governments' persuasion of citizens through branding and symbolic communications.
-The latter is important given the the detrimental implications of the emotive effect of symbols, mainly its ability to compensate for organizations' poor functioning, and to elicit undue trust.
-Building on social psychology, I hypothesize that citizens are less susceptible to persuasion by symbolic communication, the more they perceive the policy issue in the communication as personally relevant.
-I test this expectation through a survey experiment, focused on air-pollution policy, utilizing natural variation in the perceived personal relevance between citizens residing in a polluted area and elsewhere.
-Contrary to my expectations, the results indicate that even high levels of perceived personal relevance do not attenuate the symbols' effect, which entails that the boundaries of persuasion through symbols are wider than expected.*
+*Recent studies have demonstrated the potency of government branding to positively affect citizens' judgments of government organizations and policies.
+Additionally, studies have pointed to the detrimental implications of the emotive effect of symbols, mainly its ability to compensate for organizations' poor functioning, and accordingly to elicit undue trust.
+In light of these concerns, this study explores the boundaries of governments' persuasion of citizens through branding and symbolic communications.
+Building on social psychology and marketing research, I hypothesize that citizens are less susceptible to persuasion by symbolic communication, the more they perceive the policy issue in the communication as personally relevant.
+I test this expectation through a survey experiment, focused on air-pollution policy in Israel, exploiting the natural variation in the perceived personal relevance between citizens residing in a polluted area in the country and others.
+The results consistently indicate that even high levels of perceived personal relevance do not significaly attenuate the effect of symbols, which entails that the boundaries of persuasion and manipulation through branding are wider than expected.*
 
@@
 Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather then on uncontious emotive responses.
-A yet more serious concern regards the potency of symbolic communication to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017; @alonbarkat_2018].
+A yet more serious concern regards the potency of symbolic communication to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017] AUTHOR.
 Congruently, government branding can yield a misalignment between citizens' positive view and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
@@
 In this paper, I focus on those methodological and empirical parts of the study that are consequential for the examination of the moderating role or perceived personal relevance.
-A summary statistics and correlation of all variables, as well as the full survey are available in the supplementary Appendix, and replication materials are available in a github repository [url to be added upon publication].
+A summary statistics and correlation of all variables, as well as the full survey are available in the supplementary Appendix (sections 5, 8), and replication materials are available in a github repository [url to be added upon publication].
 
@@
 Accordingly, I selected the major cities in the Haifa Bay area (*Haifa*, *Nesher*, *Qiryat-Hayiim*,[^footnote_qiryat-Hayiim] *Qiryat-Bialik*, *Qiryat-Mozkin*, *Qiryat-Ata* and *Qiryat-Yam*), and matched them with citizens from cities with a similar profile and population size at the center of the country (*Natania*, *Petach-Tikva* and *Rishon-Lezion*).
-The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section ##).
+The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section 1).
 I further searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.
@@
 
-[^footnote_unfiltered_sample]: In the supplementary appendix, I replicate the main models on the unfiltered sample, with no significant change to the results.
+[^footnote_unfiltered_sample]: In the supplementary appendix, I replicate the main models on the unfiltered sample, with no significant change to the results (section 7).
 
@@
 The symbols conditions are displayed in **Appendix B**.
-Further details about the real and fake symbols are found in section ## of the supplementary appendix.
+Further details about the real and fake symbols are found the supplementary appendix (section 2).
 
@@
 [^footnote_reliability_information_manipulation]: A possible concern about that design is that participants would question the reliability of the weak policy.
-I assess that concern in the supplementary appendix (section ##).
+I assess that concern in the supplementary appendix (section 3.2).
 
@@
 As for the interactions with the relevance manipulation (among Haifa Bay respondents), I estimate that the detectable coefficients of their interactions with the symbols and information conditions are 0.36 and 0.29 SDs, respectively.
-The power estimations are reported in details in Section ## of the supplementary appendix.
+The power estimations are reported in details in the supplementary appendix (Section 4).
 
@@
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
-The results of all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables.
+The results of all manipulation and validation checks are available from the supplementary appendix, along with summary statistics and correlation matrix for all variables (sections 3, 5).
 
@@
 
-[^footnote_raw_means]: Means and SDs of outcome variables across the two areas and the experimental conditions are reported in section XX of the supplementary appendix.
+[^footnote_raw_means]: Means and SDs of outcome variables across the two areas and the experimental conditions are reported in section XX of the supplementary appendix (section 6).
 
@@
 
-I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix.
+I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix (section 7).
 *First*, I replicate the main models while restricting the analyses to the first policy seen by the participants.
@@
 as in the case of center subjects).
-In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A second explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' prior beliefs on their judgments of the policy plans, an effect that can be related to motivated reasoning [@taber_2006; @christensen_2018; @baekgaard_2016].
-It can be theorized that symbols attenuate motivated reasoning, when symbolic associations are not strongly related to identities of specific groups having strong prior positions on the policy or the organization (as in the case of the EPM symbols and the Haifa Bay locals).
-On the other hand, when symbolic associations do activate such group identities, they are likely to exacerbate partisan motivated reasoning in that regard, and polarization [@teodoro_2018].
-For instance, it is possible that EPM "green" symbols enhance partisan motivated reasoning among groups divided on their support for environmental policy.
-Certainly, we must be cautious about these tentative explanations, which may be tested by future studies.
+In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A second explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' negative prior beliefs on their judgments of the policy plans.
+Accordingly, theoretically there could be an interaction between the emotive effect of symbols and citizens' prior positions embedded in their group affiliation and social identities (in our case, the local identity of Haifa Bay residents).
+I theorize, tentatively, that the direction of the interaction depends on whether or not the symbolic associations are related to the relevant group identities.
+When the symbols are not strongly linked to identities of specific groups having strong prior positions on the policy or the organization (as in our case) symbols would attenuate the influence of the prior beliefs on people's judgements.
+Conversely, when symbolic associations activate group identities and make them more salient, they may enhance the effect of dominant positions embedded in them, and increase polarization between parties [@teodoro_2018].
+These theoretical expectations may also have important implications on citizens'  motivated reasoning and biased processing of new information and messages [@taber_2006; @christensen_2018; @baekgaard_2016; @james_2017a].
+Hence, future reseasrch may further examine the interactions between different types of symbols and citizens' prior beliefs and motivated reasoning.
 

### 2019-07-29 paper3_revision_text.Rmd
Add files via upload

@@
 I test this expectation through a survey experiment, focused on air-pollution policy in Israel, exploiting the natural variation in the perceived personal relevance between citizens residing in a polluted area in the country and others.
-The results consistently indicate that even high levels of perceived personal relevance do not significaly attenuate the effect of symbols, which entails that the boundaries of persuasion and manipulation through branding are wider than expected.*
+The results consistently indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols, which entails that the boundaries of persuasion and manipulation through branding are wider than expected.*
 
@@
 
-Public Administration scholarship has recently shown a growing interest in public sector branding, and its potency to influence citizens' perceptions and direct their behaviour [@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015].
-Recent behavioural studies established that symbolic, brand elements entangled in government communications (e.g.
+Public Administration scholarship has shown a growing interest in public sector branding, and its potency to influence citizens' perceptions and direct their behaviour [@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015].
+Congruently, recent behavioural studies established that symbolic, brand elements entangled in government communications (e.g.
 brand names, logos, colors and figures) can have a positive emotional effect on citizens, which leads them to view public organizations and their policies and services more favourably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
-This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade, in part due to the expension of ditigal communication platforms and the use of social media [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
+This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade or so, in part due to the vast expansion of ditigal communication and social media [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
 
 The ability of government organizations to modify citizens' attitudes via such symbolic communications can be perceived favorably, insofar as it mitigates citizens' distrust in organizations and underevaluation of their performance.
-Accordingly, Symbolic communications, as opposed to mere factual information and substantive arguments, may enable organizations to overcome citizens' negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
+Accordingly, symbolic communications, as opposed to the delivery of mere factual information and substantive arguments, may enable organizations to overcome citizens' negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
 Nonetheless, this form of persuasion is also highly problematic.
 Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather then on uncontious emotive responses.
-A yet more serious concern regards the potency of symbolic communication to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017] AUTHOR.
-Congruently, government branding can yield a misalignment between citizens' positive view and the "real world", which would undermine the democratic accountability and responsiveness of public organizations.
-Moreover, government agencies and/or politicians controlling them could use branding symbolic communication strategically as an instrument of propaganda, seeking to manipulate public opinion and mitigate justified public criticism of agencies' failures.
+A yet more serious concern regards the potency of symbolic communication to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017, AUTHOR].
+Congruently, government branding can yield a misalignment between citizens' positive view and the "real world", which would undermine governments' democratic accountability and responsiveness.
+Moreover, government agencies and/or politicians controlling them could use branding and symbolic communication strategically as an instrument of propaganda, seeking to manipulate public opinion and mitigate justified public criticism of agencies' failures.
 
 The abovementioned concerns of the negative implications of branding for democracy are the main motivation of this study.
-These concerns necessitate a better theoretical understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, which would enable to asses more effectively the scope of the risk that these practices pose for democracy.
+These concerns necessitate a better theoretical understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, which would enable us to asses more effectively the scope of the risk that these practices pose for democracy.
 In line with this motivation, this study focuses of an importnant potential limitation that regards the perceived personal relevance of the policy issue.
 I explore whether the effect of symbolic elements in communications is restricted to policy issues that are not perceived by citizens as having a significant consequence for their personal lives, or rather that citizens are similarly susceptible to persuasion via branding even with regard to such personally relevant issues.
-This factor is particularly important, since we tend to expect these affected groups to pay more attention to government actions that concern their interests, and to hold them to account for their consequences to a greater extent.
+This moderating factor is particularly important, since we tend to expect these affected groups to pay more attention to government actions that concern their interests, and to hold them to account for their consequences to a greater extent.
 That expectation can be supported, theoretically, by the social psychology theory Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
@@
 Employing a survey experiment, I test this latter theoretical expectation in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific geographical area -- the Haifa Bay.
-The research sample (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to air-pollution.
-I present all participants a policy plan regarding the air-pollution in the Haifa Bay area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and content (logically persuasive versus unpersuasive policy plans).
-I examine the effects of these manipulations on participants' trust in the policy plan accross the two areas, and test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the substantive differences).
+The research sample (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to high levels of air-pollution.
+I present all participants a policy plan regarding the air-pollution in the Haifa Bay area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and substantive information (logically persuasive versus unpersuasive policy plans).
+I examine the effects of these manipulations on participants' trust in the policy plan accross the two areas, and test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the differences in substantive arguments).
 I further supplement this observational comparison between the areas with an experimental treatment for the perceived personal relevance of the policy, and with additional robustness tests.
 
-Contrary to my initial expectations, the results indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols on citizens' trust.
+Contrary to my initial expectations, the results consistently indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols on citizens' trust.
 These findings tend to suggest that the boundaries of the effect of symbolic communication are wider than expected.
@@
 Branding, therefore, can be considerred a form of symbolic communication.
-In practice, symbolic elements that are strategically selected and designed to evoke positive emotions and associations, can be found in almost every government communication with citizens.
+In practice, symbolic elements that are strategically designed to evoke positive emotions and associations, can be found in almost every government communication with citizens.
 
@@
 As for those who are located at the low end of that continuum, also called "peripheral route", persuasion may occur mainly through processes that require little ammount of thinking, such as evaluative conditioning.
-Another example for peripheral route processing is people's reliance on the message source as a heuristic cue [@james_2017a].
+Another prominent example for peripheral route processing is people's reliance on the message source as a heuristic cue [@james_2017a].
 When people are located between the two ends of the continuum, a mixture of these persuasion processes will operate.
@@
 That variable has been considered the most important determinant of motivation to scrutinize the message [@petty_2002; @petty_2011].[^footnote_elm_factors] It has been theorized that the more people perceive an issue as personally relevant, the more motivated they are to invest in thinking about it, since the consequences of being incorrect are greater [@petty_1979; @petty_1981; @petty_1983; @johnson_1989; @petty_1990; @burnkrant_1989].
-Accordingly, experimental studies have showed that individuals are more affected by peripheral cues and less affected by argument quality, the less they perceive the issue as personally relevant.
+Accordingly, experimental studies in marketing and social psychology have showed that individuals are more affected by peripheral cues and less affected by argument quality, the less they perceive the issue as personally relevant.
 
@@
 The results of the study indicated that the celebrity endorser had a positive effect on participants' attitudes about the product under the low personal relevance condition (estimated as roughly 0.7 SDs), but had no effect under the high personal relevance condition.
-Likewise, the effect of argument quality was greater for the high personal relevance group (1.95 SDs versus 0.54 SDs in the low personal relevance group).
+Likewise, the effect of argument quality was more than three times greater for the high personal relevance group.
 
@@
 A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
-Thereafter, I filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to following criteria: multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and reported age under 18 (n=`r filter_age`).
+I further filtered out `r N_0-N_1` observations (`r round(((N_0-N_1)/N_0)*100,1)`%) due to following criteria: multiple entries from the same IP address (n=`r filter_IP`), failure at the instructional manipulation test (n=`r filter_IMC`), submitting the survey in less than 3 or more than 30 minutes (n=`r filter_time`), and reported age under 18 (n=`r filter_age`).
 These filters are neither associated with the areas nor with the experimental conditions.
@@
 After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance manipulation).
-Subjects in the relevance treatment group were asked three questions about their interest in environmental policy issues, the extent to which they follow these issues in the media, and their preference for more/less government investment in this field.
-Then, they were asked to describe the most acute environmental issue in their area of residence.
-These treatment questions were designed to prime those residing in the Haifa Bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
+Subjects in the relevance treatment group were asked three questions about their perceptions of environmental policy in general.
+They were then asked to state their area  and locaity of residence, and to describe, in their own words, the most disturbing environmental issue in their area.
+These questions were designed to prime those residing in the Haifa Bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
 
-[^footnote_relevance_manipulation]: The first three treatment questions were also initially designed to prime subjects, more generally, to think about the impact of environmental issues to their own lives.
-In this paper, I focus on the the moderating effect of the relevance manipulation on Haifa Bay citizens' responses to the Haifa Bay air-pollution policy.
+[^footnote_relevance_manipulation]: The first three questions are: "To what extent are you interested in environmental issues?"; "To what extent do you follow environmental issues in the media and/or in social networks?"; "Compared to the current situation, do you think the government should invest more or less in dealing with environmental issues?" These questions were initially designed to prime participants to think not only about the relevance of the Haifa Bay air-pollution, but of environmental issues general.
+Yet, I focus here on the moderation of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.
 
-Participants were then presented with the air-pollution and recycling policy plans (displayed in a random order).
-They were informed that these plans were obtained from EPM's annual work plan.
+Participants were then presented with the two policy plans (Haifa Bay air-pollution and recycling), displayed in a random order.
+They were informed that these plans were obtained from EPM's annual work plan for the following year.
 The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
@@
 The second element is the green color, which is strongly associated with taking care of the environment.
-The third element is an image of a celebrity comedian from an advertising campaign of the EPM.
+The third element is the images of celebrity comedians from advertising campaigns of the EPM.
 The Haifa Bay air-pollution policy (in the real symbols condition) was presented with an image from EPM campaign from 2010 under the slogan "starting to think green", starring the Israeli celebrity comedian Tal Friedman.
@@
 Accordingly, I specifically designed the "fake" symbols so that they would resemble the real symbols and have equivalent aesthetic qualities, without activating particular emotions and associations related to EPM, or environmental policy.
-The symbols conditions are displayed in **Appendix B**.
+Hence, these elements can be also regarded as peripheral cues (according to ELM conceptualization), yet they do not represent familiar symbols of EPM.
+The symbols conditions are displayed in **Appendix A**.
 Further details about the real and fake symbols are found the supplementary appendix (section 2).
@@
 For instance, a subject who first received a strong Haifa Bay air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
-The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix A**.
+The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix B**.
 
@@
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas.
-As expected, the Haifa Bay air-pollution policy is perceived as more personally relevant by Haifa Bay residents compared with center residents  (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]).
+As expected, the Haifa Bay air-pollution policy is perceived as more personally relevant by the local residents compared with those residing in the center (Cohen's D = `r relevance.areas.d[["estimate"]] %>% round(2)` [`r relevance.areas.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.areas.d[["conf.int"]][["upper"]] %>% round(2)`]).
 By comparison, the recycling policy is perceived by both groups as relatively personally relevant by both groups, with no statistically significant differences between them.
-Additional support for these differences are provided by respondents' answers to the open question about the most salient environmental issue in their area of residence, which was presented to the relevance treatment group (i.e.
-before presenting the policy plans).
-Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%).[^footnote_air_relevance_coding] Moreover, many Haifa Bay respondents explicitly linked the air-pollution to higher morbidity rates in their area.
+Additional support for these differences are provided by respondents' answers to the open question presented to the relevance treatment group about the most salient environmental issue in their area of residence.
+Indeed, `r t1<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow()``r t1` of the `r t2<-SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow()``r t2` Haifa Bay subjects who were asked this question regarded in their responses to the air-pollution generated from the industrial area (`r air.content.percent.haifa <- t1/t2*100``r air.content.percent.haifa %>% round(0)`%),[^footnote_air_relevance_coding] and many of them explicitly linked it to higher morbidity rates in their area.
 Subjects from center cities regarded to a variety of issues, including recycling, traffic jams and cleanliness, and only `r ((SVIVA2_01_center %>% filter(RELEVANCE_exp==1,air.content==1) %>% nrow())/nrow(SVIVA2_01_center)*100) %>% round(0)`% of them mentioned air-pollution as a prominent environmental concern in their area.
@@
 As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa Bay respondents' perceptions of personal relevance of the air-pollution policy.
-In fact, those assigned to the treatment group reported sightly lower level of personal relevance on average, yet these differences are not statistically significant (*t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
+The Haifa Bay participants assigned to the treatment group reported sightly lower level of personal relevance on average, yet these differences are not statistically significant (Cohen's D = `r relevance.exp.d[["estimate"]] %>% round(2)` [`r relevance.exp.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.exp.d[["conf.int"]][["upper"]] %>% round(2)`], *t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
@@
 Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]) %>% abs() %>% round(.,3)`).
-The increase in the lower bound of the box in the real symbols shows that real symbols greatly reduced the number of participants who reported very low trust score.
+The increase in the lower bound of the box in the real symbols shows that real symbols reduced to a great extent the number of participants who reported very low trust score.
 Descriptively, `r ((filter(SVIVA2_01,SYMBOL==0,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==0) %>% nrow()) *100) %>% round(1)`% of the participants in the no symbols group reported a score of 2 or less which indicates very low level of trust, compares with `r ((filter(SVIVA2_01,SYMBOL==1,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==1) %>% nrow()) *100) %>% round(1)`% and only `r ((filter(SVIVA2_01,SYMBOL==2,TRUST_air_INDEX<=2) %>% nrow())/(filter(SVIVA2_01,SYMBOL==2) %>% nrow()) *100) %>% round(1)`% in the real symbols group.
@@
 
-[^footnote_raw_means]: Means and SDs of outcome variables across the two areas and the experimental conditions are reported in section XX of the supplementary appendix (section 6).
+[^footnote_raw_means]: Means and SDs of outcome variables across the two areas and the experimental conditions are reported in the supplementary appendix (section 6).
 
@@
 I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
-I regress trust in Haifa Bay air-pollution policy on the manipulations (Model `r table.x`.1), then I add the areas (Model `r table.x`.2) and the interaction between them (Model `r table.x`.3).
-In Model `r table.x`.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
-In Models `r table.x`.3, `r table.x`.4 the interactions between living in the center and the real symbols are negative but not sufficiently significant, and the interactions with the weak information are insignificant.
-A comparison between models `r table.x`.2 and `r table.x`.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
+I regress trust in Haifa Bay air-pollution policy on the manipulations (Model 1.1), then I add the areas (Model 1.2) and the interaction between them (Model 1.3).
+In Model 1.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
+In Models 1.3, 1.4 the interactions between living in the center and the real symbols are negative but and significant at the 90% level, and the interactions with the weak information are insignificant.
+A comparison between models 1.2 and 1.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
 
@@
 
-Overall, the findings with regard to the Haifa Bay air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
-Still, as discussed in the previous section, this analysis is based on the observational comparison between the areas and not by a random assignment, and hence a concern of endogeneity cannot be entirely ruled.
+In summary, the findings with regard to the Haifa Bay air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
+Still, as discussed in the methodology section, this analysis is based on an observational comparison, and hence a concern of endogeneity cannot be entirely ruled.
 Accordingly, the null findings regarding the interactions between the areas and the manipulations can be resulted by other, unobserved differences between the two populations.
-Yet, as explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two groups, and the relevance manipulation.
+Yet, as explained, the experimental design provides two additional tests which enable to address this concern: the comparison to the recycling policy, for which there are no relevance differences between the two areas, and the relevance manipulation.
 I now discuss the results of these two tests.
@@
 Notice that Haifa Bay subjects reported lower trust on that policy as well, which may indicate that they their negative perceptions about the Ministry's actions regarding the air-pollution in their area shapes their general perceptions of the Ministry.
-The directions of the simple effects and interaction terms remain, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbols, and the two areas responded similarly to the differences in the information.
+The directions of the simple effects and interaction terms remain intact, while the main effects and conditional effects are smaller and less significant.[^footnote_recycling_model] Consistently with the air-pollution policy, Haifa Bay subjects were more affected by the symbols, and the two areas responded similarly to the differences in the information.
 The fact that similar patterns are observed across the these policies further weakens the hypotheses regarding the moderating role of personal relevance.
@@
 The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
-In model 2.5, the interaction between weak information and the center area is positive, but far from significance.
 
@@
 Next, `r table.x=table.x+1`**Table `r table.x`** presents the interaction between the relevance manipulation and the symbols and information manipulations.
-In Model `r table.x`.1, I regress trust in Haifa Bay air-pollution policy on the three manipulations, then in Model `r table.x`.2 I add the interaction between the relevance manipulation and the symbols and information manipulations, and in Model `r table.x`.3 I add controls.
+In Model 3.1, I regress trust in Haifa Bay air-pollution policy on the three manipulations, then in Model 3.2 I add the interaction between the relevance manipulation and the symbols and information manipulations, and in Model 3.3 I add controls.
 In all these models, the coefficient of the relevance treatment is negative but far from significance.
 The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the incerase in trust due to the appearance of the symbols and those who did not were slightly smaller.
-However, these interaction coefficients are relatively weak and far from significance (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).
-The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1]
+However, these interaction coefficients are far from significance and relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).
+The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1] Hence, these analyses also do not lend sufficient support for the hypotheses.
 
@@
 Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa Bay subjects.
-Still, we can assess that even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols is estimated based on Model `r table.x`.2 as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
+Still, we can assess that even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols can be estimated as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`] (based on Model based on Model 3.2).
 Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] Overall, this indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area were positively affected, at least to some degree, by familiar symbols of the ministry.
@@
 
-I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix (section 7).
+Finally, I further explored the robustness of these findings through additional analyses, reported in the supplementary appendix (section 7).
 *First*, I replicate the main models while restricting the analyses to the first policy seen by the participants.
-This enables to rule out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
+This enables me to rule out the possibility that subjects' responses are affected by the manipulations in the first policy presented to them (a carryover effect), or by their evaluation of the it (assimilation or contrast effects).
 *Second*, I restrict the analyses to Haifa Bay residents, and compare between those who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects city of residence, and its geographical proximity to the polluting industrial area; (b) parents for young children.
@@
 Contrary to my expectations, and those of extant research in social psychology and marketing, I did not find that higher levels of perceived personal relevance attenuate the effect of symbols.
-While subjects residing in the polluted Haifa Bay reported in the survey that they perceive the governmental policy for reducing air-pollution in that area as highly relevant for their lives, they were similarly, and perhaps even more affected by the appearance of familiar brand elements of the environmental protection ministry in the communication of that policy plan.
+While subjects residing in the polluted Haifa Bay reported in the survey that they perceive the governmental policy for reducing air-pollution in that area as highly relevant for their lives, they were similarly, and perhaps even more affected by the appearance of familiar brand elements of the Environmental Protection Ministry in the communication of that policy plan.
 Congruently, they did not pay more attention to the substantive content of the policy plan.
-Furthermore, the results indicate that even priming Haifa Bay residents to think about the personal relevance of the air-pollution did not significantly attenuate their susceptibility to persuasion by the symbols.
+Furthermore, I find that even priming Haifa Bay residents to think about the personal relevance of the air-pollution did not significantly attenuate their susceptibility to persuasion by the symbols.
 
@@
 One plausible explanation is that despite the relatively high involvement of Haifa Bay residents, they were still not motivated enough to rely only on the central route and disregard the peripheral cues.
-If this explanation holds, it entails that citizens may resist the emotional effect of symbols only in rare circumstances, which are characterized by extremely high levels of personal relevance -- policies that have immediate, tangible and unambiguous consequences for citizens well-being.
+If this explanation holds, it entails that citizens may resist the emotional effect of symbols perhaps only in rare circumstances, which are characterized by extremely high levels of personal relevance -- policies that have immediate, tangible and unambiguous consequences for citizens well-being.
 Indeed, social psychology ELM scholars Petty and Cacioppo have acknowledged that the high and low personal relevance conditions generated in their experimental settings were deliberately created for theory testing purposes, and can be rarely found in the world outside the laboratory [@petty_1986, p.
@@
 Rather, I tentatively suggest two other possible explanations for that.
-First, these patterns could be the result of the higher intercept of center residents' trust in EPM policies, or a ceiling effect.
+*First*, these patterns could be the result of the higher intercept of center residents' trust in EPM policies, or a ceiling effect.
 More generally, it could be the case that symbolic elements are more effective in shifting people from low to medium levels of trust (i.e.
 as in the case of Haifa Bay subjects), than shifting them from medium to high levels (i.e.
-as in the case of center subjects).
-In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A second explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' negative prior beliefs on their judgments of the policy plans.
-Accordingly, theoretically there could be an interaction between the emotive effect of symbols and citizens' prior positions embedded in their group affiliation and social identities (in our case, the local identity of Haifa Bay residents).
+as in the case of center subjects, and the recycling policy).
+In other words, symbols may be more effective in reducing citizens' distrust, then increasing their trust.[^footnote_ceiling_effect] A *second* explanation could be that EPM symbols attenuated the effect of Haifa Bay residents' negative prior beliefs on their judgments of the policy plans.
+Accordingly, there could be an interaction between the emotive effect of symbols and citizens' prior positions embedded in their group affiliation and social identities (in our case, the local identity of Haifa Bay residents).
 I theorize, tentatively, that the direction of the interaction depends on whether or not the symbolic associations are related to the relevant group identities.
-When the symbols are not strongly linked to identities of specific groups having strong prior positions on the policy or the organization (as in our case) symbols would attenuate the influence of the prior beliefs on people's judgements.
+When the symbols are not strongly linked to identities of specific groups having strong prior positions on the policy or the organization, as in this case, symbols would attenuate the influence of the prior beliefs on people's judgements.
 Conversely, when symbolic associations activate group identities and make them more salient, they may enhance the effect of dominant positions embedded in them, and increase polarization between parties [@teodoro_2018].
-These theoretical expectations may also have important implications on citizens'  motivated reasoning and biased processing of new information and messages [@taber_2006; @christensen_2018; @baekgaard_2016; @james_2017a].
-Hence, future reseasrch may further examine the interactions between different types of symbols and citizens' prior beliefs and motivated reasoning.
+An interaction between symbols and citizens' prior beliefs may also suggest that symbols can affect citizens' susceptibility to motivated reasoning and biased processing of new information [@taber_2006; @christensen_2018; @baekgaard_2016; @james_2017a].
+Hence, future research may further examine the interactions between different types of symbols and citizens' prior beliefs and motivated reasoning.
 
-[^footnote_ceiling_effect]: This explanation is supported by the comparison of the percentages of subjects who reported very low levels of trust in the policies.
-This comparison consistently shows a pattern of decreased marginal reduction.
+[^footnote_ceiling_effect]: This explanation is supported by the comparison of the percentages of subjects who reported very low levels of trust in the two policies.
 In the Haifa Bay, the percentage of those who reported a trust score of less than 2 in the Haifa Bay air-pollution policy decreased from `r ((filter(SVIVA2_01_haifa,SYMBOL==0,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==0)%>%nrow())*100)%>%round(1)`% in the no symbols group to `r ((filter(SVIVA2_01_haifa,SYMBOL==2,TRUST_air_INDEX<2) %>% nrow())/(filter(SVIVA2_01_haifa,SYMBOL==2)%>%nrow())*100)%>%round(1)`% in the real symbols.
@@
 Still, several limitations of this study should be acknowledged.
-The study focuses on one policy domain, and on a specific, local issue.
+The study focuses on one policy domain -- environmental policy, and on a specific issue -- air-pollution in a specific area.
 Future studies may put these findings to further test by exploring cases of air-pollution in other locations, as well as by exploring cases of other environmental policies, and other domains.
@@
 Future studies may conduct more rigorous investigations through natural experimental or quasi-experimental designs that could take advantage of particular cases of citizens' random allocation to varying levels of personal relevance.
-Finally, whereas this study includes an experimental manipulation for perceived personal relevance, I acknowledge the limitations of that test, namely its limited statistical power and the fact that the survey data does not confirm the effectiveness of the manipulation in altering the moderating variable.
+Finally, whereas this study includes an experimental manipulation for perceived personal relevance, I acknowledge the limitations of that test, namely its statistical power and the fact that the survey data does not confirm the effectiveness of the manipulation in altering the moderating variable.
 Therefore, future studies may explore different, possibly stronger experimental manipulations for perceived personal relevance.
@@
 Alongside the benefits of this instrument in mitigating citizens' distrust, it also has the potency to yield a distorted, emotive, overoptimistic view of government organizations and their policies, which may undermine basic democratic accountability mechanisms.
+These concerns become even more prevalent and serious in the age of digital communication and artificial intelligence technologies, which enable organizations to engage with targeted audiences much more easily, and to adapt messages and symbols to groups and individuals in a manner that would trigger their emotions more effectively.
 For good or for ill, citizens are affected by the emotional connections and associations of symbols.
 
-## Appendix A: Information manipulation
+<br>
+
+## Appendix A: Symbols manipulation
+![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/symbols_manipulation.png)
+
+<font size="0.5">
+
+*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*
+
+</font>
+
+<br>
+
+## Appendix B: Information manipulation
 
@@
 
-## Appendix B: Symbols manipulation
-![](C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper3_PA/revision/myfigures/symbols_manipulation.png)
-
-<font size="0.5">
-
-*Note: The policy plans communications presented here are the strong policies, in the version adjusted for mobile interface.*
-
-</font>
-
-<br>
-
 # References

### 2019-07-29 SVIVA_exp2_dm_03.R
Add files via upload

@@ -503,7 +503,9 @@ mutate(RECOGNIZE_waste_real = SVIVA2_raw$Q25.6+
  
   mutate(close.industrial.area = ifelse(CITY_reside_en %in% c("NESHER","QIRYAT HAIM","QIRYAT BIALIK"),1,0)) %>%  
   mutate(AREA_center = Recode(AREA,"0=1;1=0"),
-         SYMBOL_t = Recode(SYMBOL,"1=2;2=1"))
+         SYMBOL_t = Recode(SYMBOL,"1=2;2=1"),
+         SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
+         SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")))
 
 
 ####Datasets#####
@@ -562,17 +564,15 @@ SVIVA2_01_comb = SVIVA2_01 %>%
                                        ELABORATION_waste_time_log),
          MEMORY_score = ifelse(policy=="TRUST_air_INDEX",MEMORY_air_score,
                                MEMORY_waste_score),
-         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",RELEVANCE_air_obs,
+         RELEVANCE_obs = ifelse(policy=="TRUST_air_INDEX",RELEVANCE_air_obs,
                                    RELEVANCE_waste_obs),
-         RELEVANCE_obs = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
+         ELABORATION_time = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time,
                                 ELABORATION_waste_time)) %>% 
   mutate(TRUST_air_INDEX = ifelse(policy=="TRUST_air_INDEX",trust,NA),
          TRUST_waste_INDEX = ifelse(policy=="TRUST_waste_INDEX",trust,NA),
-         INFORMATION_weak = Recode(INFORMATION,"0=1;1=0"),
-         SYMBOL_t.r = factor(Recode(SYMBOL,"0=2;2=1;1=0")),
-         SYMBOL_t.r_2 = factor(Recode(SYMBOL,"0=2;2=0")),
          ORDER = ifelse(policy=="TRUST_air_INDEX",AIR_order,WASTE_order),
[…]

### 2019-07-29 paper3_revision_text.Rmd
Add files via upload

@@
       toc_depth: 3
-  pdf_document:
-    toc: yes
-  word_document: default
 link-citations: no
@@
 I test this expectation through a survey experiment, focused on air-pollution policy in Israel, exploiting the natural variation in the perceived personal relevance between citizens residing in a polluted area in the country and others.
-The results consistently indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols, which entails that the boundaries of persuasion and manipulation through branding are wider than expected.*
+The results indicate that even high levels of perceived personal relevance do not significantly attenuate the effect of symbols, which entails that the boundaries of persuasion and manipulation through branding are wider than expected.*
 
@@
 
-Public Administration scholarship has shown a growing interest in public sector branding, and its potency to influence citizens' perceptions and direct their behaviour [@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015].
-Congruently, recent behavioural studies established that symbolic, brand elements entangled in government communications (e.g.
-brand names, logos, colors and figures) can have a positive emotional effect on citizens, which leads them to view public organizations and their policies and services more favourably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
-This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade or so, in part due to the vast expansion of ditigal communication and social media [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
+Public Administration scholarship has shown a growing interest in public sector branding, and its potency to influence citizens' perceptions and direct their behavior [@eshuis_2012; @marland_2016; @marland_2017; @zavattaro_website_2018; @sataen_2015].
+Congruently, recent empirical studies established that symbolic, brand elements entangled in government communications (e.g.
+brand names, logos, colors and figures) can have a positive emotional effect on citizens, which leads them to view public organizations and their policies and services more favorably [@marvel_2015a; @karens_2016; @alonbarkat_2017; @teodoro_2018].
+This growing scholarly interest corresponds with the overall increase in the use of branding practices by public-sector organizations over the past decade or so, in part due to the expansion of digital communication and social media [@eshuis_2012; @marland_2017; @mickoleit_2014; @mergel_2013].
 
-The ability of government organizations to modify citizens' attitudes via such symbolic communications can be perceived favorably, insofar as it mitigates citizens' distrust in organizations and underevaluation of their performance.
+The ability of government organizations to modify citizens' attitudes via such symbolic communications can be perceived favorably, insofar as it mitigates citizens' distrust in organizations and undervaluation of their performance.
 Accordingly, symbolic communications, as opposed to the delivery of mere factual information and substantive arguments, may enable organizations to overcome citizens' negative prior beliefs and biases against the public sector [@marvel_2015a; @marvel_2015; @hvidman_2016; @hvidman_2019].
 Nonetheless, this form of persuasion is also highly problematic.
-Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather then on uncontious emotive responses.
+Normatively, we expect citizens in a democratic society to form their opinions about their government based on their critical thinking, rather than on unconscious emotive responses.
 A yet more serious concern regards the potency of symbolic communication to compensate for organizations' poor performance, poorly planned policy plans and logically unpersuasive explanations, as indicated by previous studies [@alonbarkat_2017, AUTHOR].
 Congruently, government branding can yield a misalignment between citizens' positive view and the "real world", which would undermine governments' democratic accountability and responsiveness.
-Moreover, government agencies and/or politicians controlling them could use branding and symbolic communication strategically as an instrument of propaganda, seeking to manipulate public opinion and mitigate justified public criticism of agencies' failures.
+Moreover, government agencies and/or politicians controlling them could exploit branding and symbolic communication as an instrument of propaganda, and seek to manipulate public opinion and mitigate justified public criticism of agencies' failures.
 
@@
 These concerns necessitate a better theoretical understanding of the boundaries of governments' persuasion (and possibly manipulation) of citizens through symbolic communication, which would enable us to asses more effectively the scope of the risk that these practices pose for democracy.
-In line with this motivation, this study focuses of an importnant potential limitation that regards the perceived personal relevance of the policy issue.
+In line with this motivation, this study focuses of an important potential limitation that regards the *perceived personal relevance of the policy issue*.
 I explore whether the effect of symbolic elements in communications is restricted to policy issues that are not perceived by citizens as having a significant consequence for their personal lives, or rather that citizens are similarly susceptible to persuasion via branding even with regard to such personally relevant issues.
 This moderating factor is particularly important, since we tend to expect these affected groups to pay more attention to government actions that concern their interests, and to hold them to account for their consequences to a greater extent.
-That expectation can be supported, theoretically, by the social psychology theory Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
+That expectation can be supported, theoretically, by the social psychology Elaboration Likelihood Model (ELM) [@petty_1986; @petty_2011].
 The model postulates that the more people perceive the communication as personally relevant, the more inclined they are to scrutinize its message, and accordingly the less likely they are to rely on peripheral, symbolic elements.
 
-Employing a survey experiment, I test this latter theoretical expectation in the context of the Israeli Environment Protection Ministry, and its policy plan for reducing the air pollution in a specific geographical area -- the Haifa Bay.
+Employing a survey experiment, I test this latter expectation in the empirical context of the Israeli Environment Protection Ministry, and its policy regarding air-pollution in a specific area -- the Haifa Bay.
 The research sample (*n* = `r SVIVA2_01 %>% nrow()`) consists of citizens residing in the polluted area, matched with residents of other cities in the center of the country that are not exposed to high levels of air-pollution.
 I present all participants a policy plan regarding the air-pollution in the Haifa Bay area, while experimentally varying both its appearance (familiar symbolic elements from the Ministry's communications versus two control groups) and substantive information (logically persuasive versus unpersuasive policy plans).
-I examine the effects of these manipulations on participants' trust in the policy plan accross the two areas, and test whether residents of the polluted area are less affected by familiar symbolic elements (and more affected by the differences in substantive arguments).
+I examine the effects of these manipulations on participants' trust in the policy plan across the two areas, and test the hypothesis that residents of the polluted area are less affected by familiar symbolic elements (and more affected by the differences in substantive arguments).
 I further supplement this observational comparison between the areas with an experimental treatment for the perceived personal relevance of the policy, and with additional robustness tests.
@@
 19].
-Branding, therefore, can be considerred a form of symbolic communication.
+Branding, therefore, can be considered a form of symbolic communication.
 In practice, symbolic elements that are strategically designed to evoke positive emotions and associations, can be found in almost every government communication with citizens.
 
-Symbolic elements entangled in communications can affect citizens' attitudes through a psychological mechanism of evaluative conditioning, whereby the positive associations triggerred by the symbols are unconsciously transferred to the public organization [@alonbarkat_2017; @dehouwer_2012].
+Symbolic elements entangled in communications can affect citizens' attitudes through a psychological mechanism of evaluative conditioning, whereby the positive associations triggered by the symbols are unconsciously transferred to the public organization [@alonbarkat_2017; @dehouwer_2012].
 So for instance, when a public organization uses a celebrity endorser in a public campaign, the positive connotations for the celebrity (e.g.
 physically attractive, funny, talented) can be extended to the organization, which would lead citizens to also view the organization and its actions more favorably.
-This mechanism is considerred a primitive form of persuasion which requires very little cognitive effort, as opposed to persuasion resulted by thoughtful consideration of substantive arguments.
-Thus, the question of under which circumbstances are citizens' more/less susceptible to persuasion via branding, is linked to a more general discussion in social psychology regarding the relations between different psychological processes of persuasion through communication, and the determinants and moderators of these different processes.
+This mechanism is considered a primitive form of persuasion which requires very little cognitive effort, as opposed to persuasion resulted by thoughtful consideration of substantive arguments.
+Thus, the question of under which circumstances are citizens' more/less susceptible to persuasion via branding, can be linked to a more general discussion in social psychology regarding the relations between different psychological processes of persuasion through communication, and the determinants and moderators of these different processes.
 
@@
 They are more likely to differentiate between strong and weak arguments, and would be persuaded mainly by strong, logically persuasive arguments.
-As for those who are located at the low end of that continuum, also called "peripheral route", persuasion may occur mainly through processes that require little ammount of thinking, such as evaluative conditioning.
-Another prominent example for peripheral route processing is people's reliance on the message source as a heuristic cue [@james_2017a].
+As for those who are located at the low end of that continuum, also called "peripheral route", persuasion may occur mainly through processes that require little amount of thinking, such as evaluative conditioning.
+Another prominent example for peripheral route processing is people's reliance on message source as a heuristic cue [@james_2017a].
 When people are located between the two ends of the continuum, a mixture of these persuasion processes will operate.
@@
 In any given situation, the position of people along that continuum (and accordingly the dominant type of processing) would be determined by their motivation and ability to scrutinize the message.
-The more motivated people are to elaborate on the message and the more capable they are of doing so, the more likely they are to focus on the substative arguments, and likewise the less susceptible they are to persuasion via peripheral route processes.
+The more motivated people are to elaborate on the message and the more capable they are of doing so, the more likely they are to focus on the substantive arguments, and likewise the less susceptible they are to persuasion via peripheral route processes.
 ELM literature has pointed to a variety of factors that may shape people's motivation and ability to think about a message, and accordingly affect their inclination to be persuaded either by the arguments or by peripheral cues.
@@
 
-[^footnote_symbols_arguments]: It should be noted that in certain cases, symbolic elements can be also regarded as arguments.
-For instance, slogans normally convey symbolic meaning, but also contain a substantive message.
+[^footnote_symbols_arguments]: In certain cases, symbolic elements can be also regarded as arguments. For instance, slogans normally convey symbolic meaning, but also contain a substantive message.
 
@@
 While EPM has claimed that its programs have been effective and led to a significant reduction in air-pollution levels, local residents, professionals and other public agencies have remained highly concerned about the issue, and  accordingly it remained high on the public agenda [@statecomptrollerofisrael_2019].
-Specifically, the issue received much media and public attention in 2015-2016, following a series of reportings and media publications about the health consequences of the air-pollution to Haifa Bay residents.
+Specifically, the issue received much media and public attention in 2015-2016, following a series of reports and media publications about the health consequences of the air-pollution to Haifa Bay residents.
 In 2015, the Ministry of Health published statistical data indicating that Haifa Bay residents experience significantly higher rates of cancer and asthma, compared to other areas of the country.
-Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly highlighted a particular finding that babies in the Haifa Bay are born with "smaller heads" [@koriel_website_2016; @rinat_website_2016; @rivlin_website_2016].
+Thereafter, in 2016, media reporters revealed the interim results of a large epidemiological study, establishing a link between air-pollution in the Haifa Bay and certain types of cancer, as well as abnormal measurements of newborn babies and growth curves of infants.[^footnote_epidemiological_study] The media reports of that study repeatedly highlighted a particular finding that babies in the Haifa Bay are born with "smaller heads" [e.g.
+@koriel_website_2016; @rivlin_website_2016].
 These publications, and others, caused much panic among the local population, and especially among young parents.
@@
 [^footnote_epidemiological_study]: The epidemiological study was originally sponsored by Ministry of Health.
-The study, which was  conducted by researchers from Haifa University, was planned to be conducted over five years, between 2015-2020.
+The study was planned to be conducted over five years, between 2015-2020.
 The findings, which leaked to the media, regarded the interim results of the first year of the study.
@@
 
-While comparing those residing in the Haifa Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation - it represents an observational comparison.
+While comparing those residing in the Haifa Bay to others enables me to examine the moderating effect of perceived personal relevance, it still has an important limitation -- it represents an observational comparison.
 The differences in personal relevance can be theoretically confounded by unobserved covariates, that cannot be effectively controlled in the analyses.
@@
 The socioeconomic characteristics of these selected cities are summarized in the supplementary appendix (section 1).
-I further searched relevant EPM documents and news websites and confirmed that there no particular reporting about high air-pollution levels in the three center cities.
+I further searched relevant EPM documents and news websites and confirmed that there were no reports of high air-pollution levels in the three center cities.
 
 *Second*, in addition to the policy regarding the Haifa Bay air-pollution, I also included in the experiment a second policy plan that is expected to be perceived by the two groups as equally relevant.
-For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling*.
-The comparison between the two EPM policies is intended to confirm that respondents’ divergent responses to symbolic elements in the communication of the first policy, if found, are attributed to differences in perceived personal relevance, and not to other covariates.
-I henceforth refer to these two policy plans as "Haifa Bay air-pollution" and "recycling".
+For this purpose, I selected a policy plan of EPM that regards *reducing domestic waste and increasing recycling* (henceforth: recycling policy).
+The comparison between the two policies is intended to confirm that respondents’ divergent responses to symbolic elements in the communication of the Haifa Bay air-pollution policy, if found, can be attributed to differences in perceived personal relevance, and not to other covariates.
 *Third*, in addition to the observational comparison between the two areas, I also included an experimental manipulation aimed at enhancing the perceived personal relevance of the air-pollution policy among the Haifa Bay residents.
@@
 [^footnote_qiryat-Hayiim]: Qiryat-Hayiim is considered a neighborhood within the jurisdiction of Haifa, although it is geographically separated from the rest of the city, and people tend to distinguish it, informally.
-
-<br>
 
@@
 The survey experiment was conducted online through Qualtrics Survey Software.
-The online survey link was sent by iPanel between 28.1-1.2.2018.
+The online survey link was sent by *iPanel* between 28.1-1.2.2018.
 A total of `r N_0` respondents completed the survey (a response rate of `r round((N_0/5077)*100,1)`%).
@@
 
-[^footnote_unfiltered_sample]: In the supplementary appendix, I replicate the main models on the unfiltered sample, with no significant change to the results (section 7).
+[^footnote_unfiltered_sample]: In the supplementary appendix (section 7), I replicate the main models on the unfiltered sample, with no significant change to the results.
 
 The survey was presented to the participants as an academic study about citizens' attitudes regarding environmental policies in general.
-After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: relevance manipulation).
+After a set of pre-manipulation questions, all subjects, regardless of their area of residence, were randomly assigned to treatment and control conditions of perceived personal relevance (hereafter: *relevance manipulation*).
 Subjects in the relevance treatment group were asked three questions about their perceptions of environmental policy in general.
-They were then asked to state their area  and locaity of residence, and to describe, in their own words, the most disturbing environmental issue in their area.
+They were then asked to state their area and locality of residence, and to describe, in their own words, the most disturbing environmental issue in their area.
 These questions were designed to prime those residing in the Haifa Bay area to think about the personal relevance of air-pollution in their area.[^footnote_relevance_manipulation] Subjects in the relevance control group were asked equivalent questions about their field of occupation.
@@
 Yet, I focus here on the moderation of the relevance manipulation on Haifa Bay citizens' responses to the air-pollution policy.
+In additional analyses, I also examine the moderating effect of the relevance treatment for center subjects’ responses to Haifa Bay air-pollution policy, as well as for the recycling policy (for the entire sample).
 
@@
 They were informed that these plans were obtained from EPM's annual work plan for the following year.
-The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: symbols manipulation): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
+The participants were randomly assigned to one of three conditions of symbolic elements in the communication (hereafter: *symbols manipulation*): treatment ("real symbols"), control-"no symbols" and control-"fake symbols".
 In the real symbols condition, the two policies are displayed with three symbolic brand elements, which have been used in EPM's public communications, and became widely recognized by the public.
@@
 
-In addition, I also included a manipulation of the argument quality of the information in the communication about the policy plan (hereafter: information manipulation).
+In addition, I also included a manipulation of the argument quality of the information in the communication about the policy plan (hereafter: *information manipulation*).
 Per each policy, subjects were randomly allocated to one of two conditions of information: strong policy (i.e.
@@
 Each subject was exposed to two policy plans, one strong and one weak, displayed in a random order.
-For instance, a subject who first received a strong Haifa Bay air-pollution policy plan, later received the weak recycling policy plan, and vice versa.
 The information in the strong policy plan condition was taken from the EPM’s real work plan and from other official sources, whereas the information in the weak policy plan was fictional, and deliberately designed to create a poor policy plan, which is incompatible with achieving the policy goals.[^footnote_reliability_information_manipulation] The full texts of the weak and strong conditions for the two policy plans is displayed in **Appendix B**.
@@
 After the trust questions of the second policy, the subjects were asked additional questions about the two policies, including the degree to which they perceive each of them as personally relevant.
-These questions were followed by an Instructional Manipulation Check (IMC) item, intended to assess participants’ diligence.
+These questions were followed by an Instructional Manipulation Check item, intended to assess participants’ diligence.
 The last sections included a set of demographic questions including questions about their place of residence and work, and manipulation checks for participants' familiarity with the real symbols.
@@
 The power estimations are reported in details in the supplementary appendix (Section 4).
-
-<br>
 
@@
 
-The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for Haifa Bay air-pollution policy, and `r alpha_waste_trust` for the recycling policy).
+The outcome variable, citizens' trust in policy, is measured in the survey using a composite index of six items (Cronbach’s alpha = `r alpha_air_trust` for Haifa Bay air-pollution policy, and `r alpha_waste_trust` for recycling policy).
 This scale was adopted with modifications from validated trust scales used by previous public-administration studies [@karens_2016; @grimmelikhuijsen_2017; @grimmelikhuijsen_2018].
@@
 Living in Haifa Bay area was coded according to respondents’ reporting of residence, work or studying in one of the Haifa Bay cities.
-To confirm the empirical assumption that the Haifa Bay air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on ["Reducing the air-pollution in the Haifa Bay" / “reducing waste and increasing recycling”] is personally relevant to you?" (1="very little"; 7="very much").
+To confirm the empirical assumption that the Haifa Bay air-pollution policy (but not the recycling policy) is perceived as more personally relevant by Haifa Bay residents compared with center residents, respondents were asked, after the outcome variable items: "To what extent did you feel that the policy on...
+is personally relevant to you?" (1="very little"; 7="very much").
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the distributions of the latter items across the two areas.
@@
 As for the relevance manipulation, data suggests that assignment to relevance priming questions did not increase Haifa Bay respondents' perceptions of personal relevance of the air-pollution policy.
-The Haifa Bay participants assigned to the treatment group reported sightly lower level of personal relevance on average, yet these differences are not statistically significant (Cohen's D = `r relevance.exp.d[["estimate"]] %>% round(2)` [`r relevance.exp.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.exp.d[["conf.int"]][["upper"]] %>% round(2)`], *t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
+The Haifa Bay participants assigned to the treatment group reported slightly lower level of personal relevance on average, yet these differences are not statistically significant (Cohen's D = `r relevance.exp.d[["estimate"]] %>% round(2)` [`r relevance.exp.d[["conf.int"]][["lower"]] %>% round(2)`,`r relevance.exp.d[["conf.int"]][["upper"]] %>% round(2)`], *t* = `r relevance.exp.t[["statistic"]] %>% round(3)`, *p*=`r round(relevance.exp.t[["p.value"]],3)`).
 This limitation should be kept in mind when interpreting the results regarding this manipulation.
@@
 `r table.x=table.x+1`**Tables `r table.x`** compares between the different conditions, within each of the two areas, on demographic variables and pre-manipulation covariates.
-These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The table furter suggests that the samples of Haifa Bay and Center residents are fairly balanced with regard to gender, trust in national-level government ministries and interest in environmental issues.
+These comparisons confirm that these random assignments yielded fairly balanced groups.[^footnote_balancing_groups_exceptions] The table further suggests that the samples of Haifa Bay and Center residents are fairly balanced with regard to gender, trust in national-level government ministries and interest in environmental issues.
 Yet, Haifa Bay respondents are somewhat older, more educated, and have more left-wing ideology.
@@
 `r figure.x=figure.x+1`**Figure `r figure.x`** shows the means and distributions of the outcome variable across the different experimental conditions of symbolic elements and information, and across the two areas.
-The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
-Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`-`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]) %>% abs() %>% round(.,3)`).
+The real symbols condition (in the left panel) has a positive and significant main effect on trust in that policy plan compared with the no symbols condition (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.no[["conf.int"]][2]*-1) %>% round(.,2)`,`r (t.symbols.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+That effect amounts to `r (main.symbols$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`,`r (t.symbols.no[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`].
+Subjects who saw the real symbols also reported, on average, greater trust in the policy, compared with those who received fake symbols, yet these differences are not significant at the 95% level (*diff* = `r (main.symbols$contrasts %>% tidy() %>% .[3,"estimate"]) %>% max(.) %>% round(.,2)` [`r (t.symbols.fake[["conf.int"]][1]) %>% round(.,2)`,`r (t.symbols.fake[["conf.int"]][2]) %>% round(.,2)`], *t* = `r t.symbols.fake[["statistic"]][["t"]] %>% abs() %>% round(.,3)`, *p* = `r (t.symbols.fake[["p.value"]]) %>% abs() %>% round(.,3)`).
 The increase in the lower bound of the box in the real symbols shows that real symbols reduced to a great extent the number of participants who reported very low trust score.
@@
 As shown in the middle panel, the main effect of the weak information condition is negative and significant (*diff* = `r (main.info %>% .[2,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.info[["conf.int"]][2]) %>% round(.,2)`-`r (t.info[["conf.int"]][1]) %>% round(.,2)`], *t* = `r t.info[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
-That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
-Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the Haifa Bay air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`-`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
+That effect amounts to `r ((main.info %>% .[2,"estimate"]*-1)/sd.air) %>% max(.) %>% round(.,2)` SDs [`r (t.info[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`,`r (t.info[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`].
+Finally, as presented in the right panel, participants from Haifa Bay reported significantly lower levels of trust in the Haifa Bay air-pollution policy, compared to center participants (*diff* = `r (main.areas %>% .[2,"estimate"]*-1) %>% max(.) %>% abs() %>% round(.,2)` [`r (t.areas[["conf.int"]][2]) %>% round(.,2) %>% abs()`,`r (t.areas[["conf.int"]][1]) %>% round(.,2) %>% abs()`], *t* = `r t.areas[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).
 Descriptively, `r ((filter(SVIVA2_01_haifa,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_haifa))*100)%>%round(1)`% of Haifa Bay subjects have a trust-index score lower than 4, the scale's middle point (compared with `r ((filter(SVIVA2_01_center,TRUST_air_INDEX<4) %>% nrow())/(nrow(SVIVA2_01_center))*100)%>% round(1)`% of the center subjects).
@@
 `r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the conditional effects of the manipulations, within each of the two areas.[^footnote_raw_means] As for the effect of the symbols manipulation (displayed in the left panel), the results show that the symbols had a greater positive effect on those living in the polluted Haifa Bay area.
-Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`-`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group.
+Their exposure to the real symbols increased their trust in the policy by `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[1,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.no.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`,`r (t.symbols.no.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`] compared with the no symbols group, and `r (cond.symbols.haifa$contrasts %>% tidy() %>% .[3,"estimate"] %>% max(.)/sd.air) %>% abs() %>% round(2)` SDs [`r (t.symbols.fake.haifa[["conf.int"]][1]/sd.air) %>% abs() %>% round(2)`,`r (t.symbols.fake.haifa[["conf.int"]][2]/sd.air) %>% abs() %>% round(2)`] compared to the fake symbols group.
 The center participants who saw the real symbols also reported, on average, higher levels of trust in the policy, compared with the two control groups.
@@
 I further examined the interactions between the manipulations and the two areas via a series of multiple linear regression models, presented in `r table.x=table.x+1`**Table `r table.x`**.
-I regress trust in Haifa Bay air-pollution policy on the manipulations (Model 1.1), then I add the areas (Model 1.2) and the interaction between them (Model 1.3).
+In Model 1.1 I regress trust in Haifa Bay air-pollution policy on the manipulations, then I add the areas and the interaction between them (Models 1.2, 1.3).
 In Model 1.4, I test the robustness of the interaction model by controlling for individual-level covariates.[^footnote_control_variables] In all regression models, I use robust standard errors to adjust for heteroskedacity.[^footnote_heteroskedacity] The results of these models are largely consistent with the raw findings presented above.
-In Models 1.3, 1.4 the interactions between living in the center and the real symbols are negative but and significant at the 90% level, and the interactions with the weak information are insignificant.
-A comparison between models 1.2 and 1.3 via anova reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
+In Models 1.3, 1.4 the interactions between living in the center and the real symbols are negative and significant at the 90% level, and the interactions with the weak information are insignificant.
+A comparison between models 1.2 and 1.3 via ANOVA reveals that adding these interactions do not significantly improve the model fit (*F(`r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(df) %>% .[2,] %>% max()`*) = `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(statistic) %>% .[2,] %>% max() %>% round(2)`, *p*= `r anova(mod_air_1.2,mod_air_1.3) %>% tidy() %>% select(p.value) %>% .[2,] %>% max() %>% round(2)`).
 
@@
 In summary, the findings with regard to the Haifa Bay air-pollution policy indicate, tentatively, that higher levels of perceived personal relevance of the communication neither attenuate the positive effect of brand elements entangled in communications, nor enhances citizens' attention to their substantive content.
-Still, as discussed in the methodology section, this analysis is based on an observational comparison, and hence a concern of endogeneity cannot be entirely ruled.
+As discussed in the methodology section, this analysis is based on an observational comparison, and hence a concern of endogeneity cannot be entirely ruled.
 Accordingly, the null findings regarding the interactions between the areas and the manipulations can be resulted by other, unobserved differences between the two populations.
@@
 
-`r table.x=table.x+1`**Table `r table.x`** replicates the models in **Table `r table.x-1`** for the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
+`r table.x=table.x+1`**Table `r table.x`** replicates the above models for trust in the recycling policy (*Mean* = `r SVIVA2_01_comb%>%summarise(mean(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *SD* = `r SVIVA2_01_comb%>%summarise(sd(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`, *Median* = `r SVIVA2_01_comb%>%summarise(median(TRUST_waste_INDEX,na.rm=T))%>%max() %>% round(2)`).
 Overall, these models reveal relatively similar patterns to those found in the air-pollution policy.
@@
 The fact that similar patterns are observed across the these policies further weakens the hypotheses regarding the moderating role of personal relevance.
-It also rules out a possible argument that greater relevance enhances (rather then reduces) the effect of symbols.
+It also rules out a possible argument that greater relevance enhances (rather than reduces) the effect of symbols.
 If this was the case, then we should not have found a similar interaction in relation to the recycling policy.
@@
 The weaker effect of the real symbols can be partly explained by the fact that I used a different celebrity campaign image for this policy, which was less familiar compared with the image presented for the Haifa Bay air-pollution policy.
-The main effect of weak information (as depicted from Model 2.1) ammounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
+The main effect of weak information (as depicted from Model 2.1) amounts to `r (diff5/sd.waste) %>% round(3)` SDs [`r ((diff5-1.96*se5)/sd.waste) %>% round(3)`-`r ((diff5+1.96*se5)/sd.waste) %>% round(3)`].
 
@@
 In all these models, the coefficient of the relevance treatment is negative but far from significance.
-The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the incerase in trust due to the appearance of the symbols and those who did not were slightly smaller.
-However, these interaction coefficients are far from significance and relatively weak (ranging between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).
-The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (ranging between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1] Hence, these analyses also do not lend sufficient support for the hypotheses.
+The interactions between the real symbols and the relevance manipulation are negative, which indicates that among those who were primed to think about the personal relevance of the air-pollution problem, the increase in trust due to the appearance of the familiar symbols was slightly smaller.
+However, these interaction coefficients are far from significance and relatively weak (estimates range between `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="SYMBOL_t1") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).
+The interactions between the relevance treatment and weak information manipulations are also in the expected direction, but again insignificant (estimates range between `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/sd.air.haifa) %>% round(2)` SDs, and attenuating approximately `r ((mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.3 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`--`r ((mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak:RELEVANCE_exp") %>% select(estimate) %>% max(.) %>% abs())/(mod_relevance_1.2 %>% tidy() %>% filter(term=="INFORMATION_weak") %>% select(estimate) %>% max(.) %>% abs())*100) %>% round(0)`% of the effect in the control group).[^footnote_relevance_manipulation_1] Hence, these analyses also do not lend sufficient support for the hypotheses.
 
@@
 Second, these analyses have more limited statistical power, compared to the observational comparisons, since they are restricted only to the sample of Haifa Bay subjects.
-Still, we can assess that even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols can be estimated as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`] (based on Model based on Model 3.2).
-Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] Overall, this indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area were positively affected, at least to some degree, by familiar symbols of the ministry.
+Still, based on the interactions in Model 3.2, we can assess that even if the relevance manipulation does attenuate the effect of the real symbols, their effect on that group compared with the no symbols can be estimated as `r (diff5/sd.air.haifa) %>% round(3)` SDs [`r ((diff5 - 1.96*se5)/sd.air.haifa) %>% round(3)`,`r ((diff5 + 1.96*se5)/sd.air.haifa) %>% round(3)`].
+Remarkably, even when restricting the relevance treatment group to those who mentioned the air-pollution as an acute environmental issue in their area of residence (`r air.content.percent.haifa %>% round(0)`% of that group, *n* = `r SVIVA2_01_haifa.relevance.aircontent %>% nrow()`), the real symbols still had a roughly similar positive effect on trust in the policy plan, compared with the no symbols (*diff* = `r (main.symbols.relevance.aircontent$contrasts %>% tidy() %>% .[1,"estimate"]*-1) %>% max(.) %>% round(.,2)` [`r (t.symbols.relevance.aircontent.no[["conf.int"]][2]*-1) %>% round(.,2)`-`r (t.symbols.relevance.aircontent.no[["conf.int"]][1]*-1) %>% round(.,2)`], *t* = `r t.symbols.relevance.aircontent.no[["statistic"]][["t"]] %>% abs() %>% round(.,3)`).[^footnote_relevance_significance_fakesymbols] Overall, the data indicates that even Haifa Bay residents that were reminded about the relevance of the air-pollution to their lives area, were positively affected by familiar symbols of the ministry, at least to some degree.
 
@@
 *Third*, I replicated the analyses on the unfiltered sample.
-These additional analyses are consistent with the analyses presented in the paper, and do not provide evidence that greater levels of perceived personal relevance attenuates the effect of symbols.
+All these additional analyses are largely consistent with the analyses presented in the paper, and do not provide evidence that greater levels of perceived personal relevance attenuates the effect of symbols.
 
@@
 I theorize, tentatively, that the direction of the interaction depends on whether or not the symbolic associations are related to the relevant group identities.
-When the symbols are not strongly linked to identities of specific groups having strong prior positions on the policy or the organization, as in this case, symbols would attenuate the influence of the prior beliefs on people's judgements.
-Conversely, when symbolic associations activate group identities and make them more salient, they may enhance the effect of dominant positions embedded in them, and increase polarization between parties [@teodoro_2018].
+When the symbols are not strongly linked to identities of specific groups having strong prior positions on the policy or the organization, as in this case, symbols would *attenuate* the influence of the prior beliefs on people's judgements.
+Conversely, when symbolic associations activate group identities and make them more salient, they may *enhance* the effect of dominant positions embedded in them, and increase polarization between parties [@teodoro_2018].
 An interaction between symbols and citizens' prior beliefs may also suggest that symbols can affect citizens' susceptibility to motivated reasoning and biased processing of new information [@taber_2006; @christensen_2018; @baekgaard_2016; @james_2017a].
@@
 Future studies may put these findings to further test by exploring cases of air-pollution in other locations, as well as by exploring cases of other environmental policies, and other domains.
-Additionally, I cannot entirely rule out the possibility that the differences in personal relevance between the two geographic areas are confounded with other differences associated with people's beliefs about the subject and the agency.
+Additionally, despite the multiple comparisons presented, I still cannot entirely rule out the possibility that the differences in personal relevance between the two geographic areas are confounded with other differences associated with people's beliefs about the subject and the agency.
 Future studies may conduct more rigorous investigations through natural experimental or quasi-experimental designs that could take advantage of particular cases of citizens' random allocation to varying levels of personal relevance.
@@
 Alongside the benefits of this instrument in mitigating citizens' distrust, it also has the potency to yield a distorted, emotive, overoptimistic view of government organizations and their policies, which may undermine basic democratic accountability mechanisms.
-These concerns become even more prevalent and serious in the age of digital communication and artificial intelligence technologies, which enable organizations to engage with targeted audiences much more easily, and to adapt messages and symbols to groups and individuals in a manner that would trigger their emotions more effectively.
+These concerns become even more prevalent and serious in the age of digital communication and artificial intelligence technologies, which enable organizations to engage with targeted audiences more easily, and to adapt messages and symbols to groups and individuals in a manner that would trigger their emotional responses more effectively.
 For good or for ill, citizens are affected by the emotional connections and associations of symbols.
